### 2020-09-02 README.Rmd
Created README skeleton

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aracari

<!-- badges: start -->
<!-- badges: end -->

The goal of aracari is to ...

## Installation

You can install the released version of aracari from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("aracari")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("javirudolph/aracari")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(aracari)
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

### 2020-09-08 appendixA/appendixA.Rmd
copied paper directory from previous repo

---
title: "Appendix A: Model fitting and selection for distances moved per minute"
output:
  pdf_document:
    toc: true
bibliography: "../paper/mybibfile.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(fitdistrplus)
library(ggpubr)

theme_set(theme_bw())
```

```{r functions}

# Extract parameters from fitted distributions to the data
build.fits.df <- function(x){

  nm <- deparse(substitute(x))

  x %>% 
  map(., `[`, c("estimate", "sd", "loglik", "n")) %>% 
  map(as_tibble) %>% 
  bind_rows()
}

```

```{r data}
# Get the data loaded. We are removing the one value with zero since it won't allow fitting. Also, zero represents no movement, but we will use perching time for that.

df <- readRDS("outputs/newpointlocs.RDS") %>%
  filter(mpm != 0) %>%
  ungroup() %>%
  mutate(Bird_ID = paste0("B", Bird_ID),
         sqR2n = sqrt(R2n))

dist.used <- c( "exp", "gamma", "weibull", "lnorm")

param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")

```

# Population vs Individual levels
## Population level
We fit the probability distributions to all the data, so it is population level. We compare fits visually with a qqplot. It is evident with this plot that the lognormal distribution is problematic at the tails and shows a significant overestimation. All the other distributions underestimate the real values, but it seems like the Weibull is closer to the diagonal.

```{r poplevel}

pop <- lapply(dist.used, function(x){fitdist(df$mpm, distr = x)})
qqcomp(pop, plotstyle = "ggplot") +
  coord_equal() +
  geom_point(shape = 16, alpha = 0.5)

prms.df <- build.fits.df(pop) %>% 
  mutate(param = param,
         dist = dist,
         data = "pop")

```

### 2020-09-08 paper/paper.Rmd
copied paper directory from previous repo

---
title: "Individual Variation in Animal Movement and Effects on Seed Dispersal Distance"
author:
- Javiera Rudolph
- Jose Miguel Ponciano
- Flavia Montano-Centellas
- Kimberly Holbrook
- Bette Loiselle
abstract: |
  Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms. In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion. Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds beyond the capacity of wind or other abiotic processes. In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance dispersal. We apply these methods to empirical data sets that contain locations for an aracari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*. We combine animal movement data and gut retention time to simulate *Virola* seed dispersal. This approach showed that there is significant variation in individual aracari movement patterns which directly influence the estimated number of long-distance dispersa events for *Virola* seeds. We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
linenumbers: yes
bibliography: mybibfile.bib
layout: 3p
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = FALSE)
```

\newpage
# Introduction
A main goal of ecologists and evolutionary biologists is to document and predict the structure and dynamics of ecological systems. Although most of our current understanding of ecological systems is based on the average patterns observed in nature, understanding variability and its consequences in ecological processes has recently raised the interests of researchers [@benedetti-cecchi_importance_2003; @inouye_importance_2005]. Variation is now considered a property of ecological systems that might contain as much ecological information as do averages and regularities in nature [@benedetti-cecchi_importance_2003; @violle_return_2012].
Individual variation, i.e. the possibility for individuals within a population to present different ecological strategies or traits [@violle_return_2012], has been widely discussed in ecology and evolutionary biology. In evolutionary biology the acknowledgement that individuals with different traits might vary in their fitness and survival under natural selection pressures dates back to Darwin’s seminal ideas [@darwin_origin_1859]. Today, it is widely recognized that individual variation plays a key role in the evolution of species and clades, and the relevance of individual variation in the performance of populations and species facing current threats (e.g. climate change, fragmentation and habitat loss) is a growing field of research [@forsman_inter-individual_2016]. In ecology, individual variation is often mentioned as a mechanism for populations to reduce competition pressure [@bolnick_ecological_2010; @araujo_ecological_2011]. Based on the niche complementarity principle, phenotypically different individuals will compete less strongly than more similar individuals [@bolnick_why_2011], thus individual variation would act as a release from intra- and interspecific competition at a local scale. Despite the well recognized importance of individual variation in ecological and evolutionary processes, ecological theory has emphasized interspecific variation [@violle_return_2012].
Not surprisingly, the role of individual variability on the outcome of species interactions has also been poorly studied; most models of species interactions assume that all conspecific individuals are equivalent and interchangeable [@bolnick_why_2011]. Individuals, however, differ in several aspects that will affect their interactions with other species. This variability makes individuals non-interchangeable from the perspective of interacting patterns [@bolnick_ecology_2003; @gonzalez-varo_labile_2016]. The consequences of individual variability in interspecies interactions can even have cascading effects, going beyond from the species-species level to the community and ecosystem level [@post_intraspecific_2008; @wolf_animal_2012].

Seed dispersal mutualisms may be a particularly attractive system to study the impacts of incorporating individual variation to understanding the importance of such variation to dispersal outcomes. Seed dispersal is one of the most critical stages in plant life history – it results in a spatial pattern of seed deposition which acts as a template that will define the distribution of plants and, consequently, community structure [@howe1982ecology; @nathan_spatial_2000; @russo_incorporating_2006]. In seed dispersal mutualisms, animals provide the dispersal services while rewarding from fruit resources they consume. Plants produce fleshy fruits to attract and reward mutualist animals and rely on the behavior of the disperser to transport their propagules [@nathan_spatial_2000]. The spatial patterns of seed deposited by disperser vectors will determine the probability of seed survival and recruitment, acting upon post-dispersal processes such as density-dependent survival and colonization [@howe2004seed]. Therefore, at a local scale, seed dispersers will determine whether plant species scape from density-dependence processes [@comita2014testing], whereas at a larger scale, they can determine how quickly plants can cope with habitat and climate shifts [@ibanez2006predicting; @russo_incorporating_2006].

From the plant perspective, not all seed disperser species provide with the same seed dispersal service, and often relatively few disperser species can have disproportionate effects on seed dispersal [@schupp1993quantity; @jordano2007differential; @schupp_seed_2010; @loayza2014seed]. Frugivores might differ on their selection of plants/fruits for consumption, in their treatment of seed while ingesting and manipulating the fruits, in their processing of seeds if ingested and in the distance where they will discard the seeds [@schupp1993quantity; @schupp_seed_2010; @cortes_integrating_2013]. Each one of these stages of the seed dispersal process will have strong consequences on the spatial seed shadow provided by each seed dispersal vector [@jordano2007differential; @carlo2014directness]. Besides inter-specific differences among dispersal vectors, there is a recent recognition of the potential role of differences among individuals in the resulting seed dispersal they provide [@bolnick_ecology_2003; @gonzalez-varo_labile_2016]. Including individual variation in traits (morphological, behavioral and physiological) in seed dispersal studies, can provide new insights into the relative role of different dispersal vectors on seed deposition and ultimately, vegetation structure [@gonzalez-varo_labile_2016]. In a recent review, Zwolak (2017) summarized the types of intraspecific variation in seed-dispersing animals that might affect the resulting seed dispersal service individuals provide, highlighting differences in sex, size or age (ontogenetic shifts), individual specialization and behavioral syndromes as the most important variation types. Incorporating these intrinsic traits into seed dispersal models may lead to more mechanistic understanding of seed dispersal, allow to build more accurate predictive frameworks of dispersal outcomes [@russo_incorporating_2006] and to identify links between characteristics of dispersal agents and the seed dispersal they provide [@zwolak_how_2018].

Differences in behavior among individuals (i.e. behavioral syndromes sensu [@sih2004behavioral]) can have remarkable consequences on ecological and evolutionary processes [@wolf_animal_2012]. For vertebrate dispersed plants, animal behavior will inﬂuence seed shadows and few species, or even individuals, might provide unique, high value dispersal services by moving farther distances from parental plants [@schupp_seed_2010]. Long distance dispersal (LDD) events are crucial to reaching suitable sites to germinate and establish and to colonize new habitats [@nathan2006long]. Furthermore, rare events (often overlooked) are critical for dispersal and might have a large effect on resulting plant demography [@loayza2014seed]. Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patters of seed dispersal.

The effect of frugivore movement on seed dispersal has been studied and we know that there exists an important link between them [@will_mechanistic_2008; @russo_incorporating_2006; @pegman_exploring_2017]. Animal movement patterns determine the extent to which seeds get distributed, and this in turn creates a range distribution for plants [@levey_modelling_2008]. Plants distribution and ranges are largely determined by the seeds that get dispersed the farthest from their parent. Animal movement is known to provide these long-distance seeds more than other dispersal sources such as wind or water[@jordano_what_2017]. Frugivore in particular is associated with longer dispersal, partly influenced by the gut retention time. We wanted to understand how individual variation in animal movement can influence the frequency and extent of long-distance seed dispersal events. We analyzed aracari telemetry data at the population level and at an individual level, to explore how these could influence seed dispersal. In addition to this, we tested several models to understand how the choice of probability distribution associated to the movement kernel can limit or overestimate seed dispersal.

# Methods
### Data collection/manipulation

We focused our study on the many-banded aracari (*Pterglossus pluricinctus*) and its role as a frugivore of the *Virola flexuosa* tree. A subset of animal movement data collected in a previous study [@holbrook_home_2011] was selected and used towards our models and simulations. In this previous study, Aracari home ranges, average movement distances, patterns and movement rates were estimated for tracked birds over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest. Further details on field methods can be found in Holbrook [-@holbrook_home_2011].  We focused on the data from the many-banded aracari, *Pteroglossus pluricinctus*, because a higher number of recorded locations were available. In addition to this, the home range of this species was found to be the largest for all the species studied, and therefore it was better suited to study long-distance seed dispersal events.

We used subsequent animal locations to estimate distance moved in a given tracking session, then calculated movement rates per minute for each movement bout. We defined a movement bout as the movement occurring between two consecutive GPS locations. *Is this ok? not sure how to describe how I considered this* We generated a distribution of movement rates and selected the animals that had a minimum of 30 observations giving us a dataset with information on twelve individual birds. Unlike previous work by Holbrook [-@holbrook_home_2011] we restricted our analysis to consecutive locations only, to better capture variation in trajectory and movement rates in meters per minute for a given flight session. We were not focused on distance to origin from the animal’s perspective, but on movement bouts in a continuous tracking session, in order to estimate trajectory movement, which would directly influence the distance that seeds get dispersed from a focus tree.

### Animal movement probability distributions

In this study, we consider population level when we consider all the tracking data together as a whole. For population level analysis we make the assumption that there is no individual variation in movement rates and therefore a single movement rate model can describe all individuals in that population. For the case of individual level analysis, we consider individual variation by analyzing the movement rates separately and fitting a probability distribution model to the tracking data for each individual. Within this framework we consider that animal movement rates (number of meters moved per minute in each individual movement bout) can be described with four different probability distribution models: an exponential distribution [@jones_closing_2017], a gamma distribution, a weibull distribution [@morales_effects_2006], and a lognormal distribution [@levey_modelling_2008]. (Comment: where do you think I should include a description of these different distributions?) The fit of each model to the data was analyzed visually via qqplots (See supplementary information).

At the population level, we compared the fit between the four distribution models using different information criteria (AIC, AICc, and BIC). At the individual level we considered five different models, four of these models corresponded to each of the four probability distributions. For the first four models, we assumed that one probability distribution could accurately describe the movement rates for each individual by changing the distribution's parameters. A fith alternative model considered instead the best fitting model for each individual and calculated the overall information criteria as a combination of the best fitting model for each individual. For each of these indivual level models, information criteria were calculated based on the number of parameters, sample size and negative log likelihood in the following way

$$AIC{_{indlevel}} = 2\sum \left ( number parameters \right ) + 2\sum \left ( negative log likelihood \right )$$

$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$

$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$

### Seed dispersal simulation

To understand the impact of individual animal movement rates over seed dispersal distances, we built a simulation model which took into account animal movement and seed gut retention time (GRT). Each simulation run consisted of an individual bird who was given five seeds at the start of the simulation. Each seed's gut retention time was randomly sampled from a Gamma distribution based on previously collected data [@holbrook_home_2011] and out of the five seeds the largest GRT determined the simulation time for each run. The simulated bird would start at point (0,0) and move across the landscape in a random walk, with angle of movement and speed determined by one minute time steps. At each minute time step, an angle of movement would be sampled from a uniform distribution and a movement rate sampled from one of movement rate models (exponential, gamma, lognormal or weibull). Seeds would get dropped at the bird's position at the time the simulation reached each seed's GRT and the simulation run would end once the bird dropped all five seeds. At the population level, we had four different simulations, each corresponding to one of the probability distributions being tested for animal movement rates. We performed 12,000 individual simulation runs with each distribution and estimated seed dispersal distances for each of the seeds. In the case of individual level simulations, we had 1000 simulation runs for each individual (twelve individuals, with a total of 12,000 simulation runs) and we did this with each of the four distribution models. Finally, we considered a (heterogeneous/mixed? need to check with JMP on terminology) model where we selected the best fitting movement rate model for each individual and used it to parameterize the simulation. For these mixed models, the probability distribution used to sample movement rates would be the best fitting distribution for each individual's movement rates (the target distribution as determined by AIC or BIC), and not a common distribution with different parameters for each individual (as in the previous individual level simulation runs).  Whether at population level or individual level, the output of the simulation runs for each model is the dispersal distance for 60,000 seeds. We performed summary statistics on seed dispersal distances for each of the models

## Results
### Animal movement rate models

We compared the fit of the different probability distributions to animal movement rate data with Akaike's Information Criteria(AIC) and it's corrected version for small sample sizes (AICc), we also used the Bayesian Information Criteria (BIC) to compare these model fittings. At the population level, all information criteria concur and show that the lognormal model fits the data for movement rates the best, with the weibull model next, see table 1. However, as we visually assessed fit of these models with QQ plots and goodness-of-fit statistics (see the supplemet), the lognormal distribution model greatly overestimates the data towards the tail, whereas all the other models are significantly more conservative and tend to underestimate the data.

```{r}
popIC_table <- readRDS(file = "output/popIC_table.RDS")

popIC_table %>% 
  knitr::kable()
```

At the individual level, we observed similar outcomes, where the lognormal distribution consistently overestimated the data, whereas the other distributions considered did not. When comparing across distribution models at the individual level, AIC and AICc showed the lognormal fit as the best one followed by the exponential model, whereas the BIC had the exponential as the best model followed by the lognormal.

```{r}
indIC_table <- readRDS(file = "output/indIC_table.RDS")

indIC_table %>% 
  knitr::kable()
```

When comparing the population level models with the ones at the individual level, we found that information criteria differed. In the case of AIC and AICc, these consistently categorized the individual level models as best fitting when compared to their equivalent distribution model at the population level. However, BIC values show that only when we consider the exponential distribution model does the individual level do a better fitting than the population, with all other models having higher BIC values for the models that include individual heterogeneity.

```{r}
AIC_table <- readRDS("manuscript/AIC_table.RDS")

AIC_table %>%
  transmute(distribution,
          aic.pop.ind = AIC.pop - AIC.ind,
         aicc.pop.ind = AICc.pop - AICc.ind,
         bic.pop.ind = BIC.pop-BIC.ind) %>% 
  knitr::kable()
```

The mixed/heterogeneous model considered the best fitting distribution for each individual, and then selected given distribution to be included in the general model that includes movement for all the individuals and calculates the information criteria value. Using different information criteria yielded different best fitting models (see supplement) for each individual, which changed the distributions included on the overall model, therefore producing two different mixed/heterogeneous modelsd with individual variation, one associated to the AIC/AICc target distributions and a different one for BIC. However, all information criteria agreed on nine out of twelve individual models. In the case of AIC and AICc four individuals were better described by an exponential distribution, three by a Weibull distribution and five by a lognormal distribution. When using BIC as the model selection tool, seven individuals were described by an exponential distribution, four by a lognormal and one by the Weibull distribution. The overall AIC, AICc and BIC values were calculated for each of the mixed/heterogenous model and compared to the previous fits, where the first five results are shown in the following table (the rest can be seen in the supplement). This shows that only the lognormal model at the population level is better than the mixed/heterogeneous model by <2 BIC units.

```{r}
allIC_table <- readRDS(file = "output/allIC_table.RDS")

head(allIC_table) %>% 
  knitr::kable()
```

### Seed Dispersal Distances

We analyzed the seed dispersal distances produced by the simulation runs and there were clear differences between the simulation models. These differences clear between models that used different distributions for movement rates, whether or not they consider individual variation, the seed dispersal distances under the lognormal distribution were extremely high with several outliers for dispersal distance. The exponential, Gamma and Weibull models for movement rates produced similar seed dispersal distance distributions at the population level. All the simulations showed that models that included individual variation in animal movement rates had a higher number of long distance dispersal events.

```{r}

get_all <- readRDS("output/get_all.RDS")

get_all %>% 
  ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  theme_bw()
```

Summarize some values for these distances. Is this table necessary? or how to reduce it? Do I need to make it smaller?

```{r}
get_all %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

## Discussion

Considering animal movement in this simple framework of movement rates allows us to easily compare between individuals and how including intraspecific variation can change our estimates and fits of different models. It is known that because of this individual variation, no one distribution will fit all individuals, and therefore approaches with mixed distributions or that select different distributions for each individual are important if we want to understand the relationship between frugivore movement and seed dispersal [@russo_incorporating_2006]. Previous research has focused on exploring the effects of lanscape fragmentation, heterogeneity [@jones_closing_2017, @levey_modelling_2008] or plant aggregation [@pegman_exploring_2017]. However, focus on intraspecific variation in frugivores and their effect on seed dispersal has only recently been studied more closely[@snell_consequences_2019]. The models we have used in this study show that individual variation between individual movement rates exist. There is clear evidence for heterogeneity across individuals with respect to which distribution explains the data best with both, the AIC and the BIC, regardless of whether these information criteria match. We need to move towards developing better animal movement models that incorporate this type of heterogeneity, where we don't just pool tracking data for all individuals, but where we consider the tail end distributions of their movement.

We have also shown that including individual variation in type of distribution for movement rates produces one of the best fitting models to the data. Although in our direct comparisson between mixed models and single distribution models, the lognormal distribution at the population level was the best fitting one, the difference of 1.900455 BIC points is too small for us to reject our mixed model that states heterogeneity across individuals. This small difference points at perhaps how small sample sizes per individual can have an effect on the fits.Using BIC, a difference of approximately 4 BIC points is equivalent to stating significant difference at an 0.05 alpha level, therefore the difference of <2 BIC points is not sufficient for us to reject our mixed models with individual variation. All other models that follow are over 10 BIC units from out mixed/heterogeneous model.

Even though LDD events are rare or infrequent, they have a disproportionately large effect on gene flow and the genetic pool of populations (Jordano 2017). In the case of well mixed populations, long-distance dispersal can cause random genetic loss through drift or have the opposite effect and maintain high genetic variance in populations that initially drifted (Bohrer, Nathan, and Volis 2005). This is important as in the long-term, these genetic consequences of dispersal can have significant effects for the survival of populations. From a metapopulation perspective, LDD events can have significant consequences for species persistence by enhancing genetic variability and as mechanism for survival in spatially and temporally heterogenous environments. In particular, long-distance dispersal events have a higher probability of reaching isolated populations and therefore establishing a connection and maintaining unrelated populations. It is of special interest to focus in highly heterogenous habitats with rapid change in spatial structure where local extinctions are high, since long-distance dispersal can allow persistence of a metapopulation with immigration and emigration based on long distance dispersal. From a more evolutionary perspective, long-distance dispersal can allow for a species to colonize distant habitats and expand its range, which can also lead to differentiation and speciation (Ronce 2007). We have shown that individual differences in frugivore movement can have significant consequences on the number of long-distance seed dispersal events and it remains to be explored how these individual differences can influence population dynamics in the long term and at larger spatial scales.

# Conclusion

# Acknowledgements

# References

### 2020-09-08 appendixA/appendixA.Rmd
add text and density figures

@@
 ---
-title: "Appendix A: Model fitting and selection for distances moved per minute"
+title: "Appendix A: Model fitting and selection for tracking data"
 output:
@@
 ---
+
+We have used the data collected by Kimberly Holbrook for her studies on toucan home ranges and movement patterns [@holbrook_home_2011].
+We cleaned original data similarly, as is shown in the `raw-data/newpointlocs.R` file of this directory, by restricting the individuals to those with a minimum of 40 observations and locations collected in intervals from 15 to 90 minutes in multiples of 15 minutes.
+As shown in previous studies [@holbrook_using_2007], the distances traveled by toucans in 15-30 minutes represent the most probable distances for seed dispersal.
+Due to data collection constraints, locations could not be obtained every 15 minutes, and birds were sometimes located at greater time intervals.
+Our goal in this section is to use a probabilistic approach that will characterize the pattern of distances moved, and use these probability distributions to later randomly sample distances from.
+In order to do this, we scaled the original data in distances moved per time interval, to distances moved per minute.
+
+Our approach involves fitting these probability distributions at three different levels: population, individual, and family.
+In the case of population level fittings, a probability distribution is used to fit all the data available, and a single distribution is used to describe the population's distanced moved.
+At the individual level, each bird is analyzed separately and a single distribution is assigned to the data of each individual bird to characterize it's distances moved.
+The family level analysis is restricted to the data points for which we have available information on family group.
+In this case, a single probability distribution is used for each individual family group to describe the distances moved.
 
@@
 
+The way we are fitting the data can be visualized as follows:
+
+```{r data}
+# Get the data loaded. We are removing the one value with zero since it won't allow fitting.
+
+load("data/newpointlocs.rda")
+
+df <- newpointlocs %>%
+  dplyr::filter(mpm != 0) %>%
+  ungroup() %>%
+  mutate(Bird_ID = paste0("B", Bird_ID),
+         sqR2n = sqrt(R2n)) %>% 
+  group_by_("id", "burst") %>% 
+  mutate(cumdt = cumsum(dt)/60) %>% 
+  ungroup()
+
+dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+
+param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+
+```
+
+```{r}
+pop_dens_plot <- df %>%
+  ggplot(., aes(x = mpm)) +
+  geom_line(stat = "density", color = "grey", lwd = 1) +
+  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  ylim(0, 0.05) +
+  labs(title = "Population") +
+  theme_classic()
+
+ind_dens_plot <- df %>%
+  ggplot(., aes(x = mpm)) +
+  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  ylim(0, 0.05) +
+  labs(title = "Individual") +
+  theme_classic()
+
+fam_dens_plot <- df %>%
+  ggplot(., aes(x = mpm)) +
+  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  ylim(0, 0.05) +
+  labs(title = "Family") +
+  theme_classic()
+
+ggarrange(pop_dens_plot, ind_dens_plot, fam_dens_plot, ncol = 3)
+
+```
+
 ```{r functions}
@@
 }
-
-```
-
-```{r data}
-# Get the data loaded. We are removing the one value with zero since it won't allow fitting. Also, zero represents no movement, but we will use perching time for that.
-
-df <- readRDS("outputs/newpointlocs.RDS") %>%
-  filter(mpm != 0) %>%
-  ungroup() %>%
-  mutate(Bird_ID = paste0("B", Bird_ID),
-         sqR2n = sqrt(R2n))
-
-dist.used <- c( "exp", "gamma", "weibull", "lnorm")
-
-param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
-dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
 

### 2020-09-08 appendixA/appendixA.Rmd
update

@@
 output:
-  pdf_document:
+  html_document:
       toc: true
@@
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-knitr::opts_chunk$set(message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
 ```
@@
 
-The way we are fitting the data can be visualized as follows:
+The way we are fitting the data can be visualized as follows, where each curve represents the population, an individual, or a family group:
 
@@
 
-```{r}
+```{r fig.width=10}
 pop_dens_plot <- df %>%
@@
 
-```{r poplevel}
+```{r poplevel, eval = FALSE}
 
@@
 ```
+
+# References

### 2020-09-08 appendixA/appendixA.Rmd
updates

@@
 ---
-title: "Appendix A: Model fitting and selection for tracking data"
+title: "Appendix A"
+subtitle: "Model fitting and selection for tracking data"
 output:
@@
 ---
+
+# Overall description
 
@@
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, results = 'hide')
 ```
@@
 theme_set(theme_bw())
+```
+
+```{r functions}
+
+# Extract parameters from fitted distributions to the data
+build.fits.df <- function(x){
+
+  nm <- deparse(substitute(x))
+
+  x %>% 
+  map(., `[`, c("estimate", "sd", "loglik", "n")) %>% 
+  map(as_tibble) %>% 
+  bind_rows()
+}
+
 ```
@@
 fam_dens_plot <- df %>%
+  filter(., fam_g != "unknown") %>% 
   ggplot(., aes(x = mpm)) +
@@
 ```
+We have chosen five common probability distributions, which are readily used in animal-mediated seed dispersal simulations.
+These are an exponential distribution [@jones_closing_2017], a gamma distribution, Weibull distribution [@morales_effects_2006], and lognormal distribution [@levey_effects_2005].
+The goal of this project is to evaluate variation in movement and how that translates to differences in seed dispersal estimates.
+Our first comparisson is made between population level and individual level estimates.
+Not all individual birds had information on family group, therefore, for our second comparisson between population level and family level fits, we used a reduced dataset with only data from individual for which we had family group information.
+We assessed fits visually through QQ plots.
 
-```{r functions}
+# Population and Individual level comparissons
 
-# Extract parameters from fitted distributions to the data
-build.fits.df <- function(x){
+At the population level analysis, we observe that the lognormal distribution has considerable overestimation of distances towards the tail.
+Although this is also worth noting in the QQ plots for individuals, not all of the individual have an overestimation, and for some other distributions seem to do a better job at characterizing the pattern.
 
-  nm <- deparse(substitute(x))
-
-  x %>% 
-  map(., `[`, c("estimate", "sd", "loglik", "n")) %>% 
-  map(as_tibble) %>% 
-  bind_rows()
-}
-
-```
-
-# Population vs Individual levels
-## Population level
-We fit the probability distributions to all the data, so it is population level.
-We compare fits visually with a qqplot.
-It is evident with this plot that the lognormal distribution is problematic at the tails and shows a significant overestimation.
-All the other distributions underestimate the real values, but it seems like the Weibull is closer to the diagonal.
-
-```{r poplevel, eval = FALSE}
+```{r poplevel, fig.height = 3}
 
 pop <- lapply(dist.used, function(x){fitdist(df$mpm, distr = x)})
-qqcomp(pop, plotstyle = "ggplot") +
+
+qqpop <- qqcomp(pop, plotstyle = "ggplot")
+
+qqpop +
   coord_equal() +
-  geom_point(shape = 16, alpha = 0.5)
+  geom_point(shape = 16, alpha = 0.5) +
+  labs(title = "Population level QQ plot")
+  scale_color_viridis_d()
 
@@
 
+```{r}
+inds <- unique(as.character(df$Bird_ID))
+#inds
+
+for(i in 1:length(inds)){
+  fit.df <- df %>% 
+    dplyr::filter(., Bird_ID == inds[i])
+
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$mpm, distr = x)})
+
+  assign(paste(inds[i]), fit)
+
+  fit.prms <- build.fits.df(fit) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = inds[i])
+
+  prms.df <- bind_rows(prms.df, fit.prms)
+}
+```
+
+```{r fig.height=5}
+
+inds.models.data <- NULL
+ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
+chr.models <- c("B1", "B13", "B19", "B22", "B28", "B29", "B3", "B30", "B49", "B5", "B7", "B84")
+for(i in 1:12){
+  x <- ind.models[[i]]
+
+  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
+    mutate(data = chr.models[i])
+  names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
+  inds.models.data <- bind_rows(inds.models.data, qqdata)
+}
+
+inds.models.data%>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  facet_wrap(~individual)+
+    geom_point(cex = 2, alpha = 0.6) +
+    geom_abline(intercept = 0, slope = 1) +
+    labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  scale_color_viridis_d() + 
+  theme(legend.position = "top") +
+  guides(color = guide_legend(title = "Distribution")) +
+  coord_equal()
+
+```
+
+## Information criteria assessment of individual level distribution fits
+Need to add the description here of how we calculated these information criteria and the reasoning as to why we decided to go with just the BIC, because of Jose's paper.
+Explain here what the mixed distribution model means, vs the others that use one distribution but allow variation in the parameters.
+
+```{r}
+all_indiv_prms <- prms.df %>% 
+  mutate(kpars = ifelse(dist == "exp", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3))
+#saveRDS(all_indiv_prms, file = "outputs/prms_indiv.RDS")
+
+prms.df %>% 
+  dplyr::select(., loglik, n, dist, data) %>% 
+  distinct() %>% 
+  mutate(kpars = ifelse(dist == "exp", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3)) -> popind.IC
+```
+
 # References

### 2020-09-15 paper/paper.Rmd
render in html to access from website

@@
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
-output:
-  word_document: default
-  pdf_document:
-    latex_engine: xelatex
+output: html_document
 linenumbers: yes

### 2020-09-21 appendixA/appendixA.Rmd
finish appendixA parameter estimation

@@
          deltaAICc = signif(AICc - min(AICc), 3)) -> popind.IC
+
 ```
 
+```{r}
+popind.IC %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = ic, y = value, color = dist)) +
+  geom_point() +
+  facet_wrap(~data, scales = "free")
+```
+
+```{r}
+prms.df %>% 
+  filter(., data != "pop") %>%
+  dplyr::select(., loglik, n, dist) %>% 
+  distinct() %>%
+  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
+  group_by(dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
+            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
+            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
+    mutate(deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3),
+         deltaBIC = signif(BIC - min(BIC), 3),
+         data = "ind") %>% 
+  full_join(., popind.IC %>% 
+  filter(., data == "pop")) -> popind.IC.comp
+
+```
+
+```{r}
+prms.df %>% 
+  mutate(fit.param = paste(dist, param)) %>% 
+  ggplot(., aes(x = data, y = estimate, color = dist)) +
+  facet_wrap(~fit.param, scales = "free") +
+  geom_point() +
+  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+  theme(legend.position = "none")
+```
+
+```{r}
+popind.IC.comp %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = ic, y = value, color = dist)) +
+  geom_point() +
+  facet_wrap(~data, scales = "free")
+```
+
+```{r}
+
+# Get the multi-distribution model fit
+popind.IC %>% 
+  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
+  ungroup() %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  as.numeric() -> multi.BIC
+
+popind.IC %>% 
+  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
+  ungroup() %>% 
+  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
+  as.numeric() -> multi.AIC
+
+popind.IC %>% 
+  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
+  ungroup() %>% 
+  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
+  as.numeric()-> multi.AICc
+
+popind.IC.comp %>% 
+  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
+  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>%
+  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = dist, y = value, color = data)) +
+  geom_point() +
+  facet_wrap(~ic, scales = "free") +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+Summary: When comparing population vs individual level fits, at the population level, the lognormal distribution fits the data better, and at the individual level it is the exponential distribution.
+When we focus only on the individual level fits, which distribution fits best depends on the information criteria considered, although most of the individuals are properly characterized by an exponential or lognormal distribution.
+What we consider as the multi distribution, it is a multi-distribution probability fit to the data in which we have allowed not only the parameters but also the shape of the distribution to vary between individuals.
+This means that each individual can be characterized by a different distribution and different parameters.
+In the case of AIC and AICc, this probability approach works best for the data, however when considering BIC, the lognormal fit is best, and the mixed distribution approach ties with a weibull distribution at population level.
+Using BIC, a population level modeling approach is the best.
+
+# Population vs Family
+
+## Population level - restricted
+Keep in mind that the family level data is reduced because some individuals had unknown family groups and therefore are not included in this analysis.This means that we cannot directly compare distribution fits from family level aggregation with that of individuals.
+To make a comparisson with the population, we need to keep only data points for which we have family information
+
+```{r}
+fams.df <- df %>% 
+  dplyr::filter(., fam_g != "unknown")
+
+fams <- paste0("f", 1:6)
+
+pop.fams <- lapply(dist.used, function(x){fitdist(fams.df$mpm, distr = x)})
+qqcomp(pop.fams, plotstyle = "ggplot") +
+  coord_equal() +
+  geom_point(shape = 16, alpha = 0.5)
+
+prms.fams.df <- build.fits.df(pop.fams) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = "pop")
+
+```
+## Family level
+
+```{r}
+
+for(i in 1:length(fams)){
+  fit.df <- fams.df %>% 
+    dplyr::filter(., fam_g == fams[i])
+
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$mpm, distr = x)})
+
+  assign(paste(fams[i]), fit)
+
+  fit.prms <- build.fits.df(fit) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = fams[i])
+
+  prms.fams.df <- bind_rows(prms.fams.df, fit.prms)
+
+}
+
+```
+
+Evaluate via qqplots
+```{r}
+
+fams.models.data <- NULL
+fams.models <- list(f1, f2, f3, f4, f5, f6)
+
+for(i in 1:6){
+  x <- fams.models[[i]]
+
+  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
+    mutate(data = fams[i])
+  names(qqdata) <- c("theoretical", "fdist", "empirical", "fam.group")
+  fams.models.data <- bind_rows(fams.models.data, qqdata)
+}
+
+fams.models.data%>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  facet_wrap(~fam.group)+
+    geom_point(cex = 2, alpha = 0.6) +
+    geom_abline(intercept = 0, slope = 1) +
+    labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() + 
+  theme(legend.position = "top") +
+  guides(color = guide_legend(title = "Distribution")) +
+  coord_equal()
+
+```
+```{r}
+all_fam_prms <- prms.fams.df %>% 
+  mutate(kpars = ifelse(dist == "exp", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3))
+```
+
+```{r}
+prms.fams.df %>% 
+  mutate(fit.param = paste(dist, param)) %>% 
+  ggplot(., aes(x = data, y = estimate, color = dist)) +
+  facet_wrap(~fit.param, scales = "free") +
+  geom_point() +
+  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+  theme(legend.position = "none")
+```
+
+## Calculate BIC for comparisons
+
+```{r fig.height=6}
+prms.fams.df %>% 
+  dplyr::select(., loglik, n, dist, data) %>% 
+  distinct() %>% 
+  mutate(kpars = ifelse(dist == "exp", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.BIC
+
+popfam.BIC %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = ic, y = value, color = dist)) +
+  geom_point() +
+  facet_wrap(~data, scales = "free")
+
+```
+
+Calculate BIC for the model at the family level
+```{r}
+prms.fams.df %>% 
+  filter(., data != "pop") %>%
+  dplyr::select(., loglik, n, dist) %>% 
+  distinct() %>%
+  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
+  group_by(dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
+            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
+            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
+    mutate(deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3),
+         deltaBIC = signif(BIC - min(BIC), 3),
+         data = "fam") %>% 
+  full_join(., popfam.BIC %>% 
+  filter(., data == "pop")) -> comp.fams
+
+comp.fams %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = ic, y = value, color = dist)) +
+  geom_point() +
+  facet_wrap(~data, scales = "free")
+
+comp.fams %>% 
+  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = dist, y = value, color = data)) +
+  geom_point() +
+  facet_wrap(~ic, scales = "free")
+
+```
+```{r}
+
+# Get the multi-distribution model fit
+popfam.BIC %>% 
+  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
+  ungroup() %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  as.numeric() -> multi.BIC
+
+popfam.BIC %>% 
+  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
+  ungroup() %>% 
+  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
+  as.numeric() -> multi.AIC
+
+popfam.BIC %>% 
+  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
+  ungroup() %>% 
+  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
+  as.numeric()-> multi.AICc
+
+comp.fams %>% 
+  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
+  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>% 
+  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
+  ggplot(., aes(x = dist, y = value, color = data)) +
+  geom_point() +
+  facet_wrap(~ic, scales = "free") +
+  theme(axis.text.x = element_text(angle = 90))
+
+```
+
+Summary.
+As with individuals, the information criteria actually changes things a lot.
+With AIC and AICc, family level aggregation is a better descriptor of the data, no matter the distribution used, whereas in BIC it is the opposite and population level data is best for all distributions.
+However, the multidistribution approach, where each family is characterized by its own independent distribution and parameters, no matter the information criteria, this one comes with the lowest value, making the multidistribution approach the best for characterizing the data.
+
 # References

### 2020-09-21 paper/paper.Rmd
spelling

@@
 Furthermore, rare events (often overlooked) are critical for dispersal and might have a large effect on resulting plant demography [@loayza2014seed].
-Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patters of seed dispersal.
+Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patterns of seed dispersal.
 

### 2020-09-21 appendixA/appendixA.Rmd
calc all parameters

@@
          deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.BIC
+         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.IC
 
-popfam.BIC %>% 
+popfam.IC %>% 
   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
@@
          data = "fam") %>% 
-  full_join(., popfam.BIC %>% 
+  full_join(., popfam.IC %>% 
   filter(., data == "pop")) -> comp.fams
@@
 # Get the multi-distribution model fit
-popfam.BIC %>% 
+popfam.IC %>% 
   dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
@@
 
-popfam.BIC %>% 
+popfam.IC %>% 
   dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
@@
 
-popfam.BIC %>% 
+popfam.IC %>% 
   dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
@@
 
+```{r}
+# Save parameters
+
+saveRDS(popfam.IC, file = "data/popfamICprms.RDS")
+saveRDS(popind.IC, file = "data/popindICprms.RDS")
+
+```
+
 # References

### 2020-09-21 appendixA/simulation.R
simulation functions

@@ -1,0 +1,197 @@
+# Gut Retention time -----------------------------------------------------
+# First step is to generate Gut retention times from gamma distribution to get maximum GRT and that is our simulation time
+
+# Our simulations are with 100 seeds
+nseeds <- 100
+
+gen_gut_ret_time <- function(nseeds){
+  gut_retention_time <- rgamma(nseeds, shape = 4, scale = 5) + 8
+  grt <- data.frame(seedID = 1:nseeds, time = round(gut_retention_time))
+  grt
+}
+
+# Out of that dataframe, get the maximum gut retention time, as that is the sim_time used
+# Basically the bird ran out of seeds and so we stop the simulation
+
+
+# Distance moved per minute -----------------------------------------------
+# Then, we simulate distances moved by the bird
+
+# Need to create a data frame for this function that only feeds the specific estimates for each bird or population, just feed the subset, not the whole data frame.
+
+
+gen_movement_data <- function(params, sim_time){
+  exp_move <- rexp(sim_time, rate = params$estimate[which(params$dist == "exp")])
+
+  gam_move <- rgamma(sim_time, shape = params$estimate[which(param$dist == "gamma") & params$param == "shape"], rate = params$estimate[which(params$dist == "gamma" & params$param == "rate")])
+
+  weib_move <- rweibull(sim_time, shape = params$estimate[which(params$dist == "weibull" & params$param == "shape")], scale = params$estimate[which(params$dist == "weibull" & params$param == "scale")])
+
+  lnorm_move <- rlnorm(sim_time, meanlog = params$estimate[which(params$dist == "lnorm" & params$param == "meanlog")], sdlog = params$estimate[which(params$dist == "lnorm" & params$param == "sdlog")])
+
+
+  list(exp_move = exp_move, gam_move = gam_move, weib_move = weib_move,
+       lnorm_move = lnorm_move)
+}
+
+
+
+
+# Generate seed dispersal given distances ---------------------------------
+# This function will generate seed dispersal distances given the animal's distance and the simulated gut retention time
+
+gen_seed_dispersal <- function(distance = NULL,
+                               grt = NULL){
+  sim_time <- max(grt$time)
+
[…]

### 2020-09-28 paper/figures_tables.Rmd
drafts

--- 2020-09-08 appendixA/appendixA.Rmd
@@
 ---
-title: "Appendix A"
-subtitle: "Model fitting and selection for tracking data"
+title: "Figures and Tables"
+subtitle: " "
 output:
@@
 ---
-
-# Overall description
-
-We have used the data collected by Kimberly Holbrook for her studies on toucan home ranges and movement patterns [@holbrook_home_2011].
-We cleaned original data similarly, as is shown in the `raw-data/newpointlocs.R` file of this directory, by restricting the individuals to those with a minimum of 40 observations and locations collected in intervals from 15 to 90 minutes in multiples of 15 minutes.
-As shown in previous studies [@holbrook_using_2007], the distances traveled by toucans in 15-30 minutes represent the most probable distances for seed dispersal.
-Due to data collection constraints, locations could not be obtained every 15 minutes, and birds were sometimes located at greater time intervals.
-Our goal in this section is to use a probabilistic approach that will characterize the pattern of distances moved, and use these probability distributions to later randomly sample distances from.
-In order to do this, we scaled the original data in distances moved per time interval, to distances moved per minute.
-
-Our approach involves fitting these probability distributions at three different levels: population, individual, and family.
-In the case of population level fittings, a probability distribution is used to fit all the data available, and a single distribution is used to describe the population's distanced moved.
-At the individual level, each bird is analyzed separately and a single distribution is assigned to the data of each individual bird to characterize it's distances moved.
-The family level analysis is restricted to the data points for which we have available information on family group.
-In this case, a single probability distribution is used for each individual family group to describe the distances moved.
 
@@
   ungroup()
-
-dist.used <- c( "exp", "gamma", "weibull", "lnorm")
-
-param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
-dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
-
 ```
@@
   ggplot(., aes(x = mpm)) +
-  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
   geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
@@
   geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.05) +
+  ylim(0, 0.055) +
   labs(title = "Individual") +
@@
   ggplot(., aes(x = mpm)) +
-  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
   geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
@@
   geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.05) +
+  ylim(0, 0.055) +
   labs(title = "Family") +
@@
 
-ggarrange(pop_dens_plot, ind_dens_plot, fam_dens_plot, ncol = 3)
-
-```
-We have chosen five common probability distributions, which are readily used in animal-mediated seed dispersal simulations.
-These are an exponential distribution [@jones_closing_2017], a gamma distribution, Weibull distribution [@morales_effects_2006], and lognormal distribution [@levey_effects_2005].
-The goal of this project is to evaluate variation in movement and how that translates to differences in seed dispersal estimates.
-Our first comparisson is made between population level and individual level estimates.
-Not all individual birds had information on family group, therefore, for our second comparisson between population level and family level fits, we used a reduced dataset with only data from individual for which we had family group information.
-We assessed fits visually through QQ plots.
-
-# Population and Individual level comparissons
-
-At the population level analysis, we observe that the lognormal distribution has considerable overestimation of distances towards the tail.
-Although this is also worth noting in the QQ plots for individuals, not all of the individual have an overestimation, and for some other distributions seem to do a better job at characterizing the pattern.
-
-```{r poplevel, fig.height = 3}
-
-pop <- lapply(dist.used, function(x){fitdist(df$mpm, distr = x)})
-
-qqpop <- qqcomp(pop, plotstyle = "ggplot")
-
-qqpop +
-  coord_equal() +
-  geom_point(shape = 16, alpha = 0.5) +
-  labs(title = "Population level QQ plot")
-  scale_color_viridis_d()
-
-prms.df <- build.fits.df(pop) %>% 
-  mutate(param = param,
-         dist = dist,
-         data = "pop")
+fam_zoom <- fam_dens_plot +
+  coord_cartesian(ylim = c(0, 0.01), xlim = c(50, 210))
 
@@
 ```{r}
-inds <- unique(as.character(df$Bird_ID))
-#inds
 
-for(i in 1:length(inds)){
-  fit.df <- df %>% 
-    dplyr::filter(., Bird_ID == inds[i])
+ind_zoom <- ind_dens_plot +
+  coord_cartesian(
+    ylim = c(0, 0.01),
+    xlim = c(60, 180))
 
-  fit <- lapply(dist.used, function(x){fitdist(fit.df$mpm, distr = x)})
+ind_grob <- ggplotGrob(ind_zoom)
 
-  assign(paste(inds[i]), fit)
-
-  fit.prms <- build.fits.df(fit) %>% 
-  mutate(param = param,
-         dist = dist,
-         data = inds[i])
-
-  prms.df <- bind_rows(prms.df, fit.prms)
-}
+ind_dens_plot +
+  annotation_custom(grob = ind_grob, xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
 ```
 
-```{r fig.height=5}
+```{r}
 
-inds.models.data <- NULL
-ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
-chr.models <- c("B1", "B13", "B19", "B22", "B28", "B29", "B3", "B30", "B49", "B5", "B7", "B84")
-for(i in 1:12){
-  x <- ind.models[[i]]
+fam_zoom <- fam_dens_plot +
+  coord_cartesian(
+    ylim = c(0, 0.01),
+    xlim = c(50, 210))
 
-  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
-    mutate(data = chr.models[i])
-  names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
-  inds.models.data <- bind_rows(inds.models.data, qqdata)
-}
-
-inds.models.data%>% 
-  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
-  facet_wrap(~individual)+
-    geom_point(cex = 2, alpha = 0.6) +
-    geom_abline(intercept = 0, slope = 1) +
-    labs(x = "Model Quantiles",
-         y = "Empirical Quantiles") +
-  scale_color_viridis_d() + 
-  theme(legend.position = "top") +
-  guides(color = guide_legend(title = "Distribution")) +
-  coord_equal()
-
+fam_dens_plot +
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
 ```
 
-## Information criteria assessment of individual level distribution fits
-Need to add the description here of how we calculated these information criteria and the reasoning as to why we decided to go with just the BIC, because of Jose's paper.
-Explain here what the mixed distribution model means, vs the others that use one distribution but allow variation in the parameters.
-
 ```{r}
-all_indiv_prms <- prms.df %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3))
-#saveRDS(all_indiv_prms, file = "outputs/prms_indiv.RDS")
-
-prms.df %>% 
-  dplyr::select(., loglik, n, dist, data) %>% 
-  distinct() %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> popind.IC
+ggarrange(ind_dens_plot, fam_dens_plot, nrow = 2)
 ```
-
-# References

### 2020-09-28 paper/figures_tables.Rmd
Movement rates

@@
 ```
+
+Movement rates, from Kimberly's paper, is the average number of meters moved per minute over the entire tracking period
+
+```{r}
+newpointlocs %>% 
+  group_by(id, burst) %>% 
+  summarise(rate = mean(mpm)) %>% 
+  ggplot(., aes(x = rate)) +
+  facet_wrap(~id, nrow = 3)+
+  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = rate, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  ylim(0, 0.055) +
+  labs(title = "Movement rates") +
+  theme_classic()
+
+```
+
+Important to keep in mind I could do movement rates or net squared displacement.
+
+```{r}
+
+# I just added this.
+If I wanted to work with movement rates instead: which are the average number of meters moved over the tracking period.
+I consider period here as the burst.
+But I am also unclear about what the entire tracking period is here.
+
+newpointlocs %>% 
+# mydata %>%
+#   add_count(Bird_ID) %>%
+  group_by(id, burst) %>% 
+  summarise(mov_rate = mean(mpm)) %>% 
+  add_count(id) -> mov_rate_test
+
+mov_rate_test %>% 
+  ggplot(., aes(x = id, y = mov_rate)) +
+  geom_boxplot()
+
+mov_rate_test %>% 
+  ggplot(., aes(x = mov_rate, group = id)) +
+  facet_wrap(~id) +
+  geom_density()
+
+mov_rate_test %>%
+  ggplot(., aes(x = mov_rate)) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = mov_rate, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  #ylim(0, 0.055) +
+  labs(title = "Movement rate") +
+  theme_classic()
+
+newpointlocs %>%
+# mydata %>%
+#   add_count(Bird_ID) %>%
+  group_by(id) %>% 
+  summarise(mov_rate_all = mean(mpm)) -> all_mov_rate
+
+summary(all_mov_rate$mov_rate_all)
+mean(all_mov_rate$mov_rate_all)
+sd(all_mov_rate$mov_rate_all)
+
+```

### 2020-10-04 paper/paper.Rmd
Decided to rename the dataset to ptpl, for pteroglossus pluricinctus

@@
 # Methods
+## Seed dispersal simulation
+the goal of this manuscript is to evaluate the effects of variation in animal movement and how these translate to seed dispersal distances.
+We developed an individual-based simulation in order to track single individuals or family groups in various tracking sessions and see how they disperse seeds.
+
+  - What is the overall goal of this simulation?
+  - What entails one simulation run
+  - Overall description of how the simulation works
+  - Variables that go into the simulation
+  - Sources I used to reference: jones
+2. Parameterization and source data
+  - Data description
+  - Gut retention time comes from previous literature and averages
+  - Calculations at the different organizational levels
+3. Evaluating fits?
+4. Statistics associated to the simulations
+
 ### Data collection/manipulation

### 2020-10-04 data-raw/ptpl.R

@@ -1,4 +1,4 @@
-## code to prepare `newpointlocs` dataset goes here
+## code to prepare `ptpl` dataset goes here
 
 # Libraries needed
 library(adehabitatLT)
@@ -85,8 +85,8 @@ mydata <- ptpl %>%
 
 mydata %>%
   add_count(Bird_ID) %>%
-  filter(n >= 30) -> newpointlocs
+  filter(n >= 30) -> ptpl
 
 
 # Last Step -----------------------------
-usethis::use_data(newpointlocs, overwrite = TRUE)
+usethis::use_data(ptpl, overwrite = TRUE)

### 2020-10-04 R/fit_distr_fxs.R
script for the functions used in fitting distributions

@@ -1,0 +1,17 @@
+#' Title
+#'
+#' @param x
+#'
+#' @return
+#' @export
+#'
+#' @examples
+build.fits.df <- function(x){
+
+  nm <- deparse(substitute(x))
+
+  x %>%
+    map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
+    map(as_tibble) %>%
+    bind_rows()
+}

### 2020-10-04 R/fit_distr_fxs.R
Edit names and description of the function

@@ -1,12 +1,13 @@
-#' Title
+#' Organize estimates and likelihood from probability model fits
 #'
-#' @param x
+#' @param x list of probability distribution fits. Probably a list of outputs from fitdistrplus::fit_dist()
 #'
 #' @return
 #' @export
 #'
 #' @examples
-build.fits.df <- function(x){
+#'
+get_fits_params_df <- function(x){
 
   nm <- deparse(substitute(x))
 

### 2020-10-04 data-raw/ptpl.R
changed name for the data

@@ -53,9 +53,7 @@ ptpl <- ld(ptpl_locs)
 
 # I want to include family groups in that data set, just in case we want to use that later
 # The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
-
 ptpl$id <- factor(ptpl$id, levels = c(1, 3, 5, 7, 13, 19, 22, 28, 49, 84, 10, 17, 20, 21, 24, 29, 30, 9))
-
 ptpl %>%
   mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
                         ifelse(id == 7, "f2",
@@ -65,26 +63,17 @@ ptpl %>%
                                                     ifelse(id %in% c(49,84),
                                                            "f6", "unknown")
                                              )))))) -> ptpl
-
 # Add new variables used for the selection later
+# Some of the data was collected on a preliminary field season and it includes other time intervals. Here, we want to focus on the intervals that are multiples of 15, as that is how the majority of data is collected. From a biological stand point, a seed has a high probability of being regurgitated in 15-30 minutes.
+# Filter by minimum number of observations. Removing the individuals with an insufficient number of observations. Since we will be fitting probability distributions, we should have at least 30 intervals per individual, so we would remove birds with ID = 17, 20, 24.
 ptpl %>%
   mutate(T_minutes = dt/60,
          Bird_ID = id,
-         mpm = dist/T_minutes) %>%
+         mpm = dist/T_minutes,
+         R2n = lead(R2n)) %>%
+  filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90)) %>%
   group_by(Bird_ID) %>%
-  add_tally()-> ptpl
-
-# Some of the data was collected on a preliminary field season and it includes other time intervals. Here, we want to focus on the intervals that are multiples of 15, as that is how the majority of data is collected. From a biological stand point, a seed has a high probability of being regurgitated in 15-30 minutes.
-
-
-mydata <- ptpl %>%
-  mutate(R2n = lead(R2n)) %>%
-  filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90))
-
-# Filter by minimum number of observations. Removing the individuals with an insufficient number of observations. Since we will be fitting probability distributions, we should have at least 30 intervals per individual, so we would remove birds with ID = 17, 20, 24.
-
-mydata %>%
[…]

### 2020-10-04 R/fit_distr_fxs.R
Changed name of the function that extracts params from the distribution fits

@@ -7,7 +7,7 @@
 #'
 #' @examples
 #'
-get_fits_params_df <- function(x){
+build_fits_df <- function(x){
 
   nm <- deparse(substitute(x))
 

### 2020-10-04 appendixA/appendixA.Rmd
get parameters into appendixA directory instead of data folder.
Was saving the wrong object for the parameters.
It works, after updating the data and the function name

@@
 ```{r}
+library(aracari)
 library(dplyr)
@@
 
-```{r functions}
-
-# Extract parameters from fitted distributions to the data
-build.fits.df <- function(x){
-
-  nm <- deparse(substitute(x))
-
-  x %>% 
-  map(., `[`, c("estimate", "sd", "loglik", "n")) %>% 
-  map(as_tibble) %>% 
-  bind_rows()
-}
-
-```
-
-The way we are fitting the data can be visualized as follows, where each curve represents the population, an individual, or a family group:
+Due to the fact that data was collected at different tracking intervals, we scaled it to represent number of meters moved per minute.
+The goal of these fittings is to obtain parameters of probability distributions that can describe how fast these animals are moving, so that in simulations, we can use these distributions for random sampling of speeds when the animals are moving.
 
@@
 
-load("data/newpointlocs.rda")
+#load("data/ptpl.rda")
+data(ptpl)
 
-df <- newpointlocs %>%
+# Here, we are taking our tracking data and removing mpm (meters moved per minute) that are equal to zero, since these won't allow for distributio fittings.
+We also create a new variable for Bird ID, and modify net squared displacement.
+df <- ptpl %>%
   dplyr::filter(mpm != 0) %>%
@@
 
-prms.df <- build.fits.df(pop) %>% 
+prms.df <- aracari::build_fits_df(pop) %>% 
   mutate(param = param,
@@
 
-  fit.prms <- build.fits.df(fit) %>% 
+  fit.prms <- build_fits_df(fit) %>% 
   mutate(param = param,
@@
 
-prms.fams.df <- build.fits.df(pop.fams) %>% 
+prms.fams.df <- build_fits_df(pop.fams) %>% 
   mutate(param = param,
@@
 
-saveRDS(popfam.IC, file = "data/popfamICprms.RDS")
-saveRDS(popind.IC, file = "data/popindICprms.RDS")
+saveRDS(all_indiv_prms, file = "appendixA/popindprms.RDS")
+saveRDS(all_fam_prms, file = "appendixA/popfamprms.RDS")
 

### 2020-10-04 appendixA/appendixA.Rmd
changing density figures

@@
 
-# Here, we are taking our tracking data and removing mpm (meters moved per minute) that are equal to zero, since these won't allow for distributio fittings.
+# Here, we are taking our tracking data and removing mpm (meters moved per minute) that are equal to zero, since these won't allow for distribution fittings.
 We also create a new variable for Bird ID, and modify net squared displacement.
@@
   ungroup() %>%
-  mutate(Bird_ID = paste0("B", Bird_ID),
-         sqR2n = sqrt(R2n)) %>% 
+  mutate(Bird_ID = paste0("B", Bird_ID)) %>% 
   group_by_("id", "burst") %>% 
@@
 
+# These are the distributions I am considering for characterizing the meters moved per minute in the data
 dist.used <- c( "exp", "gamma", "weibull", "lnorm")
 
+# These are the parameters and associated distributions that will be needed later to build a dataframe of parameters
 param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
@@
 
-```{r fig.width=10}
-pop_dens_plot <- df %>%
-  ggplot(., aes(x = mpm)) +
-  geom_line(stat = "density", color = "grey", lwd = 1) +
-  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.05) +
-  labs(title = "Population") +
-  theme_classic()
+Density plots showing variation in biological classification levels, where the red line shows the density plot for what we consider the population (all the data together), and grey lines show individuals (left) or family groups (right).
 
+```{r fig.width=12, fig.height=5}
 ind_dens_plot <- df %>%
   ggplot(., aes(x = mpm)) +
-  #geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
   geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
@@
 
-ggarrange(pop_dens_plot, ind_dens_plot, fam_dens_plot, ncol = 3)
+ggarrange(ind_dens_plot, fam_dens_plot)
 

### 2020-10-04 appendixA/appendixA.Rmd
progress with insets for density plots

@@
 ```{r fig.width=12, fig.height=5}
+
+zoom_dims <- c(110, 210, 0, 0.01)
+annot_xy <- c(50, 250, 0.02, 0.04)
+
 ind_dens_plot <- df %>%
@@
   geom_hline(yintercept = 0, color = "grey") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
   ylim(0, 0.055) +
+  xlim(0, 250) +
   labs(title = "Individual") +
   theme_classic()
+
+ind_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> ind_zoom
+
+ind_dens_plot +
+  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = 50 , xmax = 250 , ymin = 0.02 , ymax = 0.04) -> a
 
@@
   geom_hline(yintercept = 0, color = "grey") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
   ylim(0, 0.055) +
+  xlim(0, 250) + 
   labs(title = "Family") +
@@
 
-ggarrange(ind_dens_plot, fam_dens_plot)
+fam_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> fam_zoom
+
+fam_dens_plot +
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 100 , xmax = 200 , ymin = 0.02 , ymax = 0.05) -> b
+
+ggarrange(a, b)
 

### 2020-10-04 appendixA/appendixA.Rmd
qq plot individual level is ready. Working on params now.

@@
 library(purrr)
+library(stringr)
 library(fitdistrplus)
-library(ggpubr)
+library(cowplot)
+library(RColorBrewer)
 
@@
 
-```{r fig.width=12, fig.height=5}
+```{r fig.width=12, fig.height=4}
 
 zoom_dims <- c(110, 210, 0, 0.01)
-annot_xy <- c(50, 250, 0.02, 0.04)
+annot_xy <- c(50, 250, 0.025, 0.045)
 
@@
 ind_dens_plot +
-  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = 50 , xmax = 250 , ymin = 0.02 , ymax = 0.04) -> a
+  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a
 
@@
 fam_dens_plot +
-  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 100 , xmax = 200 , ymin = 0.02 , ymax = 0.05) -> b
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b
 
-ggarrange(a, b)
+plot_grid(a, b)
 
@@
 We have chosen five common probability distributions, which are readily used in animal-mediated seed dispersal simulations.
-These are an exponential distribution [@jones_closing_2017], a gamma distribution, Weibull distribution [@morales_effects_2006], and lognormal distribution [@levey_effects_2005].
+These are an exponential distribution [@jones_closing_2017], a gamma distribution, Weibull distribution [@morales_effects_2006], and Log-normal distribution [@levey_effects_2005].
 The goal of this project is to evaluate variation in movement and how that translates to differences in seed dispersal estimates.
-Our first comparisson is made between population level and individual level estimates.
-Not all individual birds had information on family group, therefore, for our second comparisson between population level and family level fits, we used a reduced dataset with only data from individual for which we had family group information.
+Our first comparison is made between population level and individual level estimates.
+Not all individual birds had information on family group, therefore, for our second comparison between population level and family level fits, we used a reduced dataset with only data from individuals for which we had family group information.
 We assessed fits visually through QQ plots.
 
-# Population and Individual level comparissons
+# Population and Individual level comparisons
 
 At the population level analysis, we observe that the lognormal distribution has considerable overestimation of distances towards the tail.
-Although this is also worth noting in the QQ plots for individuals, not all of the individual have an overestimation, and for some other distributions seem to do a better job at characterizing the pattern.
+Although this is also worth noting in the QQ plots for individuals, not all of the individuals have an overestimation, and for some individuals, other distributions seem to do a better job at characterizing the pattern.
 
-```{r poplevel, fig.height = 3}
+```{r}
+
+# Fit the four models for the population level data
 
@@
 
-qqpop <- qqcomp(pop, plotstyle = "ggplot")
+# Get data for qqplot at population level
+qqpop <- qqcomp(pop, plotstyle = "ggplot")$data
+names(qqpop) <- c("theoretical", "fdist", "empirical")
 
-qqpop +
-  coord_equal() +
-  geom_point(shape = 16, alpha = 0.5) +
-  labs(title = "Population level QQ plot")
-  scale_color_viridis_d()
-
+# Save the population level parameters
 prms.df <- aracari::build_fits_df(pop) %>% 
@@
 
-```
+# Repeating the process for data at the individual level
+inds <- unique(as.character(df$Bird_ID))
 
-```{r}
-inds <- unique(as.character(df$Bird_ID))
-#inds
-
+# Fitting the four distributions for each individual and saving the parameters in a dataframe
 for(i in 1:length(inds)){
@@
 }
-```
 
-```{r fig.height=5}
-
+# Getting qqplot data for each individual
 inds.models.data <- NULL
@@
 }
+```
+
+```{r ind_QQplots, fig.width=12, fig.height=5}
+
+qqpop %>% 
+  mutate(individual = "POPULATION") %>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  facet_wrap(~individual) +
+  #coord_equal() +
+  geom_point(shape = 16, alpha = 0.8, size = 4) +
+  geom_abline(intercept = 0, slope = 1) +
+  labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral", name = "Distribution", labels = c("Exponential", "Gamma", "Weibull", "Lognormal")) +
+  theme(legend.position = c(0.8, 0.2)) +
+  NULL -> a
 
@@
   ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  #facet_grid(individual~fdist) +
   facet_wrap(~individual)+
-    geom_point(cex = 2, alpha = 0.6) +
+    geom_point(shape = 16, alpha = 0.8, size = 3) +
     geom_abline(intercept = 0, slope = 1) +
@@
          y = "Empirical Quantiles") +
-  scale_color_viridis_d() + 
-  theme(legend.position = "top") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral") +
+  theme(legend.position = "none") +
   guides(color = guide_legend(title = "Distribution")) +
-  coord_equal()
+  #coord_equal() +
+  NULL -> b
+
+plot_grid(a,b, rel_widths = c(1,2), labels = "AUTO")
 
@@
 
-## Information criteria assessment of individual level distribution fits
+## Assessment of probability distribution parameters
+We can compare the different parameter values estimated for each distribution and their standard deviations.
+These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
+
+```{r}
+
+prms.df %>% 
+  mutate(param = str_to_upper(param), 
+         dist = str_replace(dist, "exp", "Exponential"),
+         dist = str_replace(dist, "gamma", "Gamma"),
+         dist = str_replace(dist, "weibull", "Weibull"),
+         dist = str_replace(dist, "lnorm", "Lognormal"),
+         data = str_replace(data, "pop", "POP")) -> nice_prms
+
+plot_params <- function(prm_data){
+
+  prm_data%>% 
+  filter(., data == "POP") %>% 
+  dplyr::select(., estimate, sd) -> pop_est
+
+  prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    facet_grid(dist~param, switch = "y") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "Estimate") +
+    theme(legend.position = "none")
+}
+
+nice_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params()
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & data == "POP") %>% 
+  plot_params()
+
+```
+
 Need to add the description here of how we calculated these information criteria and the reasoning as to why we decided to go with just the BIC, because of Jose's paper.
@@
 
-```
-
-```{r}
-prms.df %>% 
-  mutate(fit.param = paste(dist, param)) %>% 
-  ggplot(., aes(x = data, y = estimate, color = dist)) +
-  facet_wrap(~fit.param, scales = "free") +
-  geom_point() +
-  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
-  theme(legend.position = "none")
 ```

### 2020-10-04 appendixA/appendixA.Rmd
parameter plots have population line

@@
 
+  title <- paste(dist, param)
+
   prm_data %>% 
@@
     ggplot(., aes(x = data, y = estimate)) +
-    facet_grid(dist~param, switch = "y") +
+    facet_grid(dist~param, switch = "y", scales = "free") +
     # geom_point() +
@@
 
-nice_prms %>% 
-  filter(., dist == "Exponential") %>% 
-  plot_params()
+prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    facet_grid(dist~param, switch = "y", scales = "free_y") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "Estimate") +
+    theme(legend.position = "none")
 
-nice_prms %>% 
-  filter(., dist == "Gamma" & data == "POP") %>% 
-  plot_params()
+prms.df %>% 
+  mutate(fit.param = paste(dist, param)) %>% 
+  ggplot(., aes(x = data, y = estimate, color = dist)) +
+  facet_wrap(~fit.param, scales = "free_y") +
+  geom_point() +
+  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+  theme(legend.position = "none")
 

### 2020-10-04 appendixA/appendixA.Rmd
parameters figure is done for individual level

--- 2020-10-04 appendixA/appendixA.Rmd
@@
 
-## Assessment of probability distribution parameters
+## Probability distribution parameters
 We can compare the different parameter values estimated for each distribution and their standard deviations.
@@
 
-```{r}
+```{r fig.height=10, fig.width=8}
 
@@
 
+  title <- paste(prm_data$dist, prm_data$param)
+
   prm_data %>% 
@@
     ggplot(., aes(x = data, y = estimate)) +
-    facet_grid(dist~param, switch = "y") +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
     # geom_point() +
@@
     geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
-    labs(x = "", y = "Estimate") +
-    theme(legend.position = "none")
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45))
 }
@@
   filter(., dist == "Exponential") %>% 
-  plot_params()
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
 
 nice_prms %>% 
-  filter(., dist == "Gamma" & data == "POP") %>% 
-  plot_params()
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params() -> p6
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params() ->p7
+
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v")
 

### 2020-10-04 appendixA/appendixA.Rmd
added info criteria equations

@@
 These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
+The x axis in the following plots highlights which individuals have the lowest BIC with that model.
+The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
+Overall, at the population level, the lognormal model had the lowest BIC value.
 
@@
          dist = str_replace(dist, "lnorm", "Lognormal"),
-         data = str_replace(data, "pop", "POP")) -> nice_prms
+         data = str_replace(data, "pop", "POP")) %>% 
+  mutate(kpars = ifelse(dist == "exp", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
+  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms
 
@@
     theme(legend.position = "none",
-          axis.text.x = element_text(angle = 45))
+          axis.text.x = element_text(angle = 45, color = prm_data$best_col))
 }
@@
 
-Need to add the description here of how we calculated these information criteria and the reasoning as to why we decided to go with just the BIC, because of Jose's paper.
-Explain here what the mixed distribution model means, vs the others that use one distribution but allow variation in the parameters.
+## Information criteria comparisons
+
+At the population level, we compared the fit between the four distribution models using different information criteria (AIC, AICc, and BIC).
+At the individual level we considered five different models, four of these models corresponded to each of the four probability distributions, were we essentially allowed for individuals to change parameters, but the overall shape of the distribution was the same.
+For the first four models, we assumed that one probability distribution could accurately describe the movement rates for each individual by changing the distribution's parameters.
+A fifth alternative model considered instead the best fitting model for each individual and calculated the overall information criteria as a combination of the best fitting model for each individual.
+For each of these individual level models, information criteria were calculated based on the number of parameters, sample size and negative log likelihood in the following way
+
+$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( negative log likelihood \right )$$
+
+$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$
+
+$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
 

### 2020-10-04 appendixA/appendixA.Rmd
Using a different name for the distributions

@@
          data = str_replace(data, "pop", "POP")) %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
+  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
          BIC = log(n)*kpars - 2*loglik,
@@
 
-$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( negative log likelihood \right )$$
+$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( -\ln\mathcal{L}() \right )$$
 
@@
 
-$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
+$$BIC_{indlevel} = \ln{\sum observations(samplesize)} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
 
 ```{r}
-all_indiv_prms <- prms.df %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3))
-#saveRDS(all_indiv_prms, file = "outputs/prms_indiv.RDS")
-
-prms.df %>% 
-  dplyr::select(., loglik, n, dist, data) %>% 
+nice_prms %>%
+  dplyr::select(., dist, data, deltaBIC, deltaAIC, deltaAICc) %>% 
   distinct() %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> popind.IC
-
-```
-
-```{r}
-popind.IC %>% 
   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 

### 2020-10-05 appendixA/appendixA.Rmd
Individual level is ready, but gt table not showing in the html.

@@
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, results = 'hide')
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
 ```
@@
 library(RColorBrewer)
+library(gt)
 
@@
 
-## Probability distribution parameters
-We can compare the different parameter values estimated for each distribution and their standard deviations.
-These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
-The x axis in the following plots highlights which individuals have the lowest BIC with that model.
-The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
-Overall, at the population level, the lognormal model had the lowest BIC value.
+## Information criteria comparisons
 
-```{r fig.height=10, fig.width=8}
+At the population level, we compared the fit between the four distribution models using different information criteria (AIC, AICc, and BIC).
+At the individual level we considered five different models, four of these models corresponded to each of the four probability distributions, were we essentially allowed for individuals to change parameters, but the overall shape of the distribution was the same.
+For the first four models, we assumed that one probability distribution could accurately describe the movement rates for each individual by changing the distribution's parameters.
+A fifth alternative model considered instead the best fitting model for each individual and calculated the overall information criteria as a combination of the best fitting model for each individual.
+For each of these individual level models, information criteria were calculated based on the number of parameters, sample size and negative log likelihood in the following way
 
+$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( -\ln\mathcal{L}() \right )$$
+
+$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$
+
+$$BIC_{indlevel} = \ln{\sum observations(samplesize)} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
+
+```{r}
 prms.df %>% 
@@
   mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms
+```
+
+The three information criteria differ in their model choices, with AIC and corrected AIC (AICc) selecting the same models, and BIC selecting different ones.
+
+```{r fig.width=12, fig.height=4}
+# To visualize the differences in the information criteria at the individual level
+
+nice_prms %>% 
+  dplyr::select(dist, data, deltaAIC, deltaAICc, deltaBIC) %>% 
+  distinct() %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  mutate(plot_alpha = ifelse(value == "0", 1, 0.8)) %>% 
+  ggplot(., aes(x = data, y = value, color = dist 
+                #alpha = plot_alpha
+                )) +
+  facet_wrap(~ic) +
+  geom_point(size = 3) +
+  scale_color_brewer(palette = "Spectral") + 
+  #scale_alpha_continuous(range = c(0.5, 1)) +
+  labs(x = "") +
+  theme(legend.position = "bottom",
+        axis.text.x = element_text(color = c(rep("black", 12), "red"))) +
+  guides(color = guide_legend(title = "Distribution"))
+
+```
+
+```{r}
+
+# Create the dataframe that compares the models by information criteria
+nice_prms %>% 
+  filter(., data != "POP") %>%
+  dplyr::select(., loglik, n, dist) %>% 
+  distinct() %>%
+  mutate(kpars = ifelse(dist == "Exponential", 1, 2)) %>% 
+  group_by(dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
+            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
+            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
+    mutate(deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3),
+         deltaBIC = signif(BIC - min(BIC), 3),
+         data = "Individual") %>% 
+  full_join(., nice_prms %>%
+              filter(., data == "POP") %>% 
+              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
+              distinct() %>% 
+              mutate(data = "Population")) -> popind.IC.comp
+
+# Get the multi-distribution model fit
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaBIC) %>% 
+  dplyr::filter(., data != "POP" & deltaBIC == 0) %>% 
+  distinct() %>% 
+  ungroup() %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  as.numeric() -> multi.BIC
+
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAIC) %>% 
+  dplyr::filter(., data != "POP" & deltaAIC == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
+  as.numeric() -> multi.AIC
+
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAICc) %>% 
+  dplyr::filter(., data != "POP" & deltaAICc == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
+  as.numeric()-> multi.AICc
+
+popind.IC.comp %>% 
+  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
+  bind_rows(., data.frame(dist = "Multidist", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "Multidist")) -> model_comp_IC
+
+```
+
+```{r}
+# Table for BIC only
+
+model_comp_IC %>% 
+  dplyr::select(data, dist, BIC) %>% 
+  group_by(data) %>% 
+  mutate(delta_within = signif(BIC - min(BIC), digits = 2)) %>% 
+  ungroup() %>% 
+  mutate(delta_across = signif(BIC - min(BIC), digits = 2)) %>% 
+  dplyr::select(., -data)-> data_gt
+
+gt_tbl <- gt(data_gt, rowname_col = "dist")
+
+gt_tbl %>% 
+  tab_header(
+    title = md("**BIC comparisons across levels**")
+  ) %>% 
+  tab_stubhead(label = "Model") %>% 
+  tab_row_group(
+    group = "Multidist",
+    rows = 9
+  ) %>% 
+  tab_row_group(
+    group = "Individual",
+    rows = 1:4
+  ) %>% 
+  tab_row_group(
+    group = "Population", 
+    rows = 5:8
+  ) %>% 
+  cols_label(
+    delta_within = html("&Delta; BIC<sub>within</sub>"),
+    delta_across = html("&Delta; BIC<sub>across</sub>")
+  )
+
+```
+
+## Probability distribution parameters
+We can compare the different parameter values estimated for each distribution and their standard deviations.
+These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
+The x axis in the following plots highlights which individuals have the lowest BIC with that model.
+The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
+Overall, at the population level, the lognormal model had the lowest BIC value.
+
+```{r fig.height=10, fig.width=8}
 
@@
 plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v")
-
-```
-
-## Information criteria comparisons
-
-At the population level, we compared the fit between the four distribution models using different information criteria (AIC, AICc, and BIC).
-At the individual level we considered five different models, four of these models corresponded to each of the four probability distributions, were we essentially allowed for individuals to change parameters, but the overall shape of the distribution was the same.
-For the first four models, we assumed that one probability distribution could accurately describe the movement rates for each individual by changing the distribution's parameters.
-A fifth alternative model considered instead the best fitting model for each individual and calculated the overall information criteria as a combination of the best fitting model for each individual.
-For each of these individual level models, information criteria were calculated based on the number of parameters, sample size and negative log likelihood in the following way
-
-$$AIC{_{indlevel}} = 2\cdot \sum \left ( number parameters \right ) + 2\cdot \sum \left ( -\ln\mathcal{L}() \right )$$
-
-$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$
-
-$$BIC_{indlevel} = \ln{\sum observations(samplesize)} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
-
-```{r}
-nice_prms %>%
-  dplyr::select(., dist, data, deltaBIC, deltaAIC, deltaAICc) %>% 
-  distinct() %>% 
-  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = ic, y = value, color = dist)) +
-  geom_point() +
-  facet_wrap(~data, scales = "free")
-```
-
-```{r}
-prms.df %>% 
-  filter(., data != "pop") %>%
-  dplyr::select(., loglik, n, dist) %>% 
-  distinct() %>%
-  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
-  group_by(dist) %>% 
-  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
-            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
-            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
-    mutate(deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3),
-         deltaBIC = signif(BIC - min(BIC), 3),
-         data = "ind") %>% 
-  full_join(., popind.IC %>% 
-  filter(., data == "pop")) -> popind.IC.comp
-
-```
-
-```{r}
-popind.IC.comp %>% 
-  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = ic, y = value, color = dist)) +
-  geom_point() +
-  facet_wrap(~data, scales = "free")
-```
-
-```{r}
-
-# Get the multi-distribution model fit
-popind.IC %>% 
-  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
-  ungroup() %>% 
-  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
-  as.numeric() -> multi.BIC
-
-popind.IC %>% 
-  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
-  ungroup() %>% 
-  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
-  as.numeric() -> multi.AIC
-
-popind.IC %>% 
-  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
-  ungroup() %>% 
-  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
-  as.numeric()-> multi.AICc
-
-popind.IC.comp %>% 
-  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
-  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>%
-  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = dist, y = value, color = data)) +
-  geom_point() +
-  facet_wrap(~ic, scales = "free") +
-  theme(axis.text.x = element_text(angle = 90))
 
@@
 
-```{r}
+```{r eval = FALSE}
 # Save parameters

### 2020-10-05 appendixA/appendixA.Rmd
included AIC in both parameter plots, and also the table.

@@
          deltaAICc = signif(AICc - min(AICc), 3)) %>% 
-  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms
+  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
+         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black"))-> nice_prms
 ```
@@
 model_comp_IC %>% 
-  dplyr::select(data, dist, BIC) %>% 
+  dplyr::select(data, dist, BIC, AIC) %>% 
   group_by(data) %>% 
-  mutate(delta_within = signif(BIC - min(BIC), digits = 2)) %>% 
+  mutate(delta_BIC_within = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_within = signif(AIC - min(AIC), digits = 2)) %>% 
   ungroup() %>% 
-  mutate(delta_across = signif(BIC - min(BIC), digits = 2)) %>% 
-  dplyr::select(., -data)-> data_gt
+  mutate(delta_BIC_across = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_across = signif(AIC - min(AIC), digits = 2)) %>% 
+  dplyr::select(., -data) %>% 
+  dplyr::select(dist, BIC, delta_BIC_within, delta_BIC_across, AIC, delta_AIC_within, delta_AIC_across)-> data_gt
 
@@
   tab_header(
-    title = md("**BIC comparisons across levels**")
+    title = md("**Model comparisons across levels**")
   ) %>% 
@@
   ) %>% 
+  tab_spanner(
+    label = md("**BIC**"),
+    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
+  ) %>% 
+  tab_spanner(
+    label = md("**AIC**"),
+    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
+  ) %>% 
   cols_label(
-    delta_within = html("&Delta; BIC<sub>within</sub>"),
-    delta_across = html("&Delta; BIC<sub>across</sub>")
+    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
+    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
+    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
+    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
   )
@@
 
-```{r fig.height=10, fig.width=8}
+```{r}
 
-plot_params <- function(prm_data){
+plot_params <- function(prm_data, best_col){
 
@@
 
+  if(best_col == "BIC"){
     prm_data %>% 
@@
     theme(legend.position = "none",
-          axis.text.x = element_text(angle = 45, color = prm_data$best_col))
+          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
   }
+
+  if(best_col == "AIC"){
+    prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
+  }
+  return(plot)
+
+}
+
+```
+
+```{r fig.height=10, fig.width=12}
 
@@
   filter(., dist == "Exponential") %>% 
-  plot_params() +
+  plot_params(., best_col = "BIC") +
   #theme(axis.text.x = element_blank()) +
@@
   filter(., dist == "Gamma" & param == "SHAPE") %>% 
-  plot_params() +
+  plot_params(., best_col = "BIC") +
   #theme(axis.text.x = element_blank()) +
@@
   filter(., dist == "Gamma" & param == "RATE") %>% 
-  plot_params() +
+  plot_params(., best_col = "BIC") +
   #theme(axis.text.x = element_blank()) +
@@
   filter(., dist == "Weibull" & param == "SHAPE") %>% 
-  plot_params() +
+  plot_params(., best_col = "BIC") +
   #theme(axis.text.x = element_blank()) +
@@
   filter(., dist == "Weibull" & param == "SCALE") %>% 
-  plot_params() +
+  plot_params(., best_col = "BIC") +
   #theme(axis.text.x = element_blank()) +
@@
   filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
-  plot_params() -> p6
+  plot_params(., best_col = "BIC") -> p6
 
@@
   filter(., dist == "Lognormal" & param == "SDLOG") %>% 
-  plot_params() ->p7
+  plot_params(., best_col = "BIC") ->p7
 
-plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v")
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid
+
+nice_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params(., best_col = "AIC") -> p6
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params(., best_col = "AIC") ->p7
+
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid
+
+plot_grid(bic_grid, aic_grid, ncol = 2)
 

### 2020-10-05 appendixA/appendixA.Rmd
individual level is ready

@@
 
+data_gt$delta_BIC_within[which(data_gt$dist == "Multidist")] <- NA
+data_gt$delta_AIC_within[which(data_gt$dist == "Multidist")] <- NA
+
 gt_tbl <- gt(data_gt, rowname_col = "dist")
@@
 These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
-The x axis in the following plots highlights which individuals have the lowest BIC with that model.
+The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model.
 The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
-Overall, at the population level, the lognormal model had the lowest BIC value.
+Overall, at the population level, the lognormal model had the lowest AIC and BIC values.
 
@@
 Summary: When comparing population vs individual level fits, at the population level, the lognormal distribution fits the data better, and at the individual level it is the exponential distribution.
+This is shown by both AIC and BIC levels.
 When we focus only on the individual level fits, which distribution fits best depends on the information criteria considered, although most of the individuals are properly characterized by an exponential or lognormal distribution.
@@
 This means that each individual can be characterized by a different distribution and different parameters.
-In the case of AIC and AICc, this probability approach works best for the data, however when considering BIC, the lognormal fit is best, and the mixed distribution approach ties with a weibull distribution at population level.
-Using BIC, a population level modeling approach is the best.
+In the case of AIC and AICc, this probability approach works best for the data, however when considering BIC, the lognormal fit is best, and the mixed distribution approach ties with a Weibull distribution at population level.
 
@@
 Keep in mind that the family level data is reduced because some individuals had unknown family groups and therefore are not included in this analysis.This means that we cannot directly compare distribution fits from family level aggregation with that of individuals.
-To make a comparisson with the population, we need to keep only data points for which we have family information
+To make a comparison with the population, we need to keep only data points for which we have family information
 

### 2020-10-05 appendixA/appendixA.Rmd
Updated families to pretty figures

@@
          dist = str_replace(dist, "lnorm", "Lognormal"),
-         data = str_replace(data, "pop", "POP")) %>% 
+         data = str_replace(data, "pop", "POP"),
+         dist = factor(dist, levels = c("Exponential", "Gamma", "Weibull", "Lognormal"))) %>% 
   mutate(kpars = ifelse(dist == "Exponential", 1, 2),
@@
 ```{r}
+# Filter the data to include only ones with family information
 fams.df <- df %>% 
@@
 
+# Family descriptors
 fams <- paste0("f", 1:6)
 
+# Fit the distributions to family level
 pop.fams <- lapply(dist.used, function(x){fitdist(fams.df$mpm, distr = x)})
-qqcomp(pop.fams, plotstyle = "ggplot") +
-  coord_equal() +
-  geom_point(shape = 16, alpha = 0.5)
 
+# Get data for qqplot at population level
+qqpop.fams <- qqcomp(pop.fams, plotstyle = "ggplot")$data
+names(qqpop.fams) <- c("theoretical", "fdist", "empirical")
+
+# Build parameters data frame
 prms.fams.df <- build_fits_df(pop.fams) %>% 
@@
          dist = dist,
-         data = "pop")
+         data = "POP")
 
-```
-## Family level
-
-```{r}
-
+# Make the fits at the family level
 for(i in 1:length(fams)){
@@
 
-```
-
-Evaluate via qqplots
-```{r}
-
 fams.models.data <- NULL
@@
 
-fams.models.data%>% 
+# Some formatting
+prms.fams.df %>% 
+  mutate(data = str_to_upper(data),
+         param = str_to_upper(param)) -> prms.fams.df
+
+```
+
+```{r fam_QQplots, fig.width=12, fig.height=5}
+qqpop.fams %>% 
+  mutate(fam.group = "POPULATION") %>% 
   ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
-  facet_wrap(~fam.group)+
-    geom_point(cex = 2, alpha = 0.6) +
+  facet_wrap(~fam.group) +
+  #coord_equal() +
+  geom_point(shape = 16, alpha = 0.8, size = 4) +
   geom_abline(intercept = 0, slope = 1) +
@@
   #scale_color_viridis_d() +
-  theme(legend.position = "top") +
+  scale_color_brewer(palette = "Dark2", name = "Distribution", labels = c("Exponential", "Gamma", "Weibull", "Lognormal")) +
+  theme(legend.position = c(0.8, 0.2)) +
+  NULL -> a
+
+fams.models.data %>% 
+  mutate(fam.group = str_to_upper(fam.group)) %>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  #facet_grid(individual~fdist) +
+  facet_wrap(~fam.group)+
+    geom_point(shape = 16, alpha = 0.8, size = 3) +
+    geom_abline(intercept = 0, slope = 1) +
+    labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Dark2") +
+  theme(legend.position = "none") +
   guides(color = guide_legend(title = "Distribution")) +
-  coord_equal()
+  #coord_equal() +
+  NULL -> b
+plot_grid(a,b, rel_widths = c(1,2), labels = "AUTO")
+```
+
+################# COPY PASTE OF INDIVIDUAL
+
+```{r}
+prms.fams.df %>% 
+  mutate(param = str_to_upper(param), 
+         dist = str_replace(dist, "exp", "Exponential"),
+         dist = str_replace(dist, "gamma", "Gamma"),
+         dist = str_replace(dist, "weibull", "Weibull"),
+         dist = str_replace(dist, "lnorm", "Lognormal"),
+         data = str_replace(data, "pop", "POP"),
+         dist = factor(dist, levels = c("Exponential", "Gamma", "Weibull", "Lognormal"))) %>% 
+  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
+         BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
+  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
+         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black"))-> nice_fams_prms
+```
+
+The three information criteria differ in their model choices, with AIC and corrected AIC (AICc) selecting the same models, and BIC selecting different ones.
+
+```{r fig.width=12, fig.height=4}
+# To visualize the differences in the information criteria at the individual level
+nice_fams_prms %>% 
+  dplyr::select(dist, data, deltaAIC, deltaAICc, deltaBIC) %>% 
+  distinct() %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  mutate(plot_alpha = ifelse(value == "0", 1, 0.8)) %>% 
+  ggplot(., aes(x = data, y = value, color = dist 
+                #alpha = plot_alpha
+                )) +
+  facet_wrap(~ic) +
+  geom_point(size = 3) +
+  scale_color_brewer(palette = "Dark2") + 
+  #scale_alpha_continuous(range = c(0.5, 1)) +
+  labs(x = "") +
+  theme(legend.position = "bottom",
+        axis.text.x = element_text(color = c(rep("black", 6), "red"))) +
+  guides(color = guide_legend(title = "Distribution"))
 
 ```
+
+```{r}
+# Create the dataframe that compares the models by information criteria
+nice_fams_prms %>% 
+  filter(., data != "POP") %>%
+  dplyr::select(., loglik, n, dist) %>% 
+  distinct() %>%
+  mutate(kpars = ifelse(dist == "Exponential", 1, 2)) %>% 
+  group_by(dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
+            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
+            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
+    mutate(deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3),
+         deltaBIC = signif(BIC - min(BIC), 3),
+         data = "Family") %>% 
+  full_join(., nice_prms %>%
+              filter(., data == "POP") %>% 
+              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
+              distinct() %>% 
+              mutate(data = "Population")) -> popfam.IC.comp
+
+# Get the multi-distribution model fit
+nice_fams_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaBIC) %>% 
+  dplyr::filter(., data != "POP" & deltaBIC == 0) %>% 
+  distinct() %>% 
+  ungroup() %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  as.numeric() -> multi.BIC
+nice_fams_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAIC) %>% 
+  dplyr::filter(., data != "POP" & deltaAIC == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
+  as.numeric() -> multi.AIC
+nice_fams_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAICc) %>% 
+  dplyr::filter(., data != "POP" & deltaAICc == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
+  as.numeric()-> multi.AICc
+popfam.IC.comp %>% 
+  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
+  bind_rows(., data.frame(dist = "Multidist", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "Multidist")) -> model_comp_fams_IC
+```
+
+```{r}
+# Table for BIC only
+model_comp_fams_IC %>% 
+  dplyr::select(data, dist, BIC, AIC) %>% 
+  group_by(data) %>% 
+  mutate(delta_BIC_within = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_within = signif(AIC - min(AIC), digits = 2)) %>% 
+  ungroup() %>% 
+  mutate(delta_BIC_across = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_across = signif(AIC - min(AIC), digits = 2)) %>% 
+  dplyr::select(., -data) %>% 
+  dplyr::select(dist, BIC, delta_BIC_within, delta_BIC_across, AIC, delta_AIC_within, delta_AIC_across)-> data_gt
+data_gt$delta_BIC_within[which(data_gt$dist == "Multidist")] <- NA
+data_gt$delta_AIC_within[which(data_gt$dist == "Multidist")] <- NA
+gt_tbl <- gt(data_gt, rowname_col = "dist")
+gt_tbl %>% 
+  tab_header(
+    title = md("**Model comparisons across levels**")
+  ) %>% 
+  tab_stubhead(label = "Model") %>% 
+  tab_row_group(
+    group = "Multidist",
+    rows = 9
+  ) %>% 
+  tab_row_group(
+    group = "Family Group",
+    rows = 1:4
+  ) %>% 
+  tab_row_group(
+    group = "Population", 
+    rows = 5:8
+  ) %>% 
+  tab_spanner(
+    label = md("**BIC**"),
+    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
+  ) %>% 
+  tab_spanner(
+    label = md("**AIC**"),
+    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
+  ) %>% 
+  cols_label(
+    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
+    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
+    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
+    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
+  )
+
+```
+
+## Probability distribution parameters
+We can compare the different parameter values estimated for each distribution and their standard deviations.
+These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
+The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model.
+The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
+Overall, at the population level, the lognormal model had the lowest AIC and BIC values.
+
+```{r}
+plot_params <- function(prm_data, best_col){
+
+  prm_data%>% 
+  filter(., data == "POP") %>% 
+  dplyr::select(., estimate, sd) -> pop_est
+
+  title <- paste(prm_data$dist, prm_data$param)
+
+  if(best_col == "BIC"){
+    prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
+  }
+
+  if(best_col == "AIC"){
+    prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
+  }
+  return(plot)
+
+}
+```
+
+```{r fig.height=10, fig.width=12}
+nice_fams_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+nice_fams_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+nice_fams_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+nice_fams_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+nice_fams_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+nice_fams_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params(., best_col = "BIC") -> p6
+nice_fams_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params(., best_col = "BIC") ->p7
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid
+
+nice_fams_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+nice_fams_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+nice_fams_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+nice_fams_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+nice_fams_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+nice_fams_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params(., best_col = "AIC") -> p6
+nice_fams_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params(., best_col = "AIC") ->p7
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid
+plot_grid(bic_grid, aic_grid, ncol = 2)
+```
+
+####################################################################################
+
 ```{r}

### 2020-10-05 appendixA/appendixA.Rmd
finished appendix and saving parameter outputs for simulations

@@
 
-################# COPY PASTE OF INDIVIDUAL
-
 ```{r}
@@
          data = "Family") %>% 
-  full_join(., nice_prms %>%
+  full_join(., nice_fams_prms %>%
               filter(., data == "POP") %>% 
@@
 
-####################################################################################
-
-```{r}
-all_fam_prms <- prms.fams.df %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3))
-```
-
-```{r}
-prms.fams.df %>% 
-  mutate(fit.param = paste(dist, param)) %>% 
-  ggplot(., aes(x = data, y = estimate, color = dist)) +
-  facet_wrap(~fit.param, scales = "free") +
-  geom_point() +
-  geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd)) +
-  theme(legend.position = "none")
-```
-
-## Calculate BIC for comparisons
-
-```{r fig.height=6}
-prms.fams.df %>% 
-  dplyr::select(., loglik, n, dist, data) %>% 
-  distinct() %>% 
-  mutate(kpars = ifelse(dist == "exp", 1, 2),
-         BIC = log(n)*kpars - 2*loglik,
-         AIC = 2*kpars - 2*loglik,
-         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
-  group_by(data) %>% 
-  mutate(deltaBIC = signif(BIC - min(BIC), 3),
-         deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> popfam.IC
-
-popfam.IC %>% 
-  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = ic, y = value, color = dist)) +
-  geom_point() +
-  facet_wrap(~data, scales = "free")
-
-```
-
-Calculate BIC for the model at the family level
-```{r}
-prms.fams.df %>% 
-  filter(., data != "pop") %>%
-  dplyr::select(., loglik, n, dist) %>% 
-  distinct() %>%
-  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
-  group_by(dist) %>% 
-  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
-            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
-            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
-    mutate(deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3),
-         deltaBIC = signif(BIC - min(BIC), 3),
-         data = "fam") %>% 
-  full_join(., popfam.IC %>% 
-  filter(., data == "pop")) -> comp.fams
-
-comp.fams %>% 
-  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = ic, y = value, color = dist)) +
-  geom_point() +
-  facet_wrap(~data, scales = "free")
-
-comp.fams %>% 
-  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = dist, y = value, color = data)) +
-  geom_point() +
-  facet_wrap(~ic, scales = "free")
-
-```
-```{r}
-
-# Get the multi-distribution model fit
-popfam.IC %>% 
-  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
-  ungroup() %>% 
-  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
-  as.numeric() -> multi.BIC
-
-popfam.IC %>% 
-  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
-  ungroup() %>% 
-  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
-  as.numeric() -> multi.AIC
-
-popfam.IC %>% 
-  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
-  ungroup() %>% 
-  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
-  as.numeric()-> multi.AICc
-
-comp.fams %>% 
-  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
-  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>% 
-  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
-  ggplot(., aes(x = dist, y = value, color = data)) +
-  geom_point() +
-  facet_wrap(~ic, scales = "free") +
-  theme(axis.text.x = element_text(angle = 90))
-
-```
-
 Summary.
@@
 
-```{r eval = FALSE}
+```{r}
 # Save parameters
 
-saveRDS(all_indiv_prms, file = "appendixA/popindprms.RDS")
-saveRDS(all_fam_prms, file = "appendixA/popfamprms.RDS")
+saveRDS(nice_prms, file = "appendixA/popindprms.RDS")
+saveRDS(nice_fams_prms, file = "appendixA/popfamprms.RDS")
 

### 2020-10-05 appendixB/05-Simulations.Rmd
Moved simulation stuff to appendix B

---
title: "Simulation of seed dispersal distance"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
    fig_width: 12
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.cap = " ")

```

```{r loadPackages}
library(tidyverse)
library(lubridate)
library(ggpubr)
```

```{r importData}
seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS") %>% 
  mutate(type = ifelse(data == "pop", "population", "individual"))

mixed_ind <- readRDS("appendixA/mixed_ind_seed.RDS")

seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS") %>% 
  mutate(type = ifelse(data == "pop", "population", "family"))

mixed_fam <- readRDS("appendixA/mixed_fam_seed.RDS")

```

```{r eval = FALSE}
# Get all the seed distance data into a single data frame

mixed_mod %>%  
  ungroup() %>% 
  dplyr::select(dispersal, IC) %>%
  mutate(model = "mixed",
         type = str_to_lower(IC)) %>% 
  dplyr::select(model, dispersal, type) -> mixed_data

get_all <- rbind.data.frame(all_seed_data, mixed_data)
saveRDS(get_all, "output/get_all.RDS")

```

```{r}

all_ind <- rbind.data.frame(seed_data_popind, mixed_ind)
#seed_data_popind %>% 
all_ind %>% ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  theme_bw()
```

Get the ldd for the initial models:
```{r}
# how many LDD events for each model for pop or individual

#seed_data_popind %>% 
  all_ind %>% 
  dplyr::filter(dispersal >= 500) %>% 
  mutate(dispersal = 1) %>% 
  group_by(., , model) %>% 
  summarise(nLDD_events = sum(dispersal)) %>% 
  knitr::kable()
```

Summarize some values for these distances:

```{r}
#seed_data_popind %>% 
  all_ind %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
```{r fig.width=12, fig.height=6}
move_model %>% 
  #filter(model != "lnorm_move") %>% 
  ggplot(., aes(x = dispersal, color = movement_model)) + 
  geom_line(stat = "density") +
  theme_bw()
```

# Family level

```{r}
all_fam <- rbind.data.frame(seed_data_popfam, mixed_fam)

```

```{r}
all_fam %>% 
  ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  #geom_boxplot(data = mixed_fam, aes(x = type, y = dispersal)) +
  theme_bw()

```

Get the ldd for the initial models:
```{r}
# how many LDD events for each model for pop or individual

all_fam %>% 
  dplyr::filter(dispersal >= 500) %>% 
  mutate(dispersal = 1) %>% 
  group_by(., , model) %>% 
  summarise(nLDD_events = sum(dispersal)) %>% 
  knitr::kable()
```

Summarize some values for these distances:

```{r}
all_fam %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
```{r fig.width=12, fig.height=6}
move_model %>% 
  #filter(model != "lnorm_move") %>% 
  ggplot(., aes(x = dispersal, color = movement_model)) + 
  geom_line(stat = "density") +
  theme_bw()
```

### 2020-10-05 appendixB/simulation.Rmd
Moved simulation stuff to appendix B

---
title: "simulation results"
subtitle: "Visual comparisons"
output:
  html_document:
      toc: true
bibliography: "../paper/mybibfile.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.cap = " ")

```

```{r importData}
all_seed_data <- readRDS("appendixA/seed.RDS")
mixed_mod <- readRDS("appendixA/seed_data_mixed_model.RDS")
```

```{r loadPackages}
library(tidyverse)
library(lubridate)
library(ggpubr)
```

```{r}
# Get all the seed distance data into a single data frame

mixed_mod %>%  
  ungroup() %>% 
  dplyr::select(dispersal, IC) %>%
  mutate(model = "mixed",
         type = str_to_lower(IC)) %>% 
  dplyr::select(model, dispersal, type) -> mixed_data

get_all <- rbind.data.frame(all_seed_data, mixed_data)
saveRDS(get_all, "output/get_all.RDS")

```

```{r}
all_seed_data %>% 
  ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  theme_bw()
```

Get the ldd for the initial models:
```{r}
# how many LDD events for each model for pop or individual

all_seed_data %>% 
  dplyr::filter(dispersal >= 500) %>% 
  mutate(dispersal = 1) %>% 
  group_by(., type, model) %>% 
  summarise(nLDD_events = sum(dispersal)) %>% 
  knitr::kable()
```

## Try with the mixed distribution model?

```{r}
get_all %>% 
  ggplot(., aes(x = model, y = dispersal, color = type)) +
  geom_boxplot() +
  theme_bw()
```

Summarize some values for these distances:

```{r}
get_all %>% 
  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
         movement_model = paste(str_replace(model, "_move", ""), 
                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
move_model %>% 
  group_by(movement_model) %>% 
  summarise(LDD = sum(ldd),
            prcnt_ldd = 100*mean(ldd),
            avg = mean(dispersal),
            median = median(dispersal),
            max = max(dispersal)) %>% 
  arrange(prcnt_ldd) %>% 
  knitr::kable()
```

Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
```{r fig.width=12, fig.height=6}
move_model %>% 
  filter(model != "lnorm_move") %>% 
  ggplot(., aes(x = dispersal, color = movement_model)) + 
  geom_line(stat = "density") +
  theme_bw()
```

### 2020-10-05 appendixB/simulation.R
new simulations

@@ -110,22 +110,28 @@ set.seed(192)
 
 popind <- readRDS("appendixA/popindprms.RDS")
 
+popind %>%
+  mutate(dist_upper = dist,
+         dist = str_to_lower(dist),
+         dist = str_remove(dist, "onential"),
+         dist = str_replace(dist, "lognormal", "lnorm"),
+         param = str_to_lower(param)) -> popind
 
 # Population level
 popSims <- vector("list", 12000)
 for(i in 1:length(popSims)){
   popSims[[i]] <- main_simulation(nseeds = 5, params = popind %>%
-                                    dplyr::filter(data == "pop"))
+                                    dplyr::filter(data == "POP"))
 }
 
-saveRDS(popSims, "appendixA/populationSims.RDS")
+saveRDS(popSims, "appendixB/populationSims.RDS")
 
 #popSims <- readRDS("appendixA/populationSims.RDS")
 
 # These is the data for each seed that got dispersed
 # Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
 popSeed_data <- get_seed_disp_info(popSims) %>%
-  mutate(data = "pop")
+  mutate(data = "POP")
 
 ggplot(popSeed_data, aes(x = model, y = dispersal)) +
   geom_boxplot()
@@ -172,21 +178,25 @@ for(i in 1:12){
 
 indSims <- setNames(indSims, IDs)
 
-saveRDS(indSims, "appendixA/individualSims.RDS")
+saveRDS(indSims, "appendixB/individualSims.RDS")
 
 #indSims <- readRDS("appendixA/individualSims.RDS")
 
 
 seed_dispersal_popind <- rbind.data.frame(popSeed_data, indSeed_data)
 
-saveRDS(seed_dispersal_popind, file = "appendixA/seed_dispersal_popind.RDS")
+saveRDS(seed_dispersal_popind, file = "appendixB/seed_dispersal_popind.RDS")
 
 
+
+# Find more efficient way of doing this:
 
 # Mixed distribution for individuals
 popind %>%
-  filter(., data != "pop") %>%
-  filter(., deltaBIC == 0)
+  #filter(., data != "POP") %>%
+  filter(., deltaBIC == 0) %>%
+  dplyr::select(dist, data) %>%
+  distinct()
 
 i_exp <- NULL
 for(i in c(1:1000, 3001:5000, 6001:7000, 8001:12000)){
[…]

### 2020-10-05 appendixB/simulation.R
changed seeds and runs setup to the beginning

@@ -7,6 +7,12 @@ library(fitdistrplus)
 
 directory <- "appendixB/"
 
+
+## Parameter setup
+
+nseeds <- 5
+nruns <- 1000
+
 source(paste0(directory, "functions.R"))
 
 # Start with the population level parameters
@@ -23,9 +29,9 @@ popind %>%
          param = str_to_lower(param)) -> popind
 
 # Population level
-popSims <- vector("list", 12000)
+popSims <- vector("list", nruns*12)
 for(i in 1:length(popSims)){
-  popSims[[i]] <- main_simulation(nseeds = 5, params = popind %>%
+  popSims[[i]] <- main_simulation(nseeds = nseeds, params = popind %>%
                                     dplyr::filter(data == "POP"))
 }
 
@@ -58,9 +64,9 @@ popSeed_data %>%
 # Individual level simulation ---------------------------------------------
 
 indSim_fx <- function(paramList, individual){
-  sims <- vector("list", 1000)
+  sims <- vector("list", nruns)
   for(i in 1:length(sims)){
-    sims[[i]] <- main_simulation(nseeds = 5, params = paramList %>%
+    sims[[i]] <- main_simulation(nseeds = nseeds, params = paramList %>%
                                    dplyr::filter(., data == individual))
   }
   return(sims)
@@ -138,9 +144,9 @@ popfam %>%
          param = str_to_lower(param)) -> popfam
 
 # Population level
-popSims.fam <- vector("list", 6000)
+popSims.fam <- vector("list", nruns*6)
 for(i in 1:length(popSims.fam)){
-  popSims.fam[[i]] <- main_simulation(nseeds = 5, params = popfam %>%
+  popSims.fam[[i]] <- main_simulation(nseeds = nseeds, params = popfam %>%
                                     dplyr::filter(data == "POP"))
 }
 
@@ -170,9 +176,9 @@ popSeed_data_fam %>%
 
 # Family level simulation ---------------------------------------------
 famSim_fx <- function(paramList, family_group){
-  sims <- vector("list", 6000)
+  sims <- vector("list", nruns)
   for(i in 1:length(sims)){
-    sims[[i]] <- main_simulation(nseeds = 5, params = paramList %>%
+    sims[[i]] <- main_simulation(nseeds = nseeds, params = paramList %>%
                                    dplyr::filter(., data == family_group))
   }
   return(sims)

### 2020-10-05 appendixB/simulation.R
location of functions

@@ -13,7 +13,7 @@ directory <- "appendixB/"
 nseeds <- 5
 nruns <- 1000
 
-source(paste0(directory, "functions.R"))
+source("appendixB/functions.R")
 
 # Start with the population level parameters
 # I need to set a seed

### 2020-10-05 appendixB/sim10/simulation.R
testing sensitivity

@@ -1,0 +1,242 @@
+
+
+# Start getting seed dispersal simulations
+
+library(tidyverse)
+library(fitdistrplus)
+
+directory <- "appendixB/sim10/"
+
+
+## Parameter setup
+
+nseeds <- 5
+nruns <- 10
+
+source("appendixB/functions.R")
+
+# Start with the population level parameters
+# I need to set a seed
+set.seed(192)
+
+popind <- readRDS("appendixA/popindprms.RDS")
+
+popind %>%
+  mutate(dist_upper = dist,
+         dist = str_to_lower(dist),
+         dist = str_remove(dist, "onential"),
+         dist = str_replace(dist, "lognormal", "lnorm"),
+         param = str_to_lower(param)) -> popind
+
+# Population level
+popSims <- vector("list", nruns*12)
+for(i in 1:length(popSims)){
+  popSims[[i]] <- main_simulation(nseeds = nseeds, params = popind %>%
+                                    dplyr::filter(data == "POP"))
+}
+
+saveRDS(popSims, paste0(directory, "populationSims.RDS"))
+
+#popSims <- readRDS("appendixA/populationSims.RDS")
+
+# These is the data for each seed that got dispersed
+# Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
+popSeed_data <- get_seed_disp_info(popSims) %>%
+  mutate(data = "POP")
+
+ggplot(popSeed_data, aes(x = model, y = dispersal)) +
+  geom_boxplot()
+
+popSeed_data %>%
+  #dplyr::filter(., dispersal > 500) %>%
+  ggplot(., aes(x = dispersal, color = model)) +
+  facet_grid(~model) +
+  geom_line(stat = "density", lwd = 1) +
+  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  #geom_hline(yintercept = 0, color = "grey") +
+  #ylim(0, 0.05) +
+  labs(title = "Population") +
+  #scale_x_log10() +
+  theme_classic()
+
+
+# Individual level simulation ---------------------------------------------
+
+indSim_fx <- function(paramList, individual){
+  sims <- vector("list", nruns)
+  for(i in 1:length(sims)){
[…]

### 2020-10-05 appendixB/sim100/simulation.R

@@ -1,0 +1,242 @@
+
+
+# Start getting seed dispersal simulations
+
+library(tidyverse)
+library(fitdistrplus)
+
+directory <- "appendixB/sim100"
+
+
+## Parameter setup
+
+nseeds <- 5
+nruns <- 100
+
+source("appendixB/functions.R")
+
+# Start with the population level parameters
+# I need to set a seed
+set.seed(192)
+
+popind <- readRDS("appendixA/popindprms.RDS")
+
+popind %>%
+  mutate(dist_upper = dist,
+         dist = str_to_lower(dist),
+         dist = str_remove(dist, "onential"),
+         dist = str_replace(dist, "lognormal", "lnorm"),
+         param = str_to_lower(param)) -> popind
+
+# Population level
+popSims <- vector("list", nruns*12)
+for(i in 1:length(popSims)){
+  popSims[[i]] <- main_simulation(nseeds = nseeds, params = popind %>%
+                                    dplyr::filter(data == "POP"))
+}
+
+saveRDS(popSims, paste0(directory, "populationSims.RDS"))
+
+#popSims <- readRDS("appendixA/populationSims.RDS")
+
+# These is the data for each seed that got dispersed
+# Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
+popSeed_data <- get_seed_disp_info(popSims) %>%
+  mutate(data = "POP")
+
+ggplot(popSeed_data, aes(x = model, y = dispersal)) +
+  geom_boxplot()
+
+popSeed_data %>%
+  #dplyr::filter(., dispersal > 500) %>%
+  ggplot(., aes(x = dispersal, color = model)) +
+  facet_grid(~model) +
+  geom_line(stat = "density", lwd = 1) +
+  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  #geom_hline(yintercept = 0, color = "grey") +
+  #ylim(0, 0.05) +
+  labs(title = "Population") +
+  #scale_x_log10() +
+  theme_classic()
+
+
+# Individual level simulation ---------------------------------------------
+
+indSim_fx <- function(paramList, individual){
+  sims <- vector("list", nruns)
+  for(i in 1:length(sims)){
[…]

### 2020-10-05 appendixB/sim10k/simulation.R

@@ -1,0 +1,242 @@
+
+
+# Start getting seed dispersal simulations
+
+library(tidyverse)
+library(fitdistrplus)
+
+directory <- "appendixB/sim10k"
+
+
+## Parameter setup
+
+nseeds <- 5
+nruns <- 10000
+
+source("appendixB/functions.R")
+
+# Start with the population level parameters
+# I need to set a seed
+set.seed(192)
+
+popind <- readRDS("appendixA/popindprms.RDS")
+
+popind %>%
+  mutate(dist_upper = dist,
+         dist = str_to_lower(dist),
+         dist = str_remove(dist, "onential"),
+         dist = str_replace(dist, "lognormal", "lnorm"),
+         param = str_to_lower(param)) -> popind
+
+# Population level
+popSims <- vector("list", nruns*12)
+for(i in 1:length(popSims)){
+  popSims[[i]] <- main_simulation(nseeds = nseeds, params = popind %>%
+                                    dplyr::filter(data == "POP"))
+}
+
+saveRDS(popSims, paste0(directory, "populationSims.RDS"))
+
+#popSims <- readRDS("appendixA/populationSims.RDS")
+
+# These is the data for each seed that got dispersed
+# Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
+popSeed_data <- get_seed_disp_info(popSims) %>%
+  mutate(data = "POP")
+
+ggplot(popSeed_data, aes(x = model, y = dispersal)) +
+  geom_boxplot()
+
+popSeed_data %>%
+  #dplyr::filter(., dispersal > 500) %>%
+  ggplot(., aes(x = dispersal, color = model)) +
+  facet_grid(~model) +
+  geom_line(stat = "density", lwd = 1) +
+  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  #geom_hline(yintercept = 0, color = "grey") +
+  #ylim(0, 0.05) +
+  labs(title = "Population") +
+  #scale_x_log10() +
+  theme_classic()
+
+
+# Individual level simulation ---------------------------------------------
+
+indSim_fx <- function(paramList, individual){
+  sims <- vector("list", nruns)
+  for(i in 1:length(sims)){
[…]

### 2020-10-05 appendixB/sim10k/simulation.R
changed directory

@@ -5,7 +5,7 @@
 library(tidyverse)
 library(fitdistrplus)
 
-directory <- "appendixB/sim10k"
+directory <- "appendixB/sim10k/"
 
 
 ## Parameter setup

### 2020-10-05 appendixB/sim100/simulation.R
directory change

@@ -5,7 +5,7 @@
 library(tidyverse)
 library(fitdistrplus)
 
-directory <- "appendixB/sim100"
+directory <- "appendixB/sim100/"
 
 
 ## Parameter setup

### 2020-10-05 appendixB/appendixB.Rmd
Creating markdown to show results of seed dispersal

--- 2020-10-05 appendixB/05-Simulations.Rmd
@@
 library(lubridate)
-library(ggpubr)
+library(cowplot)
 ```
@@
 ```{r importData}
-seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS") %>% 
-  mutate(type = ifelse(data == "pop", "population", "individual"))
+seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS")
 
-mixed_ind <- readRDS("appendixA/mixed_ind_seed.RDS")
-
-seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS") %>% 
-  mutate(type = ifelse(data == "pop", "population", "family"))
-
-mixed_fam <- readRDS("appendixA/mixed_fam_seed.RDS")
+seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS")
 
 ```
-
-```{r eval = FALSE}
-# Get all the seed distance data into a single data frame
-
-mixed_mod %>%  
-  ungroup() %>% 
-  dplyr::select(dispersal, IC) %>%
-  mutate(model = "mixed",
-         type = str_to_lower(IC)) %>% 
-  dplyr::select(model, dispersal, type) -> mixed_data
-
-get_all <- rbind.data.frame(all_seed_data, mixed_data)
-saveRDS(get_all, "output/get_all.RDS")
-
-```
-
-```{r}
-
-all_ind <- rbind.data.frame(seed_data_popind, mixed_ind)
-#seed_data_popind %>% 
-all_ind %>% ggplot(., aes(x = model, y = dispersal, color = type)) +
-  geom_boxplot() +
-  theme_bw()
-```
-
-Get the ldd for the initial models:
-```{r}
-# how many LDD events for each model for pop or individual
-
-#seed_data_popind %>% 
-  all_ind %>% 
-  dplyr::filter(dispersal >= 500) %>% 
-  mutate(dispersal = 1) %>% 
-  group_by(., , model) %>% 
-  summarise(nLDD_events = sum(dispersal)) %>% 
-  knitr::kable()
-```
-
-Summarize some values for these distances:
-
-```{r}
-#seed_data_popind %>% 
-  all_ind %>% 
-  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
-         movement_model = paste(str_replace(model, "_move", ""), 
-                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
-move_model %>% 
-  group_by(movement_model) %>% 
-  summarise(LDD = sum(ldd),
-            prcnt_ldd = 100*mean(ldd),
-            avg = mean(dispersal),
-            median = median(dispersal),
-            max = max(dispersal)) %>% 
-  arrange(prcnt_ldd) %>% 
-  knitr::kable()
-```
-
-Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
-```{r fig.width=12, fig.height=6}
-move_model %>% 
-  #filter(model != "lnorm_move") %>% 
-  ggplot(., aes(x = dispersal, color = movement_model)) + 
-  geom_line(stat = "density") +
-  theme_bw()
-```
-
-# Family level
-
-```{r}
-all_fam <- rbind.data.frame(seed_data_popfam, mixed_fam)
-
-```
-
-```{r}
-all_fam %>% 
-  ggplot(., aes(x = model, y = dispersal, color = type)) +
-  geom_boxplot() +
-  #geom_boxplot(data = mixed_fam, aes(x = type, y = dispersal)) +
-  theme_bw()
-
-```
-
-Get the ldd for the initial models:
-```{r}
-# how many LDD events for each model for pop or individual
-
-all_fam %>% 
-  dplyr::filter(dispersal >= 500) %>% 
-  mutate(dispersal = 1) %>% 
-  group_by(., , model) %>% 
-  summarise(nLDD_events = sum(dispersal)) %>% 
-  knitr::kable()
-```
-
-Summarize some values for these distances:
-
-```{r}
-all_fam %>% 
-  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
-         movement_model = paste(str_replace(model, "_move", ""), 
-                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
-move_model %>% 
-  group_by(movement_model) %>% 
-  summarise(LDD = sum(ldd),
-            prcnt_ldd = 100*mean(ldd),
-            avg = mean(dispersal),
-            median = median(dispersal),
-            max = max(dispersal)) %>% 
-  arrange(prcnt_ldd) %>% 
-  knitr::kable()
-```
-
-Keep in mind that the figure only goes to 2000, when the max for lognormal movement models is close to 9000, it really sends the estimates far far. 
-```{r fig.width=12, fig.height=6}
-move_model %>% 
-  #filter(model != "lnorm_move") %>% 
-  ggplot(., aes(x = dispersal, color = movement_model)) + 
-  geom_line(stat = "density") +
-  theme_bw()
-```

### 2020-10-12 appendixB/sim10/appendixB_10.Rmd
restuls for 10 simulation runs

---
title: "Simulation of seed dispersal distance - 10 runs"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
    fig_width: 12
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, fig.cap = " ")

```

```{r loadPackages}
library(tidyverse)
library(lubridate)
library(cowplot)
```

```{r importData}

directory <- "appendixB/sim10/"

seed_data_popind <- readRDS(paste0(directory, "seed_dispersal_popind.RDS"))

seed_data_popfam <- readRDS(paste0(directory, "seed_dispersal_popfam.RDS"))

```

# Seed dispersal distance at the different organizational levels

```{r}
seed_data_popind %>%
  mutate(., type = ifelse(data == "POP", "POP", "IND")) %>% 
  #filter(., dist == "exp") %>% 
  ggplot(., aes(x = data, y = dispersal, color = type)) +
  facet_wrap(~dist, ncol = 4) +
  geom_boxplot() -> a

seed_data_popfam %>%
  mutate(., type = ifelse(data == "POP", "POP", "FAM")) %>% 
  #filter(., dist == "exp") %>% 
  ggplot(., aes(x = data, y = dispersal, color = type)) +
  facet_wrap(~dist, ncol = 4) +
  geom_boxplot() -> b

plot_grid(a, b, nrow = 2)
```

```{r}

seed_data_popind %>%
  mutate(., type = ifelse(data == "POP", "POP", "IND")) %>% 
  #filter(., dist == "exp") %>% 
  ggplot(., aes(x = dispersal, color = type, group = data)) +
  facet_wrap(~dist, ncol = 4) +
  geom_density() +
  scale_x_log10() +
  NULL -> a

seed_data_popfam %>%
  mutate(., type = ifelse(data == "POP", "POP", "FAM")) %>% 
  #filter(., dist == "exp") %>% 
  ggplot(., aes(x = dispersal, color = type, group = data)) +
  facet_wrap(~dist, ncol = 4) +
  geom_density() +
  scale_x_log10() +
  NULL -> b

plot_grid(a, b, nrow = 2)

```

The figure I actually want should have all these box plots on the same one because I'm still missing the mixed distribution one.

```{r}

mixed_ind <- seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>%
  filter(., type == "IND") %>% 
  filter(., bic_b == "1") %>% 
  mutate(type = "BIC") %>% 
  bind_rows(., seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>%
  filter(., type == "IND") %>% 
  filter(., aic_b == "1") %>% 
  mutate(type = "AIC")) %>% 
  mutate(dist = "mixed")

seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
  bind_rows(., mixed_ind) %>% 
  ggplot(., aes(x = dist, y = dispersal, color = type)) +
  #facet_wrap(~dist, scales = "free") +
  geom_boxplot() -> a

mixed_fam <- seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>%
  filter(., type == "FAM") %>% 
  filter(., bic_b == "1") %>% 
  mutate(type = "BIC") %>% 
  bind_rows(., seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>%
  filter(., type == "FAM") %>% 
  filter(., aic_b == "1") %>% 
  mutate(type = "AIC")) %>% 
  mutate(dist = "mixed")

seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
  bind_rows(., mixed_fam) %>% 
  ggplot(., aes(x = dist, y = dispersal, color = type)) +
  #facet_wrap(~dist, scales = "free") +
  geom_boxplot() -> b

plot_grid(a, b, nrow = 2)

```

# Summary stats

Individual level

```{r}
seed_data_popind %>% 
  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
  bind_rows(., mixed_ind) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  knitr::kable()

```

Family level
```{r}
seed_data_popfam %>% 
  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
  bind_rows(., mixed_fam) %>% 
  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
  group_by(type, dist) %>% 
  summarise(n = n(),
            mean_disp = mean(dispersal),
            max_disp = max(dispersal), 
            n_ldd = sum(LDD),
            prcnt_ldd = n_ldd/n) %>% 
  knitr::kable()
```

```{r eval = FALSE}

# Spatial data
sims.ind <- readRDS(paste0(directory, "individualSims.RDS"))

sims.ind %>% 
  map(., "exp_move")

sims.ind$B1[[1]]$exp_move

get_seed_disp_info <- function(simulations){
  models <- c("exp_move", "gam_move", "weib_move", "lnorm_move")

  df <- NULL
  for(i in 1:4){
    oneModel <- map(simulations, models[i])
    dispInfo <- map(oneModel, "seedInfo") %>% 
      unlist()
    dispersal <- map(dispInfo, "seed_disp") %>%
      unlist()

    out <- data.frame(model = models[i], 
                      #dispersal = dispersal,
                      dispInfo)
    df <- rbind.data.frame(df, out)
  }

  return(df)
}

get_seed_disp_info(sims.ind)

IDs <- unique(seed_data_popind$data)[2:13]

indSeed_data <- NULL
indSims <- vector("list", 12)
for(i in 1:12){
  a <- indSim_fx(paramList = popind, individual = IDs[i])

  b <- get_seed_disp_info(a) %>%
    mutate(data = IDs[i])

  indSeed_data <- rbind(indSeed_data, b)

  indSims[[i]] <- a
}

```

### 2020-10-12 appendixB/appendixB.Rmd
appendix B figures

@@
 ```{r importData}
-seed_data_popind <- readRDS("appendixA/seed_dispersal_popind.RDS")
 
-seed_data_popfam <- readRDS("appendixA/seed_dispersal_popfam.RDS")
+directory <- "appendixB/"
+
+seed_data_popind <- readRDS(paste0(directory, "seed_dispersal_popind.RDS"))
+
+seed_data_popfam <- readRDS(paste0(directory, "seed_dispersal_popfam.RDS"))
 
 ```
+
+# Seed dispersal distance at the different organizational levels
+
+```{r}
+seed_data_popind %>%
+  mutate(., type = ifelse(data == "POP", "POP", "IND")) %>% 
+  #filter(., dist == "exp") %>% 
+  ggplot(., aes(x = data, y = dispersal, color = type)) +
+  facet_wrap(~dist, ncol = 4) +
+  geom_boxplot() -> a
+
+seed_data_popfam %>%
+  mutate(., type = ifelse(data == "POP", "POP", "FAM")) %>% 
+  #filter(., dist == "exp") %>% 
+  ggplot(., aes(x = data, y = dispersal, color = type)) +
+  facet_wrap(~dist, ncol = 4) +
+  geom_boxplot() -> b
+
+plot_grid(a, b, nrow = 2)
+```
+
+```{r}
+
+seed_data_popind %>%
+  mutate(., type = ifelse(data == "POP", "POP", "IND")) %>% 
+  #filter(., dist == "exp") %>% 
+  ggplot(., aes(x = dispersal, color = type, group = data)) +
+  facet_wrap(~dist, ncol = 4) +
+  geom_density() +
+  scale_x_log10() +
+  NULL -> a
+
+seed_data_popfam %>%
+  mutate(., type = ifelse(data == "POP", "POP", "FAM")) %>% 
+  #filter(., dist == "exp") %>% 
+  ggplot(., aes(x = dispersal, color = type, group = data)) +
+  facet_wrap(~dist, ncol = 4) +
+  geom_density() +
+  scale_x_log10() +
+  NULL -> b
+
+plot_grid(a, b, nrow = 2)
+
+```
+
+The figure I actually want should have all these box plots on the same one because I'm still missing the mixed distribution one.
+
+```{r}
+
+mixed_ind <- seed_data_popind %>% 
+  mutate(type = ifelse(data == "POP", "POP", "IND")) %>%
+  filter(., type == "IND") %>% 
+  filter(., bic_b == "1") %>% 
+  mutate(type = "BIC") %>% 
+  bind_rows(., seed_data_popind %>% 
+  mutate(type = ifelse(data == "POP", "POP", "IND")) %>%
+  filter(., type == "IND") %>% 
+  filter(., aic_b == "1") %>% 
+  mutate(type = "AIC")) %>% 
+  mutate(dist = "mixed")
+
+seed_data_popind %>% 
+  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
+  bind_rows(., mixed_ind) %>% 
+  ggplot(., aes(x = dist, y = dispersal, color = type)) +
+  #facet_wrap(~dist, scales = "free") +
+  geom_boxplot() -> a
+
+mixed_fam <- seed_data_popfam %>% 
+  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>%
+  filter(., type == "FAM") %>% 
+  filter(., bic_b == "1") %>% 
+  mutate(type = "BIC") %>% 
+  bind_rows(., seed_data_popfam %>% 
+  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>%
+  filter(., type == "FAM") %>% 
+  filter(., aic_b == "1") %>% 
+  mutate(type = "AIC")) %>% 
+  mutate(dist = "mixed")
+
+seed_data_popfam %>% 
+  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
+  bind_rows(., mixed_fam) %>% 
+  ggplot(., aes(x = dist, y = dispersal, color = type)) +
+  #facet_wrap(~dist, scales = "free") +
+  geom_boxplot() -> b
+
+plot_grid(a, b, nrow = 2)
+
+```
+
+# Summary stats
+
+Individual level
+
+```{r}
+seed_data_popind %>% 
+  mutate(type = ifelse(data == "POP", "POP", "IND")) %>% 
+  bind_rows(., mixed_ind) %>% 
+  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
+  group_by(type, dist) %>% 
+  summarise(n = n(),
+            mean_disp = mean(dispersal),
+            max_disp = max(dispersal), 
+            n_ldd = sum(LDD),
+            prcnt_ldd = n_ldd/n) %>% 
+  knitr::kable()
+
+```
+
+Family level
+```{r}
+seed_data_popfam %>% 
+  mutate(type = ifelse(data == "POP", "POP", "FAM")) %>% 
+  bind_rows(., mixed_fam) %>% 
+  mutate(., LDD = ifelse(dispersal >= 500, 1, 0)) %>% 
+  group_by(type, dist) %>% 
+  summarise(n = n(),
+            mean_disp = mean(dispersal),
+            max_disp = max(dispersal), 
+            n_ldd = sum(LDD),
+            prcnt_ldd = n_ldd/n) %>% 
+  knitr::kable()
+```

### 2020-10-12 appendixB/sim10/appendixB_10.Rmd
arranged all tables according to ldd n

@@
             prcnt_ldd = n_ldd/n) %>% 
+  arrange(., desc(prcnt_ldd)) %>% 
   knitr::kable()

### 2020-10-12 paper/paper.Rmd
minimal changes to equations
changed to word output for paper

@@
 title: "Individual Variation in Animal Movement and Effects on Seed Dispersal Distance"
-author:
-- Javiera Rudolph
-- Jose Miguel Ponciano
-- Flavia Montano-Centellas
-- Kimberly Holbrook
-- Bette Loiselle
+
 abstract: |
@@
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
-output: html_document
-linenumbers: yes
+output: 
+  word_document:
+    reference_docx: paper_ref.docx
 bibliography: mybibfile.bib
-layout: 3p
-header-includes:
-- \usepackage{setspace}
-- \doublespacing
-- \usepackage{lineno}
-- \linenumbers
 ---
@@
 
-$$AIC{_{indlevel}} = 2\sum \left ( number parameters \right ) + 2\sum \left ( negative log likelihood \right )$$
+$$AIC{_{indlevel}} = 2 \cdot \sum \left ( number parameters \right ) + 2 \cdot \sum \left ( negative log likelihood \right )$$
 

### 2020-10-12 paper/paper.Rmd
update on methods

@@
 In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion.
-Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds beyond the capacity of wind or other abiotic processes.
-In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance dispersal.
+Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds with them.
+In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance seed dispersal.
 We apply these methods to empirical data sets that contain locations for an aracari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*.
 We combine animal movement data and gut retention time to simulate *Virola* seed dispersal.
-This approach showed that there is significant variation in individual aracari movement patterns which directly influence the estimated number of long-distance dispersa events for *Virola* seeds.
+This approach showed that there is significant variation in individual aracari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds.
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
@@
 The spatial patterns of seed deposited by disperser vectors will determine the probability of seed survival and recruitment, acting upon post-dispersal processes such as density-dependent survival and colonization [@howe2004seed].
-Therefore, at a local scale, seed dispersers will determine whether plant species scape from density-dependence processes [@comita2014testing], whereas at a larger scale, they can determine how quickly plants can cope with habitat and climate shifts [@ibanez2006predicting; @russo_incorporating_2006].
+Therefore, at a local scale, seed dispersers will determine whether plant species escape from density-dependence processes [@comita2014testing], whereas at a larger scale, they can determine how quickly plants can cope with habitat and climate shifts [@ibanez2006predicting; @russo_incorporating_2006].
 
-From the plant perspective, not all seed disperser species provide with the same seed dispersal service, and often relatively few disperser species can have disproportionate effects on seed dispersal [@schupp1993quantity; @jordano2007differential; @schupp_seed_2010; @loayza2014seed].
+From the plant perspective, not all seed dispersers species provide with the same seed dispersal service, and often relatively few disperser species can have disproportionate effects on seed dispersal [@schupp1993quantity; @jordano2007differential; @schupp_seed_2010; @loayza2014seed].
 Frugivores might differ on their selection of plants/fruits for consumption, in their treatment of seed while ingesting and manipulating the fruits, in their processing of seeds if ingested and in the distance where they will discard the seeds [@schupp1993quantity; @schupp_seed_2010; @cortes_integrating_2013].
@@
 Including individual variation in traits (morphological, behavioral and physiological) in seed dispersal studies, can provide new insights into the relative role of different dispersal vectors on seed deposition and ultimately, vegetation structure [@gonzalez-varo_labile_2016].
-In a recent review, Zwolak (2017) summarized the types of intraspecific variation in seed-dispersing animals that might affect the resulting seed dispersal service individuals provide, highlighting differences in sex, size or age (ontogenetic shifts), individual specialization and behavioral syndromes as the most important variation types.
+In a recent review, Zwolak [@zwolak_how_2018] summarized the types of intraspecific variation in seed-dispersing animals that might affect the resulting seed dispersal service individuals provide, highlighting differences in sex, size or age (ontogenetic shifts), individual specialization and behavioral syndromes as the most important variation types.
 Incorporating these intrinsic traits into seed dispersal models may lead to more mechanistic understanding of seed dispersal, allow to build more accurate predictive frameworks of dispersal outcomes [@russo_incorporating_2006] and to identify links between characteristics of dispersal agents and the seed dispersal they provide [@zwolak_how_2018].
@@
 Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patterns of seed dispersal.
-
-The effect of frugivore movement on seed dispersal has been studied and we know that there exists an important link between them [@will_mechanistic_2008; @russo_incorporating_2006; @pegman_exploring_2017].
-Animal movement patterns determine the extent to which seeds get distributed, and this in turn creates a range distribution for plants [@levey_modelling_2008].
-Plants distribution and ranges are largely determined by the seeds that get dispersed the farthest from their parent.
-Animal movement is known to provide these long-distance seeds more than other dispersal sources such as wind or water[@jordano_what_2017].
-Frugivore in particular is associated with longer dispersal, partly influenced by the gut retention time.
-We wanted to understand how individual variation in animal movement can influence the frequency and extent of long-distance seed dispersal events.
-We analyzed aracari telemetry data at the population level and at an individual level, to explore how these could influence seed dispersal.
-In addition to this, we tested several models to understand how the choice of probability distribution associated to the movement kernel can limit or overestimate seed dispersal.
+To understand the consequences of variation in animal movement, we compare seed dispersal estimates from simulation models that incorporate seed retention time and individual, family, or population level animal movement.
 
@@
 ## Seed dispersal simulation
-the goal of this manuscript is to evaluate the effects of variation in animal movement and how these translate to seed dispersal distances.
-We developed an individual-based simulation in order to track single individuals or family groups in various tracking sessions and see how they disperse seeds.
+
+In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement and seed gut retention time (GRT).
+Our simulation time steps were based on one minute intervals, and each simulation started at the origin or source tree, where each individual bird was given five seeds and was allowed to move in the landscape until the simulation ended once all seeds were dropped.
+Each seed's gut retention time was determined at the start of each simulation run, being randomly sampled from a gamma distribution (shape = 4, scale = 5, shift = 8) [@morales_effects_2006] so that the average gut retention time was 28 minutes[@holbrook_dispersal_2009; @holbrook_using_2007].
+For each simulation run, the total simulation time was determined by the largest gut retention time sampled for the five seeds.
+We simulated animal movement using a memoryless process, a random walk with a uniformly distributed angular direction and a random step size chosen from a probability distribution.
+Commonly used probability distributions for sampling the animal movement step size included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
+These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size, with distributions such as the lognormal approaching a levy type walk (not sure this is all correct or makes sense).
 

### 2020-10-12 appendixB/sim100/appendixB_100.Rmd
arranged all tables according to ldd n
changed title

--- 2020-10-12 appendixB/sim10/appendixB_10.Rmd
@@
 ---
-title: "Simulation of seed dispersal distance - 10 runs"
+title: "Simulation of seed dispersal distance - 100 runs"
 author: "Javiera Rudolph"
@@
 
-directory <- "appendixB/sim10/"
+directory <- "appendixB/sim100/"
 

### 2020-10-13 paper/paper.Rmd
changed methods, back to html again

@@
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
-output: 
-  word_document:
-    reference_docx: paper_ref.docx
+output: html_document
 bibliography: mybibfile.bib
@@
 In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement and seed gut retention time (GRT).
-Our simulation time steps were based on one minute intervals, and each simulation started at the origin or source tree, where each individual bird was given five seeds and was allowed to move in the landscape until the simulation ended once all seeds were dropped.
-Each seed's gut retention time was determined at the start of each simulation run, being randomly sampled from a gamma distribution (shape = 4, scale = 5, shift = 8) [@morales_effects_2006] so that the average gut retention time was 28 minutes[@holbrook_dispersal_2009; @holbrook_using_2007].
-For each simulation run, the total simulation time was determined by the largest gut retention time sampled for the five seeds.
+Our landscape consisted of a single source tree at the origin, our simulation time steps were based on one minute intervals, and each simulation started at the source tree (0,0), where each individual bird was given five seeds and was allowed to move freely in the landscape until the simulation ended once all seeds were dropped.
+Each seed's gut retention time was determined at the start of each simulation run, being randomly sampled from a Gamma distribution (shape = 4, scale = 5, shift = 8) [@morales_effects_2006] so that the average gut retention time was 28 minutes[@holbrook_dispersal_2009; @holbrook_using_2007].
+For each simulation run, the total simulation time was determined by the largest gut retention time sampled for the five seeds, therefore, once the last seed was dropped, the simulation ended.
+From the simulation, we calculated the Euclidean distance from the source tree to each of the dropped seeds to determine the seed dispersal distance.
 We simulated animal movement using a memoryless process, a random walk with a uniformly distributed angular direction and a random step size chosen from a probability distribution.
+The simulation proceeded as follows: an individual bird starts the simulation at time zero and location zero zero.
+That bird is given five different seeds, with gut retention time (GRT_I), where GRT is gamma distributed.
+The animal is allowed to move freely across the landscape where at each time point T_i, a movement angle is sampled ~uniform(360) (think of greek letter) and a step size is randomly selected d_i, where D ~ f(x), where f(x) is the probability density function of one of the models we've selected.
+The movement process is repeated and at T_i == GRT_i a seed is dropped at the bird's location (x_i, y_i) and therefore that seed's final locations is (x_i, y_i).
+The simualation ends at T_i = max(GRT_1:5), and seed dispersal distances are calculated from the origin (0,0) to each seed's location (x_i, y_i).
+
+# Simulations at different organizational levels
+
 Commonly used probability distributions for sampling the animal movement step size included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
-These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size, with distributions such as the lognormal approaching a levy type walk (not sure this is all correct or makes sense).
+These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.
 

### 2020-10-13 paper/paper.Rmd
more methods text

@@
 # Simulations at different organizational levels
+
+Our main hypothesis is about the incoporation of variance in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal.
+How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal.
+We explored the effects of individual differences in movement by modifying our base simulation, in which the probability density function used to model animal movement was different between populations or a subcategory.
+In simulations at the population level, we used a single pdf to sample step sizes from, while for individual and family level simulations we used multiple pdfs to sample step sizes from, where each pdf was associated to a specific individual or family group.
 

### 2020-10-13 paper/paper.Rmd
delete previuos section on data collection

@@
 In simulations at the population level, we used a single pdf to sample step sizes from, while for individual and family level simulations we used multiple pdfs to sample step sizes from, where each pdf was associated to a specific individual or family group.
+The pdf for the population level is f(x, sigma), where sigma is the parameters for population, and fx(x, sigma_vector), is for the individual or family level and sigma vector represents a vector of parameters for the pdf, where each parameter corresponds to a different individual or family group.
+We used four different pdfs for our simulations based on used probability distributions for sampling the animal movement step size including an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
+These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.
+We also performed a mixed distribution simulation at the individual and population levels, where each individual or family group would not only have their specific set of parameter estimates, but we also allowed for variaiton in the structure of the pdf.
+Here I should write out how it looks mathematically.
 
-Commonly used probability distributions for sampling the animal movement step size included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
-These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.
-
-  - What is the overall goal of this simulation?
-  - What entails one simulation run
-  - Overall description of how the simulation works
-  - Variables that go into the simulation
-  - Sources I used to reference: jones
-2. Parameterization and source data
-  - Data description
-  - Gut retention time comes from previous literature and averages
-  - Calculations at the different organizational levels
-3. Evaluating fits?
-4. Statistics associated to the simulations
-
-### Data collection/manipulation
+## Data collection/manipulation
 
@@
 In addition to this, the home range of this species was found to be the largest for all the species studied, and therefore it was better suited to study long-distance seed dispersal events.
-
-We used subsequent animal locations to estimate distance moved in a given tracking session, then calculated movement rates per minute for each movement bout.
-We defined a movement bout as the movement occurring between two consecutive GPS locations.
-*Is this ok?
-not sure how to describe how I considered this* We generated a distribution of movement rates and selected the animals that had a minimum of 30 observations giving us a dataset with information on twelve individual birds.
-Unlike previous work by Holbrook [-@holbrook_home_2011] we restricted our analysis to consecutive locations only, to better capture variation in trajectory and movement rates in meters per minute for a given flight session.
-We were not focused on distance to origin from the animal’s perspective, but on movement bouts in a continuous tracking session, in order to estimate trajectory movement, which would directly influence the distance that seeds get dispersed from a focus tree.
 
@@
 We performed summary statistics on seed dispersal distances for each of the models
+
+  - What is the overall goal of this simulation?
+  - What entails one simulation run
+  - Overall description of how the simulation works
+  - Variables that go into the simulation
+  - Sources I used to reference: jones
+2. Parameterization and source data
+  - Data description
+  - Gut retention time comes from previous literature and averages
+  - Calculations at the different organizational levels
+3. Evaluating fits?
+4. Statistics associated to the simulations
 

### 2020-10-13 appendixB/sim10/simulation.R
Getting spatial seed data

@@ -15,6 +15,25 @@ nruns <- 10
 
 source("appendixB/functions.R")
 
+# Change post function
+get_seed_disp_info <- function(simulations){
+  models <- c("exp_move", "gam_move", "weib_move", "lnorm_move")
+
+  df <- NULL
+  for(i in 1:4){
+    oneModel <- map(simulations, models[i])
+    dispInfo <- map_df(oneModel, "seedInfo") %>%
+      rename(dispersal = seed_disp)
+    # dispersal <- map(dispInfo, "seed_disp") %>%
+    #   unlist()
+
+    out <- data.frame(model = models[i], dispInfo)
+    df <- rbind.data.frame(df, out)
+  }
+
+  return(df)
+}
+
 # Start with the population level parameters
 # I need to set a seed
 set.seed(192)

### 2020-10-13 appendixB/functions.R
getting spatial data from seeds.

@@ -87,11 +87,12 @@ get_seed_disp_info <- function(simulations){
   df <- NULL
   for(i in 1:4){
     oneModel <- map(simulations, models[i])
-    dispInfo <- map(oneModel, "seedInfo")
-    dispersal <- map(dispInfo, "seed_disp") %>%
-      unlist()
+    dispInfo <- map_df(oneModel, "seedInfo") %>%
+      rename(dispersal = seed_disp)
+    # dispersal <- map(dispInfo, "seed_disp") %>%
+    #   unlist()
 
-    out <- data.frame(model = models[i], dispersal = dispersal)
+    out <- data.frame(model = models[i], dispInfo)
     df <- rbind.data.frame(df, out)
   }
 

### 2020-10-13 appendixB/simulation.R
Got spatial data for seeds.

@@ -37,7 +37,7 @@ for(i in 1:length(popSims)){
 
 saveRDS(popSims, paste0(directory, "populationSims.RDS"))
 
-#popSims <- readRDS("appendixA/populationSims.RDS")
+#popSims <- readRDS("appendixB/populationSims.RDS")
 
 # These is the data for each seed that got dispersed
 # Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
@@ -91,8 +91,22 @@ indSims <- setNames(indSims, IDs)
 
 saveRDS(indSims, paste0(directory, "individualSims.RDS"))
 
-#indSims <- readRDS("appendixA/individualSims.RDS")
+#indSims <- readRDS("appendixB/individualSims.RDS")
 
+
+IDs <- unique(popind$data)[2:13]
+
+indSeed_data <- NULL
+for(i in 1:12){
+  a <- indSims[[i]]
+
+  b <- get_seed_disp_info(a) %>%
+    mutate(data = IDs[i])
+
+  indSeed_data <- rbind(indSeed_data, b)
+
+  indSims[[i]] <- a
+}
 
 seed_dispersal_popind <- rbind.data.frame(popSeed_data, indSeed_data)
 
@@ -152,6 +166,8 @@ for(i in 1:length(popSims.fam)){
 
 saveRDS(popSims.fam, paste0(directory, "populationSims_family.RDS"))
 
+# popSims.fam <- readRDS(paste0(directory, "populationSims_family.RDS"))
+
 # These is the data for each seed that got dispersed
 # Since there are 5 seeds in each run, with 4 models, each run gets 20 distances
 popSeed_data_fam <- get_seed_disp_info(popSims.fam) %>%
@@ -202,6 +218,21 @@ for(i in 1:6){
 famSims <- setNames(famSims, IDs)
 
 saveRDS(famSims, paste0(directory, "familySims.RDS"))
+
+#famSims <- readRDS(paste0(directory, "familySims.RDS"))
+
+famSeed_data <- NULL
+for(i in 1:6){
+  a <- famSims[[i]]
+
+  b <- get_seed_disp_info(a) %>%
+    mutate(data = IDs_fam[i])
+
+  famSeed_data <- rbind(famSeed_data, b)
+
+  famSims[[i]] <- a
+}
+
 
 
 seed_dispersal_popfam <- rbind.data.frame(popSeed_data_fam, famSeed_data)

### 2020-10-13 paper/figures_tables.Rmd
deleted old figures.

--- 2020-09-28 paper/figures_tables.Rmd
@@
 
-theme_set(theme_bw())
 ```
 
-```{r functions}
+# Layout of steps of one simulation run
 
-# Extract parameters from fitted distributions to the data
-build.fits.df <- function(x){
+# Figure with variation for parameter estimates
 
-  nm <- deparse(substitute(x))
+# Table: Info criteria for family and individual levels
 
-  x %>%
-  map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
-  map(as_tibble) %>%
-  bind_rows()
-}
+# Facetted plot for seed dispersal distances
 
-```
-
-The way we are fitting the data can be visualized as follows, where each curve represents the population, an individual, or a family group:
-
-```{r data}
-# Get the data loaded. We are removing the one value with zero since it won't allow fitting.
-
-load("data/newpointlocs.rda")
-
-df <- newpointlocs %>%
-  dplyr::filter(mpm != 0) %>%
-  ungroup() %>%
-  mutate(Bird_ID = paste0("B", Bird_ID),
-         sqR2n = sqrt(R2n)) %>%
-  group_by_("id", "burst") %>%
-  mutate(cumdt = cumsum(dt)/60) %>%
-  ungroup()
-```
-
-```{r fig.width=10}
-pop_dens_plot <- df %>%
-  ggplot(., aes(x = mpm)) +
-  geom_line(stat = "density", color = "grey", lwd = 1) +
-  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.05) +
-  labs(title = "Population") +
-  theme_classic()
-
-ind_dens_plot <- df %>%
-  ggplot(., aes(x = mpm)) +
-  geom_line(stat = "density", color = "red", lwd = 1) +
-  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.055) +
-  labs(title = "Individual") +
-  theme_classic()
-
-fam_dens_plot <- df %>%
-  filter(., fam_g != "unknown") %>%
-  ggplot(., aes(x = mpm)) +
-  geom_line(stat = "density", color = "red", lwd = 1) +
-  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  ylim(0, 0.055) +
-  labs(title = "Family") +
-  theme_classic()
-
-fam_zoom <- fam_dens_plot +
-  coord_cartesian(ylim = c(0, 0.01), xlim = c(50, 210))
-
-```
-
-```{r}
-
-ind_zoom <- ind_dens_plot +
-  coord_cartesian(
-    ylim = c(0, 0.01),
-    xlim = c(60, 180))
-
-ind_grob <- ggplotGrob(ind_zoom)
-
-ind_dens_plot +
-  annotation_custom(grob = ind_grob, xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
-```
-
-```{r}
-
-fam_zoom <- fam_dens_plot +
-  coord_cartesian(
-    ylim = c(0, 0.01),
-    xlim = c(50, 210))
-
-fam_dens_plot +
-  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = 50 , xmax = 200 , ymin = 0.02 , ymax = 0.05)
-```
-
-```{r}
-ggarrange(ind_dens_plot, fam_dens_plot, nrow = 2)
-```
+# Density figures from which step and grt are sampled from

### 2020-10-14 paper/paper.Rmd
word output
progress

@@
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
-output: html_document
+output: word_document
 bibliography: mybibfile.bib
@@
 We simulated animal movement using a memoryless process, a random walk with a uniformly distributed angular direction and a random step size chosen from a probability distribution.
+
+Caption for figure 1.
+Simulation example.
 The simulation proceeded as follows: an individual bird starts the simulation at time zero and location zero zero.
@@
 How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal.
-We explored the effects of individual differences in movement by modifying our base simulation, in which the probability density function used to model animal movement was different between populations or a subcategory.
-In simulations at the population level, we used a single pdf to sample step sizes from, while for individual and family level simulations we used multiple pdfs to sample step sizes from, where each pdf was associated to a specific individual or family group.
-The pdf for the population level is f(x, sigma), where sigma is the parameters for population, and fx(x, sigma_vector), is for the individual or family level and sigma vector represents a vector of parameters for the pdf, where each parameter corresponds to a different individual or family group.
-We used four different pdfs for our simulations based on used probability distributions for sampling the animal movement step size including an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
+We explored the effects of individual differences in movement by modifying our base simulation, described above, in which the probability density function used to sample step sizes was different between population, individual, or family level simulations.
+What we consider as population level simulations are those where all birds share the same probability density to sample step sizes from, while for individual and family level simulations we use the same overall pdf, but allow for variation in the parameters specified for such function, where each set of parameters corresponds to a specific individual or family group.
+We also performed simulations in which we allowed for variation not only of parameters, but also of the overall structure of the pdf for sampling step sizes, this means that each individual or family group was allowed to have it's own pdf and its own set of parameters (Box 1 or table 1 with description of models, either the movement or simulation).
+We used four different probability density functions for sampling the animal movement step size, these included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
 These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.
-We also performed a mixed distribution simulation at the individual and population levels, where each individual or family group would not only have their specific set of parameter estimates, but we also allowed for variaiton in the structure of the pdf.
-Here I should write out how it looks mathematically.
+**should add number of runs?
+or mention that that is in appendix B**
 
-## Data collection/manipulation
+# Parameterization
 
@@
 We focused on the data from the many-banded aracari, *Pteroglossus pluricinctus*, because a higher number of recorded locations were available.
-In addition to this, the home range of this species was found to be the largest for all the species studied, and therefore it was better suited to study long-distance seed dispersal events.
+In addition to this, the home range of this species was found to be the largest for all the toucan species studied, and therefore it was better suited to study long-distance seed dispersal events.
 
 ### Animal movement probability distributions  
+What data am I using for this parameterization?
+It is radiotracking data, and the information on continuous trajectories for each tracked bird, to scale those distances into number of meters moved per minute for each tracking segment.
+I consider a tracking segment as the distance moved between two continuous radio tracking detections.
+(Check Kimberly's paper), because here we are taking advantage of all the tracking data since there are different tracking interval times.
+Then, we used that data to fit the four models described above, and did it at the different organizational levels.
+We considered population level data, as all the data pooled from all individuals tracked, and fit the four distributions to that data to estimate parameters.
+At the individual level, we fit the four pdfs for the data in respect to each individual.
+For the family level data, we used only a subset of the total data set to include only individuals for which family level information existed.
+Because these are social individuals, they tend to move with their group and so we their movements may be correlated.
+We wanted to explore if there were any differences at the family group levels.
+We fit the four pdfs to the subset of this data, as the subset population level, and then fit each distribution to the data associated to each of the family groups.
+We used the parameters estimated from these fits to sample step sizes for our simulation models.
+We also evaluated the fit of each of these distributions visually through qq plots (found in appendix A), and further details on data organization and model fitting can be found in the online repository.
 
-In this study, we consider population level when we consider all the tracking data together as a whole.
-For population level analysis we make the assumption that there is no individual variation in movement rates and therefore a single movement rate model can describe all individuals in that population.
-For the case of individual level analysis, we consider individual variation by analyzing the movement rates separately and fitting a probability distribution model to the tracking data for each individual.
-Within this framework we consider that animal movement rates (number of meters moved per minute in each individual movement bout) can be described with four different probability distribution models: an exponential distribution [@jones_closing_2017], a gamma distribution, a weibull distribution [@morales_effects_2006], and a lognormal distribution [@levey_modelling_2008].
-(Comment: where do you think I should include a description of these different distributions?) The fit of each model to the data was analyzed visually via qqplots (See supplementary information).
-
-At the population level, we compared the fit between the four distribution models using different information criteria (AIC, AICc, and BIC).
-At the individual level we considered five different models, four of these models corresponded to each of the four probability distributions.
-For the first four models, we assumed that one probability distribution could accurately describe the movement rates for each individual by changing the distribution's parameters.
-A fith alternative model considered instead the best fitting model for each individual and calculated the overall information criteria as a combination of the best fitting model for each individual.
-For each of these indivual level models, information criteria were calculated based on the number of parameters, sample size and negative log likelihood in the following way
+### Model selection? for the step size
 
@@
 
-### Seed dispersal simulation
-
-To understand the impact of individual animal movement rates over seed dispersal distances, we built a simulation model which took into account animal movement and seed gut retention time (GRT).
-Each simulation run consisted of an individual bird who was given five seeds at the start of the simulation.
-Each seed's gut retention time was randomly sampled from a Gamma distribution based on previously collected data [@holbrook_home_2011] and out of the five seeds the largest GRT determined the simulation time for each run.
-The simulated bird would start at point (0,0) and move across the landscape in a random walk, with angle of movement and speed determined by one minute time steps.
-At each minute time step, an angle of movement would be sampled from a uniform distribution and a movement rate sampled from one of movement rate models (exponential, gamma, lognormal or weibull).
-Seeds would get dropped at the bird's position at the time the simulation reached each seed's GRT and the simulation run would end once the bird dropped all five seeds.
-At the population level, we had four different simulations, each corresponding to one of the probability distributions being tested for animal movement rates.
-We performed 12,000 individual simulation runs with each distribution and estimated seed dispersal distances for each of the seeds.
-In the case of individual level simulations, we had 1000 simulation runs for each individual (twelve individuals, with a total of 12,000 simulation runs) and we did this with each of the four distribution models.
-Finally, we considered a (heterogeneous/mixed?
-need to check with JMP on terminology) model where we selected the best fitting movement rate model for each individual and used it to parameterize the simulation.
-For these mixed models, the probability distribution used to sample movement rates would be the best fitting distribution for each individual's movement rates (the target distribution as determined by AIC or BIC), and not a common distribution with different parameters for each individual (as in the previous individual level simulation runs).
-Whether at population level or individual level, the output of the simulation runs for each model is the dispersal distance for 60,000 seeds.
-We performed summary statistics on seed dispersal distances for each of the models
-
-  - What is the overall goal of this simulation?
-  - What entails one simulation run
-  - Overall description of how the simulation works
-  - Variables that go into the simulation
-  - Sources I used to reference: jones
-2. Parameterization and source data
-  - Data description
-  - Gut retention time comes from previous literature and averages
-  - Calculations at the different organizational levels
-3. Evaluating fits?
-4. Statistics associated to the simulations
+# Statistics associated to the simulations
+We analyzed simulation outputs and had seed dispersal distance as our main focus.
+We calculated summary statistics for each of the dispersal distances, and estimated the percentage of long distance dispersal events.
+Using the 500 meter threshold which was determined in previous work.
 
@@
 
-```{r}
-popIC_table <- readRDS(file = "output/popIC_table.RDS")
-
-popIC_table %>% 
-  knitr::kable()
-```
-
 At the individual level, we observed similar outcomes, where the lognormal distribution consistently overestimated the data, whereas the other distributions considered did not.
 When comparing across distribution models at the individual level, AIC and AICc showed the lognormal fit as the best one followed by the exponential model, whereas the BIC had the exponential as the best model followed by the lognormal.
-
-```{r}
-indIC_table <- readRDS(file = "output/indIC_table.RDS")
-
-indIC_table %>% 
-  knitr::kable()
-```
 
@@
 However, BIC values show that only when we consider the exponential distribution model does the individual level do a better fitting than the population, with all other models having higher BIC values for the models that include individual heterogeneity.
-
-```{r}
-AIC_table <- readRDS("manuscript/AIC_table.RDS")
-
-AIC_table %>%
-  transmute(distribution,
-          aic.pop.ind = AIC.pop - AIC.ind,
-         aicc.pop.ind = AICc.pop - AICc.ind,
-         bic.pop.ind = BIC.pop-BIC.ind) %>% 
-  knitr::kable()
-```
 
@@
 
-```{r}
-allIC_table <- readRDS(file = "output/allIC_table.RDS")
-
-head(allIC_table) %>% 
-  knitr::kable()
-```
-
 ### Seed Dispersal Distances
@@
 
-```{r}
+## Discussion
 
-get_all <- readRDS("output/get_all.RDS")
-
-get_all %>% 
-  ggplot(., aes(x = model, y = dispersal, color = type)) +
-  geom_boxplot() +
-  theme_bw()
-```
-
-Summarize some values for these distances. Is this table necessary? or how to reduce it? Do I need to make it smaller?
-
-```{r}
-get_all %>% 
-  mutate(ldd = ifelse(dispersal >= 500, 1, 0),
-         movement_model = paste(str_replace(model, "_move", ""), 
-                                 str_sub(type, start=1, end=3), sep = "_")) -> move_model
-move_model %>% 
-  group_by(movement_model) %>% 
-  summarise(LDD = sum(ldd),
-            prcnt_ldd = 100*mean(ldd),
-            avg = mean(dispersal),
-            median = median(dispersal),
-            max = max(dispersal)) %>% 
-  arrange(prcnt_ldd) %>% 
-  knitr::kable()
-```
-
-## Discussion
+added Oct 2020: call for the need for more complex animal movement models when running seed dispersal simulations.
+Even the posibility of mixed distribution models, where not only we allow for each individual or fmailiy group to have it's own model, but also use multiple distributions for each.
+The short movements performed by these animals may be better described by a different distribution than those performed at longer intervals.
 

### 2020-12-28 paper/paper.Rmd
update article

@@
 title: "Individual Variation in Animal Movement and Effects on Seed Dispersal Distance"
-
 abstract: |
@@
 In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance seed dispersal.
-We apply these methods to empirical data sets that contain locations for an aracari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*.
+We apply these methods to empirical data sets that contain locations for an araçari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*.
 We combine animal movement data and gut retention time to simulate *Virola* seed dispersal.
-This approach showed that there is significant variation in individual aracari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds.
+This approach showed that there is significant variation in individual araçari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds.
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
-output: word_document
+output:
+  word_document: default
+  html_document:
+    df_print: paged
 bibliography: mybibfile.bib
@@
 In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement and seed gut retention time (GRT).
-Our landscape consisted of a single source tree at the origin, our simulation time steps were based on one minute intervals, and each simulation started at the source tree (0,0), where each individual bird was given five seeds and was allowed to move freely in the landscape until the simulation ended once all seeds were dropped.
+Our landscape consisted of a single source tree at the origin, our simulation time steps were based on one minute intervals, and each simulation started at the source tree (0,0), where each individual bird was given five seeds and was allowed to move freely in the landscape until the simulation ended once all seeds were dropped, Figure1.
 Each seed's gut retention time was determined at the start of each simulation run, being randomly sampled from a Gamma distribution (shape = 4, scale = 5, shift = 8) [@morales_effects_2006] so that the average gut retention time was 28 minutes[@holbrook_dispersal_2009; @holbrook_using_2007].
 For each simulation run, the total simulation time was determined by the largest gut retention time sampled for the five seeds, therefore, once the last seed was dropped, the simulation ended.
-From the simulation, we calculated the Euclidean distance from the source tree to each of the dropped seeds to determine the seed dispersal distance.
+We calculated the Euclidean distance from the source tree to each of the dropped seeds to determine their seed dispersal distance.
 We simulated animal movement using a memoryless process, a random walk with a uniformly distributed angular direction and a random step size chosen from a probability distribution.
+The probability distribution chosen to simulate step size varied according to the different models we propose in Table1.
 
@@
 
-Our main hypothesis is about the incoporation of variance in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal.
+Our main hypothesis is about the incorporation of variation in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal.
 How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal.
@@
 
-We focused our study on the many-banded aracari (*Pterglossus pluricinctus*) and its role as a frugivore of the *Virola flexuosa* tree.
+We focused our study on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan, and its role as a frugivore of the *Virola flexuosa* tree.
 A subset of animal movement data collected in a previous study [@holbrook_home_2011] was selected and used towards our models and simulations.
-In this previous study, Aracari home ranges, average movement distances, patterns and movement rates were estimated for tracked birds over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest.
+In this previous study, araçari home ranges, average movement distances, patterns and movement rates were estimated for tracked birds over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest.
 Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
-We focused on the data from the many-banded aracari, *Pteroglossus pluricinctus*, because a higher number of recorded locations were available.
-In addition to this, the home range of this species was found to be the largest for all the toucan species studied, and therefore it was better suited to study long-distance seed dispersal events.
+Although this previous study included two larger Ramphastids as well, we used data only from the many-banded araçari, because a higher number of recorded locations were available.
+In addition to this, the home range of this species was found to be the largest for all the species studied, and therefore it was better suited to study long-distance seed dispersal events.
 

### 2021-01-04 paper/paper.Rmd
Updated introduction

@@
 abstract: |
-  Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms.
+  I don't like this abstract.
+Revisit at the end...Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms.
 In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion.
@@
 output:
-  word_document: default
+  word_document:
+    reference_docx: paper_ref.docx
   html_document:
@@
 
-Differences in behavior among individuals (i.e.
-behavioral syndromes sensu [@sih2004behavioral]) can have remarkable consequences on ecological and evolutionary processes [@wolf_animal_2012].
-For vertebrate dispersed plants, animal behavior will inﬂuence seed shadows and few species, or even individuals, might provide unique, high value dispersal services by moving farther distances from parental plants [@schupp_seed_2010].
+In this paper, we focus on the implications of intraspecific variation in animal movement for seed dispersal distances and seed aggregation across the landscape.
+To understand the consequences of this variation in movement, we developed a spatially-explicit individual-based model of the many-banded aracari, *Pteroglossus pluricinctus*, one of the primary frugivores of the Amazonian canopy tree *Virola flexuosa*.
+Also, previous studies focused on this system have shown that *P.
+pluricintus* is able to disperse seeds across long distances [@holbrook_using_2007; @holbrook_dispersal_2009; @holbrook_home_2011], an important for plant population.
 Long distance dispersal (LDD) events are crucial to reaching suitable sites to germinate and establish and to colonize new habitats [@nathan2006long].
 Furthermore, rare events (often overlooked) are critical for dispersal and might have a large effect on resulting plant demography [@loayza2014seed].
-Incorporating animal behavior and the individual distances they carry seeds into seed dispersal models might result in better predictions of seed shadow and better inform about the resulting patterns of seed dispersal.
-To understand the consequences of variation in animal movement, we compare seed dispersal estimates from simulation models that incorporate seed retention time and individual, family, or population level animal movement.
+Our first objective in this work was to study the differences of simulated seed shadows between models with and without underlying variability in animal movement.
+The second objective focused on quantifying the differences of LDD events reflected between seed shadows.
+Lastly, our third objective focused on the spatial spread between seeds, and how individual variation in animal movement affects seed aggregation.
+Identifying the implications of individual variation in animal movement over seed dispersal estimates can help us improve future models and understand the effects of frugivore traits on plant population dynamics.
 

### 2021-01-04 paper/paper.Rmd
simulation model description update.

@@
 # Methods
-## Seed dispersal simulation
+## Model description
 
-In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement and seed gut retention time (GRT).
+To study the effects of individual variation in animal movement over final dispersal distances of foraged seeds, we developed a spatially-explicit individual-based model in a homogenous landscape consisting of a single source tree.
+We incorporated animal movement focusing on two characteristics, a movement distance (MD) sampled from a probability density distribution, and a movement angle (MA).
+In addition to this, we included gut retention time (GRT), the time that ingested seeds stay within the frugivore until they are dropped.
+The animal was allowed to move freely within the landscape, and GRT determined when a seed would get dispersed.
+Once a seed was dropped, its location was recorded and seed dispersal distance was estimated as the distance from the origin to the seed's location.
+The average seed dispersal distance for each simulation run was calculated and used to estimate seed dispersion, calculated as the mean distance of each seed to the average location of all seeds in the run [@jones_closing_2017].
+For each simulation run, the simulation started at the source tree, an animal received a specific number of seeds and each seed was assigned a specific GRT sampled from a gamma distribution [@morales_effects_2006].
+The simulation was based on one minute time steps, where at each time step a movement distance (MD) and movement angle (MA) would determine the path for the animal to follow.
+For each seed, the location where it would get dropped was based on the animal's location at the time it reached the GRT for each of the seeds.
+The total simulation time for each run was determined by the largest GRT sampled for that specific simulation run.
+Once all seeds were dropped, the simulation run ended.
+
+<!-- Here I would like to have a figure that incorporates all these different simulation components as a self explanatory box for how a simulation run happens, and what data goes in, what data is calculated and comes out.
+-->
+
+In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement distances and seed gut retention time (GRT).
 Our landscape consisted of a single source tree at the origin,  our simulation time steps were based on one minute intervals, and each simulation started at the source tree (0,0), where each individual bird was given five seeds and was allowed to move freely in the landscape until the simulation ended once all seeds were dropped, Figure1.

### 2021-01-05 paper/paper.Rmd
working on figure 1

@@
 The total simulation time for each run was determined by the largest GRT sampled for that specific simulation run.
-Once all seeds were dropped, the simulation run ended.
+Each simulation run focused on one individual animal dispersing seeds from one focus tree.
+Once all seeds in that run were dropped by the animal, the simulation run ended.
+
+<!--- I need to include in that first paragraph how we are comparing between models with and without individual variation--->
+
+```{r}
+
+library(ggplot2)
+
+# Panel 1: landscape with tree in the center, origin
+
+df <- data.frame()
+ggplot(df) + xlim(-100, 100) + ylim(-100, 100) + 
+  theme(
+  panel.background = element_rect(fill = "lightblue",
+                                colour = "lightblue",
+                                size = 0.5, linetype = "solid"),
+  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
+                                colour = "white"), 
+  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
+                                colour = "white")
+  ) +
+  coord_equal() +
+  geom_point(aes(x = 0, y = 0), color = "red")
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+
+grt_data <- rgamma(5, shape = 5, rate = 1/4) + 8
+
+# Panel 3: Exponential distribution used for animal movement lengths
+
+# Panel 5: Animal trajectory and locations of the seeds at the time the seeds are dropped
+
+# Panel 6: Calculation of seed dispersal distances to the focus tree
+
+# Panel 7: Calculation of seed dispersion
+```
 

### 2021-01-05 paper/paper.Rmd
figure 1 updates

--- 2021-01-04 paper/paper.Rmd
@@
 The total simulation time for each run was determined by the largest GRT sampled for that specific simulation run.
-Once all seeds were dropped, the simulation run ended.
+Each simulation run focused on one individual animal dispersing seeds from one focus tree.
+Once all seeds in that run were dropped by the animal, the simulation run ended.
+
+<!--- I need to include in that first paragraph how we are comparing between models with and without individual variation--->
+
+```{r}
+set.seed(1)
+library(ggplot2)
+library(aracari)
+
+data(ptpl)
+# Panel 1: landscape with tree in the center, origin
+
+df <- data.frame()
+ggplot(df) + xlim(-100, 100) + ylim(-100, 100) + 
+  theme(
+  panel.background = element_rect(fill = "lightblue",
+                                colour = "lightblue",
+                                size = 0.5, linetype = "solid"),
+  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
+                                colour = "white"), 
+  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
+                                colour = "white")
+  ) +
+  coord_equal() +
+  geom_point(aes(x = 0, y = 0), color = "green") -> p
+
+p
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0)) +
+  theme_bw() + labs(x = "Time in minutes")
+
+# Panel 3: Exponential distribution used for animal movement lengths
+rate <- 1/mean(ptpl$mpm)
+md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
+ggplot(md_dens, aes(x = dat)) +
+  geom_density() + 
+  theme_bw() + labs(x = "Length of movement in one minute")
+
+# Panel 5: Animal trajectory and locations of the seeds at the time the seeds are dropped
+
+distance <- sample(md_dens$dat, tt)
+angle <- runif(tt, min = 0, max = 360)
+distx <- distance*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- distance*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+seed_loc <- merge(animalTraj, grt_data, by = "time")
+mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
+
+ggplot() +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc)) +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(aes(x = 0, y = 0), color = "green")
+
+# Panel 6: Calculation of seed dispersal distances to the focus tree
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(aes(x = 0, y = 0), color = "green") +
+  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0))
+
+# Panel 7: Calculation of seed dispersion
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue") +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y))
+```
 

### 2021-01-05 paper/paper.Rmd
Draft of figure 1

--- 2021-01-04 paper/paper.Rmd
@@
 The total simulation time for each run was determined by the largest GRT sampled for that specific simulation run.
-Once all seeds were dropped, the simulation run ended.
+Each simulation run focused on one individual animal dispersing seeds from one focus tree.
+Once all seeds in that run were dropped by the animal, the simulation run ended.
+
+<!--- I need to include in that first paragraph how we are comparing between models with and without individual variation--->
+
+```{r}
+set.seed(5)
+library(ggplot2)
+library(aracari)
+library(cowplot)
+
+data(ptpl)
+# Panel 1: landscape with tree in the center, origin
+
+df <- data.frame()
+ggplot(df) + xlim(-100, 100) + ylim(-100, 100) + 
+  theme(
+  panel.background = element_rect(fill = "lightblue",
+                                colour = "lightblue",
+                                size = 0.5, linetype = "solid"),
+  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
+                                colour = "white"), 
+  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
+                                colour = "white")
+  ) +
+  coord_equal() +
+  geom_point(aes(x = 0, y = 0), color = "green") -> p1
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0)) +
+  theme_bw() + labs(x = "Time in minutes") -> p2
+
+# Panel 3: Exponential distribution used for animal movement lengths
+rate <- 1/mean(ptpl$mpm)
+md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
+ggplot(md_dens, aes(x = dat)) +
+  geom_density() + 
+  theme_bw() + labs(x = "Length of movement in one minute") -> p3
+
+# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
+
+distance <- sample(md_dens$dat, tt)
+angle <- runif(tt, min = 0, max = 360)
+distx <- distance*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- distance*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+seed_loc <- merge(animalTraj, grt_data, by = "time")
+mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
+
+ggplot() +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc)) +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(aes(x = 0, y = 0), color = "green") -> p4
+
+# Panel 5: Calculation of seed dispersal distances to the focus tree
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(aes(x = 0, y = 0), color = "green") +
+  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0)) -> p5
+
+# Panel 6: Calculation of seed dispersion
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
+  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue") +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y)) -> p6
+
+# ALL
+plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], nrow = 3)
+
+```
 

### 2021-01-07 paper/paper.Rmd
Figure 1 updates
Figures updates

@@
 
-```{r}
+```{r eval = TRUE, fig.width=6}
 set.seed(5)
@@
 # ALL
-plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], nrow = 3)
+plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], label_size = 10, nrow = 3)
 

### 2021-01-08 paper/simple_exp_paper.R
testing a simple simulation with exp movement lengths

@@ -1,0 +1,49 @@
+
+
+# how many seeds each bird gets on a simulation run, which is equivalent to how many fruits in a foraging session in the same tree
+
+# nseeds <- round(runif(1, 3, 6))
+nseeds <- 5
+
+# Sample a random Gut Retention Time for each one of the seeds
+grt_tt <- round(rgamma(nseeds, shape = 4, scale = 5) + 8)
+
+# Maximum gut retention time determines the simulation time
+tt <- max(grt_tt)
+
+movrate <- 28
+
+# Sample movement distances from an exponential distribution. These are the lengths that the animal moves at each time step in minutes.
+movedist <- rexp(tt, 1/movrate)
+
+# Movement algorithm for this random walk. Sample a random angle of movement from a uniform distribution. Determine the movement in x and y, the animal's trajectory is the cumulative sum of those. We are not imposing any limits to the area of movement.
+angle <- runif(tt, min = 0, max = 360)
+distx <- movedist*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- movedist*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+
+# Determine where the seeds are dropped based on the animal's location.
+seed_loc <- data.frame(seed_id = 1:nseeds, time = grt_tt)
+seed_loc <- merge(animalTraj, seed_loc, by = "time")
+seed_loc$dispersal <- sqrt(seed_loc$xloc^2 + seed_loc$yloc^2)
+
+# Calculate the mean location of seeds
+x_m <- mean(seed_loc$xloc)
+y_m <- mean(seed_loc$yloc)
+mean_dispersal <- mean(seed_loc$dispersal)
+
+# Calculate seed dispersion
+xi <- (x_m - seed_loc$xloc)^2
+yi <- (y_m - seed_loc$yloc)^2
+seed_dispersion <- sum(sqrt(xi + yi))/nseeds
+
+par(mfrow = c(1,3))
+hist(movedist, main = "MD")
+plot(x = xloc, y = yloc, type = "l", main = "Movement")
+points(x = seed_loc$xloc, y = seed_loc$yloc, col = "blue", pch = 16)
+hist(seed_loc$dispersal, main = "Dispersal")
+abline(v = mean_dispersal, col = "red")
+
+

### 2021-01-08 paper/paper.Rmd
Moved text over to a scrap file

@@
 # Methods
-## Model description
+## Simulation description
 
@@
 In addition to this, we included gut retention time (GRT), the time that ingested seeds stay within the frugivore until they are dropped.
-The animal was allowed to move freely within the landscape, and GRT determined when a seed would get dispersed.
+The animal was allowed to move freely within the landscape, and GRT determined when the animal would drop a seed.
 Once a seed was dropped, its location was recorded and seed dispersal distance was estimated as the distance from the origin to the seed's location.
@@
 
-<!--- I need to include in that first paragraph how we are comparing between models with and without individual variation--->
+## Study design
+
+To understand the consequences of individual variation in animal movement and how these influence seed dispersal distances, we simulated two different scenarios by varying the movement of individual animals in each of those scenarios.
+We used our first scenario as our null model, in which all the individuals from the simulation had the same average movement rate ($\lambda_1 = \lambda_2 = ...
+= \lambda_n$), used as the parameter in the probability density function, and thus their movement distances per unit of time were sampled from the same probability distribution ($f(x;\lambda) = \lambda e^{-\lambda x}$).
+Our second scenario included individual variation in animal movement by incorporating different movement rates for each individual ($\lambda_1 = \lambda_2 = ...
+= \lambda_n$), which meant that movement distances would be sampled from probability distributions with different parameters ($f(x;\lambda_i) = \lambda_i e^{-\lambda_i x}$).
+Considering that not all individuals are independent of each other, and that by belonging to social groups their movement patterns might be correlated, we also ran simulations at the scale of family group variation in animal movement by assigning a different movement rate to each social group in the simulations.
+
+<!-- Here I would like to have a figure that incorporates all these different simulation components as a self explanatory box for how a simulation run happens, and what data goes in, what data is calculated and comes out.
+-->
 
@@
 
-<!-- Here I would like to have a figure that incorporates all these different simulation components as a self explanatory box for how a simulation run happens, and what data goes in, what data is calculated and comes out.
--->
+## Parameterization
 
-In order to analyze the effect of differences in animal movement over final dispersal distances of foraged seeds we developed a spatially-explicit individual-based model in a homogeneous landscape that incorporated animal movement distances and seed gut retention time (GRT).
-Our landscape consisted of a single source tree at the origin,  our simulation time steps were based on one minute intervals, and each simulation started at the source tree (0,0), where each individual bird was given five seeds and was allowed to move freely in the landscape until the simulation ended once all seeds were dropped, Figure1.
-Each seed's gut retention time was determined at the start of each simulation run, being randomly sampled from a Gamma distribution (shape = 4, scale = 5, shift = 8) [@morales_effects_2006] so that the average gut retention time was 28 minutes[@holbrook_dispersal_2009; @holbrook_using_2007].
-For each simulation run, the total simulation time was determined by the largest gut retention time sampled for the five seeds, therefore, once the last seed was dropped, the simulation ended.
-We calculated the Euclidean distance from the source tree to each of the dropped seeds to determine their seed dispersal distance.
-We simulated animal movement using a memoryless process, a random walk with a uniformly distributed angular direction and a random step size chosen from a probability distribution.
-The probability distribution chosen to simulate step size varied according to the different models we propose in Table1.
+Where is the data coming from?
+What is a movement rate and how are we calculating it? Why are we using that (uneven time intervals)?
+Why are we using an exponential distribution and what type of movement is this? It is an uncorrelated random walk, but the step size is different.
 
-Caption for figure 1.
-Simulation example.
-The simulation proceeded as follows: an individual bird starts the simulation at time zero and location zero zero.
-That bird is given five different seeds, with gut retention time (GRT_I), where GRT is gamma distributed.
-The animal is allowed to move freely across the landscape where at each time point T_i, a movement angle is sampled ~uniform(360) (think of greek letter) and a step size is randomly selected d_i, where D ~ f(x), where f(x) is the probability density function of one of the models we've selected.
-The movement process is repeated and at T_i == GRT_i a seed is dropped at the bird's location (x_i, y_i) and therefore that seed's final locations is (x_i, y_i).
-The simualation ends at T_i = max(GRT_1:5), and seed dispersal distances are calculated from the origin (0,0) to each seed's location (x_i, y_i).
+We give randomly between 3-5 seeds, because that's what's observed in the field. We are simulating here the trajectory and fate of seeds after only one event of frugivory to make things simpler.
 
-# Simulations at different organizational levels
+We have a maximum landscape area, based on the home range size of the individuals, we chose a grid, and it's modled as a torus so that there is no edge effect.?
+But do I want this if we want to explore long distance?
 
-Our main hypothesis is about the incorporation of variation in animal movement at different organizational levels, meaning how are the differences in individual animal movement affecting population level estimates of seed dispersal.
-How does the underlying variation in individual animal movement impact our estimates of long distance seed dispersal.
-We explored the effects of individual differences in movement by modifying our base simulation, described above, in which the probability density function used to sample step sizes was different between population, individual, or family level simulations.
-What we consider as population level simulations are those where all birds share the same probability density to sample step sizes from, while for individual and family level simulations we use the same overall pdf, but allow for variation in the parameters specified for such function, where each set of parameters corresponds to a specific individual or family group.
-We also performed simulations in which we allowed for variation not only of parameters, but also of the overall structure of the pdf for sampling step sizes, this means that each individual or family group was allowed to have it's own pdf and its own set of parameters (Box 1 or table 1 with description of models, either the movement or simulation).
-We used four different probability density functions for sampling the animal movement step size, these included an exponential distribution [@jones_closing_2017], gamma distribution [citation], Weibull distribution[citation], and lognormal distribution [@levey_modelling_2008].
-These four distributions are leptokurtic, and they vary in the fatness of their tails, thus allowing for different levels of variation in step size.
-**should add number of runs?
-or mention that that is in appendix B**
+Gut retention time based on data and using a gamma distribution from morales paper.
 
-# Parameterization
+## Seed dispersal distance and agregation metrics
 
-We focused our study on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan, and its role as a frugivore of the *Virola flexuosa* tree.
-A subset of animal movement data collected in a previous study [@holbrook_home_2011] was selected and used towards our models and simulations.
-In this previous study, araçari home ranges, average movement distances, patterns and movement rates were estimated for tracked birds over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest.
-Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
-Although this previous study included two larger Ramphastids as well, we used data only from the many-banded araçari, because a higher number of recorded locations were available.
-In addition to this, the home range of this species was found to be the largest for all the species studied, and therefore it was better suited to study long-distance seed dispersal events.
+How we calculated these distances, the averages and SD, and then how we calculated the dispersion, long distance dispersal events.
 
-### Animal movement probability distributions  
-What data am I using for this parameterization?
-It is radiotracking data, and the information on continuous trajectories for each tracked bird, to scale those distances into number of meters moved per minute for each tracking segment.
-I consider a tracking segment as the distance moved between two continuous radio tracking detections.
-(Check Kimberly's paper), because here we are taking advantage of all the tracking data since there are different tracking interval times.
-Then, we used that data to fit the four models described above, and did it at the different organizational levels.
-We considered population level data, as all the data pooled from all individuals tracked, and fit the four distributions to that data to estimate parameters.
-At the individual level, we fit the four pdfs for the data in respect to each individual.
-For the family level data, we used only a subset of the total data set to include only individuals for which family level information existed.
-Because these are social individuals, they tend to move with their group and so we their movements may be correlated.
-We wanted to explore if there were any differences at the family group levels.
-We fit the four pdfs to the subset of this data, as the subset population level, and then fit each distribution to the data associated to each of the family groups.
-We used the parameters estimated from these fits to sample step sizes for our simulation models.
-We also evaluated the fit of each of these distributions visually through qq plots (found in appendix A), and further details on data organization and model fitting can be found in the online repository.
+## Seed dispersal kernel fitting
 
-### Model selection? for the step size
+Look into this, but probably use a Weibull distribution like morales and carlo, and then compare the parameters to describe them.
+An alternative approach would be to use an extreme distribution like the garcia paper to describe this.
 
-$$AIC{_{indlevel}} = 2 \cdot \sum \left ( number parameters \right ) + 2 \cdot \sum \left ( negative log likelihood \right )$$
+# Results
 
-$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$
+## Seed dispersal distances and long distance dispersal
 
-$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
+## Seed dispersion aggregation
 
-# Statistics associated to the simulations
-We analyzed simulation outputs and had seed dispersal distance as our main focus.
-We calculated summary statistics for each of the dispersal distances, and estimated the percentage of long distance dispersal events.
-Using the 500 meter threshold which was determined in previous work.
+## Extreme distributions to fit dispersal
 
-## Results
-### Animal movement rate models
-
-We compared the fit of the different probability distributions to animal movement rate data with Akaike's Information Criteria(AIC) and it's corrected version for small sample sizes (AICc), we also used the Bayesian Information Criteria (BIC) to compare these model fittings.
-At the population level, all information criteria concur and show that the lognormal model fits the data for movement rates the best, with the weibull model next, see table 1.
-However, as we visually assessed fit of these models with QQ plots and goodness-of-fit statistics (see the supplemet), the lognormal distribution model greatly overestimates the data towards the tail, whereas all the other models are significantly more conservative and tend to underestimate the data.
-
-At the individual level, we observed similar outcomes, where the lognormal distribution consistently overestimated the data, whereas the other distributions considered did not.
-When comparing across distribution models at the individual level, AIC and AICc showed the lognormal fit as the best one followed by the exponential model, whereas the BIC had the exponential as the best model followed by the lognormal.
-
-When comparing the population level models with the ones at the individual level, we found that information criteria differed.
-In the case of AIC and AICc, these consistently categorized the individual level models as best fitting when compared to their equivalent distribution model at the population level.
-However, BIC values show that only when we consider the exponential distribution model does the individual level do a better fitting than the population, with all other models having higher BIC values for the models that include individual heterogeneity.
-
-The mixed/heterogeneous model considered the best fitting distribution for each individual, and then selected given distribution to be included in the general model that includes movement for all the individuals and calculates the information criteria value.
-Using different information criteria yielded different best fitting models (see supplement) for each individual, which changed the distributions included on the overall model, therefore producing two different mixed/heterogeneous modelsd with individual variation, one associated to the AIC/AICc target distributions and a different one for BIC.
-However, all information criteria agreed on nine out of twelve individual models.
-In the case of AIC and AICc four individuals were better described by an exponential distribution, three by a Weibull distribution and five by a lognormal distribution.
-When using BIC as the model selection tool, seven individuals were described by an exponential distribution, four by a lognormal and one by the Weibull distribution.
-The overall AIC, AICc and BIC values were calculated for each of the mixed/heterogenous model and compared to the previous fits, where the first five results are shown in the following table (the rest can be seen in the supplement).
-This shows that only the lognormal model at the population level is better than the mixed/heterogeneous model by <2 BIC units.
-
-### Seed Dispersal Distances
-
-We analyzed the seed dispersal distances produced by the simulation runs and there were clear differences between the simulation models.
-These differences clear between models that used different distributions for movement rates, whether or not they consider individual variation, the seed dispersal distances under the lognormal distribution were extremely high with several outliers for dispersal distance.
-The exponential, Gamma and Weibull models for movement rates produced similar seed dispersal distance distributions at the population level.
-All the simulations showed that models that included individual variation in animal movement rates had a higher number of long distance dispersal events.
-
-## Discussion
-
-added Oct 2020: call for the need for more complex animal movement models when running seed dispersal simulations.
-Even the posibility of mixed distribution models, where not only we allow for each individual or fmailiy group to have it's own model, but also use multiple distributions for each.
-The short movements performed by these animals may be better described by a different distribution than those performed at longer intervals.
-
-Considering animal movement in this simple framework of movement rates allows us to easily compare between individuals and how including intraspecific variation can change our estimates and fits of different models.
-It is known that because of this individual variation, no one distribution will fit all individuals, and therefore approaches with mixed distributions or that select different distributions for each individual are important if we want to understand the relationship between frugivore movement and seed dispersal [@russo_incorporating_2006].
-Previous research has focused on exploring the effects of lanscape fragmentation, heterogeneity [@jones_closing_2017, @levey_modelling_2008] or plant aggregation [@pegman_exploring_2017].
-However, focus on intraspecific variation in frugivores and their effect on seed dispersal has only recently been studied more closely[@snell_consequences_2019].
-The models we have used in this study show that individual variation between individual movement rates exist.
-There is clear evidence for heterogeneity across individuals with respect to which distribution explains the data best with both, the AIC and the BIC, regardless of whether these information criteria match.
-We need to move towards developing better animal movement models that incorporate this type of heterogeneity, where we don't just pool tracking data for all individuals, but where we consider the tail end distributions of their movement.
-
-We have also shown that including individual variation in type of distribution for movement rates produces one of the best fitting models to the data.
-Although in our direct comparisson between mixed models and single distribution models, the lognormal distribution at the population level was the best fitting one, the difference of 1.900455 BIC points is too small for us to reject our mixed model that states heterogeneity across individuals.
-This small difference points at perhaps how small sample sizes per individual can have an effect on the fits.Using BIC, a difference of approximately 4 BIC points is equivalent to stating significant difference at an 0.05 alpha level, therefore the difference of <2 BIC points is not sufficient for us to reject our mixed models with individual variation.
-All other models that follow are over 10 BIC units from out mixed/heterogeneous model.
-
-Even though LDD events are rare or infrequent, they have a disproportionately large effect on gene flow and the genetic pool of populations (Jordano 2017).
-In the case of well mixed populations, long-distance dispersal can cause random genetic loss through drift or have the opposite effect and maintain high genetic variance in populations that initially drifted (Bohrer, Nathan, and Volis 2005).
-This is important as in the long-term, these genetic consequences of dispersal can have significant effects for the survival of populations.
-From a metapopulation perspective, LDD events can have significant consequences for species persistence by enhancing genetic variability and as mechanism for survival in spatially and temporally heterogenous environments.
-In particular, long-distance dispersal events have a higher probability of reaching isolated populations and therefore establishing a connection and maintaining unrelated populations.
-It is of special interest to focus in highly heterogenous habitats with rapid change in spatial structure where local extinctions are high, since long-distance dispersal can allow persistence of a metapopulation with immigration and emigration based on long distance dispersal.
-From a more evolutionary perspective, long-distance dispersal can allow for a species to colonize distant habitats and expand its range, which can also lead to differentiation and speciation (Ronce 2007).
-We have shown that individual differences in frugivore movement can have significant consequences on the number of long-distance seed dispersal events and it remains to be explored how these individual differences can influence population dynamics in the long term and at larger spatial scales.
+# Discussion
 

### 2021-01-08 paper/paper.Rmd
added parameterization paragraph

@@
 
-To understand the consequences of individual variation in animal movement and how these influence seed dispersal distances, we simulated two different scenarios by varying the movement of individual animals in each of those scenarios.
+To understand the consequences of individual variation in animal movement and how these influence seed dispersal distances, we simulated three different scenarios by varying the movement of individual animals in each of those scenarios.
 We used our first scenario as our null model, in which all the individuals from the simulation had the same average movement rate ($\lambda_1 = \lambda_2 = ...
@@
 = \lambda_n$), which meant that movement distances would be sampled from probability distributions with different parameters ($f(x;\lambda_i) = \lambda_i e^{-\lambda_i x}$).
-Considering that not all individuals are independent of each other, and that by belonging to social groups their movement patterns might be correlated, we also ran simulations at the scale of family group variation in animal movement by assigning a different movement rate to each social group in the simulations.
+Considering that not all individuals are independent of each other, and that by belonging to social groups their movement patterns might be correlated, our third scenario ran simulations at the scale of family group variation in animal movement by assigning a different movement rate to each social group in the simulations.
 
@@
 
-Where is the data coming from?
-What is a movement rate and how are we calculating it? Why are we using that (uneven time intervals)?
-Why are we using an exponential distribution and what type of movement is this? It is an uncorrelated random walk, but the step size is different.
+We focused our study on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan, and its role as a frugivore of the *Virola flexuosa* tree.
+Previous studies by Holbrook [-@holbrook_home_2011] collected radiotracking information for various dispersers over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest.
+The methodology used at the time consisted of capturing and radio-tagging individuals from various toucan species, including *Pterglossus pluricinctus* and two larger Ramphastids, although data on these was scarce.
+Tracking periods lasted between four and six daylight hours, alternating morning and afternoons, attempting to record bird locations every 15 minutes, a time interval shown to represent the minimum seed retention time for *Virola flexuosa* seeds [@holbrook_using_2007].
+Out of the data collected, and following Holbrook [-@holbrook_home_2011], we selected bird individuals with at least 40 recorded point locations.
+Even though location recordings were attempted every 15 minutes, this was not always possible, due to the individual being too far out from range or canopy cover, therefore point locations data is available every 15 minutes or multiples of 15 minutes, with the majority of point location recordings between 15 and 30 minutes [@holbrook_home_2011].
+Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
+
+To take advantage of all the locations recorded, despite this variation in duration of time intervals, we calculated rates of movement, as the average number of meters moved per minute over the entire tracking period for that individual bird.
+These movement rates were later used in our simulation models as the parameter to describe the probability distribution of movement distances at each one minute time step for each simulation run.
+In the case of our null model, the movement rate was averaged across all individuals for all the tracking periods, and at the social group level we took the average number of meters moved per minute over the tracking periods for all individuals belonging to that group, with a total of 7 independent groups.
+
+Parameter values for gut retention time were also based on empirically collected data from previous studies [@holbrook_using_2007], were  passage trials were carried out with *Pteroglossus pluricinctus* individuals.
+However, these passage trials were not performed on every individual captured and some of the trials were also performed with captive birds, thus we could not explore individual variation in gut retention times for the individuals in the movement data set.
+These trials showed that the average gut retention time for *Pterglossus pluricinctus* was 28 minutes [@holbrook_using_2007], and maximum retention times over 100 minutes.
+The distribution of gut retention times is characteristically fat-tailed, thus we used a gamma distribution (shape = 4, scale = 5) with the appropriate shift to match our average retention time of 28 minutes [@morales_effects_2006; @levey_effects_2005].
+
+## Model processes
 
@@
 But do I want this if we want to explore long distance?
-
-Gut retention time based on data and using a gamma distribution from morales paper.
 

### 2021-01-08 paper/paper.Rmd
update to model processes

@@
 
-To take advantage of all the locations recorded, despite this variation in duration of time intervals, we calculated rates of movement, as the average number of meters moved per minute over the entire tracking period for that individual bird.
+To take advantage of all the locations recorded for series of successive points, despite this variation in duration of time intervals, we calculated rates of movement, as the average number of meters moved per minute over the entire tracking period for that individual bird.
 These movement rates were later used in our simulation models as the parameter to describe the probability distribution of movement distances at each one minute time step for each simulation run.
@@
 These trials showed that the average gut retention time for *Pterglossus pluricinctus* was 28 minutes [@holbrook_using_2007], and maximum retention times over 100 minutes.
-The distribution of gut retention times is characteristically fat-tailed, thus we used a gamma distribution (shape = 4, scale = 5) with the appropriate shift to match our average retention time of 28 minutes [@morales_effects_2006; @levey_effects_2005].
+The distribution of gut retention times is characteristically fat-tailed, thus we used a gamma distribution (shape = 4, scale = 5) with the appropriate shift to match our average retention time of 28 minutes [@morales_effects_2006; @levey_effects_2005], and used this distribution to sample gut retention times for each of our simulation runs.
 
@@
 
-We give randomly between 3-5 seeds, because that's what's observed in the field. We are simulating here the trajectory and fate of seeds after only one event of frugivory to make things simpler.
+Each simulation run in our models consisted of one animal in a homogeneous landscape starting at the focus tree located at coordinates (0,0).
+We assume the landscape is in meters, as the sampling of movement distances for animal movement comes from estimates of meters moved per minute, the movement rates.
+Informed from field observations, *Pteroglossus pluricinctus* have a mean visit length of 4.0 minutes for each fruiting tree, consuming between 2 and 5 seeds during each visit, and not visiting another fruiting tree immediately after feeding (Holbrook's dissertation and personal communication [@holbrook2007seed]).
+Due to this underlying behavior, we decided to focus our simulations specifically to the events associated to feeding from one focus tree, and the animal movement occurring after foraging and before visiting another fruiting tree.
+Since one of the objectives for this paper is to explore the occurrence of long-distance dispersal events, we did not set boundaries for the landscape.
+*Pteroglossus pluricinctus* has shown maximum travel distances exceeding 3500m in a single 30 minute tracking interval, thus showing the potential to disperse *Virola* seeds at long ranges [@holbrook_home_2011].
 
-We have a maximum landscape area, based on the home range size of the individuals, we chose a grid, and it's modled as a torus so that there is no edge effect.?
-But do I want this if we want to explore long distance?
+At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8).
+Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (which varied depending on the underlying model such as the null, individual or family group model) and a random direction from $0^o$ to $360^o$ degrees was used to determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency.
+Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape.
+For each of our models we ran 10,000 simulation runs per individual or family group, depending on the model, and collected information on animal and seed locations at every time step.
+
+## Seed dispersal and aggregation metrics
+
+Bring up that each seed gets dropped when the simulation reaches the seed's previously determined gut retention time, and thus the seed's location is the lcoation of the bird at the simulation time that matches the gut retention time.
+The simulation run ends when the last seed is dropped, which is determined by the largest gut retention time.
+We did not have limits set on the landscape, as we are trying to also understand the effects of this variation on the potential for long-distance dispersal events in toucan-generated seed dispersal curves.
+Maximum recorded distances for these toucans in the datasets is of 3665m in a single 30 minute tracking interval, so we didn't want to limit the dispersal potential by setting the landscape to a torus and constricting its size.
 

### 2021-01-08 paper/paper.Rmd
shuffled some text sections

@@
 
-Bring up that each seed gets dropped when the simulation reaches the seed's previously determined gut retention time, and thus the seed's location is the lcoation of the bird at the simulation time that matches the gut retention time.
-The simulation run ends when the last seed is dropped, which is determined by the largest gut retention time.
-We did not have limits set on the landscape, as we are trying to also understand the effects of this variation on the potential for long-distance dispersal events in toucan-generated seed dispersal curves.
-Maximum recorded distances for these toucans in the datasets is of 3665m in a single 30 minute tracking interval, so we didn't want to limit the dispersal potential by setting the landscape to a torus and constricting its size.
+We calculated seed dispersal distance as the euclidean distance of each seed to the parent plant.
+Given that our models only considered one parent plant located at the origin per simmulation, we calculated seed dispersal distance (DD) as the distance from each seed's location to the origin as follows:
+$$DD_i = \sqrt{(0-x_i)^2 + (0-y_i)^2} $$
+where $DD_i$ is the dispersal distance for seed $i$ in the simulation run and $x_i$ and $y_i$ are its xy coordinates in the landscape.
+We also used an aggregation metric to determine how evenly seeds would be dispersed across the landscape, and calculated seed dispersion (SD) as the average distance of each seed to the mean seed location in each simulation run (following methods in [@jones_closing_2017]):
+$$SD = \frac{\sum \sqrt{(x_m - x_i)^2 + (y_m - y_i)^2}}{n}$$
+where $n$ is the number of seeds for each simulation run (5), and $x_m$ and $y_m$ is the mean seed location in the simulation run.
+The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007].
+The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation.
 
-## Seed dispersal distance and agregation metrics
-
-How we calculated these distances, the averages and SD, and then how we calculated the dispersion, long distance dispersal events.
-
-## Seed dispersal kernel fitting
+## Seed dispersal kernels
 
@@
 
+Even though LDD events are rare or infrequent, they have a disproportionately large effect on gene flow and the genetic pool of populations (Jordano 2017).
+In the case of well mixed populations, long-distance dispersal can cause random genetic loss through drift or have the opposite effect and maintain high genetic variance in populations that initially drifted (Bohrer, Nathan, and Volis 2005).
+This is important as in the long-term, these genetic consequences of dispersal can have significant effects for the survival of populations.
+From a metapopulation perspective, LDD events can have significant consequences for species persistence by enhancing genetic variability and as mechanism for survival in spatially and temporally heterogenous environments.
+In particular, long-distance dispersal events have a higher probability of reaching isolated populations and therefore establishing a connection and maintaining unrelated populations.
+It is of special interest to focus in highly heterogenous habitats with rapid change in spatial structure where local extinctions are high, since long-distance dispersal can allow persistence of a metapopulation with immigration and emigration based on long distance dispersal.
+From a more evolutionary perspective, long-distance dispersal can allow for a species to colonize distant habitats and expand its range, which can also lead to differentiation and speciation (Ronce 2007).
+We have shown that individual differences in frugivore movement can have significant consequences on the number of long-distance seed dispersal events and it remains to be explored how these individual differences can influence population dynamics in the long term and at larger spatial scales.
+
 # Conclusion

### 2021-01-08 paper/paper.Rmd
knit to html
Tried to make figures in manuscript Rmd but word makes them horrible.

@@
 ```{r setup, echo=FALSE}
-knitr::opts_chunk$set(eval = FALSE, echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+```
+
+```{r libraries}
+library(ggplot2)
+library(aracari)
+library(cowplot)
+library(dplyr)
+
 ```
@@
 set.seed(5)
-library(ggplot2)
-library(aracari)
-library(cowplot)
 

### 2021-01-08 paper/Figures.R
Saving code for figures here in the meantime

@@ -1,0 +1,34 @@
+
+load("paper/simple_exp_runs.RData")
+
+
+library(fitdistrplus)
+library(ggplot2)
+library(dplyr)
+
+
+# Figure for movement rates at the three levels
+
+rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
+  bind_rows(., indiv_moverate %>%
+              rename(level = Bird_ID)) %>%
+  bind_rows(., fam_moverate %>%
+              rename(level = fam_g)) %>%
+  mutate(model = ifelse(level == "null", "Null",
+                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))
+
+n <- 1000
+dens_rates <- NULL
+for(i in 1:length(rates$level)) {
+  dens_exp <- rexp(n, rate = 1/rates$movrate[i])
+
+  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
+  dens_rates <- rbind.data.frame(dens_rates, out)
+}
+
+dens_rates %>%
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
+  ggplot(., aes(x = value, group = level, color = model)) +
+  facet_wrap(~model) +
+  geom_density() +
+  scale_color_manual(values = c("red", "grey", "black"))

### 2021-01-08 paper/dispersal_kernels.R
about to fit dispersal kernels

@@ -1,0 +1,35 @@
+
+
+load("paper/simple_exp_runs.RData")
+
+
+library(fitdistrplus)
+library(ggplot2)
+library(dplyr)
+
+
+# Figure for movement rates at the three levels
+
+rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
+  bind_rows(., indiv_moverate %>%
+              rename(level = Bird_ID)) %>%
+  bind_rows(., fam_moverate %>%
+              rename(level = fam_g)) %>%
+  mutate(model = ifelse(level == "null", "Null",
+                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))
+
+n <- 1000
+dens_rates <- NULL
+for(i in 1:length(rates$level)) {
+  dens_exp <- rexp(n, rate = 1/rates$movrate[i])
+
+  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
+  dens_rates <- rbind.data.frame(dens_rates, out)
+}
+
+dens_rates %>%
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
+  ggplot(., aes(x = value, group = level, color = model)) +
+  facet_wrap(~model) +
+  geom_density() +
+  scale_color_manual(values = c("red", "grey", "black"))

### 2021-01-08 paper/figures_tables.Rmd
not liking Rmd version much
Fine, doing figures in rmd

@@
 
-```{r}
+```{r movementdensity, fig.width=6, fig.height=2}
+
+load("paper/simple_exp_runs.RData")
+
+library(ggplot2)
 library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(purrr)
-library(fitdistrplus)
-library(ggpubr)
+
+# Figure for movement rates at the three levels
+
+rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
+  bind_rows(., indiv_moverate %>%
+              rename(level = Bird_ID)) %>%
+  bind_rows(., fam_moverate %>%
+              rename(level = fam_g)) %>%
+  mutate(model = ifelse(level == "null", "Null",
+                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))
+
+n <- 1000
+dens_rates <- NULL
+for(i in 1:length(rates$level)) {
+  dens_exp <- rexp(n, rate = 1/rates$movrate[i])
+
+  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
+  dens_rates <- rbind.data.frame(dens_rates, out)
+}
+
+dens_rates %>%
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
+  ggplot(., aes(x = value, group = level, color = model)) +
+  facet_wrap(~model) +
+  geom_density() +
+  scale_color_manual(values = c("red", "grey", "black"), guide = "none") +
+  theme_bw() + labs(x = "Distance in meters per minute") +
+  #coord_cartesian(xlim = c(100, 300), ylim = c(0, 0.0025))+
+  NULL
+```
+
+```{r grt, fig.width=3, fig.height=2}
+
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0)) +
+  theme_bw() + labs(x = "Time in minutes")
 
 ```
-
-# Layout of steps of one simulation run
-
-# Figure with variation for parameter estimates
-
-# Table: Info criteria for family and individual levels
-
-# Facetted plot for seed dispersal distances
-
-# Density figures from which step and grt are sampled from

### 2021-01-08 paper/Figures.R

@@ -1,34 +1,0 @@
-
-load("paper/simple_exp_runs.RData")
-
-
-library(fitdistrplus)
-library(ggplot2)
-library(dplyr)
-
-
-# Figure for movement rates at the three levels
-
-rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
-  bind_rows(., indiv_moverate %>%
-              rename(level = Bird_ID)) %>%
-  bind_rows(., fam_moverate %>%
-              rename(level = fam_g)) %>%
-  mutate(model = ifelse(level == "null", "Null",
-                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))
-
-n <- 1000
-dens_rates <- NULL
-for(i in 1:length(rates$level)) {
-  dens_exp <- rexp(n, rate = 1/rates$movrate[i])
-
-  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
-  dens_rates <- rbind.data.frame(dens_rates, out)
-}
-
-dens_rates %>%
-  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
-  ggplot(., aes(x = value, group = level, color = model)) +
-  facet_wrap(~model) +
-  geom_density() +
-  scale_color_manual(values = c("red", "grey", "black"))

### 2021-01-10 paper/dispersal_kernels.R
Fit weibull to dispersal kernels and summary table

@@ -14,18 +14,18 @@ library(dplyr)
 null_weibull <- fitdist(null_dispersal$dispersal, distr = "weibull")
 
 null_weibull$estimate
-plot(null_weibull)
+# plot(null_weibull)
 
 
 indiv_weibull <- fitdist(indiv_dispersal$dispersal, distr = "weibull")
 
 indiv_weibull$estimate
-plot(indiv_weibull)
+# plot(indiv_weibull)
 
 fam_weibull <- fitdist(fam_dispersal$dispersal, distr = "weibull")
 
 fam_weibull$estimate
-plot(fam_weibull)
+# plot(fam_weibull)
 
 
 
@@ -36,22 +36,69 @@ null_dispersal %>%
   group_by(., id) %>%
   summarize(max_d = max(dispersal),
             n_ldd = n(),
-            prop_ldd = n_ldd/10000)
+            prop_ldd = n_ldd/10000) %>%
+  ungroup() %>%
+  summarise(global_max = max(max_d),
+            max_mean = mean(max_d),
+            max_sd = sd(max_d),
+            sd_ldd = sd(prop_ldd),
+            prop_ldd = mean(prop_ldd),
+            prcnt_ldd = prop_ldd *100) -> null_ldd
 
 indiv_dispersal %>%
   filter(., dispersal >= 500) %>%
   group_by(., id) %>%
   summarize(max_d = max(dispersal),
             n_ldd = n(),
-            prop_ldd = n_ldd/10000)
+            prop_ldd = n_ldd/10000) %>%
+  ungroup() %>%
+  summarise(global_max = max(max_d),
+            max_mean = mean(max_d),
+            max_sd = sd(max_d),
+            sd_ldd = sd(prop_ldd),
+            prop_ldd = mean(prop_ldd),
+            prcnt_ldd = prop_ldd *100) -> indiv_ldd
 
 fam_dispersal %>%
   filter(., dispersal >= 500) %>%
   group_by(., id) %>%
   summarize(max_d = max(dispersal),
             n_ldd = n(),
-            prop_ldd = n_ldd/10000)
+            prop_ldd = n_ldd/10000)%>%
+  ungroup() %>%
+  summarise(global_max = max(max_d),
+            max_mean = mean(max_d),
+            max_sd = sd(max_d),
+            sd_ldd = sd(prop_ldd),
+            prop_ldd = mean(prop_ldd),
+            prcnt_ldd = prop_ldd *100) -> fam_ldd
 
+# Dispersal and dispersion calculation
+
[…]

### 2021-01-10 paper/dispersal_kernels.R
gofstat for weibull fit to dispersal kernel

@@ -14,17 +14,20 @@ library(dplyr)
 null_weibull <- fitdist(null_dispersal$dispersal, distr = "weibull")
 
 null_weibull$estimate
+gofstat(null_weibull)
 # plot(null_weibull)
 
 
 indiv_weibull <- fitdist(indiv_dispersal$dispersal, distr = "weibull")
 
 indiv_weibull$estimate
+gofstat(indiv_weibull)
 # plot(indiv_weibull)
 
 fam_weibull <- fitdist(fam_dispersal$dispersal, distr = "weibull")
 
 fam_weibull$estimate
+gofstat(fam_weibull)
 # plot(fam_weibull)
 
 

### 2021-01-10 paper/paper.Rmd
Adding skeleton figures

@@
 output:
+  html_document:
+    df_print: paged
   word_document:
     reference_docx: paper_ref.docx
-  html_document:
-    df_print: paged
 bibliography: mybibfile.bib
@@
 The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007].
-The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation.
+The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation (Table1).
 
@@
 
-Look into this, but probably use a Weibull distribution like morales and carlo, and then compare the parameters to describe them.
-An alternative approach would be to use an extreme distribution like the garcia paper to describe this.
+- Already fit the weibull distribution for this. I have
 
 # Results
+
+```{r}
+load("dispersal_kernels.RData")
+```
+
+```{r fig.width=6}
+plot_grid(
+  fam_dispersal %>%
+    ggplot(., aes(x = dispersal)) +
+    geom_histogram(),
+  plot_grid(fam_dispersion %>%
+            ggplot(., aes(y = mean_dispersal)) +
+            geom_boxplot(),
+          fam_dispersion %>%
+            ggplot(., aes(y = seed_dispersion)) +
+            geom_boxplot()), nrow = 2)
+```
 
@@
 ## Seed dispersion aggregation
+
+## Weibull seed dispersal kernel
+
+**Table 1.**
+```{r}
+
+knitr::kable(dispersal_kernel_table)
+```
 

### 2021-01-10 paper/paper.Rmd
Add figure 3 and 4 skeletons

@@
 ```
+## Seed dispersal distances and long distance dispersal
 
+**Figure 3.**
 ```{r fig.width=6}
-plot_grid(
-  fam_dispersal %>%
+
+null_kernel <- null_dispersal %>% 
   ggplot(., aes(x = dispersal)) +
-    geom_histogram(),
-  plot_grid(fam_dispersion %>%
-            ggplot(., aes(y = mean_dispersal)) +
-            geom_boxplot(),
-          fam_dispersion %>%
-            ggplot(., aes(y = seed_dispersion)) +
-            geom_boxplot()), nrow = 2)
+  geom_histogram(aes(y = ..density..))
+
+indiv_kernel <- indiv_dispersal %>% 
+  ggplot(., aes(x = dispersal)) +
+  geom_histogram(aes(y = ..density..))
+
+fam_kernel <- fam_dispersal %>% 
+  ggplot(., aes(x = dispersal)) +
+  geom_histogram(aes(y = ..density..))
+
+plot_grid(null_kernel, indiv_kernel, fam_kernel, nrow = 3)
+
+# Make the axis be the same length and beaks
+# Remove redundant labels
+# Test 3 rows or 3 columns
+# Add red vertical line for LDD cutoff
+# Include a zoom cut off for the tail
+
+# plot_grid(
+#   fam_dispersal %>%
+#     ggplot(., aes(x = dispersal)) +
+#     geom_histogram(),
+#   plot_grid(fam_dispersion %>%
+#             ggplot(., aes(y = mean_dispersal)) +
+#             geom_boxplot(),
+#           fam_dispersion %>%
+#             ggplot(., aes(y = seed_dispersion)) +
+#             geom_boxplot()), nrow = 2)
 ```
 
-## Seed dispersal distances and long distance dispersal
+## Seed dispersion aggregation
+The mean dispersal in the boxplots is not the same as the dispersal distances before.
+This mean dispersal is the distance from the origin to the mean seed location in each simulation run.
+The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
 
-## Seed dispersion aggregation
+**Figure 4.**
+```{r fig.width=3, fig.height=5}
+
+null_dispersion %>% 
+  mutate(model = "Null") %>% 
+  bind_rows(indiv_dispersion %>% 
+              mutate(model = "Individual")) %>% 
+  bind_rows(fam_dispersion %>% 
+              mutate(model = "Family")) -> all_disp_data
+
+all_disp_data %>% 
+  ggplot(., aes(y = mean_dispersal, x = model)) +
+  geom_boxplot() -> dispersal_box
+
+all_disp_data %>% 
+  ggplot(., aes(y = seed_dispersion, x = model)) +
+  geom_boxplot() -> dispersion_box
+
+plot_grid(dispersal_box, dispersion_box, nrow = 2)
+
+# Edit redundant labels
+# Fix names for axes
+
+```
 

### 2021-01-10 paper/simple_exp_paper.R
mean_xy_dispersal as the distance to the mean seed location in each simulation run

@@ -77,6 +77,7 @@ sim_run <- function(movrate){
 
   x_m <- mean(seed_loc$xloc)
   y_m <- mean(seed_loc$yloc)
+  mean_xy_dispersal <- sqrt((x_m^2) + (y_m^2))
   mean_dispersal <- mean(seed_loc$dispersal)
   se_dispersal <- sd(seed_loc$dispersal)/sqrt(length(seed_loc$dispersal))
 
@@ -88,6 +89,7 @@ sim_run <- function(movrate){
   outsim <- list(lengths = movedist,
                  movement = animalTraj,
                  seed = seed_loc,
+                 mean_xy_dispersal = mean_xy_dispersal,
                  mean_dispersal = mean_dispersal,
                  se_dispersal = se_dispersal,
                  seed_dispersion = seed_dispersion)
@@ -142,6 +144,7 @@ for(j in 1:length(null_moverate$Bird_ID)){
 
   dispersal <- map_df(manysims, "seed")$dispersal
   id <- null_moverate$Bird_ID[j]
+  mean_xy_dispersal <- map_dbl(manysims, "mean_xy_dispersal")
   mean_dispersal <- map_dbl(manysims, "mean_dispersal")
   se_dispersal <- map_dbl(manysims, "se_dispersal")
   seed_dispersion <- map_dbl(manysims, "seed_dispersion")
@@ -150,6 +153,7 @@ for(j in 1:length(null_moverate$Bird_ID)){
   null_dispersal <- rbind.data.frame(null_dispersal, out)
 
   out2 <- data.frame(id = id,
+                     mean_xy_dispersal = mean_xy_dispersal,
                      mean_dispersal = mean_dispersal,
                      se_dispersal = se_dispersal,
                      seed_dispersion = seed_dispersion)
@@ -185,6 +189,7 @@ for(j in 1:length(indiv_moverate$Bird_ID)){
 
   dispersal <- map_df(manysims, "seed")$dispersal
   id <- indiv_moverate$Bird_ID[j]
+  mean_xy_dispersal <- map_dbl(manysims, "mean_xy_dispersal")
   mean_dispersal <- map_dbl(manysims, "mean_dispersal")
   se_dispersal <- map_dbl(manysims, "se_dispersal")
   seed_dispersion <- map_dbl(manysims, "seed_dispersion")
@@ -193,6 +198,7 @@ for(j in 1:length(indiv_moverate$Bird_ID)){
   indiv_dispersal <- rbind.data.frame(indiv_dispersal, out)
 
[…]

### 2021-01-10 paper/paper.Rmd
Added dispersal to mean seed location

@@
   bind_rows(fam_dispersion %>% 
-              mutate(model = "Family")) -> all_disp_data
+              mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
+
+all_disp_data %>% 
+  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
+  geom_boxplot() -> dispersal_xy_box
 
@@
 
-plot_grid(dispersal_box, dispersion_box, nrow = 2)
+plot_grid(dispersal_xy_box, dispersal_box, dispersion_box, nrow = 3)
 

### 2021-01-10 paper/paper.Rmd
comments after reading on extreme value distributions

@@
 
+*Include table in the supplement with the movement rates*
+
 ## Model processes
@@
 
-- Already fit the weibull distribution for this. I have
+- Already fit the weibull distribution for this.
+Mention that we chose this distribution because it is commonly used in dispersal ecology due to its felixibility, how adjusting the scale parameter changes the tail of the distribution.
+This is both in Garcia2017 (>1 fast decaying, <1 low decay fat tail, =1 exponential decay) and Carlomorales2006 papers, but I think they present it slightly different.
+
+- We inspected the QQ plots to check for fitting. Figuere Supplement
+
+- They mention declustering the data, and perhaps in that case I could be using the mean_xy_dispersal.
 
@@
 
+Explain what are statistics of extremes and why they can be useful here.
+cite the GArcia 2017 paper, the Gaines and Denny 1993, Katz 2005.
+Coles 2001 for the theory or base knowledge.
+In our case, because we are looking at these simulated seed dispersal kernels, we use a peak over threshold (POT) approach, in which we find the threshold for the data and use an extreme value distribution to fit the tail.
+Describe the math probabilty density functions and the three laws that the extreme value distribution follows. 
+For POT use a generalized pareto distribution.
+
+- Based on Diagnostic plots, we used these values as the threshold for each of the models.
+
 # Discussion

### 2021-01-11 paper/paper.Rmd
checking the results from Garcia paper. They are not reproducible from what they give. Why don't they just share code/

@@
 
+From extRemes package: "where shape = 0 gives rise to the exponential df (light tail), shape > 0 the Pareto df (heavy tail) and shape < 0 the Beta df (bounded upper tail at location - scale.u/shape).
+Theoretical justification supports the use of the GP df family for modeling excesses over a high threshold (i.e., y = x - threshold)."
+
 # Discussion

### 2021-01-11 paper/fevd.R

@@ -9,39 +9,36 @@ library(cowplot)
 library(extRemes)
 
 
-data("damage", package="extRemes")
-
-plot(damage$Year, damage$Dam, xlab = "Year",
-     ylab = "U.S. Hurricane Damage (billion USD)", cex = 1.25,
-     cex.lab = 1.25, col = "darkblue", bg = "lightblue", pch = 21)
-
-plot(damage[, "Year"], log(damage[, "Dam"]), xlab = "Year",
-     ylab = "ln(Damage)", ylim = c(-10, 5), cex.lab = 1.25,
-     col = "darkblue", bg = "lightblue", pch = 21)
-
-qqnorm(log(damage[, "Dam"]), ylim = c(-10, 5), cex.lab = 1.25)
-hist(damage$Dam)
-threshrange.plot(damage$Dam, r = c(1, 15), nint = 20)
-
-mrlplot(damage$Dam, xlim = c(0, 12))
-
-
 # My data
 
 null_sample <- sample(null_dispersal$dispersal, 10000)
 hist(null_sample)
-hist(log(null_sample))
-qqnorm(log(null_sample))
+#hist(log(null_sample))
+#qqnorm(log(null_sample))
 qqnorm(null_sample)
 # Qq plots don't show straight lines, not consistent with a normal distribution of the data,
 
-threshrange.plot(null_sample, r = c(300, 800), nint = 100)
+a <- threshrange.plot(null_sample, r = c(300, 700), nint = 100)
+b <- mrlplot(null_sample, xlim = c(300, 700), nint = 100)
 
 fit_D <- fevd(null_sample, threshold = 500, type = "GP")
+fit_D$results
+summary(fit_D)
 plot(fit_D)
+t <- plot(fit_D, type = "qq2")
 pextRemes(fit_D, c(500, 1000, 1500, 2000, 3000, 3500, 4000), lower.tail = FALSE)
+
+
 
 hist(sample(indiv_dispersal$dispersal, 100))
 threshrange.plot(sample(indiv_dispersal$dispersal, 100), r = c(1, 700), nint = 100)
 
+
+garcia <- read.csv("paper/crap.txt", header = FALSE)
+hist(garcia$V1)
+threshrange.plot(garcia$V1, r = c(1, 700), nint = 200)
+mrlplot(garcia$V1)
+
+fit_garcia <- fevd(garcia$V1, threshold = 170, type = "GP")
+summary(fit_garcia)
 

### 2021-01-11 paper/fevd.R
steps to fit and visualize the extreme distributions

@@ -9,7 +9,7 @@ library(cowplot)
 library(extRemes)
 
 
-# My data
+# Just testing
 
 null_sample <- sample(null_dispersal$dispersal, 10000)
 hist(null_sample)
@@ -18,27 +18,26 @@ hist(null_sample)
 qqnorm(null_sample)
 # Qq plots don't show straight lines, not consistent with a normal distribution of the data,
 
-a <- threshrange.plot(null_sample, r = c(300, 700), nint = 100)
+a <- threshrange.plot(null_sample, r = c(300, 700), nint = 200)
 b <- mrlplot(null_sample, xlim = c(300, 700), nint = 100)
 
 fit_D <- fevd(null_sample, threshold = 500, type = "GP")
-fit_D$results
+#fit_D$results
 summary(fit_D)
 plot(fit_D)
-t <- plot(fit_D, type = "qq2")
+t <- plot(fit_D, type = "qq")
 pextRemes(fit_D, c(500, 1000, 1500, 2000, 3000, 3500, 4000), lower.tail = FALSE)
 
+scale <- fit_D$results$par[1]
+shape <- fit_D$results$par[2]
+dens <- revd(10000, scale = scale, shape = shape, type = "GP")
+hist(dens)
+d <- density(dens)
+plot(d)
 
-
-hist(sample(indiv_dispersal$dispersal, 100))
-threshrange.plot(sample(indiv_dispersal$dispersal, 100), r = c(1, 700), nint = 100)
-
-
-garcia <- read.csv("paper/crap.txt", header = FALSE)
-hist(garcia$V1)
-threshrange.plot(garcia$V1, r = c(1, 700), nint = 200)
-mrlplot(garcia$V1)
-
-fit_garcia <- fevd(garcia$V1, threshold = 170, type = "GP")
-summary(fit_garcia)
+ggplot(data = data.frame(x = c(0.1, 6)), aes(x)) +
+  stat_function(fun = devd, n = 101, args = list(type = "GP", scale = 1, shape = 0)) +
+  stat_function(fun = devd, n = 101, args = list(type = "GP", scale = 1, shape = 0.5))
+  ylab("") +
+  scale_y_continuous(breaks = NULL)
 

### 2021-01-12 paper/paper.Rmd
Edits to methods section

@@
 We incorporated animal movement focusing on two characteristics, a movement distance (MD) sampled from a probability density distribution, and a movement angle (MA).
-In addition to this, we included gut retention time (GRT), the time that ingested seeds stay within the frugivore until they are dropped.
+In addition to this, we included gut retention time (GRT), the time that ingested seeds stay inside the frugivore until they are dropped.
 The animal was allowed to move freely within the landscape, and GRT determined when the animal would drop a seed.
 Once a seed was dropped, its location was recorded and seed dispersal distance was estimated as the distance from the origin to the seed's location.
-The average seed dispersal distance for each simulation run was calculated and used to estimate seed dispersion, calculated as the mean distance of each seed to the average location of all seeds in the run [@jones_closing_2017].
+The average seed dispersal distance for each simulation run was also estimated and used to for seed dispersion, calculated as the mean distance of each seed to the average location of all seeds in the run [@jones_closing_2017].
 For each simulation run, the simulation started at the source tree, an animal received a specific number of seeds and each seed was assigned a specific GRT sampled from a gamma distribution [@morales_effects_2006].
@@
 
-To understand the consequences of individual variation in animal movement and how these influence seed dispersal distances, we simulated three different scenarios by varying the movement of individual animals in each of those scenarios.
+To understand the consequences of individual variation in animal movement and how these influence seed dispersal distances, we simulated three different scenarios by varying the movement of individual animals.
 We used our first scenario as our null model, in which all the individuals from the simulation had the same average movement rate ($\lambda_1 = \lambda_2 = ...
 = \lambda_n$), used as the parameter in the probability density function, and thus their movement distances per unit of time were sampled from the same probability distribution ($f(x;\lambda) = \lambda e^{-\lambda x}$).
+We chose this as our null model as it is the approach most commonly used in frugivore-generated seed dispersal kernels, where the movement rate for the frugivore population is determined and used either as a constant movement speed or to sample from a single distribution (EDIT citation, Will Tackenberg, 2008, constant rate, Jones 2017, exponential with different values for theoretical model, Levey bolker 2 papers lognormal).
 Our second scenario included individual variation in animal movement by incorporating different movement rates for each individual ($\lambda_1 = \lambda_2 = ...
-= \lambda_n$), which meant that movement distances would be sampled from probability distributions with different parameters ($f(x;\lambda_i) = \lambda_i e^{-\lambda_i x}$).
-Considering that not all individuals are independent of each other, and that by belonging to social groups their movement patterns might be correlated, our third scenario ran simulations at the scale of family group variation in animal movement by assigning a different movement rate to each social group in the simulations.
+= \lambda_n$), which meant that movement distances would be sampled from the same overall probability distribution, but with different parameters ($f(x;\lambda_i) = \lambda_i e^{-\lambda_i x}$).
+**Double check if these are the Erlang and hyperexponential distributions, not sure it is worth it to mention here though**.
+Considering that *Pteroglossus pluricinctus*, the focus frugivore in this paper, by belonging to social groups their movement patterns might be correlated, our third scenario ran simulations at the scale of family group variation in animal movement by assigning a different movement rate to each social group in the simulations, where the movement rate where considered as the average movement in meters per unit of time for all the tracking sessions for all individuals belonging to that social group.
 
@@
 Previous studies by Holbrook [-@holbrook_home_2011] collected radiotracking information for various dispersers over a period of four years, from 2001 to 2005, in the Ecuadorian Amazon rainforest.
-The methodology used at the time consisted of capturing and radio-tagging individuals from various toucan species, including *Pterglossus pluricinctus* and two larger Ramphastids, although data on these was scarce.
+The methodology used at the time consisted of capturing and radio-tagging individuals from various toucan species, including *Pterglossus pluricinctus* and two larger Ramphastids, although data on the latter was scarce.
 Tracking periods lasted between four and six daylight hours, alternating morning and afternoons, attempting to record bird locations every 15 minutes, a time interval shown to represent the minimum seed retention time for *Virola flexuosa* seeds [@holbrook_using_2007].
-Out of the data collected, and following Holbrook [-@holbrook_home_2011], we selected bird individuals with at least 40 recorded point locations.
-Even though location recordings were attempted every 15 minutes, this was not always possible, due to the individual being too far out from range or canopy cover, therefore point locations data is available every 15 minutes or multiples of 15 minutes, with the majority of point location recordings between 15 and 30 minutes [@holbrook_home_2011].
+Out of the data collected, and following Holbrook [-@holbrook_home_2011], we selected data from individuals with at least 40 recorded point locations.
+Even though location recordings were attempted every 15 minutes, this was not always possible, due to the individual being too far out from range or due to canopy cover, therefore point locations data is available every 15 minutes or multiples of 15 minutes, with the majority of point location recordings between 15 and 30 minutes [@holbrook_home_2011].
 Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
@@
 These movement rates were later used in our simulation models as the parameter to describe the probability distribution of movement distances at each one minute time step for each simulation run.
-In the case of our null model, the movement rate was averaged across all individuals for all the tracking periods, and at the social group level we took the average number of meters moved per minute over the tracking periods for all individuals belonging to that group, with a total of 7 independent groups.
+In the case of our null model, the movement rate was averaged across all individuals for all the tracking periods, and at the social group level we took the average number of meters moved per minute over the tracking periods for all individuals belonging to that group, with a total of 7 independent movement rates.
 
@@
 However, these passage trials were not performed on every individual captured and some of the trials were also performed with captive birds, thus we could not explore individual variation in gut retention times for the individuals in the movement data set.
-These trials showed that the average gut retention time for *Pterglossus pluricinctus* was 28 minutes [@holbrook_using_2007], and maximum retention times over 100 minutes.
-The distribution of gut retention times is characteristically fat-tailed, thus we used a gamma distribution (shape = 4, scale = 5) with the appropriate shift to match our average retention time of 28 minutes [@morales_effects_2006; @levey_effects_2005], and used this distribution to sample gut retention times for each of our simulation runs.
+These trials showed that the average gut retention time for *Pterglossus pluricinctus* was 28 minutes [@holbrook_using_2007], and presented a maximum retention time of over 100 minutes.
+The distribution of gut retention times is characteristically fat-tailed, thus we used a gamma distribution (shape = 4, scale = 5) with the appropriate shift to match our average retention time of 28 minutes [@morales_effects_2006; @levey_effects_2005], and used this distribution to sample gut retention times for each seed in our simulation runs.
 
@@
 We assume the landscape is in meters, as the sampling of movement distances for animal movement comes from estimates of meters moved per minute, the movement rates.
-Informed from field observations, *Pteroglossus pluricinctus* have a mean visit length of 4.0 minutes for each fruiting tree, consuming between 2 and 5 seeds during each visit, and not visiting another fruiting tree immediately after feeding (Holbrook's dissertation and personal communication [@holbrook2007seed]).
+Informed from field observations, *Pteroglossus pluricinctus* have a mean visit length of 4.0 minutes for each fruiting tree, consuming between 2 and 5 seeds during each visit, and not visiting another fruiting tree immediately after feeding (Holbrook's dissertation and [@holbrook2007seed]).
 Due to this underlying behavior, we decided to focus our simulations specifically to the events associated to feeding from one focus tree, and the animal movement occurring after foraging and before visiting another fruiting tree.
-Since one of the objectives for this paper is to explore the occurrence of long-distance dispersal events, we did not set boundaries for the landscape.
+Since one of the objectives for this paper is to explore the occurrence of long-distance dispersal events, we did not set boundaries for the landscape, as using the boundaries associated to the radiotracking sampling would limit animal movement and seed dispersal distances to only the scale sampled by previous researchers.
 *Pteroglossus pluricinctus* has shown maximum travel distances exceeding 3500m in a single 30 minute tracking interval, thus showing the potential to disperse *Virola* seeds at long ranges [@holbrook_home_2011].
@@
 At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8).
-Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (which varied depending on the underlying model such as the null, individual or family group model) and a random direction from $0^o$ to $360^o$ degrees was used to determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency.
+Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (which varied depending on the underlying model such as the null, individual or family group model) and a random direction from $0^o$ to $360^o$ degrees was used to determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency (*Edit references* Turchin 1998).
 Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape.
@@
 We also used an aggregation metric to determine how evenly seeds would be dispersed across the landscape, and calculated seed dispersion (SD) as the average distance of each seed to the mean seed location in each simulation run (following methods in [@jones_closing_2017]):
-$$SD = \frac{\sum \sqrt{(x_m - x_i)^2 + (y_m - y_i)^2}}{n}$$
-where $n$ is the number of seeds for each simulation run (5), and $x_m$ and $y_m$ is the mean seed location in the simulation run.
-The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007].
+$$SD_j = \frac{\sum \sqrt{(x_{mj} - x_{ij})^2 + (y_{mj} - y_{ij})^2}}{n}$$
+where $n$ is the number of seeds for each simulation run (5), and $x_{mj}$ and $y_{mj}$ is the mean seed location in the $j$ simulation run.
+We obtained measures of seed dispersion for each simulation run, thus we calculated the average seed dispersion for each model as $\overline{SD} = \frac{\sum{SD_j}}{N}$, where $N$ is the total number of simulation runs for the model being considered.The information on seed dispersal distance was used for the toucan-generated seed dispersal kernels for each one of our models (null, individual, and family group), and these seed dispersal distances were also classified as long distance dispersal events if they exceeded 500m [@holbrook_using_2007].
 The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation (Table1).
@@
 
-- They mention declustering the data, and perhaps in that case I could be using the mean_xy_dispersal.
+- They mention declustering the data, and perhaps in that case I could be using the mean_xy_dispersal, but no because this immendiately brings down the extent of long distance dispersal events.
 

### 2021-01-15 paper/paper.Rmd
addig methods

@@
 
+Seed dispersal kernels are functions used to describe the probability of a seed being dispersed or deposited at a specific distance away from its parent plant [@nathan_spatial_2000].
+The resulting data from our three simulation models provided a dispersal distance for each simulated seed, and thus we used this information to describe the seed dispersal kernels for each model (null, individual, and family).
+Dispersal kernels in nature tend to be leptokurtic, with a peak near the origin and long tails, therefore kernel shape can be summarized by its kurtosis [@morales_effects_2006].
+We quantified the dispersal kernels produced in our models by the sample statistics of mean and kurtosis to describe the overall shape and tail of distribution of seed dispersal distances.
+In addition to this, we also fit a Weibull distribution via maximum likelihood to obtain estimates of the shape and scale parameters in this distribution.
+A Weibull probability distribution is commonly used in dispersal ecology due to the flexible shape and ability to accommodate variability in the tail of the distribution.
+
+In order to describe the seed dispersal kernels generated by our simulations under the three different models, we chose a Weibull distribution.
+This probability distribution is commonly used in dispersal ecology and has been shown to be flexible enough to accommodate variability in the tails and provide informative parameters associated to the mean dispersal distance and shape of the tail [@morales_effects_2006].
+We fit the data associated to seed dispersal distances produced by each of the three models via Maximum Likelihood using the Weibull density function:
+$$W(x) = \left(\frac{\kappa}{\nu}\right) \left(\frac{x}{\nu}\right)^{\kappa-1} exp[-(x/{\nu})^{\kappa}]$$
+
+f(x) = (a/b) (x/b)^(a-1) exp(- (x/b)^a)
+Where the shape parameter $\kappa$ is found to be the average seed dispersal distance from the data, and the scale parameter $\nu$ determines the tail of the distribution.
+Other variations of the Weibull density distribution describe the
+
+```{r}
+library(ggplot2)
+
+ggplot(data = data.frame(x = c(0.1, 10)), aes(x)) +
+  stat_function(fun = dweibull, n = 10, args = list(scale = 1, shape = 1), color = "red") +
+  stat_function(fun = dweibull, n = 10, args = list(scale = 2, shape = 1), color = "blue") +
+  stat_function(fun = dweibull, n = 10, args = list(scale = -2, shape = 1)) +
+  ylab("")
+
+```
+
 - Already fit the weibull distribution for this.

### 2021-01-15 paper/dispersal_kernels.R
Ugh. had it mislabelled

@@ -136,12 +136,13 @@ dispersal_kernel_table <- data.frame(
   LDD = c(paste0(signif(null_ldd$prcnt_ldd, 3), " (", signif(null_ldd$sd_ldd, 1), ")", "%"),
           paste0(signif(indiv_ldd$prcnt_ldd, 3), " (", signif(indiv_ldd$sd_ldd, 1), ")", "%"),
           paste0(signif(fam_ldd$prcnt_ldd, 3), " (", signif(fam_ldd$sd_ldd, 1), ")", "%")),
-  Weibull_Shape = c(paste0(signif(null_weibull$estimate[2], 4), " (", signif(null_weibull$sd[2], 2), ")"),
+  Weibull_Shape = c(paste0(signif(null_weibull$estimate[1], 4), " (", signif(null_weibull$sd[1], 2), ")"),
+                    paste0(signif(indiv_weibull$estimate[1], 4), " (", signif(indiv_weibull$sd[1], 2), ")"),
+                    paste0(signif(fam_weibull$estimate[1], 4), " (", signif(fam_weibull$sd[1], 2), ")")),
+  Weibull_Scale = c(paste0(signif(null_weibull$estimate[2], 4), " (", signif(null_weibull$sd[2], 2), ")"),
                      paste0(signif(indiv_weibull$estimate[2], 4), " (", signif(indiv_weibull$sd[2], 2), ")"),
-                     paste0(signif(fam_weibull$estimate[2], 4), " (", signif(fam_weibull$sd[2], 2), ")")),
-  Weibull_Scale = c(paste0(signif(null_weibull$estimate[1], 4), " (", signif(null_weibull$sd[1], 2), ")"),
-                  paste0(signif(indiv_weibull$estimate[1], 4), " (", signif(indiv_weibull$sd[1], 2), ")"),
-                  paste0(signif(fam_weibull$estimate[1], 4), " (", signif(fam_weibull$sd[1], 2), ")"))
+                     paste0(signif(fam_weibull$estimate[2], 4), " (", signif(fam_weibull$sd[2], 2), ")"))
+
 )
 
 

### 2021-01-15 paper/paper.Rmd
Section on weibull distribution for the methods

--- 2021-01-12 paper/paper.Rmd
@@
 
+Seed dispersal kernels are functions used to describe the probability of a seed being dispersed or deposited at a specific distance away from its parent plant [@nathan_spatial_2000].
+The resulting data from our three simulation models provided a dispersal distance for each simulated seed, and thus we used this information to describe the seed dispersal kernels for each model (null, individual, and family).
+Dispersal kernels in nature tend to be leptokurtic, with a peak near the origin and long tails, therefore kernel shape can be summarized by its kurtosis [@morales_effects_2006].
+We quantified the dispersal kernels produced in our models by the sample statistics of mean and kurtosis to describe the overall shape and tail of distribution of seed dispersal distances.
+In addition to this, we also fit a Weibull distribution via maximum likelihood to obtain estimates of the shape and scale parameters in this distribution.
+This probability distribution is commonly used in dispersal ecology and has been shown to be flexible enough to accommodate variability in the tails and provide informative parameters associated to the mean dispersal distance and fatness of the tail [@morales_effects_2006].
+We fit the data associated to seed dispersal distances produced by each of the three models via Maximum Likelihood using the Weibull density function associated with the package 'fitdistrplus'[@fitdistrplus]:
+$$W(x) = \left(\frac{a}{b}\right) \left(\frac{x}{b}\right)^{a-1} exp[-(x/{b})^{a}]$$
+
+Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter.
+It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo [-@Morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$.
+Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.
+Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 2.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
+
+Fig 2.
+Capation: Variation in Weibull distributions determined by the value of the shape parameter.
+The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
+
+```{r}
+library(ggplot2)
+
+# shape
+exptail <- 1
+thintail <- 0.2
+fattail <- 2
+
+#scale
+b <- 1
+kappaexp <- b^-exptail
+kappathin <- b^-thintail
+kappafat <- b^-fattail
+
+ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
+                color = "black", linetype = "dashed", size = 1.2) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
+                color = "black", linetype = "dotted", size = 1.2) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
+                color = "black", linetype = "solid", size = 1.2) +
+  ylab("") +
+  theme_bw()
+
+```
+
 - Already fit the weibull distribution for this.

### 2021-01-15 paper/paper.Rmd
Making the figures on a separate file

@@
 output:
+  word_document:
+    reference_docx: paper_ref.docx
   html_document:
     df_print: paged
-  word_document:
-    reference_docx: paper_ref.docx
 bibliography: mybibfile.bib
@@
 
-```{r eval = TRUE, fig.width=6}
-set.seed(5)
-
-data(ptpl)
-# Panel 1: landscape with tree in the center, origin
-
-df <- data.frame()
-ggplot(df) + xlim(-100, 100) + ylim(-100, 100) + 
-  theme(
-  panel.background = element_rect(fill = "lightblue",
-                                colour = "lightblue",
-                                size = 0.5, linetype = "solid"),
-  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
-                                colour = "white"), 
-  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
-                                colour = "white")
-  ) +
-  coord_equal() +
-  geom_point(aes(x = 0, y = 0), color = "green") -> p1
-
-# Panel 2: Table with gut retention times and the gamma distribution used for it
-n <- 10000
-grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
-grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
-tt <- max(grt_data$time)
-ggplot(grt_dens, aes(x = dat)) +
-  geom_density() + 
-  geom_point(data = grt_data, aes(x = time, y = 0)) +
-  theme_bw() + labs(x = "Time in minutes") -> p2
-
-# Panel 3: Exponential distribution used for animal movement lengths
-rate <- 1/mean(ptpl$mpm)
-md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
-ggplot(md_dens, aes(x = dat)) +
-  geom_density() + 
-  theme_bw() + labs(x = "Length of movement in one minute") -> p3
-
-# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
-
-distance <- sample(md_dens$dat, tt)
-angle <- runif(tt, min = 0, max = 360)
-distx <- distance*cos(angle)
-xloc <- c(0, cumsum(distx))
-disty <- distance*sin(angle)
-yloc <- c(0, cumsum(disty))
-animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
-seed_loc <- merge(animalTraj, grt_data, by = "time")
-mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
-
-ggplot() +
-  geom_path(data = animalTraj, aes(x = xloc, y = yloc)) +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
-  geom_point(aes(x = 0, y = 0), color = "green") -> p4
-
-# Panel 5: Calculation of seed dispersal distances to the focus tree
-
-ggplot() +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
-  geom_point(aes(x = 0, y = 0), color = "green") +
-  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0)) -> p5
-
-# Panel 6: Calculation of seed dispersion
-
-ggplot() +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red") +
-  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue") +
-  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y)) -> p6
-
-# ALL
-plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], label_size = 10, nrow = 3)
-
-```
-
 ## Parameterization
@@
 Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter.
-It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo [-@Morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$.
-Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.
+It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo  [-@morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$.
+<!-- Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.
+-->
 Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 2.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
@@
 Fig 2.
-Capation: Variation in Weibull distributions determined by the value of the shape parameter.
+Caption: Variation in Weibull distributions determined by the value of the shape parameter.
 The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
 
-```{r}
+```{r fig.width=3, fig.height=2.5}
 library(ggplot2)
+library(dplyr)
 
@@
                 color = "black", linetype = "solid", size = 1.2) +
-  ylab("") +
+  ylab("") + xlab("") +
   theme_bw()
@@
 ```
+Explain what are statistics of extremes and why they can be useful here.
+cite the GArcia 2017 paper, the Gaines and Denny 1993, Katz 2005.
+Coles 2001 for the theory or base knowledge.
+In our case, because we are looking at these simulated seed dispersal kernels, we use a peak over threshold (POT) approach, in which we find the threshold for the data and use an extreme value distribution to fit the tail.
+Describe the math probabilty density functions and the three laws that the extreme value distribution follows. 
+For POT use a generalized pareto distribution.
 
-- Already fit the weibull distribution for this.
-Mention that we chose this distribution because it is commonly used in dispersal ecology due to its felixibility, how adjusting the scale parameter changes the tail of the distribution.
-This is both in Garcia2017 (>1 fast decaying, <1 low decay fat tail, =1 exponential decay) and Carlomorales2006 papers, but I think they present it slightly different.
+- Based on Diagnostic plots, we used these values as the threshold for each of the models.
 
-- We inspected the QQ plots to check for fitting. Figuere Supplement
-
-- They mention declustering the data, and perhaps in that case I could be using the mean_xy_dispersal, but no because this immendiately brings down the extent of long distance dispersal events.
+From extRemes package: "where shape = 0 gives rise to the exponential df (light tail), shape > 0 the Pareto df (heavy tail) and shape < 0 the Beta df (bounded upper tail at location - scale.u/shape).
+Theoretical justification supports the use of the GP df family for modeling excesses over a high threshold (i.e., y = x - threshold)."
 
@@
 ```{r fig.width=6}
+library(dplyr)
+library(cowplot)
 
@@
 
+```{r}
+knitr::kable(dispersion_table)
+```
+
 ## Weibull seed dispersal kernel

### 2021-01-15 paper/dispersal_kernels.R
no change

@@ -146,8 +146,5 @@ dispersal_kernel_table <- data.frame(
 )
 
 
-
-
-
 save.image("paper/dispersal_kernels.RData")
 

### 2021-01-15 paper/paper.Rmd
removing figures

@@
 
-Fig 2.
-Caption: Variation in Weibull distributions determined by the value of the shape parameter.
-The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
-
-```{r fig.width=3, fig.height=2.5}
-library(ggplot2)
-library(dplyr)
-
-# shape
-exptail <- 1
-thintail <- 0.2
-fattail <- 2
-
-#scale
-b <- 1
-kappaexp <- b^-exptail
-kappathin <- b^-thintail
-kappafat <- b^-fattail
-
-ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
-                color = "black", linetype = "dashed", size = 1.2) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
-                color = "black", linetype = "dotted", size = 1.2) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
-                color = "black", linetype = "solid", size = 1.2) +
-  ylab("") + xlab("") +
-  theme_bw()
-
-```
 Explain what are statistics of extremes and why they can be useful here.

### 2021-01-15 paper/figures_tables.Rmd
Figures 1 and 2

@@
 knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, results = 'hide')
+```
+
+```{r libraries}
+library(ggplot2)
+library(aracari)
+library(cowplot)
+library(dplyr)
+
+```
+
+```{r}
+# Simulate the data for one run
+
+set.seed(5)
+
+data(ptpl)
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0), color = "red") +
+  #geom_point(aes(x = tt, y = 0), color = "red") +
+  theme_bw() + labs(x = "Time in minutes", y = "Density") -> fig_GRT
+
+# Panel 3: Exponential distribution used for animal movement lengths
+rate <- 1/mean(ptpl$mpm)
+md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
+md_hist <- data.frame(md = round(sample(md_dens$dat, tt)))
+
+ggplot(md_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = md_hist, aes(x = md, y = 0)) +
+  theme_bw() + labs(x = "Distance in meters", y = "Density") -> fig_MD
+
+ggplot(md_hist, aes(x = md)) +
+  geom_histogram() +
+  theme_bw() + labs(x = "Distance in meters", y = "Count") -> fig_MD_hist
+
+# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
+set.seed(5)
+distance <- md_hist$md
+angle <- runif(tt, min = 0, max = 360)
+distx <- distance*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- distance*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+seed_loc <- merge(animalTraj, grt_data, by = "time")
+mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
+
+ggplot() +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
+  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_traj
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_disp
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  #geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y), linetype = "dashed", color = "blue") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_agg
+
+```
+
+## Figure 1. 
+Density distributions from which we sample gut retention time (GRT) and movement distance (MD).
+
+```{r fig.width=2.5, fig.height=4}
+plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
+#ggsave("testfig.tiff", dpi = 300, width = 3, units = "in")
+```
+
+## Figure 2.
+Simulation example where animal movement determines location for seeds dropped.
+Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.
+
+```{r fig.height=2, fig.width=6}
+plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
+```
+
+## Figure 3.
+Variation in Weibull distributions determined by the value of the shape parameter.
+The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
+
+```{r}
+# shape
+exptail <- 1
+thintail <- 0.2
+fattail <- 2
+
+#scale
+b <- 1
+kappaexp <- b^-exptail
+kappathin <- b^-thintail
+kappafat <- b^-fattail
+
+ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
+                color = "black", linetype = "dashed", size = 1.2) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
+                color = "black", linetype = "dotted", size = 1.2) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
+                color = "black", linetype = "solid", size = 1.2) +
+  ylab("") + xlab("") +
+  theme_bw()
+
+```
+
+## Figure 4. 
+Seed dispersal kernels produced by the three models considered
+
+```{r}
+
 ```

### 2021-01-15 paper/figures_tables.Rmd
updates

@@
 
-```{r}
+```{r fig.width=3, fig.height=2.5}
 # shape
@@
   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
-                color = "black", linetype = "dashed", size = 1.2) +
+                color = "black", linetype = "dashed", size = 0.8) +
   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
-                color = "black", linetype = "dotted", size = 1.2) +
+                color = "black", linetype = "dotted", size = 0.8) +
   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
-                color = "black", linetype = "solid", size = 1.2) +
+                color = "black", linetype = "solid", size = 0.8) +
   ylab("") + xlab("") +
@@
 
+```{r}
+load("paper/dispersal_kernels.RData")
+
+```
+
 ## Figure 4. 
-Seed dispersal kernels produced by the three models considered
+Seed dispersal kernels produced by the three models considered with Weibull distribution overlaid
+
+```{r fig.width=3}
+bind_rows(null_dispersal %>% mutate(model = "Null"), 
+          indiv_dispersal %>% mutate(model = "Individual"),
+          fam_dispersal %>% mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data
+
+dispersal_data %>% 
+  ggplot(., aes(x = dispersal, group = model)) +
+  facet_wrap(~model, nrow = 3) +
+  geom_histogram(aes(y = ..density..), binwidth = 50) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)")
+
+```
+
+```{r}
+null_dispersal %>% 
+  ggplot(., aes(x = dispersal)) +
+  geom_histogram(aes(y = ..density..), binwidth = 50) +
+  stat_function(fun = dweibull, n = 100, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2]),
+                linetype = "solid", size = 1) +
+  theme_bw() +
+  labs(y = "Density", "Seed dispersal (m)") +
+  lims(y = c(0, 0.004), x = c(0, 1500))
+```
 
@@
 
-```
+null_dispersion %>% 
+  mutate(model = "Null") %>% 
+  bind_rows(indiv_dispersion %>% 
+              mutate(model = "Individual")) %>% 
+  bind_rows(fam_dispersion %>% 
+              mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
 
-```{r movementdensity, fig.width=6, fig.height=2}
+all_disp_data %>% 
+  ggplot(., aes(y = mean_dispersal, group = model)) +
+  #facet_wrap(~model, ncol = 3) +
+  geom_boxplot() +
+  theme_bw()  +
+  labs(y = "Seed dispersal (m)") -> b
 
-load("paper/simple_exp_runs.RData")
+all_disp_data %>% 
+  ggplot(., aes(y = seed_dispersion)) +
+  facet_wrap(~model, ncol = 3) +
+  geom_boxplot() +
+  theme_bw() +
+  theme(strip.background = element_blank(),
+        strip.text = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank()) +
+  labs(y = "Dispersion (m)") -> c
 
-library(ggplot2)
-library(dplyr)
+#plot_grid(a,b, nrow = 2)
 
-# Figure for movement rates at the three levels
-
-rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
-  bind_rows(., indiv_moverate %>%
-              rename(level = Bird_ID)) %>%
-  bind_rows(., fam_moverate %>%
-              rename(level = fam_g)) %>%
-  mutate(model = ifelse(level == "null", "Null",
-                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))
-
-n <- 1000
-dens_rates <- NULL
-for(i in 1:length(rates$level)) {
-  dens_exp <- rexp(n, rate = 1/rates$movrate[i])
-
-  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
-  dens_rates <- rbind.data.frame(dens_rates, out)
-}
-
-dens_rates %>%
-  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
-  ggplot(., aes(x = value, group = level, color = model)) +
-  facet_wrap(~model) +
-  geom_density() +
-  scale_color_manual(values = c("red", "grey", "black"), guide = "none") +
-  theme_bw() + labs(x = "Distance in meters per minute") +
-  #coord_cartesian(xlim = c(100, 300), ylim = c(0, 0.0025))+
-  NULL
-```
-
-```{r grt, fig.width=3, fig.height=2}
-
-n <- 10000
-grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
-grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
-tt <- max(grt_data$time)
-ggplot(grt_dens, aes(x = dat)) +
-  geom_density() + 
-  geom_point(data = grt_data, aes(x = time, y = 0)) +
-  theme_bw() + labs(x = "Time in minutes")
+# Edit redundant labels
+# Fix names for axes
 

### 2021-01-15 paper/paper.Rmd
remove a figure

@@
 
-```{r}
-load("dispersal_kernels.RData")
-```
 ## Seed dispersal distances and long distance dispersal
-
-**Figure 3.**
-```{r fig.width=6}
-library(dplyr)
-library(cowplot)
-
-null_kernel <- null_dispersal %>% 
-  ggplot(., aes(x = dispersal)) +
-  geom_histogram(aes(y = ..density..))
-
-indiv_kernel <- indiv_dispersal %>% 
-  ggplot(., aes(x = dispersal)) +
-  geom_histogram(aes(y = ..density..))
-
-fam_kernel <- fam_dispersal %>% 
-  ggplot(., aes(x = dispersal)) +
-  geom_histogram(aes(y = ..density..))
-
-plot_grid(null_kernel, indiv_kernel, fam_kernel, nrow = 3)
-
-# Make the axis be the same length and beaks
-# Remove redundant labels
-# Test 3 rows or 3 columns
-# Add red vertical line for LDD cutoff
-# Include a zoom cut off for the tail
-
-# plot_grid(
-#   fam_dispersal %>%
-#     ggplot(., aes(x = dispersal)) +
-#     geom_histogram(),
-#   plot_grid(fam_dispersion %>%
-#             ggplot(., aes(y = mean_dispersal)) +
-#             geom_boxplot(),
-#           fam_dispersion %>%
-#             ggplot(., aes(y = seed_dispersion)) +
-#             geom_boxplot()), nrow = 2)
-```
 
@@
 The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
-
-**Figure 4.**
-```{r fig.width=3, fig.height=5}
-
-null_dispersion %>% 
-  mutate(model = "Null") %>% 
-  bind_rows(indiv_dispersion %>% 
-              mutate(model = "Individual")) %>% 
-  bind_rows(fam_dispersion %>% 
-              mutate(model = "Family")) %>% 
-  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
-
-all_disp_data %>% 
-  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
-  geom_boxplot() -> dispersal_xy_box
-
-all_disp_data %>% 
-  ggplot(., aes(y = mean_dispersal, x = model)) +
-  geom_boxplot() -> dispersal_box
-
-all_disp_data %>% 
-  ggplot(., aes(y = seed_dispersion, x = model)) +
-  geom_boxplot() -> dispersion_box
-
-plot_grid(dispersal_xy_box, dispersal_box, dispersion_box, nrow = 3)
-
-# Edit redundant labels
-# Fix names for axes
-
-```
 

### 2021-01-15 paper/paper.Rmd
delete the tables
Updating with figures in the right place

@@
 
-```{r setup, echo=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
 ```
@@
 ```
-
 \newpage
@@
 
-At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8).
-Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (which varied depending on the underlying model such as the null, individual or family group model) and a random direction from $0^o$ to $360^o$ degrees was used to determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency (*Edit references* Turchin 1998).
-Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape.
+At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8, Figure 1a).
+Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (Figure 1b), which varied depending on the underlying model such as the null, individual or family group model.
+A random direction from $0^o$ to $360^o$ degrees was used to determine the angle of movement, which with the movement distance would determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency (*Edit references* Turchin 1998).
+Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape (Figure 2a).
 For each of our models we ran 10,000 simulation runs per individual or family group, depending on the model, and collected information on animal and seed locations at every time step.
+
+```{r}
+# Simulate the data for one run
+
+set.seed(5)
+
+data(ptpl)
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0), color = "red") +
+  #geom_point(aes(x = tt, y = 0), color = "red") +
+  theme_bw() + labs(x = "Time in minutes", y = "Density") -> fig_GRT
+
+# Panel 3: Exponential distribution used for animal movement lengths
+rate <- 1/mean(ptpl$mpm)
+md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
+md_hist <- data.frame(md = round(sample(md_dens$dat, tt)))
+
+ggplot(md_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = md_hist, aes(x = md, y = 0)) +
+  theme_bw() + labs(x = "Distance in meters", y = "Density") -> fig_MD
+
+ggplot(md_hist, aes(x = md)) +
+  geom_histogram() +
+  theme_bw() + labs(x = "Distance in meters", y = "Count") -> fig_MD_hist
+
+# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
+set.seed(5)
+distance <- md_hist$md
+angle <- runif(tt, min = 0, max = 360)
+distx <- distance*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- distance*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+seed_loc <- merge(animalTraj, grt_data, by = "time")
+mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
+
+ggplot() +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
+  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_traj
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_disp
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  #geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y), linetype = "dashed", color = "blue") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_agg
+
+```
+
+#### Figure 1. 
+Density distributions from which we sample gut retention time (GRT) and movement distance (MD).
+
+```{r fig.width=2.5, fig.height=4}
+plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
+```
 
@@
 The proportion of long-distance dispersal events, maximum dispersal distance, and average seed dispersion were used to compare seed dispersal between our three models of individual variation (Table1).
+
+#### Figure 2.
+Simulation example where animal movement determines location for seeds dropped.
+Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.
+
+```{r fig.height=2, fig.width=6}
+plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
+```
 
@@
 -->
-Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 2.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
+Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
+
+#### Figure 3.
+Variation in Weibull distributions determined by the value of the shape parameter.
+The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
+
+```{r fig.width=3, fig.height=2.5}
+# shape
+exptail <- 1
+thintail <- 0.2
+fattail <- 2
+
+#scale
+b <- 1
+kappaexp <- b^-exptail
+kappathin <- b^-thintail
+kappafat <- b^-fattail
+
+ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
+                color = "black", linetype = "dashed", size = 0.8) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
+                color = "black", linetype = "dotted", size = 0.8) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
+                color = "black", linetype = "solid", size = 0.8) +
+  ylab("") + xlab("") +
+  theme_bw()
+
+```
 
@@
 
-```{r}
-knitr::kable(dispersion_table)
-```
-
 ## Weibull seed dispersal kernel
-
-**Table 1.**
-```{r}
-
-knitr::kable(dispersal_kernel_table)
-```
 

### 2021-01-15 paper/figures_tables.Rmd
adding figure

@@
 title: "Figures and Tables"
-subtitle: " "
+subtitle: ' '
 output:
   html_document:
-      toc: true
-bibliography: "../paper/mybibfile.bib"
+    toc: yes
+  word_document:
+    toc: yes
+bibliography: ../paper/mybibfile.bib
 ---
@@
 plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
-#ggsave("testfig.tiff", dpi = 300, width = 3, units = "in")
 ```
@@
 
-## Figure 4. 
-Seed dispersal kernels produced by the three models considered with Weibull distribution overlaid
-
-```{r fig.width=3}
+```{r eval = FALSE,  fig.width=3}
 bind_rows(null_dispersal %>% mutate(model = "Null"), 
@@
 
-```{r}
+```{r eval = FALSE}
+null_prms <- null_weibull$estimate
+null_sd <- null_weibull$sd
 null_dispersal %>% 
   ggplot(., aes(x = dispersal)) +
-  geom_histogram(aes(y = ..density..), binwidth = 50) +
-  stat_function(fun = dweibull, n = 100, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2]),
-                linetype = "solid", size = 1) +
+  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
+  stat_function(fun = dweibull, n = 100, args = list(shape = null_prms[1], scale = null_prms[2]),
+                linetype = "solid", size = 1, color = "black") +
   theme_bw() +
-  labs(y = "Density", "Seed dispersal (m)") +
-  lims(y = c(0, 0.004), x = c(0, 1500))
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  lims(y = c(0, 0.004), x = c(0, 1500)) -> null_kernel
+
+indiv_prms <- indiv_weibull$estimate
+indiv_sd <- indiv_weibull$sd
+indiv_dispersal %>% 
+  ggplot(., aes(x = dispersal)) +
+  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
+  stat_function(fun = dweibull, n = 100, args = list(shape = indiv_prms[1], scale = indiv_prms[2]),
+                linetype = "solid", size = 1, color = "black") +
+  theme_bw() +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  lims(y = c(0, 0.004), x = c(0, 1500)) -> indiv_kernel
+
+fam_prms <- fam_weibull$estimate
+fam_sd <- fam_weibull$sd
+fam_dispersal %>% 
+  ggplot(., aes(x = dispersal)) +
+  geom_histogram(aes(y = ..density..), color = "grey", fill = "grey") +
+  stat_function(fun = dweibull, n = 100, args = list(shape = fam_prms[1], scale = fam_prms[2]),
+                linetype = "solid", size = 1, color = "black") +
+  theme_bw() +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  lims(y = c(0, 0.004), x = c(0, 1500)) -> fam_kernel
+
+plot_grid(null_kernel, indiv_kernel, fam_kernel, ncol = 1)
 ```
+
+## Figure 4. 
+Box plots to show the distribution of mean seed dispersal distance and seed dispersion per simulation run.
+In this case, we are looking at the data per simulation run, since we calculate seed dispersion in relation to the mean seed location, and this is done for each simulation run with five seeds each.
+Here, we consider mean seed dispersal as the distance from the origin to the mean seed location for each simulation run.
 
@@
 all_disp_data %>% 
-  ggplot(., aes(y = mean_dispersal, group = model)) +
-  #facet_wrap(~model, ncol = 3) +
+  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
   geom_boxplot() +
   theme_bw() +
-  labs(y = "Seed dispersal (m)") -> b
+  labs(y = "Mean dispersal (m)") +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank()) -> a
 
 all_disp_data %>% 
-  ggplot(., aes(y = seed_dispersion)) +
-  facet_wrap(~model, ncol = 3) +
+  ggplot(., aes(y = seed_dispersion, x = model)) +
   geom_boxplot() +
   theme_bw() +
-  theme(strip.background = element_blank(),
-        strip.text = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) +
-  labs(y = "Dispersion (m)") -> c
+  labs(y = "Seed dispersion (m)") +
+  theme(axis.title.x = element_blank()) -> b
 
-#plot_grid(a,b, nrow = 2)
+plot_grid(a,b, nrow = 2)
 
@@
 ```
+
+# Table 1.
+
+```{r}
+dispersal_kernel_table <- data.frame(
+  Model = c("Null", "Individual", "Family"),
+  Mean_dispersal = c(signif(mean(null_dispersal$dispersal), 4),
+                     signif(mean(indiv_dispersal$dispersal), 4),
+                     signif(mean(fam_dispersal$dispersal),4)),
+  Seed_dispersion = c(signif(mean(null_dispersion$seed_dispersion), 4),
+                      signif(mean(indiv_dispersion$seed_dispersion), 4),
+                      signif(mean(fam_dispersion$seed_dispersion),4)),
+  Max_dispersal = c(signif(max(null_ldd$global_max), 4),
+                           signif(max(indiv_ldd$global_max), 4),
+                           signif(max(fam_ldd$global_max), 4)),
+  # Max_dispersal = c(paste0(signif(null_ldd$max_mean, 3), " (", signif(null_ldd$max_sd, 1), ")"),
+  #                   paste0(signif(indiv_ldd$max_mean, 3), " (", signif(indiv_ldd$max_sd, 1), ")"),
+  #                   paste0(signif(fam_ldd$max_mean, 3), " (", signif(fam_ldd$max_sd, 1), ")")),
+  LDD = c(paste0(signif(null_ldd$prcnt_ldd, 3), " (", signif(null_ldd$sd_ldd, 1), ")", "%"),
+          paste0(signif(indiv_ldd$prcnt_ldd, 3), " (", signif(indiv_ldd$sd_ldd, 1), ")", "%"),
+          paste0(signif(fam_ldd$prcnt_ldd, 3), " (", signif(fam_ldd$sd_ldd, 1), ")", "%")),
+  Weibull_Shape = c(paste0(signif(null_weibull$estimate[1], 4), " (", signif(null_weibull$sd[1], 2), ")"),
+                    paste0(signif(indiv_weibull$estimate[1], 4), " (", signif(indiv_weibull$sd[1], 2), ")"),
+                    paste0(signif(fam_weibull$estimate[1], 4), " (", signif(fam_weibull$sd[1], 2), ")")),
+  Weibull_Scale = c(paste0(signif(null_weibull$estimate[2], 4), " (", signif(null_weibull$sd[2], 2), ")"),
+                     paste0(signif(indiv_weibull$estimate[2], 4), " (", signif(indiv_weibull$sd[2], 2), ")"),
+                     paste0(signif(fam_weibull$estimate[2], 4), " (", signif(fam_weibull$sd[2], 2), ")"))
+
+)
+
+```

### 2021-01-15 paper/figures_tables.Rmd
Trying a different layout

@@
 
-```{r eval = FALSE,  fig.width=3}
+### Figure x.
+Distribution of dispersal distances produced by each of the simulation models considered.
+```{r fig.width=3}
 bind_rows(null_dispersal %>% mutate(model = "Null"), 
@@
 
+```{r fig.width=6, fig.height=3}
+plot_grid(a,b, ncol = 2)
+```
+
 # Table 1.

### 2021-01-15 paper/simple_exp_paper.R
change seed

@@ -108,7 +108,7 @@ library(ggplot2)
 library(purrr)
 library(cowplot)
 
-set.seed(27)
+set.seed(227)
 
 data(ptpl)
 

### 2021-01-15 paper/dispersal_kernels.R
separate tables into smaller ones

@@ -30,7 +30,11 @@ fam_weibull$estimate
 gofstat(fam_weibull)
 # plot(fam_weibull)
 
-
+weibull_params <- data.frame(model = c("Null", "Individual", "Family"),
+                             shape = c(null_weibull$estimate[1], indiv_weibull$estimate[1], fam_weibull$estimate[1]),
+                             shape_sd = c(null_weibull$sd[1], indiv_weibull$sd[1], fam_weibull$sd[1]),
+                             scale = c(null_weibull$estimate[2], indiv_weibull$estimate[2], fam_weibull$estimate[2]),
+                             scale_sd = c(null_weibull$sd[2], indiv_weibull$sd[2], fam_weibull$sd[2]))
 
 # Long distance dispersal calculations
 
@@ -46,7 +50,8 @@ null_dispersal %>%
             max_sd = sd(max_d),
             sd_ldd = sd(prop_ldd),
             prop_ldd = mean(prop_ldd),
-            prcnt_ldd = prop_ldd *100) -> null_ldd
+            prcnt_ldd = prop_ldd *100) %>%
+  mutate(model = "Null")-> null_ldd
 
 indiv_dispersal %>%
   filter(., dispersal >= 500) %>%
@@ -60,7 +65,8 @@ indiv_dispersal %>%
             max_sd = sd(max_d),
             sd_ldd = sd(prop_ldd),
             prop_ldd = mean(prop_ldd),
-            prcnt_ldd = prop_ldd *100) -> indiv_ldd
+            prcnt_ldd = prop_ldd *100) %>%
+  mutate(model = "Individual") -> indiv_ldd
 
 fam_dispersal %>%
   filter(., dispersal >= 500) %>%
@@ -74,7 +80,10 @@ fam_dispersal %>%
             max_sd = sd(max_d),
             sd_ldd = sd(prop_ldd),
             prop_ldd = mean(prop_ldd),
-            prcnt_ldd = prop_ldd *100) -> fam_ldd
+            prcnt_ldd = prop_ldd *100) %>%
+  mutate(model = "Family") -> fam_ldd
+
+ldd_table <- bind_rows(null_ldd, indiv_ldd, fam_ldd)
 
 # Dispersal and dispersion calculation
 
@@ -112,7 +121,17 @@ indiv_dispersal %>%
   facet_wrap(~id, nrow=2) +
   geom_histogram()
 
[…]

### 2021-01-15 paper/paper.Rmd
updated figures and tables

@@
 ```
+
+```{r}
+load("paper/dispersal_kernels.RData")
+```
+
 \newpage
@@
   geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
-  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y), linetype = "dashed", color = "blue") +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y),
+               linetype = "dashed", color = "blue") +
+  geom_segment(aes(x = 0, xend = mean_seed_loc$x, y = 0, yend = mean_seed_loc$y),
+               linetype = "solid", color = "black") +
   labs(x = "x", y = "y") +
@@
 We calculated seed dispersal distance as the euclidean distance of each seed to the parent plant.
-Given that our models only considered one parent plant located at the origin per simmulation, we calculated seed dispersal distance (DD) as the distance from each seed's location to the origin as follows:
+Given that our models only considered one parent plant located at the origin per simulation, we calculated seed dispersal distance (DD) as the distance from each seed's location to the origin as follows:
 $$DD_i = \sqrt{(0-x_i)^2 + (0-y_i)^2} $$
@@
 
-## Seed dispersal distances and long distance dispersal
+## Seed dispersal distances and aggregation
 
-## Seed dispersion aggregation
+```{r fig.width=6}
+bind_rows(null_dispersal %>% mutate(model = "Null"), 
+          indiv_dispersal %>% mutate(model = "Individual"),
+          fam_dispersal %>% mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data
+
+dispersal_data %>% 
+  ggplot(., aes(x = dispersal, group = model)) +
+  facet_wrap(~model, ncol = 3) +
+  geom_histogram(aes(y = ..density..), binwidth = 50) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> histograms
+
+null_dispersion %>% 
+  mutate(model = "Null") %>% 
+  bind_rows(indiv_dispersion %>% 
+              mutate(model = "Individual")) %>% 
+  bind_rows(fam_dispersion %>% 
+              mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
+
+all_disp_data %>% 
+  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
+  geom_boxplot() +
+  theme_bw() +
+  labs(y = "Mean dispersal (m)") +
+  theme(axis.title.x = element_blank()) -> a
+
+all_disp_data %>% 
+  ggplot(., aes(y = seed_dispersion, x = model)) +
+  geom_boxplot() +
+  theme_bw() +
+  labs(y = "Seed dispersion (m)") +
+  theme(axis.title.x = element_blank()) -> b
+
+boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))
+
+plot_grid(histograms, boxplots, nrow=2, labels = c("a", ""))
+
+# Edit redundant labels
+# Fix names for axes
+
+```
+
+## Long distance dispersal
+
 The mean dispersal in the boxplots is not the same as the dispersal distances before.
@@
 
+```{r}
+knitr::kable(dispersal_kernel_table %>% 
+               rename(Long_distance = LDD))
+```
+
 ## Weibull seed dispersal kernel 
+```{r}
+knitr::kable(weibull_table)
+```
 

### 2021-01-22 paper/dispersal_kernels.R
Add sd to measures of dispersal and dispersion

@@ -140,12 +140,18 @@ fam_dispersal %>%
 
 dispersal_kernel_table <- data.frame(
   Model = c("Null", "Individual", "Family"),
-  Mean_dispersal = c(signif(mean(null_dispersal$dispersal), 4),
-                     signif(mean(indiv_dispersal$dispersal), 4),
-                     signif(mean(fam_dispersal$dispersal),4)),
-  Seed_dispersion = c(signif(mean(null_dispersion$seed_dispersion), 4),
-                      signif(mean(indiv_dispersion$seed_dispersion), 4),
-                      signif(mean(fam_dispersion$seed_dispersion),4)),
+  Mean.dispersal_sd = c(paste0(signif(mean(null_dispersal$dispersal), 4),
+                               " (", signif(sd(null_dispersal$dispersal), 2), ")"),
+                        paste0(signif(mean(indiv_dispersal$dispersal), 4),
+                               " (", signif(sd(indiv_dispersal$dispersal), 2), ")"),
+                        paste0(signif(mean(fam_dispersal$dispersal), 4),
+                               " (", signif(sd(fam_dispersal$dispersal), 2), ")")),
+  Seed.dispersion_sd = c(paste0(signif(mean(null_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(null_dispersion$seed_dispersion), 2), ")"),
+                         paste0(signif(mean(indiv_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(indiv_dispersion$seed_dispersion), 2), ")"),
+                         paste0(signif(mean(fam_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(fam_dispersion$seed_dispersion), 2), ")")),
   Max_dispersal = c(signif(max(null_ldd$global_max), 4),
                            signif(max(indiv_ldd$global_max), 4),
                            signif(max(fam_ldd$global_max), 4)),

### 2021-01-22 paper/figures_tables.Rmd
adding alternatives to the figures.
Ok. Getting figures and tables on different Rmd

--- 2021-01-15 paper/figures_tables.Rmd
@@
 ```
-
-```{r}
-# Simulate the data for one run
-
-set.seed(5)
-
-data(ptpl)
-
-# Panel 2: Table with gut retention times and the gamma distribution used for it
-n <- 10000
-grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
-grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
-tt <- max(grt_data$time)
-ggplot(grt_dens, aes(x = dat)) +
-  geom_density() + 
-  geom_point(data = grt_data, aes(x = time, y = 0), color = "red") +
-  #geom_point(aes(x = tt, y = 0), color = "red") +
-  theme_bw() + labs(x = "Time in minutes", y = "Density") -> fig_GRT
-
-# Panel 3: Exponential distribution used for animal movement lengths
-rate <- 1/mean(ptpl$mpm)
-md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
-md_hist <- data.frame(md = round(sample(md_dens$dat, tt)))
-
-ggplot(md_dens, aes(x = dat)) +
-  geom_density() + 
-  geom_point(data = md_hist, aes(x = md, y = 0)) +
-  theme_bw() + labs(x = "Distance in meters", y = "Density") -> fig_MD
-
-ggplot(md_hist, aes(x = md)) +
-  geom_histogram() +
-  theme_bw() + labs(x = "Distance in meters", y = "Count") -> fig_MD_hist
-
-# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
-set.seed(5)
-distance <- md_hist$md
-angle <- runif(tt, min = 0, max = 360)
-distx <- distance*cos(angle)
-xloc <- c(0, cumsum(distx))
-disty <- distance*sin(angle)
-yloc <- c(0, cumsum(disty))
-animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
-seed_loc <- merge(animalTraj, grt_data, by = "time")
-mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
-
-ggplot() +
-  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
-  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
-  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
-  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
-  labs(x = "x", y = "y") +
-  coord_fixed() +
-  theme_bw() -> fig_traj
-
-ggplot() +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
-  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
-  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
-  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
-  labs(x = "x", y = "y") +
-  coord_fixed() +
-  theme_bw() -> fig_disp
-
-ggplot() +
-  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
-  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
-  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
-  #geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
-  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
-  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y), linetype = "dashed", color = "blue") +
-  labs(x = "x", y = "y") +
-  coord_fixed() +
-  theme_bw() -> fig_agg
-
-```
-
-## Figure 1. 
-Density distributions from which we sample gut retention time (GRT) and movement distance (MD).
-
-```{r fig.width=2.5, fig.height=4}
-plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
-#ggsave("testfig.tiff", dpi = 300, width = 3, units = "in")
-```
-
-## Figure 2.
-Simulation example where animal movement determines location for seeds dropped.
-Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.
-
-```{r fig.height=2, fig.width=6}
-plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
-```
-
-## Figure 3.
-Variation in Weibull distributions determined by the value of the shape parameter.
-The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
-
-```{r fig.width=3, fig.height=2.5}
-# shape
-exptail <- 1
-thintail <- 0.2
-fattail <- 2
-
-#scale
-b <- 1
-kappaexp <- b^-exptail
-kappathin <- b^-thintail
-kappafat <- b^-fattail
-
-ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
-                color = "black", linetype = "dashed", size = 0.8) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
-                color = "black", linetype = "dotted", size = 0.8) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
-                color = "black", linetype = "solid", size = 0.8) +
-  ylab("") + xlab("") +
-  theme_bw()
-
-```
-
-```{r}
-load("paper/dispersal_kernels.RData")
-
-```
-
-## Figure 4. 
-Seed dispersal kernels produced by the three models considered with Weibull distribution overlaid
-
-```{r fig.width=3}
-bind_rows(null_dispersal %>% mutate(model = "Null"), 
-          indiv_dispersal %>% mutate(model = "Individual"),
-          fam_dispersal %>% mutate(model = "Family")) %>% 
-  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data
-
-dispersal_data %>% 
-  ggplot(., aes(x = dispersal, group = model)) +
-  facet_wrap(~model, nrow = 3) +
-  geom_histogram(aes(y = ..density..), binwidth = 50) +
-  theme_bw() +
-  theme(strip.background = element_rect(fill = "white")) +
-  labs(y = "Density", x = "Seed dispersal (m)")
-
-```
-
-```{r}
-null_dispersal %>% 
-  ggplot(., aes(x = dispersal)) +
-  geom_histogram(aes(y = ..density..), binwidth = 50) +
-  stat_function(fun = dweibull, n = 100, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2]),
-                linetype = "solid", size = 1) +
-  theme_bw() +
-  labs(y = "Density", "Seed dispersal (m)") +
-  lims(y = c(0, 0.004), x = c(0, 1500))
-```
-
-```{r}
-
-null_dispersion %>% 
-  mutate(model = "Null") %>% 
-  bind_rows(indiv_dispersion %>% 
-              mutate(model = "Individual")) %>% 
-  bind_rows(fam_dispersion %>% 
-              mutate(model = "Family")) %>% 
-  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
-
-all_disp_data %>% 
-  ggplot(., aes(y = mean_dispersal, group = model)) +
-  #facet_wrap(~model, ncol = 3) +
-  geom_boxplot() +
-  theme_bw()  +
-  labs(y = "Seed dispersal (m)") -> b
-
-all_disp_data %>% 
-  ggplot(., aes(y = seed_dispersion)) +
-  facet_wrap(~model, ncol = 3) +
-  geom_boxplot() +
-  theme_bw() +
-  theme(strip.background = element_blank(),
-        strip.text = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank()) +
-  labs(y = "Dispersion (m)") -> c
-
-#plot_grid(a,b, nrow = 2)
-
-# Edit redundant labels
-# Fix names for axes
-
-```

### 2021-01-22 paper/figures_tables.Rmd
Updated figures here

@@
 ```
+
+```{r}
+load("paper/dispersal_kernels.RData")
+```
+
+```{r}
+# Simulate the data for one run
+
+set.seed(5)
+
+data(ptpl)
+
+# Panel 2: Table with gut retention times and the gamma distribution used for it
+n <- 10000
+grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
+grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
+tt <- max(grt_data$time)
+ggplot(grt_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = grt_data, aes(x = time, y = 0), color = "red") +
+  #geom_point(aes(x = tt, y = 0), color = "red") +
+  theme_bw() + labs(x = "Time in minutes", y = "Density") -> fig_GRT
+
+# Panel 3: Exponential distribution used for animal movement lengths
+rate <- 1/mean(ptpl$mpm)
+md_dens <- data.frame(seq = 1:n, dat = rexp(n, rate = rate))
+md_hist <- data.frame(md = round(sample(md_dens$dat, tt)))
+
+ggplot(md_dens, aes(x = dat)) +
+  geom_density() + 
+  geom_point(data = md_hist, aes(x = md, y = 0)) +
+  theme_bw() + labs(x = "Distance in meters", y = "Density") -> fig_MD
+
+ggplot(md_hist, aes(x = md)) +
+  geom_histogram() +
+  theme_bw() + labs(x = "Distance in meters", y = "Count") -> fig_MD_hist
+
+# Panel 4: Animal trajectory and locations of the seeds at the time the seeds are dropped
+set.seed(5)
+distance <- md_hist$md
+angle <- runif(tt, min = 0, max = 360)
+distx <- distance*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- distance*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:tt, xloc = xloc, yloc = yloc)
+seed_loc <- merge(animalTraj, grt_data, by = "time")
+mean_seed_loc <- data.frame(x = mean(seed_loc$xloc), y = mean(seed_loc$yloc))
+
+ggplot() +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
+  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_traj
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_disp
+
+ggplot() +
+  geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
+  geom_point(aes(x = 0, y = 0), color = "black", size = 5)+
+  geom_vline(aes(xintercept=0), linetype = "dotted") + geom_hline(aes(yintercept = 0), linetype = "dotted") +
+  #geom_segment(aes(x = seed_loc$xloc, xend = 0, y = seed_loc$yloc, yend = 0), linetype = "dashed", color = "red") +
+  geom_point(data = mean_seed_loc, aes(x = x, y = y), color = "blue", size = 4) +
+  geom_segment(aes(x = seed_loc$xloc, xend = mean_seed_loc$x, y = seed_loc$yloc, yend = mean_seed_loc$y),
+               linetype = "dashed", color = "blue") +
+  geom_segment(aes(x = 0, xend = mean_seed_loc$x, y = 0, yend = mean_seed_loc$y),
+               linetype = "solid", color = "black") +
+  labs(x = "x", y = "y") +
+  coord_fixed() +
+  theme_bw() -> fig_agg
+
+```
+
+#### Figure 1. 
+Density distributions from which we sample gut retention time (GRT) and movement distance (MD).
+
+```{r fig.width=2.5, fig.height=4}
+plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
+```
+
+#### Figure 2.
+Simulation example where animal movement determines location for seeds dropped.
+Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.
+
+```{r fig.height=2, fig.width=6}
+plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
+```
+
+#### Figure 3.
+Variation in Weibull distributions determined by the value of the shape parameter.
+The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
+
+```{r fig.width=3, fig.height=2.5}
+# shape
+exptail <- 1
+thintail <- 0.2
+fattail <- 2
+
+#scale
+b <- 1
+kappaexp <- b^-exptail
+kappathin <- b^-thintail
+kappafat <- b^-fattail
+
+ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
+                color = "black", linetype = "dashed", size = 0.8) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
+                color = "black", linetype = "dotted", size = 0.8) +
+  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
+                color = "black", linetype = "solid", size = 0.8) +
+  ylab("") + xlab("") +
+  theme_bw()
+
+```
+## Seed dispersal distances and aggregation
+
+```{r fig.width=6}
+bind_rows(null_dispersal %>% mutate(model = "Null"), 
+          indiv_dispersal %>% mutate(model = "Individual"),
+          fam_dispersal %>% mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> dispersal_data
+
+dispersal_data %>% 
+  ggplot(., aes(x = dispersal, group = model)) +
+  facet_wrap(~model, ncol = 3) +
+  geom_histogram(aes(y = ..density..), binwidth = 50) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> histograms
+
+null_dispersion %>% 
+  mutate(model = "Null") %>% 
+  bind_rows(indiv_dispersion %>% 
+              mutate(model = "Individual")) %>% 
+  bind_rows(fam_dispersion %>% 
+              mutate(model = "Family")) %>% 
+  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data
+
+all_disp_data %>% 
+  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
+  geom_boxplot() +
+  theme_bw() +
+  labs(y = "Mean dispersal (m)") +
+  theme(axis.title.x = element_blank()) -> a
+
+all_disp_data %>% 
+  ggplot(., aes(y = seed_dispersion, x = model)) +
+  geom_boxplot() +
+  theme_bw() +
+  labs(y = "Seed dispersion (m)") +
+  theme(axis.title.x = element_blank()) -> b
+
+boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))
+
+plot_grid(histograms, boxplots, nrow=2, labels = c("a", ""))
+
+# Edit redundant labels
+# Fix names for axes
+
+```
+
+## Long distance dispersal
+
+The mean dispersal in the boxplots is not the same as the dispersal distances before.
+This mean dispersal is the distance from the origin to the mean seed location in each simulation run.
+The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
+
+```{r}
+knitr::kable(dispersal_kernel_table %>% 
+               rename(Long_distance = LDD))
+```
+
+## Weibull seed dispersal kernel 
+```{r}
+knitr::kable(weibull_table)
+```

### 2021-01-22 paper/paper.Rmd
remove figures and tables

--- 2021-01-15 paper/paper.Rmd
@@
 
-```{r setup, echo=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
-```
-
-```{r libraries}
-library(ggplot2)
-library(aracari)
-library(cowplot)
-library(dplyr)
-
+```{r setup, include=FALSE}
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
 ```
@@
 
-At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8).
-Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (which varied depending on the underlying model such as the null, individual or family group model) and a random direction from $0^o$ to $360^o$ degrees was used to determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency (*Edit references* Turchin 1998).
-Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape.
+At the beginning of each simulation run, the animal consumed five seeds at the focus tree location, and each of these seeds was assigned a gut retention time sampled from a gamma distribution (shape=4, scale=5, shift=8, Figure 1a).
+Once the animal in the simulation consumed the seeds, a movement distance was sampled from the assigned exponential distribution (Figure 1b), which varied depending on the underlying model such as the null, individual or family group model.
+A random direction from $0^o$ to $360^o$ degrees was used to determine the angle of movement, which with the movement distance would determine the animal's position for the next time step, repeating this process for every time step and thus following an uncorrelated random walk with no directional tendency (*Edit references* Turchin 1998).
+Once the simulation run's time matched the gut retention time for a seed, that seed would get dropped at the animal's location at that specific time point, thus allowing us to record seed location in the landscape (Figure 2a).
 For each of our models we ran 10,000 simulation runs per individual or family group, depending on the model, and collected information on animal and seed locations at every time step.
@@
 -->
-Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 2.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
+Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
 
@@
 # Results
-
-## Seed dispersal distances and long distance dispersal
-
-## Seed dispersion aggregation
-The mean dispersal in the boxplots is not the same as the dispersal distances before.
-This mean dispersal is the distance from the origin to the mean seed location in each simulation run.
-The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
-
-```{r}
-knitr::kable(dispersion_table)
-```
-
-## Weibull seed dispersal kernel
-
-**Table 1.**
-```{r}
-
-knitr::kable(dispersal_kernel_table)
-```
 

### 2021-01-22 paper/dispersal_kernels.R
add pearson's measure of kurtosis

@@ -4,6 +4,7 @@ load("paper/simple_exp_runs.RData")
 
 
 library(fitdistrplus)
+library(moments)
 library(ggplot2)
 library(dplyr)
 
@@ -135,7 +136,6 @@ fam_dispersal %>%
 
 
 
-
 # Table:
 
 dispersal_kernel_table <- data.frame(
@@ -146,6 +146,9 @@ dispersal_kernel_table <- data.frame(
                                " (", signif(sd(indiv_dispersal$dispersal), 2), ")"),
                         paste0(signif(mean(fam_dispersal$dispersal), 4),
                                " (", signif(sd(fam_dispersal$dispersal), 2), ")")),
+  kurtosis = c(signif(kurtosis(null_dispersal$dispersal), 3),
+               signif(kurtosis(indiv_dispersal$dispersal), 3),
+               signif(kurtosis(fam_dispersal$dispersal), 3)),
   Seed.dispersion_sd = c(paste0(signif(mean(null_dispersion$seed_dispersion), 4),
                                 " (", signif(sd(null_dispersion$seed_dispersion), 2), ")"),
                          paste0(signif(mean(indiv_dispersion$seed_dispersion), 4),

### 2021-01-22 paper/paper.Rmd
removed figures and tables
minor progress on methods

@@
 Where the shape parameter $a$ determines the tail of the distribution, and $b$ is the scale parameter.
-It is worth mentioning that the standard parameterization of the Weibull in 'R' is different from the parameterization used in Morales and Carlo  [-@morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$.
+It is worth mentioning that the standard parameterization of the Weibull distribution in 'R' is different from the parameterization used in Morales and Carlo  [-@morales_effects_2006], where the shape parameter $a = \nu$ remains the same, but the scale parameter is defined as $\kappa = b^{-\nu}$, giving a density distribution function of $W(r)= \kappa\nu r^{\nu-1} exp[-{\kappa r}^\nu]$.
 <!-- Here, we report the scale parameter following the alternative parameterization, but the original values returned after fitting the Weibull distribution using R can be found in the Supplementary Table 1.
 -->
-Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit (Supplementary information).
+Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit.
+
+Given our interest in the tail-end of the seed dispersal kernels and our focus on the occurrence of long-distance events, we decided to use an extreme value theory approach and fit a Generalized Pareto distribution to the dispersal distances above the 500m threshold established.
 

### 2021-01-28 paper/paper.Rmd
writing evd methods

@@
 Given our interest in the tail-end of the seed dispersal kernels and our focus on the occurrence of long-distance events, we decided to use an extreme value theory approach and fit a Generalized Pareto distribution to the dispersal distances above the 500m threshold established.
+Statistics of extremes are useful to understand the stochastic behavior of rare extreme events [@coles2001introduction] and have previously been used in ecological scenarios [@gaines1993largest; @katz2005statistics] and evolutionary genetics [@beisel2007testing; @joyce2008general].
+More recently, statistics of extremes have been used to model extended dispersal kernels of seeds and pollen [@garcia_extended_2017] and in particular have been proposed to understand long-distance dispersal events [@rogers_total_2019].
+In our particular case, we were interested to evaluate how an approach using statistics of extremes could help us fit the tail of the frugivore-generated seed dispersal kernels for each of the models we simulated.
+We used a peak over threshold (POT) approach, in which we filtered the dispersal distances above a given threshold and fit a Generalized Pareto (GP) distribution to those values.
+This differs from a block maxima (BM) approach, where the maximum value is selected for each sampling unit and a Generalized Extreme Value (GEV) distribution is used, therefore the choice in the approach is determined by the structure in sampling for a given study (further details can be found in [@coles2001introduction; @garcia_extended_2017]).
 
-Explain what are statistics of extremes and why they can be useful here.
-cite the GArcia 2017 paper, the Gaines and Denny 1993, Katz 2005.
-Coles 2001 for the theory or base knowledge.
-In our case, because we are looking at these simulated seed dispersal kernels, we use a peak over threshold (POT) approach, in which we find the threshold for the data and use an extreme value distribution to fit the tail.
-Describe the math probabilty density functions and the three laws that the extreme value distribution follows. 
-For POT use a generalized pareto distribution.
+<!-- Describe the density functions for both distributions, how they are related and what information is given by their parameters  -->
 
-- Based on Diagnostic plots, we used these values as the threshold for each of the models.
-
-From extRemes package: "where shape = 0 gives rise to the exponential df (light tail), shape > 0 the Pareto df (heavy tail) and shape < 0 the Beta df (bounded upper tail at location - scale.u/shape).
-Theoretical justification supports the use of the GP df family for modeling excesses over a high threshold (i.e., y = x - threshold)."
+Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007].
+However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold.
+We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and probability estimates of long-distance events using our original 500m threshold.
 

### 2021-01-28 paper/paper.Rmd
updated methods

@@
 This differs from a block maxima (BM) approach, where the maximum value is selected for each sampling unit and a Generalized Extreme Value (GEV) distribution is used, therefore the choice in the approach is determined by the structure in sampling for a given study (further details can be found in [@coles2001introduction; @garcia_extended_2017]).
-
-<!-- Describe the density functions for both distributions, how they are related and what information is given by their parameters  -->
+Further details on these two approaches and applications to dispersal can be found [@garcia_extended_2017].
 
@@
 However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold.
-We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and probability estimates of long-distance events using our original 500m threshold.
+We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and expected probability of occurrence of long-distance events using our original 500m threshold.
+We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [Rcit].
 

### 2021-02-01 paper/figures_tables.Rmd
Up to fit of evd to kernel
Up to figure 3 with captions

@@
 library(dplyr)
+library(extRemes)
 
@@
 ```{r}
-load("paper/dispersal_kernels.RData")
+load("paper/fevd.RData")
 ```
@@
 #### Figure 1. 
-Density distributions from which we sample gut retention time (GRT) and movement distance (MD).
+Density distributions from which we sample **A.** gut retention time (GRT) and **B.** movement distance (MD).
+Red dots represent an example for one simulation run, where we sample five gut retention times.
+The maximum GRT for that simulation run determines the number of movement distances sampled in that simulation run, represented in the figure by the black dots.
 
 ```{r fig.width=2.5, fig.height=4}
-plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
+plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)
 ```
@@
 #### Figure 2.
-Simulation example where animal movement determines location for seeds dropped.
-Calculations for seed dispersal distance from the parent tree and seed distance to the mean seed location as a measure of aggregation.
+Example of one simulation run and variables measured for each run.
+**A.** Shows the animal trajectory followed after starting at the origin (big circle at location 0,0).
+The animal moves every minute following the movement distances (MD) sampled from the distribution as show in example of Figure 1.
+Every small black dot represents the animal's location at every minute interval.
+Seeds get dropped every time the simulation reaches one of the sampled gut retention times (GRT), at the animal's location in that time (red dots).
+**B.** Seed dispersal calculations as euclidean distances from the parent plant located at the origin (black circle at 0,0) to each of the five seeds for the simulation run (red dots).
+**C.** Calculation of seed dispersion measures and average seed dispersal.
+The average seed location for the simulation run is shown by the blue circle.
+The distance from each seed to the average location is used to calculate seed dispersion as a measure of seed aggregation, dashed blue lines.
+Average seed dispersal is calculated as the distance from the parent plant to the average seed location, shown as the black line connecting the black circle to the blue dot.
 
 ```{r fig.height=2, fig.width=6}
-plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
+plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)
 ```
@@
 #### Figure 3.
-Variation in Weibull distributions determined by the value of the shape parameter.
-The scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=1$ shows an exponential decay tail, dashed line $a=\nu=0.2$ shows a thin tail, and $a=\nu=2$ describes a fat tail with the dotted line.
+Variation in Weibull and Generalized Pareto distributions determined by the value of the shape parameter.
+**A.** In the case of the Weibull distribution, the scale parameter is defined as $b=1$, and the shape parameters are defined as follows: solid line $a=\nu=0.4$ shows a heavy tail, the dashed line $a=\nu=2$ shows a thin tail, and $a=\nu=1$ describes an exponential tail with the dotted line.
+This follows the assumption that a shape parameter $\nu<1$ describes a fat tail, $\nu>1$ a thin tail, and $\nu=1$ a tail following an exponential distribution.
+*Check here these statements about the tail.
+Maybe parameterization has changed it, but I don't see the heavy tail of the solid line with $\beta > 1$* **B.** In the case of the Generalized Pareto distribution, a shape parameter $=0$ describes an exponential distribution function, shape $>0$ describes a heavy tail, and $<0$ a tail with Beta distribution function, bounded at an upper value as a function of the threshold, shape and scale parameters.
+In the second panel, the scale parameter is set to $\sigma = 1$ the solid line $\xi = 1$ shows a heavy tail, dashed line $\xi=-0.6$ shows a Beta tail, and $\xi = 0$ describes aan exponential decay with the dotted line.
 
-```{r fig.width=3, fig.height=2.5}
+```{r fig.width=6, fig.height=2.5}
 # shape
 exptail <- 1
-thintail <- 0.2
-fattail <- 2
+thintail <- 2
+fattail <- 0.4
 
@@
   ylab("") + xlab("") +
-  theme_bw()
+  lims(y = c(0, 1)) +
+  theme_bw() -> weib_dens
+
+# The shape parameter determines the behavior of the tail of the Generalized Pareto
+# ?extRemes::devd
+# shape = 0 gives rise to exponential disttribution function (thin tail)
+# shape > 0 is a heavy tail
+# shape < 0 is a tail following a Beta distribution function, a bounded upper tail at location-scale.u/shape
+
+# shape
+exptail <- 0
+heavytail <- 1.2
+betatail <- -0.6
+
+# scale
+gp_scale <- 1
+
+ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP"),
+                color = "black", linetype = "dashed", size = 0.8) +
+  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP"), 
+                color = "black", linetype = "dotted", size = 0.8) +
+  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP"),
+                color = "black", linetype = "solid", size = 0.8) +
+  ylab("") + xlab("") +
+  lims(y = c(0, 1)) +
+  theme_bw() -> gp_dens
+
+plot_grid(weib_dens, gp_dens, ncol = 2, labels = "AUTO", label_size = 8)
 
 ```
+
 ## Seed dispersal distances and aggregation
@@
 ```
+
+## Generalized Pareto tail distribution for seed dispersal
+
+```{r}
+knitr::kable(evd_table_500)
+```

### 2021-02-01 paper/figures_tables.Rmd
Methods and figures up to methods are ready!

@@
 This follows the assumption that a shape parameter $\nu<1$ describes a fat tail, $\nu>1$ a thin tail, and $\nu=1$ a tail following an exponential distribution.
-*Check here these statements about the tail.
-Maybe parameterization has changed it, but I don't see the heavy tail of the solid line with $\beta > 1$* **B.** In the case of the Generalized Pareto distribution, a shape parameter $=0$ describes an exponential distribution function, shape $>0$ describes a heavy tail, and $<0$ a tail with Beta distribution function, bounded at an upper value as a function of the threshold, shape and scale parameters.
-In the second panel, the scale parameter is set to $\sigma = 1$ the solid line $\xi = 1$ shows a heavy tail, dashed line $\xi=-0.6$ shows a Beta tail, and $\xi = 0$ describes aan exponential decay with the dotted line.
+**B.** In the case of the Generalized Pareto distribution, a shape parameter $\xi=0$ describes an exponential distribution function, shape $\xi>0$ describes a heavy tail, and $\xi<0$ a tail with Beta distribution function, bounded at an upper value as a function of the threshold and scale parameters.
+In the second panel, the scale parameter is set to $\sigma = 1$ the solid line $\xi = 1$ shows a heavy tail, dashed line $\xi=-0.6$ shows a Beta tail, and $\xi = 0$ describes an exponential decay with the dotted line.
 

### 2021-02-01 paper/paper.Rmd
Methods and figures up to methods are ready!

@@
 -->
-Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu <1$ the tail shows fast-decay, and when $\nu>1$ we can see a fat-tailed distribution (Fig 3.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit.
+Since the shape parameter remains the same, we can note that for $a=\nu=1$ the distribution shows a tail with exponential decay, with values of $\nu > 1$ the tail shows fast-decay or thin tail, and when $\nu<1$ we can see a fat-tailed distribution as shown in [@morales_effects_2006] (Fig 3a.) We visually assessed the fit of the distributions via qqplots and used the Kolmogorov-Smirnov statistic to assess goodness of fit.
 
@@
 This differs from a block maxima (BM) approach, where the maximum value is selected for each sampling unit and a Generalized Extreme Value (GEV) distribution is used, therefore the choice in the approach is determined by the structure in sampling for a given study (further details can be found in [@coles2001introduction; @garcia_extended_2017]).
-Further details on these two approaches and applications to dispersal can be found [@garcia_extended_2017].
+The family of generalized Pareto distributions is [@coles2001introduction]:
+
+$$H(y) = 1 - \left(1 + \frac{\xi y }{\tilde{\sigma}}\right)^{-1/\xi}$$
+
+defined on $\{y : y>0$ and $1 + \xi y/\tilde{\sigma}\}$, where
+$$\tilde{\sigma} = \sigma + \xi(x - \mu)$$
+An approximation between the GEV and GP distributions occurs where the values over a threshold excess (location, $\mu$) have a corresponding approximate GP distribution [@coles2001introduction].
+The parameters in the GP distribution of threshold excesses are determined by the values in the corresponding GEV distribution of a random variable $X$ (scale $\sigma$, location $\mu$).
+In both distributions, the shape parameter $\xi$ is dominant to determine the tail of the distribution.
+In the generalized Pareto distribution, a shape parameter $\xi<0$ the tail has an upper bound at $\mu - \tilde{\sigma}/\xi$ following a Beta distribution function;whereas a shape parameter $\xi>0$ follows a heavy tail with no upper limit.
+In the special case of $\xi = 0$, the GP distribution function approximates to an exponential distribution with a parameter of $1/\tilde{\sigma}$ (Figure 3b.) [@coles2001introduction].
 
@@
 We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and expected probability of occurrence of long-distance events using our original 500m threshold.
-We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [Rcit].
+We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].
 

### 2021-02-02 paper/figures_tables.Rmd
Updates to figures and captions in 4.

@@
 ## Seed dispersal distances and aggregation
+#### Figure 4.
+Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates.
+**A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates.
+Each individual line represents the dispersal kernel generated by each individual animal.
+The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group.
+**B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models.
+**C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models.
+*Is there more comparison I should mention here?
+Like, how the larger values are more abundant in the individual model?*
 
 ```{r fig.width=6}
+
+# Dispersal data for each of the seeds
 bind_rows(null_dispersal %>% mutate(model = "Null"), 
@@
 
+dispersal_data %>% 
+  ggplot(., aes(x = dispersal, group = id)) +
+  facet_wrap(~model, ncol = 3) +
+  geom_density() +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> histograms_by_id
+
+# These measures are by simulation run. So, they are average/mean seed dispersal and seed dispersion. Only one value per simulation run.  
 null_dispersion %>% 
@@
   theme_bw() +
-  labs(y = "Mean dispersal (m)") +
+  labs(y = "Average seed location (m)") +
   theme(axis.title.x = element_blank()) -> a
@@
 
-boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))
+boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("B", "C"))
 
-plot_grid(histograms, boxplots, nrow=2, labels = c("a", ""))
+plot_grid(histograms_by_id, boxplots, nrow=2, labels = c("A", ""))
 

### 2021-02-02 paper/figures_tables.Rmd
supp updates

@@
 library(extRemes)
+library(moments)
+library(fitdistrplus)
 
@@
 ```
+
+## Methods
 
@@
 **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models.
+The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
 *Is there more comparison I should mention here?
@@
 
-The mean dispersal in the boxplots is not the same as the dispersal distances before.
-This mean dispersal is the distance from the origin to the mean seed location in each simulation run.
-The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.
+#### Table 1.
+Summary table of seed dispersal metrics for each of the simulation models.
+Seed dispersal and seed dispersion metrics represent the average value for each of the models, with standard errors in parentheses.
+Kurtosis is calculated for each of the three simulation models as described in the main text.
+Maximum seed dispersal distance represents the longest dispersal distance out of all seeds dispersed for each of the simulation models.
+Long-distance dispersal events are calculated as the percentage of seed dispersal distances greater than 500m for each simulated individual, with standard deviations calculated between the individuals in each simulation model.
 
 ```{r}
-knitr::kable(dispersal_kernel_table %>% 
-               rename(Long_distance = LDD))
+knitr::kable(dispersal_kernel_table)
 ```
@@
 ```
+
+## Supplementary Figures and tables
+
+### Threshold diagnostic plots
+```{r}
+aligned_plots(null_mrl, null_threshplot, orig_thres, title = "Null model")
+aligned_plots(indiv_mrl, indiv_threshplot, orig_thres, title = "Individual model")
+aligned_plots(fam_mrl, fam_threshplot, orig_thres, title = "Family model")
+```

### 2021-02-03 paper/figures_tables.Rmd
include legend to density

@@
 kappafat <- b^-fattail
+# 
+# ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
+#                 color = "black", linetype = "dashed", size = 0.8) +
+#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
+#                 color = "black", linetype = "dotted", size = 0.8) +
+#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
+#                 color = "black", linetype = "solid", size = 0.8) +
+#   ylab("") + xlab("") +
+#   lims(y = c(0, 1)) +
+#   theme_bw() -> weib_dens
 
 ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
-                color = "black", linetype = "dashed", size = 0.8) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
-                color = "black", linetype = "dotted", size = 0.8) +
-  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
-                color = "black", linetype = "solid", size = 0.8) +
+  stat_function(aes(linetype = "Thin tail"), fun = dweibull, n = 100, args = list(scale = b, shape = thintail)) +
+  stat_function(aes(linetype = "Exponential"), fun = dweibull, n = 100, args = list(scale = b, shape = exptail)) +
+  stat_function(aes(linetype = "Heavy tail"), fun = dweibull, n = 100, args = list(scale = b, shape = fattail)) +
   ylab("") + xlab("") +
   lims(y = c(0, 1)) +
-  theme_bw() -> weib_dens
+  theme_bw() +
+  theme(legend.position = c(0.7, 0.7),
+        legend.title = element_blank()) -> weib_dens
 
@@
 
+# ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
+#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP"),
+#                 color = "black", linetype = "dashed", size = 0.8) +
+#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP"), 
+#                 color = "black", linetype = "dotted", size = 0.8) +
+#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP"),
+#                 color = "black", linetype = "solid", size = 0.8) +
+#   ylab("") + xlab("") +
+#   lims(y = c(0, 1)) +
+#   theme_bw() -> gp_dens
+
 ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
-  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP"),
-                color = "black", linetype = "dashed", size = 0.8) +
-  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP"), 
-                color = "black", linetype = "dotted", size = 0.8) +
-  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP"),
-                color = "black", linetype = "solid", size = 0.8) +
+  stat_function(aes(linetype = "Beta"), fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP")) +
+  stat_function(aes(linetype = "Exponential"), fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP")) +
+  stat_function(aes(linetype = "Pareto"), fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP")) +
   ylab("") + xlab("") +
   lims(y = c(0, 1)) +
-  theme_bw() -> gp_dens
+  theme_bw()  +
+  theme(legend.position = c(0.7, 0.7),
+        legend.title = element_blank()) -> gp_dens
 

### 2021-02-03 paper/figures_tables.Rmd
updates

@@
 ```{r fig.width=6, fig.height=2.5}
+
+## 
+# Need to change the order of the lines assigned and the legend
+
+##
 # shape
@@
 
-```{r fig.width=6}
+```{r fig.width=6, fig.height=7}
 
@@
   labs(y = "Density", x = "Seed dispersal (m)") -> histograms_by_id
+
+dispersal_data %>% 
+  ggplot() +
+  geom_density(aes(x = dispersal, group = id), color = "grey") +
+  geom_density(aes(x = dispersal), color = "red") +
+  # stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
+  facet_wrap(~model, ncol = 3) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> dens_by_id
 
@@
 
-plot_grid(histograms_by_id, boxplots, nrow=2, labels = c("A", ""))
+plot_grid(dens_by_id, boxplots, nrow=2, labels = c("A", ""))
 
@@
 # Fix names for axes
+
+```
+
+```{r eval=FALSE}
+
+dispersal_data %>% 
+  filter(., model == "Null") %>% 
+  ggplot() +
+  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
+  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
+  lims(y = c(0, 0.009)) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> a
+
+dispersal_data %>% 
+  filter(., model == "Individual") %>% 
+  ggplot() +
+  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
+  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
+  lims(y = c(0, 0.009)) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> b
+
+dispersal_data %>% 
+  filter(., model == "Family") %>% 
+  ggplot() +
+  geom_density(aes(x = dispersal, group = id), color = "darkgrey") +
+  stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
+  lims(y = c(0, 0.009)) +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(y = "Density", x = "Seed dispersal (m)") -> c
+
+plot_grid(a, b, c)
 
@@
 ## Weibull seed dispersal kernel
+
 ```{r}
@@
 
+## Figures for seed dispersal kernels and comparison to the fit
+Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family.
+The reason for this, is that when you sample seedlings or seed dispersal distances, you don't know which animal moved which, you just get plant level information and distance to the parent tree.
+So, now, we visualize the seed dispersal kernels for each of the three models, without considering the variation contributed to the kernel by each individual.
+
+```{r}
+# Fit to the data?
+
+dispersal_data %>% 
+  ggplot(aes(x = dispersal, linetype = model)) +
+  stat_density(geom = "line", position = "identity") +
+  # geom_function(aes(color = "Null"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
+  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
+  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
+  geom_vline(xintercept = 500, color = "red") +
+  theme_half_open(10) +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  theme(legend.position = c(0.8, 0.8),
+        legend.title = element_blank()) -> dispersal_data_plot
+
+dispersal_data_plot +
+  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
+  #theme_minimal_hgrid(8) +
+  theme(legend.position = "none", 
+        axis.title = element_blank()) -> dispersal_inset
+
+ggdraw() +
+  draw_plot(dispersal_data_plot) +
+  draw_plot(dispersal_inset, x = 0.4, y = 0.35, width = 0.5, height = 0.4) -> plot.with.inset
+
+plot.with.inset
+
+# ggsave(filename = "test.png", 
+#        plot = plot.with.inset,
+#        width = 6, 
+#        height = 4,
+#        units = "in",
+#        dpi = 300)
+
+```
+
+```{r fig.height=9, fig.width=6}
+# Fit to the data?
+
+dispersal_data %>% 
+  filter(., model == "Null") %>% 
+  ggplot(aes(x = dispersal)) +
+  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
+  # geom_function(aes(color = "Individual"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
+  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
+  geom_vline(xintercept = 500, color = "red") +
+  theme_half_open(10) +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  theme(legend.position = c(0.8, 0.8),
+        legend.title = element_blank()) -> A
+
+A +
+  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
+  #theme_minimal_hgrid(8) +
+  theme(legend.position = "none", 
+        axis.title = element_blank()) -> B
+
+ggdraw() +
+  draw_plot(A) +
+  draw_plot(B, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> C
+
+########
+
+dispersal_data %>% 
+  filter(., model == "Individual") %>% 
+  ggplot(aes(x = dispersal)) +
+  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
+   geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
+  # geom_function(aes(color = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
+  geom_vline(xintercept = 500, color = "red") +
+  theme_half_open(10) +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  theme(legend.position = c(0.8, 0.8),
+        legend.title = element_blank()) -> AA
+
+AA +
+  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
+  #theme_minimal_hgrid(8) +
+  theme(legend.position = "none", 
+        axis.title = element_blank()) -> BB
+
+ggdraw() +
+  draw_plot(AA) +
+  draw_plot(BB, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> CC
+
+#########
+
+dispersal_data %>% 
+  filter(., model == "Individual") %>% 
+  ggplot(aes(x = dispersal)) +
+  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
+   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
+  geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
+  geom_vline(xintercept = 500, color = "red") +
+  theme_half_open(10) +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  theme(legend.position = c(0.8, 0.8),
+        legend.title = element_blank()) -> AAA
+
+AAA +
+  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
+  #theme_minimal_hgrid(8) +
+  theme(legend.position = "none", 
+        axis.title = element_blank()) -> BBB
+
+ggdraw() +
+  draw_plot(AAA) +
+  draw_plot(BBB, x = 0.45, y = 0.35, width = 0.5, height = 0.4) -> CCC
+
+plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO")
+
+```
+
 ## Supplementary Figures and tables

### 2021-02-04 paper/resampling_evd_densplots.R
bootstrap plots

@@ -6,212 +6,25 @@ library(cowplot)
 library(extRemes)
 
 
-# just checking:
-
-evd_table
-
-#### THRESHOLD PLOTS
-# NULL
-
-orig_thres <- 500
-nint <- 100
-r <- c(0, 700)
-null_threshplot <- threshrange.plot(null_dispersal$dispersal, r = r, type = "GP", nint = nint)
-null_mrl <- mrlplot(null_dispersal$dispersal, nint = nint)
-
-# threshplot: using extRemes source code
-par(mfrow=c(2,1))
-# r <- quantile(null_dispersal$dispersal, probs=c(0.75,0.99))
-u.i <- matrix(seq(r[1],r[2],, nint), ncol=1)
-out <- null_threshplot
-xlb <- "Threshold"
-yl <- range(c(out[,c("low.t.scale","t.scale","up.t.scale")]), finite=TRUE)
-plot(u.i, out[,"t.scale"], ylim=yl, xlab=xlb, ylab="reparameterized scale", type="b")
-for(j in 1:nint) lines(c(u.i[j],u.i[j]), out[j,c("low.t.scale","up.t.scale")])
-
-yl <- range(c(out[,c("low.shape","shape","up.shape")]), finite=TRUE)
-plot(u.i, out[,"shape"], ylim=yl, xlab="Threshold", ylab="shape", type="b")
-for(j in 1:nint) lines(c(u.i[j],u.i[j]), out[j,c("low.shape","up.shape")])
-
-# ggplot threshold
-as.data.frame(null_threshplot) %>%
-  mutate(u.i = seq(r[1], r[2], length.out = nint)) %>%
-  ggplot(., aes(y = t.scale, x = u.i)) +
-  geom_point(shape = 1, size = 2) +
-  #geom_line(linetype = "dashed") +
-  geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
-  labs(x = "Threshold", y = "Reparameterized \n scale") +
-  theme_bw() +
-  # coord_cartesian(xlim = c(200, 550)) +
-  NULL
-
-as.data.frame(null_threshplot) %>%
-  mutate(u.i = seq(r[1], r[2], length.out = nint)) %>%
-  ggplot(., aes(y = shape, x = u.i)) +
-  geom_point(shape = 1, size = 2) +
-  geom_linerange(aes(x = u.i, ymin = low.shape, ymax = up.shape)) +
[…]

### 2021-02-04 paper/test_thresh_dec.Rmd
Comparing declustering, and orig vs specific thresholds

---
title: "Untitled"
author: "Javiera Rudolph"
date: "2/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r}

load("paper/thresholds.RData")
```

```{r}
library(dplyr)
library(ggplot2)
library(cowplot)
library(extRemes)
```

# NULL

```{r}
orig_thres <- 500

#*****************************************************************************************
# NULL MODEL

# 1. Determine threshold : done in threshold.R script
null_thresh
# 2. Fit Generalized Pareto Distribution

dec_null <- decluster(null_dispersal$dispersal, threshold = null_thresh)
null_fit_dec <- fevd(dec_null, threshold = null_thresh, type = "GP")
plot(null_fit_dec)
summary(null_fit_dec)
ci(null_fit_dec, type = "parameter")

null_fit <- fevd(null_dispersal$dispersal, threshold = null_thresh, type = "GP")
plot(null_fit)
summary(null_fit)
ci(null_fit, type = "parameter")

null_fit_500 <- fevd(null_dispersal$dispersal, threshold = orig_thres, type = "GP")
plot(null_fit_500)
summary(null_fit_500)
ci(null_fit_500, type = "parameter")
```

# INDIVIDUAL

```{r}
indiv_thresh

dec_indiv <- decluster(indiv_dispersal$dispersal, threshold = indiv_thresh)
indiv_fit_dec <- fevd(dec_indiv, threshold = indiv_thresh, type = "GP")
plot(indiv_fit_dec)
summary(indiv_fit_dec)
ci(indiv_fit_dec, type = "parameter")

indiv_fit <- fevd(indiv_dispersal$dispersal, threshold = indiv_thresh, type = "GP")
plot(indiv_fit)
summary(indiv_fit)
ci(indiv_fit, type = "parameter")

indiv_fit_500 <- fevd(indiv_dispersal$dispersal, threshold = orig_thres, type = "GP")
plot(indiv_fit_500)
summary(indiv_fit_500)
ci(indiv_fit_500, type = "parameter")
```

# FAMILY

```{r}
fam_thresh

dec_fam <- decluster(fam_dispersal$dispersal, threshold = fam_thresh)
fam_fit_dec <- fevd(dec_fam, threshold = fam_thresh, type = "GP")
plot(fam_fit_dec)
summary(fam_fit_dec)
ci(fam_fit_dec, type = "parameter")

fam_fit <- fevd(fam_dispersal$dispersal, threshold = fam_thresh, type = "GP")
plot(fam_fit)
summary(fam_fit)
ci(fam_fit, type = "parameter")

fam_fit_500 <- fevd(fam_dispersal$dispersal, threshold = orig_thres, type = "GP")
plot(fam_fit_500)
summary(fam_fit_500)
ci(fam_fit_500, type = "parameter")
```

### 2021-02-04 paper/thresholds.R
changed threshold

@@ -132,14 +132,14 @@ aligned_plots <- function(mrl_data, thresh_data, threshold, title = NULL){
 }
 
 # Null
-null_thresh <- round(null_mrl$u.i_mrl[20])
+null_thresh <- round(null_mrl$u.i_mrl[15])
 mrl_plot(null_mrl, title = "Null model mean excess plot") +
   coord_equal() +
   geom_vline(xintercept = null_thresh, color = "red", linetype = "dashed")
 threshplot_fx(null_threshplot, null_thresh, title = "Null model threshold plots")
 
 # Indiv
-indiv_thresh <- round(indiv_mrl$u.i_mrl[16])
+indiv_thresh <- round(indiv_mrl$u.i_mrl[15])
 mrl_plot(indiv_mrl) +
   coord_equal()+
   geom_vline(xintercept = indiv_thresh, color = "red", linetype = "dotted")
@@ -147,7 +147,7 @@ threshplot_fx(indiv_threshplot, indiv_thresh, title = "Individual model threshol
 
 
 # Fam
-fam_thresh <- round(fam_mrl$u.i_mrl[17])
+fam_thresh <- round(fam_mrl$u.i_mrl[15])
 mrl_plot(fam_mrl) +
   coord_equal()+
   geom_vline(xintercept = fam_thresh, color = "red", linetype = "dotted")

### 2021-02-04 paper/figures_tables.Rmd
minor changes

@@
 
-```{r fig.width=6, fig.height=7}
+```{r fig.width=6, fig.height=6}
 
@@
   ggplot() +
-  geom_density(aes(x = dispersal, group = id), color = "grey") +
-  geom_density(aes(x = dispersal), color = "red") +
+  geom_density(aes(x = dispersal, group = id), color = "grey70") +
+  geom_density(aes(x = dispersal), color = "black") +
   # stat_density(aes(x = dispersal), geom = "line", position = "identity", color = "red") +
@@
 ## Generalized Pareto tail distribution for seed dispersal
+Actually, do use the thresholds from the diagnostic plots. These are the parameters with those thresholds.
 
 ```{r}
-knitr::kable(evd_table_500)
+
+knitr::kable(bind_rows(evd_table %>% 
+  mutate(Threshold = c(null_thresh, indiv_thresh, fam_thresh))))
+
 ```
@@
   ggplot(aes(x = dispersal)) +
-  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  stat_density(aes(linetype = "Null data"), geom = "line", position = "identity") +
   geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
@@
   geom_vline(xintercept = 500, color = "red") +
+  lims(x = c(0, 1500)) +
   theme_half_open(10) +
@@
   ggplot(aes(x = dispersal)) +
-  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  stat_density(aes(linetype = "Individual data"), geom = "line", position = "identity") +
   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
@@
   ggplot(aes(x = dispersal)) +
-  stat_density(aes(linetype = "Simulated data"), geom = "line", position = "identity") +
+  stat_density(aes(linetype = "Family data"), geom = "line", position = "identity") +
   # geom_function(aes(linetype = "Weibull Kernel"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
@@
 
-plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO")
+plot_grid(C, CC, CCC, nrow = 3, labels = "AUTO") -> D
+
+ggsave("paper/test.png",
+       D,
+       width = 6,
+       height = 9,
+       dpi = 300)
 
@@
 ```{r}
-aligned_plots(null_mrl, null_threshplot, orig_thres, title = "Null model")
-aligned_plots(indiv_mrl, indiv_threshplot, orig_thres, title = "Individual model")
-aligned_plots(fam_mrl, fam_threshplot, orig_thres, title = "Family model")
+
+threshplot_fx <- function(thresh_data, th, title = NULL){
+
+  thresh_data %>%
+    ggplot(., aes(y = t.scale, x = u.i)) +
+    geom_point(shape = 1, size = 2) +
+    # geom_line(linetype = "dashed") +
+    geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
+    labs(title = title, x = "Threshold", y = "Scale") +
+    theme_bw() +
+    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
+    geom_vline(xintercept = 500, color = "black", linetype = "dashed") +
+    scale_x_continuous(limits = c(0, 700), n.breaks = 7 ) +
+    # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
+    # theme(axis.title.x = element_blank(),
+    #       axis.ticks.x = element_blank(),
+    #       axis.text.x = element_blank()) +
+    # coord_cartesian(xlim = c(200, 550)) +
+    NULL -> thresh_scale
+
+  thresh_data %>%
+    ggplot(., aes(y = shape, x = u.i)) +
+    geom_point(shape = 1, size = 2) +
+    geom_linerange(aes(x = u.i, ymin = low.shape, ymax = up.shape)) +
+    labs(x = "Threshold", y = "Shape") +
+    theme_bw() +
+    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
+    geom_vline(xintercept = 500, color = "black", linetype = "dashed") +
+    scale_x_continuous(limits = c(0, 700), n.breaks = 7 ) +
+    # coord_cartesian(xlim = c(200, 550)) +
+    NULL -> thresh_shape
+
+  plot_grid(thresh_scale, thresh_shape, nrow = 2)
+
+}
+
+mrl_plot <- function(mrl_data, title = NULL){
+
+  mrl_data %>%
+    ggplot(., aes(x = u.i_mrl, y = `Mean Excess`)) +
+    geom_line() +
+    geom_line(aes(y = `95% lower`), linetype = "dashed", color = "black") +
+    geom_line(aes(y = `95% upper`), linetype = "dashed", color = "black") +
+    labs(title = title, x = "Threshold values") +
+    scale_x_continuous(n.breaks = ceiling(round(max(mrl_data$u.i_mrl))/100)) +
+    theme_bw()
+}
+aligned_plots <- function(mrl_data, thresh_data, threshold, title = NULL){
+  title <- ggdraw() +
+    draw_label(
+      title,
+      fontface = 'bold',
+      x = 0,
+      hjust = 0
+    ) +
+    theme(
+      # add margin on the left of the drawing canvas,
+      # so title is aligned with left edge of first plot
+      plot.margin = margin(0, 0, 0, 7)
+    )
+
+  plot_grid(mrl_plot(mrl_data) +
+              #coord_equal() +
+              geom_vline(xintercept = threshold, color = "red", linetype = "dashed") +
+              geom_vline(xintercept = 500, color = "black", linetype = "dashed"),
+            threshplot_fx(thresh_data, threshold),
+            nrow = 2,
+            rel_heights = c(2,3),
+            labels = "auto") -> actual_plots
+
+  plot_grid(title,
+            actual_plots,
+            ncol = 1,
+            rel_heights = c(0.1,1))
+}
+
+# Null
+null_thresh <- round(null_mrl$u.i_mrl[15])
+
+# Indiv
+indiv_thresh <- round(indiv_mrl$u.i_mrl[15])
+
+# Fam
+fam_thresh <- round(fam_mrl$u.i_mrl[15])
+
+aligned_plots(null_mrl, null_threshplot, null_thresh, title = "Null model")
+aligned_plots(indiv_mrl, indiv_threshplot, indiv_thresh, title = "Individual model")
+aligned_plots(fam_mrl, fam_threshplot, fam_thresh, title = "Family model")
 ```

### 2021-02-04 paper/figures_tables.Rmd
update with GP tails

@@
 
+```{r, fig.width=6, fig.height=3}
+ggplot(data = data.frame(x = c(160, 1000)), aes(x)) +
+  stat_function(aes(linetype = "Null"), fun = devd, args = list(scale = null_ci[1,2], shape = null_ci[2,2], type = "GP")) +
+  stat_function(aes(linetype = "Individual"), fun = devd, args = list(scale = indiv_ci[1,2], shape = indiv_ci[2,2], type = "GP")) +
+  stat_function(aes(linetype = "Family"), fun = devd, args = list(scale = fam_ci[1,2], shape = fam_ci[2,2], type = "GP")) +
+  ylab("Density") + xlab("Distance (m)") +
+  theme_bw()  +
+  theme(legend.position = c(0.7, 0.7),
+        legend.title = element_blank())
+```
+
 ## Figures for seed dispersal kernels and comparison to the fit
@@
 
-ggsave("paper/test.png",
-       D,
-       width = 6,
-       height = 9,
-       dpi = 300)
+# ggsave("paper/test.png",
+#        D,
+#        width = 6,
+#        height = 9,
+#        dpi = 300)
+
+D
 

### 2021-02-04 paper/resampling_evd_densplots.R
GP tails

@@ -116,6 +116,15 @@ plot_grid(null_boot_plot,
           fam_boot_plot,
           nrow = 3)
 
+ggplot(data = data.frame(x = c(160, 1000)), aes(x)) +
+  stat_function(aes(linetype = "Null"), fun = devd, args = list(scale = null_ci[1,2], shape = null_ci[2,2], type = "GP")) +
+  stat_function(aes(linetype = "Individual"), fun = devd, args = list(scale = indiv_ci[1,2], shape = indiv_ci[2,2], type = "GP")) +
+  stat_function(aes(linetype = "Family"), fun = devd, args = list(scale = fam_ci[1,2], shape = fam_ci[2,2], type = "GP")) +
+  ylab("Density") + xlab("Distance (m)") +
+  theme_bw()  +
+  theme(legend.position = c(0.7, 0.7),
+        legend.title = element_blank())
+
 
 # 4. Calculate probability of getting those LDD events
 #   a. make a figure with probability on the y axis, and distance in the x.

### 2021-02-05 paper/figures_tables.Rmd
add table of conditional probabilities for evd

@@
 ```{r}
-load("paper/fevd.RData")
+load("paper/resampling_evd_densplots.RData")
 ```
@@
 
+```{r eval=FALSE, fig.width=6, fig.height=9}
+
+plot_grid(null_boot_plot,
+          indiv_boot_plot,
+          fam_boot_plot,
+          nrow = 3)
+```
+
+### Probabilities
+
+```{r}
+dist_range <- c(250, 500, 1000, 1250, 1500, 1750, 2000)
+null_probs <- pextRemes(null_fit, dist_range, lower.tail = FALSE)
+indiv_probs <- pextRemes(indiv_fit, dist_range, lower.tail = FALSE)
+fam_probs <- pextRemes(fam_fit, dist_range, lower.tail = FALSE)
+
+evd_probs <- as.data.frame(rbind(null_probs, indiv_probs, fam_probs))
+names(evd_probs) <- dist_range
+row.names(evd_probs) <- c("Null", "Individual", "Family")
+
+knitr::kable(evd_probs)
+```
+
 ## Figures for seed dispersal kernels and comparison to the fit

### 2021-02-05 paper/resampling_evd_densplots.R

@@ -4,7 +4,7 @@ library(dplyr)
 library(ggplot2)
 library(cowplot)
 library(extRemes)
-
+library(Rmisc)
 
 #*****************************************************************************************
 
@@ -40,6 +40,16 @@ for(i in 1:1000){
 null_lines <- purrr::map(seq(1:1000), function(y)
   stat_function(fun = devd, args = list(type = "GP",
                                         scale = null_boot$scale[y], shape = null_boot$shape[y]), color = "grey"))
+
+# ggplot(data = data.frame(x = c(null_thresh, 1000)), aes(x)) +
+#   null_lines +
+#   stat_function(aes(linetype = "CI"), fun = devd, args = list(scale = CI(null_boot$scale)[1], shape = CI(null_boot$shape)[1], type = "GP")) +
+#   stat_function(aes(linetype = "Model"), fun = devd, args = list(scale = null_scale, shape = null_shape, type = "GP")) +
+#   stat_function(aes(linetype = "CI"), fun = devd, args = list(scale = CI(null_boot$scale)[3], shape = CI(null_boot$shape)[3], type = "GP")) +
+#   ylab("Density") + xlab("Distance (m)") +
+#   theme_bw()  +
+#   theme(legend.position = c(0.7, 0.7),
+#         legend.title = element_blank()) -> null_boot_plot
 
 ggplot(data = data.frame(x = c(null_thresh, 1000)), aes(x)) +
   null_lines +
@@ -116,6 +126,11 @@ plot_grid(null_boot_plot,
           fam_boot_plot,
           nrow = 3)
 
+# The confidence intervals are for the bootstrapped data, not for the MLE estimate
+# Figure out how to do that.
+
+
+
 ggplot(data = data.frame(x = c(160, 1000)), aes(x)) +
   stat_function(aes(linetype = "Null"), fun = devd, args = list(scale = null_ci[1,2], shape = null_ci[2,2], type = "GP")) +
   stat_function(aes(linetype = "Individual"), fun = devd, args = list(scale = indiv_ci[1,2], shape = indiv_ci[2,2], type = "GP")) +
@@ -129,8 +144,13 @@ ggplot(data = data.frame(x = c(160, 1000)), aes(x)) +
 # 4. Calculate probability of getting those LDD events
 #   a. make a figure with probability on the y axis, and distance in the x.
 
-dist_range <- seq(null_thresh, 4000, by = 100)
[…]

### 2021-02-05 paper/paper.Rmd
methods done with thresholds from diagnostic pltos

@@
 However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold.
-We performed these analysis (Supplementary information), and given that parameter estimates were similar, we report our parameter estimates and expected probability of occurrence of long-distance events using our original 500m threshold.
+We performed these analysis and we report our parameter estimates and expected probability of occurrence of long-distance events using the thresholds from diagnostics plots.
 We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].

### 2021-02-08 paper/paper.Rmd
Adding results

@@
 In both distributions, the shape parameter $\xi$ is dominant to determine the tail of the distribution.
-In the generalized Pareto distribution, a shape parameter $\xi<0$ the tail has an upper bound at $\mu - \tilde{\sigma}/\xi$ following a Beta distribution function;whereas a shape parameter $\xi>0$ follows a heavy tail with no upper limit.
+In the generalized Pareto distribution, a shape parameter $\xi<0$ the tail has an upper bound at $\mu - \tilde{\sigma}/\xi$ following a Beta distribution function, whereas a shape parameter $\xi>0$ follows a heavy tail with no upper limit.
 In the special case of $\xi = 0$, the GP distribution function approximates to an exponential distribution with a parameter of $1/\tilde{\sigma}$ (Figure 3b.) [@coles2001introduction].
+The focus on these shape parameters, both in the case of the Generalized Pareto and the Weibull distribution, is due to the interest in long-distance dispersal events, and using these parameters as a comparisson between dispersal kernels allows us to compare which kernels have higher probabilities for long-distance dispersal events.
 
-Our study focused on long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007].
-However, when selecting a threshold for a POT approach, it is also possible to use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold.
-We performed these analysis and we report our parameter estimates and expected probability of occurrence of long-distance events using the thresholds from diagnostics plots.
+Initially, we defined long-distance dispersal events defined as any dispersal event over 500m from the parent tree in order to compare our results to previous studies in this same ecological system [@holbrook_dispersal_2009; @holbrook_home_2011; @holbrook_using_2007].
+We used this threshold to assess the percentage of LDD events reported in table 1.
+However, when selecting a threshold for a POT approach, using a generalized Pareto distribution, we can use diagnostic plots by fitting the data to a sequence of thresholds, with the goal of finding the lowest threshold that provides similar parameter values to any other higher threshold.
+We performed these analysis and we report our parameter estimates for the generalized Pareto and expected conditional probabilities of long-distance dispersal events using the thresholds from diagnostics plots.
 We fit Generalized Pareto distributions to the data via maximum likelihood using the package extRemes [@extRemes2] in R [@Rcit].
@@
 # Results
+
+## Simulation of seed dispersal distances under the three movement models
+We generated seed dispersal distances from combining animal movement and seed gut retention time.
+The three models we used to simulate the dispersal distances differ in their approach to characterize variation between the animals dispersing seeds.
+In the case of our null model, where each animal's step length is sampled from an exponential distribution with the same rate parameter, we would expect to find no differences between the dispersal kernels generated by each of the animals.
+On the contrary, for the case of simulation models that include individual and family level variation in animal movement, we expected the seed dispersal kernels generated by each individual to show variation.
+Indeed, Figure 4A shows that individual and family level simulation models show different seed dispersal kernels for each individual bird, whereas in the null model, individual seed dispersal kernels actually overlap with the average dispersal kernel (black line).
+We generated the average seed dispersal kernels (black lines in Figure 4A) for each of the simulation models by taking all of the seed dispersal distances from the simulation.
+We did this as in the field we can perform maternity analysis to know seed origin, but it is more complicated to know which specific animal dispersed each seed.
+Therefore, the average seed dispersal kernels would better reflect the type of data we would collect from field surveys of seed dispersal.
+From now on, we refer to each of these average seed dispersal kernels as the kernel generated by each of the three simulation models: null kernel, individual kernel, and family kernel.
 

### 2021-02-08 paper/figures_tables.Rmd
Edits to captions

@@
 
-## Seed dispersal distances and aggregation
+## Results
 #### Figure 4.
@@
 
-## Long distance dispersal
-
 #### Table 1.
@@
 
-## Weibull seed dispersal kernel
+### Weibull seed dispersal kernel
+
+#### Table 2.
+Parameter estimates for seed dispersal kernels on each of the simulation models using a Weibull distribution to characterize the kernel.
+Parameter values are reported with their standard deviations in parentheses.
 
@@
 
+#### Figure 5.
+Kernels produced from Weibull functions using the estimated parameters for each of the simulated models.
+Inset shows a zoom to the tail of the distribution emphasizing the variation in long-distance dispersal events described by each of the models.
+Red line is used for reference as the original 500m threshold to describe long-distance dispersal events in previous studies.
+We observe fatter tails for the model with individual variation in animal movement, followed by family level variation, and a thinner tail for the null simulation model with no variation in animal movement.
+
+```{r}
+dispersal_data %>% 
+  ggplot(aes(x = dispersal)) +
+  # stat_density(aes(linetype = model), geom = "line", position = "identity") +
+  geom_function(aes(linetype = "Null"), fun = dweibull, args = list(shape = null_weibull$estimate[1], scale = null_weibull$estimate[2])) +
+  geom_function(aes(linetype = "Individual"),
+                fun = dweibull, args = list(shape = indiv_weibull$estimate[1], scale = indiv_weibull$estimate[2])) +
+  geom_function(aes(linetype = "Family"), fun = dweibull, args = list(shape = fam_weibull$estimate[1], scale = fam_weibull$estimate[2])) +
+  geom_vline(xintercept = 500, color = "red") +
+  theme_half_open(10) +
+  labs(y = "Density", x = "Seed dispersal (m)") +
+  theme(legend.position = c(0.8, 0.8),
+        legend.title = element_blank()) -> dispersal_data_plot
+
+dispersal_data_plot +
+  coord_cartesian(xlim = c(495, 1000), ylim = c(0, 3e-4)) +
+  #theme_minimal_hgrid(8) +
+  theme(legend.position = "none", 
+        axis.title = element_blank()) -> dispersal_inset
+
+ggdraw() +
+  draw_plot(dispersal_data_plot) +
+  draw_plot(dispersal_inset, x = 0.4, y = 0.35, width = 0.5, height = 0.4) -> plot.with.inset
+
+plot.with.inset
+```
+
 ## Generalized Pareto tail distribution for seed dispersal
-Actually, do use the thresholds from the diagnostic plots. These are the parameters with those thresholds.
+
+#### Table 3. Threshold values and parameter estimates for generalized Pareto distribution fits, and associated standard error for parameter estimates.
 
@@
 ```
+
+#### Figure 6.
 
@@
 
-### Probabilities
+#### Table 4. Probability of long-distance dispersal events for the three models following a generalized Pareto distribution.
 
@@
 
-## Figures for seed dispersal kernels and comparison to the fit
-Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family.
+<!-- ## Figures for seed dispersal kernels and comparison to the fit -->
+<!-- Now, we focus on the seed dispersal kernel as a whole for each simulated model: Null, Individual, Family.
 The reason for this, is that when you sample seedlings or seed dispersal distances, you don't know which animal moved which, you just get plant level information and distance to the parent tree.
 So, now, we visualize the seed dispersal kernels for each of the three models, without considering the variation contributed to the kernel by each individual.
+-->
 
-```{r}
+```{r eval = FALSE}
 # Fit to the data?
@@
 
-```{r fig.height=9, fig.width=6}
+```{r eval=FALSE, fig.height=9, fig.width=6}
 # Fit to the data?
@@
 
+### Variation in kernels produced by individual birds in each of the three models
+
+```{r}
+dispersal_data %>% 
+  dplyr::filter(model == "Null") %>% 
+  ggplot(., aes(x = dispersal)) +
+  facet_wrap(~id) +
+  geom_density() +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(title = "Null simulation model", y = "Density", x = "Seed dispersal (m)")
+
+dispersal_data %>% 
+  dplyr::filter(model == "Individual") %>% 
+  ggplot(., aes(x = dispersal)) +
+  facet_wrap(~id) +
+  geom_density() +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(title = "Individual simulation model", y = "Density", x = "Seed dispersal (m)")
+
+dispersal_data %>% 
+  dplyr::filter(model == "Family") %>% 
+  ggplot(., aes(x = dispersal)) +
+  facet_wrap(~id) +
+  geom_density() +
+  theme_bw() +
+  theme(strip.background = element_rect(fill = "white")) +
+  labs(title = "Family simulation model", y = "Density", x = "Seed dispersal (m)")
+
+```
+
 ### Threshold diagnostic plots

### 2021-02-08 paper/paper.Rmd
Added results

@@
 
+Average seed locations provided a metric for seed dispersal in each simulation run, and seed dispersion shows how far apart each of the seeds are from each other in every simulation run.
+We show average seed locations and seed dispersion for the three models (Figure 4B-C) and although the average measures for these are comparable between models, location and dispersion have a greater number of outliers in the indvidual and family models.
+This suggests that although the average measures are similar between models, the variation between them is different, with the individual and family models showing both a greater maximum dispersal distance, and a higher percentage of long-distance dispersal events (Table 1.) Interestingly, the higher percentage of LDD events in the individual kernels also has a higher standard deviation, a result of the variation in the dispersal kernels produced by each bird (Figure 4A), where some birds or social groups where characteristically long-dispersers versus individuals with shorter dispersal distances and even one individual for which simulated seed dispersal distances were all below 500m (Supplementary information).
+
+## Kernel functions for frugivore-generated dispersal distances
+
+For the seed dispersal data generated from each of the three simulation models, we fit a Weibull distribution function and estimated the parameters for each of the models (Table 2).
+The shape parameters provided information on the fatness of the tails, as previously mentioned in the methods section above.
+Although all three models have shape parameters $>1$, describing thin tails, we find that there are differences between the three simulation models, with the null model having the largest shape parameter value and thus showing the thinnest tail among the three models (Figure 5).
+The individual model shows the smallest shape parameter value, and thus describing the dispersal kernel with the heaviest tail among the three models.
+
+Given our interest in long-distance dispersal events and the potential to use statistics of extremes in seed dispersal ecology, we fit the data of the three simulated models to a generalized Pareto distribution following a peak-over-threshold approach.
+Using this approach, we also performed analysis with threshold diagnostic plots and mean residual life plots (Supplementary information) to estimate the best thresholds for our data.
+These type of diagnostic approach helps us identify the distances above which we can consider seed dispersal events as long-distance dispersal.
+We report these threshold values, and parameter estimates (Table 3.) showing that all three dispersal kernels have shape parameter values $<0$ thus corresponding to thin tails, following a Beta distribution with an upper limit.
+Although the parameter estimates are close and they show thin tail for all three models, the generalized Pareto fit shows a similar trend as that in the Weibull kernels, with the individual model showing a fatter tail, followed by the family model, and the null model with the thinnest tail (Figure 6).
+Using these parameter values, we calculated the probabilities of long-distance dispersal events at different distances from the parent tree (Table 4), ranging from 250 to 2000m over the threshold.
+Although these are very low probabilities, it is worth noting that the parameters associated with the null model reach a zero probability of dispersal for seeds beyond 1250m conditional on the null threshold, whereas the individual level model has probabilites greater than zero for dispersal events of 1750m beyond the threshold ($P(X=1750) = 2e^-7$).
+All three models had a probability of zero for dispersal events greater than 2000 meters beyond the LDD threshold.
+
 ## Extreme distributions to fit dispersal

### 2021-02-08 paper/paper.Rmd
delete comments

@@
 
-## Extreme distributions to fit dispersal
-
-Explain what are statistics of extremes and why they can be useful here.
-cite the GArcia 2017 paper, the Gaines and Denny 1993, Katz 2005.
-Coles 2001 for the theory or base knowledge.
-In our case, because we are looking at these simulated seed dispersal kernels, we use a peak over threshold (POT) approach, in which we find the threshold for the data and use an extreme value distribution to fit the tail.
-Describe the math probabilty density functions and the three laws that the extreme value distribution follows. 
-For POT use a generalized pareto distribution.
-
-- Based on Diagnostic plots, we used these values as the threshold for each of the models.
-
-From extRemes package: "where shape = 0 gives rise to the exponential df (light tail), shape > 0 the Pareto df (heavy tail) and shape < 0 the Beta df (bounded upper tail at location - scale.u/shape).
-Theoretical justification supports the use of the GP df family for modeling excesses over a high threshold (i.e., y = x - threshold)."
-
 # Discussion

### 2021-02-09 paper/paper.Rmd
discussion

@@
 Revisit at the end...Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms.
-In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion.
-Animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds with them.
+In the case of frugivore-generated seed dispersal patterns, a large influence is observed by animal movement patterns, and intraspecific variation in animal movement and behaviors can result in interesting seed dispersal patterns.
+In particular, long-distance seed dispersal (LDD) plays a significant role in determining a population's genetic diversity and range expansion and animal-mediated seed dispersal is a key component of LDD events, as frugivores can travel long distances and transport seeds with them.
 In this study we seek to understand the implications of individual variation in animal movement and how these can impact estimates of long distance seed dispersal.
 We apply these methods to empirical data sets that contain locations for an araçari, *Pteroglossus pluricintus*, one of the primary frugivores for the Amazonian canopy tree *Virola flexuosa*.
-We combine animal movement data and gut retention time to simulate *Virola* seed dispersal.
-This approach showed that there is significant variation in individual araçari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds.
+We combine animal movement data and gut retention time to simulate *Virola* seed dispersal with an individual-based model on a homogeneous landscape.
+This approach showed that there is significant variation in individual araçari movement patterns which directly influence the estimated number of long-distance dispersal events for *Virola* seeds and estimates for seed dispersal kernel functions.
+Additionally, we include an approach using statistics of extremes to characterize the tail behavior of generated seed dispersal kernels under varying levels of intraspecific variation of animal movement.
 We found that models that ignore this underlying variation in individual animal movement, underestimate the percentage of long-distance seed dispersal events and maximum seed dispersal distances.
 output:
+  html_document:
+    df_print: paged
   word_document:
     reference_docx: paper_ref.docx
-  html_document:
-    df_print: paged
 bibliography: mybibfile.bib
@@
 
-Even though LDD events are rare or infrequent, they have a disproportionately large effect on gene flow and the genetic pool of populations (Jordano 2017).
-In the case of well mixed populations, long-distance dispersal can cause random genetic loss through drift or have the opposite effect and maintain high genetic variance in populations that initially drifted (Bohrer, Nathan, and Volis 2005).
+Frugivore-generated seed dispersal kernels have been used to estimate seed dispersal distances in multiple studies [@jones_closing_2017; @levey_effects_2005; @levey_modelling_2008; @russo_incorporating_2006; @will_mechanistic_2008], often with the goal of understanding how incorporating animal movement and behavior will impact seed dispersal distances.
+Usually, the focus tends to be on seed dispersal and how spatial patterns of seed aggregation can change in response to animal behavior or landscape heterogeneity.
+However, fewer studies have emphasized the role of intraspecific variation in animal movement over generated seed dispersal patterns, or even the relative importance that different disperser species may have in carrying seeds and contributing to seed dispersal [@rehm_differences_2018; @zwolak_how_2018].
+Extending on the concept of the total dispersal kernel, where we seek to understand and characterize all the different components contributing to a specific parent tree or plant species dispersal kernel, greater emphasis has been given to the role of disperser species and abiotic processes that may influence a total dispersal kernel [@rogers_total_2019].
+However, we show that individual variation in animal movement within a single species can also influence a plant's seed dispersal kernel, specifically in a system of toucan-generated seed dispersal kernels.
+In our particular case, the variation introduced in animal movement patterns included variation at the level of individual animals and variation between family groups.
+Given that *Pteroglossus pluricinctus* maintain cooperative social groups and previous studies showed overlapping home ranges between individuals belonging to the same social group [@holbrook_home_2011], we wanted to explore how variation in movement between social groups could alter the simulated dispersal kernels.
+We found that incorporating heterogeneity in animal movement produced seed dispersal kernels with fatter tails, longer dispersal distances, and a higher percentage of long-distance dispersal events compared to null models where no animal movement heterogeneity is included.
+
+Even though long-distance dispersal events are rare or infrequent, they have a disproportionately large effect on gene flow and the genetic pool of populations [@jordano_what_2017].
+In the case of well mixed populations, long-distance dispersal can cause random genetic loss through drift or have the opposite effect and maintain high genetic variance in populations that initially drifted [@bohrer2005effects].
 This is important as in the long-term, these genetic consequences of dispersal can have significant effects for the survival of populations.
@@
 It is of special interest to focus in highly heterogenous habitats with rapid change in spatial structure where local extinctions are high, since long-distance dispersal can allow persistence of a metapopulation with immigration and emigration based on long distance dispersal.
-From a more evolutionary perspective, long-distance dispersal can allow for a species to colonize distant habitats and expand its range, which can also lead to differentiation and speciation (Ronce 2007).
+From an evolutionary perspective, long-distance dispersal can allow for a species to colonize distant habitats and expand its range [@jordano_what_2017].
 We have shown that individual differences in frugivore movement can have significant consequences on the number of long-distance seed dispersal events and it remains to be explored how these individual differences can influence population dynamics in the long term and at larger spatial scales.
+We also show that the approach using statistics of extremes allows us to estimate the probability of dispersal for distances beyond those directly observed in our simulated dispersal kernels, and that simulation models including individual variation in animal movement have higher probabilities for these events.
+Our simulated dispersal distances had a maximum of over 1500 meters under the model with individual variation, an estimate that is not unreasonable for this system, and that actually underestimates previous estimates [@holbrook_using_2007].
+Parameters estimated for generalized Pareto functions fitted to our frugivore-generated seed dispersal distances showed shape parameters $<0$ pointing towards thin tails constrained by upper bounds.
+Although we observed differences between the kernels fitted to the three simulation models, all of them still presented parameter values smaller than zero, and thus showing thin tails.
+Nonetheless, using an approach of statistics of extremes proved to be valuable in selecting seed dispersal thresholds for considering long-distance dispersal events and carrying out analyses focused on the tail of dispersal kernels, whether that is for seeds or pollen [@garcia_extended_2017].
 
-# Conclusion
+The thing tails estimated by seed dispersal kernel functions can be in part due to the fact that we used a very simple animal movement model incorporating only step lengths and turning angles.
+Step lengths for all simulation models we randomly drawn from exponential distributions, with varying rate parameters depending on the model.
+Using an exponential distribution and a simple movement model such as this one can certainly limit the extent to which an animal can move and thus have an upper bound on seed dispersal distances, something we observe not only on fits with the generalized Pareto, but also with the Weibull dispersal kernels.
+Previous studies looking at a mechanistic understanding of seed dispersal by frugivores have modeled animal movement with approaches similar to this one, varying step lengths to constants or switching to a lognormal distribution [@jones_closing_2017; @levey_effects_2005; @will_mechanistic_2008], or other incorporating more complex animal movement models with diffusion processes[@morales_effects_2006; @pegman_exploring_2017].
+There has been emphasis on adding different animal behaviors into mechanistic models of seed dispersal, such as perching or sleeping[@jones_closing_2017; @russo_incorporating_2006], however a focus on individual animal movement is still not coomon.
+Incorporating individual variation in animal movement models is an active area in the movement ecology field, with various approaches being developed to incorporate this heterogeneity in hierarchical frameworks [@bastille-rousseau_flexible_2016; @borger2012quantifying].
+Future directions for this work should focus on taking a step back from seed dispersal, and first characterizing the differences in individual animal movement patterns, since as we observed from our results, individuals generate a wide range of seed dispersal kernels based on their individual movements.
+In the present study we only focused on using movement rates for each indvidual bird, an average measure of their movement, and thus it is likely that we are also underestimating the frequency of long-distance movements in frugivores.
+This presents a novel opportunity to also incorporate statistics of extremes for rare long-distance animal movements.
+Previous work has shown that maximum travel distances for *Pteroglossus pluricinctus* can reach up to 3665 meters in a 30 minute tracking interval [@holbrook_home_2011], estimates that our movement simulations were not able to capture, and thus underestimate how far animals and seeds can travel.
+In addition to this, our simulations also assume equal contributions of seed dispersal by each individual, when in reality we understand that not all dispersers are the same, with some distributing larger numbers of seeds depending on their breeding status, age or size [don't have a citation for this].
+Future research focusing on animal movement models and seed dispersal would also greatly benefit from understanding the relative contributions of individual dispersers to overall seed dispersal kernels.
 

### 2021-02-11 paper/paper.Rmd
Up0dated abstract

@@
 abstract: |
-  I don't like this abstract.
-Revisit at the end...Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms.
+  Seed dispersal is a fundamental process in plant ecology and due to its high importance in the ecosystem, various modelling approaches have been developed to understand seed movement and dispersal mechanisms.
 In the case of frugivore-generated seed dispersal patterns, a large influence is observed by animal movement patterns, and intraspecific variation in animal movement and behaviors can result in interesting seed dispersal patterns.

### 2021-02-11 paper/figures_tables.Rmd
Finished figures in docx fortmat

@@
 output:
+  word_document:
+    toc: yes
   html_document:
-    toc: yes
-  word_document:
     toc: yes
@@
   geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
-  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black", size = 1) +
+  geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black") +
   geom_point(data = seed_loc, aes(x = xloc, y = yloc), color = "red", size = 3) +
@@
 plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)
+
+# ggsave("paper/figures/Figure1.png",
+#        width = 2.5,
+#        height = 4,
+#        units = "in",
+#        dpi = 300)
 ```
@@
 plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)
+
+# ggsave("paper/figures/Figure2.png",
+#        width = 6,
+#        height = 2,
+#        units = "in",
+#        dpi = 300)
 ```
@@
 plot_grid(weib_dens, gp_dens, ncol = 2, labels = "AUTO", label_size = 8)
+
+# ggsave("paper/figures/Figure3.png",
+#        width = 6,
+#        height = 2.5,
+#        units = "in",
+#        dpi = 300)
 

### 2021-02-11 movement_paper/2_11_explora.Rmd
Progress.

---
title: "Incorporating individual variation in animal movement models"
subtitle: "Explore data and sampling sequences"
output:
  html_document:
      toc: true
bibliography: "aracari_movement.bib"
---

# Overall description

We have used the data collected by Kimberly Holbrook for her studies on toucan home ranges and movement patterns [@holbrook2011home]. We are starting the original raw data here. Previous work used clean data, as is shown in the `raw-data/newpointlocs.R`, by restricting the individuals to those with a minimum of 40 observations and locations collected in intervals from 15 to 90 minutes in multiples of 15 minutes. As shown in previous studies [@holbrook2007using], the distances traveled by toucans in 15-30 minutes represent the most probable distances for seed dispersal. Due to data collection constraints, locations could not be obtained every 15 minutes, and birds were sometimes located at greater time intervals. Our goal in this section is to explore the raw data again, and use a probabilistic approach that will characterize the pattern of distances moved, and use these probability distributions to later randomly sample distances from.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(aracari)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(stringr)
library(adehabitatLT)
library(cowplot)
library(RColorBrewer)
library(gt)
library(lubridate)

theme_set(theme_bw())
```

```{r data}
# First, read in the raw tracking data
aracari_data<- read.csv("data/raw_location_data.csv")
# Time is presented as a time ID
# Each time interval is equivalent to 15 minutes
# Interval 1 == 6AM, so if we start at midnight, 6am is 24 intervals of 15 minutes each. I'm setting 6am as the start just because I don't have actual data on it, but we know they started early morning and that's what the time IDs are for in Kimberly's work.

# create a column for number of minutes equivalent to the intervals

seconds <- (24*15 + aracari_data$Time_ID * 15) * 60
td <- seconds_to_period(seconds)
aracari_data$time <- sprintf("%02d:%02d:%02d", td@hour, minute(td), second(td))

date <- paste(aracari_data$DATE, aracari_data$time)
aracari_data$date <- parse_date_time(date, "dmyHMS")
aracari_data$burst <- paste(aracari_data$Bird_ID, aracari_data$DATE, sep="_")

# Only keep the columns we need for adehabitat

aracari_data <- dplyr::select(aracari_data, Bird_ID, burst,
                           date, X_Estimate, Y_Estimate)
names(aracari_data) <- c("animal_id","burst_id", "date_time", "x", "y")
```

We can visualize the locations for each of the individuals tagged. The two separate groups represent the two locations considered: Yasuni Biosphere Reserve (upper left) and Tiputini Biodiversity Station (lower right).
```{r}
plot(aracari_data$y~aracari_data$x, 
     col = as.factor(aracari_data$animal_id), 
     pch = 16)
```

And the individual trajectories for each animal
```{r}
# we set the spatial coordinates for our data frame
aracari_spatial <- aracari_data
coordinates(aracari_spatial) <- c("x", "y")

#Assign a projection, I know it is UTM zone 18 because it is Ecuadorian Amazon
proj4string(aracari_spatial) <- CRS("+proj=utm +zone=18 +datum=WGS84")

# Create ltraj object for work with adehabitat
# We set typeII = TRUE because we have variable time frames, although locations were attempted every 15 minutes, this didn't always happen.
aracari_ltraj <- as.ltraj(coordinates(aracari_spatial), 
                          burst = aracari_spatial$burst_id,
                          date=aracari_spatial$date_time,
                          id=aracari_spatial$animal_id,
                          typeII = TRUE)

# We can see the locations for all the individuals tracked
plot(aracari_ltraj)
```

The trajectory for each animal measures [source](https://jamesepaterson.github.io/jamespatersonblog/02_trackingworkshop_trajectories):

* distance,
* dt (the difference in seconds between relocations),
* R2n (the squared distance between the first relocation of the trajectory and the current relocation), and
* two angle measurements (absolute and relative).

We can see the **bursts**, which describe continuous relocations during the same tracking session, which in this case is one day for four hours. Tracking periods are 4-6 daylight hours, with individual bird locations recorded every 15 minutes. Although, not always possible to get a reading every 15 minutes, some have other intervals. Tracking alternates between morning and afternoon to capture daily variation in movement.

  -   So, there is sampling error. A success/failure of capturing a signal every 15 minutes in those 4-6hours.

```{r}
aracari_ltraj
```

### References

### 2021-02-12 movement_paper/2_11_explora.Rmd
Playing with the data

@@
      pch = 16)
+
 ```
@@
   -   So, there is sampling error. A success/failure of capturing a signal every 15 minutes in those 4-6hours.
+  -   And, there are multiple tracking periods, each tracking period represented by a "burst"
 
 ```{r}
-aracari_ltraj
+head(aracari_ltraj)
+
+# Transform to a dataframe
+aracari_df <- ld(aracari_ltraj)
+
+aracari_df %>% drop_na(dt) %>% group_by(id) %>% distinct(burst) %>% tally()
+```
+
+```{r}
+
+# I want to include family groups in that data set, just in case we want to use that later
+# The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
+# I've added another group for birds (29,30) which are Yasuni birds, with overlapping territories and I would assume they are a social group.
+# All others are left as unknown.
+aracari_df$id <- factor(aracari_df$id, levels = c(1, 3, 5, 7, 13, 19, 22, 28, 49, 84, 10, 17, 20, 21, 24, 29, 30, 9))
+aracari_df %>%
+  mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
+                        ifelse(id == 7, "f2",
+                               ifelse(id %in% c(13, 19), "f3",
+                                      ifelse(id == 22, "f4",
+                                             ifelse(id == 28, "f5",
+                                                    ifelse(id %in% c(49,84),
+                                                           "f6", 
+                                                           ifelse(id %in% c(29, 30), "f7", "unknown")
+                                             ))))))) -> aracari_df
+```
+
+```{r}
+aracari_df %>% 
+  group_by(id) %>% 
+  distinct(burst) %>% 
+  tally()
+
+test <- aracari_df %>% 
+   mutate(T_minutes = dt/60,
+         #Bird_ID = id,
+         mpm = dist/T_minutes,
+         #R2n = lead(R2n)
+         ) 
+# %>%
+#   filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90)) %>%
+#   group_by(Bird_ID) %>%
+#   add_tally()
+
+path <- data.frame(aracari_ltraj[[1]], id = attr(aracari_ltraj[[1]], "id"))
+for(i in 2:length(aracari_ltraj)){
+  path <- rbind(path,
+                data.frame(aracari_ltraj[[i]], id = attr(aracari_ltraj[[i]], "id")))
+}
+
+path$distperday <- path$dist/(path$dt/60/60/24)
+
+# Aggregate to show mean distance per day for each turtle
+path.summary <- aggregate(distperday~id, data = path, FUN = mean)
+path.summary$sd <- aggregate(distperday~id, data = path, FUN = sd)$distperday
+
+# Look at summmary dataframe
+path.summary
+
+# Make a graph to visualize data using ggplot
+
+# Create limits used for error bars in graph
+limits <- aes(ymax = path.summary$distperday + path.summary$sd, 
+              ymin = path.summary$distperday - path.summary$sd)
+
+# Make plot. Choose the dataframe (data) and aesthetics (aes; for the x and y)
+ggplot(data = path.summary, aes(x = id, y = distperday, colour = id)) + 
+  geom_point(size = 3) + # add points
+  geom_errorbar(limits, width = 0.2) + # adds error bars
+  labs(x = "Animal number", 
+       y = "Mean distance travelled per day (m)" ) + # Axis labels
+  theme_classic() + # Make plot black and white with no background grid
+  theme(legend.position = "none")
+
 ```

### 2021-02-12 movement_paper/rudolph_ch2.Rmd
start file for manuscript

---
title: "Individual Variation in Animal Movement"
abstract: |
  This should be the abstract
output:
  word_document: default
  html_document:
    df_print: paged
bibliography: aracari_movement.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

<!-- For YAML -->
<!--   word_document: -->
<!--     reference_docx: paper_ref.docx -->

\newpage
# Introduction

### 2021-02-13 movement_paper/rudolph_ch2.Rmd
subtitles
Progress on introduction

@@
 output:
-  word_document: default
   html_document:
     df_print: paged
+  word_document: default
 bibliography: aracari_movement.bib
@@
 # Introduction
+
+## Animal movement models overview
+## Individual variation in animal movement
+## Consequences of individual variation in movement
+## Statistical approaches to model movement
+## Incorporating individual variation
+## Markov Models overview
+## Statistics of extremes overview
+
+Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels.
+This focus on generality has driven to a lack of frameworks for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
+Although there have been recent calls for incorporating individual variation in movement [@snell2019consequences, @shaw2020causes] we still need to develop theory that explores different types of variation in movement patterns to understand its consequences across these levels.
+In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].
+
+The specific case of seed dispersal is interesting because of the different levels and interactions happening.
+At the individual level, we focus on an individual bird consuming fruit and dispersing the seeds of the tree.
+How this particular individual moves across the landscape directly affects the dispersal for that specific tree and other trees from which it consumes fruit.
+At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting.
+Interspecific interactions come at play as multiple species find themselves together feeding from the same tress, and thus competing for these resources, while at the same time intraspecific interactions due to social behavior broadly determine general movement patterns.
+From the plant's perspective, the variation in movement patterns across all dispersers will determine eventual plant population spatial spread and success.
+Individuals will vary in their distances traveled while foraging or searching, directly influencing seed dispersal for the plant.
+Individuals with a tendency to travel larger distances or with higher probabilities of long-distance movements, will have a larger impact on plant population dynamics by increasing the plant's long-distance dispersal.
+These long-distance movements for seed-dispersing animals, or long-distance dispersal events for plants, can lead to spatial sorting of populations and range expansions [These are sources I haven't finished reading yet: Shine2011PNAS, Philips2008AmNat, Riotte-Lambert2019Trends.]
+
+Long-distance dispersal in plants is fundamental.....
+
+And thus providing theoretical frameworks that incorporate individual variation in animal movement can help us link that variation to seed dispersal patterns, and in particular to range expansion dynamics, having consequences at the landscape and regional scales.
+
+Shaw makes references to how interspecific interactions can contribute to individual movement variation in parasite/pathogen systems.
+In my case, I would consider how presence of other competitive frugivores could influence this variation (Competition between toucans for the virola fruits and space.
+Larger aracari kick out the little ones [@holbrook2011home]).
+Shaw brings up how worse conditions can cause increased movement for searching better habitats and escape from these areas.
+
+Traits that vary throughout an individuals lifetime can contribute to intra-individual variation. We saw this with the data from holbrook 2011 where breeding state and such would have impacts over
+
+Seems like I am mostly focused here on variation in foraging movements?
+Although the long-distance movements, or deviations from typical movement patterns (the rare events) might not be associated to foraging?
+
+Since I'm also interested in bees and pollination, it's like the two sides of the same coin.
+Basically plant animal interactions, specifically mutualisms.
+How individual variation in animal movement patterns or foraging patterns will change seed dispersal or pollination patterns that scale to forest community or landscape patterns.

### 2021-02-14 movement_paper/rudolph_ch2.Rmd
Add citation format

@@
 bibliography: aracari_movement.bib
+csl: ecology-letters.csl
 ---

### 2021-02-14 movement_paper/rudolph_ch2.Rmd
add nathan citation

@@
 How individual variation in animal movement patterns or foraging patterns will change seed dispersal or pollination patterns that scale to forest community or landscape patterns.
+
+Providing a general framework for movement ecology that allows to link movement patterns and processes, starting with a focus on movement itself and the individual's internal state,navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
+Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales.
+
+# References

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
add state-space model citation

@@
 Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales.
+In this regard, state-space models (SSMs) have been suggested as flexible options to describe the general framework that incorporates observation error and noisy data, as it is common in the case of radiotelemetry data, and even the use of hierarchical structures or mixed-effects SSMs that can explicitly model variability across individuals [@patterson2008state].
 

### 2021-02-15 movement_paper/2_11_explora.Rmd
Add raw data and format using adehabitatLT

@@
 # First, read in the raw tracking data
-aracari_data<- read.csv("data/raw_location_data.csv")
+# aracari_data <- read.csv("data/raw_location_data.csv")
+aracari_data <- read.csv("movement_paper/rawdata_ptpl.csv")
 # Time is presented as a time ID
@@
 
-seconds <- (24*15 + aracari_data$Time_ID * 15) * 60
-td <- seconds_to_period(seconds)
-aracari_data$time <- sprintf("%02d:%02d:%02d", td@hour, minute(td), second(td))
+dt <- paste(aracari_data$DATE, aracari_data$TIME) %>% 
+  parse_date_time(., "dmy IMS p")
 
-date <- paste(aracari_data$DATE, aracari_data$time)
-aracari_data$date <- parse_date_time(date, "dmyHMS")
-aracari_data$burst <- paste(aracari_data$Bird_ID, aracari_data$DATE, sep="_")
+aracari_data$dt <- dt
+
+names(aracari_data)[1] <- "TRANS"
+
+# seconds <- (24*15 + aracari_data$Time_ID * 15) * 60
+# td <- seconds_to_period(seconds)
+# aracari_data$time <- sprintf("%02d:%02d:%02d", td@hour, minute(td), second(td))
+# 
+# date <- paste(aracari_data$DATE, aracari_data$time)
+# aracari_data$date <- parse_date_time(date, "dmyHMS")
+# aracari_data$burst <- paste(aracari_data$Bird_ID, aracari_data$DATE, sep="_")
+
+aracari_data$burst <- paste(aracari_data$TRANS, aracari_data$DATE)
 
@@
 
-aracari_data <- dplyr::select(aracari_data, Bird_ID, burst,
-                           date, X_Estimate, Y_Estimate)
+# aracari_data <- dplyr::select(aracari_data, Bird_ID, burst,
+#                            date, X_Estimate, Y_Estimate)
+
+aracari_data %>% 
+  dplyr::select(., TRANS, burst, dt, X_Estimate, Y_Estimate) -> aracari_data
+
 names(aracari_data) <- c("animal_id","burst_id", "date_time", "x", "y")
+
+```
+
+```{r eval=FALSE}
+# Just checking some summary information:
+aracari_data %>% 
+  group_by(animal_id) %>% 
+  summarise(nlocs = n())
 ```
@@
 
-aracari_df %>% drop_na(dt) %>% group_by(id) %>% distinct(burst) %>% tally()
+nbursts <- aracari_df %>% drop_na(dt) %>% group_by(id) %>% distinct(burst) %>% tally() %>% arrange(id) %>% rename(nbursts = n)
+nlocs <- aracari_df %>% group_by(id) %>% tally() %>% arrange(id) %>% rename(nlocs = n)
+
+merge(nbursts, nlocs, by = "id", all=TRUE) %>% arrange(nlocs)
+
 ```
@@
 # All others are left as unknown.
-aracari_df$id <- factor(aracari_df$id, levels = c(1, 3, 5, 7, 13, 19, 22, 28, 49, 84, 10, 17, 20, 21, 24, 29, 30, 9))
+aracari_df$id <- factor(aracari_df$id, levels = unique(aracari_df$id))
+unique(aracari_df$id)
 aracari_df %>%
@@
 ```{r}
-aracari_df %>% 
-  group_by(id) %>% 
-  distinct(burst) %>% 
-  tally()
-
-test <- aracari_df %>% 
-   mutate(T_minutes = dt/60,
-         #Bird_ID = id,
-         mpm = dist/T_minutes,
-         #R2n = lead(R2n)
-         ) 
-# %>%
-#   filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90)) %>%
-#   group_by(Bird_ID) %>%
-#   add_tally()
-
 path <- data.frame(aracari_ltraj[[1]], id = attr(aracari_ltraj[[1]], "id"))
@@
 
-# Aggregate to show mean distance per day for each turtle
+# Aggregate to show mean distance per day for each
 path.summary <- aggregate(distperday~id, data = path, FUN = mean)

### 2021-02-15 movement_paper/2_11_explora.Rmd
exploring home range stuff.

@@
 
+## Home range
+
+```{r}
+# Use only ones with more than 40 locations
+
+aracari_data %>% 
+  group_by(animal_id) %>% 
+  tally() %>% 
+  filter(., n >= 38) %>%
+  dplyr::select(., animal_id) ->ids
+
+aracari_sp <- aracari_data %>% 
+  filter(., animal_id %in% ids$animal_id) %>% 
+  dplyr::select(., animal_id, x, y) %>% 
+  rename(id = animal_id)
+
+coordinates(aracari_sp) <- c("x", "y")
+proj4string(aracari_sp) <- CRS("+proj=utm +zone=18 +datum=WGS84")
+
+library(adehabitatHR)
+aracari_mcp <- mcp(aracari_sp, percent = 95)
+aracari_mcp
+plot(aracari_mcp)
+
+# Kernel
+kernel_ref <- kernelUD(aracari_sp)
+image(kernel_ref)
+
+aracari_kernel_poly <- getverticeshr(kernel_ref, percent = 95)
+print(aracari_kernel_poly)
+
+```
+
 ### References

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
skeleton introduction done

--- 2021-02-14 movement_paper/rudolph_ch2.Rmd
@@
     df_print: paged
-  word_document: default
+  word_document:
+    reference_docx: move_ref.docx
 bibliography: aracari_movement.bib
@@
 
-<!-- For YAML -->
-<!--   word_document: -->
-<!--     reference_docx: paper_ref.docx -->
-
 \newpage
@@
 
-## Animal movement models overview
-## Individual variation in animal movement
-## Consequences of individual variation in movement
-## Statistical approaches to model movement
-## Incorporating individual variation
-## Markov Models overview
-## Statistics of extremes overview
+## Why do we study animal movement and what can it tell us?
+   Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment.
+The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how, and these questions can be answered at the scales of individuals or populations.
+A general framework for movement ecology that allows to link movement patterns and processes, starts with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
+The overall goal of studying movement seeks to find the linkages between the causes and mechanisms of animal movement, that result in spatiotemporal patterns that feedback to various ecological and evolutionary processes.
 
+## What is the importance of individual variation in animal movement?  
   Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels.
@@
 
+## How does this relate to mutualisms and long-distance movements?
   The specific case of seed dispersal is interesting because of the different levels and interactions happening.
@@
 How this particular individual moves across the landscape directly affects the dispersal for that specific tree and other trees from which it consumes fruit.
-At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting.
+At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting, or even smaller scale variation related to different states, such as foraging or resting.
 Interspecific interactions come at play as multiple species find themselves together feeding from the same tress, and thus competing for these resources, while at the same time intraspecific interactions due to social behavior broadly determine general movement patterns.
@@
 Individuals with a tendency to travel larger distances or with higher probabilities of long-distance movements, will have a larger impact on plant population dynamics by increasing the plant's long-distance dispersal.
-These long-distance movements for seed-dispersing animals, or long-distance dispersal events for plants, can lead to spatial sorting of populations and range expansions [These are sources I haven't finished reading yet: Shine2011PNAS, Philips2008AmNat, Riotte-Lambert2019Trends.]
-
-Long-distance dispersal in plants is fundamental.....
-
-And thus providing theoretical frameworks that incorporate individual variation in animal movement can help us link that variation to seed dispersal patterns, and in particular to range expansion dynamics, having consequences at the landscape and regional scales.
-
+These long-distance movements for seed-dispersing animals, or long-distance dispersal events for plants, can lead to spatial sorting of populations and range expansions [These are sources I haven't finished reading yet: Shine2011PNAS, Philips2008AmNat, Riotte-Lambert2019Trends.] This is also the case for pollination, where pollinator variability in movement patterns and long-distance movements has direct implications for pollination success and plant population persistence, specially in fragmented landscapes [need to find sources for this].
   Shaw makes references to how interspecific interactions can contribute to individual movement variation in parasite/pathogen systems.
@@
 
-Traits that vary throughout an individuals lifetime can contribute to intra-individual variation. We saw this with the data from holbrook 2011 where breeding state and such would have impacts over
+## What will this paper actually do to address the main question?  
+  In this paper we would like to present a statistical framework that incorporates variability among individuals into population level movement patterns.
+Providing theoretical frameworks that incorporate individual variation in animal movement can help us link that variation to seed dispersal patterns, and in particular to range expansion dynamics, having consequences at the landscape and regional scales.
+We will also explore how the variation in long-distance movements translates to population level estimates and how these long-distance movements or deviations from typical movement patterns can be incorporated into this framework.Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales.
+In this regard, state-space models (SSMs) have been suggested as flexible options to describe the general framework that incorporates observation error and noisy data, as it is common in the case of radiotelemetry data, and even the use of hierarchical structures or mixed-effects SSMs that can explicitly model variability across individuals [@patterson2008state].
+With our work, we seek to expand on the use of state-space models that incorporate variability in movement and can later be used to simulate movement patterns that affect seed dispersal or pollination patterns at the landscape scale.
 
-Seems like I am mostly focused here on variation in foraging movements?
-Although the long-distance movements, or deviations from typical movement patterns (the rare events) might not be associated to foraging?
+# Methods
 
-Since I'm also interested in bees and pollination, it's like the two sides of the same coin.
-Basically plant animal interactions, specifically mutualisms.
-How individual variation in animal movement patterns or foraging patterns will change seed dispersal or pollination patterns that scale to forest community or landscape patterns.
+## Overview of state-space models for movement
+
+# References

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
Brief state space description for movement

@@
 ## Overview of state-space models for movement  
+  State-space models provide a probabilistic framework that allow for prediction of future states of a system based from previous states, by coupling an observation model with an underlying mechanistic model.
+When extending this framework to movement ecology, we understand that the process model provides the mechanism for movement across space and time, and the observation model is related to the sampling process.
+In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state].
 

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
update and add citations for methods

@@
 
+  The moveHMM package allows for fitting hmm models to different time series, which can come from different individuals, assuming that all individuals share the same movement models, meaning the same distributions and parameters for step length and angle.
+This is referred to as 'complete pooling' [@moveHMM, @langrock2012flexible, @michelot2016movehmm]
+
 # References

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
updates to methods, etc

@@
 output:
+  word_document:
+    reference_docx: move_ref.docx
   html_document:
     df_print: paged
-  word_document:
-    reference_docx: move_ref.docx
 bibliography: aracari_movement.bib
@@
 In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state].
+In general, state-space models are used to identify different states, or behavioral states, that determine different movement patterns associated to step length and turning angle.
+And some of the main questions asked with this approach are related to identifying these different states, or behavioral state-switching, from time series data on location tracking.HMMs can be used to categorize this movement data into behavioral states, and link it to foraging or mating activity, as an example.
 
   The moveHMM package allows for fitting hmm models to different time series, which can come from different individuals, assuming that all individuals share the same movement models, meaning the same distributions and parameters for step length and angle.
-This is referred to as 'complete pooling' [@moveHMM, @langrock2012flexible, @michelot2016movehmm]
+This is referred to as 'complete pooling' [@langrock2012flexible, @michelot2016movehmm], but there is no current implementation for fitting HMMs to highly irregular and noisy tracking data, that explicitly incorporates variability among individuals.
+In this paper, we would like to show the effects of incorporating individual variability under a HMM framework that allows for variation not only in parameter values associated to udnerlying model distributions of step length and angle, but also on overall distribution function.
 

### 2021-03-04 paper/figures_tables.Rmd
Save figures as separate files

@@
 ggplot() +
-  geom_path(data = animalTraj, aes(x = xloc, y = yloc), size = 1, color = "darkgrey") +
+  geom_path(data = animalTraj, aes(x = xloc, y = yloc), 
+            #size = 1,
+            color = "darkgrey") +
   geom_point(data = animalTraj, aes(x = xloc, y = yloc), color = "black") +
@@
 ```{r fig.width=2.5, fig.height=4}
-plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "AUTO", label_size = 10)
+plot_grid(fig_GRT, fig_MD, align = "v", nrow = 2, labels = "auto", label_size = 10)
 
-# ggsave("paper/figures/Figure1.png",
+# ggsave(filename = "figures/Figure1.tiff",
+#        device = "tiff",
 #        width = 2.5,
@@
 ```{r fig.height=2, fig.width=6}
-plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "AUTO", label_size = 8)
+plot_grid(fig_traj, fig_disp, fig_agg, ncol = 3, align = "h", labels = "auto", label_size = 8)
 
-# ggsave("paper/figures/Figure2.png",
+# ggsave("figures/Figure2.tiff",
 #        width = 6,
@@
 
-plot_grid(weib_dens, gp_dens, ncol = 2, labels = "AUTO", label_size = 8)
+plot_grid(weib_dens, gp_dens, ncol = 2, labels = "auto", label_size = 8)
 
-# ggsave("paper/figures/Figure3.png",
+# ggsave("figures/Figure3.tiff",
 #        width = 6,
@@
 
-boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("B", "C"))
+boxplots <- plot_grid(a,b, ncol = 2, align = "h", labels = c("b", "c"))
 
-plot_grid(dens_by_id, boxplots, nrow=2, labels = c("A", ""))
+plot_grid(dens_by_id, boxplots, nrow=2, labels = c("a", ""))
 
-# Edit redundant labels
-# Fix names for axes
+# ggsave(filename = "figures/Figure4.tiff",
+#        device = "tiff",
+#        width = 6,
+#        height = 6,
+#        units = "in",
+#        dpi = 300)
 

### 2021-03-15 distributions_paper/format_raw_dat.Rmd
New paper on fitting distributions

--- 2021-02-15 movement_paper/2_11_explora.Rmd
@@
       toc: true
-bibliography: "aracari_movement.bib"
+bibliography: "aracari_refs.bib"
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
@@
 # aracari_data <- read.csv("data/raw_location_data.csv")
-aracari_data <- read.csv("movement_paper/rawdata_ptpl.csv")
+aracari_data <- read.csv("rawdata_ptpl.csv")
 # Time is presented as a time ID
@@
 
-## Home range
+<!-- ## Home range -->
 
-```{r}
+```{r eval = FALSE}
 # Use only ones with more than 40 locations

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
New paper on fitting distributions

---
title: "Variation in distance between consecutive animal locations"
abstract: |
  This should be the abstract
output:
  word_document:
    reference_docx: docx_ref.docx
  html_document:
    df_print: paged
bibliography: aracari_refs.bib
csl: ecology-letters.csl
---

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(data)
```

\newpage
# Questions  
* What is the distribution of distances between consecutive recorded locations? 
* Are there differences between individuals or can we use the same distribution to describe these distances between two locations?

The reasoning behind this, is that distances between locations can be used later on to describe variation in step length when simulating animal movement under simple models such as random walk.

# References

### 2021-03-15 distributions_paper/format_raw_dat.Rmd
save data frame after calculating net squared displacement

@@
                                              ))))))) -> aracari_df
+
+saveRDS(aracari_df, "aracari_df.RDS")
 ```

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
add libraries and data
Making density plots

@@
 ```{r}
-library(data)
+library(tidyverse)
+library(aracari)
+library(stringr)
+library(fitdistrplus)
+library(cowplot)
+library(RColorBrewer)
+library(gt)
+
+theme_set(theme_bw())
+```
+
+```{r}
+aracari_df <- readRDS("aracari_df.RDS")
+```
+
+```{r}
+# Which individuals will we conside? Need at least a certain number of data points to fit distributions
+# Don't remove any yet, just make sure you make it clear how many data points you have for each
+
+aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>% 
+  tally()
 ```
@@
 
+### I'll go first with just the distances between locations, might switch to net displacement or net squared displacement later. 
+**Visualize the variation and distribution of these distances between locations**
+
+```{r}
+
+aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  ggplot(., aes((x = dist))) +
+  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Distance in meters") +
+  theme_classic()
+
+```
+
+```{r}
+aracari_df %>% 
+  dplyr::filter(dist != 0,
+                fam_g != "unknown") %>%
+  ggplot(., aes((x = dist))) +
+  facet_wrap(~fam_g) +
+  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  # geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Distance in meters") +
+  #theme_classic() +
+  NULL
+
+aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  ggplot(., aes((x = dist))) +
+  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Distance in meters") +
+  theme_classic()
+```
+
+```{r eval = FALSE, fig.width=12, fig.height=4}
+
+zoom_dims <- c(110, 210, 0, 0.01)
+annot_xy <- c(50, 250, 0.025, 0.045)
+
+ind_dens_plot <- df %>%
+  ggplot(., aes(x = mpm)) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  ylim(0, 0.055) +
+  xlim(0, 250) +
+  labs(title = "Individual") +
+  theme_classic()
+
+ind_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> ind_zoom
+
+ind_dens_plot +
+  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a
+
+fam_dens_plot <- df %>%
+  filter(., fam_g != "unknown") %>% 
+  ggplot(., aes(x = mpm)) +
+  geom_line(stat = "density", color = "red", lwd = 1) +
+  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = "blue") +
+  ylim(0, 0.055) +
+  xlim(0, 250) + 
+  labs(title = "Family") +
+  theme_classic()
+
+fam_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> fam_zoom
+
+fam_dens_plot +
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b
+
+plot_grid(a, b)
+
+```
+
 # References

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
cauchy makes no sense

@@
 output:
+  html_document:
+    df_print: paged
   word_document:
     reference_docx: docx_ref.docx
-  html_document:
-    df_print: paged
 bibliography: aracari_refs.bib
@@
   tally()
+
+aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>% 
+  filter(., n() >= 10) %>% 
+  ungroup()
 ```
@@
 ```{r}
-
 aracari_df %>%
+  dplyr::filter(dist != 0) %>%
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
   dplyr::filter(dist != 0) %>%
@@
 aracari_df %>% 
-  dplyr::filter(dist != 0,
-                fam_g != "unknown") %>%
-  ggplot(., aes((x = dist))) +
-  facet_wrap(~fam_g) +
-  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
-  # geom_line(stat = "density", color = "#1191d1", lwd = 1) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = "Distance in meters") +
-  #theme_classic() +
-  NULL
-
-aracari_df %>% 
   dplyr::filter(dist != 0) %>% 
-  ggplot(., aes((x = dist))) +
-  geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
-  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  ggplot(., aes(x = dist)) +
+  facet_wrap(~id) +
+  geom_line(stat = "density") +
   geom_vline(xintercept = 0, color = "grey") +
@@
 
+# Fit distribution  
+Useful resource to use the package [fitdistrplus](https://cran.r-project.org/web/packages/fitdistrplus/vignettes/FAQ.html)
+```{r}
+# These are the distributions I am considering for characterizing the meters moved per minute in the data
+dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+
+# These are the parameters and associated distributions that will be needed later to build a dataframe of parameters
+param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+
+df <- aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  mutate(tmin = dt/60,
+         mpm = dist/tmin,
+         Bird_ID = paste0("B", id)) %>% 
+  filter(., mpm != 0) %>% 
+  {.}
+
+```
+
+```{r eval=FALSE}
+descdist(df$dist, boot = 1000)
+hist(df$dist)
+
+# problem
+fitdist(df$dist, distr = "exp")
+fitdist(df$dist, distr = "gamma")
+#no issue
+fitdist(df$dist, distr = "lnorm")
+fitdist(df$dist, distr = "weibull")
+fitdist(df$dist, distr = "cauchy")
+```
+
+```{r}
+# These are the distributions I am considering for characterizing the meters moved per minute in the data
+dist.used <- c("lnorm", "weibull", "cauchy")
+
+# These are the parameters and associated distributions that will be needed later to build a dataframe of parameters
+param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
+dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
+
+```
+
+```{r}
+
+# Fit the four models for the population level data
+
+pop <- lapply(dist.used, function(x){fitdist(df$dist, distr = x)})
+
+# Get data for qqplot at population level
+qqpop <- qqcomp(pop, plotstyle = "ggplot")$data
+names(qqpop) <- c("theoretical", "fdist", "empirical")
+
+# Save the population level parameters
+prms.df <- aracari::build_fits_df(pop) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = "pop")
+
+# Repeating the process for data at the individual level
+inds <- unique(as.character(df$Bird_ID))
+
+# Fitting the four distributions for each individual and saving the parameters in a dataframe
+for(i in 1:length(inds)){
+  fit.df <- df %>% 
+    dplyr::filter(., Bird_ID == inds[i])
+
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$dist, distr = x)})
+
+  assign(paste(inds[i]), fit)
+
+  fit.prms <- build_fits_df(fit) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = inds[i])
+
+  prms.df <- bind_rows(prms.df, fit.prms)
+}
+
+# Getting qqplot data for each individual
+inds.models.data <- NULL
+ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
+# ind.models <- list(B1, B13, B17, B19, B20, B22, B24, B28, B29, B3, B30, B49, B5, B7, B84)
+chr.models <- inds
+for(i in 1:length(chr.models)){
+  x <- ind.models[[i]]
+
+  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
+    mutate(data = chr.models[i])
+  names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
+  inds.models.data <- bind_rows(inds.models.data, qqdata)
+}
+```
+
+```{r eval=FALSE}
+# OLD MPM
+# Fit the four models for the population level data
+
+pop <- lapply(dist.used, function(x){fitdist(df$mpm, distr = x)})
+
+# Get data for qqplot at population level
+qqpop <- qqcomp(pop, plotstyle = "ggplot")$data
+names(qqpop) <- c("theoretical", "fdist", "empirical")
+
+# Save the population level parameters
+prms.df <- aracari::build_fits_df(pop) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = "pop")
+
+# Repeating the process for data at the individual level
+inds <- unique(as.character(df$Bird_ID))
+
+# Fitting the four distributions for each individual and saving the parameters in a dataframe
+for(i in 1:length(inds)){
+  fit.df <- df %>% 
+    dplyr::filter(., Bird_ID == inds[i])
+
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$mpm, distr = x)})
+
+  assign(paste(inds[i]), fit)
+
+  fit.prms <- build_fits_df(fit) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = inds[i])
+
+  prms.df <- bind_rows(prms.df, fit.prms)
+}
+
+# Getting qqplot data for each individual
+inds.models.data <- NULL
+ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
+# ind.models <- list(B1, B13, B17, B19, B20, B22, B24, B28, B29, B3, B30, B49, B5, B7, B84)
+chr.models <- inds
+for(i in 1:length(chr.models)){
+  x <- ind.models[[i]]
+
+  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
+    mutate(data = chr.models[i])
+  names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
+  inds.models.data <- bind_rows(inds.models.data, qqdata)
+}
+```
+
+```{r ind_QQplots, fig.width=12, fig.height=5}
+
+qqpop %>% 
+  mutate(individual = "POPULATION") %>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  facet_wrap(~individual) +
+  #coord_equal() +
+  geom_point(shape = 16, alpha = 0.8, size = 4) +
+  geom_abline(intercept = 0, slope = 1) +
+  labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral", name = "Distribution") +
+  theme(legend.position = c(0.8, 0.2)) +
+  NULL -> a
+
+inds.models.data%>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  #facet_grid(individual~fdist) +
+  facet_wrap(~individual)+
+    geom_point(shape = 16, alpha = 0.8, size = 3) +
+    geom_abline(intercept = 0, slope = 1) +
+    labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral") +
+  theme(legend.position = "none") +
+  guides(color = guide_legend(title = "Distribution")) +
+  #coord_equal() +
+  NULL -> b
+
+plot_grid(a,b, rel_widths = c(1,2), labels = "AUTO")
+
+```
+
 # References

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
added if statement to easily switch between focus variables

--- 2021-03-15 distributions_paper/rudolph_distributions.Rmd
@@
 ```{r}
-library(data)
+library(tidyverse)
+library(aracari)
+library(stringr)
+library(fitdistrplus)
+library(cowplot)
+library(RColorBrewer)
+library(gt)
+
+theme_set(theme_bw())
+```
+
+```{r}
+aracari_df <- readRDS("aracari_df.RDS")
+```
+
+```{r eval=FALSE}
+# Which individuals will we conside? Need at least a certain number of data points to fit distributions
+# Don't remove any yet, just make sure you make it clear how many data points you have for each
+
+aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>% 
+  tally()
+
+```
+
+```{r}
+# Create my focus variable and only for individuals with 30+ observations
+
+# focus <- "dist"
+# focus <- "R2n"
+focus <- "mpm"
+
+if(focus == "dist"){
+  df <- aracari_df %>%
+  dplyr::filter(dist != 0) %>%
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  dplyr::filter(dist != 0) %>% 
+    mutate(Bird_ID = paste0("B", id),
+           focus = dist)
+
+  dist.used <- c("lnorm", "weibull", "cauchy")
+  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
+  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
+}
+
+if(focus == "R2n"){
+  df <- aracari_df %>%
+  dplyr::filter(R2n != 0) %>%
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  dplyr::filter(R2n != 0) %>% 
+    mutate(Bird_ID = paste0("B", id),
+           focus = R2n)
+}
+
+if(focus == "mpm"){
+  df <- aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  mutate(tmin = dt/60,
+         mpm = dist/tmin,
+         Bird_ID = paste0("B", id),
+         focus = mpm) %>% 
+  dplyr::filter(., mpm != 0)
+
+  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+}
+
 ```
@@
 
+### I'll go first with just the distances between locations, might switch to net displacement or net squared displacement later. 
+**Visualize the variation and distribution of these distances between locations**
+
+```{r}
+ df %>%
+  ggplot(., aes((x = focus))) +
+  geom_line(aes(x = focus, group = id), stat = "density", alpha = 0.4) +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = paste(focus)) +
+  theme_classic()
+
+```
+
+```{r}
+df %>%
+  ggplot(., aes(x = focus)) +
+  facet_wrap(~id) +
+  geom_line(stat = "density") +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = paste(focus)) +
+  theme_classic()
+```
+
+# Fit distribution  
+Useful resource to use the package [fitdistrplus](https://cran.r-project.org/web/packages/fitdistrplus/vignettes/FAQ.html)
+
+```{r eval=FALSE}
+descdist(df$dist, boot = 1000)
+hist(df$dist)
+
+# problem
+fitdist(df$dist, distr = "exp")
+fitdist(df$dist, distr = "gamma")
+#no issue
+fitdist(df$dist, distr = "lnorm")
+fitdist(df$dist, distr = "weibull")
+fitdist(df$dist, distr = "cauchy")
+
+```
+
+```{r}
+
+# Fit the four models for the population level data
+
+pop <- lapply(dist.used, function(x){fitdist(df$focus, distr = x)})
+
+# Get data for qqplot at population level
+qqpop <- qqcomp(pop, plotstyle = "ggplot")$data
+names(qqpop) <- c("theoretical", "fdist", "empirical")
+
+# Save the population level parameters
+
+build_fits_df <- function(x){
+
+  nm <- deparse(substitute(x))
+
+  x %>%
+    map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
+    map(as_tibble) %>%
+    bind_rows()
+}
+
+prms.df <- build_fits_df(pop) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = "pop")
+
+# Repeating the process for data at the individual level
+inds <- unique(as.character(df$Bird_ID))
+
+# Fitting the four distributions for each individual and saving the parameters in a dataframe
+for(i in 1:length(inds)){
+  fit.df <- df %>% 
+    dplyr::filter(., Bird_ID == inds[i])
+
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})
+
+  assign(paste(inds[i]), fit)
+
+  fit.prms <- build_fits_df(fit) %>% 
+  mutate(param = param,
+         dist = dist,
+         data = inds[i])
+
+  prms.df <- bind_rows(prms.df, fit.prms)
+}
+
+# Getting qqplot data for each individual
+inds.models.data <- NULL
+ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
+# ind.models <- list(B1, B13, B17, B19, B20, B22, B24, B28, B29, B3, B30, B49, B5, B7, B84)
+chr.models <- inds
+for(i in 1:length(chr.models)){
+  x <- ind.models[[i]]
+
+  qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
+    mutate(data = chr.models[i])
+  names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
+  inds.models.data <- bind_rows(inds.models.data, qqdata)
+}
+```
+
+```{r ind_QQplots, fig.width=12, fig.height=5}
+
+qqpop %>% 
+  mutate(individual = "POPULATION") %>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  facet_wrap(~individual) +
+  #coord_equal() +
+  geom_point(shape = 16, alpha = 0.8, size = 4) +
+  geom_abline(intercept = 0, slope = 1) +
+  labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral", name = "Distribution") +
+  theme(legend.position = c(0.8, 0.2)) +
+  NULL -> a
+
+inds.models.data%>% 
+  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
+  #facet_grid(individual~fdist) +
+  facet_wrap(~individual)+
+    geom_point(shape = 16, alpha = 0.8, size = 3) +
+    geom_abline(intercept = 0, slope = 1) +
+    labs(x = "Model Quantiles",
+         y = "Empirical Quantiles") +
+  #scale_color_viridis_d() +
+  scale_color_brewer(palette = "Spectral") +
+  theme(legend.position = "none") +
+  guides(color = guide_legend(title = "Distribution")) +
+  #coord_equal() +
+  NULL -> b
+
+plot_grid(a,b, rel_widths = c(1,2), labels = "AUTO")
+
+```
+
 # References

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
Building distribution fits

@@
   dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
+  kpars <- c(2, 2, 2, 2, 2, 2)
 }
@@
   dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+  kpars <- c(1, 2, 2, 2, 2, 2, 2)
+}
+
+if(focus == "m15"){
+  df <- aracari_df %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>%
+  filter(., n() >= 30) %>%
+  ungroup() %>%
+  mutate(tmin = dt/60,
+         mpm = dist/tmin,
+         m15 = mpm*15,
+         Bird_ID = paste0("B", id),
+         focus = m15) %>% 
+  dplyr::filter(., m15 != 0)
+
+  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+  kpars <- c(1, 2, 2, 2, 2, 2, 2)
 }
@@
 
-```{r eval=FALSE}
-descdist(df$dist, boot = 1000)
-hist(df$dist)
-
-# problem
-fitdist(df$dist, distr = "exp")
-fitdist(df$dist, distr = "gamma")
-#no issue
-fitdist(df$dist, distr = "lnorm")
-fitdist(df$dist, distr = "weibull")
-fitdist(df$dist, distr = "cauchy")
-
-```
-
 ```{r}
@@
          dist = dist,
+         kpars = kpars,
          data = "pop")
@@
 # Fitting the four distributions for each individual and saving the parameters in a dataframe
+ind.models <- NULL
 for(i in 1:length(inds)){
@@
 
+  ind.models[[i]] <- fit
+
   assign(paste(inds[i]), fit)
@@
          dist = dist,
+         kpars = kpars,
          data = inds[i])
@@
 inds.models.data <- NULL
-ind.models <- list(B1, B13, B19, B22, B28, B29, B3, B30, B49, B5, B7, B84)
-# ind.models <- list(B1, B13, B17, B19, B20, B22, B24, B28, B29, B3, B30, B49, B5, B7, B84)
-chr.models <- inds
-for(i in 1:length(chr.models)){
+for(i in 1:length(inds)){
   x <- ind.models[[i]]
@@
   qqdata <- qqcomp(x, plotstyle = "ggplot")$data %>% 
-    mutate(data = chr.models[i])
+    mutate(data = inds[i])
   names(qqdata) <- c("theoretical", "fdist", "empirical", "individual")
@@
 
+## Information criteria
+
+```{r}
+
+ic_calc <- function(n, kpars, loglik){
+
+  BIC <- log(n)*kpars - 2*loglik
+  AIC <- 2*kpars - 2*loglik
+  AICc <- AIC + (2* kpars * (kpars+1)/(n-kpars-1))
+}
+
+prms.df %>% 
+  mutate(BIC = log(n)*kpars - 2*loglik,
+         AIC = 2*kpars - 2*loglik,
+         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
+  group_by(data) %>% 
+  mutate(deltaBIC = signif(BIC - min(BIC), 3),
+         deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3)) -> prms_ic
+```
+
+So, for each individual, which is the best fitting distribution, based on AIC or BIC? Here we are just focusing on the model fits for each individual.
+
+```{r}
+prms_ic %>% 
+  filter(., data != "pop") %>% 
+  dplyr::select(dist, data, deltaAIC,
+                #deltaAICc,
+                deltaBIC) %>% 
+  distinct() %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  filter(value == 0) %>% 
+  dplyr::select(-value) %>% 
+  pivot_wider(., names_from = ic, values_from = dist) %>% 
+  mutate(agree = ifelse(deltaAIC == deltaBIC, "yes", "no"))
+```
+
+```{r fig.width=12, fig.height=4}
+# To visualize the differences in the information criteria at the individual level
+
+prms_ic %>% 
+  filter(., data != "pop") %>% 
+  dplyr::select(dist, data, deltaAIC, 
+                deltaAICc,
+                deltaBIC) %>% 
+  distinct() %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  mutate(plot_alpha = ifelse(value == "0", 1, 0.8)) %>% 
+  ggplot(., aes(x = data, y = value, color = dist 
+                #alpha = plot_alpha
+                )) +
+  facet_wrap(~ic) +
+  geom_point(size = 3) +
+  scale_color_brewer(palette = "Spectral") + 
+  #scale_alpha_continuous(range = c(0.5, 1)) +
+  labs(x = "") +
+  theme(legend.position = "bottom") +
+  guides(color = guide_legend(title = "Distribution"))
+
+```
+Now we can compare what we call *models*, in which we compare a model that does complete pooling and considers all the data together, and the other model that considers individual variation. 
+So, the complete pooling, takes all the data and fits a distribution to it. 
+The individual variation models will fit a distribution to each individual.
+At one level we will use the same distribution for all individuals and only consider variation in parameters.
+At the next level, we will consider a change in parameters and distributions, where individuals can have different distributions, and this is what we call the mixed distribution model for individual variation.
+
 # References

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
2 units for delta AIC

@@
  focus <- "mpm"
+# focus <- "m15"
 
@@
     mutate(Bird_ID = paste0("B", id),
-           focus = R2n)
+           focus = sqrt(R2n))
+
+  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+  kpars <- c(1, 2, 2, 2, 2, 2, 2)
 }
@@
 Useful resource to use the package [fitdistrplus](https://cran.r-project.org/web/packages/fitdistrplus/vignettes/FAQ.html)
+Also check [this](https://stackoverflow.com/questions/37152482/power-law-fitted-by-fitdistr-function-in-package-fitdistrplus). Should I do the opimization by hand?
 
@@
 
-So, for each individual, which is the best fitting distribution, based on AIC or BIC? Here we are just focusing on the model fits for each individual.
+So, for each individual, which is the best fitting distribution, based on AIC or BIC?
+Here we are just focusing on the model fits for each individual.
+Best model is that with the lowest AIC or BIC, but other competitive models would be those that are within 2 units of those.
 
@@
   filter(value == 0) %>%  
-  dplyr::select(-value) %>% 
   pivot_wider(., names_from = ic, values_from = dist) %>% 
-  mutate(agree = ifelse(deltaAIC == deltaBIC, "yes", "no"))
+  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
+  dplyr::select(., data, agree) %>% 
+  rename(Individual = data,
+            `Best model` = agree)
+
+prms_ic %>% 
+  filter(., data != "pop") %>% 
+  dplyr::select(dist, data, deltaAIC,
+                #deltaAICc,
+                deltaBIC) %>% 
+  distinct() %>% 
+  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  filter(value > 0 & value <= 2) %>%  
+  pivot_wider(., names_from = ic, values_from = dist) %>% 
+  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
+  dplyr::select(., data, agree) %>% 
+  rename(Individual = data,
+            `Best model` = agree)
+
 ```

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
calc info crit for each model

@@
 prms.df %>% 
+  mutate(param = str_to_upper(param), 
+         dist = str_replace(dist, "exp", "Exponential"),
+         dist = str_replace(dist, "gamma", "Gamma"),
+         dist = str_replace(dist, "weibull", "Weibull"),
+         dist = str_replace(dist, "lnorm", "Lognormal"),
+         data = str_replace(data, "pop", "POP")) %>% 
   mutate(BIC = log(n)*kpars - 2*loglik,
@@
          deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> prms_ic
+         deltaAICc = signif(AICc - min(AICc), 3)) -> nice_prms
 ```
 
-So, for each individual, which is the best fitting distribution, based on AIC or BIC?
-Here we are just focusing on the model fits for each individual.
-Best model is that with the lowest AIC or BIC, but other competitive models would be those that are within 2 units of those.
+So, for each individual, which is the best fitting distribution, based on AIC or BIC? This is the distribution with the lowest AIC or BIC score for each individual.
 
 ```{r}
-prms_ic %>% 
-  filter(., data != "pop") %>% 
+nice_prms %>% 
+  filter(., str_detect(data, "B")) %>% 
   dplyr::select(dist, data, deltaAIC,
@@
             `Best model` = agree)
-
-prms_ic %>% 
-  filter(., data != "pop") %>% 
-  dplyr::select(dist, data, deltaAIC,
-                #deltaAICc,
-                deltaBIC) %>% 
-  distinct() %>% 
-  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-  filter(value > 0 & value <= 2) %>%  
-  pivot_wider(., names_from = ic, values_from = dist) %>% 
-  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
-  dplyr::select(., data, agree) %>% 
-  rename(Individual = data,
-            `Best model` = agree)
+# 
+# 
+# nice_prms %>% 
+#   filter(., data != "pop") %>% 
+#   dplyr::select(dist, data, deltaAIC,
+#                 #deltaAICc,
+#                 deltaBIC) %>% 
+#   distinct() %>% 
+#   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+#   filter(value > 0 & value <= 2) %>%  
+#   pivot_wider(., names_from = ic, values_from = dist) %>% 
+#   mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
+#   dplyr::select(., data, agree) %>% 
+#   rename(Individual = data,
+#             `Best model` = agree)
 
@@
 
+However, it is not as straight-forward since there are multiple competing models for certain individuals, which we consider as those within less than 2 units of the delta AIC or BIC.
+When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models.
 ```{r fig.width=12, fig.height=4}
@@
 
-prms_ic %>% 
-  filter(., data != "pop") %>% 
+nice_prms %>% 
+  filter(., str_detect(data, "B")) %>% 
   dplyr::select(dist, data, deltaAIC, 
@@
   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
+  filter(value >= 0 & value <= 2) %>%  
   mutate(plot_alpha = ifelse(value == "0", 1, 0.8)) %>% 
@@
 ```
-Now we can compare what we call *models*, in which we compare a model that does complete pooling and considers all the data together, and the other model that considers individual variation. 
-So, the complete pooling, takes all the data and fits a distribution to it. 
+Now we can compare what we call *models*, in which we compare a model that does complete pooling and considers all the data together, and the other model that considers individual variation, and so it fits a separate distribution to the data from each individual.
+
 The individual variation models will fit a distribution to each individual.
@@
 
+```{r}
+
+# Create the dataframe that compares the models by information criteria
+nice_prms %>% 
+  filter(., str_detect(data, "B")) %>%
+  dplyr::select(., loglik, n, dist, kpars) %>% 
+  distinct() %>%
+  group_by(dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
+            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
+            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
+    mutate(deltaAIC = signif(AIC - min(AIC), 3),
+         deltaAICc = signif(AICc - min(AICc), 3),
+         deltaBIC = signif(BIC - min(BIC), 3),
+         data = "Individual") %>% 
+  full_join(., nice_prms %>%
+              filter(., str_detect(data, "B", negate = TRUE)) %>% 
+              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
+              distinct() %>% 
+              mutate(data = "Population")) -> popind.IC.comp
+
+# Get the multi-distribution model fit
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaBIC) %>% 
+  dplyr::filter(., data != "POP" & deltaBIC == 0) %>% 
+  distinct() %>% 
+  ungroup() %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  as.numeric() -> multi.BIC
+
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAIC) %>% 
+  dplyr::filter(., data != "POP" & deltaAIC == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
+  as.numeric() -> multi.AIC
+
+nice_prms %>% 
+  dplyr::select(., dist, data, loglik, n, kpars, deltaAICc) %>% 
+  dplyr::filter(., data != "POP" & deltaAICc == 0) %>% 
+  distinct() %>%
+  ungroup() %>% 
+  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
+  as.numeric()-> multi.AICc
+
+popind.IC.comp %>% 
+  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
+  bind_rows(., data.frame(dist = "Multidist", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "Multidist")) -> model_comp_IC
+
+```
+
 # References

### 2021-03-15 distributions_paper/rudolph_distributions.Rmd
add desc test
up to showing variation in parameters

@@
          deltaAIC = signif(AIC - min(AIC), 3),
-         deltaAICc = signif(AICc - min(AICc), 3)) -> nice_prms
+         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
+  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
+         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms
 ```
 
-So, for each individual, which is the best fitting distribution, based on AIC or BIC? This is the distribution with the lowest AIC or BIC score for each individual.
+So, for each individual, which is the best fitting distribution, based on AIC or BIC?
+This is the distribution with the lowest AIC or BIC score for each individual.
+These are basically the distributions that will be used for the mixed distribution model later on.
 
@@
 nice_prms %>% 
+  filter(., str_detect(data, "B")) %>% 
   dplyr::select(., dist, data, loglik, n, kpars, deltaBIC) %>% 
-  dplyr::filter(., data != "POP" & deltaBIC == 0) %>% 
+  dplyr::filter(., deltaBIC == 0) %>% 
   distinct() %>% 
@@
 nice_prms %>% 
+  filter(., str_detect(data, "B")) %>% 
   dplyr::select(., dist, data, loglik, n, kpars, deltaAIC) %>% 
-  dplyr::filter(., data != "POP" & deltaAIC == 0) %>% 
+  dplyr::filter(., deltaAIC == 0) %>% 
   distinct() %>%
@@
 nice_prms %>% 
+  filter(., str_detect(data, "B")) %>% 
   dplyr::select(., dist, data, loglik, n, kpars, deltaAICc) %>% 
-  dplyr::filter(., data != "POP" & deltaAICc == 0) %>% 
+  dplyr::filter(., deltaAICc == 0) %>% 
   distinct() %>%
@@
 
+Considering just focusing on BIC because of JMP's paper, and also in this specific case, it provides less competing models for each individual
+```{r}
+# Table for BIC and AIC only
+
+model_comp_IC %>% 
+  dplyr::select(data, dist, BIC, AIC) %>% 
+  group_by(data) %>% 
+  mutate(delta_BIC_within = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_within = signif(AIC - min(AIC), digits = 2)) %>% 
+  ungroup() %>% 
+  mutate(delta_BIC_across = signif(BIC - min(BIC), digits = 2),
+         delta_AIC_across = signif(AIC - min(AIC), digits = 2)) %>% 
+  dplyr::select(., -data) %>% 
+  dplyr::select(dist, BIC, delta_BIC_within, delta_BIC_across, AIC, delta_AIC_within, delta_AIC_across)-> data_gt
+
+data_gt$delta_BIC_within[which(data_gt$dist == "Multidist")] <- NA
+data_gt$delta_AIC_within[which(data_gt$dist == "Multidist")] <- NA
+
+gt_tbl <- gt(data_gt, rowname_col = "dist")
+
+gt_tbl %>% 
+  tab_header(
+    title = md("**Model comparisons across levels**")
+  ) %>% 
+  tab_stubhead(label = "Model") %>% 
+  tab_row_group(
+    group = "Multidist",
+    rows = 9
+  ) %>% 
+  tab_row_group(
+    group = "Individual",
+    rows = 1:4
+  ) %>% 
+  tab_row_group(
+    group = "Population", 
+    rows = 5:8
+  ) %>% 
+  tab_spanner(
+    label = md("**BIC**"),
+    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
+  ) %>% 
+  tab_spanner(
+    label = md("**AIC**"),
+    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
+  ) %>% 
+  cols_label(
+    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
+    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
+    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
+    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
+  )
+
+```
+
+## Probability distribution parameters
+We can compare the different parameter values estimated for each distribution and their standard deviations.
+These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
+The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model.
+The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
+Overall, at the population level, the lognormal model had the lowest AIC and BIC values.
+
+```{r}
+
+plot_params <- function(prm_data, best_col){
+
+  prm_data%>% 
+  filter(., data == "POP") %>% 
+  dplyr::select(., estimate, sd) -> pop_est
+
+  title <- paste(prm_data$dist, prm_data$param)
+
+  if(best_col == "BIC"){
+    prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
+  }
+
+  if(best_col == "AIC"){
+    prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
+  }
+  return(plot)
+
+}
+
+```
+
+```{r fig.height=10, fig.width=12}
+
+nice_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params(., best_col = "BIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params(., best_col = "BIC") -> p6
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params(., best_col = "BIC") ->p7
+
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid
+
+nice_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params(., best_col = "AIC") +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params(., best_col = "AIC") -> p6
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params(., best_col = "AIC") ->p7
+
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid
+
+plot_grid(bic_grid, aic_grid, ncol = 2)
+
+```
 # References

### 2021-03-15 distributions_paper/rudolph_distributions_testing.Rmd
Playing with the other focus variables

--- 2021-03-15 distributions_paper/rudolph_distributions.Rmd
@@
 # focus <- "R2n"
- focus <- "mpm"
+# focus <- "mpm"
 # focus <- "m15"
@@
            focus = dist)
+  dlevy <- function(x, m, s) sqrt(s/(2*pi*(x-m)^3))*exp(-s/(2*(x-m)))
+  plevy <- function(q, m, s) 2*(1-pnorm(1/sqrt((q-m)/s)))
+  qlevy <- function(p, m, s) s/qnorm(1-p/2)^2+m
+  rlevy <- function(n, m, s) s/qnorm(1-runif(n)/2)^2+m
+  fitlevy <- fitdist(df$dist, "levy", start=list(m=0, s=0.5))
 
-  dist.used <- c("lnorm", "weibull", "cauchy")
-  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
-  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
-  kpars <- c(2, 2, 2, 2, 2, 2)
+  dist.used <- c("lnorm", "weibull", "cauchy", "levy")
+  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale", "location" , "scale")
+  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy", "levy", "levy")
+  kpars <- c(2, 2, 2, 2, 2, 2, 2, 2)
 }
@@
 
-pop <- lapply(dist.used, function(x){fitdist(df$focus, distr = x)})
+pop <- lapply(dist.used, function(x){
+  if(x == "levy"){
+    fitdist(df$focus, "levy", start=list(m=0, s=0.5))
+  }
+  else{
+    fitdist(df$focus, distr = x)
+  }
+})
 
@@
 
-  fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})
+  #fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})
+
+  fit <- lapply(dist.used, function(x){
+  if(x == "levy"){
+    fitdist(fit.df$focus, "levy", start=list(m=0, s=0.5))
+  }
+  else{
+    fitdist(fit.df$focus, distr = x)
+  }
+})
 
@@
          dist = str_replace(dist, "lnorm", "Lognormal"),
+         dist = str_replace(dist, "levy", "Levy"),
          data = str_replace(data, "pop", "POP")) %>% 
@@
 
-```{r fig.height=10, fig.width=12}
+```{r eval=FALSE, fig.height=10, fig.width=12}
 

### 2021-03-19 distributions_paper/r2n_rudolph_distributions.Rmd
distributions

--- 2021-03-15 distributions_paper/rudolph_distributions.Rmd
@@
 # focus <- "dist"
-# focus <- "R2n"
- focus <- "mpm"
+ focus <- "R2n"
+# focus <- "mpm"
 # focus <- "m15"
@@
 if(focus == "R2n"){
+
   df <- aracari_df %>%
+    mutate(R2n = lead(R2n)) %>% 
     dplyr::filter(R2n != 0) %>%
@@
     mutate(Bird_ID = paste0("B", id),
-           focus = sqrt(R2n))
+           tmin = dt/60)
 

### 2021-03-19 long_distance_paper/long_distance_paper.Rmd
distributions

---
title: Individual variation in animal movement and its consequences for long-distance
  seed dispersal patterns
author: "F. Javiera Rudolph"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-03-19 README.Rmd
added my logo to readme
added links
update Rmd for README

@@
 
-# aracari
+# aracari <img src="images/aracari.png" align="right" height="139" />
 
@@
 
-The goal of aracari is to ...
+Access the
 
+- [seed dispersal paper](https://javirudolph.github.io/aracari/paper/paper.html) and the [figures](https://javirudolph.github.io/aracari/paper/figures_tables.html)
+- [animal movement paper](https://javirudolph.github.io/aracari/movement_paper/rudolph_ch2.html)  
+- [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)
+
+---
 ## Installation
 
-You can install the released version of aracari from [CRAN](https://CRAN.R-project.org) with:
-
-``` r
-install.packages("aracari")
-```
-
-And the development version from [GitHub](https://github.com/) with:
+You can install the development version from [GitHub](https://github.com/) with:
 
@@
 ```
-## Example
-
-This is a basic example which shows you how to solve a common problem:
-
-```{r example}
-library(aracari)
-## basic example code
-```
-
-What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:
-
-```{r cars}
-summary(cars)
-```
-
-You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.
-
-You can also embed plots, for example:
-
-```{r pressure, echo = FALSE}
-plot(pressure)
-```
-
-In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

### 2021-03-19 README.Rmd
add a link

@@
 - [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)
+  - [info on the data](https://javirudolph.github.io/aracari/distributions_paper/format_raw_dat.html)
 

### 2021-03-24 movement_paper/rudolph_ch2.Rmd
distributions
Removed section went to distributions paper

@@
 # Introduction
-
-## Why do we study animal movement and what can it tell us?
-   Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment.
-The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how, and these questions can be answered at the scales of individuals or populations.
-A general framework for movement ecology that allows to link movement patterns and processes, starts with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
-The overall goal of studying movement seeks to find the linkages between the causes and mechanisms of animal movement, that result in spatiotemporal patterns that feedback to various ecological and evolutionary processes.
-
-## What is the importance of individual variation in animal movement?  
-  Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels.
-This focus on generality has driven to a lack of frameworks for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
-Although there have been recent calls for incorporating individual variation in movement [@snell2019consequences, @shaw2020causes] we still need to develop theory that explores different types of variation in movement patterns to understand its consequences across these levels.
-In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].
 
@@
 
+# Notes on March 17, 2021
+
+So, one of the main questions I have is that I am trying to decipher animal paths yet it seems like most animal movement ecologists are trying to figure out behavioral states out of movement data, which is not my focus.
+Reading the [@langrock2012flexible] paper.
+
 # References

### 2021-03-26 introduction/introduction.Rmd
Organizing intro files

---
title: "Introduction"
output:
  html_document:
    df_print: paged
bibliography: intro_refs.bib
csl: ecology-letters.csl
---

# Introduction

## What is dispersal?

## What is the difference with movement?

## What is the role of individual variation in dispersal and movement?

## How can we explore the role and importance of this variation?

## What statistical tools can we leverage to understand and predict the role of individual variation in dispersal and how does this extend to populations and ecosystems?

## The importance of characterizing dispersal in metapopulation models

### 2021-03-26 distributions_paper/rudolph_distributions.Rmd
Update to using mpm
Adding text

@@
 output:
+  word_document:
+    reference_docx: docx_ref.docx
   html_document:
     df_print: paged
-  word_document:
-    reference_docx: docx_ref.docx
 bibliography: aracari_refs.bib
@@
 ---
+
+# Introduction
+   Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment.
+The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how an animal moves, and these questions can be answered at the scales of individuals or populations.
+A general framework for movement ecology that allows to link movement patterns and processes, starts with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
+The overall goal of studying movement seeks to find the linkages between the causes and mechanisms of animal movement, that result in spatiotemporal patterns that feed back into various ecological and evolutionary processes.
+Some of these approaches involve separating different movement patterns into behavioral states, with each state having an associated set of parameters that determine that specific movement pattern[@langrock2012flexible].
+
+  Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels, with the simplest approach assuming model parameters are the same across individuals, known as 'complete pooling' [@langrock2012flexible].
+This focus on generality has driven to a lack of frameworks for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
+Some alternatives have been considered to incorporate individual variation with 'no pooling' or 'partial pooling' approaches, where each or some individuals have their own set of parameters [@patterson2009classifying, @jonsen2006robust], however a high number of parameters quickly limits applications to high levels of individual variation.
+Recent calls for incorporating individual variation in movement [@snell2019consequences, @shaw2020causes] have pushed for the need to develop theory that explores different types of variation in movement patterns to understand its consequences across ecological organizational levels.
+In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].
+
+**Could I find anything pre HMMs of SSMs? Wondering what people could do before? And wondering this because we have broken up tracking periods, not continuous ones**  
+Seems like I need to focus more on random walks
+
+Assume weibull distributions for step length and wrapped cauchy distributions for the turning angles [@langrock2012flexible], but they tried Gamma and von Mises, respectively, but got outperformed by AIC.
+Used negative binomial for the state dwell times.
+
+# Methods
+Describe the data collection from the animov outline. 
+Add a section that describes the limitations for this telemetry data. 
+From book chapter: Attached radio-transmitters at the base of the central tail feathers. Toucan locations measured by triangulation using receivers and hand-held two-element Yagi antennas. 
+Tracking periods laster 4-5 hours with individual birds located every 15 minutes.
+The 15 minute interval to ensure locations within the time frame of seed passage or regurgitation, which are expected to be longer than 15 minutes.
+
+"Location accuracy using radio telemetry may be reduced in tropical forests...
+conservative distance categories of 100-m increments to beteter represent precision.
+Time categories: 15, 30, 60, 90 minutes.
+Then calculated probability of movements made within each distance category within each time category, summed accross each time category to give a final probability for each distance category."
+
+"Distances travelled per movement bout ranged from 0 to >2000m.
+Strong leptokurtic distributions of movements with most being <300m.
+Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)
+
+From each of the locations for the twelve individuals, we calculated turning angles (in radians) between subsequent directions, and the associated Euclidean step lengths in meters.
+
+Evaluating models with their individual-specific counterparts, using AIC or BIC. In individual-specific models the AIC results from the joint likelihood of the individual-specific models.
+
+Consider incorporating NAs for missed observations so we keep the regular 15 minute time interval.
 
@@
 
-### I'll go first with just the distances between locations, might switch to net displacement or net squared displacement later. 
+### MPM: meters per minute
+Due to the variation in time between consecutive locations, we scaled the step lengths to displacement in one minute.
 **Visualize the variation and distribution of these distances between locations**

### 2021-03-27 distributions_paper/rudolph_distributions.Rmd
adding new source
Text developments.

@@
 Used negative binomial for the state dwell times.
+
+Random walks used broadly in biology to characterize animal and cell movement.
+Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions.
+[@codling2008random]
+- IDEA: so maybe use these distributions for the angles.
+We might see that there is not much difference in angle movement across individuals?
+They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances.
+- Also might be intriguing to incorporate the time as a set of multiple random walks?
+or repeats the velocity value for that number of minutes.
+Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
+  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
+  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$).
+Hence, turning events occur as a Poisson process with rate $\lambda$.
+**This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
+    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose.
+So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data.
+
+As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
 

### 2021-03-29 distributions_paper/rudolph_distributions.Rmd
Paragraph of methods

@@
 So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data.
+    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$
 
@@
 # Methods
+
+We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
+Previous studies used radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
+Over a period of four years, from 2001 to 2005, *P.
+pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central trail feathers [@holbrook2011home].
+Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
+It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and for each subsequent set of locations we calculated turning angles (in radians), and the associated Euclidean step lengths in meters.
+We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded.
+This gave us a total of **600ish?** data points for angles and velocities.
+
 Describe the data collection from the animov outline. 
@@
 Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)
-
-From each of the locations for the twelve individuals, we calculated turning angles (in radians) between subsequent directions, and the associated Euclidean step lengths in meters.
 

### 2021-03-29 distributions_paper/rudolph_distributions.Rmd
Add text

@@
    Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment.
-The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how an animal moves, and these questions can be answered at the scales of individuals or populations.
-A general framework for movement ecology that allows to link movement patterns and processes, starts with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
-The overall goal of studying movement seeks to find the linkages between the causes and mechanisms of animal movement, that result in spatiotemporal patterns that feed back into various ecological and evolutionary processes.
+The study of animal movement tends to focus on four basic mechanistic questions: the why, when, where, and how an animal moves, and these questions can be answered at the scale of individuals or populations.
+A general framework for movement ecology is needed to link movement patterns and processes.
+Such a framework would start with a focus on movement itself and the individual's internal state, navigation capacity, motion capacity, and responses to external factors [@nathan2008movement].
+The overall goal of studying movement is to find the linkages between the causes and mechanisms of animal movement, that explain spatiotemporal patterns that then feed back into various ecological and evolutionary processes.
 Some of these approaches involve separating different movement patterns into behavioral states, with each state having an associated set of parameters that determine that specific movement pattern[@langrock2012flexible].
+Other approaches have focused on segmenting movement patterns, again in an attempt to associate specific types of movement to underlying behaviors or fine-scale environmental influences (Getz citations, Morales, more focus on the random walk models, Patterson2008).
+*Indeed, animal movement has consequences.
+Such consequences might influence species interactions, ecological function, and vital demographic processes (survival, reproduction, dispersal) that can result in population impacts and evolutionary change (?).*
 
   Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels, with the simplest approach assuming model parameters are the same across individuals, known as 'complete pooling' [@langrock2012flexible].
-This focus on generality has driven to a lack of frameworks for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
+This focus on generality has driven to *a lack of frameworks* for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
 Some alternatives have been considered to incorporate individual variation with 'no pooling' or 'partial pooling' approaches, where each or some individuals have their own set of parameters [@patterson2009classifying, @jonsen2006robust], however a high number of parameters quickly limits applications to high levels of individual variation.
@@
 We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
-Previous studies used radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
+We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
 Over a period of four years, from 2001 to 2005, *P.
-pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central trail feathers [@holbrook2011home].
+pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home].
 Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
+Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
 It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
-For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and for each subsequent set of locations we calculated turning angles (in radians), and the associated Euclidean step lengths in meters.
+For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions.
 We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded.
-This gave us a total of **600ish?** data points for angles and velocities.
-
-Describe the data collection from the animov outline. 
-Add a section that describes the limitations for this telemetry data. 
-From book chapter: Attached radio-transmitters at the base of the central tail feathers. Toucan locations measured by triangulation using receivers and hand-held two-element Yagi antennas. 
-Tracking periods laster 4-5 hours with individual birds located every 15 minutes.
-The 15 minute interval to ensure locations within the time frame of seed passage or regurgitation, which are expected to be longer than 15 minutes.
+This gave us a total of **600ish?** data points for turning angles and velocities.
 
@@
 Strong leptokurtic distributions of movements with most being <300m.
-Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)
+Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)" *this is a corresponding velocity of `r 3665/30` meters per minute.
 
@@
 # knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
+                      eval=FALSE,
+                      echo = FALSE)
+
 ```

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
Adding more text and reference

@@
     - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$
+  - Pg11. A correlated random walk, CRW, consisting of a series of independet draws from a step length PDF and a turning angle PDF for each step, a first order markov process.
+    - using mean square displacement. The effect of step length variability on MSD can be quite significant.
+    - MSD being of interest to ecologists due to its relation with the diffusion coefficient D. equations 2.13 and 2.14
+** Should write a conclusion about this paper**
+
+# Kareiva Shigesada paper [@kareiva1983analyzing]
+
+We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions.
+Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.
 
@@
 "Location accuracy using radio telemetry may be reduced in tropical forests...
-conservative distance categories of 100-m increments to beteter represent precision.
+conservative distance categories of 100-m increments to better represent precision.
 Time categories: 15, 30, 60, 90 minutes.
-Then calculated probability of movements made within each distance category within each time category, summed accross each time category to give a final probability for each distance category."
+Then calculated probability of movements made within each distance category within each time category, summed across each time category to give a final probability for each distance category."
 

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
More intro draaft

@@
 Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.
+Unlike other studies which focus on deciphering the underlying behaviors from animal movement data, our focus was to uncover potential differences between individuals and how these differences can be obscured when modeling population-level animal movement.
+
+"We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
+However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data.
+In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events."
+
+A simple correlated random walk, which involves a directional correlation between successive step movement (coddling2008)
 

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
Test to use mpm only for 15 min intervals. Still get error if trying to use full distances instead of velocities

@@
 
+[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle. 
+*Would be interesting to add a figure with what I am actually analyzing.
+So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval.
+Or we could just multiply everything?
+So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*
+
 "We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
@@
 In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events."
+
+probabilistic rules of movement.
 
@@
 
+aracari_df %>% 
+  mutate(tmin = dt/60,
+         mpm = dist/tmin) %>% 
+  drop_na(tmin) %>% 
+  filter(tmin == 15) %>% 
+  group_by(id) %>% 
+  tally() %>% 
+  filter(n >=20)
+
+```
+
+```{r}
+focus <- "dist15"
+
+df <- aracari_df %>%
+  mutate(tmin = dt/60,
+         mpm = dist/tmin,
+         Bird_ID = paste0("B", id),
+         focus = mpm) %>% 
+  drop_na(tmin) %>% 
+  filter(tmin == 15) %>% 
+  dplyr::filter(dist != 0) %>% 
+  group_by(id) %>%
+  filter(., n() >= 20) %>%
+  ungroup()
+
+  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
+  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
+  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+  kpars <- c(1, 2, 2, 2, 2, 2, 2)
 ```

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
explore angles

@@
 [@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle.
+Using square displacement instead of linear displacement, because it's expectation can be calculated from turning angles and step lengths.
+Assume that the length of each move and the turning angle are independent random variables, each with its own probability density.
+Assume that a series of moves can be represented by random draws from these probability densities, and since each random draw is independent from the preceding ones, the random draw process is a first order markov chain.
+The result is a correlated random walk, and the distribution g(theta) gives a measure of the degree to which the angles of movement are correlated.
 *Would be interesting to add a figure with what I am actually analyzing.
@@
 However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data.
-In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events."
+In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events." Written by Javi
 
@@
   kpars <- c(1, 2, 2, 2, 2, 2, 2)
+```
+
+```{r}
+df %>% 
+  ggplot(., aes(x = abs.angle)) +
+  geom_histogram() +
+  facet_wrap(~Bird_ID)
+```
+
+```{r}
+df %>%
+  drop_na(rel.angle) %>%
+  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
+                          rel.angle * 180/pi + 360)) %>%
+  ggplot(., aes(x = d.angle)) +
+  #facet_wrap(~id) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none")
 ```

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
finished draft of introduction

@@
 The overall goal of studying movement is to find the linkages between the causes and mechanisms of animal movement, that explain spatiotemporal patterns that then feed back into various ecological and evolutionary processes.
-Some of these approaches involve separating different movement patterns into behavioral states, with each state having an associated set of parameters that determine that specific movement pattern[@langrock2012flexible].
-Other approaches have focused on segmenting movement patterns, again in an attempt to associate specific types of movement to underlying behaviors or fine-scale environmental influences (Getz citations, Morales, more focus on the random walk models, Patterson2008).
-*Indeed, animal movement has consequences.
-Such consequences might influence species interactions, ecological function, and vital demographic processes (survival, reproduction, dispersal) that can result in population impacts and evolutionary change (?).*
+Some of these approaches involve separating different movement patterns into states, with each state having an associated set of parameters that determine that specific movement pattern [@langrock2012flexible].
+These approaches segment movement patterns, in order to associate specific types of movement to underlying behaviors or fine-scale environmental influences (Getz citations, Morales, more focus on the random walk models, Patterson2008).
+Several of these approaches focus on the why and underlying processes that drive animal movement, whether that is an animal's internal state or responses to their environment.
 
-  Although there is variation in animal movement at the individual scale, the general focus has been on understanding the typical movement patterns, built around average measures at population levels, with the simplest approach assuming model parameters are the same across individuals, known as 'complete pooling' [@langrock2012flexible].
-This focus on generality has driven to *a lack of frameworks* for understanding variation, how it is maintained, and the consequences of this variation across populations, communities, and ecosystems.
-Some alternatives have been considered to incorporate individual variation with 'no pooling' or 'partial pooling' approaches, where each or some individuals have their own set of parameters [@patterson2009classifying, @jonsen2006robust], however a high number of parameters quickly limits applications to high levels of individual variation.
-Recent calls for incorporating individual variation in movement [@snell2019consequences, @shaw2020causes] have pushed for the need to develop theory that explores different types of variation in movement patterns to understand its consequences across ecological organizational levels.
+   Random walks have been used broadly in biology to characterize animal movement, and increasing levels of complexity can be incorporated by using multiple random walks, continuous time or different levels of correlation between turning angles [@codling2008random; @morales2004extracting].
+More recent developments have focused on implementing higher order Markov processes through state-space models, which provide a probabilistic framework that allows for prediction of future states of a system based from previous states, by coupling an observation model with an underlying mechanistic model.
+When extending this framework to movement ecology, we understand that the process model provides the mechanism for movement across space and time, and the observation model is related to the sampling process.
+In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state].
+In general, state-space models are used to identify different states, or behavioral states, that determine different movement patterns associated to step length and turning angle.
+And some of the main questions asked with this approach are related to identifying these different states, or behavioral state-switching, from time series data on location tracking.
+
+   Although I have mostly described approaches used to understand why movement happens, animal movement also has consequences, which might influence species interactions, ecological function, and vital demographic processes (such as survival, reproduction, or dispersal of other species) and thus result in population or regional level impacts.
+A clear example of the consequences of animal movement on other species involves animal-mediated seed dispersal or pollination, impacting a plant's spatial population dynamics.The specific case of seed dispersal is interesting because of the different levels and interactions happening.
+At the individual level, we focus on an individual bird consuming fruit and dispersing the seeds of the tree.
+How this particular individual moves across the landscape directly affects the dispersal for that specific tree and other trees from which it consumes fruit.
+At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting, or even smaller scale variation related to different states, such as foraging or resting.
+Interspecific interactions come at play as multiple species find themselves together feeding from the same trees, and thus competing for these resources, while at the same time intraspecific interactions due to social behavior broadly determine general movement patterns for animals restricted within family home ranges.
+From the plant's perspective, the variation in movement patterns across all dispersers will determine eventual plant population spatial spread.
+
+  Specifically in the context of seed dispersal ecology, the general focus has been on understanding how the typical movement patterns, built around average measures at population levels, can influence plant population spread and seed dispersal [sources].
+Animal movement can be modeled with a simple diffusion process or a random walk [@jones2017closing; @levey2005effects], with the simplest approach assuming model parameters are the same across individuals, something known as 'complete pooling' [@langrock2012flexible].
+This focus on generality has driven to a lack of frameworks for understanding how variation in animal movement is maintained, and the consequences of this variation across populations and communities.
+From the animal movement perspective, some alternatives have been considered to incorporate individual variation with 'no pooling' or 'partial pooling' approaches, where each or some individuals have their own set of parameters [@patterson2009classifying, @jonsen2006robust], however a high number of parameters quickly limits applications to high levels of individual variation.
+Recent calls for incorporating individual variation in movement and their consequences to seed dispersal or even pathogen spread [@snell2019consequences, @shaw2020causes] have pushed for the need to develop theory that explores different types of variation in movement patterns to understand its consequences across ecological organizational levels.
 In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].
+
+  We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions.
+Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.A simple correlated random walk, which involves a directional correlation between successive step movement [@codling2008random].
+Unlike other studies which focus on deciphering the underlying behaviors from animal movement data, our focus was to uncover potential differences between individuals and how these differences can be obscured when modeling population-level animal movement.
+We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
+However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data.
+In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events.
+
+# Methods
 
@@
 
-# Kareiva Shigesada paper [@kareiva1983analyzing]
-
-We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions.
-Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.
-Unlike other studies which focus on deciphering the underlying behaviors from animal movement data, our focus was to uncover potential differences between individuals and how these differences can be obscured when modeling population-level animal movement.
-
 [@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle.
@@
 
-"We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
-However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data.
-In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events." Written by Javi
-
 probabilistic rules of movement.
 
-A simple correlated random walk, which involves a directional correlation between successive step movement (coddling2008)
-
 As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
-
-# Methods
 
@@
 Consider incorporating NAs for missed observations so we keep the regular 15 minute time interval.
+
+$$AIC{_{indlevel}} = 2 \cdot \sum \left ( number parameters \right ) + 2 \cdot \sum \left ( negative log likelihood \right )$$
+
+$$ AICc{_{indlevel}} =  AIC{_{indlevel}} + (2 \cdot \sum{nparams}  \cdot \left(\sum{nparams}+1\right)/\left(\sum{observations} - \left(\sum{nparams} - 1\right)\right)$$
+
+$$BIC_{indlevel} = \ln{\sum observations} \cdot \sum{number parameters} + 2\cdot \sum {negative log likelihood}$$
 
@@
   drop_na(tmin) %>% 
-  filter(tmin == 15) %>% 
+  filter(tmin == 60) %>% 
   group_by(id) %>% 

### 2021-03-31 movement_paper/rudolph_ch2.Rmd
finished draft of introduction

@@
 ## How does this relate to mutualisms and long-distance movements?
-  The specific case of seed dispersal is interesting because of the different levels and interactions happening.
-At the individual level, we focus on an individual bird consuming fruit and dispersing the seeds of the tree.
-How this particular individual moves across the landscape directly affects the dispersal for that specific tree and other trees from which it consumes fruit.
-At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting, or even smaller scale variation related to different states, such as foraging or resting.
-Interspecific interactions come at play as multiple species find themselves together feeding from the same tress, and thus competing for these resources, while at the same time intraspecific interactions due to social behavior broadly determine general movement patterns.
-From the plant's perspective, the variation in movement patterns across all dispersers will determine eventual plant population spatial spread and success.
    Individuals will vary in their distances traveled while foraging or searching, directly influencing seed dispersal for the plant.
@@
 
-## Overview of state-space models for movement  
-  State-space models provide a probabilistic framework that allow for prediction of future states of a system based from previous states, by coupling an observation model with an underlying mechanistic model.
-When extending this framework to movement ecology, we understand that the process model provides the mechanism for movement across space and time, and the observation model is related to the sampling process.
-In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state].
-In general, state-space models are used to identify different states, or behavioral states, that determine different movement patterns associated to step length and turning angle.
-And some of the main questions asked with this approach are related to identifying these different states, or behavioral state-switching, from time series data on location tracking.HMMs can be used to categorize this movement data into behavioral states, and link it to foraging or mating activity, as an example.
-
   The moveHMM package allows for fitting hmm models to different time series, which can come from different individuals, assuming that all individuals share the same movement models, meaning the same distributions and parameters for step length and angle.

### 2021-03-31 distributions_paper/rudolph_distributions.Rmd
moved around. Intro draft ready. Methods first paragraph

@@
 
+We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
+We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
+Over a period of four years, from 2001 to 2005, *P.
+pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home].
+Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
+Further details on field methods can be found in Holbrook [-@holbrook2011home].
+It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+<span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions.
+We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded.
+This gave us a total of **600ish?** data points for turning angles and velocities.red</span>
+
 **Could I find anything pre HMMs of SSMs? Wondering what people could do before? And wondering this because we have broken up tracking periods, not continuous ones**  
@@
 As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
-
-We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
-We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
-Over a period of four years, from 2001 to 2005, *P.
-pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home].
-Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
-Further details on field methods can be found in Holbrook [-@holbrook_home_2011].
-It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
-For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions.
-We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded.
-This gave us a total of **600ish?** data points for turning angles and velocities.
 

### 2021-04-01 distributions_paper/rudolph_distributions.Rmd
eval r chunks for results

@@
 knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
-                      eval=FALSE,
+                      #eval=FALSE,
                       echo = FALSE)
@@
 
-```{r}
+```{r eval=FALSE}
 focus <- "dist15"
@@
 
-```{r}
+```{r eval=FALSE}
 df %>% 
@@
 
-```{r}
+```{r eval=FALSE}
 df %>%
@@
 \newpage
-# Questions  
-* What is the distribution of distances between consecutive recorded locations? 
-* Are there differences between individuals or can we use the same distribution to describe these distances between two locations?
-
-The reasoning behind this, is that distances between locations can be used later on to describe variation in step length when simulating animal movement under simple models such as random walk.
 
@@
 # Fit distribution
-Useful resource to use the package [fitdistrplus](https://cran.r-project.org/web/packages/fitdistrplus/vignettes/FAQ.html)
-Also check [this](https://stackoverflow.com/questions/37152482/power-law-fitted-by-fitdistr-function-in-package-fitdistrplus). Should I do the opimization by hand?
 
@@
 
-So, for each individual, which is the best fitting distribution, based on AIC or BIC?
-This is the distribution with the lowest AIC or BIC score for each individual.
-These are basically the distributions that will be used for the mixed distribution model later on.
-
 ```{r}
@@
   rename(Individual = data,
-            `Best model` = agree)
+            `Best model` = agree) -> best_model
+
+knitr::kable(best_model)
 # 
@@
     delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
-  )
+  ) -> gt_table_bic
 
+gtsave(gt_table_bic, "aic_bic_table.png")  
+```
+
+```{r eval=FALSE}
+knitr::include_graphics("aic_bic_table.png")
 ```
@@
 ```
-# References
+
+#References

### 2021-04-05 distributions_paper/rudolph_distributions.Rmd
Editing methods

@@
 Further details on field methods can be found in Holbrook [-@holbrook2011home].
-It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+It is important to note that these methods did not track all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+From the relocation data, we calculated animal trajectories by considering discrete steps between successive relocations of each animal [@turchin1998quantitative], quantifying their turning angle after each movement, estimating the Euclidean distance between successive relocations, and estimating the velocity for each segment as the displacement distance divided by the length of the time interval.
+We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate the descriptive parameters for each trajectory, such as turning angles and net squared displacement.
+
+# Results  
+The majority of trajectories obtained were regular, with 15 minute time lags between successive relocations, however, some relocations were gathered at different time intervals, making them irregular.
+To analyze all trajectories and compare their descriptive parameters, we decided to work under a velocity-based framework.
+
 <span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions.
@@
 When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models.
+We should use 4 for BIC and 3 for AIC.
+Look for the paper Taper Ponciano 2016.
 ```{r fig.width=12, fig.height=4}

### 2021-04-13 distributions_paper/rudolph_distributions.Rmd
updates to the introduction

@@
 # Introduction
+
 Movement is a fundamental ecological process, critical to an animal's biology and it's interactions with the environment.
@@
 The overall goal of studying movement is to find the linkages between the causes and mechanisms of animal movement, that explain spatiotemporal patterns that then feed back into various ecological and evolutionary processes.
-Some of these approaches involve separating different movement patterns into states, with each state having an associated set of parameters that determine that specific movement pattern [@langrock2012flexible].
-These approaches segment movement patterns, in order to associate specific types of movement to underlying behaviors or fine-scale environmental influences (Getz citations, Morales, more focus on the random walk models, Patterson2008).
-Several of these approaches focus on the why and underlying processes that drive animal movement, whether that is an animal's internal state or responses to their environment.
+However, we can also focus on the effects and consequences that different movement patterns can have over species interactions and other ecological processes.
 
-   Random walks have been used broadly in biology to characterize animal movement, and increasing levels of complexity can be incorporated by using multiple random walks, continuous time or different levels of correlation between turning angles [@codling2008random; @morales2004extracting].
-More recent developments have focused on implementing higher order Markov processes through state-space models, which provide a probabilistic framework that allows for prediction of future states of a system based from previous states, by coupling an observation model with an underlying mechanistic model.
-When extending this framework to movement ecology, we understand that the process model provides the mechanism for movement across space and time, and the observation model is related to the sampling process.
-In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state].
-In general, state-space models are used to identify different states, or behavioral states, that determine different movement patterns associated to step length and turning angle.
-And some of the main questions asked with this approach are related to identifying these different states, or behavioral state-switching, from time series data on location tracking.
+Random walks have been used broadly in biology to model movement of animals and microorganisms, starting with the simplest models of movement using uncorrelated and unbiased random walks [@codling2008random].
+These movement models show no preference in direction and movement at each step is completely independent of the direction taken in previous movements.
+Extensions of simple random walk processes are regularly used to accommodate for more complex behaviors or to include drift.
+Some of these extensions involve the use of correlated random walks, which incorporate a correlation between directions in successive movements, biased random walks, which incorporate a directional bias, or even building movement models as mixtures of random walks to account for more complex behaviors [@morales2004extracting].
+Modeling approaches using random walks generally assume a homogeneous environment and behaviors that don't drastically change the movement pattern [@kareiva1983analyzing].
+A simple random walk approximates displacements by connecting a series of straight lines, and can summarize animal movement based on parameters for movement length and turning angle, or the use of net squared displacement.
+Connecting theoretical movement models based on correlated random walks to data had often relied on the use of these parameters or displacement measures [@turchin1998quantitative], but more current and efficient approaches have used likelihood-based techniques to estimate parameters by fitting a discrete approximation of the model directly to the location data [@jonsen2003meta].
 
-   Although I have mostly described approaches used to understand why movement happens, animal movement also has consequences, which might influence species interactions, ecological function, and vital demographic processes (such as survival, reproduction, or dispersal of other species) and thus result in population or regional level impacts.
-A clear example of the consequences of animal movement on other species involves animal-mediated seed dispersal or pollination, impacting a plant's spatial population dynamics.The specific case of seed dispersal is interesting because of the different levels and interactions happening.
-At the individual level, we focus on an individual bird consuming fruit and dispersing the seeds of the tree.
-How this particular individual moves across the landscape directly affects the dispersal for that specific tree and other trees from which it consumes fruit.
-At the same time, that individual has intra-individual variation in movement patterns associated to specific events in that individual's lifetime, such as breeding and nesting, or even smaller scale variation related to different states, such as foraging or resting.
-Interspecific interactions come at play as multiple species find themselves together feeding from the same trees, and thus competing for these resources, while at the same time intraspecific interactions due to social behavior broadly determine general movement patterns for animals restricted within family home ranges.
-From the plant's perspective, the variation in movement patterns across all dispersers will determine eventual plant population spatial spread.
-
-  Specifically in the context of seed dispersal ecology, the general focus has been on understanding how the typical movement patterns, built around average measures at population levels, can influence plant population spread and seed dispersal [sources].
+   In the context of species interactions and the consequences of animal movement to dispersal, the general focus has been on understanding how the typical movement patterns, built around average measures at population levels, can influence plant population spread [@levey2005effects], seed dispersal [@jones2017closing, @holbrook2007using], pollen dispersal [@garcia2007contemporary], and even pathogens [@shaw2017vector].
 Animal movement can be modeled with a simple diffusion process or a random walk [@jones2017closing; @levey2005effects], with the simplest approach assuming model parameters are the same across individuals, something known as 'complete pooling' [@langrock2012flexible].
@@
 From the animal movement perspective, some alternatives have been considered to incorporate individual variation with 'no pooling' or 'partial pooling' approaches, where each or some individuals have their own set of parameters [@patterson2009classifying, @jonsen2006robust], however a high number of parameters quickly limits applications to high levels of individual variation.
+The decision to pool data or not may also come from the modeling framework chosen, as frameworks that allow for random effects may have a better structure to incorporate this variation than simpler frameworks.
 Recent calls for incorporating individual variation in movement and their consequences to seed dispersal or even pathogen spread [@snell2019consequences, @shaw2020causes] have pushed for the need to develop theory that explores different types of variation in movement patterns to understand its consequences across ecological organizational levels.
-In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment [@shaw2020causes].
+In particular, when considering species interactions, incorporating individual variation becomes essential to understand how positive or negative feedback loops play into the maintenance of variation in movement as individuals respond to external factors in their environment.
 
   We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions.
-Following the methods of Kareiva and Shigesada [-@kareiva1983analyzing], we assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.A simple correlated random walk, which involves a directional correlation between successive step movement [@codling2008random].
+We assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.
 Unlike other studies which focus on deciphering the underlying behaviors from animal movement data, our focus was to uncover potential differences between individuals and how these differences can be obscured when modeling population-level animal movement.
 We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
-However, our goal in this study was to use a simpler model and focus on potential differences when analyzing complete pooling versus no pooling data.
-In the context of animal-mediated seed dispersal, understanding these indivdiual level differences can help us describe and characterize the implications that different animals may have over spatial distributions of plant populations, and thus identify potential dispersers with higher or more importance, particularly when associated to long-distance seed dispersal events.
+However, our goal in this study was to use a simpler model and focus on potential differences that arise when comparing data from multiple individuals under frameworks that completely pool data in contrast to those that don't.
 
 # Methods
+
+## Animal movement model
+
+As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
+
+## Description of the models considered
+
+## Specific case with telemetry data
 
@@
 It is important to note that these methods did not track all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+Due to the nature of the data, and the irregular time lags between two consecutive locations, previous work calculated movement rate for each individual in order to take advantage of all the data despite variable time intervals [see Table 1 in @holbrook2011home].
+Movement rates were calculated as the displacement in meters over the total length of the tracking period in minutes, where the tracking period was defined as the total active tracking time for a bird over the season when the data was collected.
+In other words, the movement rate could be defined as the average velocity of the animal over the entire tracking period, and thus there is one movement rate value associated to each individual bird.
+In our case, we wanted to extend the use of the telemetry data and use all locations in a modeling framework.
 From the relocation data, we calculated animal trajectories by considering discrete steps between successive relocations of each animal [@turchin1998quantitative], quantifying their turning angle after each movement, estimating the Euclidean distance between successive relocations, and estimating the velocity for each segment as the displacement distance divided by the length of the time interval.
-We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate the descriptive parameters for each trajectory, such as turning angles and net squared displacement.
+We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate other descriptive parameters for each trajectory, such as turning angles and net squared displacement.
 
@@
 This gave us a total of **600ish?** data points for turning angles and velocities.red</span>
+
+What do we consider a trajectory?
+The path followed by consecutive relocations during a tracking session.
+The tracking session for this data is the 4-5 hour period each day that they follow the bird.
+Then, the number of relocations for each trajectory varies from one to 26, with a mean of 4 relocations.
+This is a limitation of the data, since it's not easy to characterize a full trajectory of movement with such a small number of relocations in a trajectory.
+
+Dealing with the issue of autocorrelation in this case: what does that mean? Or we just assume each step is independent from the others. Think I saw this in the Kareiva Shigesada paper. 
+```{r eval=FALSE}
+# For this to run I need to move the load of data and such higher up
+aracari_df %>%
+  group_by(id, burst) %>% 
+  tally() -> relocs
+
+# Having a minimum number of relocations for "time series analysis" or something, fitting.
+relocs %>% 
+  filter(n >= 5) %>% 
+  distinct(id)
+
+relocs %>% 
+  ggplot(., aes(x = n, fill = id)) +
+  geom_histogram()
+summary(relocs$n)
+```
+
+```{r eval=FALSE}
+aracari_df %>% 
+  filter(R2n >0) %>% 
+  ggplot(., aes(x = R2n)) +
+  geom_histogram() +
+  facet_wrap(~id)
+```
 
@@
 
-As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
-
 "Location accuracy using radio telemetry may be reduced in tropical forests...
@@
 knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
-                      #eval=FALSE,
+                      eval=FALSE,
                       echo = FALSE)
@@
   filter(n >=20)
+
+```
+
+```{r eval=FALSE}
+# Table replicating results from Holbrook 2011, movement rates
+# The values are close, but not the same, so I don't know how Kimberly estimated her movement rates
+
+aracari_df %>%
+  drop_na(dist) %>% 
+  mutate(mpm = dist/(dt/60)) %>% 
+  group_by(id) %>% 
+  summarise(movrate = mean(mpm)) %>% 
+  ungroup() %>% 
+  summarise(mean = mean(movrate),
+            sd = sd(movrate),
+            median = median(movrate),
+            range = range(movrate))
+
+aracari_df %>%
+  drop_na(dist) %>% 
+  group_by(id) %>% 
+  summarise(movrate = sum(dist)/sum(dt/60)) %>% 
+  ungroup() %>% 
+  summarise(mean = mean(movrate),
+            sd = sd(movrate),
+            median = median(movrate),
+            range = range(movrate))
 

### 2021-04-15 distributions_paper/rudolph_distributions.Rmd
Progress with methods

@@
 
-  We focus here on developing a process to analyze animal movement sequences based on movement lengths, or step lengths, and turning angle probability distributions.
-We assume the movement is a correlated random walk and derive expected square displacements associated to a number of consecutive moves under various probability distribution models.
+Animal telemetry data are collected by determining an animal's location at various points in time.
+Many of the movement models used to analyze animal telemetry data rely on regular time intervals between locations [@jonsen2003meta; @jonsen2005robust].
+However, based on field methods, or environmental variables such as heavy cloud cover or dense forest, can make data collection at regular intervals difficult, and thus location data becomes more opportunistic and with irregular time intervals.
+Previous methods to analyze data under these irregular conditions have relied on interpolating, subsampling, or aggregating data during pre-processing in order to make it fit model assumptions[@johnson2008continuous].
+In this study, we propose the use of a model capable of handling irregular time intervals by considering movement as a stochastic process on a continuous time scale, and thus focus on the animal's instantaneous velocity rather than on its absolute displacements between locations.
+Using this continuous-time framework, we are able to estimate movement paths by integrating velocity functions.
+We also explore the effects of individual variation in speeds as a comparison between velocity probability density functions across different levels of data aggregation between individuals.
 Unlike other studies which focus on deciphering the underlying behaviors from animal movement data, our focus was to uncover potential differences between individuals and how these differences can be obscured when modeling population-level animal movement.
-We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in higher order markov processes show to be promising.
-However, our goal in this study was to use a simpler model and focus on potential differences that arise when comparing data from multiple individuals under frameworks that completely pool data in contrast to those that don't.
+We know these simple correlated random walks, or simple movement models might not be enough to describe net displacements under more complex processes, for which developments in state-space modeling frameworks show to be promising.
+However, our goal in this study was to use a simpler model that would adjust to irregular and sparse telemetry data, and focus on potential differences that arise when comparing data from multiple individuals under frameworks that completely pool data in contrast to those that don't.
+We illustrate the use of this model and the individual variation comparison by analyzing a telemetry data set of twelve many-banded aracari individuals, *Pteroglossus pluricinctus*.
 
@@
 
-## Animal movement model
+## Velocity-based continuous-time model
 
-As in other papers. Note that we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
+We developed an animal movement model with telemetry data in mind, thus we considered a movement trajectory as a series of consecutive recordings of an animal's location.
+To first set up the framework for a velocity-based model, we consider movement as the change in locations across two coordinates.
+We let $\mu(t)=[\mu_x(t), \mu_y(t)]'$ be the location of an individual at time $t$ in the coordinates $x$ and $y$.
+We establish $\boldsymbol{d}_{\Delta}(t) = \boldsymbol{\mu}(t+\Delta) - \boldsymbol{\mu}(t)$ as the difference in locations across both coordinates over $\Delta$ time units.
+The differential equation $d\boldsymbol{\mu}(t)=\boldsymbol{\nu}(t)dt$ represents the instantaneous velocity as $\Delta$ approaches zero under the assumption that $\boldsymbol\mu(t)$ is a continuous movement path [@johnson2008continuous].
+Although the bivariate velocity process $\boldsymbol\nu(t) = [\nu_x(t), \nu_y(t)]'$ could be considered as cross-correlated between the axes, these correlated velocities produce strange directed travel and thus velocity in each coordinate is considered to be an independent process [@johnson2008continuous].
+We decided instead, to focus on a velocity-based movement process using velocity scalars and turning angles.
+Under this framework, we define a scalar for instantaneous directionless velocity as $$\nu(t+\Delta) = \sqrt{(\mu_x(t+\Delta)-\mu_x(t))^2 + (\mu_y(t+\Delta) - \mu_y(t))^2}$$ and assume it to be a random variable with probability density $N \sim f(t|\boldsymbol\sigma)$ where $\boldsymbol\sigma$ represents the vector of parameters and determines the overall variability in velocity according to a specific probability density function $f(\boldsymbol\sigma)$.
+We assumed velocities to be independent of turning angles and chose to describe each with a separate probability density function, which is common practice when using movement lengths [@kareiva1983analyzing].
+We calculated the turning angle $\theta(t+\Delta)$ describing the turning direction of the animal at time $t+\Delta$ and assumed the distribution of angles along a continuous movement path to be distributed with probability density $g(\theta)$.
+For the specific case of a correlated random walk, the distribution of $g(\theta)$ can be used as a measure of correlation in the direction of movement, where if no correlation is present, the distribution is uniform [@kareiva1983analyzing].
+As in other papers, we adopt the convention of using upper case letters for random variables and lower case letters for possible numerical values of these random variables.
 
-## Description of the models considered
+Using this velocity process and turning angles, the continuous-time location process $\boldsymbol\mu(t)$ can be obtained by integrating over the velocity process [@johnson2008continuous]:
+$$\boldsymbol\mu(t) = \boldsymbol\mu(0) + \int_0^t\boldsymbol\nu(u)du$$
+where 
+$$\int_0^t\boldsymbol\nu(u)du =\int_0^t [\nu_x(u), \nu_y(u)]' du = \int_0^t [\sin(\theta_u), \cos(\theta_u)]' \cdot \nu(u)du$$
+This integral describes the location at time $t$ as the sum of steps determined by velocities in each direction plus a starting location at time $t=0$.
 
-## Specific case with telemetry data
+## Model formulations
+
+## Model evaluation using information criteria
+
+## Example: Many-banded aracari movement
 

### 2021-04-15 distributions_paper/rudolph_distributions.Rmd
Progress with results

@@
 
-## Model evaluation using information criteria
-
-## Example: Many-banded aracari movement
-
-We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
-We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
-Over a period of four years, from 2001 to 2005, *P.
-pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home].
-Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
-Further details on field methods can be found in Holbrook [-@holbrook2011home].
-It is important to note that these methods did not track all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
-Due to the nature of the data, and the irregular time lags between two consecutive locations, previous work calculated movement rate for each individual in order to take advantage of all the data despite variable time intervals [see Table 1 in @holbrook2011home].
-Movement rates were calculated as the displacement in meters over the total length of the tracking period in minutes, where the tracking period was defined as the total active tracking time for a bird over the season when the data was collected.
-In other words, the movement rate could be defined as the average velocity of the animal over the entire tracking period, and thus there is one movement rate value associated to each individual bird.
-In our case, we wanted to extend the use of the telemetry data and use all locations in a modeling framework.
-From the relocation data, we calculated animal trajectories by considering discrete steps between successive relocations of each animal [@turchin1998quantitative], quantifying their turning angle after each movement, estimating the Euclidean distance between successive relocations, and estimating the velocity for each segment as the displacement distance divided by the length of the time interval.
-We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate other descriptive parameters for each trajectory, such as turning angles and net squared displacement.
-
-# Results  
-The majority of trajectories obtained were regular, with 15 minute time lags between successive relocations, however, some relocations were gathered at different time intervals, making them irregular.
-To analyze all trajectories and compare their descriptive parameters, we decided to work under a velocity-based framework.
-
-<span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions.
-We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded.
-This gave us a total of **600ish?** data points for turning angles and velocities.red</span>
-
-What do we consider a trajectory?
-The path followed by consecutive relocations during a tracking session.
-The tracking session for this data is the 4-5 hour period each day that they follow the bird.
-Then, the number of relocations for each trajectory varies from one to 26, with a mean of 4 relocations.
-This is a limitation of the data, since it's not easy to characterize a full trajectory of movement with such a small number of relocations in a trajectory.
-
-Dealing with the issue of autocorrelation in this case: what does that mean? Or we just assume each step is independent from the others. Think I saw this in the Kareiva Shigesada paper. 
-```{r eval=FALSE}
-# For this to run I need to move the load of data and such higher up
-aracari_df %>%
-  group_by(id, burst) %>% 
-  tally() -> relocs
-
-# Having a minimum number of relocations for "time series analysis" or something, fitting.
-relocs %>% 
-  filter(n >= 5) %>% 
-  distinct(id)
-
-relocs %>% 
-  ggplot(., aes(x = n, fill = id)) +
-  geom_histogram()
-summary(relocs$n)
-```
-
-```{r eval=FALSE}
-aracari_df %>% 
-  filter(R2n >0) %>% 
-  ggplot(., aes(x = R2n)) +
-  geom_histogram() +
-  facet_wrap(~id)
-```
-
-**Could I find anything pre HMMs of SSMs? Wondering what people could do before? And wondering this because we have broken up tracking periods, not continuous ones**  
-Seems like I need to focus more on random walks
-
 Assume weibull distributions for step length and wrapped cauchy distributions for the turning angles [@langrock2012flexible], but they tried Gamma and von Mises, respectively, but got outperformed by AIC.
@@
 
-Consider incorporating NAs for missed observations so we keep the regular 15 minute time interval.
+## Model evaluation using information criteria
 
@@
 
+# Example: Many-banded aracari movement
+
+We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador.
+We used previously collected data from studies using radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin].
+Over a period of four years, from 2001 to 2005, *P.
+pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central tail feathers [@holbrook2011home].
+Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes.
+Further details on field methods can be found in Holbrook [-@holbrook2011home].
+It is important to note that these methods did not track all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15.
+Due to the nature of the data, and the irregular time lags between two consecutive locations, previous work calculated movement rate for each individual in order to take advantage of all the data despite variable time intervals [see Table 1 in @holbrook2011home].
+Movement rates were calculated as the displacement in meters over the total length of the tracking period in minutes, where the tracking period was defined as the total active tracking time for a bird over the season when the data was collected.
+In other words, the movement rate could be defined as the average velocity of the animal over the entire tracking period, and thus there is one movement rate value associated to each individual bird.
+In our case, we wanted to extend the use of the telemetry data and use all locations in a modeling framework.
+From the relocation data, we calculated animal trajectories by considering discrete steps between successive relocations of each animal [@turchin1998quantitative], quantifying their turning angle after each movement, estimating the Euclidean distance between successive relocations, and estimating the velocity for each segment as the displacement distance divided by the length of the time interval.
+We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate other descriptive parameters for each trajectory, such as turning angles and net squared displacement.
+
 ```{r setup, include=FALSE}
@@
 
-```{r eval=FALSE}
-# Which individuals will we conside? Need at least a certain number of data points to fit distributions
-# Don't remove any yet, just make sure you make it clear how many data points you have for each
+```{r}
+aracari_df %>% 
+  mutate(nu = dist/(dt/60)) %>% 
+  dplyr::select(id, nu, rel.angle, dt) %>% 
+  drop_na(nu) %>% 
+  mutate(B_id = paste0("B", id))-> df
 
-aracari_df %>% 
-  dplyr::filter(dist != 0) %>% 
-  group_by(id) %>% 
-  tally()
-
-aracari_df %>% 
-  mutate(tmin = dt/60,
-         mpm = dist/tmin) %>% 
-  drop_na(tmin) %>% 
-  filter(tmin == 60) %>% 
+# Select individuals with at least 30 data points for velocity
+df %>% 
+  dplyr::select(id, nu) %>% 
   group_by(id) %>% 
   tally() %>% 
-  filter(n >=20)
+  filter(., n >= 30) %>% 
+  dplyr::pull(id) -> nu_id
+
+# Select individuals with 20 or 30? angles
+df %>% 
+  dplyr::select(id, rel.angle, dt) %>%
+  mutate(dt = dt/60) %>% 
+  drop_na(rel.angle) %>% 
+  #filter(., dt == 15) %>% 
+  group_by(id) %>% 
+  tally() %>% 
+  filter(., n >= 25) %>% 
+  dplyr::pull(id) -> angle_id
 
@@
 
-```{r eval=FALSE}
-focus <- "dist15"
+```{r}
 
-df <- aracari_df %>%
-  mutate(tmin = dt/60,
-         mpm = dist/tmin,
-         Bird_ID = paste0("B", id),
-         focus = mpm) %>% 
-  drop_na(tmin) %>% 
-  filter(tmin == 15) %>% 
-  dplyr::filter(dist != 0) %>% 
-  group_by(id) %>%
-  filter(., n() >= 20) %>%
-  ungroup()
+nu_df <- df %>% 
+  dplyr::filter(nu != 0,
+                id %in% nu_id) %>% 
+  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
+                          rel.angle * 180/pi + 360))
 
@@
 kpars <- c(1, 2, 2, 2, 2, 2, 2)
+
 ```
 
-```{r eval=FALSE}
-df %>% 
-  ggplot(., aes(x = abs.angle)) +
-  geom_histogram() +
-  facet_wrap(~Bird_ID)
+\newpage
+Figure 1. Probability densities of velocities for each individual bird (gray lines) compared to the complete pooling of data (light blue).
+
+```{r}
+nu_df %>%
+  ggplot(., aes((x = nu))) +
+  geom_line(aes(x = nu, group = id), stat = "density", alpha = 0.4) +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in meters/minute") +
+  theme_classic()
 ```
 
-```{r eval=FALSE}
-df %>%
+Figure 2. Probability densities of turning angles in radians
+
+```{r}
+nu_df %>% 
   drop_na(rel.angle) %>% 
-  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
-                          rel.angle * 180/pi + 360)) %>%
+  ggplot(., aes(x = rel.angle)) +
+  geom_line(aes(x =  rel.angle, group = id), stat = "density", alpha = 0.4) +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Turning angle in radians")
+```
+
+Figure 3. Comparison between histograms of turning angles in degrees for individuals versus complete pooling of data.
+
+```{r}
+p1_angles <- nu_df %>% 
+  drop_na(d.angle) %>% 
   ggplot(., aes(x = d.angle)) +
-  #facet_wrap(~id) +
   geom_histogram(color = "grey", fill = "grey") +
@@
         axis.text.y = element_blank(),
-        legend.position = "none")
-```
+        legend.position = "none") +
+  labs(title = "Complete pooling")
 
-```{r}
-# Create my focus variable and only for individuals with 30+ observations
+p2_angles <- nu_df %>% 
+  drop_na(d.angle) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  facet_wrap(~B_id) +
+  theme(axis.text = element_blank()) +
+  labs(title = "No pooling")
 
-# focus <- "dist"
-# focus <- "R2n"
- focus <- "mpm"
-# focus <- "m15"
-
-if(focus == "dist"){
-  df <- aracari_df %>%
-  dplyr::filter(dist != 0) %>%
-  group_by(id) %>%
-  filter(., n() >= 30) %>%
-  ungroup() %>%
-  dplyr::filter(dist != 0) %>% 
-    mutate(Bird_ID = paste0("B", id),
-           focus = dist)
-
-  dist.used <- c("lnorm", "weibull", "cauchy")
-  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
-  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
-  kpars <- c(2, 2, 2, 2, 2, 2)
-}
-
-if(focus == "R2n"){
-  df <- aracari_df %>%
-  dplyr::filter(R2n != 0) %>%
-  group_by(id) %>%
-  filter(., n() >= 30) %>%
-  ungroup() %>%
-  dplyr::filter(R2n != 0) %>% 
-    mutate(Bird_ID = paste0("B", id),
-           focus = sqrt(R2n))
-
-  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
-  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
-  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
-  kpars <- c(1, 2, 2, 2, 2, 2, 2)
-}
-
-if(focus == "mpm"){
-  df <- aracari_df %>% 
-  dplyr::filter(dist != 0) %>% 
-  group_by(id) %>%
-  filter(., n() >= 30) %>%
-  ungroup() %>%
-  mutate(tmin = dt/60,
-         mpm = dist/tmin,
-         Bird_ID = paste0("B", id),
-         focus = mpm) %>% 
-  dplyr::filter(., mpm != 0)
-
-  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
-  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
-  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
-  kpars <- c(1, 2, 2, 2, 2, 2, 2)
-}
-
-if(focus == "m15"){
-  df <- aracari_df %>% 
-  dplyr::filter(dist != 0) %>% 
-  group_by(id) %>%
-  filter(., n() >= 30) %>%
-  ungroup() %>%
-  mutate(tmin = dt/60,
-         mpm = dist/tmin,
-         m15 = mpm*15,
-         Bird_ID = paste0("B", id),
-         focus = m15) %>% 
-  dplyr::filter(., m15 != 0)
-
-  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
-  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
-  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
-  kpars <- c(1, 2, 2, 2, 2, 2, 2)
-}
+plot_grid(p1_angles, p2_angles)
 
 ```
-
-\newpage
-
-### MPM: meters per minute
-Due to the variation in time between consecutive locations, we scaled the step lengths to displacement in one minute.
-**Visualize the variation and distribution of these distances between locations**
-
-```{r}
- df %>%
-  ggplot(., aes((x = focus))) +
-  geom_line(aes(x = focus, group = id), stat = "density", alpha = 0.4) +
-  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = paste(focus)) +
-  theme_classic()
-
-```
-
-```{r}
-df %>%
-  ggplot(., aes(x = focus)) +
-  facet_wrap(~id) +
-  geom_line(stat = "density") +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = paste(focus)) +
-  theme_classic()
-```
-
-# Fit distribution
 
@@
 
-pop <- lapply(dist.used, function(x){fitdist(df$focus, distr = x)})
+pop <- lapply(dist.used, function(x){fitdist(nu_df$nu, distr = x)})
 
@@
 # Repeating the process for data at the individual level
-inds <- unique(as.character(df$Bird_ID))
+inds <- unique(as.character(nu_df$B_id))
 
@@
 for(i in 1:length(inds)){
-  fit.df <- df %>% 
-    dplyr::filter(., Bird_ID == inds[i])
+  fit.df <- nu_df %>% 
+    dplyr::filter(., B_id == inds[i])
 
-  fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})
+  fit <- lapply(dist.used, function(x){fitdist(fit.df$nu, distr = x)})
 
@@
 
+Figure 4. QQplot fits of each distribution model to the velocity data
+
 ```{r ind_QQplots, fig.width=12, fig.height=5}
@@
 qqpop %>% 
-  mutate(individual = "POPULATION") %>% 
+  mutate(individual = "Complete Pooling") %>% 
   ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
@@
 ```
-
 ## Information criteria
@@
          best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms
-```
 
-```{r}
 nice_prms %>% 
@@
 
-knitr::kable(best_model)
-# 
-# 
-# nice_prms %>% 
-#   filter(., data != "pop") %>% 
-#   dplyr::select(dist, data, deltaAIC,
-#                 #deltaAICc,
-#                 deltaBIC) %>% 
-#   distinct() %>% 
-#   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
-#   filter(value > 0 & value <= 2) %>%  
-#   pivot_wider(., names_from = ic, values_from = dist) %>% 
-#   mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
-#   dplyr::select(., data, agree) %>% 
-#   rename(Individual = data,
-#             `Best model` = agree)
-
+# knitr::kable(best_model)
 ```
 
-However, it is not as straight-forward since there are multiple competing models for certain individuals, which we consider as those within less than 2 units of the delta AIC or BIC.
-When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models.
-We should use 4 for BIC and 3 for AIC.
-Look for the paper Taper Ponciano 2016.
 ```{r fig.width=12, fig.height=4}
@@
 ```
-Now we can compare what we call *models*, in which we compare a model that does complete pooling and considers all the data together, and the other model that considers individual variation, and so it fits a separate distribution to the data from each individual.
-
-The individual variation models will fit a distribution to each individual.
-At one level we will use the same distribution for all individuals and only consider variation in parameters.
-At the next level, we will consider a change in parameters and distributions, where individuals can have different distributions, and this is what we call the mixed distribution model for individual variation.
 
@@
 
-Considering just focusing on BIC because of JMP's paper, and also in this specific case, it provides less competing models for each individual
 ```{r}
@@
   tab_row_group(
-    group = "Multidist",
+    group = "No Pooling",
     rows = 9
@@
   tab_row_group(
-    group = "Individual",
+    group = "Partial Pooling",
     rows = 1:4
@@
   tab_row_group(
-    group = "Population", 
+    group = "Complete Pooling", 
     rows = 5:8
@@
 
-## Probability distribution parameters
-We can compare the different parameter values estimated for each distribution and their standard deviations.
-These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute.
-The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model.
-The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate.
-Overall, at the population level, the lognormal model had the lowest AIC and BIC values.
-
-```{r}
-
-plot_params <- function(prm_data, best_col){
-
-  prm_data%>% 
-  filter(., data == "POP") %>% 
-  dplyr::select(., estimate, sd) -> pop_est
-
-  title <- paste(prm_data$dist, prm_data$param)
-
-  if(best_col == "BIC"){
-    prm_data %>% 
-    filter(data != "POP") %>% 
-    ggplot(., aes(x = data, y = estimate)) +
-    #facet_grid(dist~param, switch = "y", scales = "free") +
-    # geom_point() +
-    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
-    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
-    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
-    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
-    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
-    labs(x = "", y = "", subtitle = title) +
-    theme(legend.position = "none",
-          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
-  }
-
-  if(best_col == "AIC"){
-    prm_data %>% 
-    filter(data != "POP") %>% 
-    ggplot(., aes(x = data, y = estimate)) +
-    #facet_grid(dist~param, switch = "y", scales = "free") +
-    # geom_point() +
-    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
-    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
-    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
-    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
-    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
-    labs(x = "", y = "", subtitle = title) +
-    theme(legend.position = "none",
-          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
-  }
-  return(plot)
-
-}
-
-```
-
-```{r fig.height=10, fig.width=12}
-
-nice_prms %>% 
-  filter(., dist == "Exponential") %>% 
-  plot_params(., best_col = "BIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p1
-
-nice_prms %>% 
-  filter(., dist == "Gamma" & param == "SHAPE") %>% 
-  plot_params(., best_col = "BIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL -> p2
-
-nice_prms %>% 
-  filter(., dist == "Gamma" & param == "RATE") %>% 
-  plot_params(., best_col = "BIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL -> p3
-
-nice_prms %>% 
-  filter(., dist == "Weibull" & param == "SHAPE") %>% 
-  plot_params(., best_col = "BIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p4
-
-nice_prms %>% 
-  filter(., dist == "Weibull" & param == "SCALE") %>% 
-  plot_params(., best_col = "BIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p5
-
-nice_prms %>% 
-  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
-  plot_params(., best_col = "BIC") -> p6
-
-nice_prms %>% 
-  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
-  plot_params(., best_col = "BIC") ->p7
-
-plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid
-
-nice_prms %>% 
-  filter(., dist == "Exponential") %>% 
-  plot_params(., best_col = "AIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p1
-
-nice_prms %>% 
-  filter(., dist == "Gamma" & param == "SHAPE") %>% 
-  plot_params(., best_col = "AIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL -> p2
-
-nice_prms %>% 
-  filter(., dist == "Gamma" & param == "RATE") %>% 
-  plot_params(., best_col = "AIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL -> p3
-
-nice_prms %>% 
-  filter(., dist == "Weibull" & param == "SHAPE") %>% 
-  plot_params(., best_col = "AIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p4
-
-nice_prms %>% 
-  filter(., dist == "Weibull" & param == "SCALE") %>% 
-  plot_params(., best_col = "AIC") +
-  #theme(axis.text.x = element_blank()) +
-  NULL-> p5
-
-nice_prms %>% 
-  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
-  plot_params(., best_col = "AIC") -> p6
-
-nice_prms %>% 
-  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
-  plot_params(., best_col = "AIC") ->p7
-
-plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid
-
-plot_grid(bic_grid, aic_grid, ncol = 2)
-
-```
-
-#References
+# References

### 2021-04-15 movement_paper/rudolph_ch2.Rmd
Update to introduction

@@
 output:
+  html_document:
+    df_print: paged
   word_document:
     reference_docx: move_ref.docx
-  html_document:
-    df_print: paged
 bibliography: aracari_movement.bib
@@
 # Introduction
+
+   Modeling animal telemetry data is is often necessary to  understand animal behavior, space use patterns, movement patterns, and responses to the environment.
+This type of data is usually analyzed with discrete time movement models, defining regular time steps between animal relocations.
+However, certain telemetry data such as that for marine animals, or data collected in environmental conditions that interfere with satellite signals, such as dense forest or cloud cover, can lack regular time intervals in data collection, causing these telemetry data to be observed irregularly.
+Although technological advances have allowed for new and more precise data collection methods, smaller tags, and data storage, some of the same problems remain and data with irregular time steps and high levels of uncertainty pose complex statistical problems [@albertsen2019generalizing].
+The flexible framework of state-space models has been used as a valuable tool to model this irregularity and uncertainty, as state-space models allow for separation of the movement process from the sampling mechanism.
+State-space models are used to analyze time series of location observations, also referred to as movement pathways or trajectories [@jonsen2003meta].
+In movement data, a state-space process allows us to couple a statistical model for the observation method, accounting for errors in sampling or detection, with a separate model for the movement dynamics which are determined by the effects of behavior or responses to the environment [@patterson2008state], thus modeling true animal locations directly with a stochastic process, and model observed locations as the conditional distribution given the true locations.
+Although the flexibility of a state-space framework allows for both continuous and discrete time, the applications of these approaches are still limited by number of observations, as they require good time series data and long enough animal trajectories with multiple consecutive relocations.
 

### 2021-04-15 distributions_paper/rudolph_distributions.Rmd
update notation

@@
 To first set up the framework for a velocity-based model, we consider movement as the change in locations across two coordinates.
-We let $\mu(t)=[\mu_x(t), \mu_y(t)]'$ be the location of an individual at time $t$ in the coordinates $x$ and $y$.
-We establish $\boldsymbol{d}_{\Delta}(t) = \boldsymbol{\mu}(t+\Delta) - \boldsymbol{\mu}(t)$ as the difference in locations across both coordinates over $\Delta$ time units.
-The differential equation $d\boldsymbol{\mu}(t)=\boldsymbol{\nu}(t)dt$ represents the instantaneous velocity as $\Delta$ approaches zero under the assumption that $\boldsymbol\mu(t)$ is a continuous movement path [@johnson2008continuous].
-Although the bivariate velocity process $\boldsymbol\nu(t) = [\nu_x(t), \nu_y(t)]'$ could be considered as cross-correlated between the axes, these correlated velocities produce strange directed travel and thus velocity in each coordinate is considered to be an independent process [@johnson2008continuous].
+We let $\boldsymbol{u}(t)=[u_x(t), u_y(t)]'$ be the location of an individual at time $t$ in the coordinates $x$ and $y$.
+We establish $\boldsymbol{d}_{\Delta}(t) = \boldsymbol{u}(t+\Delta) - \boldsymbol{u}(t)$ as the difference in locations across both coordinates over $\Delta$ time units.
+The differential equation $d\boldsymbol{u}(t)=\boldsymbol{v}(t)dt$ represents the instantaneous velocity as $\Delta$ approaches zero under the assumption that $\boldsymbol{u}(t)$ is a continuous movement path [@johnson2008continuous].
+Although the bivariate velocity process $\boldsymbol{v}(t) = [u_x(t), u_y(t)]'$ could be considered as cross-correlated between the axes, these correlated velocities produce strange directed travel and thus velocity in each coordinate is considered to be an independent process [@johnson2008continuous].
 We decided instead, to focus on a velocity-based movement process using velocity scalars and turning angles.
-Under this framework, we define a scalar for instantaneous directionless velocity as $$\nu(t+\Delta) = \sqrt{(\mu_x(t+\Delta)-\mu_x(t))^2 + (\mu_y(t+\Delta) - \mu_y(t))^2}$$ and assume it to be a random variable with probability density $N \sim f(t|\boldsymbol\sigma)$ where $\boldsymbol\sigma$ represents the vector of parameters and determines the overall variability in velocity according to a specific probability density function $f(\boldsymbol\sigma)$.
+Under this framework, we define a scalar for instantaneous directionless velocity as
+$$v(t+\Delta) = \sqrt{(u_x(t+\Delta)-u_x(t))^2 + (u_y(t+\Delta) - u_y(t))^2}$$
+and assume $v(t)$ to be a random variable with probability density $h(\boldsymbol\sigma)$ where $\boldsymbol\sigma$ represents the vector of parameters and determines the overall variability in velocity.
 We assumed velocities to be independent of turning angles and chose to describe each with a separate probability density function, which is common practice when using movement lengths [@kareiva1983analyzing].
@@
 
-Using this velocity process and turning angles, the continuous-time location process $\boldsymbol\mu(t)$ can be obtained by integrating over the velocity process [@johnson2008continuous]:
-$$\boldsymbol\mu(t) = \boldsymbol\mu(0) + \int_0^t\boldsymbol\nu(u)du$$
+Using this velocity process and turning angles, the continuous-time location process $\boldsymbol{u}(t)$ can be obtained by integrating over the velocity process [@johnson2008continuous]:
+$$\boldsymbol{u}(t) = \boldsymbol{u}(0) + \int_0^t\boldsymbol{v}(\tau)d\tau$$
 where 
-$$\int_0^t\boldsymbol\nu(u)du =\int_0^t [\nu_x(u), \nu_y(u)]' du = \int_0^t [\sin(\theta_u), \cos(\theta_u)]' \cdot \nu(u)du$$
+$$\int_0^t\boldsymbol{v}(\tau)d\tau =\int_0^t [v_x(\tau), v_y(\tau)]' d\tau = \int_0^t [\sin(\theta_\tau), \cos(\theta_\tau)]' \cdot v(\tau)d\tau$$
 This integral describes the location at time $t$ as the sum of steps determined by velocities in each direction plus a starting location at time $t=0$.
@@
 
-# Example: Many-banded aracari movement
+## Example: Many-banded aracari movement
 
@@
 We used the package 'adehabitatLT'[@adehabitatLT] in R [@Rlang] to calculate other descriptive parameters for each trajectory, such as turning angles and net squared displacement.
+
+# Results
+## Fitting velocity probability density functions
+
+We compared the fit of the different probability distributions to animal movement rate data with Akaike's Information Criteria(AIC) and it's corrected version for small sample sizes (AICc), we also used the Bayesian Information Criteria (BIC) to compare these model fittings.
+At the population level, all information criteria concur and show that the lognormal model fits the data for movement rates the best, with the weibull model next, see table 1.
+However, as we visually assessed fit of these models with QQ plots and goodness-of-fit statistics (see the supplemet), the lognormal distribution model greatly overestimates the data towards the tail, whereas all the other models are significantly more conservative and tend to underestimate the data.
+
+At the individual level, we observed similar outcomes, where the lognormal distribution consistently overestimated the data, whereas the other distributions considered did not.
+When comparing across distribution models at the individual level, AIC and AICc showed the lognormal fit as the best one followed by the exponential model, whereas the BIC had the exponential as the best model followed by the lognormal.
+
+When comparing the population level models with the ones at the individual level, we found that information criteria differed.
+In the case of AIC and AICc, these consistently categorized the individual level models as best fitting when compared to their equivalent distribution model at the population level.
+However, BIC values show that only when we consider the exponential distribution model does the individual level do a better fitting than the population, with all other models having higher BIC values for the models that include individual heterogeneity.
+
+The mixed/heterogeneous model considered the best fitting distribution for each individual, and then selected given distribution to be included in the general model that includes movement for all the individuals and calculates the information criteria value.
+Using different information criteria yielded different best fitting models (see supplement) for each individual, which changed the distributions included on the overall model, therefore producing two different mixed/heterogeneous modelsd with individual variation, one associated to the AIC/AICc target distributions and a different one for BIC.
+However, all information criteria agreed on nine out of twelve individual models.
+In the case of AIC and AICc four individuals were better described by an exponential distribution, three by a Weibull distribution and five by a lognormal distribution.
+When using BIC as the model selection tool, seven individuals were described by an exponential distribution, four by a lognormal and one by the Weibull distribution.
+The overall AIC, AICc and BIC values were calculated for each of the mixed/heterogenous model and compared to the previous fits, where the first five results are shown in the following table (the rest can be seen in the supplement).
+This shows that only the lognormal model at the population level is better than the mixed/heterogeneous model by <2 BIC units.
 
@@
 
+```{r fig.height=10, fig.width=12}
+plot_params <- function(prm_data){
+
+  prm_data%>% 
+  filter(., data == "POP") %>% 
+  dplyr::select(., estimate, sd) -> pop_est
+
+  title <- paste(prm_data$dist, prm_data$param)
+
+prm_data %>% 
+    filter(data != "POP") %>% 
+    ggplot(., aes(x = data, y = estimate)) +
+    #facet_grid(dist~param, switch = "y", scales = "free") +
+    # geom_point() +
+    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
+    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
+    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
+    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
+    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
+    labs(x = "", y = "", subtitle = title) +
+    theme(legend.position = "none",
+          axis.text.x = element_text(angle = 45))
+}
+
+nice_prms %>% 
+  filter(., dist == "Exponential") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p1
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "SHAPE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p2
+
+nice_prms %>% 
+  filter(., dist == "Gamma" & param == "RATE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL -> p3
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SHAPE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p4
+
+nice_prms %>% 
+  filter(., dist == "Weibull" & param == "SCALE") %>% 
+  plot_params() +
+  #theme(axis.text.x = element_blank()) +
+  NULL-> p5
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
+  plot_params() -> p6
+
+nice_prms %>% 
+  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
+  plot_params() ->p7
+
+plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v")
+```
+
 # References

### 2021-04-15 distributions_paper/rudolph_distributions.Rmd
update

@@
 
-Assume weibull distributions for step length and wrapped cauchy distributions for the turning angles [@langrock2012flexible], but they tried Gamma and von Mises, respectively, but got outperformed by AIC.
-Used negative binomial for the state dwell times.
-
-Random walks used broadly in biology to characterize animal and cell movement.
-Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions.
-[@codling2008random]
-- IDEA: so maybe use these distributions for the angles.
-We might see that there is not much difference in angle movement across individuals?
-They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances.
-- Also might be intriguing to incorporate the time as a set of multiple random walks?
-or repeats the velocity value for that number of minutes.
-Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
-  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
-  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$).
-Hence, turning events occur as a Poisson process with rate $\lambda$.
-**This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
-    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose.
-So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data.
-    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$
-  - Pg11. A correlated random walk, CRW, consisting of a series of independet draws from a step length PDF and a turning angle PDF for each step, a first order markov process.
-    - using mean square displacement. The effect of step length variability on MSD can be quite significant.
-    - MSD being of interest to ecologists due to its relation with the diffusion coefficient D. equations 2.13 and 2.14
-** Should write a conclusion about this paper**
-
-[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle.
-Using square displacement instead of linear displacement, because it's expectation can be calculated from turning angles and step lengths.
-Assume that the length of each move and the turning angle are independent random variables, each with its own probability density.
-Assume that a series of moves can be represented by random draws from these probability densities, and since each random draw is independent from the preceding ones, the random draw process is a first order markov chain.
-The result is a correlated random walk, and the distribution g(theta) gives a measure of the degree to which the angles of movement are correlated.
-*Would be interesting to add a figure with what I am actually analyzing.
-So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval.
-Or we could just multiply everything?
-So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*
-
-probabilistic rules of movement.
-
-"Location accuracy using radio telemetry may be reduced in tropical forests...
-conservative distance categories of 100-m increments to better represent precision.
-Time categories: 15, 30, 60, 90 minutes.
-Then calculated probability of movements made within each distance category within each time category, summed across each time category to give a final probability for each distance category."
-
-"Distances travelled per movement bout ranged from 0 to >2000m.
-Strong leptokurtic distributions of movements with most being <300m.
-Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)" *this is a corresponding velocity of `r 3665/30` meters per minute.
-
-Evaluating models with their individual-specific counterparts, using AIC or BIC. In individual-specific models the AIC results from the joint likelihood of the individual-specific models.
+Here describe the nine different models which vary according to pooling level and use of a different probability density.
 

### 2021-07-06 distributions_paper/rudolph_distributions.Rmd
Damn, it has been so long I don't even remember what this is. Cross fingers nothing breaks.

@@
 We illustrate the use of this model and the individual variation comparison by analyzing a telemetry data set of twelve many-banded aracari individuals, *Pteroglossus pluricinctus*.
+
+**2021-05-03**
+
+- Explain what levy processes are and why they are suggested. Random search for resources. 
+- Classical random walks for homogeneous environments, and in more complex environments, use mixtures of these 'classical' random walks, to show the animals adaptability to the changes in the environment.
+- Levy walks claimed to be more efficient than classical random walks for search or activity patterns.
+- Levy walks are non-oriented and superdiffusive. Interesting too because they may be involved when the random variable follows a power-law distribution. 
+- Classical random walks have step lengths distributed with finite variance, and in their simplest form, both their step length and turning angles are uniformly distributed.
+Levy walks are also uncorrelated and unbiased, like mere random walks, but their step lengths are characterized by infinite variance (i.e.
+drawn from a heavy-tail distribution).
+simplest example with a pareto distribution.
+[Benhamou 2007]
+
+Bartumeus 2007
+Levy-type processes can be relevant in large-scale animal movement.
 
@@
   mutate(B_id = paste0("B", id))-> df
+
+# jmp <- aracari_df %>% 
+#   drop_na(dist) %>% 
+#   filter(id == 5) %>% 
+#   dplyr::select(dist, dt) %>% 
+#   mutate(vel = dist/(dt/60))
+# 
+# save(jmp, file = "ex_data.RData")
 

### 2021-07-06 distributions_paper/velocity_framework.Rmd
Damn, it has been so long I don't even remember what this is. Cross fingers nothing breaks.

---
title: "Testing velocity framework"
output: html_notebook
---

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(aracari)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(stringr)
library(adehabitatLT)
library(cowplot)
library(RColorBrewer)
library(gt)
library(lubridate)

library(tidyverse)
library(fitdistrplus)

theme_set(theme_bw())
```

```{r data}
# First, read in the raw tracking data
aracari_data <- read.csv("rawdata_ptpl.csv")
# Time is presented as a time ID
# Each time interval is equivalent to 15 minutes
# Interval 1 == 6AM, so if we start at midnight, 6am is 24 intervals of 15 minutes each. I'm setting 6am as the start just because I don't have actual data on it, but we know they started early morning and that's what the time IDs are for in Kimberly's work.

# create a column for number of minutes equivalent to the intervals

dt <- paste(aracari_data$DATE, aracari_data$TIME) %>% 
  parse_date_time(., "dmy IMS p")

aracari_data$dt <- dt

names(aracari_data)[1] <- "TRANS"

# seconds <- (24*15 + aracari_data$Time_ID * 15) * 60
# td <- seconds_to_period(seconds)
# aracari_data$time <- sprintf("%02d:%02d:%02d", td@hour, minute(td), second(td))
# 
# date <- paste(aracari_data$DATE, aracari_data$time)
# aracari_data$date <- parse_date_time(date, "dmyHMS")
# aracari_data$burst <- paste(aracari_data$Bird_ID, aracari_data$DATE, sep="_")

aracari_data$burst <- paste(aracari_data$TRANS, aracari_data$DATE)

# Only keep the columns we need for adehabitat

# aracari_data <- dplyr::select(aracari_data, Bird_ID, burst,
#                            date, X_Estimate, Y_Estimate)

aracari_data %>% 
  dplyr::select(., TRANS, burst, dt, X_Estimate, Y_Estimate) -> aracari_data

names(aracari_data) <- c("animal_id","burst_id", "date_time", "x", "y")

```

```{r}
# we set the spatial coordinates for our data frame
aracari_spatial <- aracari_data
coordinates(aracari_spatial) <- c("x", "y")

#Assign a projection, I know it is UTM zone 18 because it is Ecuadorian Amazon
proj4string(aracari_spatial) <- CRS("+proj=utm +zone=18 +datum=WGS84")

# Create ltraj object for work with adehabitat
# We set typeII = TRUE because we have variable time frames, although locations were attempted every 15 minutes, this didn't always happen.
aracari_ltraj <- as.ltraj(coordinates(aracari_spatial), 
                          burst = aracari_spatial$burst_id,
                          date=aracari_spatial$date_time,
                          id=aracari_spatial$animal_id,
                          typeII = TRUE)

# We can see the locations for all the individuals tracked
# plot(aracari_ltraj)
```

```{r}
# head(aracari_ltraj)

# Transform to a dataframe
aracari_df <- ld(aracari_ltraj)

nbursts <- aracari_df %>% drop_na(dt) %>% group_by(id) %>% distinct(burst) %>% tally() %>% arrange(id) %>% rename(nbursts = n)
nlocs <- aracari_df %>% group_by(id) %>% tally() %>% arrange(id) %>% rename(nlocs = n)

# Check number of bursts per animal and the number of locations
# merge(nbursts, nlocs, by = "id", all=TRUE) %>% arrange(nlocs)

# I want to include family groups in that data set, just in case we want to use that later
# The social groups are as follows: (1, 3, 5), (7), (13, 19), (22), (28), and (49, 84).
# I've added another group for birds (29,30) which are Yasuni birds, with overlapping territories and I would assume they are a social group.
# All others are left as unknown.
aracari_df$id <- factor(aracari_df$id, levels = unique(aracari_df$id))
# unique(aracari_df$id)
aracari_df %>%
  mutate(fam_g = ifelse(id %in% c(1,3,5), "f1",
                        ifelse(id == 7, "f2",
                               ifelse(id %in% c(13, 19), "f3",
                                      ifelse(id == 22, "f4",
                                             ifelse(id == 28, "f5",
                                                    ifelse(id %in% c(49,84),
                                                           "f6", 
                                                           ifelse(id %in% c(29, 30), "f7", "unknown")
                                             ))))))) -> aracari_df

```

# Velocity-based framework

Animal telemetry data are collected by determining an animal's location at various points in time. Many of the movement models used to analyze animal telemetry data rely on regular time intervals between locations (Jonsen et al. 2003 and 2005, Turchin 1998). However, based on field methods, or environmental variables such as heavy cloud cover or dense forest, can make data collection at regular intervals difficult, and thus location data becomes more opportunistic and with irregular time intervals. Previous methods to analyze data under these irregular conditions have relied on interpolating, subsampling, or aggregating data during pre-processing in order to make it fit model assumptions. In this study, we propose the use of a model capable of handling irregular time intervals by considering movement as a stochastic process on a continuous time scale, and thus focus on the animal's instantaneous velocity rather than on its absolute displacements between locations. Using this continuous-time framework, we are able to estimate movement paths by integrating velocity functions. We also explore the effects of individual variation in speeds as a comparison between velocity probability density functions across different levels of data aggregation between individuals. We illustrate the use of this model and the individual variation comparison by analyzing a telemetry data set of twelve many-banded aracari individuals, *Pteroglossus pluricinctus*.

To first set up the framework for a velocity-based model, we consider movement as the change in locations across two coordinates. We let $\mu(t)=[\mu_x(t), \mu_y(t)]$ be the location of an individual at time $t$ in the coordinates $x$ and $y$, and establish $\boldsymbol{d}_{\Delta}(t) = \boldsymbol{\mu}(t+\Delta) - \boldsymbol{\mu}(t)$ as the difference in locations across both coordinates over $\Delta$ time units. The differential equation $d\boldsymbol{\mu}(t)=\boldsymbol{\nu}(t)dt$ represents the instantaneous velocity as $\Delta$ approaches zero under the assumption that $\boldsymbol\mu(t)$ is a continuous movement path (Johnson et al. 2008).

Although the bivariate velocity process $\boldsymbol\nu(t) = [\nu_x(t), \nu_y(t)]$ could be considered as cross-correlated between the axes, these correlated velocities produce strange directed travel (Johnson et. al. 2008), therefore we considered the velocity in each coordinate to be an independent process.

We consider turning angle and velocity as independent processes. You need at least three relocations for relative angle calculations, and only two to calculate velocities. So, fitting the data makes more sense if they are completely separate. Based on a correlated random walk framework, you assess the level of correlation based on the distribution and symmetry of the probability density of the angles.

nu, velocity in meters per minute

```{r}
aracari_df %>% 
  mutate(nu = dist/(dt/60)) %>% 
  dplyr::select(id, nu, rel.angle, dt) %>% 
  drop_na(nu) -> df

# Select individuals with at least 30 data points for velocity
df %>% 
  dplyr::select(id, nu) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(., n >= 30) %>% 
  dplyr::pull(id) -> nu_id

# Select individuals with 20 or 30? angles
df %>% 
  dplyr::select(id, rel.angle, dt) %>%
  mutate(dt = dt/60) %>% 
  drop_na(rel.angle) %>% 
  #filter(., dt == 15) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(., n >= 25) %>% 
  dplyr::pull(id) -> angle_id
```

```{r}
df %>% 
  dplyr::select(., id, nu) %>% 
  filter(., id %in% nu_id) %>% 
  ggplot(., aes(x = nu)) +
  geom_histogram() +
  facet_wrap(~id)
```

```{r}
df %>% 
  dplyr::select(id, rel.angle, dt) %>% 
  mutate(dt = dt/60,
         d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  drop_na(rel.angle) %>% 
  filter(., id %in% angle_id,
         dt ==15) %>%
  ggplot(., aes(x = rel.angle)) +
  #ggplot(., aes(x = d.angle)) +
  geom_histogram() +
  facet_wrap(~id)
```

# Fit distributions to velocity data

Assume weibull distributions for step length and wrapped cauchy distributions for the turning angles [@langrock2012flexible], but they tried Gamma and von Mises, respectively, but got outperformed by AIC. Used negative binomial for the state dwell times.

Random walks used broadly in biology to characterize animal and cell movement. Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions. [@codling2008random]
- IDEA: so maybe use these distributions for the angles. We might see that there is not much difference in angle movement across individuals? They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances. 
- Also might be intriguing to incorporate the time as a set of multiple random walks? or repeats the velocity value for that number of minutes. Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$). Hence, turning events occur as a Poisson process with rate $\lambda$. **This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose. So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data. 
    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$
  - Pg11. A correlated random walk, CRW, consisting of a series of independet draws from a step length PDF and a turning angle PDF for each step, a first order markov process.
    - using mean square displacement. The effect of step length variability on MSD can be quite significant.
    - MSD being of interest to ecologists due to its relation with the diffusion coefficient D. equations 2.13 and 2.14
** Should write a conclusion about this paper**

[@kareiva1983analyzing] - approximating displacements by connecting a series of straight lines, and thus summarize animal movement based on parameters for movement length and turning angle. Using square displacement instead of linear displacement, because it's expectation can be calculated from turning angles and step lengths. Assume that the length of each move and the turning angle are independent random variables, each with its own probability density. Assume that a series of moves can be represented by random draws from these probability densities, and since each random draw is independent from the preceding ones, the random draw process is a first order markov chain. The result is a correlated random walk, and the distribution g(theta) gives a measure of the degree to which the angles of movement are correlated.
*Would be interesting to add a figure with what I am actually analyzing. So, visually show how the gps locations get turned into straight lines, and angles, with an associated time interval. Or we could just multiply everything? So have it all for 15 minute intervals, and then repeat the ones that went on longer, perhaps set a limit for 60 minutes?*

probabilistic rules of movement.

"Location accuracy using radio telemetry may be reduced in tropical forests... conservative distance categories of 100-m increments to better represent precision. Time categories: 15, 30, 60, 90 minutes. Then calculated probability of movements made within each distance category within each time category, summed across each time category to give a final probability for each distance category."

"Distances travelled per movement bout ranged from 0 to >2000m. Strong leptokurtic distributions of movements with most being <300m. Longest recorded movement for Pluricinctus is 3665m (recorded in 30 minutes)" *this is a corresponding velocity of `r 3665/30` meters per minute.

Evaluating models with their individual-specific counterparts, using AIC or BIC. In individual-specific models the AIC results from the joint likelihood of the individual-specific models.

### 2021-07-06 distributions_paper/test_methods.R

@@ -1,0 +1,41 @@
+
+# Needs an ltraj object for the location data
+# so, run `format_raw_dat.Rmd` to get that one (up to line 143)
+
+library(adehabitatLT)
+
+is.regular(aracari_ltraj)
+
+aracari_ltraj
+
+
+
+refda <- as.POSIXlt(Sys.Date(), "UTC")
+
+refda <- strptime("2003-06-01 00:00", "%Y-%m-%d %H:%M", tz = "UTC")
+
+
+aracari_reg <- setNA(aracari_ltraj, dt = 900, refda, units = "sec")
+
+
+plotltr(aracari_ltraj, "dt/60")
+
+dev.off()
+
+aracariI <- typeII2typeI(aracari_ltraj)
+aracariI
+plot(aracariI)
+
+aracariIr <- redisltraj(aracariI, 100)
+
+
+aracari_df %>%
+  filter(R2n >0) %>%
+  ggplot(., aes(x = R2n)) +
+  geom_histogram() +
+  facet_wrap(~id)
+
+wawotest(aracari_ltraj)
+testang.ltraj(aracari_ltraj, "relative")
+
+aracari_ltraj[3] -> a

### 2021-08-12 Ch1_movement_rates/Ch1_markdown.Rmd
organizing files as dissertation chapters
simulations for individual variation

--- 2021-03-19 long_distance_paper/long_distance_paper.Rmd
@@
 ---
-title: Individual variation in animal movement and its consequences for long-distance
-  seed dispersal patterns
-author: "F. Javiera Rudolph"
+title: "Implications of animal movement rate variation in spatial patterns of seed dispersal"
+author: "Javiera Rudolph"
+date: "8/12/2021"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+```
+
+Let's say there is a variation in animal movement rates, and it depends on multiple factors, such as size of the animal, breeding status, nesting, etc.
+So, it can also be seasonal.
+Since movement rates can't really be negative, we will use a lognormal distribution to describe this variation in movement rates.
+
+Let $X_i$ be a positive random variable that is log-normally distributed $(i.e.
+X_i \sim Lognormal(\mu_i, \sigma_i^2)$ describing the distribution of movement rates for an animal population $i$.
+Such animal population's average movement rate being $\mu_i$ and the variance of their movement rates $\sigma_i^2$.
+We can assume we have three different populations, where perhaps some of them have larger home ranges, creating more variance across movement rates.
+To make things a little easier, we will consider all populations have the same average movement rate $(i.e.
+\mu_1=\mu_1=\mu_3 = 1)$, but different standard deviation $(\sigma_1=0.3, \sigma_2=0.5, \sigma_3=0.5)$.
+We can visualize the distribution of movement rates for each of these populations:
+
+```{r}
+mycols <- c("black", "blue", "purple")
+#create density plots
+curve(dlnorm(x, meanlog=1, sdlog=.3), from=0, to=10, col=mycols[1],
+      main = 'Log Normal Distribution', #add title
+      ylab = 'Density', #change y-axis label
+      )
+curve(dlnorm(x, meanlog=1, sdlog=.5), from=0, to=10, col=mycols[2], add=TRUE)
+curve(dlnorm(x, meanlog=1, sdlog=1), from=0, to=10, col=mycols[3], add=TRUE)
+
+#add legend
+legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
+       col=mycols, lty=1, cex=1.2)
+```
+
+Now, lets sample a movement rate, $m$, for 10 individuals $(i.e.
+j = 1...10)$ from the first population $(i.e.
+m_{1,j} = m_{1,1}, ....., m_{1,10})$.
+We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, movement angle, $\alpha$, from a uniform distribution, $\alpha \sim U(0, 360)$.
+We can visualize the movement for one of the individuals in the first population:
+
+```{r}
+m_1 <- rlnorm(10, meanlog = 1, sdlog = 0.3)
+m_2 <- rlnorm(10, meanlog = 1, sdlog = 0.5)
+m_3 <- rlnorm(10, meanlog = 1, sdlog = 1)
+```
+
+We can look at how those exponential distributions look for each of the individuals in those populations
+
+```{r}
+
+```
+
+```{r}
+t <- 1000 # Number of time steps
+
+tru.rate <- m_1[1]
+movedist <- rexp(t, rate = tru.rate)
+angle <- runif(t, min = 0, max = 360)
+distx <- movedist*cos(angle)
+xloc <- c(0, cumsum(distx))
+disty <- movedist*sin(angle)
+yloc <- c(0, cumsum(disty))
+animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
+
+plot(x = xloc, y = yloc, type = "l", main = paste("Rate", tru.rate))
+
+```
+```{r}
+sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
+  tru.rate <- round(prm, 3)
+  movedist <- rexp(t, rate = tru.rate)
+  angle <- runif(t, min = 0, max = 360)
+  distx <- movedist*cos(angle)
+  xloc <- c(0, cumsum(distx))
+  disty <- movedist*sin(angle)
+  yloc <- c(0, cumsum(disty))
+  animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
+  if(plot.it == TRUE){
+    plot(x = xloc, y = yloc, type = "l", main = paste("Rate=",tru.rate))
+  }
+  if(return.data.frame == TRUE){
+    return(animalTraj)
+  }
+}
+```
+
+```{r}
+par(mfrow=c(2,5))
+
+for(j in 1:10){
+  sim_movement(m_1[j])}
+
+```
+
+Use ggplot to make multiple rounds of each individual
+```{r}
+library(dplyr)
+library(ggplot2)
+
+df <- sim_movement(m_1[1], plot.it = FALSE, return.data.frame = TRUE)
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc)) +
+  geom_path()
+
+```
+Overlay 5 runs for that individual
+
+```{r}
+
+df <- NULL
+
+for(k in 1:8){
+  a <- sim_movement(m_1[1], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(run = paste("r_", k))
+  df <- rbind.data.frame(df, a)
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, color = run)) +
+  geom_path()
 ```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
populations with different levels of variation in the movement rates

@@
 knitr::opts_chunk$set(echo = TRUE)
+```
+
+```{r message=FALSE}
+library(dplyr)
+library(ggplot2)
 ```
@@
 curve(dlnorm(x, meanlog=1, sdlog=.3), from=0, to=10, col=mycols[1],
-      main = 'Log Normal Distribution', #add title
+      main = 'Log Normally distributed movement rates for three populations', #add title
       ylab = 'Density', #change y-axis label
@@
 
-Now, lets sample a movement rate, $m$, for 10 individuals $(i.e.
-j = 1...10)$ from the first population $(i.e.
-m_{1,j} = m_{1,1}, ....., m_{1,10})$.
-We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, movement angle, $\alpha$, from a uniform distribution, $\alpha \sim U(0, 360)$.
+Now, lets sample a movement rate, $m$, for 5 individuals $(i.e.
+j = 1, ...,5)$ from the first population $(i.e.
+m_{1,j} = m_{1,1}, ....., m_{1,5})$.
+We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, movement angle, $\theta$, from a uniform distribution, $\theta \sim U(0, 360)$.
 We can visualize the movement for one of the individuals in the first population:
@@
 ```{r}
-m_1 <- rlnorm(10, meanlog = 1, sdlog = 0.3)
-m_2 <- rlnorm(10, meanlog = 1, sdlog = 0.5)
-m_3 <- rlnorm(10, meanlog = 1, sdlog = 1)
+m_1 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.3),3))
+m_2 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.5),3))
+m_3 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 1),3))
 ```
@@
 
+mycols <- rainbow(5, s=0.8)
+
+# range <- c(-0.9,5)
+#create density plots
+curve(dexp(x, m_1[5]), 
+      #from=range[1], to=range[2], 
+      col=mycols[1],
+      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
+      ylab = 'Density', #change y-axis label
+      )
+for(i in 1:4){
+  curve(dexp(x, m_1[i]), 
+        #from=range[1], to=range[2],
+        col=mycols[i], add=TRUE)
+}
+
+#add legend
+legend("topright", legend= m_1,
+       col=mycols, lty=1, cex=1.2)
 ```
@@
 ```{r}
-t <- 1000 # Number of time steps
+t <- 100 # Number of time steps
+individual <- 5
 
-tru.rate <- m_1[1]
+tru.rate <- m_1[individual] # In case I want to do scale 1/rate
 movedist <- rexp(t, rate = tru.rate)
@@
 
-plot(x = xloc, y = yloc, type = "l", main = paste("Rate", tru.rate))
+plot(x = xloc, y = yloc, col = mycols[individual], type = "l", main = paste("Rate", tru.rate))
 
@@
 
-```{r}
+```{r eval=FALSE}
 par(mfrow=c(2,5))
 
-for(j in 1:10){
+for(j in 1:individual){
   sim_movement(m_1[j])}
@@
 Use ggplot to make multiple rounds of each individual
-```{r}
-library(dplyr)
-library(ggplot2)
+```{r eval=FALSE}
 
@@
 ```
-Overlay 5 runs for that individual
 
+Population1
 ```{r}
@@
 
-for(k in 1:8){
-  a <- sim_movement(m_1[1], plot.it = FALSE, return.data.frame = TRUE) %>% 
-    mutate(run = paste("r_", k))
+for(j in 1:individual){
+  for(k in 1:10){
+  a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(indiv = as.factor(j),
+           run = paste("r_", k))
   df <- rbind.data.frame(df, a)
+}
 }
@@
 df %>% 
-  ggplot(., aes(x = xloc, y=yloc, color = run)) +
-  geom_path()
+  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
 ```
 
-## R Markdown
+Population2
+```{r}
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+df <- NULL
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+for(j in 1:individual){
+  for(k in 1:10){
+  a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(indiv = as.factor(j),
+           run = paste("r_", k))
+  df <- rbind.data.frame(df, a)
+}
+}
 
-```{r cars}
-summary(cars)
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
 ```
 
-## Including Plots
+Population3
+```{r}
 
-You can also embed plots, for example:
+df <- NULL
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+for(j in 1:individual){
+  for(k in 1:10){
+  a <- sim_movement(m_3[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(indiv = as.factor(j),
+           run = paste("r_", k))
+  df <- rbind.data.frame(df, a)
+}
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
changing the rate, to 1/sampled lognormal variable. It is a longer tail for higher numbers

@@
 
-# range <- c(-0.9,5)
+range <- c(-0.1,12)
 #create density plots
-curve(dexp(x, m_1[5]), 
-      #from=range[1], to=range[2], 
+curve(dexp(x, 1/m_1[1]), 
+      from=range[1], to=range[2], 
       col=mycols[1],
@@
       )
-for(i in 1:4){
-  curve(dexp(x, m_1[i]), 
-        #from=range[1], to=range[2],
+for(i in 2:5){
+  curve(dexp(x, 1/m_1[i]), 
+        from=range[1], to=range[2],
         col=mycols[i], add=TRUE)

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Seed locations added

--- 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
@@
 
-We can look at how those exponential distributions look for each of the individuals in those populations
+We can look at how those exponential distributions look for each of the individuals in those populations.
 
@@
 
-# range <- c(-0.9,5)
+range <- c(-0.1,15)
 #create density plots
-curve(dexp(x, m_1[5]), 
-      #from=range[1], to=range[2], 
+curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2], 
       col=mycols[1],
@@
 tru.rate <- m_1[individual] # In case I want to do scale 1/rate
-movedist <- rexp(t, rate = tru.rate)
+movedist <- rexp(t, rate = 1/tru.rate)
 angle <- runif(t, min = 0, max = 360)
@@
   tru.rate <- round(prm, 3)
-  movedist <- rexp(t, rate = tru.rate)
+  movedist <- rexp(t, rate = 1/tru.rate)
   angle <- runif(t, min = 0, max = 360)
@@
 ```
+
+Now, we get the animals to disperse seeds. Seeds gut retention time are sampled from a gamma distribution.
+```{r eval=FALSE}
+nseeds <- 20
+grt <- round(rgamma(nseeds, shape = 4, scale = 5))
+t.grt <- max(grt)
+
+animalTraj <- sim_movement(m_1[1], t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
+
+# Determine where the seeds are dropped based on the animal's location.
+seed_loc <- data.frame(seed_id = 1:nseeds, time = grt)
+seed_loc <- merge(animalTraj, seed_loc, by = "time")
+seed_loc$dispersal <- sqrt(seed_loc$xloc^2 + seed_loc$yloc^2)
+
+animalTraj %>% 
+  ggplot(., aes(x = xloc, y=yloc)) +
+  geom_path() +
+  geom_point(data=seed_loc, aes(x = xloc, y = yloc))
+
+```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Add code for dispersion/dispersal measures

@@
 
+# Calculate the mean location of seeds
+x_m <- mean(seed_loc$xloc)
+y_m <- mean(seed_loc$yloc)
+mean_dispersal <- mean(seed_loc$dispersal)
+se_dispersal <- sd(seed_loc$dispersal)/sqrt(length(seed_loc$dispersal))
+
+# Calculate seed dispersion
+xi <- (x_m - seed_loc$xloc)^2
+yi <- (y_m - seed_loc$yloc)^2
+seed_dispersion <- sum(sqrt(xi + yi))/length(seed_loc$time)
+
 animalTraj %>% 
@@
   geom_path() +
-  geom_point(data=seed_loc, aes(x = xloc, y = yloc))
+  geom_point(data=seed_loc, aes(x = xloc, y = yloc)) +
+  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds
 

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Keep animal and seed locations in one df

@@
 library(dplyr)
+library(tidyr)
 library(ggplot2)
@@
 
-# Determine where the seeds are dropped based on the animal's location.
-seed_loc <- data.frame(seed_id = 1:nseeds, time = grt)
-seed_loc <- merge(animalTraj, seed_loc, by = "time")
-seed_loc$dispersal <- sqrt(seed_loc$xloc^2 + seed_loc$yloc^2)
+animalTraj %>% 
+  left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
+  mutate(disp = sqrt(xloc^2+yloc^2)) -> df
 
@@
 
-animalTraj %>% 
+df %>% 
   ggplot(., aes(x = xloc, y=yloc)) +
   geom_path() +
-  geom_point(data=seed_loc, aes(x = xloc, y = yloc)) +
+  geom_point(data = df %>% drop_na(s.id), aes(x = xloc, y = yloc)) +
   geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
summary measures of seed dispersal with dplyr
calculate all seed summary stats with dplyr

@@
 
+df %>% 
+  drop_na(s.id) %>% 
+  mutate(xi = (mean(xloc)-xloc)^2,
+         yi = (mean(yloc)-yloc)^2) %>% 
+  summarise(x = mean(xloc),
+            y = mean(yloc),
+            av.disp = mean(disp),
+            se.disp = sd(disp)/sqrt(n()),
+            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
+
 # Calculate the mean location of seeds
@@
   geom_path() +
-  geom_point(data = df %>% drop_na(s.id), aes(x = xloc, y = yloc)) +
-  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds
+  geom_point(data = df %>% drop_na(s.id), 
+             aes(x = xloc, y = yloc)) +
+  geom_point(data = s.df,
+             aes(x = x, y = y), color = "Red") # Mean location of seeds
 

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
functions to simulate seed dispersal and calculate summary stats for that.

@@
 ```
+
+```{r}
+sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
+  grt <- round(rgamma(nseeds, shape = 4, scale = 5))
+  t.grt <- max(grt)
+
+  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
+
+  df %>% 
+    left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
+    mutate(disp = sqrt(xloc^2+yloc^2)) -> df
+
+  return(df)
+}
+
+summ_seeds <- function(df = NULL){
+  df %>% 
+  drop_na(s.id) %>% 
+  mutate(xi = (mean(xloc)-xloc)^2,
+         yi = (mean(yloc)-yloc)^2) %>% 
+  summarise(x = mean(xloc),
+            y = mean(yloc),
+            av.disp = mean(disp),
+            se.disp = sd(disp)/sqrt(n()),
+            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
+  return(s.df)
+}
+
+a <- sim_seeds(m.prms = m_1[1])
+summ_seeds(a)
+```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
simulate for one individual with multiple runs

@@
 
-a <- sim_seeds(m.prms = m_1[1])
-summ_seeds(a)
+# a <- sim_seeds(m.prms = m_1[1])
+# summ_seeds(a)
 ```
+
+Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
+```{r message=FALSE}
+
+df <- NULL
+summ.df <- NULL
+
+for(j in 1:1){
+  for(k in 1:3){
+    a <- sim_seeds(m.prms = m_1[j]) %>% 
+      mutate(indiv = as.factor(j),
+             run = paste0("r_",k))
+
+    b <- summ_seeds(a) %>% 
+      mutate(indiv = as.factor(j),
+             run = paste0("r_",k))
+
+    df <- rbind.data.frame(df, a) 
+    summ.df <- rbind.data.frame(summ.df, b) 
+}
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, 
+                #group = run,
+                color = indiv)) +
+  facet_wrap(~run) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  geom_point(data = df %>% drop_na(s.id), 
+             aes(x = xloc, y = yloc)) +
+  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
+  theme_bw()
+```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Adding a radius to plot for se or dispersion

@@
              aes(x = xloc, y = yloc)) +
-  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
+  geom_point(data = summ.df, aes(x = x, y=y, size = dsprsn), color = "black") +
   theme_bw()

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
factor runs to make them in proper order.

--- 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
@@
 
-a <- sim_seeds(m.prms = m_1[1])
-summ_seeds(a)
+# a <- sim_seeds(m.prms = m_1[1])
+# summ_seeds(a)
 ```
+
+Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
+```{r message=FALSE}
+nruns <- 10
+
+df <- NULL
+summ.df <- NULL
+
+for(j in 1:1){
+  for(k in 1:nruns){
+    a <- sim_seeds(m.prms = m_1[j]) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    b <- summ_seeds(a) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    df <- rbind.data.frame(df, a) 
+    summ.df <- rbind.data.frame(summ.df, b) 
+}
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, 
+                #group = run,
+                color = indiv)) +
+  facet_wrap(~run) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  geom_point(data = df %>% drop_na(s.id), 
+             aes(x = xloc, y = yloc)) +
+  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
+  theme_bw()
+
+summ.df %>% 
+  ggplot(., aes(y = dsprsn)) +
+  geom_boxplot()
+```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
visualizing dispersal of seeds

@@
 ```{r message=FALSE}
-nruns <- 10
+nruns <- 100
 
@@
   ggplot(., aes(x = xloc, y=yloc, 
-                #group = run,
+                group = run,
                 color = indiv)) +
-  facet_wrap(~run) +
+  # facet_wrap(~run) +
   geom_path() +
@@
   geom_boxplot()
+
+summ.df %>% 
+  ggplot(., aes(x = av.disp)) +
+  geom_density(color = "blue") + # for the average dispersal per run
+  geom_density(data = df %>% drop_na(s.id),
+                 aes(x = disp)) + # for every seed
+  theme_bw()
 ```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
fit weibull to seed data and subsamps

@@
 ```
+
+Next steps.
+Fit a weibull distribution to the raw seed dispersal data, probably subsample.
+Provide summary stats for the dispersal and dispersion measures.
+
+```{r}
+# s.df <- df %>% drop_na(s.id)
+
+s.df <- df %>% drop_na(s.id) %>% 
+  sample_n(., 50)
+
+library(fitdistrplus)
+
+g <- fitdist(s.df$disp, distr = "weibull")
+summary(g)
+plot(g)
+
+# library(MASS)
+# fitdistr(s.df$disp, densfun = "weibull")
+```

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Testing different plots for 2d distribution of animal movements
fit weibull for a population, with bootstrapping.

@@
 
+df %>% 
+  ggplot(., aes(x = xloc, y = yloc)) +
+  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
+  geom_bin2d() +
+  # geom_hex() +
+  scale_fill_continuous(type = "viridis") +
+  theme_bw()
+
 summ.df %>% 
@@
 ```
+
+# Simulation for population 1
+```{r message=FALSE}
+nruns <- 20
+
+df <- NULL
+summ.df <- NULL
+
+for(j in 1:individual){
+  for(k in 1:nruns){
+    a <- sim_seeds(m.prms = m_1[j]) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    b <- summ_seeds(a) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    df <- rbind.data.frame(df, a) 
+    summ.df <- rbind.data.frame(summ.df, b) 
+}
+}
+```
+
+Visualize animal movement and seed dispersal 
+```{r}
+df %>% 
+  ggplot(., aes(x = xloc, y = yloc)) +
+  facet_wrap(~indiv) +
+  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
+  geom_bin2d() +
+  # geom_hex() +
+  # scale_fill_continuous(type = "viridis") +
+  # geom_point(data = df %>% drop_na(s.id), 
+  #            aes(x = xloc, y = yloc)) +
+  geom_point(data = summ.df, aes(x = x, y=y), color = "red") +
+  theme_bw()
+```
+Seed dispersal kernels
+```{r}
+df %>% 
+  drop_na(s.id) %>% 
+  ggplot(., aes(x = disp, color = indiv)) +
+  geom_density() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
+
+```
+
+Dispersion
+```{r}
+summ.df %>% 
+  ggplot(., aes(y = dsprsn, x = indiv)) + 
+  geom_boxplot()
+```
+```{r}
+s.df <- df %>% drop_na(s.id) %>%
+  group_by(indiv) %>%
+  sample_n(., 50)
+
+# s.df <- df %>% drop_na(s.id)
+
+weib.fits <- NULL
+
+for(i in 1:individual){
+  dat <- s.df %>% 
+    filter(indiv == i)
+  #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+  g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
+  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                          est.scale = as.numeric(g$estimate[2]),
+                          loglik = g$loglik, indiv = i)
+  weib.fits <- rbind.data.frame(weib.fits, prms.weib)
+  # plot(g)
+}
+
+weib.fits
+```
+Bootstrapping?
+```{r}
+weib.boot <- NULL
+
+for(j in 1:10){
+      s.df <- df %>% drop_na(s.id) %>%
+      group_by(indiv) %>%
+      sample_n(., 50)
+
+    # s.df <- df %>% drop_na(s.id)
+
+    weib.fits <- NULL
+
+    for(i in 1:individual){
+      dat <- s.df %>% 
+        filter(indiv == i)
+      #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+      g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
+      prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                              est.scale = as.numeric(g$estimate[2]),
+                              loglik = g$loglik, indiv = i)
+      weib.fits <- rbind.data.frame(weib.fits, prms.weib)
+      # plot(g)
+    }
+
+    weib.boot <- rbind.data.frame(weib.boot, weib.fits %>% mutate(boot = j))
+}
+
+weib.boot
+```
+
+```{r}
+library(Hmisc)
+
+weib.boot %>% 
+  ggplot(., aes(x = factor(indiv), y = est.scale)) +
+  geom_violin() +
+  #geom_boxplot(width = 0.1) +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="red") +
+  theme_bw()
+
+```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Generalizing code to make easier to change averages or number of individuals

@@
 ```{r}
+
+av.mov.rate <- 2
+max.x <- 20
+
 mycols <- c("black", "blue", "purple")
 #create density plots
-curve(dlnorm(x, meanlog=1, sdlog=.3), from=0, to=10, col=mycols[1],
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.3),
+      from=0, to=max.x,
+      col=mycols[1],
       main = 'Log Normally distributed movement rates for three populations', #add title
@@
       )
-curve(dlnorm(x, meanlog=1, sdlog=.5), from=0, to=10, col=mycols[2], add=TRUE)
-curve(dlnorm(x, meanlog=1, sdlog=1), from=0, to=10, col=mycols[3], add=TRUE)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.5), 
+      from=0, to=max.x,
+      col=mycols[2], add=TRUE)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=1), 
+      from=0, to=max.x,
+      col=mycols[3], add=TRUE)
 
@@
 ```{r}
-m_1 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.3),3))
-m_2 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 0.5),3))
-m_3 <- sort(round(rlnorm(5, meanlog = 1, sdlog = 1),3))
+n.individuals <- 5
+m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.3),3))
+m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.5),3))
+m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 1),3))
 ```
@@
 
-range <- c(-0.1,15)
+range <- c(-0.1,max.x+5)
 #create density plots
@@
 
-```{r}
+```{r eval=FALSE}
 t <- 100 # Number of time steps
@@
 
-for(j in 1:individual){
-  for(k in 1:10){
+for(j in 1:n.individuals){
+  for(k in 1:3){
   a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
so many updates.

@@
 library(ggplot2)
+library(cowplot)
 ```
@@
 ```
+
 ```{r}
@@
 
-Population1
-```{r}
-
+## Movement for individuals in the three populations
+```{r eval=FALSE}
+nruns <- 3
+# Population1
 df <- NULL
@@
 for(j in 1:n.individuals){
-  for(k in 1:3){
+  for(k in 1:nruns){
   a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(indiv = as.factor(j),
+           run = paste("r_", k))
+  df <- rbind.data.frame(df, a)
+}
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
+
+# Population2
+df <- NULL
+
+for(j in 1:n.individuals){
+  for(k in 1:nruns){
+  a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+    mutate(indiv = as.factor(j),
+           run = paste("r_", k))
+  df <- rbind.data.frame(df, a)
+}
+}
+
+df %>% 
+  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  geom_path() +
+  scale_color_manual(values = mycols) +
+  theme_bw()
+
+# Population3
+df <- NULL
+
+for(j in 1:n.individuals){
+  for(k in 1:nruns){
+  a <- sim_movement(m_3[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
     mutate(indiv = as.factor(j),
@@
 
-Population2
 ```{r}
+nruns <- 3
+m.data <- data.frame(m_1, m_2, m_3)
 
@@
 
-for(j in 1:individual){
-  for(k in 1:10){
+for(m in 1:3){
+  m.0 <- m.data[m]
+  for(j in 1:n.individuals){
+  for(k in 1:nruns){
   a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
     mutate(indiv = as.factor(j),
-           run = paste("r_", k))
+           run = paste0("r_", k),
+           pop.id = paste0("p_",m))
   df <- rbind.data.frame(df, a)
@@
 
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  theme_bw()
-```
-
-Population3
-```{r}
-
-df <- NULL
-
-for(j in 1:individual){
-  for(k in 1:10){
-  a <- sim_movement(m_3[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
-    mutate(indiv = as.factor(j),
-           run = paste("r_", k))
-  df <- rbind.data.frame(df, a)
-}
 }
@@
   ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+  facet_wrap(~pop.id) +
   geom_path() +
   scale_color_manual(values = mycols) +
-  theme_bw()
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  NULL
 ```
@@
 }
+```
+
+```{r}
 
@@
   geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
-  theme_bw()
+  theme_bw() +
+  labs(title = "Animal seed droppings", caption = "Lines show an individual's trajectory.\n Red dots show all seed droppings.\n Black dots show average location of seed per run") +
+  theme(legend.position = "none") -> p1
+# p1
 
@@
   # geom_hex() +
-  scale_fill_continuous(type = "viridis") +
-  theme_bw()
+  # scale_fill_continuous(type = "viridis") +
+  scale_fill_gradient(low = "grey", high = "black") +
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  labs(title = "Density of animal movement") -> p2
+p2
 
-summ.df %>% 
-  ggplot(., aes(y = dsprsn)) +
-  geom_boxplot()
+cowplot::plot_grid(p1, p2)
 
-summ.df %>% 
-  ggplot(., aes(x = av.disp)) +
-  geom_density(color = "blue") + # for the average dispersal per run
-  geom_density(data = df %>% drop_na(s.id),
-                 aes(x = disp)) + # for every seed
-  theme_bw()
+# summ.df %>% 
+#   ggplot(., aes(y = dsprsn)) +
+#   geom_boxplot()
+# 
+# summ.df %>% 
+#   ggplot(., aes(x = av.disp)) +
+#   geom_density(color = "blue") + # for the average dispersal per run
+#   geom_density(data = df %>% drop_na(s.id),
+#                  aes(x = disp)) + # for every seed
+#   theme_bw()
 ```
@@
 
-for(j in 1:individual){
+for(j in 1:n.individuals){
   for(k in 1:nruns){
@@
 
-Visualize animal movement and seed dispersal 
+Visualize animal movement and seed dispersal.
+It is kind of obvious, but individuals that move further away, also disperse seeds further away and scatter them more.
+Red points are every seed dispersed, black points show the average seed location per run.
+Each panel corresponds to one individual disperser.
 ```{r}
@@
   # scale_fill_continuous(type = "viridis") +
-  # geom_point(data = df %>% drop_na(s.id), 
-  #            aes(x = xloc, y = yloc)) +
-  geom_point(data = summ.df, aes(x = x, y=y), color = "red") +
+  scale_fill_gradient(low = "grey", high = "black") +
+  geom_point(data = df %>% drop_na(s.id),
+             aes(x = xloc, y = yloc), color = "red", alpha = 0.3) +
+  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
   theme_bw()
 ```
-Seed dispersal kernels
+
+Seed dispersal kernels produced by each individual.
 ```{r}
@@
 
-Dispersion
+Dispersion.
+We calculate dispersion for every simulated run.
+Every run means an individual disperser gets 20 seeds, they move until they drop all seeds.
+Then, dispersion measures how far away from each other every seed is.
 ```{r}

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
adding data points to boxplot of dispersion

@@
 summ.df %>% 
-  ggplot(., aes(y = dsprsn, x = indiv)) + 
-  geom_boxplot()
+  ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  theme_bw()
 ```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Dispersion and average dispersal measures.

--- 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
@@
 summ.df %>% 
-  ggplot(., aes(y = dsprsn, x = indiv)) + 
-  geom_boxplot()
+  ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Dispersion") +
+  theme_bw() +
+  theme(legend.position = "none") -> p1
+# p1
+
+summ.df %>% 
+  ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Average dispersal per run") +
+  theme_bw() +
+  theme(legend.position = "none") -> p2
+# p2
+
+plot_grid(p1, p2)
 ```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
comment out chunks not to run

@@
 ```
-```{r}
+```{r eval=FALSE}
+# Sample once for estimating parameters
 s.df <- df %>% drop_na(s.id) %>%
@@
 
-for(i in 1:individual){
+for(i in 1:n.individuals){
   dat <- s.df %>% 
@@
 
-    for(i in 1:individual){
+    for(i in 1:n.individuals){
       dat <- s.df %>% 

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
updating markdown

@@
 date: "8/12/2021"
-output: html_document
+output: 
+  html_document:
+    toc: true
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(fig.width=12, fig.height=6) 
 ```
 
-```{r message=FALSE}
+```{r message=FALSE, warning=FALSE}
 library(dplyr)
@@
   labs(title = "Density of animal movement") -> p2
-p2
+# p2
 
@@
 
-weib.boot
+# weib.boot
 ```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Updating html

@@
 library(cowplot)
+library(fitdistrplus)
+library(Hmisc)
 ```
@@
 
-```{r}
+```{r message=FALSE, warning=FALSE}
 # s.df <- df %>% drop_na(s.id)
@@
   sample_n(., 50)
-
-library(fitdistrplus)
 
@@
 ```{r}
-library(Hmisc)
 

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Editing text

@@
 So, it can also be seasonal.
-Since movement rates can't really be negative, we will use a lognormal distribution to describe this variation in movement rates.
+Since movement rates can't really be negative, we will use a lognormal distribution to describe this variation in movement rates among individuals from a population.
 
@@
 X_i \sim Lognormal(\mu_i, \sigma_i^2)$ describing the distribution of movement rates for an animal population $i$.
-Such animal population's average movement rate being $\mu_i$ and the variance of their movement rates $\sigma_i^2$.
-We can assume we have three different populations, where perhaps some of them have larger home ranges, creating more variance across movement rates.
+Such population's average movement rate being $\mu_i$ and the variance of their movement rates $\sigma_i^2$.
+These average movement rates can depend on homerange size for example, or seasonality (i.e.
+breeding, nesting, etc.).
+We will assume we have three different populations, where perhaps some of them have larger home ranges, creating more variance across movement rates.
 To make things a little easier, we will consider all populations have the same average movement rate $(i.e.
@@
 m_{1,j} = m_{1,1}, ....., m_{1,5})$.
-We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, movement angle, $\theta$, from a uniform distribution, $\theta \sim U(0, 360)$.
-We can visualize the movement for one of the individuals in the first population:
+We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, and movement angle, $\theta$, from a uniform distribution, $\theta \sim U(0, 360)$.
 
@@
 We can look at how those exponential distributions look for each of the individuals in those populations.
+Each curve describes the distribution of movement lengths for each of the five individuals in the first population.
 
-```{r}
+```{r fig.width=12}
 
@@
 #create density plots
+#########################################################################
+# Fist population
 curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
@@
       col=mycols[1],
-      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
+      main = 'Distribution of movement lengths', #add title
       ylab = 'Density', #change y-axis label
+      xlab = "x"
       )
@@
 legend("topright", legend= m_1,
+       col=mycols, lty=1, cex=1.2)
+#########################################################################
+# Second population
+curve(dexp(x, 1/m_2[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2], 
+      col=mycols[1],
+      main = 'Distribution of movement lengths', #add title
+      ylab = 'Density', #change y-axis label
+      xlab = "x"
+      )
+for(i in 2:5){
+  curve(dexp(x, 1/m_2[i]), 
+        from=range[1], to=range[2],
+        col=mycols[i], add=TRUE)
+}
+
+#add legend
+legend("topright", legend= m_2,
+       col=mycols, lty=1, cex=1.2)
+
+#########################################################################
+# Third population
+curve(dexp(x, 1/m_3[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2], 
+      col=mycols[1],
+      main = 'Distribution of movement lengths', #add title
+      ylab = 'Density', #change y-axis label
+      xlab = "x"
+      )
+for(i in 2:5){
+  curve(dexp(x, 1/m_3[i]), 
+        from=range[1], to=range[2],
+        col=mycols[i], add=TRUE)
+}
+
+#add legend
+legend("topright", legend= m_3,
        col=mycols, lty=1, cex=1.2)

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Editing text to match figures

@@
 We can look at how those exponential distributions look for each of the individuals in those populations.
-Each curve describes the distribution of movement lengths for each of the five individuals in the first population.
+Each curve describes the distribution of movement lengths for each of the five individuals in the population.
+Each panel represents one of the populations.
 
@@
 
-mycols <- rainbow(5, s=0.8)
+par(mfrow=c(1,3))
+mycols <- rainbow(n.individuals, s=1)
 
@@
 
-Use ggplot to make multiple rounds of each individual
 ```{r eval=FALSE}
@@
 
-## Movement for individuals in the three populations
+## Individual movement
+For each population, we can simulate the movement of every individual using a random walk.
+Colors correspond to the individuals in the plot above.
+Every individual is sorted based on their average movement rate, so that the first individuals, colored in red, correspond to the smallest movement rate.
+In contrast, individuals described by violet correspond to the individuals with the highest movement rate in that population.
 ```{r eval=FALSE}

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Editing headlines

@@
 
-Now, we get the animals to disperse seeds. Seeds gut retention time are sampled from a gamma distribution.
+## Example individual
+### Simulate movement and seed droppings
+
+Now, we get the animals to disperse seeds.
+To do this, we combine seed gut retention times and animal movement.
+We can visualize this for one individual.
+Each simulation run consists of the animal disperser starting at point (0,0) and getting a number of seeds, each of which has an associated gut retention time $(grt \sim Gamma(4,5))$.
+The simulation run ends once all seeds have dropped.
+For that run, we calculate the average seed location by taking the average of x and y coordinates of all seeds.
+We also calculate seed dispersion as a measure of how close to each other or how scattered the seeds are for that run.
 ```{r eval=FALSE}
@@
 
-Run a simulation for one individual, multiple runs, display animal movement, seed dispersal and print summary for all runs
 ```{r message=FALSE}
 nruns <- 100
-
+ex.i <- 1
 df <- NULL
@@
 
-for(j in 1:1){
+for(j in 1:ex.i){
   for(k in 1:nruns){
@@
   scale_fill_gradient(low = "grey", high = "black") +
+  # geom_point(data = df %>% drop_na(s.id), 
+  #            aes(x = xloc, y = yloc), color = mycols[ex.i], alpha = 0.3) +
+  # geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
   theme_bw() +
@@
 ```
+### Fit distribution function to seed dispersal data
+The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns.
+To get a metric of this seed dispersal, we fit a weibull distribution to the seed dispersal data generated by the previous simulation.
+Every run has 20 seeds, and we did this 100 times, thus we randomly sample 50 seeds to fit a Weibull distribution and get an approximated seed dispersal kernel.
 
-Next steps.
-Fit a weibull distribution to the raw seed dispersal data, probably subsample.
-Provide summary stats for the dispersal and dispersion measures.
-
-```{r message=FALSE, warning=FALSE}
+```{r message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
 # s.df <- df %>% drop_na(s.id)
@@
 g <- fitdist(s.df$disp, distr = "weibull")
+```
+
+```{r}
 summary(g)

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Update html and edit weibull plot titles

@@
 ### Fit distribution function to seed dispersal data
+
 The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns.
@@
                  geom="pointrange", color="red") +
-  theme_bw()
+  labs(title = "Scale") +
+  theme_bw() -> p1
 
+weib.boot %>% 
+  ggplot(., aes(x = factor(indiv), y = est.shape)) +
+  geom_violin() +
+  #geom_boxplot(width = 0.1) +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="red") +
+  labs(title = "Shape") +
+  theme_bw() -> p2
+
+plot_grid(p1, p2)
  ```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
knit

@@
 weib.boot %>% 
+  ggplot(., aes(x = factor(indiv), y = est.shape)) +
+  geom_violin() +
+  #geom_boxplot(width = 0.1) +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="red") +
+  labs(title = "Shape") +
+  theme_bw() -> p1
+
+weib.boot %>% 
   ggplot(., aes(x = factor(indiv), y = est.scale)) +
@@
   labs(title = "Scale") +
-  theme_bw() -> p1
+  theme_bw() -> p2
+
+plot_grid(p1, p2)
+```
+
+**What happens when we do complete pooling of the data instead of analyzing the variation by individuals.
+If instead we take all seed dispersal data and randomly sample seeds, and fit a Weibull kernel?** This is the comparisson between pooling or no pooling of seed dispersal data.
+
+```{r}
+weib.boot.pool <- NULL
+
+for(j in 1:10){
+      s.df <- df %>% drop_na(s.id) %>%
+      sample_n(., 50)
+
+    g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
+
+    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                              est.scale = as.numeric(g$estimate[2]),
+                              loglik = g$loglik, indiv = 0)
+
+    weib.boot.pool <- rbind.data.frame(weib.boot.pool, prms.weib %>% mutate(boot = j))
+}
+
+```
+
+```{r}
+
+weib.boot %>% 
+  rbind.data.frame(., weib.boot.pool) -> weib.boot
 
@@
   labs(title = "Shape") +
+  theme_bw() -> p1
+
+weib.boot %>% 
+  ggplot(., aes(x = factor(indiv), y = est.scale)) +
+  geom_violin() +
+  #geom_boxplot(width = 0.1) +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="red") +
+  labs(title = "Scale") +
   theme_bw() -> p2
@@
 ```
+
+ **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
+ Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach.

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Update html and added comments for next steps.
modifying text

@@
 
-av.mov.rate <- 2
-max.x <- 20
+av.mov.rate <- 1
+max.x <- 10
 
@@
 ```
+
 Bootstrapping?  
+Since there are hundreds or thousands of seeds getting dispersed between all the simulations, we will randomly sample seeds and fit a weibull distribution to generate the seed dispersal kernels.
+The visualization shows the parameters estimated for each bootstrap, for each individual (no pooling) or when we pool all the seed dispersal data (complete pooling).
 ```{r}
+n.boots <- 10
+samp.size <- 30
 weib.boot <- NULL
 
-for(j in 1:10){
+for(j in 1:n.boots){
       s.df <- df %>% drop_na(s.id) %>%
       group_by(indiv) %>%
-      sample_n(., 50)
+      sample_n(., samp.size)
 
@@
 
-```{r}
+```{r eval=FALSE}
 
@@
 
-for(j in 1:10){
+for(j in 1:n.boots){
       s.df <- df %>% drop_na(s.id) %>%
-      sample_n(., 50)
+      sample_n(., samp.size)
 
@@
  **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
- Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach.
+ Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population.
+I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
+ Also, edit colors in violin plots to show each individuals color, and only use the one that includes the population as well. Leave population in black. Change red lines and dot to black too.

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Edit colors in violin plots for weibull fits to dispersal data

@@
 weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.shape)) +
+  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
   geom_violin() +
-  #geom_boxplot(width = 0.1) +
+  scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.1) +
+  # geom_point(color = "grey", alpha = 0.5) +
   stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="red") +
+                 geom="pointrange", color="black") +
   labs(title = "Shape") +
   theme_bw() -> p1
+# p1
 
 weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.scale)) +
+  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
   geom_violin() +
+  scale_color_manual(values = c("black", mycols)) +
   #geom_boxplot(width = 0.1) +
+  # geom_point() +
   stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="red") +
+                 geom="pointrange", color="black") +
   labs(title = "Scale") +
@@
 I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
- Also, edit colors in violin plots to show each individuals color, and only use the one that includes the population as well. Leave population in black. Change red lines and dot to black too.

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Building density plots for weibull seed dispersal kernels for each bootstrap

@@
 
+```{r}
+mycols2 <- c("black", mycols)
+
+weib.curves <- NULL
+
+for(i in 0:5){
+  weib.boot %>% 
+  filter(indiv == i) -> a
+
+  b <- purrr::map(seq(1:nrow(a)), function(y)
+    stat_function(fun = dweibull, args = list(scale = a$est.scale[y], shape = a$est.shape[y]), color = mycols2[i+1], alpha = 0.3))
+
+  weib.curves <- append(weib.curves, b)
+}
+
+# ggplot(data = data.frame(x = c(1, 60)), aes(x)) +
+#   weib.curves +
+#   ylab("Density") + xlab("Distance (m)") +
+#   theme_bw()  +
+#   theme(legend.position = c(0.7, 0.7),
+#         legend.title = element_blank()) 
+df %>%
+  drop_na(s.id) %>% 
+  ggplot(., aes(x = disp)) +
+  geom_histogram(aes(y = ..density..), fill = "grey") +
+  theme_bw() -> p
+# p
+# 
+# p +
+#   stat_function(fun = dweibull, args = list(scale = weib.boot$est.scale[1], shape = weib.boot$est.shape[1]), color = "red")
+
+p + weib.curves
+
+```
+
  **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
update html to compare populations

@@
 ```{r}
-mycols2 <- c("black", mycols)
-
 weib.curves <- NULL
 
-for(i in 0:5){
+for(i in 1:5){
   weib.boot %>% 
@@
   b <- purrr::map(seq(1:nrow(a)), function(y)
-    stat_function(fun = dweibull, args = list(scale = a$est.scale[y], shape = a$est.shape[y]), color = mycols2[i+1], alpha = 0.3))
+    stat_function(fun = dweibull, args = list(scale = a$est.scale[y], shape = a$est.shape[y]), color = mycols[i], alpha = 0.3))
 
@@
 }
+
+weib.boot %>% 
+  filter(indiv == 0) -> c
+weib.curves.pool <- purrr::map(seq(1:nrow(a)), function(y)
+    stat_function(fun = dweibull, args = list(scale = c$est.scale[y], shape = c$est.shape[y]), color = "black", alpha = 0.8))
 
@@
 
-p + weib.curves
+p + 
+  weib.curves +
+  weib.curves.pool
 
@@
 
- **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
- Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population.
-I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
+This is only an example for the first population, but the overall idea is that if an individual has a larger movement rate, it moves more and this tends to translate into moving further away.
+As a consequence, the individuals with higher movement rates disperse seeds farther away and more scattered, in comparison to individuals with lower movement rates.
+Thus, the seed dispersal kernels produced by these individuals also show this trend, where individuals with higher movement rates disperse seeds further.
+This shows with the fatter tails of the kernels, evidenced by the larger scale parameters from fitted Weibull distributions.
+When we pool the seed dispersal data, we ignore individual differences in how each disperser moved the seeds, and we estimate a seed dispersal kernel for that whole population or group.
+
+## Comparisson of seed dispersal kernels across populations  
+These populations all have the same average movement rates, but their variance is different.
+This means that in the first population, all individuals have relatively similar movement rates, whereas in the third population, there is a lot more variation among the movement rates of individuals.
+
+```{r}
+
+# For second population
+df2 <- NULL
+summ.df2 <- NULL
+
+for(j in 1:n.individuals){
+  for(k in 1:nruns){
+    a <- sim_seeds(m.prms = m_2[j]) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    b <- summ_seeds(a) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    df2 <- rbind.data.frame(df2, a) 
+    summ.df2 <- rbind.data.frame(summ.df2, b) 
+  }
+}
+
+# #If we wanted to visualize 
+# summ.df2 %>% 
+#   ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
+#   geom_boxplot() +
+#   geom_point(color = "grey", alpha = 0.5) +
+#   labs(title = "Dispersion") +
+#   theme_bw() +
+#   theme(legend.position = "none") -> p1
+# # p1
+# 
+# summ.df2 %>% 
+#   ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
+#   geom_boxplot() +
+#   geom_point(color = "grey", alpha = 0.5) +
+#   labs(title = "Average dispersal per run") +
+#   theme_bw() +
+#   theme(legend.position = "none") -> p2
+# # p2
+# 
+# plot_grid(p1, p2)
+
+########################################################
+# Bootstrap for individuals
+weib.boot2 <- NULL
+
+for(j in 1:n.boots){
+  s.df <- df2 %>% drop_na(s.id) %>%
+    group_by(indiv) %>%
+    sample_n(., samp.size)
+
+  # s.df <- df %>% drop_na(s.id)
+
+  weib.fits <- NULL
+
+  for(i in 1:n.individuals){
+    dat <- s.df %>% 
+      filter(indiv == i)
+    #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+    g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
+    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                            est.scale = as.numeric(g$estimate[2]),
+                            loglik = g$loglik, indiv = i)
+    weib.fits <- rbind.data.frame(weib.fits, prms.weib)
+    # plot(g)
+  }
+
+  weib.boot2 <- rbind.data.frame(weib.boot2, weib.fits %>% mutate(boot = j))
+}
+
+# Pooled bootstrap
+weib.boot.pool2 <- NULL
+
+for(j in 1:n.boots){
+  s.df <- df2 %>% drop_na(s.id) %>%
+    sample_n(., samp.size)
+
+  g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
+
+  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                          est.scale = as.numeric(g$estimate[2]),
+                          loglik = g$loglik, indiv = 0)
+
+  weib.boot.pool2 <- rbind.data.frame(weib.boot.pool2, prms.weib %>% mutate(boot = j))
+}
+```
+
+```{r}
+
+# For Third population
+df3 <- NULL
+summ.df3 <- NULL
+
+for(j in 1:n.individuals){
+  for(k in 1:nruns){
+    a <- sim_seeds(m.prms = m_3[j]) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    b <- summ_seeds(a) %>% 
+      mutate(indiv = as.factor(j),
+             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
+
+    df3 <- rbind.data.frame(df3, a) 
+    summ.df3 <- rbind.data.frame(summ.df3, b) 
+  }
+}
+
+# #If we wanted to visualize 
+# summ.df3 %>% 
+#   ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
+#   geom_boxplot() +
+#   geom_point(color = "grey", alpha = 0.5) +
+#   labs(title = "Dispersion") +
+#   theme_bw() +
+#   theme(legend.position = "none") -> p1
+# # p1
+# 
+# summ.df3 %>% 
+#   ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
+#   geom_boxplot() +
+#   geom_point(color = "grey", alpha = 0.5) +
+#   labs(title = "Average dispersal per run") +
+#   theme_bw() +
+#   theme(legend.position = "none") -> p2
+# # p2
+# 
+# plot_grid(p1, p2)
+
+########################################################
+# Bootstrap for individuals
+weib.boot3 <- NULL
+
+for(j in 1:n.boots){
+  s.df <- df3 %>% drop_na(s.id) %>%
+    group_by(indiv) %>%
+    sample_n(., samp.size)
+
+  # s.df <- df %>% drop_na(s.id)
+
+  weib.fits <- NULL
+
+  for(i in 1:n.individuals){
+    dat <- s.df %>% 
+      filter(indiv == i)
+    #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+    g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
+    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                            est.scale = as.numeric(g$estimate[2]),
+                            loglik = g$loglik, indiv = i)
+    weib.fits <- rbind.data.frame(weib.fits, prms.weib)
+    # plot(g)
+  }
+
+  weib.boot3 <- rbind.data.frame(weib.boot3, weib.fits %>% mutate(boot = j))
+}
+
+# Pooled bootstrap
+weib.boot.pool3 <- NULL
+
+for(j in 1:n.boots){
+  s.df <- df3 %>% drop_na(s.id) %>%
+    sample_n(., samp.size)
+
+  g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
+
+  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                          est.scale = as.numeric(g$estimate[2]),
+                          loglik = g$loglik, indiv = 0)
+
+  weib.boot.pool3 <- rbind.data.frame(weib.boot.pool3, prms.weib %>% mutate(boot = j))
+}
+```
+
+```{r}
+
+weib.boot.pool %>% 
+  mutate(popu = 1) %>% 
+  bind_rows(., weib.boot.pool2 %>% 
+              mutate(popu = 2)) %>% 
+  bind_rows(., weib.boot.pool3 %>% 
+              mutate(popu = 3)) -> weib.boot.pool
+
+weib.boot.pool %>% 
+  ggplot(., aes(x = factor(popu), y = est.shape, color = factor(popu))) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.1) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="black") +
+  labs(title = "Shape") +
+  theme_bw() -> p1
+# p1
+
+weib.boot.pool %>% 
+  ggplot(., aes(x = factor(popu), y = est.scale, color = factor(popu))) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  #geom_boxplot(width = 0.1) +
+  # geom_point() +
+  stat_summary(fun.data=mean_sdl, mult=1, 
+                 geom="pointrange", color="black") +
+  labs(title = "Scale") +
+  theme_bw() -> p2
+
+plot_grid(p1, p2)
+```

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Updated to comparisson between populations. Simple examples without many runs.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 knitr::opts_chunk$set(fig.width=12, fig.height=6) 
@@
 \mu_1=\mu_1=\mu_3 = 1)$, but different standard deviation $(\sigma_1=0.3, \sigma_2=0.5, \sigma_3=0.5)$.
+Note that variance, $\sigma^2$ is the square of standard deviation, $\sigma$.
 We can visualize the distribution of movement rates for each of these populations:
@@
 #create density plots
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.3),
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.3),
       from=0, to=max.x,
@@
 
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=.5), 
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.5), 
       from=0, to=max.x,

### 2021-08-18 Ch1_movement_rates/Ch1_Appendix_A.Rmd
Actually just changed the name
Added more text.

--- 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
@@
 ```{r}
+set.seed(98)
 
@@
 This shows with the fatter tails of the kernels, evidenced by the larger scale parameters from fitted Weibull distributions.
-When we pool the seed dispersal data, we ignore individual differences in how each disperser moved the seeds, and we estimate a seed dispersal kernel for that whole population or group.
+When we pool the seed dispersal data, we ignore individual differences in how each disperser moved the seeds, and estimate a single dispersal kernel sampling from all the seeds, regardless of who dispersed it.
 
@@
 These populations all have the same average movement rates, but their variance is different.
-This means that in the first population, all individuals have relatively similar movement rates, whereas in the third population, there is a lot more variation among the movement rates of individuals.
+Since we are sampling individuals from these lognormally distributed populations, that means that the populations have similar averages, but in the first population individuals are very similar to each other, whereas in the third population, the individuals have movement rates more spread out.
+By having individuals more spread out, it means that not only are we getting individuals with much higher movement rates, we are also getting them with much lower movement rates as well.
+Depending on the population, we could also ask whether or not all populations follow this lognormal distribution.
+This is more of a behavior question, do all animals move at the same rate?
+meaning all very close to the average.
+Do most animals move at the same rate, except for some very few that like to explore and go far away?
+Perhaps this population needs a more skewed distribution with a longer tail.
+Or perhaps this relates to breeding seasons instead, or droughts.
 

### 2021-08-18 Ch1_movement_rates/Ch1_Appendix_A.Rmd
Dispersion and dispersal comparison among populations

@@
 animalTraj %>% 
-  left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
+  left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
   mutate(disp = sqrt(xloc^2+yloc^2)) -> df
@@
   df %>% 
-    left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
+    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
     mutate(disp = sqrt(xloc^2+yloc^2)) -> df
@@
 weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.shape)) +
+  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
   geom_violin() +
+  scale_color_manual(values = mycols) +
   #geom_boxplot(width = 0.1) +
   stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="red") +
+                 geom="pointrange", color="black") +
   labs(title = "Shape") +
@@
 weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.scale)) +
+  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
   geom_violin() +
+  scale_color_manual(values = mycols) +
   #geom_boxplot(width = 0.1) +
   stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="red") +
+                 geom="pointrange", color="black") +
   labs(title = "Scale") +
@@
 ```
+```{r}
+summ.df %>% 
+  mutate(popu = 1) %>% 
+  bind_rows(summ.df2 %>% 
+              mutate(popu = 2)) %>% 
+  bind_rows(., summ.df3 %>% 
+              mutate(popu = 3)) %>% 
+  ggplot(., aes(y = dsprsn, x = factor(popu), color = factor(popu))) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Dispersion") +
+  theme_bw() +
+  theme(legend.position = "none") -> p1
+# p1
+
+summ.df %>% 
+  mutate(popu = 1) %>% 
+  bind_rows(summ.df2 %>% 
+              mutate(popu = 2)) %>% 
+  bind_rows(., summ.df3 %>% 
+              mutate(popu = 3)) %>% 
+  ggplot(., aes(y = av.disp, x = factor(popu), color = factor(popu))) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Average dispersal per run") +
+  theme_bw() +
+  theme(legend.position = "none") -> p2
+# p2
+
+plot_grid(p1, p2)
+```

### 2021-08-18 Ch1_movement_rates/Ch1_Appendix_A.Rmd
update html

@@
 
-mycols <- c("black", "blue", "purple")
+mycols <- c("red", "green", "blue")
 #create density plots

### 2021-08-18 Ch1_movement_rates/Ch1_theo_sims.R
Starting the script for big simulations

@@ -1,0 +1,35 @@
+# Script to run simulations for theoretical populations with three levels of variation in movement rates
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(cowplot)
+library(fitdistrplus)
+library(Hmisc)
+
+set.seed(98)
+
+av.mov.rate <- 1
+sd.mov.rate <- c(0.3, 0.5, 1)
+max.x <- 10
+
+mycols <- c("red", "green", "blue")
+#create density plots
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[1]),
+      from=0, to=max.x,
+      col=mycols[1],
+      main = 'Log Normally distributed movement rates for three populations', #add title
+      ylab = 'Density', #change y-axis label
+)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[2]),
+      from=0, to=max.x,
+      col=mycols[2], add=TRUE)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[3]),
+      from=0, to=max.x,
+      col=mycols[3], add=TRUE)
+
+#add legend
+legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
+       col=mycols, lty=1, cex=1.2)

### 2021-08-18 Ch1_movement_rates/Ch1_theo_sims.R
Generate movement rates for 30 individuals in each population

@@ -9,6 +9,7 @@ library(Hmisc)
 
 set.seed(98)
 
+# Three populations ---------------------------------------------------------------------
 av.mov.rate <- 1
 sd.mov.rate <- c(0.3, 0.5, 1)
 max.x <- 10
@@ -33,3 +34,9 @@ curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[3]),
 #add legend
 legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
        col=mycols, lty=1, cex=1.2)
+
+## Simulate movement rates -------------------------------------------------------------
+n.individuals <- 30
+m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[1]),3))
+m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[2]),3))
+m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[3]),3))

### 2021-08-18 Ch1_movement_rates/Ch1_theo_sims.R
Vis exponential dist for 30 indivs in 3 populations

@@ -40,3 +40,67 @@ n.individuals <- 30
 m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[1]),3))
 m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[2]),3))
 m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[3]),3))
+
+## Visualize individual differences ----------------------------------------------------
+
+par(mfrow=c(1,3))
+mycols <- rainbow(n.individuals, s=1)
+
+range <- c(-0.1,max.x+5)
+#create density plots
+### Fist population--------------------------------------------------------------------
+curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2],
+      col=mycols[1],
+      main = 'Distribution of movement lengths', #add title
+      ylab = 'Density', #change y-axis label
+      xlab = "x"
+)
+for(i in 2:5){
+  curve(dexp(x, 1/m_1[i]),
+        from=range[1], to=range[2],
+        col=mycols[i], add=TRUE)
+}
+
+#add legend
+legend("topright", legend= m_1,
+       col=mycols, lty=1, cex=1.2)
+
+
+### Second population----------------------------------------------------------------
+curve(dexp(x, 1/m_2[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2],
+      col=mycols[1],
+      main = 'Distribution of movement lengths', #add title
+      ylab = 'Density', #change y-axis label
+      xlab = "x"
+)
+for(i in 2:5){
+  curve(dexp(x, 1/m_2[i]),
+        from=range[1], to=range[2],
+        col=mycols[i], add=TRUE)
+}
+
+#add legend
+legend("topright", legend= m_2,
+       col=mycols, lty=1, cex=1.2)
+
+
+
+### Third population ---------------------------------------------------------------
+curve(dexp(x, 1/m_3[1]), #notice rate for exponential is 1/movement rate.
+      from=range[1], to=range[2],
+      col=mycols[1],
+      main = 'Distribution of movement lengths', #add title
+      ylab = 'Density', #change y-axis label
+      xlab = "x"
+)
+for(i in 2:5){
+  curve(dexp(x, 1/m_3[i]),
[…]

### 2021-08-18 Ch1_movement_rates/Ch1_theo_sims.R
Added functions

@@ -104,3 +104,48 @@ for(i in 2:5){
 #add legend
 legend("topright", legend= m_3,
        col=mycols, lty=1, cex=1.2)
+
+# Functions --------------------------------------------------------------------------
+sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
+  tru.rate <- round(prm, 3)
+  movedist <- rexp(t, rate = 1/tru.rate)
+  angle <- runif(t, min = 0, max = 360)
+  distx <- movedist*cos(angle)
+  xloc <- c(0, cumsum(distx))
+  disty <- movedist*sin(angle)
+  yloc <- c(0, cumsum(disty))
+  animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
+  if(plot.it == TRUE){
+    plot(x = xloc, y = yloc, type = "l", main = paste("Rate=",tru.rate))
+  }
+  if(return.data.frame == TRUE){
+    return(animalTraj)
+  }
+}
+
+sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
+  grt <- round(rgamma(nseeds, shape = 4, scale = 5))
+  t.grt <- max(grt)
+
+  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
+
+  df %>%
+    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>%
+    mutate(disp = sqrt(xloc^2+yloc^2)) -> df
+
+  return(df)
+}
+
+summ_seeds <- function(df = NULL){
+  df %>%
+    drop_na(s.id) %>%
+    mutate(xi = (mean(xloc)-xloc)^2,
+           yi = (mean(yloc)-yloc)^2) %>%
+    summarise(x = mean(xloc),
+              y = mean(yloc),
+              av.disp = mean(disp),
+              se.disp = sd(disp)/sqrt(n()),
+              dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
+  return(s.df)
+}
+

### 2021-08-19 Ch1_movement_rates/Ch1_theo_sims.R
Settled on colors for individuals

@@ -45,6 +45,8 @@ m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.ra
 
 par(mfrow=c(1,3))
 mycols <- rainbow(n.individuals, s=1)
+mycols <- colorRampPalette(c("#F46036", "#5B85AA", "#414770", "#372248", "#171123"))(n.individuals)
+mycols <- colorRampPalette(c("#ffba08", "#d00000", "#03071e"))(n.individuals)
 
 range <- c(-0.1,max.x+5)
 #create density plots
@@ -56,7 +58,7 @@ curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
       ylab = 'Density', #change y-axis label
       xlab = "x"
 )
-for(i in 2:5){
+for(i in 2:n.individuals){
   curve(dexp(x, 1/m_1[i]),
         from=range[1], to=range[2],
         col=mycols[i], add=TRUE)
@@ -64,7 +66,7 @@ for(i in 2:5){
 
 #add legend
 legend("topright", legend= m_1,
-       col=mycols, lty=1, cex=1.2)
+       col=mycols, lty=1, cex=1.2, lwd = 2)
 
 
 ### Second population----------------------------------------------------------------
@@ -75,7 +77,7 @@ curve(dexp(x, 1/m_2[1]), #notice rate for exponential is 1/movement rate.
       ylab = 'Density', #change y-axis label
       xlab = "x"
 )
-for(i in 2:5){
+for(i in 2:n.individuals){
   curve(dexp(x, 1/m_2[i]),
         from=range[1], to=range[2],
         col=mycols[i], add=TRUE)
@@ -83,7 +85,7 @@ for(i in 2:5){
 
 #add legend
 legend("topright", legend= m_2,
-       col=mycols, lty=1, cex=1.2)
+       col=mycols, lty=1, cex=1.2, lwd = 2)
 
 
 
@@ -95,7 +97,7 @@ curve(dexp(x, 1/m_3[1]), #notice rate for exponential is 1/movement rate.
       ylab = 'Density', #change y-axis label
       xlab = "x"
 )
-for(i in 2:5){
+for(i in 2:n.individuals){
   curve(dexp(x, 1/m_3[i]),
         from=range[1], to=range[2],
         col=mycols[i], add=TRUE)
@@ -103,7 +105,7 @@ for(i in 2:5){
 
 #add legend
[…]

### 2021-08-19 Ch1_movement_rates/Ch1_Appendix_A.Rmd
extra line
Fix parameters

@@
     for(k in 1:nruns){
-  a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
+      a <- sim_movement(m.0[j,], plot.it = FALSE, return.data.frame = TRUE) %>% 
         mutate(indiv = as.factor(j),
                run = paste0("r_", k),
-           pop.id = paste0("p_",m))
+               popu = paste0("p_",m))
       df <- rbind.data.frame(df, a)
@@
   }
-
 }
@@
   ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  facet_wrap(~pop.id) +
+  facet_wrap(~popu) +
   geom_path() +

### 2021-08-19 Ch1_movement_rates/Ch1_theo_sims.R
Testing plot

@@ -153,31 +153,125 @@ summ_seeds <- function(df = NULL){
 
 # Simulate seed dispersal ------------------------------------------------------------
 ## Animal movement first ---------------------------------------------------------------
-nruns <- 3
+
+## Don't run this, too heavy of a plot and you can't really see anything.
+# nruns <- 3
+# m.data <- data.frame(m_1, m_2, m_3)
+
+# df <- NULL
+#
+# for(m in 1:3){
+#   m.0 <- m.data[m]
+#   for(j in 1:n.individuals){
+#     for(k in 1:nruns){
+#       a <- sim_movement(m.0[j,], plot.it = FALSE, return.data.frame = TRUE) %>%
+#         mutate(indiv = as.factor(j),
+#                run = paste0("r_", k),
+#                pop.id = paste0("p_",m))
+#       df <- rbind.data.frame(df, a)
+#     }
+#   }
+#
+# }
+#
+#
+# df %>%
+#   ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
+#   facet_wrap(~pop.id) +
+#   geom_path() +
+#   scale_color_manual(values = mycols) +
+#   theme_bw() +
+#   theme(legend.position = "bottom") +
+#   NULL
+
+## Generate seed dispersal data -----------------------------------------------
 m.data <- data.frame(m_1, m_2, m_3)
+kruns <- 100
+nseeds <- 20
 
 df <- NULL
+summ.df <- NULL
 
 for(m in 1:3){
   m.0 <- m.data[m]
   for(j in 1:n.individuals){
-    for(k in 1:nruns){
-      a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>%
+    for(k in 1:kruns){
+      a <- sim_seeds(m.prms = m.0[j,], nseeds = nseeds) %>%
         mutate(indiv = as.factor(j),
-               run = paste0("r_", k),
-               pop.id = paste0("p_",m))
+               run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
+               popu = as.factor(m))
+
+      b <- summ_seeds(a) %>%
+        mutate(indiv = as.factor(j),
+               run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
+               popu = as.factor(m))
+
       df <- rbind.data.frame(df, a)
+      summ.df <- rbind.data.frame(summ.df, b)
     }
   }
-
 }
 
[…]

### 2021-10-06 Ch1_movement_rates/complete_pooling.R
minor changes in names

@@ -236,8 +236,8 @@ save(cp.df, cp.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_cp.RData"
 
 ### CP Kernel ------------------------------------------------------------
 # sample with replacement groups of 100 seeds and fit weibull , here are the parameters.
-n.boots <- 100
-samp.size <- 50
+n.boots <- 1000
+samp.size <- 100
 weib.boot.cp <- NULL
 
 for(j in 1:n.boots){

### 2021-10-06 Ch1_movement_rates/no_pooling.R

@@ -152,8 +152,8 @@ save(np.df, np.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_np.RData"
 # plot_grid(np_p1, np_p2)
 
 ### Kernel -----
-n.boots <- 100
-samp.size <- 50
+n.boots <- 1000
+samp.size <- 100
 weib.boot.np <- NULL
 
 for(j in 1:n.boots){
@@ -172,7 +172,8 @@ for(j in 1:n.boots){
 
   for(i in 1:3){
     dat <- s.df %>%
-      filter(popu == i)
+      filter(popu == i) %>%
+      filter(disp != 0)
 
     g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
     #g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))

### 2021-10-06 Ch1_movement_rates/partial_pooling.R

@@ -139,12 +139,12 @@ for(j in 1:7){
     a <- sim_seeds(m.prms = fam_moverate$movrate[j], nseeds = nseeds) %>%
       mutate(fam_g = fam_moverate$fam_g[j],
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
-             model = paste0("pp_1"))
+             model = paste0("pp"))
 
     b <- summ_seeds(a) %>%
       mutate(fam_g = fam_moverate$fam_g[j],
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
-             model = paste0("pp_1"))
+             model = paste0("pp"))
 
     pp.df <- rbind.data.frame(pp.df, a)
     pp.summ.df <- rbind.data.frame(pp.summ.df, b)
@@ -156,8 +156,8 @@ save(pp.df, pp.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_pp.RData"
 
 
 # sample with replacement groups of 100 seeds and fit weibull , here are the parameters.
-n.boots <- 100
-samp.size <- 50
+n.boots <- 1000
+samp.size <- 100
 weib.boot.pp <- NULL
 
 for(j in 1:n.boots){

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
All figures in one place

---
title: "Implications of animal movement rate variation in spatial patterns of seed dispersal"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(Hmisc)
```

```{r}
set.seed(98)

# Source functions -----------------------------------------------------------------

source("Ch1_movement_rates/Ch1_functions.R")

# LOAD the data ------------------------------------------------------------------------

load(file = "Ch1_movement_rates/ptpl.RData")

null_moverate <- data.frame(Bird_ID = unique(ptpl$Bird_ID), movrate = mean(ptpl$mpm))

indiv_moverate <- ptpl %>%
  group_by(Bird_ID, fam_g) %>%
  summarise(movrate = mean(mpm))

fam_moverate <- ptpl %>%
  group_by(fam_g) %>%
  summarise(movrate = mean(mpm),
            sd = sd(mpm))

ids <- ptpl %>% distinct(., Bird_ID, fam_g)

# Average movement rate for this 'population'
mean(indiv_moverate$movrate)
mean(ptpl$mpm)

# Color palette ----------------------------------------
my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")

# Vis Movement Rates ---------------------------------------------
# Fit a lognormal to the distribution of movement rates
# Keep in mind these are all males.

logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
# Mean using the fit
exp(logfit$estimate[1])

# Visualize distribution and data points
vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  geom_point(size = 3, alpha = 0.8) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to movement rates",
       subtitle = "Each dot is an individual") +
  geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
```

```{r}
# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:

mean(indiv_moverate$movrate)
# 27.94211 meters/minute

# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.

## Compare exponential movement distances to full dataset ----------------------------------

movrate_cp <- mean(indiv_moverate$movrate)
movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))

# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
#
# test %>%
#   ggplot(., aes(x = mpm)) +
#   geom_histogram(aes(y = ..density..)) +
#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")

ptpl %>%
  ggplot(., aes(x = mpm)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
  labs(title = "Histogram of movement distances per minute from data set",
       x = "Movement distance per minute",
       y = "Density",
       caption = "Orange line is exponential density using average movement rate for population \n
       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/Movement_dist_comparison_2exp.png", width = 6, height = 4, units = "in")

## Sample run -------

# Which estimate to use?
# So, we are saying here that complete pooling takes the average of all the data as one. We took all the data, then fitted a lognormal distribution. So, the parameter we use, is the average movement rate that the lognormal gives us. Since we are assuming that the lognormal distribution will describe this population's movement rates across individuals. So, we use the expected value (mean) of the fit to describe the average movement rate of the population.

movrate_cp_ln

# How many seeds to use? Landon used 100 because he was taking averages.
# I guess we are focusing on a very short time frame: what does the bird do after it eats those seeds at one tree, and how does it move until it drops them all? So, only use 5 seeds.

nseeds <- 5

# Let's visualize one run quickly

sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
# Print the data frame with seed info
test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
test_run

# Calculate summary for seeds in this run
summ_test_run <- summ_seeds(test_run)
# Visualize this one run:
test_run %>%
  ggplot(., aes(x = xloc, y = yloc)) +
  geom_path(color = "#2D3335") +
  geom_point(aes(x=0, y=0), color = "#87A986", size = 3) +
  geom_point(data = test_run %>% drop_na(s.id),
             aes(x = xloc, y = yloc)) +
  # geom_point(data = summ_test_run,
  #            aes(x = x, y = y), color = "#59879A") +
  labs(x = "x", y = "y",
       title = "Example of one simulation run") +
  theme_bw() -> A

test_run %>%
  ggplot(., aes(x = xloc, y = yloc)) +
  geom_path(color = "white", alpha = 0.1) +
  geom_point(aes(x=0, y=0), color = "#87A986", size = 3) +
  geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = "#87A986", lty = 2) +
  geom_point(data = test_run %>% drop_na(s.id),
             aes(x = xloc, y = yloc)) +
  geom_segment(data = test_run %>% drop_na(s.id),
               aes(x = xloc, y = yloc, xend = summ_test_run$x, yend = summ_test_run$y), lty = 2, color = "#E2BF80") +
  geom_point(data = summ_test_run,
             aes(x = x, y = y), color = "#E2BF80", size = 5) +
  labs(x = "x", y = "y",
       title = "Average dispersal and dispersion per run") +
  theme_bw() -> B

test_run %>%
  ggplot(., aes(x = xloc, y = yloc)) +
  geom_path(color = "white", alpha = 0.1) +
  #geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = "#87A986", lty = 2) +
  geom_point(data = test_run %>% drop_na(s.id),
             aes(x = xloc, y = yloc)) +
  geom_segment(data = test_run %>% drop_na(s.id),
               aes(x = xloc, y = yloc, xend = 0, yend = 0), lty = 2, color = "black") +
  geom_point(data = summ_test_run,
             aes(x = x, y = y), color = "#E2BF80", size = 3) +
  geom_point(aes(x=0, y=0), color = "#87A986", size = 5) +
  labs(x = "x", y = "y",
       title = "Seed dispersal distance from parent tree") +
  theme_bw() -> C

test_run %>%
  drop_na(s.id) %>%
  ggplot(., aes(x = disp)) +
    geom_histogram(bins = 30) +
  labs(x = "Dispersal distance in meters", y = "Count",
       title = "Seed dispersal distance for each seed") +
  theme_bw() -> D

plot_grid(A, B, C, D, labels = "AUTO")

# ggsave2(filename = "Ch1_movement_rates/Figures/Ex_one_sim_run.png")
```

```{r}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(pp_1, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
exp(logfit_fam$estimate[1])

# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
  #               color = "black", alpha = 0.8, size = 1) +
  # geom_point(size = 3, alpha = 0.8) +
  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to family group movement rates") +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")

```

```{r}
## PP w/fam moverates ---------------------------------------
# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.

fam_moverate %>%
  arrange(., movrate) -> fam_moverate

fam_moverate %>%
  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
  geom_point(size = 3) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  xlim(0, 60) +
  labs(title = "Lognormal fitted to family group",
       x = "Movement rate",
       y = "Density") +
  scale_color_viridis_c() +
  theme_bw() +
  theme(legend.position = "none") -> pp_logfit

mycols2 <- viridisLite::viridis(7)
expcurves_pp1 <- purrr::map(seq(1:7), function(y)
  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))

ggplot() +
  expcurves_pp1 +
  xlim(-1, 125) +
  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> pp_expdraws

cowplot::plot_grid(pp_logfit, pp_expdraws)
# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
```

```{r}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
exp(logfit_fam$estimate[1])

# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  geom_point(size = 3, alpha = 0.8) +
  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Average movement rates lognormal fits") +
  theme_bw()
```

```{r}
# This one looks at individual variation.
# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')

n.individuals <- 20
m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))

logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0)) +
  geom_point(size = 5) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
  # scale_color_viridis_d(option="magma") +
  scale_color_viridis_d() +
  xlim(0, 60) +
  labs(title = "Sampling individuals from lognormal",
       x = "Movement rate",
       y = "Density") +
  theme_bw() +
  theme(legend.position = "none") -> plot.logfitdraw

plot.logfitdraw

mycols <- viridisLite::viridis(20)

expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))

expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))

expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))

logfitdraw %>%
  ggplot() +
  expcurves_m1 +
  expcurves_m2 +
  expcurves_m3 +
  xlim(-1, 125) +
  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> expdraws
expdraws

cowplot::plot_grid(plot.logfitdraw, expdraws)

# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
```

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")

# Dispersion and Dispersal --------------------------------------------------------------------

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, popu) %>%
  mutate(model = "cp") %>%
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "pp")) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn, popu) %>%
              mutate(model = paste0("np_", popu))) %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> disp_df

disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

plot_grid(p_dispersal, p_dispersion)

# ggsave2(filename = "Ch1_movement_rates/Figures/disp_plot.png")

```

```{r}

# Weibull fit ------------------------------------------------------------

weib.boot.cp %>%
  mutate(model = "cp") %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.pp %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.np %>%
              mutate(model = paste0("np_", popu)) %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> joint_weib

joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

plot_grid(weib_shape, weib_scale)

# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")

```

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Display just the figures

@@
 
-```{r}
+```{r include=FALSE}
 set.seed(98)
@@
 # Average movement rate for this 'population'
-mean(indiv_moverate$movrate)
-mean(ptpl$mpm)
+# mean(indiv_moverate$movrate)
+# mean(ptpl$mpm)
 
@@
 exp(logfit$estimate[1])
+```
 
+```{r}
 # Visualize distribution and data points
@@
 
-```{r}
+```{r include=FALSE}
 # The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:
 
-mean(indiv_moverate$movrate)
+# mean(indiv_moverate$movrate)
 # 27.94211 meters/minute
@@
 
+```
+
+```{r}
 # ggsave2(filename = "Ch1_movement_rates/Figures/Movement_dist_comparison_2exp.png", width = 6, height = 4, units = "in")
@@
 
-movrate_cp_ln
+# movrate_cp_ln
 
@@
 
-sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
+#sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
 # Print the data frame with seed info
 test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
-test_run
+#test_run
 
@@
 
-```{r}
+```{r include=FALSE}
 ## Visualize mov rates ---------------
@@
 # Mean using the fit
-exp(logfit_fam$estimate[1])
+# exp(logfit_fam$estimate[1])
 
+```
+
+```{r}
 # Visualize distribution and data points
@@
 
+```{r include=FALSE}
+## Visualize mov rates ---------------
+pp_1 <- sort(round(fam_moverate$movrate,3))
+
+### Compare lognorm fits CP and PP -----------
+
+logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
+# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
+
+# Mean using the fit
+exp(logfit_fam$estimate[1])
+
+```
+
+```{r}
+# Visualize distribution and data points
+vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
+
+indiv_moverate %>%
+  ggplot(., aes(x = movrate, y = 0.002)) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
+                color = "black", alpha = 0.8, size = 1) +
+  geom_point(size = 3, alpha = 0.8) +
+  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
+  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
+                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
+                color = my.cols1[4], alpha = 0.8, size = 1) +
+  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
+  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
+  labs(x = "Movement Rate (meters/minute)", y = "Density",
+       title = "Average movement rates lognormal fits") +
+  theme_bw()
+```
+
 ```{r}
@@
   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
+                color = my.cols1[4], alpha = 0.8, size = 1) +
   xlim(0, 60) +
@@
 
-```{r}
-## Visualize mov rates ---------------
-pp_1 <- sort(round(fam_moverate$movrate,3))
-
-### Compare lognorm fits CP and PP -----------
-
-logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-
-# Mean using the fit
-exp(logfit_fam$estimate[1])
-
-# Visualize distribution and data points
-vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
-  geom_point(size = 3, alpha = 0.8) +
-  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Average movement rates lognormal fits") +
-  theme_bw()
-```
-
-```{r}
+```{r include=FALSE}
 # This one looks at individual variation.
@@
 expdraws
+
+```
+
+```{r}
 

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Added ppi

@@
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
+load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 
@@
               mutate(model = paste0("np_", popu))) %>% 
-  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> disp_df
+  bind_rows(., ppi.summ.df %>% 
+              dplyr::select(av.disp, dsprsn, model) %>% 
+              mutate(model = "ppi")) %>% 
+  mutate(model = factor(model, levels = c("cp", "pp", "ppi","np_1", "np_2", "np_3"))) -> disp_df
 

### 2021-10-06 R/data_generation.R

@@ -207,13 +207,15 @@ save(np.df, np.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_np.RData"
 
 n.individuals <- 6
 
-f.data <- NULL
+f.data <- data.frame(indiv = 1:n.individuals)
 
 for(i in 1:7){
   samp <- rlnorm(n.individuals, meanlog = fam_moverate$logpar[i], sdlog = logfit$estimate[2])
-  f.data <- bind_cols(f.data, samp)
-  names(f.data)[i] <- paste(fam_moverate$fam_g[i])
+  f.data <- cbind.data.frame(f.data, samp)
+  names(f.data)[i+1] <- paste(fam_moverate$fam_g[i])
 }
+
+f.data <- f.data[2:8]
 
 # NP Generate data
 kruns <- 1000
@@ -241,8 +243,6 @@ for(f in 1:7){
     }
   }
 }
-
-
 
 
 save(ppi.df, ppi.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_ppi.RData")

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.R
Cleaning up since new scripts have everything better organized

@@ -1,100 +1,0 @@
-# Script to run simulations using parameters from aracari movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# Bring data --------------------------------------------
-load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
-load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
-load("Ch1_movement_rates/sims_backup/datagen_np.RData")
-
-load("Ch1_movement_rates/sims_backup/weib_cp.RData")
-load("Ch1_movement_rates/sims_backup/weib_pp.RData")
-load("Ch1_movement_rates/sims_backup/weib_np.RData")
-
-# Dispersion and Dispersal --------------------------------------------------------------------
-
-cp.summ.df %>%
-  dplyr::select(av.disp, dsprsn, popu) %>%
-  mutate(model = "cp") %>%
-  bind_rows(., pp.summ.df %>%
-              dplyr::select(av.disp, dsprsn, model)) %>%
-  bind_rows(., np.summ.df %>%
-              dplyr::select(av.disp, dsprsn, popu) %>%
-              mutate(model = paste0("np_", popu))) -> disp_df
-
-disp_df %>%
-  group_by(., model) %>%
-  sample_n(., 100) %>%
-  ggplot(., aes(y = dsprsn, x = model)) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> p_dispersion
-
-disp_df %>%
-  group_by(., model) %>%
-  sample_n(., 100) %>%
-  ggplot(., aes(y = av.disp, x = model)) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> p_dispersal
-
-plot_grid(p_dispersal, p_dispersion)
-
-ggsave2(filename = "Ch1_movement_rates/Figures/disp_plot.png")
-
-
-
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_data_analysis.R

@@ -1,0 +1,103 @@
+# Analyze data from the Ch1_data_generation.R script
+# Includes fitting weibull distributions to seed dispersal distances to estimate seed dispersal kernel
+# LIBRARIES --------------------------------------------------------------------------------
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(cowplot)
+library(fitdistrplus)
+library(Hmisc)
+
+set.seed(98)
+
+# Bring data --------------------------------------------
+load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
+load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
+load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
+load("Ch1_movement_rates/sims_backup/datagen_np.RData")
+
+# CP Kernel ------------------------------------------------------------
+# sample with replacement groups of 100 seeds and fit weibull , here are the parameters.
+n.boots <- 1000
+samp.size <- 100
+weib.boot.cp <- NULL
+
+for(j in 1:n.boots){
+  s.df <- cp.df %>% drop_na(s.id) %>%
+    sample_n(., samp.size) %>%
+    mutate(disp = round(disp, digits = 2))
+
+  g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+
+
+  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                          est.scale = as.numeric(g$estimate[2]),
+                          loglik = g$loglik,
+                          model = "cp")
+  weib.boot.cp <- rbind.data.frame(weib.boot.cp, prms.weib %>% mutate(boot = j))
+}
+
+save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
+
+# PP Kernel ---------------------------------------------------------------------
+n.boots <- 1000
+samp.size <- 100
+weib.boot.pp <- NULL
+
+for(j in 1:n.boots){
+  s.df <- pp.df %>% drop_na(s.id) %>%
+    sample_n(., samp.size) %>%
+    mutate(disp = round(disp, digits = 2))
+
+  g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+
+
+  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_data_sims.R

@@ -1,689 +1,0 @@
-# Script to run simulations using parameters from aracari movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# LOAD the data ------------------------------------------------------------------------
-
-data(ptpl)
-
-null_moverate <- data.frame(Bird_ID = unique(ptpl$Bird_ID), movrate = mean(ptpl$mpm))
-
-indiv_moverate <- ptpl %>%
-  group_by(Bird_ID, fam_g) %>%
-  summarise(movrate = mean(mpm))
-
-fam_moverate <- ptpl %>%
-  group_by(fam_g) %>%
-  summarise(movrate = mean(mpm),
-            sd = sd(mpm))
-
-ids <- ptpl %>% distinct(., Bird_ID, fam_g)
-
-# Visualize the movement rates on top of a density distribution, so that we can "assume" these movement rates are sampled from that distribution. The case of theory is with a lognormal distribution.
-
-indiv_moverate %>%
-  arrange(., movrate) %>%
-  ggplot(., aes(x = movrate)) +
-  geom_histogram()
-
-
-# Average movement rate for this 'population'
-mean(indiv_moverate$movrate)
-mean(ptpl$mpm)
-sum.indivs <- summary(indiv_moverate$movrate)
-
-
-# Color palette ----------------------------------------
-my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
-
-# Vis Movement Rates ---------------------------------------------
-# Fit a lognormal to the distribution of movement rates
-# Keep in mind these are all males.
-
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-# Mean using the fit
-exp(logfit$estimate[1])
-
-# Visualize distribution and data points
-vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  geom_point(size = 3, alpha = 0.8) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_theo_sims.R

@@ -1,777 +1,0 @@
-# Script to run simulations for theoretical populations with three levels of variation in movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# Three populations ---------------------------------------------------------------------
-av.mov.rate <- 1
-sd.mov.rate <- c(0.3, 0.5, 1)
-max.x <- 10
-
-mycols <- c("red", "green", "blue")
-#create density plots
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[1]),
-      from=0, to=max.x,
-      col=mycols[1],
-      main = 'Log Normally distributed movement rates for three populations', #add title
-      ylab = 'Density', #change y-axis label
-)
-
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[2]),
-      from=0, to=max.x,
-      col=mycols[2], add=TRUE)
-
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[3]),
-      from=0, to=max.x,
-      col=mycols[3], add=TRUE)
-
-#add legend
-legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
-       col=mycols, lty=1, cex=1.2)
-
-## Simulate movement rates -------------------------------------------------------------
-n.individuals <- 20
-m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[1]),3))
-m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[2]),3))
-m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[3]),3))
-
-## Visualize individual differences ----------------------------------------------------
-
-par(mfrow=c(1,3))
-mycols <- rainbow(n.individuals, s=1)
-mycols <- colorRampPalette(c("#F46036", "#5B85AA", "#414770", "#372248", "#171123"))(n.individuals)
-mycols <- colorRampPalette(c("#ffba08", "#d00000", "#03071e"))(n.individuals)
-
-range <- c(-0.1,max.x+5)
-#create density plots
[…]

### 2021-10-06 Ch1_movement_rates/complete_pooling.R

@@ -1,290 +1,0 @@
-# Script to run simulations using parameters from aracari movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# Source functions -----------------------------------------------------------------
-source("Ch1_movement_rates/Ch1_functions.R")
-
-# LOAD the data ------------------------------------------------------------------------
-
-data(ptpl)
-
-null_moverate <- data.frame(Bird_ID = unique(ptpl$Bird_ID), movrate = mean(ptpl$mpm))
-
-indiv_moverate <- ptpl %>%
-  group_by(Bird_ID, fam_g) %>%
-  summarise(movrate = mean(mpm))
-
-fam_moverate <- ptpl %>%
-  group_by(fam_g) %>%
-  summarise(movrate = mean(mpm),
-            sd = sd(mpm))
-
-ids <- ptpl %>% distinct(., Bird_ID, fam_g)
-
-# Average movement rate for this 'population'
-mean(indiv_moverate$movrate)
-mean(ptpl$mpm)
-
-# Color palette ----------------------------------------
-my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
-
-# Vis Movement Rates ---------------------------------------------
-# Fit a lognormal to the distribution of movement rates
-# Keep in mind these are all males.
-
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-# Mean using the fit
-exp(logfit$estimate[1])
-
-# Visualize distribution and data points
-vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  geom_point(size = 3, alpha = 0.8) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Lognormal fit to movement rates",
-       subtitle = "Each dot is an individual") +
[…]

### 2021-10-06 Ch1_movement_rates/no_pooling.R

@@ -1,223 +1,0 @@
-# Script to run simulations using parameters from aracari movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# Source functions -----------------------------------------------------------------
-source("Ch1_movement_rates/Ch1_functions.R")
-
-# LOAD the data ------------------------------------------------------------------------
-
-data(ptpl)
-
-null_moverate <- data.frame(Bird_ID = unique(ptpl$Bird_ID), movrate = mean(ptpl$mpm))
-
-indiv_moverate <- ptpl %>%
-  group_by(Bird_ID, fam_g) %>%
-  summarise(movrate = mean(mpm))
-
-fam_moverate <- ptpl %>%
-  group_by(fam_g) %>%
-  summarise(movrate = mean(mpm),
-            sd = sd(mpm))
-
-ids <- ptpl %>% distinct(., Bird_ID, fam_g)
-
-# Average movement rate for this 'population'
-mean(indiv_moverate$movrate)
-mean(ptpl$mpm)
-
-# Color palette ----------------------------------------
-my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
-# No pooling --------------------------------------------
-# This one looks at individual variation.
-# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
-
-n.individuals <- 20
-m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-
-logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)
-
-indiv_moverate %>%
[…]

### 2021-10-06 Ch1_movement_rates/partial_pooling.R

@@ -1,210 +1,0 @@
-# Script to run simulations using parameters from aracari movement rates
-# LIBRARIES --------------------------------------------------------------------------------
-
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
-
-set.seed(98)
-
-# Source functions -----------------------------------------------------------------
-source("Ch1_movement_rates/Ch1_functions.R")
-
-# LOAD the data ------------------------------------------------------------------------
-
-data(ptpl)
-
-null_moverate <- data.frame(Bird_ID = unique(ptpl$Bird_ID), movrate = mean(ptpl$mpm))
-
-indiv_moverate <- ptpl %>%
-  group_by(Bird_ID, fam_g) %>%
-  summarise(movrate = mean(mpm))
-
-fam_moverate <- ptpl %>%
-  group_by(fam_g) %>%
-  summarise(movrate = mean(mpm),
-            sd = sd(mpm))
-
-ids <- ptpl %>% distinct(., Bird_ID, fam_g)
-
-# Average movement rate for this 'population'
-mean(indiv_moverate$movrate)
-mean(ptpl$mpm)
-
-# Color palette ----------------------------------------
-my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
-
-fam_moverate
-
-ptpl %>%
-  distinct(fam_g, Bird_ID)
-
-ptpl %>%
-  dplyr::select(fam_g, Bird_ID) %>%
-  distinct(Bird_ID, .keep_all = TRUE) %>%
-  group_by(fam_g) %>%
-  summarise(n = n()) %>%
-  right_join(., fam_moverate) %>%
-  mutate(logpar = log(movrate),
-         fitted_sd = logfit$estimate[2]) -> fam_moverate
-fam_moverate
-
-# Using the average movement rate per family group as the meanlog for a lognormal distribution, and the sdlog from the fitted distribution to the whole dataset since we don't have enough individuals per fmaily group to fit a new lognormal.
-
-
-# My question now is whether or not I would be considering individual variation. I'm saying no, because that's like douible variaion of no pooling? Like, we have a lognormal for each family group, and then get individuals from each family group. That is one thing.
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Including ppi

@@
 load("Ch1_movement_rates/sims_backup/weib_np.RData")
+load("Ch1_movement_rates/sims_backup/weib_ppi.RData")
 
@@
               dplyr::select(., est.shape, est.scale, boot, model)) %>%
+  bind_rows(., weib.boot.ppi %>%
+              # mutate(model = paste0(model, "_", popu)) %>% 
+              dplyr::select(., est.shape, est.scale, boot, model)) %>%
   bind_rows(., weib.boot.np %>%
@@
 joint_weib %>% 
-  mutate(model = factor(model, levels = c("cp", "pp", "np_1", "np_2", "np_3"))) -> joint_weib
+  mutate(model = factor(model, levels = c("cp", "pp", "ppi", "np_1", "np_2", "np_3"))) -> joint_weib
+```
 
+```{r}
 joint_weib %>%
   group_by(model) %>%
-  sample_n(., 100) %>%
+  sample_n(., 200) %>%
   ggplot(., aes(x = model, y = est.shape)) +
@@
   group_by(model) %>%
-  sample_n(., 100) %>%
+  sample_n(., 200) %>%
   ggplot(., aes(x = model, y = est.scale)) +

### 2021-10-06 Ch1_movement_rates/Ch1_data_analysis.R
Small edits

@@ -17,8 +17,9 @@ load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
 load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
 
-# CP Kernel ------------------------------------------------------------
-# sample with replacement groups of 100 seeds and fit weibull , here are the parameters.
+# Weibull Seed Dispersal Kernels --------------------------------------------------------
+## CP Kernel ------------------------------------------------------------
+# sample with replacement groups of 100 seeds and fit weibull
 n.boots <- 1000
 samp.size <- 100
 weib.boot.cp <- NULL
@@ -40,7 +41,7 @@ for(j in 1:n.boots){
 
 save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
 
-# PP Kernel ---------------------------------------------------------------------
+## PP Kernel ---------------------------------------------------------------------
 n.boots <- 1000
 samp.size <- 100
 weib.boot.pp <- NULL
@@ -62,7 +63,50 @@ for(j in 1:n.boots){
 
 save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
 
-### NP Kernel ------------------------------------------------------------------
+## PPi Kernel -------------------------------------------------------------------
+
+n.boots <- 1000
+samp.size <- 100
+weib.boot.ppi <- NULL
+
+for(j in 1:n.boots){
+  s.df <- ppi.df %>% drop_na(s.id) %>%
+    group_by(model) %>%
+    sample_n(., samp.size) %>%
+    mutate(disp = round(disp, digits = 2))
+
+  # s.df %>%
+  #   ggplot(., aes(x = disp, fill = popu)) +
+  #   geom_histogram()
+
+  # s.df <- df %>% drop_na(s.id)
+
+  weib.fits <- NULL
+
+  for(i in 1:7){
+    dat <- s.df %>%
+      filter(model == paste0("ppi_", i)) %>%
+      filter(disp != 0)
+
+    g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+    #g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
+    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
+                            est.scale = as.numeric(g$estimate[2]),
+                            loglik = g$loglik,
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_Appendix_A.R
changed name

@@ -1,0 +1,777 @@
+# Script to run simulations for theoretical populations with three levels of variation in movement rates
+# LIBRARIES --------------------------------------------------------------------------------
+
+
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(cowplot)
+library(fitdistrplus)
+library(Hmisc)
+
+set.seed(98)
+
+# Three populations ---------------------------------------------------------------------
+av.mov.rate <- 1
+sd.mov.rate <- c(0.3, 0.5, 1)
+max.x <- 10
+
+mycols <- c("red", "green", "blue")
+#create density plots
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[1]),
+      from=0, to=max.x,
+      col=mycols[1],
+      main = 'Log Normally distributed movement rates for three populations', #add title
+      ylab = 'Density', #change y-axis label
+)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[2]),
+      from=0, to=max.x,
+      col=mycols[2], add=TRUE)
+
+curve(dlnorm(x, meanlog=av.mov.rate, sdlog=sd.mov.rate[3]),
+      from=0, to=max.x,
+      col=mycols[3], add=TRUE)
+
+#add legend
+legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
+       col=mycols, lty=1, cex=1.2)
+
+## Simulate movement rates -------------------------------------------------------------
+n.individuals <- 20
+m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[1]),3))
+m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[2]),3))
+m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = sd.mov.rate[3]),3))
+
+## Visualize individual differences ----------------------------------------------------
+
+par(mfrow=c(1,3))
+mycols <- rainbow(n.individuals, s=1)
+mycols <- colorRampPalette(c("#F46036", "#5B85AA", "#414770", "#372248", "#171123"))(n.individuals)
+mycols <- colorRampPalette(c("#ffba08", "#d00000", "#03071e"))(n.individuals)
+
+range <- c(-0.1,max.x+5)
+#create density plots
[…]

### 2021-10-06 Ch1_movement_rates/Ch1_data_generation.R
missing object at the beginning

@@ -8,7 +8,7 @@ library(cowplot)
 library(fitdistrplus)
 library(Hmisc)
 
-set.seed(98)
+set.seed(927)
 
 # Functions --------------------------------------------------------------------------
 sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
@@ -76,6 +76,8 @@ ids <- ptpl %>% distinct(., Bird_ID, fam_g)
 my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
 
 
+logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
+
 movrate_cp <- mean(indiv_moverate$movrate)
 movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))
 # Which estimate to use?
@@ -113,7 +115,7 @@ for(k in 1:kruns){
 save(cp.df, cp.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_cp.RData")
 
 ## PP Simulations -----------------------------------------------------------------------
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
+
 
 ptpl %>%
   dplyr::select(fam_g, Bird_ID) %>%

### 2021-10-12 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 1 is ready

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
-knitr::opts_chunk$set(fig.width=12, fig.height=6)
+# knitr::opts_chunk$set(fig.width=12, fig.height=6)
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
@@
 
-# Vis Movement Rates ---------------------------------------------
 # Fit a lognormal to the distribution of movement rates
-# Keep in mind these are all males.
 
 logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-# Mean using the fit
-exp(logfit$estimate[1])
+movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))
+
+```
+
+```{r}
+# Figure 1 - example of how the process works.
+# set.seed(72)
+# set.seed(987)
+set.seed(235)
+
+cols.fig1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
+#library(scales)
+#show_col(cols.fig1)
+
+# We are using 5 seeds
+nseeds <- 5
+
+# Doing one run for the first three panels.
+
+test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
+#test_run
+
+# Calculate summary for seeds in this run
+summ_test_run <- summ_seeds(test_run)
+# Visualize this one run:
+test_run %>%
+  ggplot(., aes(x = xloc, y = yloc)) +
+  geom_path(color = cols.fig1[2]) +
+  geom_point(aes(x=0, y=0), color = cols.fig1[6], size = 4) +
+  geom_point(data = test_run %>% drop_na(s.id),
+             aes(x = xloc, y = yloc), shape = "diamond", size = 2.5) +
+  # geom_point(data = summ_test_run,
+  #            aes(x = x, y = y), color = "#59879A") +
+  labs(x = "x", 
+       #title = "Example of one simulation run",
+       y = "y") +
+  theme_bw() -> A
+
+test_run %>%
+  ggplot(., aes(x = xloc, y = yloc)) +
+  geom_path(color = "white", alpha = 0.1) +
+  geom_segment(data = test_run %>% drop_na(s.id),
+               aes(x = xloc, y = yloc, xend = summ_test_run$x, yend = summ_test_run$y), lty = 2, color = cols.fig1[4]) +
+  geom_point(data = test_run %>% drop_na(s.id),
+             aes(x = xloc, y = yloc), shape = "diamond", size = 2.5) +
+  geom_point(aes(x=0, y=0), color = cols.fig1[6], size = 4) +
+  geom_point(data = summ_test_run,
+             aes(x = x, y = y), color = cols.fig1[4], size = 4, shape = "square") +
+  labs(x = "x", 
+       #title = "Average dispersal and dispersion per run",
+       y = "y") +
+  theme_bw() -> B
+
+test_run %>%
+  ggplot(., aes(x = xloc, y = yloc)) +
+  geom_path(color = "white", alpha = 0.1) +
+  geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = cols.fig1[1], lty = "twodash") +
+  geom_segment(data = test_run %>% drop_na(s.id),
+               aes(x = xloc, y = yloc, xend = 0, yend = 0), lty = 2, color = cols.fig1[6]) +
+  #geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = "#87A986", lty = 2) +
+  geom_point(data = test_run %>% drop_na(s.id),
+             aes(x = xloc, y = yloc), shape = "diamond", size = 2.5) +
+  geom_point(data = summ_test_run,
+             aes(x = x, y = y), color = cols.fig1[4], size = 4, shape = "square") +
+  geom_point(aes(x=0, y=0), color = cols.fig1[6], size = 4) +
+  labs(x = "x",
+       #title = "Seed dispersal distance from parent tree",
+       y = "y") +
+  theme_bw() -> C
+
+# The fourth panel will show the histogram and weibull fit for the seed dispersal kernel generated from 100 simulation runs
+kruns <- 100
+test.df <- NULL
+test.summ.df <- NULL
+
+for(k in 1:kruns){
+  a <- sim_seeds(m.prms = movrate_cp_ln, nseeds = nseeds) %>%
+    mutate(run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
+           model = "test")
+
+  b <- summ_seeds(a) %>%
+    mutate(run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
+           model = "test")
+
+  test.df <- rbind.data.frame(test.df, a)
+  test.summ.df <- rbind.data.frame(test.summ.df, b)
+}
+
+test.df %>% drop_na(s.id) -> seed.df
+
+weib.fit <- fitdistr(seed.df$disp, densfun = "weibull")
+
+test.df %>%
+  drop_na(s.id) %>%
+  ggplot(., aes(x = disp)) +
+  geom_histogram(aes(y = ..density..), bins = 30, fill = cols.fig1[7], color = cols.fig1[6]) +
+  stat_function(fun = dweibull, args = list(shape = weib.fit$estimate[1], scale = weib.fit$estimate[2]),
+                color = "black", alpha = 0.8, size = 1) +
+  labs(x = "Distance in meters", 
+       #title = "SDK from 100 runs",
+       y = "Density") +
+  theme_bw() -> D
+
+plot_grid(A, B, C, D, labels = "AUTO")
+
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
 ```
@@
 
-```
-
-```{r}
-# ggsave2(filename = "Ch1_movement_rates/Figures/Movement_dist_comparison_2exp.png", width = 6, height = 4, units = "in")
-
-## Sample run -------
-
-# Which estimate to use?
-# So, we are saying here that complete pooling takes the average of all the data as one.
-We took all the data, then fitted a lognormal distribution.
-So, the parameter we use, is the average movement rate that the lognormal gives us.
-Since we are assuming that the lognormal distribution will describe this population's movement rates across individuals.
-So, we use the expected value (mean) of the fit to describe the average movement rate of the population.
-
-# movrate_cp_ln
-
-# How many seeds to use? Landon used 100 because he was taking averages.
-# I guess we are focusing on a very short time frame: what does the bird do after it eats those seeds at one tree, and how does it move until it drops them all? So, only use 5 seeds.
-
-nseeds <- 5
-
-# Let's visualize one run quickly
-
-#sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
-# Print the data frame with seed info
-test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
-#test_run
-
-# Calculate summary for seeds in this run
-summ_test_run <- summ_seeds(test_run)
-# Visualize this one run:
-test_run %>%
-  ggplot(., aes(x = xloc, y = yloc)) +
-  geom_path(color = "#2D3335") +
-  geom_point(aes(x=0, y=0), color = "#87A986", size = 3) +
-  geom_point(data = test_run %>% drop_na(s.id),
-             aes(x = xloc, y = yloc)) +
-  # geom_point(data = summ_test_run,
-  #            aes(x = x, y = y), color = "#59879A") +
-  labs(x = "x", y = "y",
-       title = "Example of one simulation run") +
-  theme_bw() -> A
-
-test_run %>%
-  ggplot(., aes(x = xloc, y = yloc)) +
-  geom_path(color = "white", alpha = 0.1) +
-  geom_point(aes(x=0, y=0), color = "#87A986", size = 3) +
-  geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = "#87A986", lty = 2) +
-  geom_point(data = test_run %>% drop_na(s.id),
-             aes(x = xloc, y = yloc)) +
-  geom_segment(data = test_run %>% drop_na(s.id),
-               aes(x = xloc, y = yloc, xend = summ_test_run$x, yend = summ_test_run$y), lty = 2, color = "#E2BF80") +
-  geom_point(data = summ_test_run,
-             aes(x = x, y = y), color = "#E2BF80", size = 5) +
-  labs(x = "x", y = "y",
-       title = "Average dispersal and dispersion per run") +
-  theme_bw() -> B
-
-test_run %>%
-  ggplot(., aes(x = xloc, y = yloc)) +
-  geom_path(color = "white", alpha = 0.1) +
-  #geom_segment(aes(x = summ_test_run$x, xend = 0, y = summ_test_run$y, yend = 0), color = "#87A986", lty = 2) +
-  geom_point(data = test_run %>% drop_na(s.id),
-             aes(x = xloc, y = yloc)) +
-  geom_segment(data = test_run %>% drop_na(s.id),
-               aes(x = xloc, y = yloc, xend = 0, yend = 0), lty = 2, color = "black") +
-  geom_point(data = summ_test_run,
-             aes(x = x, y = y), color = "#E2BF80", size = 3) +
-  geom_point(aes(x=0, y=0), color = "#87A986", size = 5) +
-  labs(x = "x", y = "y",
-       title = "Seed dispersal distance from parent tree") +
-  theme_bw() -> C
-
-test_run %>%
-  drop_na(s.id) %>%
-  ggplot(., aes(x = disp)) +
-    geom_histogram(bins = 30) +
-  labs(x = "Dispersal distance in meters", y = "Count",
-       title = "Seed dispersal distance for each seed") +
-  theme_bw() -> D
-
-plot_grid(A, B, C, D, labels = "AUTO")
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Ex_one_sim_run.png")
 ```

### 2021-10-14 Ch1_movement_rates/Ch1_Figures.Rmd
comment out saving
making table of movement rates

@@
 
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
 ```
@@
                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
+  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
+  #               color = my.cols1[4], alpha = 0.8, size = 1) +
   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Average movement rates lognormal fits") +
+  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
+  labs(x = "Movement Rate (meters/minute)",
+       # title = "Average movement rates lognormal fits",
+       y = "Density") +
   theme_bw()

### 2021-10-18 data-raw/grt_data.R
created script to get gut retention time data.

@@ -1,3 +1,24 @@
 ## code to prepare `grt_data` dataset goes here
 
+# Libraries needed
+library(dplyr)
+library(stringr)
+
+
+# Read the data csv
+
+grt_raw <- read.csv("data/gut_ret_time.csv")
+
+
+# This data is from field trials on gut retention times for four individual toucans
+# The field trial seeds included a thread, and so we will keep only the data for regurgitated seeds with a thread.
+
+grt_raw %>%
+  dplyr::select(Name, X..Min, R.P, Seed.cond) %>%
+  mutate(R.P = str_sub(R.P, start = 1, end = 1)) %>%
+  drop_na(X..Min) %>%
+  filter(R.P == 'R', Seed.cond == "THREAD") %>%
+  transmute(Bird_ID = Name,
+            grt = X..Min) -> grt_data
+
 usethis::use_data(grt_data, overwrite = TRUE)

### 2021-10-18 Ch1_movement_rates/Ch1_Figures.Rmd
Included gut retention time.

@@
 library(Hmisc)
+library(gtsummary)
 ```
@@
 ```
+
+# Figure 1
 
@@
 ```
+**Figure1** - Simulation process overview and seed dispersal measures.
+Panels A through C represent one simulation run, whereas panel D shows the results from 100 simulation runs.
+A) An animal starts at the origin (coordinates (0,0) represented by the teal dot) where it ingests five seeds.
+The animal moves in the landscape (grey trajectory path) and drops seeds (black diamonds) as it reaches their gut retention time.
+B) The mean seed location per run is calculated and shown in the orange square.
+The distance of each seed to the mean location is used to calculate seed dispersion as described in the main text.
+C) Average seed dispersal per run (black dashed line) is calculated as the distance from the origin (teal dot) to the mean seed location (orange square).
+Seed dispersal distance for each seed (teal dashed lines) are calculated as the distance of each seed from the origin.
+D) Seed dispersal distances for each seed in 100 simulation runs are used to generate a seed dispersal distance histogram.
+A Weibull distribution is fit to the data to describe the seed dispersal kernel.
+
+# Table 1
+
+```{r}
+ptpl %>% 
+  group_by(Bird_ID, fam_g) %>% 
+  summarise(movrate = round(mean(mpm),1),
+            obs = n()) %>% 
+  left_join(., ptpl %>% 
+              group_by(fam_g) %>% 
+              summarise(famrate = round(mean(mpm), 1))) %>% 
+  dplyr::select(Bird_ID, obs, movrate, fam_g, famrate) -> table1
+
+knitr::kable(table1)
+write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")
+
+```
+
+# Figure 2
+
+# Figure 3 - gut retention times:
+
+```{r include=FALSE}
+load("data/grt_data.rda")
+
+grt_fit <- fitdist(grt_data$grt, "gamma")
+plot(grt_fit)
+
+```
+
+```{r}
+
+grt_data %>% 
+  ggplot() +
+  geom_histogram(aes(x = grt, y = ..density..), fill = my.cols1[7], bins = 20) +
+  stat_function(fun = dgamma, args = list(shape = grt_fit$estimate[1], rate = grt_fit$estimate[2])) +
+  #stat_function(fun = dgamma, args = list(shape = 4, scale = 5), color = "red") + 
+  geom_point(aes(x = grt, color = Bird_ID, y = 0), size = 4) +
+  scale_color_manual(values = c(my.cols1[4], my.cols1[2], my.cols1[3], my.cols1[1])) +
+  theme_bw() +
+  labs(x = "Gut retention time in minutes", y = "Density") +
+  theme(legend.position = "none")+
+  NULL
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure3.png")
+
+```
 
@@
   geom_point(size = 3, alpha = 0.8) +
+  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),

### 2021-10-18 Ch1_movement_rates/Ch1_data_generation.R
Fixed parameters, trying a larger number of simulations.

@@ -28,18 +28,18 @@ sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALS
   }
 }
 
-sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
-  grt <- round(rgamma(nseeds, shape = 4, scale = 5))
-  t.grt <- max(grt)
-
-  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
-
-  df %>%
-    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>%
-    mutate(disp = sqrt(xloc^2+yloc^2)) -> df
-
-  return(df)
-}
+# sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
+#   grt <- round(rgamma(nseeds, shape = 4, scale = 5) + 7)
+#   t.grt <- max(grt)
+#
+#   df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
+#
+#   df %>%
+#     left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>%
+#     mutate(disp = sqrt(xloc^2+yloc^2)) -> df
+#
+#   return(df)
+# }
 
 summ_seeds <- function(df = NULL){
   df %>%
@@ -72,35 +72,58 @@ fam_moverate <- ptpl %>%
 
 ids <- ptpl %>% distinct(., Bird_ID, fam_g)
 
+# Gut retention time
+load("data/grt_data.rda")
+
+
+grt_fit <- fitdist(grt_data$grt, "gamma")
+
+# change the seeds function to our parameters
+
+sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
+  grt <- round(rgamma(nseeds, shape = grt_fit$estimate[1], rate = grt_fit$estimate[2]))
+  t.grt <- max(grt)
+
+  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
+
+  df %>%
+    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>%
+    mutate(disp = sqrt(xloc^2+yloc^2)) -> df
+
+  return(df)
+}
+
 # Color palette ----------------------------------------
[…]

### 2021-10-18 Ch1_movement_rates/Ch1_data_generation.R
mixed up letters in loops

@@ -133,7 +133,7 @@ for(k in 1:kruns){
 
   cp.df <- rbind.data.frame(cp.df, a)
   cp.summ.df <- rbind.data.frame(cp.summ.df, b)
-  print("cp_run", i)
+  print("cp_run", k)
 }
 
 save(cp.df, cp.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_cp.RData")
@@ -179,7 +179,7 @@ for(j in 1:7){
 
     pp.df <- rbind.data.frame(pp.df, a)
     pp.summ.df <- rbind.data.frame(pp.summ.df, b)
-    print("pp_run", i, "family_" j)
+    print("pp_run", k, "family_", j)
   }
 }
 
@@ -219,7 +219,7 @@ for(m in 1:1){
 
       np.df <- rbind.data.frame(np.df, a)
       np.summ.df <- rbind.data.frame(np.summ.df, b)
-      print("np_run", i, "individual_", j)
+      print("np_run", k, "individual_", j)
     }
   }
 }
@@ -234,48 +234,48 @@ save(np.df, np.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_np.RData"
 # Have a lognorm for each family group = using the mean from the family group, sd from population
 # Sample 6 adults (That's how many adult aracari are supposed to be in family groups)
 
-n.individuals <- 6
-
-f.data <- data.frame(indiv = 1:n.individuals)
-
-for(i in 1:7){
-  samp <- rlnorm(n.individuals, meanlog = fam_moverate$logpar[i], sdlog = logfit$estimate[2])
-  f.data <- cbind.data.frame(f.data, samp)
-  names(f.data)[i+1] <- paste(fam_moverate$fam_g[i])
-}
-
-f.data <- f.data[2:8]
-
-# NP Generate data
-kruns <- 1000
-nseeds <- 5
-
-ppi.df <- NULL
-ppi.summ.df <- NULL
-
-for(f in 1:7){
-  f.0 <- f.data[f]
-  for(j in 1:n.individuals){
-    for(k in 1:kruns){
-      a <- sim_seeds(m.prms = f.0[j,], nseeds = nseeds) %>%
-        mutate(indiv = as.factor(j),
-               run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
-               model = paste0("ppi_", f))
-
-      b <- summ_seeds(a) %>%
[…]

### 2021-10-18 Ch1_movement_rates/Ch1_data_generation.R
I'm tired. not printing the loop number

@@ -133,7 +133,7 @@ for(k in 1:kruns){
 
   cp.df <- rbind.data.frame(cp.df, a)
   cp.summ.df <- rbind.data.frame(cp.summ.df, b)
-  print("cp_run", k)
+  #print("cp_run", k)
 }
 
 save(cp.df, cp.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_cp.RData")
@@ -179,7 +179,7 @@ for(j in 1:7){
 
     pp.df <- rbind.data.frame(pp.df, a)
     pp.summ.df <- rbind.data.frame(pp.summ.df, b)
-    print("pp_run", k, "family_", j)
+    #print("pp_run", k, "family_", j)
   }
 }
 
@@ -219,7 +219,7 @@ for(m in 1:1){
 
       np.df <- rbind.data.frame(np.df, a)
       np.summ.df <- rbind.data.frame(np.summ.df, b)
-      print("np_run", k, "individual_", j)
+      #print("np_run", k, "individual_", j)
     }
   }
 }

### 2021-10-18 Ch1_movement_rates/Ch1_data_generation.R
Changed my mind. Put actual values here, not reference to output fit.

@@ -78,10 +78,14 @@ load("data/grt_data.rda")
 
 grt_fit <- fitdist(grt_data$grt, "gamma")
 
+grt_fit$estimate[1]
+grt_fit$estimate[2]
+
+
 # change the seeds function to our parameters
 
 sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
-  grt <- round(rgamma(nseeds, shape = grt_fit$estimate[1], rate = grt_fit$estimate[2]))
+  grt <- round(rgamma(nseeds, shape = 2.05623, rate = 0.07210437))
   t.grt <- max(grt)
 
   df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)

### 2021-10-18 Ch1_movement_rates/Ch1_data_analysis.R
updates to analysis to include ldd calculations

@@ -14,7 +14,7 @@ set.seed(98)
 # Bring data --------------------------------------------
 load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
 load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
-load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
+#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
 
 # Weibull Seed Dispersal Kernels --------------------------------------------------------
@@ -26,6 +26,7 @@ weib.boot.cp <- NULL
 
 for(j in 1:n.boots){
   s.df <- cp.df %>% drop_na(s.id) %>%
+    filter(disp != 0) %>%
     sample_n(., samp.size) %>%
     mutate(disp = round(disp, digits = 2))
 
@@ -48,6 +49,7 @@ weib.boot.pp <- NULL
 
 for(j in 1:n.boots){
   s.df <- pp.df %>% drop_na(s.id) %>%
+    filter(disp != 0) %>%
     sample_n(., samp.size) %>%
     mutate(disp = round(disp, digits = 2))
 
@@ -64,46 +66,46 @@ for(j in 1:n.boots){
 save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
 
 ## PPi Kernel -------------------------------------------------------------------
-
-n.boots <- 1000
-samp.size <- 100
-weib.boot.ppi <- NULL
-
-for(j in 1:n.boots){
-  s.df <- ppi.df %>% drop_na(s.id) %>%
-    group_by(model) %>%
-    sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2))
-
-  # s.df %>%
-  #   ggplot(., aes(x = disp, fill = popu)) +
-  #   geom_histogram()
-
-  # s.df <- df %>% drop_na(s.id)
-
-  weib.fits <- NULL
-
-  for(i in 1:7){
-    dat <- s.df %>%
-      filter(model == paste0("ppi_", i)) %>%
-      filter(disp != 0)
-
-    g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-    #g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
[…]

### 2021-10-18 Ch1_movement_rates/Ch1_Figures.Rmd
updating figures

@@
 knitr::kable(table1)
-write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")
+# write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")
 
@@
 # Figure 2
+
+In process
 
@@
 
-```{r}
-# Visualize distribution and data points
-vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
+<!-- ```{r} -->
+<!-- # Visualize distribution and data points -->
+<!-- vlines <- summary(indiv_moverate$movrate)[c(1,3,6)] -->
 
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  geom_point(size = 3, alpha = 0.8) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Lognormal fit to movement rates",
-       subtitle = "Each dot is an individual") +
-  geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
-  theme_bw()
+<!-- indiv_moverate %>% -->
+<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
+<!--   geom_point(size = 3, alpha = 0.8) + -->
+<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
+<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
+<!--                 color = "black", alpha = 0.8, size = 1) + -->
+<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
+<!--        title = "Lognormal fit to movement rates", -->
+<!--        subtitle = "Each dot is an individual") + -->
+<!--   geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) + -->
+<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
+<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
+<!--   #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) + -->
+<!--   theme_bw() -->
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
-```
+<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png") -->
+<!-- ``` -->
 
-```{r include=FALSE}
-# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:
+<!-- ```{r include=FALSE} -->
+<!-- # The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual: -->
 
-# mean(indiv_moverate$movrate)
-# 27.94211 meters/minute
+<!-- # mean(indiv_moverate$movrate) -->
+<!-- # 27.94211 meters/minute -->
 
-# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.
+<!-- # In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step. -->
 
-## Compare exponential movement distances to full dataset ----------------------------------
+<!-- ## Compare exponential movement distances to full dataset ---------------------------------- -->
 
-movrate_cp <- mean(indiv_moverate$movrate)
-movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))
+<!-- movrate_cp <- mean(indiv_moverate$movrate) -->
+<!-- movrate_cp_ln <- as.numeric(exp(logfit$estimate[1])) -->
 
-# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
-#
-# test %>%
-#   ggplot(., aes(x = mpm)) +
-#   geom_histogram(aes(y = ..density..)) +
-#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")
+<!-- # test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp)) -->
+<!-- # -->
+<!-- # test %>% -->
+<!-- #   ggplot(., aes(x = mpm)) + -->
+<!-- #   geom_histogram(aes(y = ..density..)) + -->
+<!-- #   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red") -->
 
-ptpl %>%
-  ggplot(., aes(x = mpm)) +
-  geom_histogram(aes(y = ..density..)) +
-  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
-  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
-  labs(title = "Histogram of movement distances per minute from data set",
-       x = "Movement distance per minute",
-       y = "Density",
-       caption = "Orange line is exponential density using average movement rate for population \n
-       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
-  theme_bw()
+<!-- ptpl %>% -->
+<!--   ggplot(., aes(x = mpm)) + -->
+<!--   geom_histogram(aes(y = ..density..)) + -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) + -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) + -->
+<!--   labs(title = "Histogram of movement distances per minute from data set", -->
+<!--        x = "Movement distance per minute", -->
+<!--        y = "Density", -->
+<!--        caption = "Orange line is exponential density using average movement rate for population \n -->
+<!--        Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") + -->
+<!--   theme_bw() -->
 
-```
+<!-- ``` -->
 
-```{r include=FALSE}
-## Visualize mov rates ---------------
-pp_1 <- sort(round(fam_moverate$movrate,3))
+<!-- ```{r include=FALSE} -->
+<!-- ## Visualize mov rates --------------- -->
+<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->
 
-### Compare lognorm fits CP and PP -----------
+<!-- ### Compare lognorm fits CP and PP ----------- -->
 
-logfit_fam <- fitdist(pp_1, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
+<!-- logfit_fam <- fitdist(pp_1, distr = 'lnorm') -->
+<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->
 
-# Mean using the fit
-# exp(logfit_fam$estimate[1])
+<!-- # Mean using the fit -->
+<!-- # exp(logfit_fam$estimate[1]) -->
 
-```
+<!-- ``` -->
 
-```{r}
-# Visualize distribution and data points
-vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
+<!-- ```{r} -->
+<!-- # Visualize distribution and data points -->
+<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->
 
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-  #               color = "black", alpha = 0.8, size = 1) +
-  # geom_point(size = 3, alpha = 0.8) +
-  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
-  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Lognormal fit to family group movement rates") +
-  theme_bw()
+<!-- indiv_moverate %>% -->
+<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
+<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
+<!--   #               color = "black", alpha = 0.8, size = 1) + -->
+<!--   # geom_point(size = 3, alpha = 0.8) + -->
+<!--   # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
+<!--   # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
+<!--   #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
+<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
+<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
+<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
+<!--   geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
+<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60), -->
+<!--                      labels = c(0, "Min.", 20, "Median.", "Max.", 60)) + -->
+<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
+<!--        title = "Lognormal fit to family group movement rates") + -->
+<!--   theme_bw() -->
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")
+<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png") -->
 
-```
+<!-- ``` -->
 
-```{r include=FALSE}
-## Visualize mov rates ---------------
-pp_1 <- sort(round(fam_moverate$movrate,3))
+<!-- ```{r include=FALSE} -->
+<!-- ## Visualize mov rates --------------- -->
+<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->
 
-### Compare lognorm fits CP and PP -----------
+<!-- ### Compare lognorm fits CP and PP ----------- -->
 
-logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
+<!-- logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm') -->
+<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->
 
-# Mean using the fit
-exp(logfit_fam$estimate[1])
+<!-- # Mean using the fit -->
+<!-- exp(logfit_fam$estimate[1]) -->
 
-```
+<!-- ``` -->
 
-```{r}
-# Visualize distribution and data points
-vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
+<!-- ```{r} -->
+<!-- # Visualize distribution and data points -->
+<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->
 
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
-  geom_point(size = 3, alpha = 0.8) +
-  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-  #               color = my.cols1[4], alpha = 0.8, size = 1) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  labs(x = "Movement Rate (meters/minute)",
-       # title = "Average movement rates lognormal fits",
-       y = "Density") +
-  theme_bw()
-```
+<!-- indiv_moverate %>% -->
+<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
+<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
+<!--                 color = "black", alpha = 0.8, size = 1) + -->
+<!--   geom_point(size = 3, alpha = 0.8) + -->
+<!--   geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
+<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
+<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
+<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
+<!--   #               color = my.cols1[4], alpha = 0.8, size = 1) + -->
+<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
+<!--   # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
+<!--   labs(x = "Movement Rate (meters/minute)", -->
+<!--        # title = "Average movement rates lognormal fits", -->
+<!--        y = "Density") + -->
+<!--   theme_bw() -->
+<!-- ``` -->
 
-```{r}
-## PP w/fam moverates ---------------------------------------
-# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.
+<!-- ```{r} -->
+<!-- ## PP w/fam moverates --------------------------------------- -->
+<!-- # Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation. -->
 
-fam_moverate %>%
-  arrange(., movrate) -> fam_moverate
+<!-- fam_moverate %>% -->
+<!--   arrange(., movrate) -> fam_moverate -->
 
-fam_moverate %>%
-  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
-  geom_point(size = 3) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
-  xlim(0, 60) +
-  labs(title = "Lognormal fitted to family group",
-       x = "Movement rate",
-       y = "Density") +
-  scale_color_viridis_c() +
-  theme_bw() +
-  theme(legend.position = "none") -> pp_logfit
+<!-- fam_moverate %>% -->
+<!--   ggplot(., aes(x = movrate, y = 0, color = movrate)) + -->
+<!--   geom_point(size = 3) + -->
+<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
+<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
+<!--   xlim(0, 60) + -->
+<!--   labs(title = "Lognormal fitted to family group", -->
+<!--        x = "Movement rate", -->
+<!--        y = "Density") + -->
+<!--   scale_color_viridis_c() + -->
+<!--   theme_bw() + -->
+<!--   theme(legend.position = "none") -> pp_logfit -->
 
-mycols2 <- viridisLite::viridis(7)
-expcurves_pp1 <- purrr::map(seq(1:7), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))
+<!-- mycols2 <- viridisLite::viridis(7) -->
+<!-- expcurves_pp1 <- purrr::map(seq(1:7), function(y) -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8)) -->
 
-ggplot() +
-  expcurves_pp1 +
-  xlim(-1, 125) +
-  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
-  theme_bw() -> pp_expdraws
+<!-- ggplot() + -->
+<!--   expcurves_pp1 + -->
+<!--   xlim(-1, 125) + -->
+<!--   labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") + -->
+<!--   theme_bw() -> pp_expdraws -->
 
-cowplot::plot_grid(pp_logfit, pp_expdraws)
-# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
-```
+<!-- cowplot::plot_grid(pp_logfit, pp_expdraws) -->
+<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png") -->
+<!-- ``` -->
 
-```{r include=FALSE}
-# This one looks at individual variation.
-# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
+<!-- ```{r include=FALSE} -->
+<!-- # This one looks at individual variation. -->
+<!-- # We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population -->
+<!-- logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm') -->
 
-n.individuals <- 20
-m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
+<!-- n.individuals <- 20 -->
+<!-- m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
+<!-- m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
+<!-- m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
 
-logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)
+<!-- logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3) -->
 
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0)) +
-  geom_point(size = 5) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
-  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
-  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
-  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
-  # scale_color_viridis_d(option="magma") +
-  scale_color_viridis_d() +
-  xlim(0, 60) +
-  labs(title = "Sampling individuals from lognormal",
-       x = "Movement rate",
-       y = "Density") +
-  theme_bw() +
-  theme(legend.position = "none") -> plot.logfitdraw
+<!-- indiv_moverate %>% -->
+<!--   ggplot(., aes(x = movrate, y = 0)) + -->
+<!--   geom_point(size = 5) + -->
+<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) + -->
+<!--   geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) + -->
+<!--   geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) + -->
+<!--   geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) + -->
+<!--   # scale_color_viridis_d(option="magma") + -->
+<!--   scale_color_viridis_d() + -->
+<!--   xlim(0, 60) + -->
+<!--   labs(title = "Sampling individuals from lognormal", -->
+<!--        x = "Movement rate", -->
+<!--        y = "Density") + -->
+<!--   theme_bw() + -->
+<!--   theme(legend.position = "none") -> plot.logfitdraw -->
 
-plot.logfitdraw
+<!-- plot.logfitdraw -->
 
-mycols <- viridisLite::viridis(20)
+<!-- mycols <- viridisLite::viridis(20) -->
 
-expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))
+<!-- expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y) -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8)) -->
 
-expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))
+<!-- expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y) -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8)) -->
 
-expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))
+<!-- expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y) -->
+<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8)) -->
 
-logfitdraw %>%
-  ggplot() +
-  expcurves_m1 +
-  expcurves_m2 +
-  expcurves_m3 +
-  xlim(-1, 125) +
-  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
-  theme_bw() -> expdraws
-expdraws
+<!-- logfitdraw %>% -->
+<!--   ggplot() + -->
+<!--   expcurves_m1 + -->
+<!--   expcurves_m2 + -->
+<!--   expcurves_m3 + -->
+<!--   xlim(-1, 125) + -->
+<!--   labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") + -->
+<!--   theme_bw() -> expdraws -->
+<!-- expdraws -->
 
-```
+<!-- ``` -->
 
-```{r}
+<!-- ```{r} -->
 
-cowplot::plot_grid(plot.logfitdraw, expdraws)
+<!-- cowplot::plot_grid(plot.logfitdraw, expdraws) -->
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
-```
+<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png") -->
+<!-- ``` -->
 
@@
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
-load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
+#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 
@@
 load("Ch1_movement_rates/sims_backup/weib_np.RData")
-load("Ch1_movement_rates/sims_backup/weib_ppi.RData")
+#load("Ch1_movement_rates/sims_backup/weib_ppi.RData")
 
@@
 cp.summ.df %>%
-  dplyr::select(av.disp, dsprsn, popu) %>%
-  mutate(model = "cp") %>%
+  dplyr::select(av.disp, dsprsn, model) %>% 
   bind_rows(., pp.summ.df %>%
+              dplyr::select(av.disp, dsprsn, model)) %>%
+  bind_rows(., np.summ.df %>%
               dplyr::select(av.disp, dsprsn,  model) %>%
-              mutate(model = "pp")) %>%
-  bind_rows(., np.summ.df %>%
-              dplyr::select(av.disp, dsprsn, popu) %>%
-              mutate(model = paste0("np_", popu))) %>% 
-  bind_rows(., ppi.summ.df %>% 
-              dplyr::select(av.disp, dsprsn, model) %>% 
-              mutate(model = "ppi")) %>% 
-  mutate(model = factor(model, levels = c("cp", "pp", "ppi","np_1", "np_2", "np_3"))) -> disp_df
+              mutate(model = "np")) %>% 
+  # bind_rows(., ppi.summ.df %>% 
+  #             dplyr::select(av.disp, dsprsn, model) %>% 
+  #             mutate(model = "ppi")) %>% 
+  mutate(model = factor(model, levels = c("cp", "pp",
+                                          #"ppi",
+                                          #"np_1", "np_2", "np_3",
+                                          "np"))) -> disp_df
+```
 
+```{r}
 disp_df %>%
@@
 weib.boot.cp %>%
-  mutate(model = "cp") %>%
   dplyr::select(., est.shape, est.scale, boot, model) %>%
@@
               dplyr::select(., est.shape, est.scale, boot, model)) %>%
-  bind_rows(., weib.boot.ppi %>%
-              # mutate(model = paste0(model, "_", popu)) %>% 
-              dplyr::select(., est.shape, est.scale, boot, model)) %>%
+  # bind_rows(., weib.boot.ppi %>%
+  #             # mutate(model = paste0(model, "_", popu)) %>% 
+  #             dplyr::select(., est.shape, est.scale, boot, model)) %>%
   bind_rows(., weib.boot.np %>%
-              mutate(model = paste0("np_", popu)) %>%
+              mutate(model = "np") %>%
               dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib
@@
 joint_weib %>% 
-  mutate(model = factor(model, levels = c("cp", "pp", "ppi", "np_1", "np_2", "np_3"))) -> joint_weib
+  mutate(model = factor(model, levels = c("cp", "pp",
+                                          # "ppi", "np_1", "np_2", "np_3"
+                                          "np"))) -> joint_weib
 ```
@@
   group_by(model) %>%
-  sample_n(., 200) %>%
+  sample_n(., 100) %>%
   ggplot(., aes(x = model, y = est.shape)) +
@@
   group_by(model) %>%
-  sample_n(., 200) %>%
+  sample_n(., 100) %>%
   ggplot(., aes(x = model, y = est.scale)) +
@@
 ```
+# Table 2 - results
+
+```{r}
+
+```

### 2021-10-18 Ch1_movement_rates/Ch1_data_analysis.R
Table for seed dispersal

@@ -172,4 +172,40 @@ calc_ldd(pp.df)
 calc_ldd(np.df)
 
 
+disp_table <- data.frame(
+  Model = c("CP", "PP", "NP"),
+  Mean.dispersal_sd = c(paste0(signif(mean(null_dispersal$dispersal), 4),
+                               " (", signif(sd(null_dispersal$dispersal), 2), ")"),
+                        paste0(signif(mean(indiv_dispersal$dispersal), 4),
+                               " (", signif(sd(indiv_dispersal$dispersal), 2), ")"),
+                        paste0(signif(mean(fam_dispersal$dispersal), 4),
+                               " (", signif(sd(fam_dispersal$dispersal), 2), ")")),
+  Seed.dispersion_sd = c(paste0(signif(mean(null_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(null_dispersion$seed_dispersion), 2), ")"),
+                         paste0(signif(mean(indiv_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(indiv_dispersion$seed_dispersion), 2), ")"),
+                         paste0(signif(mean(fam_dispersion$seed_dispersion), 4),
+                                " (", signif(sd(fam_dispersion$seed_dispersion), 2), ")")),
+  kurtosis = c(signif(kurtosis(null_dispersal$dispersal), 3),
+               signif(kurtosis(indiv_dispersal$dispersal), 3),
+               signif(kurtosis(fam_dispersal$dispersal), 3)),
+  Max_dispersal = c(signif(max(null_ldd$global_max), 4),
+                    signif(max(indiv_ldd$global_max), 4),
+                    signif(max(fam_ldd$global_max), 4)),
+  # Max_dispersal = c(paste0(signif(null_ldd$max_mean, 3), " (", signif(null_ldd$max_sd, 1), ")"),
+  #                   paste0(signif(indiv_ldd$max_mean, 3), " (", signif(indiv_ldd$max_sd, 1), ")"),
+  #                   paste0(signif(fam_ldd$max_mean, 3), " (", signif(fam_ldd$max_sd, 1), ")")),
+  LDD = c(paste0(signif(null_ldd$prcnt_ldd, 3), " (", signif(null_ldd$sd_ldd*100, 2), ")", "%"),
[…]

### 2021-10-18 Ch1_movement_rates/Ch1_data_analysis.R
Checked that it runs well until disp table.

@@ -8,6 +8,7 @@ library(ggplot2)
 library(cowplot)
 library(fitdistrplus)
 library(Hmisc)
+library(moments)
 
 set.seed(98)
 
@@ -26,9 +27,9 @@ weib.boot.cp <- NULL
 
 for(j in 1:n.boots){
   s.df <- cp.df %>% drop_na(s.id) %>%
-    filter(disp != 0) %>%
     sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2))
+    mutate(disp = round(disp, digits = 2))%>%
+    dplyr::filter(., disp > 0)
 
   g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
 
@@ -47,14 +48,17 @@ n.boots <- 1000
 samp.size <- 100
 weib.boot.pp <- NULL
 
+pp.df %>% drop_na(s.id) %>%
+  dplyr::filter(disp == 0) -> pp.df.zeros
+
 for(j in 1:n.boots){
   s.df <- pp.df %>% drop_na(s.id) %>%
-    filter(disp != 0) %>%
     sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2))
+    mutate(disp = round(disp, digits = 2)) %>%
+    dplyr::filter(., disp > 0)
 
   g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-
+  print(j)
 
   prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                           est.scale = as.numeric(g$estimate[2]),
@@ -152,14 +156,14 @@ save(weib.boot.np, file = "Ch1_movement_rates/sims_backup/weib_np.RData")
 
 # Long distance dispersal percentage ------------------
 
-calc_ldd <- function(df, ...){
+calc_ldd <- function(df, thresh = 500, ...){
   t.seeds <- df %>%
     drop_na(., s.id) %>%
     count()
 
   n.ldd <- df %>%
     drop_na(., s.id) %>%
-    filter(., disp >= 500) %>%
+    filter(., disp >= thresh) %>%
     count()
 
   value <- n.ldd/t.seeds
@@ -174,38 +178,197 @@ calc_ldd(np.df)
 
 disp_table <- data.frame(
   Model = c("CP", "PP", "NP"),
-  Mean.dispersal_sd = c(paste0(signif(mean(null_dispersal$dispersal), 4),
[…]

### 2021-10-18 Ch1_movement_rates/Ch1_Figures.Rmd
vis table
waaaa updates

@@
 
+# Figure x - average dispersal and dispersion per run
+
+Importance of the outliers here
+
 ```{r}
@@
   group_by(., model) %>%
-  sample_n(., 100) %>%
+  sample_n(., 1000) %>%
   ggplot(., aes(y = dsprsn, x = model)) +
   geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
+  #geom_point(color = "grey", alpha = 0.5) +
   labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
@@
   group_by(., model) %>%
-  sample_n(., 100) %>%
+  sample_n(., 1000) %>%
   ggplot(., aes(y = av.disp, x = model)) +
   geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
+  #geom_point(color = "grey", alpha = 0.5) +
   labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
@@
 ```
+
+# Figure x - seed dispersal kernel parameters
+Here we are using the distance of each seed
 
@@
 
+## Variation 1 - violin plot with 100 out of 1000 of the parameter fits
+
 ```{r}
@@
   geom_jitter(position = position_jitter(0.1)) +
+  geom_hline(aes(yintercept = 1), lty = "dashed") +
   labs(title = "Shape") +
+  #scale_y_continuous(limits = c(0, 2)) +
   theme_bw() -> weib_shape
@@
 ```
-# Table 2 - results
+
+## Variation 2 - violin plot with all 1000 of the parameter fits
 
 ```{r}
+joint_weib %>%
+  group_by(model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(x = model, y = est.shape)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(position = position_jitter(0.1)) +
+  geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(title = "Shape") +
+  #scale_y_continuous(limits = c(0, 2)) +
+  theme_bw() -> weib_shape
+
+joint_weib %>%
+  group_by(model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(x = model, y = est.scale)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(position = position_jitter(0.1)) +
+  labs(title = "Scale") +
+  theme_bw() -> weib_scale
+
+plot_grid(weib_shape, weib_scale)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
 
 ```
+
+## Variation 3 - boxplot with all the fits, 1000
+
+```{r}
+joint_weib %>%
+  group_by(model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(x = model, y = est.shape)) +
+  geom_boxplot() +
+  # geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  #geom_jitter(position = position_jitter(0.1)) +
+  geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(title = "Shape") +
+  #scale_y_continuous(limits = c(0, 2)) +
+  theme_bw() -> weib_shape
+
+joint_weib %>%
+  group_by(model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(x = model, y = est.scale)) +
+  geom_boxplot() +
+  #geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  #geom_jitter(position = position_jitter(0.1)) +
+  labs(title = "Scale") +
+  theme_bw() -> weib_scale
+
+plot_grid(weib_shape, weib_scale)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
+
+```
+
+```{r eval=FALSE}
+
+smean.cl.normal(weib.boot.cp$est.shape) -> cp.shape
+smean.cl.normal(weib.boot.cp$est.scale) -> cp.scale
+
+smean.cl.normal(weib.boot.pp$est.shape) -> pp.shape
+smean.cl.normal(weib.boot.pp$est.scale) -> pp.scale
+
+smean.cl.normal(weib.boot.np$est.shape) -> np.shape
+smean.cl.normal(weib.boot.np$est.scale) -> np.scale
+
+cp.df %>% 
+  bind_rows(pp.df, np.df) %>% 
+  drop_na(., s.id) %>% 
+  group_by(model) %>% 
+  sample_n(5000) %>% 
+  ggplot(., aes(x = disp)) +
+  geom_histogram(aes(y = ..density..), fill = "lightgray") +
+  stat_function(fun = dweibull, args = list(shape = cp.shape[1], scale = cp.scale[1]), color = "blue") +
+  # stat_function(fun = dweibull, args = list(shape = cp.shape[2], scale = cp.scale[2]), color = "blue", lty = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = cp.shape[3], scale = cp.scale[3]), color = "blue", lty = "dashed") +
+  stat_function(fun = dweibull, args = list(shape = pp.shape[1], scale = pp.scale[1]), color = "black") +
+  # stat_function(fun = dweibull, args = list(shape = pp.shape[2], scale = pp.scale[2]), color = "black", lty = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = pp.shape[3], scale = pp.scale[3]), color = "black", lty = "dashed") +
+  stat_function(fun = dweibull, args = list(shape = np.shape[1], scale = np.scale[1]), color = "red") +
+  # stat_function(fun = dweibull, args = list(shape = np.shape[2], scale = np.scale[2]), color = "red", lty = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = np.shape[3], scale = np.scale[3]), color = "red", lty = "dashed") +
+  theme_bw() +
+  geom_vline(aes(xintercept = 500)) +
+  coord_cartesian(xlim = c(500, 1700), ylim = c(0, 0.0005))
+
+```
+
+# Table 2 - results  
+Data for each seed, not per run
+
+```{r}
+# here::here()
+disp_table <- read.csv("Ch1_movement_rates/Figures/table2.csv")
+
+knitr::kable(disp_table)
+
+```

### 2021-10-18 Ch1_movement_rates/Ch1_data_generation.R

@@ -117,6 +117,7 @@ nseeds <- 5
 # We will simulate around 1000 simulation runs per individual
 
 
+# SIMULATED ONLY--------------
 ## CP Simulations -----------------------------------------------------------------------
 # Generate seed dispersal data under a complete pooling scenario
 
@@ -161,23 +162,26 @@ logfit_fam <- fitdist(pp_1, distr = 'lnorm')
 fam_moverate %>%
   arrange(., movrate) -> fam_moverate
 
+n.fams <- 10
+pp_rates <- sort(round(rlnorm(n.fams, meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),3))
+
 # PP Generate data
 
-kruns <- 5000
+kruns <- 3000
 nseeds <- 5
 
 pp.df <- NULL
 pp.summ.df <- NULL
 
-for(j in 1:7){
+for(j in 1:length(pp_rates)){
   for(k in 1:kruns){
-    a <- sim_seeds(m.prms = fam_moverate$movrate[j], nseeds = nseeds) %>%
-      mutate(fam_g = fam_moverate$fam_g[j],
+    a <- sim_seeds(m.prms = pp_rates[j], nseeds = nseeds) %>%
+      mutate(fam_g = paste0("simfam_", j),
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
              model = "pp")
 
     b <- summ_seeds(a) %>%
-      mutate(fam_g = fam_moverate$fam_g[j],
+      mutate(fam_g = paste0("simfam_", j),
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
              model = "pp")
 
@@ -233,7 +237,117 @@ for(m in 1:1){
 
 save(np.df, np.summ.df, file = "Ch1_movement_rates/sims_backup/datagen_np.RData")
 
-## PP w/indiv Simulations -----------------------------------------------
+# REAL DATA ---------------
+## CPr Simulations -----------------------------------------------------------------------
+# Generate seed dispersal data under a complete pooling scenario from the fit
+
+movrate_cpr <- logfit$estimate[1]
+
+kruns <- 30000
+nseeds <- 5
+
+cpr.df <- NULL
+cpr.summ.df <- NULL
+
+for(k in 1:kruns){
+  a <- sim_seeds(m.prms = movrate_cpr, nseeds = nseeds) %>%
[…]

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
not loading those other scenarios

@@
 
+# Real data --------------------------------------
+load("Ch1_movement_rates/sims_backup/datagen_cpr.RData")
+load("Ch1_movement_rates/sims_backup/datagen_ppr.RData")
+load("Ch1_movement_rates/sims_backup/datagen_npr.RData")
+
+load("Ch1_movement_rates/sims_backup/weib_cpr.RData")
+load("Ch1_movement_rates/sims_backup/weib_ppr.RData")
+load("Ch1_movement_rates/sims_backup/weib_npr.RData")
+
+```
+
+```{r}
 # Dispersion and Dispersal --------------------------------------------------------------------
@@
                                           "np"))) -> disp_df
+
+cpr.summ.df %>%
+  dplyr::select(av.disp, dsprsn, model) %>% 
+  bind_rows(., ppr.summ.df %>%
+              dplyr::select(av.disp, dsprsn, model)) %>%
+  bind_rows(., npr.summ.df %>%
+              dplyr::select(av.disp, dsprsn,  model) %>%
+              mutate(model = "npr")) %>% 
+  mutate(model = factor(model, levels = c("cpr", "ppr",
+                                          "npr"))) -> disp_r_df
 ```
@@
 
+### With the real data
+
+```{r}
+disp_r_df %>%
+  group_by(., model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(y = dsprsn, x = model)) +
+  geom_boxplot() +
+  #geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
+  theme_bw() +
+  theme(legend.position = "none") -> pr_dispersion
+
+disp_r_df %>%
+  group_by(., model) %>%
+  sample_n(., 1000) %>%
+  ggplot(., aes(y = av.disp, x = model)) +
+  geom_boxplot() +
+  #geom_point(color = "grey", alpha = 0.5) +
+  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
+  theme_bw() +
+  theme(legend.position = "none") -> pr_dispersal
+
+plot_grid(pr_dispersal, pr_dispersion)
+```
+
 # Figure x - seed dispersal kernel parameters
@@
                                           "np"))) -> joint_weib
+
+weib.boot.cpr %>%
+  dplyr::select(., est.shape, est.scale, boot, model) %>%
+  bind_rows(., weib.boot.ppr %>%
+              dplyr::select(., est.shape, est.scale, boot, model)) %>%
+  bind_rows(., weib.boot.npr %>%
+              mutate(model = "npr") %>%
+              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_r_weib
+
+joint_r_weib %>% 
+  mutate(model = factor(model, levels = c("cpr", "ppr",
+                                          # "ppi", "np_1", "np_2", "np_3"
+                                          "npr"))) -> joint_r_weib
 ```
@@
 
+```
+
+Real data
+
+```{r}
+joint_r_weib %>%
+  group_by(model) %>%
+  sample_n(., 100) %>%
+  ggplot(., aes(x = model, y = est.shape)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(position = position_jitter(0.1)) +
+  geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(title = "Shape") +
+  #scale_y_continuous(limits = c(0, 2)) +
+  theme_bw() -> weib_r_shape
+
+joint_r_weib %>%
+  group_by(model) %>%
+  sample_n(., 100) %>%
+  ggplot(., aes(x = model, y = est.scale)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(position = position_jitter(0.1)) +
+  labs(title = "Scale") +
+  theme_bw() -> weib_r_scale
+
+plot_grid(weib_r_shape, weib_r_scale)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
 ```

### 2021-10-25 Ch1_movement_rates/Ch1_data_analysis.R
Not using these scenarios, and also not running the ppi idea

@@ -15,13 +15,7 @@ set.seed(98)
 # Bring data --------------------------------------------
 load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
 load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
-#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
-
-load("Ch1_movement_rates/sims_backup/datagen_cpr.RData")
-load("Ch1_movement_rates/sims_backup/datagen_ppr.RData")
-#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
-load("Ch1_movement_rates/sims_backup/datagen_npr.RData")
 
 # Weibull Seed Dispersal Kernels --------------------------------------------------------
 ## CP Kernel ------------------------------------------------------------
@@ -73,48 +67,6 @@ for(j in 1:n.boots){
 }
 
 save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
-
-## PPi Kernel -------------------------------------------------------------------
-#
-# n.boots <- 1000
-# samp.size <- 100
-# weib.boot.ppi <- NULL
-#
-# for(j in 1:n.boots){
-#   s.df <- ppi.df %>% drop_na(s.id) %>%
-#     group_by(model) %>%
-#     sample_n(., samp.size) %>%
-#     mutate(disp = round(disp, digits = 2))
-#
-#   # s.df %>%
-#   #   ggplot(., aes(x = disp, fill = popu)) +
-#   #   geom_histogram()
-#
-#   # s.df <- df %>% drop_na(s.id)
-#
-#   weib.fits <- NULL
-#
-#   for(i in 1:7){
-#     dat <- s.df %>%
-#       filter(model == paste0("ppi_", i)) %>%
-#       filter(disp != 0)
-#
-#     g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-#     #g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-#     prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-#                             est.scale = as.numeric(g$estimate[2]),
-#                             loglik = g$loglik,
-#                             popu = i,
-#                             model = "ppi")
[…]

### 2021-10-25 Ch1_movement_rates/Ch1_data_analysis.R
Only running 30 individuals on the np scenario, not three samples from it.

@@ -47,8 +47,8 @@ n.boots <- 1000
 samp.size <- 100
 weib.boot.pp <- NULL
 
-pp.df %>% drop_na(s.id) %>%
-  dplyr::filter(disp == 0) -> pp.df.zeros
+# pp.df %>% drop_na(s.id) %>%
+#   dplyr::filter(disp == 0) -> pp.df.zeros
 
 for(j in 1:n.boots){
   s.df <- pp.df %>% drop_na(s.id) %>%
@@ -57,7 +57,7 @@ for(j in 1:n.boots){
     dplyr::filter(., disp > 0)
 
   g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-  print(j)
+  # print(j)
 
   prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                           est.scale = as.numeric(g$estimate[2]),
@@ -76,37 +76,19 @@ weib.boot.np <- NULL
 
 for(j in 1:n.boots){
   s.df <- np.df %>% drop_na(s.id) %>%
-    #group_by(popu) %>%
     sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2))
+    mutate(disp = round(disp, digits = 2)) %>%
+    dplyr::filter(., disp > 0)
 
-  # s.df %>%
-  #   ggplot(., aes(x = disp, fill = popu)) +
-  #   geom_histogram()
+  g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
+  # print(j)
 
-  # s.df <- df %>% drop_na(s.id)
-
-  weib.fits <- NULL
-
-  for(i in 1:1){
-    dat <- s.df %>%
-      #filter(popu == i) %>%
-      filter(disp != 0)
-
-    g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-    #g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                            est.scale = as.numeric(g$estimate[2]),
-                            loglik = g$loglik,
-                            popu = i,
-                            model = paste0("np_", i))
-    weib.fits <- rbind.data.frame(weib.fits, prms.weib)
-    # plot(g)
-  }
-
-  weib.boot.np <- rbind.data.frame(weib.boot.np, weib.fits %>% mutate(boot = j))
[…]

### 2021-10-25 Ch1_movement_rates/Ch1_data_analysis.R
no "real" data anymore.

@@ -237,7 +237,7 @@ as.data.frame(np_mrl) %>%
 
 
 
-# Plots
+# Plot functions
 
 threshplot_fx <- function(thresh_data, th, title = NULL){
 
@@ -339,347 +339,3 @@ threshplot_fx(np_threshplot, np_thresh, title = "NP threshold plots")
 aligned_plots(cp_mrl, cp_threshplot, cp_thresh, title = "CP model")
 aligned_plots(pp_mrl, pp_threshplot, pp_thresh, title = "PP model")
 aligned_plots(np_mrl, np_threshplot, np_thresh, title = "NP model")
-
-# REAL data ----------------------
-
-# Weibull Seed Dispersal Kernels --------------------------------------------------------
-## CPr Kernel ------------------------------------------------------------
-# sample with replacement groups of 100 seeds and fit weibull
-n.boots <- 1000
-samp.size <- 100
-weib.boot.cpr <- NULL
-
-for(j in 1:n.boots){
-  s.df <- cpr.df %>% drop_na(s.id) %>%
-    sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2))%>%
-    dplyr::filter(., disp > 0)
-
-  g <- fitdist(s.df$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-
-
-  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                          est.scale = as.numeric(g$estimate[2]),
-                          loglik = g$loglik,
-                          model = "cpr")
-  weib.boot.cpr <- rbind.data.frame(weib.boot.cpr, prms.weib %>% mutate(boot = j))
-}
-
-save(weib.boot.cpr, file = "Ch1_movement_rates/sims_backup/weib_cpr.RData")
-
-## PPr Kernel ---------------------------------------------------------------------
-n.boots <- 1000
-samp.size <- 100
-weib.boot.ppr <- NULL
-
-ppr.df %>% drop_na(s.id) %>%
-  dplyr::filter(disp == 0) -> ppr.df.zeros
-
-for(j in 1:n.boots){
-  s.df <- ppr.df %>% drop_na(s.id) %>%
-    sample_n(., samp.size) %>%
-    mutate(disp = round(disp, digits = 2)) %>%
-    dplyr::filter(., disp > 0)
-
[…]

### 2021-10-25 Ch1_movement_rates/Ch1_data_generation.R
don't know where this x came from.

@@ -111,6 +111,8 @@ logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
 logfit.mu <- logfit$estimate[1]
 logfit.sigma <- as.numeric(logfit$estimate[2])
 
+x
+
 ## Movement rates -----------------------------------------------------
 ### Complete pooling movrate -------------------
 # For the complete pooling scenario we use the expected value of the lognormal distribution we fit to the data

### 2021-10-25 Ch1_movement_rates/Ch1_data_generation.R
no x?

@@ -111,7 +111,6 @@ logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
 logfit.mu <- logfit$estimate[1]
 logfit.sigma <- as.numeric(logfit$estimate[2])
 
-x
 
 ## Movement rates -----------------------------------------------------
 ### Complete pooling movrate -------------------

### 2021-10-25 Ch1_movement_rates/Ch1_data_analysis.R
small number of boots just to test.

@@ -20,8 +20,8 @@ load("Ch1_movement_rates/sims_backup/datagen_np.RData")
 # Weibull Seed Dispersal Kernels --------------------------------------------------------
 ## CP Kernel ------------------------------------------------------------
 # sample with replacement groups of 100 seeds and fit weibull
-n.boots <- 1000
-samp.size <- 100
+n.boots <- 100
+samp.size <- 10
 weib.boot.cp <- NULL
 
 for(j in 1:n.boots){
@@ -43,8 +43,8 @@ for(j in 1:n.boots){
 save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
 
 ## PP Kernel ---------------------------------------------------------------------
-n.boots <- 1000
-samp.size <- 100
+n.boots <- 100
+samp.size <- 10
 weib.boot.pp <- NULL
 
 # pp.df %>% drop_na(s.id) %>%
@@ -70,8 +70,8 @@ save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
 
 
 ## NP Kernel ------------------------------------------------------------------
-n.boots <- 1000
-samp.size <- 100
+n.boots <- 100
+samp.size <- 10
 weib.boot.np <- NULL
 
 for(j in 1:n.boots){

### 2021-10-25 Ch1_movement_rates/Ch1_data_analysis.R
It works so trying real num of samples

@@ -20,8 +20,8 @@ load("Ch1_movement_rates/sims_backup/datagen_np.RData")
 # Weibull Seed Dispersal Kernels --------------------------------------------------------
 ## CP Kernel ------------------------------------------------------------
 # sample with replacement groups of 100 seeds and fit weibull
-n.boots <- 100
-samp.size <- 10
+n.boots <- 1000
+samp.size <- 100
 weib.boot.cp <- NULL
 
 for(j in 1:n.boots){
@@ -43,8 +43,8 @@ for(j in 1:n.boots){
 save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
 
 ## PP Kernel ---------------------------------------------------------------------
-n.boots <- 100
-samp.size <- 10
+n.boots <- 1000
+samp.size <- 100
 weib.boot.pp <- NULL
 
 # pp.df %>% drop_na(s.id) %>%
@@ -70,8 +70,8 @@ save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
 
 
 ## NP Kernel ------------------------------------------------------------------
-n.boots <- 100
-samp.size <- 10
+n.boots <- 1000
+samp.size <- 100
 weib.boot.np <- NULL
 
 for(j in 1:n.boots){

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
No 'real' data

@@
 load("Ch1_movement_rates/sims_backup/datagen_np.RData")
-#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")
 
@@
 load("Ch1_movement_rates/sims_backup/weib_np.RData")
-#load("Ch1_movement_rates/sims_backup/weib_ppi.RData")
-
-# Real data --------------------------------------
-load("Ch1_movement_rates/sims_backup/datagen_cpr.RData")
-load("Ch1_movement_rates/sims_backup/datagen_ppr.RData")
-load("Ch1_movement_rates/sims_backup/datagen_npr.RData")
-
-load("Ch1_movement_rates/sims_backup/weib_cpr.RData")
-load("Ch1_movement_rates/sims_backup/weib_ppr.RData")
-load("Ch1_movement_rates/sims_backup/weib_npr.RData")
 

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 lognormal fit

@@
 
+```{r}
+# Visualize distribution and data points
+#vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
+cols.fig2 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
+
+indiv_moverate %>%
+  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
+  geom_point(size = 3, alpha = 0.8) +
+  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
+                color = "black", alpha = 0.8, size = 1) +
+  scale_color_manual(values = cols.fig2) +
+  labs(x = "Movement Rate (meters/minute)", y = "Density",
+       title = "Lognormal fit to individual movement rates") +
+  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
+  scale_x_continuous(limits = c(0, 70)) +
+  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
+  guides(color = guide_legend(title = "Social Group",
+                              ncol = 2)) +
+  theme_bw() +
+  theme(legend.position = c(0.8, 0.6))
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
+```
+
+```{r include=FALSE}
+# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:
+
+# mean(indiv_moverate$movrate)
+# 27.94211 meters/minute
+
+# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.
+
+## Compare exponential movement distances to full dataset ----------------------------------
+
+movrate_cp <- mean(indiv_moverate$movrate)
+movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))
+
+# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
+#
+# test %>%
+#   ggplot(., aes(x = mpm)) +
+#   geom_histogram(aes(y = ..density..)) +
+#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")
+
+ptpl %>%
+  ggplot(., aes(x = mpm)) +
+  geom_histogram(aes(y = ..density..)) +
+  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
+  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
+  labs(title = "Histogram of movement distances per minute from data set",
+       x = "Movement distance per minute",
+       y = "Density",
+       caption = "Orange line is exponential density using average movement rate for population \n
+       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
+  theme_bw()
+
+```
+
+```{r include=FALSE}
+## Visualize mov rates ---------------
+pp_1 <- sort(round(fam_moverate$movrate,3))
+
+### Compare lognorm fits CP and PP -----------
+
+logfit_fam <- fitdist(pp_1, distr = 'lnorm')
+# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
+
+# Mean using the fit
+# exp(logfit_fam$estimate[1])
+
+```
+
+```{r}
+# Visualize distribution and data points
+vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
+
+indiv_moverate %>%
+  ggplot(., aes(x = movrate, y = 0.002)) +
+  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
+  #               color = "black", alpha = 0.8, size = 1) +
+  # geom_point(size = 3, alpha = 0.8) +
+  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
+  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
+  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
+                color = my.cols1[4], alpha = 0.8, size = 1) +
+  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
+  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
+  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
+                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
+  labs(x = "Movement Rate (meters/minute)", y = "Density",
+       title = "Lognormal fit to family group movement rates") +
+  theme_bw()
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")
+
+```
+
+```{r include=FALSE}
+## Visualize mov rates ---------------
+pp_1 <- sort(round(fam_moverate$movrate,3))
+
+### Compare lognorm fits CP and PP -----------
+
+logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
+# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
+
+# Mean using the fit
+exp(logfit_fam$estimate[1])
+
+```
+
+```{r}
+# Visualize distribution and data points
+vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
+
+indiv_moverate %>%
+  ggplot(., aes(x = movrate, y = 0.002)) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
+                color = "black", alpha = 0.8, size = 1) +
+  geom_point(size = 3, alpha = 0.8) +
+  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
+  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
+                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
+  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
+  #               color = my.cols1[4], alpha = 0.8, size = 1) +
+  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
+  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
+  labs(x = "Movement Rate (meters/minute)",
+       # title = "Average movement rates lognormal fits",
+       y = "Density") +
+  theme_bw()
+```
+
+```{r}
+## PP w/fam moverates ---------------------------------------
+# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.
+
+fam_moverate %>%
+  arrange(., movrate) -> fam_moverate
+
+fam_moverate %>%
+  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
+  geom_point(size = 3) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
+                color = my.cols1[4], alpha = 0.8, size = 1) +
+  xlim(0, 60) +
+  labs(title = "Lognormal fitted to family group",
+       x = "Movement rate",
+       y = "Density") +
+  scale_color_viridis_c() +
+  theme_bw() +
+  theme(legend.position = "none") -> pp_logfit
+
+mycols2 <- viridisLite::viridis(7)
+expcurves_pp1 <- purrr::map(seq(1:7), function(y)
+  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))
+
+ggplot() +
+  expcurves_pp1 +
+  xlim(-1, 125) +
+  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
+  theme_bw() -> pp_expdraws
+
+cowplot::plot_grid(pp_logfit, pp_expdraws)
+# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
+```
+
+```{r include=FALSE}
+# This one looks at individual variation.
+# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
+logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
+
+n.individuals <- 20
+m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
+m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
+m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
+
+logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)
+
+indiv_moverate %>%
+  ggplot(., aes(x = movrate, y = 0)) +
+  geom_point(size = 5) +
+  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
+  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
+  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
+  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
+  # scale_color_viridis_d(option="magma") +
+  scale_color_viridis_d() +
+  xlim(0, 60) +
+  labs(title = "Sampling individuals from lognormal",
+       x = "Movement rate",
+       y = "Density") +
+  theme_bw() +
+  theme(legend.position = "none") -> plot.logfitdraw
+
+plot.logfitdraw
+
+mycols <- viridisLite::viridis(20)
+
+expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
+  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))
+
+expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
+  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))
+
+expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
+  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))
+
+logfitdraw %>%
+  ggplot() +
+  expcurves_m1 +
+  expcurves_m2 +
+  expcurves_m3 +
+  xlim(-1, 125) +
+  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
+  theme_bw() -> expdraws
+expdraws
+
+```
+
+```{r}
+
+cowplot::plot_grid(plot.logfitdraw, expdraws)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
+```
+
 In process
@@
 ```
-
-<!-- ```{r} -->
-<!-- # Visualize distribution and data points -->
-<!-- vlines <- summary(indiv_moverate$movrate)[c(1,3,6)] -->
-
-<!-- indiv_moverate %>% -->
-<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
-<!--   geom_point(size = 3, alpha = 0.8) + -->
-<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
-<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
-<!--                 color = "black", alpha = 0.8, size = 1) + -->
-<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
-<!--        title = "Lognormal fit to movement rates", -->
-<!--        subtitle = "Each dot is an individual") + -->
-<!--   geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) + -->
-<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
-<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
-<!--   #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) + -->
-<!--   theme_bw() -->
-
-<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png") -->
-<!-- ``` -->
-
-<!-- ```{r include=FALSE} -->
-<!-- # The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual: -->
-
-<!-- # mean(indiv_moverate$movrate) -->
-<!-- # 27.94211 meters/minute -->
-
-<!-- # In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step. -->
-
-<!-- ## Compare exponential movement distances to full dataset ---------------------------------- -->
-
-<!-- movrate_cp <- mean(indiv_moverate$movrate) -->
-<!-- movrate_cp_ln <- as.numeric(exp(logfit$estimate[1])) -->
-
-<!-- # test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp)) -->
-<!-- # -->
-<!-- # test %>% -->
-<!-- #   ggplot(., aes(x = mpm)) + -->
-<!-- #   geom_histogram(aes(y = ..density..)) + -->
-<!-- #   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red") -->
-
-<!-- ptpl %>% -->
-<!--   ggplot(., aes(x = mpm)) + -->
-<!--   geom_histogram(aes(y = ..density..)) + -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) + -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) + -->
-<!--   labs(title = "Histogram of movement distances per minute from data set", -->
-<!--        x = "Movement distance per minute", -->
-<!--        y = "Density", -->
-<!--        caption = "Orange line is exponential density using average movement rate for population \n -->
-<!--        Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") + -->
-<!--   theme_bw() -->
-
-<!-- ``` -->
-
-<!-- ```{r include=FALSE} -->
-<!-- ## Visualize mov rates --------------- -->
-<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->
-
-<!-- ### Compare lognorm fits CP and PP ----------- -->
-
-<!-- logfit_fam <- fitdist(pp_1, distr = 'lnorm') -->
-<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->
-
-<!-- # Mean using the fit -->
-<!-- # exp(logfit_fam$estimate[1]) -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- # Visualize distribution and data points -->
-<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->
-
-<!-- indiv_moverate %>% -->
-<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
-<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
-<!--   #               color = "black", alpha = 0.8, size = 1) + -->
-<!--   # geom_point(size = 3, alpha = 0.8) + -->
-<!--   # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
-<!--   # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
-<!--   #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
-<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
-<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
-<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
-<!--   geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
-<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60), -->
-<!--                      labels = c(0, "Min.", 20, "Median.", "Max.", 60)) + -->
-<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
-<!--        title = "Lognormal fit to family group movement rates") + -->
-<!--   theme_bw() -->
-
-<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png") -->
-
-<!-- ``` -->
-
-<!-- ```{r include=FALSE} -->
-<!-- ## Visualize mov rates --------------- -->
-<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->
-
-<!-- ### Compare lognorm fits CP and PP ----------- -->
-
-<!-- logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm') -->
-<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->
-
-<!-- # Mean using the fit -->
-<!-- exp(logfit_fam$estimate[1]) -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- # Visualize distribution and data points -->
-<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->
-
-<!-- indiv_moverate %>% -->
-<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
-<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
-<!--                 color = "black", alpha = 0.8, size = 1) + -->
-<!--   geom_point(size = 3, alpha = 0.8) + -->
-<!--   geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
-<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
-<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
-<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
-<!--   #               color = my.cols1[4], alpha = 0.8, size = 1) + -->
-<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
-<!--   # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
-<!--   labs(x = "Movement Rate (meters/minute)", -->
-<!--        # title = "Average movement rates lognormal fits", -->
-<!--        y = "Density") + -->
-<!--   theme_bw() -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- ## PP w/fam moverates --------------------------------------- -->
-<!-- # Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation. -->
-
-<!-- fam_moverate %>% -->
-<!--   arrange(., movrate) -> fam_moverate -->
-
-<!-- fam_moverate %>% -->
-<!--   ggplot(., aes(x = movrate, y = 0, color = movrate)) + -->
-<!--   geom_point(size = 3) + -->
-<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
-<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
-<!--   xlim(0, 60) + -->
-<!--   labs(title = "Lognormal fitted to family group", -->
-<!--        x = "Movement rate", -->
-<!--        y = "Density") + -->
-<!--   scale_color_viridis_c() + -->
-<!--   theme_bw() + -->
-<!--   theme(legend.position = "none") -> pp_logfit -->
-
-<!-- mycols2 <- viridisLite::viridis(7) -->
-<!-- expcurves_pp1 <- purrr::map(seq(1:7), function(y) -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8)) -->
-
-<!-- ggplot() + -->
-<!--   expcurves_pp1 + -->
-<!--   xlim(-1, 125) + -->
-<!--   labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") + -->
-<!--   theme_bw() -> pp_expdraws -->
-
-<!-- cowplot::plot_grid(pp_logfit, pp_expdraws) -->
-<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png") -->
-<!-- ``` -->
-
-<!-- ```{r include=FALSE} -->
-<!-- # This one looks at individual variation. -->
-<!-- # We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population -->
-<!-- logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm') -->
-
-<!-- n.individuals <- 20 -->
-<!-- m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
-<!-- m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
-<!-- m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
-
-<!-- logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3) -->
-
-<!-- indiv_moverate %>% -->
-<!--   ggplot(., aes(x = movrate, y = 0)) + -->
-<!--   geom_point(size = 5) + -->
-<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) + -->
-<!--   geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) + -->
-<!--   geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) + -->
-<!--   geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) + -->
-<!--   # scale_color_viridis_d(option="magma") + -->
-<!--   scale_color_viridis_d() + -->
-<!--   xlim(0, 60) + -->
-<!--   labs(title = "Sampling individuals from lognormal", -->
-<!--        x = "Movement rate", -->
-<!--        y = "Density") + -->
-<!--   theme_bw() + -->
-<!--   theme(legend.position = "none") -> plot.logfitdraw -->
-
-<!-- plot.logfitdraw -->
-
-<!-- mycols <- viridisLite::viridis(20) -->
-
-<!-- expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y) -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8)) -->
-
-<!-- expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y) -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8)) -->
-
-<!-- expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y) -->
-<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8)) -->
-
-<!-- logfitdraw %>% -->
-<!--   ggplot() + -->
-<!--   expcurves_m1 + -->
-<!--   expcurves_m2 + -->
-<!--   expcurves_m3 + -->
-<!--   xlim(-1, 125) + -->
-<!--   labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") + -->
-<!--   theme_bw() -> expdraws -->
-<!-- expdraws -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-
-<!-- cowplot::plot_grid(plot.logfitdraw, expdraws) -->
-
-<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png") -->
-<!-- ``` -->
 

### 2021-10-25 Ch1_movement_rates/Ch1_data_generation.R
Save the movement rates to use in the figures

@@ -148,6 +148,7 @@ n.individuals <- 30
 movrate_np <- rlnorm(n.individuals, meanlog = logfit.mu, sdlog = logfit.sigma)
 
 
+
 ## Other Simulation parameters ---------------------------------
 
 
@@ -163,6 +164,10 @@ build.filename <- function(rdata.name){
 
   here::here("Ch1_movement_rates", "sims_backup", rdata.name)
 }
+
+# Save the movement rates
+
+save(movrate_cp, movrate_np, movrate_pp, file = build.filename("movrates"))
 
 # number of seeds we give every individual
 nseeds <- 5

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 shows distribution of movement rates for the "population" and the social groups.

@@
 
-```{r}
+```{r fig.height=12}
 # Visualize distribution and data points
-#vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]
+
+load("Ch1_movement_rates/sims_backup/movrates.RData")
+
 cols.fig2 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
@@
   theme_bw() +
-  theme(legend.position = c(0.8, 0.6))
+  theme(legend.position = c(0.8, 0.6)) -> logfit_plot
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
+# Estimate the mu's for each family group based on their movement rate.
+logfit.sigma <- logfit$estimate[2]
+get_mu <- function(movrate, sigma = logfit.sigma){
+  mu <- log(movrate)-((sigma^2)/2)
+  return(mu)
+}
+
+fam_mus <- get_mu(fam_moverate$movrate)
+
+glines <- purrr::map(1:7, function(y)
+    stat_function(fun = dlnorm, args = list(meanlog = fam_mus[y], sdlog = logfit.sigma), color = cols.fig2[y]))
+
+fam_moverate %>%
+  ggplot(., aes(x = movrate, y = -0.002, color = fam_g)) +
+  geom_point(size = 3, alpha = 0.8) +
+  glines +
+  scale_color_manual(values = cols.fig2) +
+  labs(x = "Movement Rate (meters/minute)", y = "Density",
+       title = "Distribution for social group movement rates") +
+  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
+  scale_x_continuous(limits = c(0, 70)) +
+  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
+  guides(color = guide_legend(title = "Social Group",
+                              ncol = 2)) +
+  theme_bw() +
+  theme(legend.position = c(0.8, 0.6)) -> social_group_curves
+
+plot_grid(logfit_plot, social_group_curves, nrow = 2)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
+
 ```

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 is ready

@@
 
-```{r fig.height=12}
+```{r}
 # Visualize distribution and data points
@@
 cols.fig2 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
+
+# Movement rates used for each scenario
+
+movrate_cp
+movrate_np
+movrate_pp
+
+movratedf <- data.frame(scenario = "cp", group = NA, movrate = movrate_cp) %>% 
+  bind_rows(., data.frame(scenario = rep("pp", 42), group = movrate_pp$fam_g, movrate = movrate_pp$movrate)) %>% 
+  bind_rows(., data.frame(scenario = rep("np", 30), group = NA, movrate = movrate_np))
+
+# Logfit plot
 
@@
   theme_bw() +
-  theme(legend.position = c(0.8, 0.6)) -> logfit_plot
+  theme(legend.position = "none") -> logfit_plot
 
@@
 
-plot_grid(logfit_plot, social_group_curves, nrow = 2)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
+movratedf %>% 
+  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
+  geom_point(size = 3, alpha = 0.8) +
+  scale_color_manual(values = cols.fig2) +
+  scale_x_continuous(limits = c(0, 70)) +
+  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
+       title = "Sampled movement rates for each simulated scenario") +
+  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
+  guides(color = guide_legend(title = "Social Group",
+                              ncol = 2)) +
+  theme_bw() +
+  theme(legend.position = "none") -> movrates_used
 
@@
 
-```{r include=FALSE}
-# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:
+```{r fig.height=12}
+plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1))
 
-# mean(indiv_moverate$movrate)
-# 27.94211 meters/minute
-
-# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.
-
-## Compare exponential movement distances to full dataset ----------------------------------
-
-movrate_cp <- mean(indiv_moverate$movrate)
-movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))
-
-# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
-#
-# test %>%
-#   ggplot(., aes(x = mpm)) +
-#   geom_histogram(aes(y = ..density..)) +
-#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")
-
-ptpl %>%
-  ggplot(., aes(x = mpm)) +
-  geom_histogram(aes(y = ..density..)) +
-  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
-  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
-  labs(title = "Histogram of movement distances per minute from data set",
-       x = "Movement distance per minute",
-       y = "Density",
-       caption = "Orange line is exponential density using average movement rate for population \n
-       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
-  theme_bw()
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
 
 ```
-
-```{r include=FALSE}
-## Visualize mov rates ---------------
-pp_1 <- sort(round(fam_moverate$movrate,3))
-
-### Compare lognorm fits CP and PP -----------
-
-logfit_fam <- fitdist(pp_1, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-
-# Mean using the fit
-# exp(logfit_fam$estimate[1])
-
-```
-
-```{r}
-# Visualize distribution and data points
-vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-  #               color = "black", alpha = 0.8, size = 1) +
-  # geom_point(size = 3, alpha = 0.8) +
-  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
-  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Lognormal fit to family group movement rates") +
-  theme_bw()
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")
-
-```
-
-```{r include=FALSE}
-## Visualize mov rates ---------------
-pp_1 <- sort(round(fam_moverate$movrate,3))
-
-### Compare lognorm fits CP and PP -----------
-
-logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
-# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
-
-# Mean using the fit
-exp(logfit_fam$estimate[1])
-
-```
-
-```{r}
-# Visualize distribution and data points
-vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0.002)) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
-                color = "black", alpha = 0.8, size = 1) +
-  geom_point(size = 3, alpha = 0.8) +
-  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
-  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
-                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
-  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-  #               color = my.cols1[4], alpha = 0.8, size = 1) +
-  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
-  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
-  labs(x = "Movement Rate (meters/minute)",
-       # title = "Average movement rates lognormal fits",
-       y = "Density") +
-  theme_bw()
-```
-
-```{r}
-## PP w/fam moverates ---------------------------------------
-# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.
-
-fam_moverate %>%
-  arrange(., movrate) -> fam_moverate
-
-fam_moverate %>%
-  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
-  geom_point(size = 3) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
-                color = my.cols1[4], alpha = 0.8, size = 1) +
-  xlim(0, 60) +
-  labs(title = "Lognormal fitted to family group",
-       x = "Movement rate",
-       y = "Density") +
-  scale_color_viridis_c() +
-  theme_bw() +
-  theme(legend.position = "none") -> pp_logfit
-
-mycols2 <- viridisLite::viridis(7)
-expcurves_pp1 <- purrr::map(seq(1:7), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))
-
-ggplot() +
-  expcurves_pp1 +
-  xlim(-1, 125) +
-  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
-  theme_bw() -> pp_expdraws
-
-cowplot::plot_grid(pp_logfit, pp_expdraws)
-# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
-```
-
-```{r include=FALSE}
-# This one looks at individual variation.
-# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
-logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
-
-n.individuals <- 20
-m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
-
-logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)
-
-indiv_moverate %>%
-  ggplot(., aes(x = movrate, y = 0)) +
-  geom_point(size = 5) +
-  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
-  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
-  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
-  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
-  # scale_color_viridis_d(option="magma") +
-  scale_color_viridis_d() +
-  xlim(0, 60) +
-  labs(title = "Sampling individuals from lognormal",
-       x = "Movement rate",
-       y = "Density") +
-  theme_bw() +
-  theme(legend.position = "none") -> plot.logfitdraw
-
-plot.logfitdraw
-
-mycols <- viridisLite::viridis(20)
-
-expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))
-
-expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))
-
-expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
-  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))
-
-logfitdraw %>%
-  ggplot() +
-  expcurves_m1 +
-  expcurves_m2 +
-  expcurves_m3 +
-  xlim(-1, 125) +
-  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
-  theme_bw() -> expdraws
-expdraws
-
-```
-
-```{r}
-
-cowplot::plot_grid(plot.logfitdraw, expdraws)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
-```
-
-In process
 

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
I think I did something stupid and now the third panel isn't showing colors.

@@
 
-movrate_cp
-movrate_np
-movrate_pp
+# movrate_cp
+# movrate_np
+# movrate_pp
 
@@
   theme_bw() +
-  theme(legend.position = "none") -> logfit_plot
+  #theme(legend.position = "none") +
+  NULL -> logfit_plot
 
@@
   theme_bw() +
-  theme(legend.position = "none") -> movrates_used
+  #theme(legend.position = "none") +
+  NULL-> movrates_used
 

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 2 is ready

@@
   ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
-  geom_point(size = 3, alpha = 0.8) +
+  geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
   scale_color_manual(values = cols.fig2) +
@@
   NULL-> movrates_used
+
+movrates_used
 

### 2021-10-25 Ch1_movement_rates/Ch1_data_generation.R
mistake with model name

@@ -247,12 +247,12 @@ for(j in 1:length(movrate_np)){
                    gamma.shape = gamma.shape, gamma.scale = gamma.scale) %>%
       mutate(id = paste0("i_", j),
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
-             model = "pp")
+             model = "np")
 
     b <- summ_seeds(a) %>%
       mutate(id = paste0("i_", j),
              run = factor(paste0("r_", k), levels = paste0("r_", 1:kruns)),
-             model = "pp")
+             model = "np")
 
     np.df <- rbind.data.frame(np.df, a)
     np.summ.df <- rbind.data.frame(np.summ.df, b)

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Fig 2 set.

--- 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
@@
   theme_bw() +
-  #theme(legend.position = "none") +
+  theme(legend.position = "none") +
   NULL -> logfit_plot
@@
   theme_bw() +
-  #theme(legend.position = "none") +
+  theme(legend.position = "none") +
   NULL-> movrates_used
@@
 
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
 
@@
   bind_rows(., np.summ.df %>%
-              dplyr::select(av.disp, dsprsn,  model) %>%
-              mutate(model = "np")) %>% 
-  # bind_rows(., ppi.summ.df %>% 
-  #             dplyr::select(av.disp, dsprsn, model) %>% 
-  #             mutate(model = "ppi")) %>% 
-  mutate(model = factor(model, levels = c("cp", "pp",
-                                          #"ppi",
-                                          #"np_1", "np_2", "np_3",
-                                          "np"))) -> disp_df
-
-cpr.summ.df %>%
-  dplyr::select(av.disp, dsprsn, model) %>% 
-  bind_rows(., ppr.summ.df %>%
               dplyr::select(av.disp, dsprsn,  model)) %>% 
-  bind_rows(., npr.summ.df %>%
-              dplyr::select(av.disp, dsprsn,  model) %>%
-              mutate(model = "npr")) %>% 
-  mutate(model = factor(model, levels = c("cpr", "ppr",
-                                          "npr"))) -> disp_r_df
+  mutate(model = factor(model, levels = c("cp", "pp","np"))) -> disp_df
 ```

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
sample 5000 points for dispersion dispersal plot

@@
   group_by(., model) %>%
-  sample_n(., 1000) %>%
+  sample_n(., 5000) %>%
   ggplot(., aes(y = dsprsn, x = model)) +
@@
   group_by(., model) %>%
-  sample_n(., 1000) %>%
+  sample_n(., 5000) %>%
   ggplot(., aes(y = av.disp, x = model)) +

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 4 disp ready

@@
 
-# Figure x - average dispersal and dispersion per run
+# Figure 4 - average dispersal and dispersion per run
 
@@
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/disp_plot.png")
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
 
-```
-
-### With the real data
-
-```{r}
-disp_r_df %>%
-  group_by(., model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(y = dsprsn, x = model)) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> pr_dispersion
-
-disp_r_df %>%
-  group_by(., model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(y = av.disp, x = model)) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> pr_dispersal
-
-plot_grid(pr_dispersal, pr_dispersion)
 ```

### 2021-10-26 Ch1_movement_rates/Ch1_Figures.Rmd
Figures updated

@@
 ```
+
 **Figure1** - Simulation process overview and seed dispersal measures.
@@
 
-```{r fig.height=12}
+```{r fig.height=12, fig.width=6}
 plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1))
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
 
@@
               dplyr::select(., est.shape, est.scale, boot, model)) %>%
-  # bind_rows(., weib.boot.ppi %>%
-  #             # mutate(model = paste0(model, "_", popu)) %>% 
-  #             dplyr::select(., est.shape, est.scale, boot, model)) %>%
   bind_rows(., weib.boot.np %>%
-              mutate(model = "np") %>%
               dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib
@@
   mutate(model = factor(model, levels = c("cp", "pp",
-                                          # "ppi", "np_1", "np_2", "np_3"
                                           "np"))) -> joint_weib
 
-weib.boot.cpr %>%
-  dplyr::select(., est.shape, est.scale, boot, model) %>%
-  bind_rows(., weib.boot.ppr %>%
-              dplyr::select(., est.shape, est.scale, boot, model)) %>%
-  bind_rows(., weib.boot.npr %>%
-              mutate(model = "npr") %>%
-              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_r_weib
-
-joint_r_weib %>% 
-  mutate(model = factor(model, levels = c("cpr", "ppr",
-                                          # "ppi", "np_1", "np_2", "np_3"
-                                          "npr"))) -> joint_r_weib
 ```
 
-## Variation 1 - violin plot with 100 out of 1000 of the parameter fits
+## Variation 1 - violin plot with 200 out of 1000 of the parameter fits
 
@@
   group_by(model) %>%
-  sample_n(., 100) %>%
+  sample_n(., 200) %>%
   ggplot(., aes(x = model, y = est.shape)) +
@@
 
-```
-
-Real data
-
-```{r}
-joint_r_weib %>%
-  group_by(model) %>%
-  sample_n(., 100) %>%
-  ggplot(., aes(x = model, y = est.shape)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
-  geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(title = "Shape") +
-  #scale_y_continuous(limits = c(0, 2)) +
-  theme_bw() -> weib_r_shape
-
-joint_r_weib %>%
-  group_by(model) %>%
-  sample_n(., 100) %>%
-  ggplot(., aes(x = model, y = est.scale)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
-  labs(title = "Scale") +
-  theme_bw() -> weib_r_scale
-
-plot_grid(weib_r_shape, weib_r_scale)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
 ```
@@
   theme_bw() +
-  geom_vline(aes(xintercept = 500)) +
-  coord_cartesian(xlim = c(500, 1700), ylim = c(0, 0.0005))
+  # geom_vline(aes(xintercept = 500)) +
+  # coord_cartesian(xlim = c(500, 1700), ylim = c(0, 0.0005)) +
+  NULL
 

### 2021-11-08 Ch1_movement_rates/Ch1_Figures.Rmd
Saving results figures.

@@
   scale_color_manual(values = cols.fig2) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Lognormal fit to individual movement rates") +
+  labs(x = "Movement Rate (meters/minute)",
+       y = "Density",
+       subtitle = "Lognormal fit to individual movement rates") +
   #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
@@
   theme_bw() +
-  theme(legend.position = "none") +
+  theme(legend.position = "none",
+        axis.title.x = element_blank()) +
   NULL -> logfit_plot
@@
   scale_color_manual(values = cols.fig2) +
-  labs(x = "Movement Rate (meters/minute)", y = "Density",
-       title = "Distribution for social group movement rates") +
+  labs(x = "Movement Rate (meters/minute)", 
+       y = "Density",
+       subtitle = "Distribution for social group movement rates") +
   #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
@@
   theme_bw() +
-  theme(legend.position = c(0.8, 0.6)) -> social_group_curves
+  theme(legend.position = c(0.8, 0.6),
+        axis.title.x = element_blank()) -> social_group_curves
 
@@
   scale_x_continuous(limits = c(0, 70)) +
-  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
-       title = "Sampled movement rates for each simulated scenario") +
+  labs(x = "Movement Rate (meters/minute)", y = "Scenario",
+       subtitle = "Sampled movement rates for each simulated scenario") +
   #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
@@
 
-```{r fig.height=12, fig.width=6}
-plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1))
+```{r fig.height=7, fig.width=5}
+plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1), labels = "AUTO")
 
@@
 
-# Figure x - seed dispersal kernel parameters
+# Figure 5 - seed dispersal kernel parameters
 Here we are using the distance of each seed
@@
 
-## Variation 2 - violin plot with all 1000 of the parameter fits
-
-```{r}
-joint_weib %>%
-  group_by(model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(x = model, y = est.shape)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
-  geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(title = "Shape") +
-  #scale_y_continuous(limits = c(0, 2)) +
-  theme_bw() -> weib_shape
-
-joint_weib %>%
-  group_by(model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(x = model, y = est.scale)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
-  labs(title = "Scale") +
-  theme_bw() -> weib_scale
-
-plot_grid(weib_shape, weib_scale)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
-
-```
-
-## Variation 3 - boxplot with all the fits, 1000
-
-```{r}
-joint_weib %>%
-  group_by(model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(x = model, y = est.shape)) +
-  geom_boxplot() +
-  # geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  #geom_jitter(position = position_jitter(0.1)) +
-  geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(title = "Shape") +
-  #scale_y_continuous(limits = c(0, 2)) +
-  theme_bw() -> weib_shape
-
-joint_weib %>%
-  group_by(model) %>%
-  sample_n(., 1000) %>%
-  ggplot(., aes(x = model, y = est.scale)) +
-  geom_boxplot() +
-  #geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  #geom_jitter(position = position_jitter(0.1)) +
-  labs(title = "Scale") +
-  theme_bw() -> weib_scale
-
-plot_grid(weib_shape, weib_scale)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
-
-```
-
 ```{r eval=FALSE}

### 2021-11-18 Ch1_movement_rates/Ch1_Figures.Rmd
Editing kernel density estimations for parameter values from weibull dists.
Updating figure for dispersaal and dispersion

@@
   group_by(., model) %>%
-  sample_n(., 5000) %>%
+  #sample_n(., 5000) %>%
   ggplot(., aes(y = dsprsn, x = model)) +
@@
   group_by(., model) %>%
-  sample_n(., 5000) %>%
+  #sample_n(., 5000) %>%
   ggplot(., aes(y = av.disp, x = model)) +
@@
 # ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+
+```
+
+# Idea for dispersal and dispersion
+Too many points, since we have 500k seeds, take 2%
+
+```{r fig.height=12}
+
+points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
+  seed.data %>% 
+    drop_na(s.id) %>% 
+    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
+    sample_n(s.size) %>% 
+      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
+      geom_point(alpha = lalpha) +
+      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
+      theme_bw()
+
+}
+
+A <- points_plot(seed.data = cp.df)
+B <- points_plot(seed.data = pp.df)
+C <- points_plot(seed.data = np.df)
+
+plot_grid(A, B, C, nrow = 3)
+
+# To do:
+# Remove xy labels
+# change colors so only over 500 shows blue
+# remove legends
+# Add boxplots for dispersion next to it
+# Am I adding dispersal?
+# For final figure increase sample size to 50,000 so we have 10% of the data visualized.
 
@@
 ```
-
-## Variation 1 - violin plot with 200 out of 1000 of the parameter fits
 
@@
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/weib_plot.png")
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")
+
+```
+
+```{r}
+library(kde1d)
+
+# Kernel density estimation:
+
+cp.shape.kde <- kde1d(weib.boot.cp$est.shape)
+pp.shape.kde <- kde1d(weib.boot.pp$est.shape)
+np.shape.kde <- kde1d(weib.boot.np$est.shape)
+
+cp.scale.kde <- kde1d(weib.boot.cp$est.scale)
+pp.scale.kde <- kde1d(weib.boot.pp$est.scale)
+np.scale.kde <- kde1d(weib.boot.np$est.scale)
+
+CIs.cp.shape <- qkde1d(p=c(0.025,0.5, 0.975), cp.shape.kde)
+CIs.pp.shape <- qkde1d(p=c(0.025,0.5, 0.975), pp.shape.kde)
+CIs.np.shape <- qkde1d(p=c(0.025,0.5, 0.975), np.shape.kde)
+
+CIs.cp.scale <- qkde1d(p=c(0.025,0.5, 0.975), cp.scale.kde)
+CIs.pp.scale <- qkde1d(p=c(0.025,0.5, 0.975), pp.scale.kde)
+CIs.np.scale <- qkde1d(p=c(0.025,0.5, 0.975), np.scale.kde)
+
+# The proportion of shape parameter values above the sampling distribution is 
+prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
+prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
+prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
+
+plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
+lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
+lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")
+
+plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
+lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
+lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
 

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
exploring so many options to try and visualize this.

@@
   group_by(., model) %>%
-  #sample_n(., 5000) %>%
+  sample_n(., 50000) %>%
   ggplot(., aes(y = dsprsn, x = model)) +
@@
   group_by(., model) %>%
-  #sample_n(., 5000) %>%
+  sample_n(., 50000) %>%
   ggplot(., aes(y = av.disp, x = model)) +
@@
 
-```{r fig.height=12}
+```{r}
 
-points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
+points_plot <- function(seed.data, summ.data, s.size = 25, xylims=1250, lalpha = 0.5){
   seed.data %>% 
     drop_na(s.id) %>% 
-    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
-    sample_n(s.size) %>% 
-      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
+    #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
+    slice_head(., n = s.size) %>% 
+    #sample_n(s.size) %>% 
+      ggplot(., aes(x = xloc, y = yloc, color = run)) +
       geom_point(alpha = lalpha) +
+      #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
       coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
-      theme_bw()
+      theme_bw() +
+      theme(legend.position = "none",
+            axis.title = element_blank()) +
+       NULL -> seedlocplot
 
+  summ.data %>%
+    #cp.summ.df %>%
+    #sample_n(s.size) %>%
+    slice_head(., n = s.size/5) %>%
+    #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
+    #ggplot(., aes(x = name, y = value)) +
+    ggplot(., aes(y = dsprsn)) +
+    #geom_violin() +
+    #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
+    #geom_boxplot(width = 0.1) +
+    geom_point(aes(x=0, color = run)) +
+    lims(y = c(0, 650)) +
+    labs(y = "Dispersion in meters") +
+    theme_bw() +
+    NULL -> dispersionplot
+
+  plot_grid(seedlocplot, dispersionplot, ncol=2, rel_widths = c(2,1))
+  # 
 }
 
-A <- points_plot(seed.data = cp.df)
-B <- points_plot(seed.data = pp.df)
-C <- points_plot(seed.data = np.df)
+A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df)
 
-plot_grid(A, B, C, nrow = 3)
+A
+
+# B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df)
+# C <- points_plot(seed.data = np.df, summ.data = np.summ.df)
+# 
+# plot_grid(A, B, C, ncol = 3)
 

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
Still working on the results figures

--- 2021-11-18 Ch1_movement_rates/Ch1_Figures.Rmd
@@
               dplyr::select(av.disp, dsprsn,  model)) %>% 
-  mutate(model = factor(model, levels = c("cp", "pp","np"))) -> disp_df
+  mutate(model = toupper(model),
+         model = factor(model, levels = c("CP", "PP","NP"))) -> disp_df
 ```
@@
 
-Importance of the outliers here
+Build a table with quantiles or summary stats for the dispersal and dispersion per run.
+Dispersion tells us how spread appart the seeds are from each other during a simulation.
+I would expect that for individuals with higher movement rates dispersion might be higher for their simulation runs too.
+This because a higher movement rate would extend the tail of the exponential distribution for movement distances, and thus have a larger range for movement distances, with a higher probability larger movement distances.
+So, during a simulation, a bird would see itself taking larger steps if they have a larger movement rate.
+Thus, their seeds would potentially be distributed more far apart.
 
@@
 disp_df %>% 
-  group_by(., model) %>%
-  #sample_n(., 5000) %>%
-  ggplot(., aes(y = dsprsn, x = model)) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> p_dispersion
+  group_by(model) %>% 
+  summarise(av.disp = round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1),
+            dsprsn = round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1),
+            q = c("min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
+  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
+  pivot_wider(., names_from = q, values_from = value) %>% 
+  arrange(., property) -> qtable_models
 
-disp_df %>%
-  group_by(., model) %>%
-  #sample_n(., 5000) %>%
-  ggplot(., aes(y = av.disp, x = model)) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
-  theme_bw() +
-  theme(legend.position = "none") -> p_dispersal
-
-plot_grid(p_dispersal, p_dispersion)
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
-
+qtable_models
 ```
 
-# Idea for dispersal and dispersion
-Too many points, since we have 500k seeds, take 2%
+### Idea for dispersal and dispersion
 
-```{r fig.height=12}
+Too many points, since we have 500k seeds, show only a percentage.
 
-points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
+```{r fig.width=9, fig.height=3.5}
+
+points_plot <- function(seed.data, summ.data, s.size = 1000, xylims=1250, lalpha = 0.5, scenario = NULL){
+
   seed.data %>% 
     drop_na(s.id) %>% 
-    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
+    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
+    #slice_head(., n = s.size) %>% 
     sample_n(s.size) %>% 
-      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
+      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
       geom_point(alpha = lalpha) +
+      labs(subtitle = scenario) +
+      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
       coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
-      theme_bw()
+      theme_bw() +
+      theme(legend.position = "none",
+            axis.title = element_blank()) +
+       NULL -> seedlocplot
 
+  # summ.data %>%
+  #   #cp.summ.df %>%
+  #   sample_n(s.size) %>%
+  #   #slice_head(., n = s.size/5) %>%
+  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
+  #   #ggplot(., aes(x = name, y = value)) +
+  #   ggplot(., aes(y = dsprsn)) +
+  #   #geom_violin() +
+  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
+  #   geom_boxplot(width = 0.1) +
+  #   #geom_point(aes(x=0, color = run)) +
+  #   lims(y = c(0, 650)) +
+  #   labs(y = "Dispersion in meters") +
+  #   theme_bw() +
+  #   NULL -> dispersionplot
+  # 
+  # summ.data %>%
+  #   #cp.summ.df %>%
+  #   sample_n(s.size) %>%
+  #   #slice_head(., n = s.size/5) %>%
+  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
+  #   #ggplot(., aes(x = name, y = value)) +
+  #   ggplot(., aes(y = av.disp)) +
+  #   #geom_violin() +
+  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
+  #   geom_boxplot(width = 0.1) +
+  #   #geom_point(aes(x=0, color = run)) +
+  #   lims(y = c(0, 1300)) +
+  #   labs(y = "Dispersal in meters") +
+  #   theme_bw() +
+  #   NULL -> dispersalplot
+  # 
+  # plot_grid(seedlocplot, dispersalplot, dispersionplot, ncol=3, rel_widths = c(2,1,1))
+  # 
 }
 
-A <- points_plot(seed.data = cp.df)
-B <- points_plot(seed.data = pp.df)
-C <- points_plot(seed.data = np.df)
+A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")
 
-plot_grid(A, B, C, nrow = 3)
+#A
+
+B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
+C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")
+
+seedplots2d <- plot_grid(A, B, C, ncol = 3)
 
@@
 # For final figure increase sample size to 50,000 so we have 10% of the data visualized.
+
+```
+
+```{r fig.width=9, fig.height=4}
+
+disp_df %>%
+  group_by(., model) %>%
+  sample_n(., 50000) %>%
+  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
+  ggplot(., aes(y = dsprsn, x = model)) +
+  geom_boxplot() +
+  #geom_point(color = "grey", alpha = 0.5) +
+  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
+  labs(y = "Dispersion in meters") +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title = element_blank()) -> p_dispersion
+
+disp_df %>%
+  group_by(., model) %>%
+  sample_n(., 50000) %>%
+  mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
+  ggplot(., aes(y = av.disp, x = model, color = dispcat)) +
+  geom_boxplot() +
+  geom_point(color = "grey", alpha = 0.5) +
+  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
+  labs(y = "Average dispersal in meters") +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title = element_blank()) -> p_dispersal
+
+plot_grid(p_dispersal, p_dispersion)
+
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+
+```
+
+```{r}
+cp.df %>% 
+  drop_na(s.id) %>% 
+  left_join(., cp.summ.df) -> testdata
+
+testdata %>% 
+  sample_n(1000) %>% 
+  ggplot(., aes(x = xloc, y = yloc, color = dsprsn)) +
+  geom_point() +
+  scale_color_viridis_c(direction = -1) +
+  theme_bw()
+
+cp.summ.df %>% 
+  sample_n(1000) %>% 
+  ggplot(., aes(y = dsprsn, x = av.disp)) +
+  geom_point()
+
+cp.summ.df %>% 
+  sample_n(100) %>% 
+  ggplot(., aes(x = x, y = y, color = dsprsn)) +
+  scale_color_gradient(low = "green", high = "blue") +
+  geom_point(alpha = 0.8) +
+  coord_equal() +
+  theme_bw()
 

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
Getting somewhere!!

@@
 
-points_plot <- function(seed.data, summ.data, s.size = 1000, xylims=1250, lalpha = 0.5, scenario = NULL){
+points_plot <- function(seed.data, summ.data, s.size = 5000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){
 
@@
       geom_point(alpha = lalpha) +
+      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
+      geom_text(label = scenario, x = -1000, y = -1000, color = "black") +
+      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
+      theme_bw() +
+      theme(legend.position = "none",
+            axis.title = element_blank()) +
+       NULL -> seedlocplot
+
+    if(twoplots == TRUE){
+
+          summ.data %>% 
+    #drop_na(s.id) %>% 
+    mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>% 
+    #slice_head(., n = s.size) %>% 
+    sample_n(s.size*5) %>% 
+      ggplot(., aes(x = x, y = y, color = dispcat)) +
+      geom_point(alpha = lalpha) +
       labs(subtitle = scenario) +
@@
             axis.title = element_blank()) +
-       NULL -> seedlocplot
+       NULL -> summaryplot
 
-  # summ.data %>%
-  #   #cp.summ.df %>%
-  #   sample_n(s.size) %>%
-  #   #slice_head(., n = s.size/5) %>%
-  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
-  #   #ggplot(., aes(x = name, y = value)) +
-  #   ggplot(., aes(y = dsprsn)) +
-  #   #geom_violin() +
-  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
-  #   geom_boxplot(width = 0.1) +
-  #   #geom_point(aes(x=0, color = run)) +
-  #   lims(y = c(0, 650)) +
-  #   labs(y = "Dispersion in meters") +
-  #   theme_bw() +
-  #   NULL -> dispersionplot
-  # 
-  # summ.data %>%
-  #   #cp.summ.df %>%
-  #   sample_n(s.size) %>%
-  #   #slice_head(., n = s.size/5) %>%
-  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
-  #   #ggplot(., aes(x = name, y = value)) +
-  #   ggplot(., aes(y = av.disp)) +
-  #   #geom_violin() +
-  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
-  #   geom_boxplot(width = 0.1) +
-  #   #geom_point(aes(x=0, color = run)) +
-  #   lims(y = c(0, 1300)) +
-  #   labs(y = "Dispersal in meters") +
-  #   theme_bw() +
-  #   NULL -> dispersalplot
-  # 
-  # plot_grid(seedlocplot, dispersalplot, dispersionplot, ncol=3, rel_widths = c(2,1,1))
-  # 
+      plot_grid(seedlocplot, summaryplot, ncol = 2)
     }
 
+  else{seedlocplot}
+}
+
+# A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP", twoplots = TRUE)
+# A
+
 A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")
-
-#A
-
 B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
@@
 
-seedplots2d <- plot_grid(A, B, C, ncol = 3)
-
-# To do:
-# Remove xy labels
-# change colors so only over 500 shows blue
-# remove legends
-# Add boxplots for dispersion next to it
-# Am I adding dispersal?
-# For final figure increase sample size to 50,000 so we have 10% of the data visualized.
+seedplots2d <- plot_grid(A, B, C, ncol = 3, labels = "A")
+#seedplots2d
 
@@
   group_by(., model) %>%
-  sample_n(., 50000) %>%
+  sample_n(., 5000) %>%
   #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
@@
   theme(legend.position = "none",
-        axis.title = element_blank()) -> p_dispersion
+        axis.title.x = element_blank()) -> p_dispersion
 
@@
   group_by(., model) %>%
-  sample_n(., 50000) %>%
-  mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
-  ggplot(., aes(y = av.disp, x = model, color = dispcat)) +
+  sample_n(., 5000) %>%
+  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
+  ggplot(., aes(y = av.disp, x = model
+                #, color = dispcat
+                )) +
   geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
+  #geom_point(color = "grey", alpha = 0.5) +
   scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
@@
   theme(legend.position = "none",
-        axis.title = element_blank()) -> p_dispersal
+        axis.title.x = element_blank()) -> p_dispersal
 
-plot_grid(p_dispersal, p_dispersion)
+disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("B", "C"))
+#disp2_plot
+
+```
+
+```{r fig.height=9}
+plot_grid(seedplots2d, disp2_plot, nrow = 2)
 

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
YEs! we have figure 4
Ok, almost finished with the figures for ch1.

@@
 my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
+scales::show_col(my.cols1)
 
@@
 
-qtable_models
+knitr::kable(qtable_models)
 ```
@@
 
-points_plot <- function(seed.data, summ.data, s.size = 5000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){
+points_plot <- function(seed.data, summ.data, s.size = 50000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){
 
@@
   group_by(., model) %>%
-  sample_n(., 5000) %>%
+  sample_n(., 10000) %>%
   #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
@@
   group_by(., model) %>%
-  sample_n(., 5000) %>%
+  sample_n(., 10000) %>%
   #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
@@
 
-```{r fig.height=9}
+```{r fig.height=7.5, fig.width=9}
 plot_grid(seedplots2d, disp2_plot, nrow = 2)
@@
 # ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
-
-```
-
-```{r}
-cp.df %>% 
-  drop_na(s.id) %>% 
-  left_join(., cp.summ.df) -> testdata
-
-testdata %>% 
-  sample_n(1000) %>% 
-  ggplot(., aes(x = xloc, y = yloc, color = dsprsn)) +
-  geom_point() +
-  scale_color_viridis_c(direction = -1) +
-  theme_bw()
-
-cp.summ.df %>% 
-  sample_n(1000) %>% 
-  ggplot(., aes(y = dsprsn, x = av.disp)) +
-  geom_point()
-
-cp.summ.df %>% 
-  sample_n(100) %>% 
-  ggplot(., aes(x = x, y = y, color = dsprsn)) +
-  scale_color_gradient(low = "green", high = "blue") +
-  geom_point(alpha = 0.8) +
-  coord_equal() +
-  theme_bw()
 
@@
 joint_weib %>% 
-  mutate(model = factor(model, levels = c("cp", "pp",
-                                          "np"))) -> joint_weib
+  mutate(model = toupper(model),
+         model = factor(model, levels = c("CP", "PP","NP"))) -> joint_weib
 
 ```
+
+The violin plot here is made with all the data, the jitter points are a random sample of 200
 
@@
   group_by(model) %>%
-  sample_n(., 200) %>%
+  #sample_n(., 100) %>%
   ggplot(., aes(x = model, y = est.shape)) +
@@
   #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
+  geom_jitter(data = joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
   geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(title = "Shape") +
+  labs(y = "Shape") +
   #scale_y_continuous(limits = c(0, 2)) +
-  theme_bw() -> weib_shape
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL -> weib_shape
 
@@
   group_by(model) %>%
-  sample_n(., 200) %>%
+  #sample_n(., 200) %>%
   ggplot(., aes(x = model, y = est.scale)) +
@@
   #              geom="pointrange", color="black") +
-  geom_jitter(position = position_jitter(0.1)) +
-  labs(title = "Scale") +
-  theme_bw() -> weib_scale
+  geom_jitter(data = joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  labs(y = "Scale") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL-> weib_scale
 
@@
 
-```{r}
+Kernel density estimation plots with kde1d
+
+```{r fig.width=9, fig.height=3.5}
 library(kde1d)
@@
 
+rbind(CIs.cp.shape, CIs.pp.shape, CIs.np.shape, CIs.cp.scale, CIs.pp.scale, CIs.np.scale) %>% 
+  as.data.frame() %>% 
+  rename(low = V1, mean = V2, high = V3) %>%
+  tibble::rownames_to_column("model") %>% 
+  mutate(param = stringr::str_sub(model, start = 8),
+         model =stringr::str_sub(model, start = 5, end = 6),
+         model = toupper(model),
+         model = factor(model, levels = c("CP", "PP", "NP"))) -> CIdata
+
+CIdata %>% 
+  filter(., param == "shape") %>% 
+  ggplot(., aes(x  = model, y = mean)) +
+  geom_point() +
+  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
+  labs(y = "Value", x = "Shape") +
+  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
+  theme_bw() +
+  theme(legend.title = element_blank(),
+        legend.position = c(0.9, 0.2)) -> ShapeCI
+
+CIdata %>% 
+  filter(., param == "scale") %>% 
+  ggplot(., aes(x  = model, y = mean)) +
+  geom_point() +
+  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
+  labs(y = "Value", x = "Scale") +
+  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
+  theme_bw() +
+  theme(legend.title = element_blank(),
+        legend.position = c(0.9, 0.2)) -> ScaleCI
+
+plot_grid(ShapeCI, ScaleCI)
+
 # The proportion of shape parameter values above the sampling distribution is 
@@
 
-plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
-lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
-lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")
+```
 
-plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
-lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
-lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
+```{r fig.width=9}
+data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
+  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
+  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
+  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
+  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
+  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
+  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata
+
+kerneldata %>% 
+  filter(., param == "shape") %>% 
+  ggplot(., aes(x = grid_points, y = values, color = model)) +
+  geom_line() +
+  labs(y = "Density", x = "Shape") +
+  scale_color_manual(values = my.cols1[c(1,4,6)]) +
+  theme_bw() +
+  theme(legend.title = element_blank(),
+        legend.position = c(0.9, 0.2)) -> shapeplot
+
+kerneldata %>% 
+  filter(., param == "scale") %>% 
+  ggplot(., aes(x = grid_points, y = values, color = model)) +
+  geom_line() +
+  labs(y = "Density", x = "Scale") +
+  scale_color_manual(values = my.cols1[c(1,4,6)]) +
+  theme_bw() +
+  theme(legend.title = element_blank(),
+        legend.position = c(0.9, 0.2)) -> scaleplot
+
+plot_grid(shapeplot, scaleplot, ncol = 2)
+
+# plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
+# lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
+# lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")
+# 
+# plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
+# lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
+# lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
 

### 2021-11-19 Ch1_movement_rates/Ch1_data_analysis.R
So I don't overwrite stuff again.

@@ -40,7 +40,7 @@ for(j in 1:n.boots){
   weib.boot.cp <- rbind.data.frame(weib.boot.cp, prms.weib %>% mutate(boot = j))
 }
 
-save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
+#save(weib.boot.cp, file = "Ch1_movement_rates/sims_backup/weib_cp.RData")
 
 ## PP Kernel ---------------------------------------------------------------------
 n.boots <- 1000
@@ -66,7 +66,7 @@ for(j in 1:n.boots){
   weib.boot.pp <- rbind.data.frame(weib.boot.pp, prms.weib %>% mutate(boot = j))
 }
 
-save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
+#save(weib.boot.pp, file = "Ch1_movement_rates/sims_backup/weib_pp.RData")
 
 
 ## NP Kernel ------------------------------------------------------------------
@@ -90,7 +90,7 @@ for(j in 1:n.boots){
   weib.boot.np <- rbind.data.frame(weib.boot.np, prms.weib %>% mutate(boot = j))
 }
 
-save(weib.boot.np, file = "Ch1_movement_rates/sims_backup/weib_np.RData")
+#save(weib.boot.np, file = "Ch1_movement_rates/sims_backup/weib_np.RData")
 
 
 # Long distance dispersal percentage ------------------
@@ -159,7 +159,7 @@ disp_table <- data.frame(
             paste0(signif(calc_ldd(pp.seed, thresh = 100)*100, 4), "%"),
             paste0(signif(calc_ldd(np.seed, thresh = 100)*100, 4), "%")))
 
-write.csv(disp_table, "Ch1_movement_rates/Figures/table2.csv")
+#write.csv(disp_table, "Ch1_movement_rates/Figures/table2.csv")
 
 # weibull_table <- data.frame(
 #   Weibull_Shape = c(paste0(signif(null_weibull$estimate[1], 4), " (", signif(null_weibull$sd[1], 2), ")"),

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
Working on Figures 4 and 5 from results

@@
     drop_na(s.id) %>% 
-    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
+    mutate(dispcat = ifelse(disp <150, "non", 
+                            ifelse(disp <500, "med", "ldd"))) %>% 
     #slice_head(., n = s.size) %>% 
@@
       geom_point(alpha = lalpha) +
-      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
-      geom_text(label = scenario, x = -1000, y = -1000, color = "black") +
+      scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
+      geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
       coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
@@
   scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
-  labs(y = "Average dispersal in meters") +
+  labs(y = "Average dispersal per run in meters") +
   theme_bw() +
@@
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
 
@@
 
-# Figure 5 - seed dispersal kernel parameters
+# Figure 5 - All about the seed dispersal Kernels - Weibull
+
 Here we are using the distance of each seed
@@
          model = factor(model, levels = c("CP", "PP","NP"))) -> joint_weib
+
+### Calculate the mean and variance for these weibull distributions based on their estimated parameters
+
+meanvar.weibull <- function(shape, scale){
+
+  meanweibull <- scale * gamma(1+(1/shape))
+
+  varweibull <- (scale^2)*(gamma(1+(2/shape))-(gamma(1+(1/shape))^2))
+
+  return(c(meanweibull, varweibull))
+}
+
+joint_weib %>% 
+  mutate(meanweib = est.scale * gamma(1+(1/est.shape)),
+         varweib = (est.scale^2)*(gamma(1+(2/est.shape))-(gamma(1+(1/est.shape))^2))) -> joint_weib
 
@@
 
-plot_grid(weib_shape, weib_scale)
+joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = meanweib)) +
+  geom_violin() +
+  geom_jitter(data = joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  #geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(y = "Mean") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL -> weib_mean
+
+joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = varweib)) +
+  geom_violin() +
+  geom_jitter(data = joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  labs(y = "Variance") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL-> weib_variance
+
+plot_grid(weib_shape, weib_scale, weib_mean, weib_variance, ncol = 4)
 
 #ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")
+
+```
+
+```{r}
+z.joint_weib <- joint_weib %>% 
+  mutate(est.shape = scale(est.shape),
+         est.scale = scale(est.scale),
+         meanweib = scale(meanweib),
+         varweib = scale(varweib))
+
+z.joint_weib %>%
+  group_by(model) %>%
+  #sample_n(., 100) %>%
+  ggplot(., aes(x = model, y = est.shape)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(data = z.joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  #geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(y = "Shape") +
+  #scale_y_continuous(limits = c(0, 2)) +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL -> weib_shape
+
+z.joint_weib %>%
+  group_by(model) %>%
+  #sample_n(., 200) %>%
+  ggplot(., aes(x = model, y = est.scale)) +
+  geom_violin() +
+  # scale_color_manual(values = c("black", mycols)) +
+  # geom_boxplot(width = 0.01) +
+  # geom_point(color = "grey", alpha = 0.5) +
+  # stat_summary(fun.data=mean_sdl, mult=1,
+  #              geom="pointrange", color="black") +
+  geom_jitter(data = z.joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  labs(y = "Scale") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL-> weib_scale
+
+z.joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = meanweib)) +
+  geom_violin() +
+  geom_jitter(data = z.joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  #geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(y = "Mean") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL -> weib_mean
+
+z.joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = varweib)) +
+  geom_violin() +
+  geom_jitter(data = z.joint_weib %>% 
+                group_by(model) %>% 
+                sample_n(200),
+              position = position_jitter(0.1)) +
+  labs(y = "Variance") +
+  theme_bw() +
+  theme(axis.title.x = element_blank()) +
+  NULL-> weib_variance
+
+plot_grid(weib_shape, weib_scale, weib_mean, weib_variance, ncol = 4)
+
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")
+
+```
+
+```{r}
+z.joint_weib %>% 
+  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
+  ggplot(., aes(x = name, y = value, color = model)) +
+  geom_boxplot() +
+  theme_bw()
 

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
Gosh, i think I figured out how they calculated their stuff in the garcia borda de agua paper.

@@
 
-knitr::kable(qtable_models)
+qtable_models
 ```
@@
 
-```{r fig.width=9}
+```{r fig.width=10}
 data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
@@
 ```
+
+### EVD generalized pareto results
+
+```{r}
+library(extRemes)
+
+```
+
+```{r fig.show='hide'}
+
+nint <- 70 # number of intervals. how many thresholds to try
+r <- c(0, 700) # range over which to try the thresholds
+nsamps <- 500 # random sample form the distances
+
+cp.df %>%
+  drop_na(., s.id) %>%
+  sample_n(., nsamps) -> cp.evd
+
+cp_threshplot <- threshrange.plot(cp.evd$disp, r = r, type = "GP", nint = nint)
+
+```
+
+```{r}
+as.data.frame(cp_threshplot) %>%
+  mutate(u.i = seq(r[1], r[2], length.out = nint)) -> cp_threshplot
+
+```
+
+```{r}
+a <- read.table("Ch1_movement_rates/dispdistancestest.txt")
+a
+
+threshrange.plot(a$V1, type = "GP", nint = 100, r = c(0,700))
+c <- mrlplot(a$V1)
+mrlplot(a$V1)
+
+max(c[,3])
+
+b <- decluster(a$V1, threshold = 170)
+
+threshrange.plot(b)
+
+fevd(b, threshold = 170, type = "GP")
+
+as.data.frame(c) -> d
+
+model <- lm(d$`Mean Excess`~1)
+confint(model, level = 0.9)
+
+```

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
evd results process is getting there.

@@
 
+1. Make threshold plot to figure out threshold
+2. Make associated mean excess plot
+3. Calculate the 95% quantile for mean excess to use as threshold
+4. Make threshplot and show the threshold based on the mean excess
+5. fit a gpd distribution using that threshold and report parameter values
+6. Calculate conditional probabilities over certain distances
+
 ```{r}
@@
 
-b <- decluster(a$V1, threshold = 170)
-
-threshrange.plot(b)
-
-fevd(b, threshold = 170, type = "GP")
-
 as.data.frame(c) -> d
@@
 
+b <- decluster(a$V1, threshold = 170)
+
+threshrange.plot(b)
+
+fit <- fevd(b, threshold = 170, type = "GP")
+plot(fit)
+fit$results
+
+1-pevd(1000,threshold = 170, scale= fit$results$par[1], shape = fit$results$par[2], type = "GP")
+
+# OR
+
+dist_range <- c(1000, 5000, 10000)
+pextRemes(fit, dist_range, lower.tail = FALSE)
+
 ```

### 2021-11-22 Ch1_movement_rates/Ch1_data_analysis_evd.R
Need a new script to analyze the evd stuff

@@ -1,0 +1,10 @@
+# Script for evd analysis
+
+library(dplyr)
+library(extRemes)
+library(ggplot2)
+
+# Bring data --------------------------------------------
+load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
+load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
+load("Ch1_movement_rates/sims_backup/datagen_np.RData")

### 2021-11-22 Ch1_movement_rates/Ch1_Figures.Rmd
just added a comment

@@
 
+# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
 dist_range <- c(1000, 5000, 10000)
@@
 
+# Not sure this is right though. I want the conditional probability that a dispersal distance that is already over the threshold goes beyong 1000, 5000, and 10000 meters.
+
 ```

### 2021-11-23 Ch1_movement_rates/Ch1_Figures.Rmd
I'm going to say, figure 4 is ready.

@@
 library(gtsummary)
+library(extRemes)
 ```
@@
 
+  # seed.data %>% 
+  #   drop_na(s.id) %>% 
+  #   mutate(dispcat = ifelse(disp <150, "non", 
+  #                           ifelse(disp <500, "med", "ldd"))) %>% 
+  #   #slice_head(., n = s.size) %>% 
+  #   sample_n(s.size) %>% 
+  #     ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
+  #     geom_point(alpha = lalpha) +
+  #     scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
+  #     geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
+  #     coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
+  #     theme_bw() +
+  #     theme(legend.position = "none",
+  #           axis.title = element_blank()) +
+  #      NULL -> seedlocplot
+
   seed.data %>% 
     drop_na(s.id) %>% 
-    mutate(dispcat = ifelse(disp <150, "non", 
-                            ifelse(disp <500, "med", "ldd"))) %>% 
-    #slice_head(., n = s.size) %>% 
+    mutate(LDD = ifelse(disp <500, NA, "Over 500")) %>% 
     sample_n(s.size) %>% 
-      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
-      geom_point(alpha = lalpha) +
-      scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
+      ggplot(., aes(x = xloc, 
+                    y = yloc
+                    , color = LDD
+                    )) +
+      geom_hex()+
+      scale_fill_gradient(low = "grey", high = "black") +
+      #geom_point(alpha = lalpha) +
+      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
       geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
@@
     #drop_na(s.id) %>% 
-    mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>% 
+    mutate(dispcat = ifelse(av.disp <500, "non", "Over 500")) %>% 
     #slice_head(., n = s.size) %>% 
@@
 
-seedplots2d <- plot_grid(A, B, C, ncol = 3, labels = "A")
+prow <- plot_grid(A, B, C, ncol = 3, labels = "A")
+
+legend <- get_legend(C + scale_fill_gradient(low = "grey", high = "black",
+                                             name = "Count",
+                          guide = guide_colorbar(barwidth = 15, 
+                                                barheight = 0.5,
+                                                title.position = "left",
+                                                title.vjust = 1.1,
+                                                 #label.position = "left",
+                                                 nbin = 100)) +
+  scale_color_manual(values = c(LDD = my.cols1[6]), name = "")+
+    guides(color = guide_legend(override.aes = list(fill = my.cols1[6]))) +
+    theme(legend.position = "bottom"))
+
+seedplots2d <- plot_grid(prow, legend, rel_heights = c(1,0.1), ncol = 1)
 #seedplots2d
@@
 ```{r fig.height=7.5, fig.width=9}
-plot_grid(seedplots2d, disp2_plot, nrow = 2)
+plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))
 
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
 
@@
 
-### EVD generalized pareto results
+### FIGURE 6 EVD generalized pareto results
 
@@
 
-```{r}
-library(extRemes)
+```{r results='hide'}
 
-```
+# subset data ---------------------------------
 
-```{r fig.show='hide'}
-
-nint <- 70 # number of intervals. how many thresholds to try
-r <- c(0, 700) # range over which to try the thresholds
-nsamps <- 500 # random sample form the distances
+nsamps <- 10000
+itera <- 1000
 
@@
 
-cp_threshplot <- threshrange.plot(cp.evd$disp, r = r, type = "GP", nint = nint)
+pp.df %>%
+  drop_na(., s.id) %>%
+  sample_n(., nsamps) -> pp.evd
+
+np.df %>%
+  drop_na(., s.id) %>%
+  sample_n(., nsamps) -> np.evd
+
+cp.evd %>%
+  mutate(model = toupper(model)) %>%
+  bind_rows(pp.evd %>% mutate(model = toupper(model))) %>%
+  bind_rows(np.evd %>% mutate(model = toupper(model))) %>%
+  group_by(model) %>%
+  summarise(q75 = quantile(disp, 0.75),
+            q90 = quantile(disp, 0.9),
+            q99 = quantile(disp, 0.99),
+            max = max(disp))
+
+# Find threshold -------------------------------------
+## CP ----------------------------
+
+r <- c(0, 600)
+
+nint <- 100
+# r <- quantile(cp.evd$disp, c(0.75, 0.99))
+u.i <- matrix(seq(r[1],r[2],,nint), ncol=1)
+
+cp.mrl <- mrlplot(cp.evd$disp)
+lm.cp <- lm(cp.mrl[,2]~1)
+tval.cp <- confint(lm.cp, level = 0.9)[2]
+
+thresh.cp <- threshrange.plot(cp.evd$disp, r = r, type = "GP", nint = nint) %>%
+  as.data.frame() %>%
+  mutate(u.i = u.i)
+
+## PP ----------------------------
+
+nint <- 100
+# r <- quantile(pp.evd$disp, c(0.75, 0.99))
+u.i <- matrix(seq(r[1],r[2],,nint), ncol=1)
+
+pp.mrl <- mrlplot(pp.evd$disp)
+lm.pp <- lm(pp.mrl[,2]~1)
+tval.pp <- confint(lm.pp, level = 0.9)[2]
+
+thresh.pp <- threshrange.plot(pp.evd$disp, r = r, type = "GP", nint = nint) %>%
+  as.data.frame() %>%
+  mutate(u.i = u.i)
+
+## NP ----------------------------
+
+nint <- 100
+# r <- quantile(pp.evd$disp, c(0.75, 0.99))
+u.i <- matrix(seq(r[1],r[2],,nint), ncol=1)
+
+np.mrl <- mrlplot(np.evd$disp)
+lm.np <- lm(np.mrl[,2]~1)
+tval.np <- confint(lm.np, level = 0.9)[2]
+
+thresh.np <- threshrange.plot(np.evd$disp, r = r, type = "GP", nint = nint) %>%
+  as.data.frame() %>%
+  mutate(u.i = u.i)
 
@@
 
-```{r}
-as.data.frame(cp_threshplot) %>%
-  mutate(u.i = seq(r[1], r[2], length.out = nint)) -> cp_threshplot
+```{r fig.width=12, fig.height=3}
+# Threshold figures
+
+threshplot_fx <- function(thresh_data, th, r, model){
+
+  th <- round(th)
+
+  thresh_data %>%
+    ggplot(., aes(y = t.scale, x = u.i)) +
+    geom_point(shape = 1, size = 2) +
+    # geom_line(linetype = "dashed") +
+    geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
+    labs(title = paste(model, "threshold =", th, "m"), 
+         x = "Threshold in meters", y = "Scale") +
+    theme_bw() +
+    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
+    scale_x_continuous(limits = r, n.breaks = 7 ) +
+    # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
+    # theme(axis.title.x = element_blank(),
+    #       axis.ticks.x = element_blank(),
+    #       axis.text.x = element_blank()) +
+    # coord_cartesian(xlim = c(200, 550)) +
+    NULL -> thresh_scale
+
+  thresh_data %>%
+    ggplot(., aes(y = shape, x = u.i)) +
+    geom_point(shape = 1, size = 2) +
+    geom_linerange(aes(x = u.i, ymin = low.shape, ymax = up.shape)) +
+    labs(x = "Threshold in meters", y = "Shape") +
+    theme_bw() +
+    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
+    scale_x_continuous(limits = r, n.breaks = 7 ) +
+    # coord_cartesian(xlim = c(200, 550)) +
+    NULL -> thresh_shape
+
+  plot_grid(thresh_scale, thresh_shape, nrow = 2)
+
+}
+
+plot.cp <- threshplot_fx(thresh_data = thresh.cp, th = tval.cp, r = r, model = "CP")
+plot.pp <- threshplot_fx(thresh_data = thresh.pp, th = tval.pp, r = r, model = "PP")
+plot.np <- threshplot_fx(thresh_data = thresh.np, th = tval.np, r = r, model = "NP")
+
+plot_grid(plot.cp, plot.pp, plot.np, ncol = 3)
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure6.png")
 
@@
 
+## Fit values
+
 ```{r}
-a <- read.table("Ch1_movement_rates/dispdistancestest.txt")
-a
 
-threshrange.plot(a$V1, type = "GP", nint = 100, r = c(0,700))
-c <- mrlplot(a$V1)
-mrlplot(a$V1)
+evd.fit.cp <-fevd(cp.evd$disp, threshold = tval.cp, type = "GP")
+evd.fit.pp <- fevd(pp.evd$disp, threshold = tval.cp, type = "GP")
+evd.fit.np <- fevd(np.evd$disp, threshold = tval.cp, type = "GP")
 
-max(c[,3])
+summary(evd.fit.cp)
+summary(evd.fit.pp)
+summary(evd.fit.np)
 
-as.data.frame(c) -> d
+```
 
-model <- lm(d$`Mean Excess`~1)
-confint(model, level = 0.9)
+Find the conditional probabilities. Probability of exceeding a distance x, based on the fitted distribution
 
-b <- decluster(a$V1, threshold = 170)
-
-threshrange.plot(b)
-
-fit <- fevd(b, threshold = 170, type = "GP")
-plot(fit)
-fit$results
-
-1-pevd(1000,threshold = 170, scale= fit$results$par[1], shape = fit$results$par[2], type = "GP")
-
-# OR
+```{r}
 
 # To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
-dist_range <- c(1000, 5000, 10000)
-pextRemes(fit, dist_range, lower.tail = FALSE)
+dist_range <- c(200, 500, 1000, 5000, 10000)
+
+pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE)
+pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE)
+pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)
 

### 2021-11-23 Ch1_movement_rates/Ch1_Figures.Rmd
Progress with figures.
Modified figure 4 so it only has the dispersion and dispersal per run.

@@
 ```{r}
+
 disp_df %>% 
   group_by(model) %>% 
-  summarise(av.disp = round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1),
-            dsprsn = round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1),
-            q = c("min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
+  summarise(av.disp = c(mean(av.disp), sd(av.disp), n(), round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1)),
+            dsprsn = c(mean(dsprsn), sd(dsprsn), n(), round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1)),
+            q = c("mean", "sd", "n", "min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
   pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
@@
 
-Too many points, since we have 500k seeds, show only a percentage.
+```{r fig.width=9, fig.height=3}
+
+disp_df %>%
+  group_by(., model) %>%
+  ggplot(., aes(x = dsprsn, y = factor(model, levels = c("NP", "PP", "CP")))) +
+  geom_violin(color = my.cols1[7], fill = my.cols1[7]) +
+  geom_boxplot(width = 0.1, color = "black") +
+  labs(x = "Dispersion per run (m)") +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title.y = element_blank()) -> p_dispersion
+
+disp_df %>%
+  group_by(., model) %>%
+  ggplot(., aes(x = av.disp, y = factor(model, levels = c("NP", "PP", "CP")))) +
+  geom_violin(color = my.cols1[7], fill = my.cols1[7]) +
+  geom_boxplot(width = 0.1, color = "black") +
+  #geom_point(color = "grey", alpha = 0.5) +
+  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
+  labs(x = "Average dispersal per run (m)") +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title.y = element_blank()) -> p_dispersal
+
+disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
+
+disp2_plot
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+
+# Thinking about the long distance or spread: visualize or focus on the 90th percentile data?
+
+```
+
+Figure 5 - Dispersal for each seed and dispersal kernels
 
@@
 
-```{r fig.width=9, fig.height=4}
-
-disp_df %>%
-  group_by(., model) %>%
-  sample_n(., 10000) %>%
-  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
-  ggplot(., aes(y = dsprsn, x = model)) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
-  labs(y = "Dispersion in meters") +
-  theme_bw() +
-  theme(legend.position = "none",
-        axis.title.x = element_blank()) -> p_dispersion
-
-disp_df %>%
-  group_by(., model) %>%
-  sample_n(., 10000) %>%
-  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
-  ggplot(., aes(y = av.disp, x = model
-                #, color = dispcat
-                )) +
-  geom_boxplot() +
-  #geom_point(color = "grey", alpha = 0.5) +
-  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
-  labs(y = "Average dispersal per run in meters") +
-  theme_bw() +
-  theme(legend.position = "none",
-        axis.title.x = element_blank()) -> p_dispersal
-
-disp2_plot <- plot_grid(p_dispersal, p_dispersion, ncol = 2, labels = c("B", "C"))
-#disp2_plot
-
-```
-
-```{r fig.height=7.5, fig.width=9}
+```{r fig.height=7.5, fig.width=9, eval = FALSE}
 plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))
 
-#ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
-
-```
-
-# Figure 5 - All about the seed dispersal Kernels - Weibull
-
-Here we are using the distance of each seed
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+
+```
 

### 2021-11-23 Ch1_movement_rates/Ch1_Figures.Rmd
Updates on Figures

@@
 
-disp2_plot
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+# disp2_plot
+# ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
 
@@
 
-Figure 5 - Dispersal for each seed and dispersal kernels
-
-```{r fig.width=9, fig.height=3.5}
-
-points_plot <- function(seed.data, summ.data, s.size = 50000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){
-
-  # seed.data %>% 
-  #   drop_na(s.id) %>% 
-  #   mutate(dispcat = ifelse(disp <150, "non", 
-  #                           ifelse(disp <500, "med", "ldd"))) %>% 
-  #   #slice_head(., n = s.size) %>% 
-  #   sample_n(s.size) %>% 
-  #     ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
-  #     geom_point(alpha = lalpha) +
-  #     scale_color_manual(values = c(my.cols1[6], my.cols1[7], "black")) +
-  #     geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
-  #     coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
-  #     theme_bw() +
-  #     theme(legend.position = "none",
-  #           axis.title = element_blank()) +
-  #      NULL -> seedlocplot
+```{r}
+points_plot <- function(seed.data, s.size = 50000, xylims=1250, scenario = NULL, lalpha = 0.5){
 
@@
     drop_na(s.id) %>% 
-    mutate(LDD = ifelse(disp <500, NA, "Over 500")) %>% 
+    mutate(LDD = ifelse(disp <500, NA, "Over 500m")) %>% 
     sample_n(s.size) %>% 
@@
       #geom_point(alpha = lalpha) +
-      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
+      scale_color_manual(values = my.cols1[6], na.translate = F) +
       geom_text(label = scenario, x = -1100, y = -1100, color = "black") +
@@
             axis.title = element_blank()) +
-       NULL -> seedlocplot
-
-    if(twoplots == TRUE){
-
-          summ.data %>% 
-    #drop_na(s.id) %>% 
-    mutate(dispcat = ifelse(av.disp <500, "non", "Over 500")) %>% 
-    #slice_head(., n = s.size) %>% 
-    sample_n(s.size*5) %>% 
-      ggplot(., aes(x = x, y = y, color = dispcat)) +
-      geom_point(alpha = lalpha) +
-      labs(subtitle = scenario) +
-      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
-      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
-      theme_bw() +
-      theme(legend.position = "none",
-            axis.title = element_blank()) +
-       NULL -> summaryplot
-
-      plot_grid(seedlocplot, summaryplot, ncol = 2)
+       NULL
 }
-
-  else{seedlocplot}
-}
-
-# A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP", twoplots = TRUE)
-# A
-
-A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")
-B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
-C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")
-
-prow <- plot_grid(A, B, C, ncol = 3, labels = "A")
-
-legend <- get_legend(C + scale_fill_gradient(low = "grey", high = "black",
+```
+
+```{r fig.width=9, fig.height=3.5}
+A <- points_plot(seed.data = cp.summ.df %>% 
+              mutate(disp = av.disp,
+                     s.id = run,
+                     xloc = x,
+                     yloc = y), scenario = "CP")
+B <- points_plot(seed.data = pp.summ.df %>% 
+              mutate(disp = av.disp,
+                     s.id = id,
+                     xloc = x,
+                     yloc = y), scenario = "PP")
+C <- points_plot(seed.data = np.summ.df %>% 
+              mutate(disp = av.disp,
+                     s.id = id,
+                     xloc = x,
+                     yloc = y), scenario = "NP")
+prowB <- plot_grid(A, B, C, ncol = 3)
+legend <- get_legend(C + theme(legend.position = "bottom") +
+  scale_fill_gradient(low = "lightgray", high = "black",
                                              name = "Count",
@@
                                                  nbin = 100)) +
-  scale_color_manual(values = c(LDD = my.cols1[6]), name = "")+
-    guides(color = guide_legend(override.aes = list(fill = my.cols1[6]))) +
-    theme(legend.position = "bottom"))
+    guides(color = guide_legend(title = element_blank(),override.aes = list(fill = "lightgray",
+                                                                            size = 5), direction = "horizontal")))
+hexplot <- plot_grid(prowB, legend, rel_heights = c(1,0.1), ncol = 1, labels = c("C)"), hjust = 0, vjust = 1, label_size = 10)
+
+```
+
+```{r fig.height=7.5, fig.width=9}
+plot_grid(disp2_plot, NULL, hexplot, nrow = 3, rel_heights = c(1,0.05,1))
+
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+
+```
+
+Figure 5 - Dispersal kernels
+
+```{r fig.width=9, fig.height=3.5, eval = FALSE}
+
+A <- points_plot(seed.data = cp.df, scenario = "CP")
+B <- points_plot(seed.data = pp.df, scenario = "PP")
+C <- points_plot(seed.data = np.df, scenario = "NP")
+
+prow <- plot_grid(A, B, C, ncol = 3, labels = "A")
+
+legend <- get_legend(C + theme(legend.position = "bottom") +
+  scale_fill_gradient(low = "lightgray", high = "black",
+                                             name = "Count",
+                          guide = guide_colorbar(barwidth = 15, 
+                                                barheight = 0.5,
+                                                title.position = "left",
+                                                title.vjust = 1.1,
+                                                 #label.position = "left",
+                                                 nbin = 100)) +
+    guides(color = guide_legend(title = element_blank(),override.aes = list(fill = "lightgray",
+                                                                            size = 5), direction = "horizontal")))
 
 seedplots2d <- plot_grid(prow, legend, rel_heights = c(1,0.1), ncol = 1)
-#seedplots2d
-
-```
-
-```{r fig.height=7.5, fig.width=9, eval = FALSE}
-plot_grid(seedplots2d, NULL, disp2_plot, nrow = 3, rel_heights = c(1,0.2,1))
-
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+seedplots2d
 
@@
 
-```{r results='hide'}
+```{r include = FALSE}
 

### 2021-11-24 Ch1_movement_rates/Ch1_Figures.Rmd
Hmmm. I think my computer hates me now. I may need to give it a break. Working on density plots with thousands of lines.

@@
 
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure4.png")
 
@@
 # lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
+
+```
+
+## Figure Dispersal Kernels
+
+```{r}
+cp_lines <- purrr::map(seq(1:1000), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = "lightgray"))
+
+pp_lines <- purrr::map(seq(1:1000), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = "lightgray"))
+
+np_lines <- purrr::map(seq(1:1000), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = "lightgray"))
+
+ggplot() +
+  cp_lines +
+  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[1], scale = CIs.cp.scale[1]), 
+                color = "black", linetype = "dashed") +
+  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[2], scale = CIs.cp.scale[2]), color = "black") +
+  stat_function(fun = dweibull, args = list(shape = CIs.cp.shape[3], scale = CIs.cp.scale[3]),
+                color = "black", linetype = "dashed") +
+  lims(x = c(0, 1250)) +
+  theme_bw() -> CPweibdens
+
+ggplot() +
+  pp_lines +
+  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[1], scale = CIs.pp.scale[1]), 
+                color = "black", linetype = "dashed") +
+  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[2], scale = CIs.pp.scale[2]), color = "black") +
+  stat_function(fun = dweibull, args = list(shape = CIs.pp.shape[3], scale = CIs.pp.scale[3]),
+                color = "black", linetype = "dashed") +
+  lims(x = c(0, 1250)) +
+  theme_bw() -> PPweibdens
+
+ggplot() +
+  np_lines +
+  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[1], scale = CIs.np.scale[1]), 
+                color = "black", linetype = "dashed") +
+  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[2], scale = CIs.np.scale[2]), color = "black") +
+  stat_function(fun = dweibull, args = list(shape = CIs.np.shape[3], scale = CIs.np.scale[3]),
+                color = "black", linetype = "dashed") +
+  lims(x = c(0, 1250)) +
+  theme_bw() -> NPweibdens
+
+plot_grid(CPweibdens, PPweibdens, NPweibdens, nrow = 3)
 

### 2021-11-24 Ch1_movement_rates/Ch1_Figures.Rmd
Working on figure 5

@@
 
-```
-
-The violin plot here is made with all the data, the jitter points are a random sample of 200
+z.joint_weib <- joint_weib %>% 
+  mutate(est.shape = scale(est.shape),
+         est.scale = scale(est.scale),
+         meanweib = scale(meanweib),
+         varweib = scale(varweib))
+
+```
+
+```{r}
+
+fig.5col <- c("#68655a", "#ff814f", "#31aec5")
+
+z.joint_weib %>% 
+  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
+  ggplot(., aes(x = name, y = value, color = model)) +
+  geom_boxplot() +
+  labs(x = "Parameter", y = "Z score") +
+  scale_x_discrete(labels = c("est.scale" = "Scale", "est.shape"="Shape", "meanweib" = "Mean", "varweib"="Variance")) +
+  scale_color_manual(values = fig.5col) +
+  theme_bw() +
+  guides(color = guide_legend(title = "Model")) -> zscoreplot
+
+#plot_grid(meanweib, varweib, nrow = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
+
+```
 
@@
 
-```{r}
-z.joint_weib <- joint_weib %>% 
-  mutate(est.shape = scale(est.shape),
-         est.scale = scale(est.scale),
-         meanweib = scale(meanweib),
-         varweib = scale(varweib))
-
-z.joint_weib %>%
-  group_by(model) %>%
-  #sample_n(., 100) %>%
-  ggplot(., aes(x = model, y = est.shape)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(data = z.joint_weib %>% 
-                group_by(model) %>% 
-                sample_n(200),
-              position = position_jitter(0.1)) +
-  #geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(y = "Shape") +
-  #scale_y_continuous(limits = c(0, 2)) +
-  theme_bw() +
-  theme(axis.title.x = element_blank()) +
-  NULL -> weib_shape
-
-z.joint_weib %>%
-  group_by(model) %>%
-  #sample_n(., 200) %>%
-  ggplot(., aes(x = model, y = est.scale)) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.01) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  # stat_summary(fun.data=mean_sdl, mult=1,
-  #              geom="pointrange", color="black") +
-  geom_jitter(data = z.joint_weib %>% 
-                group_by(model) %>% 
-                sample_n(200),
-              position = position_jitter(0.1)) +
-  labs(y = "Scale") +
-  theme_bw() +
-  theme(axis.title.x = element_blank()) +
-  NULL-> weib_scale
-
-z.joint_weib %>%
-  group_by(model) %>%
-  ggplot(., aes(x = model, y = meanweib)) +
-  geom_violin() +
-  geom_jitter(data = z.joint_weib %>% 
-                group_by(model) %>% 
-                sample_n(200),
-              position = position_jitter(0.1)) +
-  #geom_hline(aes(yintercept = 1), lty = "dashed") +
-  labs(y = "Mean") +
-  theme_bw() +
-  theme(axis.title.x = element_blank()) +
-  NULL -> weib_mean
-
-z.joint_weib %>%
-  group_by(model) %>%
-  ggplot(., aes(x = model, y = varweib)) +
-  geom_violin() +
-  geom_jitter(data = z.joint_weib %>% 
-                group_by(model) %>% 
-                sample_n(200),
-              position = position_jitter(0.1)) +
-  labs(y = "Variance") +
-  theme_bw() +
-  theme(axis.title.x = element_blank()) +
-  NULL-> weib_variance
-
-plot_grid(weib_shape, weib_scale, weib_mean, weib_variance, ncol = 4)
-
-#ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")
-
-```
-
-```{r}
-z.joint_weib %>% 
-  pivot_longer(., cols = c(est.shape, est.scale, meanweib, varweib)) %>% 
-  ggplot(., aes(x = name, y = value, color = model)) +
-  geom_boxplot() +
-  theme_bw()
-
-```
-
 Kernel density estimation plots with kde1d
@@
   as.data.frame() %>% 
-  rename(low = V1, mean = V2, high = V3) %>%
+  rename(low = V1, median = V2, high = V3) %>%
   tibble::rownames_to_column("model") %>% 
@@
 
+joint_weib %>% 
+  group_by(., model) %>% 
+  summarise(meanshape = mean(est.shape),
+            meanscale = mean(est.scale)) %>% 
+  pivot_longer(cols = starts_with("mean")) %>% 
+  mutate(param = stringr::str_sub(name, start = 5),
+         mean = value) %>% 
+  dplyr::select(., -c(value, name)) %>% 
+  left_join(., CIdata) -> CIdata
+
+CIdata %>% 
+  pivot_longer(., cols = c(median, mean, low, high)) %>% 
+  filter(., param == "shape" & name != "median") %>% 
+  pivot_wider(names_from = name) -> CIshape
+
+CIdata %>% 
+  pivot_longer(., cols = c(median, mean, low, high)) %>% 
+  filter(., param == "scale" & name != "median") %>% 
+  pivot_wider(names_from = name) -> CIscale
+
+```
+
+```{r}
+
+cp_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))
+
+pp_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))
+
+np_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))
+
+ggplot() +
+  cp_lines +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
+  lims(x = c(0, 1250), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") -> cp.dens
+
+ggplot() +
+  pp_lines +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
+  lims(x = c(0, 1250), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") -> pp.dens
+
+ggplot() +
+  np_lines +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = "black", size = 1) +
+  lims(x = c(0, 1250), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") -> np.dens
+
+plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)
+
+```
+
+```{r}
+cp.dens +
+  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> cp.tail
+
+pp.dens +
+  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> pp.tail
+
+np.dens +
+  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> np.tail
+
+plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
+
+```
+
+```{r}
+cp.dens +
+  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> cp.tail
+
+pp.dens +
+  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> pp.tail
+
+np.dens +
+  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> np.tail
+
+plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
+```
+
+```{r}
+# all density means
+
+ggplot() +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
+  # Everything after this line is the confidence intervals
+  #   stat_function(fun = dweibull, args = list(shape = CIshape$low[1], scale = CIscale$low[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = CIshape$low[2], scale = CIscale$low[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = CIshape$low[3], scale = CIscale$low[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
+  # lims(x = c(0, 1500), y = c(0, 0.006)) +
+  #     stat_function(fun = dweibull, args = list(shape = CIshape$high[1], scale = CIscale$high[1]), color = fig.5col[1], size = 1, linetype = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = CIshape$high[2], scale = CIscale$high[2]), color = fig.5col[2], size = 1, linetype = "dashed") +
+  # stat_function(fun = dweibull, args = list(shape = CIshape$high[3], scale = CIscale$high[3]), color = fig.5col[3], size = 1, linetype = "dashed") +
+  lims(x = c(0, 1500), y = c(0, 0.0062)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") +
+#coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0002)) +
+    NULL
+```
+
+```{r}
+ggplot() +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
+  lims(x = c(0, 1500), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") +
+  coord_cartesian(xlim = c(500, 1500), ylim = c(0, 0.0003))
+```
+
+```{r eval=FALSE}
 CIdata %>% 
@@
 prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
-
-```
-
-```{r fig.width=10}
+```
+
+```{r fig.width=10, eval = FALSE}
 data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
@@
 
-## Figure Dispersal Kernels
-
-```{r}
-cp_lines <- purrr::map(seq(1:1000), function(y)
-  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = "lightgray"))
-
-pp_lines <- purrr::map(seq(1:1000), function(y)
-  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = "lightgray"))
-
-np_lines <- purrr::map(seq(1:1000), function(y)
-  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = "lightgray"))
+Dispersal Kernels
+
+```{r}
+
+ggplot() +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
+  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
+  cp_lines +
+  pp_lines +
+  np_lines +
+  lims(x = c(0, 1250)) +
+  theme_bw()
+
+```
+
+```{r}
+cp_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))
+
+pp_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))
+
+np_lines <- purrr::map(seq(1:100), function(y)
+  stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))
 

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Dispersal Kernel Grids

@@
 
-```{r}
+```{r eval = FALSE}
 joint_weib %>%
@@
 
-```{r fig.width=9, fig.height=3.5}
+```{r fig.width=9, fig.height=3.5, include = FALSE}
 library(kde1d)
@@
 
-cp_lines <- purrr::map(seq(1:100), function(y)
+xmax <- 1500
+ncurves <- 50
+
+cp_lines <- purrr::map(seq(1:ncurves), function(y)
   stat_function(fun = dweibull, args = list(scale = weib.boot.cp$est.scale[y], shape = weib.boot.cp$est.shape[y]), color = fig.5col[1]))
 
-pp_lines <- purrr::map(seq(1:100), function(y)
+pp_lines <- purrr::map(seq(1:ncurves), function(y)
   stat_function(fun = dweibull, args = list(scale = weib.boot.pp$est.scale[y], shape = weib.boot.pp$est.shape[y]), color = fig.5col[2]))
 
-np_lines <- purrr::map(seq(1:100), function(y)
+np_lines <- purrr::map(seq(1:ncurves), function(y)
   stat_function(fun = dweibull, args = list(scale = weib.boot.np$est.scale[y], shape = weib.boot.np$est.shape[y]), color = fig.5col[3]))
+
+```
+
+```{r KernelCurves}
+
+coords <- c(600, 0.006)
 
@@
   stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = "black", size = 1) +
-  lims(x = c(0, 1250), y = c(0, 0.006)) +
-  theme_bw() +
-  labs(y = "Density", x = "Dispersal (m)") -> cp.dens
+  lims(x = c(0, xmax), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") +
+  theme(axis.title.x = element_blank(),
+        panel.grid.major = element_blank()) +
+  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
+  NULL -> cp.dens
 
@@
   stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = "black", size = 1) +
-  lims(x = c(0, 1250), y = c(0, 0.006)) +
-  theme_bw() +
-  labs(y = "Density", x = "Dispersal (m)") -> pp.dens
+  lims(x = c(0, xmax), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") +
+  theme(axis.title.x = element_blank(),
+        panel.grid.major = element_blank()) +
+  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
+  NULL -> pp.dens
 
@@
   stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = "black", size = 1) +
-  lims(x = c(0, 1250), y = c(0, 0.006)) +
-  theme_bw() +
-  labs(y = "Density", x = "Dispersal (m)") -> np.dens
-
-plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)
-
-```
-
-```{r}
+  lims(x = c(0, xmax), y = c(0, 0.006)) +
+  theme_bw() +
+  labs(y = "Density", x = "Dispersal (m)") +
+  coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
+  theme(panel.grid.major = element_blank()) +
+  NULL -> np.dens
+
+kernelcurvesfig <- plot_grid(cp.dens, pp.dens, np.dens, nrow = 3)
+#kernelcurvesfig
+
+```
+
+```{r eval = FALSE}
 cp.dens +
@@
 
-```{r}
+```{r KernelTails}
+
+backgroundcol <- "#f7f2e4"
+  #"#f7edd5"
+
 cp.dens +
-  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> cp.tail
+  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
+  theme(panel.background = element_rect(fill = backgroundcol),
+        axis.title.y = element_blank()) -> cp.tail
 
 pp.dens +
-  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> pp.tail
+  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
+  theme(panel.background = element_rect(fill = backgroundcol),
+        axis.title.y = element_blank()) -> pp.tail
 
 np.dens +
-  coord_cartesian(xlim = c(500, 1000), ylim = c(0, 0.0001)) -> np.tail
-
-plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
+  coord_cartesian(xlim = c(600, 1000), ylim = c(0, 0.0001)) +
+  theme(panel.background = element_rect(fill = backgroundcol),
+        axis.title.y = element_blank()) -> np.tail
+
+kernel_tails_fig <- plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
+#kernel_tails_fig
+```
+
+```{r KernelGrid}
+plot_grid(kernelcurvesfig, kernel_tails_fig, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
 ```

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Figure5 Ready

@@
 
-```{r}
+```{r loadingData}
 
@@
 
-Kernel density estimation plots with kde1d
-
-```{r fig.width=9, fig.height=3.5, include = FALSE}
+```{r Kde1dEstimates, include = FALSE}
 library(kde1d)
@@
 
-```{r}
+```{r RunPurrrCurves}
 
 xmax <- 1500
-ncurves <- 50
+ncurves <- 200
 
@@
   theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
         panel.grid.major = element_blank()) +
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        axis.title.y = element_blank()) -> cp.tail
+        panel.grid = element_line(color = "white")) +
+  labs(y = "") -> cp.tail
 
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        axis.title.y = element_blank()) -> pp.tail
+        panel.grid = element_line(color = "white")) +
+  labs(y = "") -> pp.tail
 
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        axis.title.y = element_blank()) -> np.tail
+        panel.grid = element_line(color = "white")) +
+  labs(y = "") -> np.tail
 
@@
 
-```{r KernelGrid}
-plot_grid(kernelcurvesfig, kernel_tails_fig, ncol = 2, labels = c("A)", "B)"), hjust = 0, vjust = 1, label_size = 10)
-```
-
-```{r}
+```{r eval = FALSE}
 # all density means
@@
     NULL
-```
-
-```{r}
+
 ggplot() +
@@
 
-```{r eval=FALSE}
+```{r ParamCIs}
 CIdata %>% 
   filter(., param == "shape") %>% 
-  ggplot(., aes(x  = model, y = mean)) +
+  ggplot(., aes(x  = model, y = mean, color = model)) +
   geom_point() +
   geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
-  labs(y = "Value", x = "Shape") +
-  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
-  theme_bw() +
-  theme(legend.title = element_blank(),
-        legend.position = c(0.9, 0.2)) -> ShapeCI
+  labs(y = "Shape value", x = "Model") +
+  scale_color_manual(values = fig.5col) +
+  theme_bw() +
+  theme(legend.position = "none") -> ShapeCI
 
@@
   filter(., param == "scale") %>% 
-  ggplot(., aes(x  = model, y = mean)) +
+  ggplot(., aes(x  = model, y = mean, color = model)) +
   geom_point() +
   geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
-  labs(y = "Value", x = "Scale") +
-  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
-  theme_bw() +
-  theme(legend.title = element_blank(),
-        legend.position = c(0.9, 0.2)) -> ScaleCI
-
-plot_grid(ShapeCI, ScaleCI)
-
-# The proportion of shape parameter values above the sampling distribution is 
-prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
-prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
-prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
+  labs(y = "Scale value", x = "Model") +
+  scale_color_manual(values = fig.5col) +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank()) -> ScaleCI
+
+CIparams_figure <- plot_grid(ScaleCI, ShapeCI, nrow = 2)
+#CIparams_figure
+# # The proportion of shape parameter values above the sampling distribution is 
+# prop.above1.10.cp.shape <- 1-pkde1d(q=1.10, cp.shape.kde)
+# prop.above1.10.pp.shape <- 1-pkde1d(q=1.10, pp.shape.kde)
+# prop.above1.10.np.shape <- 1-pkde1d(q=1.10, np.shape.kde)
+```
+
+```{r MeanVar}
+
+violincolor <- "lightgray"
+
+joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = meanweib)) +
+  geom_violin(color = violincolor, fill = violincolor) +
+  geom_boxplot(width = 0.1, aes(color = model)) +
+  scale_color_manual(values = fig.5col) +
+  # geom_violin() +
+  # geom_jitter(data = joint_weib %>% 
+  #               group_by(model) %>% 
+  #               sample_n(200),
+  #             position = position_jitter(0.1)) +
+  #geom_hline(aes(yintercept = 1), lty = "dashed") +
+  labs(y = "Est. Mean", x = "Model") +
+  theme_bw() +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        legend.position = "none") +
+  NULL -> weib_mean
+
+joint_weib %>%
+  group_by(model) %>%
+  ggplot(., aes(x = model, y = varweib)) +
+    geom_violin(color = violincolor, fill = violincolor) +
+  geom_boxplot(width = 0.1, aes(color = model)) +
+  scale_color_manual(values = fig.5col) +
+  # geom_violin() +
+  # geom_jitter(data = joint_weib %>% 
+  #               group_by(model) %>% 
+  #               sample_n(200),
+  #             position = position_jitter(0.1)) +
+  labs(y = "Est. Variance", x = "Model") +
+  theme_bw() +
+  theme(legend.position = "none") +
+  NULL-> weib_variance
+
+MeanVar_figure <- plot_grid(weib_mean, weib_variance, nrow = 2, align = "v")
+#MeanVar_figure
+```
+
+```{r Figure5, fig.width=12, fig.height=7}
+
+plot_grid(kernelcurvesfig, kernel_tails_fig, CIparams_figure, MeanVar_figure, ncol = 4, rel_widths = c(0.9, 1, 0.3, 0.6),
+          labels = c("A)", "B)", "C)", "D)"), hjust = -0.5, vjust = 1, label_size = 10)
+
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure5.png")
+
 ```
@@
 
-Dispersal Kernels
-
-```{r}
-
-ggplot() +
-  stat_function(fun = dweibull, args = list(shape = CIshape$mean[1], scale = CIscale$mean[1]), color = fig.5col[1], size = 1) +
-  stat_function(fun = dweibull, args = list(shape = CIshape$mean[2], scale = CIscale$mean[2]), color = fig.5col[2], size = 1) +
-  stat_function(fun = dweibull, args = list(shape = CIshape$mean[3], scale = CIscale$mean[3]), color = fig.5col[3], size = 1) +
-  cp_lines +
-  pp_lines +
-  np_lines +
-  lims(x = c(0, 1250)) +
-  theme_bw()
-
-```
-
-```{r}
+```{r CIkernels, eval = FALSE}
 cp_lines <- purrr::map(seq(1:100), function(y)

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 6 ready

@@
 
+disp_table %>% 
+  dplyr::select(., Model, Mean.dispersal_sd, kurtosis, Max_dispersal, LDD_500) -> disp_table
+
 knitr::kable(disp_table)
@@
 nsamps <- 10000
-itera <- 1000
 
@@
 
-```{r fig.width=12, fig.height=3}
+```{r fig.width=12, fig.height=4}
 # Threshold figures
@@
     # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
-    # theme(axis.title.x = element_blank(),
-    #       axis.ticks.x = element_blank(),
-    #       axis.text.x = element_blank()) +
+    theme(axis.title.x = element_blank(),
+          #axis.ticks.x = element_blank(),
+          axis.text.x = element_blank()) +
     # coord_cartesian(xlim = c(200, 550)) +
@@
 
-  plot_grid(thresh_scale, thresh_shape, nrow = 2)
+  plot_grid(thresh_scale, thresh_shape, nrow = 2, align = "v")
 
@@
 
-plot_grid(plot.cp, plot.pp, plot.np, ncol = 3)
-ggsave2(filename = "Ch1_movement_rates/Figures/Figure6.png")
+plot_grid(plot.cp, plot.pp, plot.np, ncol = 3, labels = c("A)", "B)", "C)"), hjust = 0, vjust = 1, label_size = 10)
+#ggsave2(filename = "Ch1_movement_rates/Figures/Figure6.png")
 

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
I think results might be ready

@@
 
-evd.fit.cp <-fevd(cp.evd$disp, threshold = tval.cp, type = "GP")
-evd.fit.pp <- fevd(pp.evd$disp, threshold = tval.cp, type = "GP")
-evd.fit.np <- fevd(np.evd$disp, threshold = tval.cp, type = "GP")
-
+evd.fit.cp <- fevd(cp.evd$disp, threshold = tval.cp, type = "GP")
+evd.fit.pp <- fevd(pp.evd$disp, threshold = tval.pp, type = "GP")
+evd.fit.np <- fevd(np.evd$disp, threshold = tval.np, type = "GP")
+
+cbind(c("CP", "PP", "NP"), rbind(evd.fit.cp$results$par,
+      evd.fit.pp$results$par,
+      evd.fit.np$results$par))
+
+```
+
+Find the conditional probabilities. Probability of exceeding a distance x, based on the fitted distribution
+
+```{r}
+
+# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
+dist_range <- c(200, 500, 1000, 5000)
+
+cbind(c("Distance", "CP", "PP", "NP"), rbind(dist_range,
+                                             pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE),
+                                             pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE),
+                                             pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)))
+
+```
+
+Summary for the fits
+
+```{r}
 summary(evd.fit.cp)
+plot(evd.fit.cp)
 summary(evd.fit.pp)
+plot(evd.fit.pp)
 summary(evd.fit.np)
-
-```
-
-Find the conditional probabilities. Probability of exceeding a distance x, based on the fitted distribution
-
-```{r}
-
-# To find the probability of exceeding 1000, 5000, or 10,000 meters based on the fitted ged 
-dist_range <- c(200, 500, 1000, 5000, 10000)
-
-pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE)
-pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE)
-pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)
-
-# Not sure this is right though. I want the conditional probability that a dispersal distance that is already over the threshold goes beyong 1000, 5000, and 10000 meters.
-
-```
+plot(evd.fit.np)
+
+```

### 2021-11-30 Ch1_movement_rates/Ch1_Figures.Rmd
Updated figure 5 to include half of the curves.
Added lines to guide the tails in Figure 5. Also using the 1000 estimates now.

@@
 xmax <- 1500
-ncurves <- 200
+ncurves <- 1000
 
@@
   theme_bw() +
-  labs(y = "Density", x = "Dispersal (m)") +
-  theme(axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        panel.grid.major = element_blank()) +
+  labs(y = "Density", x = "") +
+  theme(panel.grid.major = element_blank()) +
   coord_cartesian(xlim = c(0, coords[1]), ylim = c(0, coords[2])) +
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        panel.grid = element_line(color = "white")) +
+        panel.grid = element_line(color = "grey")) +
+  geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
   labs(y = "") -> cp.tail
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        panel.grid = element_line(color = "white")) +
+        panel.grid = element_line(color = "grey")) +
+    geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
   labs(y = "") -> pp.tail
@@
   theme(panel.background = element_rect(fill = backgroundcol),
-        panel.grid = element_line(color = "white")) +
+        panel.grid = element_line(color = "grey")) +
+    geom_vline(xintercept = 900, linetype = "dashed", color = "black") +
+  geom_hline(yintercept = 0.00005, linetype = "dashed", color = "black") +
   labs(y = "") -> np.tail

### 2021-11-30 Ch1_movement_rates/Ch1_Figures.Rmd
Organized a little and added captions.

@@
 
-```{r}
+```{r Figure1}
 # Figure 1 - example of how the process works.
@@
 
-plot_grid(A, B, C, D, labels = "AUTO")
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
+plot_grid(A, B, C, D, labels = c("A)", "B)", "C)", "D)"), hjust = 0, vjust = 1, label_size = 10)
+
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure1.png")
 ```
@@
 
-```{r}
+**Table1** - Movement rates for the twelve tagged individuals from data collected by Holbrook (2011).
+Movement rate for individuals is calculated as the distance moved in meters per minute for every movement bout, averaged across all observations during the tracking period.
+In the case of social groups, the movement rate is calculated as the average for all movement bouts across all individuals belonging to that social group.
+Movement rate units are in meters displaced per minute.
+
+```{r Table1}
 ptpl %>% 
@@
   dplyr::select(Bird_ID, obs, movrate, fam_g, famrate) -> table1
-
-knitr::kable(table1)
+table1
+#knitr::kable(table1)
 # write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")
@@
 
-movratedf <- data.frame(scenario = "cp", group = NA, movrate = movrate_cp) %>% 
-  bind_rows(., data.frame(scenario = rep("pp", 42), group = movrate_pp$fam_g, movrate = movrate_pp$movrate)) %>% 
-  bind_rows(., data.frame(scenario = rep("np", 30), group = NA, movrate = movrate_np))
+movratedf <- data.frame(scenario = "CP", group = NA, movrate = movrate_cp) %>% 
+  bind_rows(., data.frame(scenario = rep("PP", 42), group = movrate_pp$fam_g, movrate = movrate_pp$movrate)) %>% 
+  bind_rows(., data.frame(scenario = rep("NP", 30), group = NA, movrate = movrate_np))
 
@@
 movratedf %>% 
-  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
+  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("PP", "NP", "CP")), color = as.character(group))) +
   geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
@@
 ```{r fig.height=7, fig.width=5}
-plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1), labels = "AUTO")
-
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
-
-```
-
-# Figure 3 - gut retention times:
+plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1), labels = c("A)", "B)", "C)"), hjust = 0, vjust = 1, label_size = 10)
+
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure2.png")
+
+```
+**Figure 2** - Fitted distributions to movement rate data from estimated from radiotracking.
+A) lognormal distribution fitted to the twelve data points of movement rate.
+B) Lognormal distributions used to describe movement rates for each social group.
+We used the movement rate of each family group, shown by the colored dots across the x axis, as the meanlog parameter in each lognormal distribution.
+Due to data constraints, we used the estimated sdlog parameter from panel A to generate movement rate curves from panel B.
+C) movement rates used for each of the pooling scenarios.
+In the case of complete pooling (cp), estimated parameters from the lognormal distribution in panel A were used to calculate the expected value and this was used as the movement rate for cp.
+In the case of no pooling (np) we randomly sampled 30 movement rates from the distribution fitted in panel A.
+In the case of partial pooling (pp), we randomly sampled 6 movement rates from each social group’s curve and used these for the partial pooling simulations.
+
+# Figure 3
 
@@
 
-```{r}
+```{r Figure3, fig.width=3, fig.height=3}
 
@@
   ggplot() +
-  geom_histogram(aes(x = grt, y = ..density..), fill = my.cols1[7], bins = 20) +
+  #geom_histogram(aes(x = grt, y = ..density..), fill = my.cols1[7], bins = 20) +
   stat_function(fun = dgamma, args = list(shape = grt_fit$estimate[1], rate = grt_fit$estimate[2])) +
@@
 
-# ggsave2(filename = "Ch1_movement_rates/Figures/Figure3.png")
-
-```
+ggsave2(filename = "Ch1_movement_rates/Figures/Figure3.png")
+
+```
+**Figure 3** - Description of gut retention times using field data for four individuals, shown by each dot along the x axis.
+The density curve fitted corresponds to a gamma distribution with parameters shape = 2.0562 and scale = 13.
+8688.
+This gamma distribution is later used to sample gut retention times for simulations.
 
@@
 # Figure 4 - average dispersal and dispersion per run
-
-Build a table with quantiles or summary stats for the dispersal and dispersion per run.
-Dispersion tells us how spread appart the seeds are from each other during a simulation.
-I would expect that for individuals with higher movement rates dispersion might be higher for their simulation runs too.
-This because a higher movement rate would extend the tail of the exponential distribution for movement distances, and thus have a larger range for movement distances, with a higher probability larger movement distances.
-So, during a simulation, a bird would see itself taking larger steps if they have a larger movement rate.
-Thus, their seeds would potentially be distributed more far apart.
-
-```{r}
-
-disp_df %>% 
-  group_by(model) %>% 
-  summarise(av.disp = c(mean(av.disp), sd(av.disp), n(), round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1)),
-            dsprsn = c(mean(dsprsn), sd(dsprsn), n(), round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1)),
-            q = c("mean", "sd", "n", "min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
-  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
-  pivot_wider(., names_from = q, values_from = value) %>% 
-  arrange(., property) -> qtable_models
-
-qtable_models
-```
-
-### Idea for dispersal and dispersion
 
@@
 
-Figure 5 - Dispersal kernels
+**Figure 4** - Average dispersal and dispersion for 100,000 simulation runs per pooling scenario.
+A) Dispersal per run is calculated as the distance from the origin to the average location of the 5 seeds in that run.
+The average seed location is then used to calculate dispersion as the distance of each seed to the average seed location in that run.
+Overall distribution of average dispersal is similar across scenarios, with differences in the density and location of outliers, with the furthest average dispersal at 1222m in the NP scenario.
+B) Seed dispersion per run in the three pooling scenarios.
+Higher values of dispersion represent more even distribution of seeds per simulation run.
+The overall distribution of dispersion data points is comparable across scenarios.
+When we focus on outliers, we observe a higher density of points past 400m of dispersion in the NP scenario, however the most extreme outliers belong to the PP, and CP scenarios.
+C) Average seed locations per simulation run.
+This two-dimensional representation of average seed locations shows a higher density close to the origin.
+Average seed locations over 500m from the origin are outlined in green, clearly showing a higher number of average locations outside this range for the NP scenario.
+
+```{r}
+
+disp_df %>% 
+  group_by(model) %>% 
+  summarise(av.disp = c(mean(av.disp), sd(av.disp), n(), round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1)),
+            dsprsn = c(mean(dsprsn), sd(dsprsn), n(), round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1)),
+            q = c("mean", "sd", "n", "min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
+  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
+  pivot_wider(., names_from = q, values_from = value) %>% 
+  arrange(., property) -> qtable_models
+
+qtable_models
+```
+
+# Figure 5 - Dispersal kernels
 
@@
 
-```{r eval = FALSE}
-cp.dens +
-  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> cp.tail
-
-pp.dens +
-  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> pp.tail
-
-np.dens +
-  coord_cartesian(xlim = c(400, 800), ylim = c(0, 0.001)) -> np.tail
-
-plot_grid(cp.tail, pp.tail, np.tail, nrow = 3)
-
-```
-
 ```{r KernelTails}
@@
 
+**Figure 5** - Estimated seed dispersal kernels and distribution of parameter values for the three pooling scenarios.
+A) Seed dispersal kernel curves for 1000 random samples of 100 seeds for each of the pooling scenarios based on fitting a Weibull probability density function to the data.
+B) Focus on the tails of the dispersal kernels, where the dashed lines are used for guiding purposes only.
+The NP scenario (blue) has a higher density of heavy tailed kernels, when compared to the other two scenarios.
+C) Each dispersal kernel is modeled using a Weibull distribution where estimated parameter values are obtained for each of the 1000 random samples.
+For the shape and scale parameters, we calculate the mean and their 95% confidence intervals generated from a non-parametric kernel density estimation to the 1000 parameter values obtained from the 1000 Weibull fits.
+D) Calculated expected value (mean) and variance for each of the kernel density curves using the scale and shape parameters obtained from the Weibull distribution fits.
+Overall distribution of variance for the three scenarios is similar, with the number and extent of outliers for the NP scenario being relatively higher.
+
 # Table 2 - results
-Data for each seed, not per run
+
+Summary table on seed dispersal distances for each of the pooling scenarios.
+For each of the scenarios, the metrics reported in this table are based on the 500,000 seeds deposited under each of the simulated scenarios.
 
@@
 
-### FIGURE 6 EVD generalized pareto results
-
-1. Make threshold plot to figure out threshold
-2. Make associated mean excess plot
-3. Calculate the 95% quantile for mean excess to use as threshold
-4. Make threshplot and show the threshold based on the mean excess
-5. fit a gpd distribution using that threshold and report parameter values
-6. Calculate conditional probabilities over certain distances
+# Appendix FIGURE 6 EVD generalized pareto results
 
@@
 ```{r fig.width=12, fig.height=4}
+
+# 1. Make threshold plot to figure out threshold
+# 2. Make associated mean excess plot
+# 3. Calculate the 95% quantile for mean excess to use as threshold
+# 4. Make threshplot and show the threshold based on the mean excess
+# 5. fit a gpd distribution using that threshold and report parameter values
+# 6. Calculate conditional probabilities over certain distances
+
 # Threshold figures
@@
 
-Find the conditional probabilities. Probability of exceeding a distance x, based on the fitted distribution
+## Find the conditional probabilities. Probability of exceeding a distance x, based on the fitted distribution
 
@@
 
-Summary for the fits
+## Summary for the fits
 

### 2021-11-30 Ch1_movement_rates/Ch1_Figures.Rmd
Fixed captions.

@@
 ```
+
 **Figure 2** - Fitted distributions to movement rate data from estimated from radiotracking.
@@
   scale_color_manual(values = c(my.cols1[4], my.cols1[2], my.cols1[3], my.cols1[1])) +
+  lims(x = c(-.01, 105)) +
   theme_bw() +
@@
 ```
+
 **Figure 3** - Description of gut retention times using field data for four individuals, shown by each dot along the x axis.
@@
 cbind(c("Distance", "CP", "PP", "NP"), rbind(dist_range,
-                                             pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE),
-                                             pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE),
-                                             pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)))
+                                             signif(pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE), 5),
+                                             signif(pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE), 5),
+                                             signif(pextRemes(evd.fit.np, dist_range, lower.tail = FALSE), 5)))
 

### 2021-12-13 Ch2_distributions/Ch2_data_analysis.R
Building ch2.

@@ -1,0 +1,116 @@
+# 20211207 Data analysis
+
+# Libraries -----------------------------------------------
+set.seed(20211207)
+
+library(aracari)
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(purrr)
+library(fitdistrplus)
+
+# Data ----------------------------------------------------
+# The script for this data is in the data-raw folder
+load("data/ptpl.rda")
+
+ptpl %>%
+  filter(., mpm != 0) -> ptpl
+
+
+dist.used <- c("gamma", "weibull", "lnorm")
+param <- c("shape", "rate", "shape", "scale", "meanlog", "sdlog")
+dist <- c("gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
+kpars <- c(2, 2, 2, 2, 2, 2)
+
+# Functions ----------------------------------------------------
+
+build_fits_df <- function(x){
+
+  nm <- deparse(substitute(x))
+
+  x %>%
+    map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
+    map(as_tibble) %>%
+    bind_rows()
+}
+
+# Figure 1 ---------------------------------------------
+# Distribution of velocities at the different pooling levels
+
+ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
+  #           color = "blue") +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+  theme_classic()
+
+# Complete pooling fits -------------------------------------
+pop <- lapply(dist.used, function(x){fitdist(ptpl$mpm, distr = x)})
+
+# Get data for qqplot at population level
+qqpop <- qqcomp(pop, plotstyle = "ggplot")$data
+names(qqpop) <- c("theoretical", "fdist", "empirical")
+
+# Save the population level parameters
+
+build_fits_df <- function(x){
+
+  nm <- deparse(substitute(x))
+
+  x %>%
+    map(., `[`, c("estimate", "sd", "loglik", "n")) %>%
+    map(as_tibble) %>%
+    bind_rows()
+}
+
[…]

### 2021-12-13 Ch2_distributions/Ch2_Figures.Rmd
Getting figures going

---
title: "Distributions"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE}
library(aracari)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)

```

```{r include=FALSE}
set.seed(20211207)

# Data ----------------------------------------------------
# The script for this data is in the data-raw folder
load("data/ptpl.rda")

ptpl %>%
  filter(., mpm != 0) -> ptpl
```

# Figure 1

```{r Figure1}
# Figure 1 ---------------------------------------------
# Distribution of velocities at the different pooling levels

ptpl %>%
  ggplot(., aes((x = mpm))) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
  #           color = "blue") +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  theme_classic()
```

# Figure X - angles

```{r}
p1_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

p2_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360),
         B_id = paste0("B", id)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~B_id) +
  theme(axis.text = element_blank()) +
  labs(title = "No pooling")

plot_grid(p1_angles, p2_angles)

```

### 2021-12-13 Ch2_distributions/Ch2_Figures.Rmd
small preview of figures

@@
 ```
+
+# Fits
+
+```{r}
+load("Ch2_distributions/fits_df.RData")
+```
+
+```{r}
+nboots <- 1000
+
+cp.fits %>%
+  dplyr::select(., bic, dist, dBIC, boot) %>%
+  group_by(boot) %>%
+  distinct() %>%
+  ungroup() %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  mutate(model = "CP") %>%
+  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+  geom_col()
+
+pp.fits %>%
+  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
+  group_by(fgroup, boot) %>%
+  distinct() %>%
+  group_by(fgroup) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
+  geom_col()
+
+np.fits %>%
+  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
+  group_by(individual, boot) %>%
+  distinct() %>%
+  group_by(individual) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
+  geom_col()
+
+```

### 2021-12-13 Ch2_distributions/Ch2_data_analysis.R
changing number of samples to make real bootstrap

@@ -40,7 +40,7 @@ build_fits_df <- function(x){
 ## CP bootstrapping -----------------------------------------
 
 nboots <- 1000
-nsamples <- 30
+nsamples <- length(ptpl$mpm)
 
 cp.fits <- NULL
 
@@ -81,13 +81,19 @@ ids <- unique(ptpl$id)
 
 np.fits <- NULL
 
+
 for(i in 1:nboots){
 
   boot.df <- ptpl %>%
     ungroup() %>%
     dplyr::select(.,id, mpm) %>%
-    group_by(., id) %>%
-    sample_n(., size = nsamples, replace = TRUE)
+    group_by(id) %>%
+    nest() %>%
+    ungroup() %>%
+    mutate(n = map_int(data, nrow)) %>%
+    mutate(samp = map2(data, n, sample_n, replace = TRUE)) %>%
+    dplyr::select(-data) %>%
+    unnest(samp)
 
   for(j in 1:length(ids)){
 
@@ -130,18 +136,19 @@ fgs <- unique(ptpl$fam_g)
 
 pp.fits <- NULL
 
+
 for(i in 1:nboots){
 
   boot.df <- ptpl %>%
     ungroup() %>%
     dplyr::select(.,fam_g, mpm) %>%
-    group_by(., fam_g) %>%
-    sample_n(., size = nsamples, replace = TRUE)
-
-  for(j in 1:length(fgs)){
-
-    fg.df <- boot.df %>%
-      filter(., fam_g == fgs[j])
+    group_by(fam_g) %>%
+    nest() %>%
+    ungroup() %>%
+    mutate(n = map_int(data, nrow)) %>%
+    mutate(samp = map2(data, n, sample_n, replace = TRUE)) %>%
+    dplyr::select(-data) %>%
+    unnest(samp)
 
     fit <- lapply(dist.used, function(x){fitdist(fg.df$mpm, distr = x)})
 
@@ -172,5 +179,5 @@ pp.fits %>%
   ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
   geom_col()
 
-save(cp.fits, pp.fits, np.fits, file = "Ch2_distributions/fits_df.RDS")
+save(cp.fits, pp.fits, np.fits, file = "Ch2_distributions/fits_df.RData")
 

### 2021-12-15 Ch2_distributions/Ch2_Figures.Rmd
Updated figures

--- 2021-12-13 Ch2_distributions/Ch2_Figures.Rmd
@@
 
-```{r Figure1}
+```{r Figure1, fig.height=6, fig.width=4}
 # Figure 1 ---------------------------------------------
 # Distribution of velocities at the different pooling levels
+
+ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  #geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
+  #           color = "blue") +
+  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+  theme_classic() -> cp_lines
 
@@
   #           color = "blue") +
-  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  #geom_line(stat = "density", color = "#1191d1", lwd = 1) +
   geom_vline(xintercept = 0, color = "grey") +
@@
   labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic()
+  theme_classic() -> pp_lines
+
+ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  #geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
+  #geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+  theme_classic() -> np_lines
+
+plot_grid(cp_lines, pp_lines, np_lines, nrow = 3)
 ```
@@
 
-```{r}
+```{r fig.width=8, fig.height=6}
 p1_angles <- ptpl %>% 
@@
   mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
+                          rel.angle * 180/pi + 360)) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  facet_wrap(~fam_g, nrow = 2) +
+  theme(axis.text = element_blank()) +
+  labs(title = "Partial pooling")
+
+p3_angles <- ptpl %>% 
+  drop_na(rel.angle) %>% 
+  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                           rel.angle * 180/pi + 360),
@@
         legend.position = "none") +
-  facet_wrap(~B_id) +
+  facet_wrap(~B_id, nrow = 2) +
   theme(axis.text = element_blank()) +
@@
 
-plot_grid(p1_angles, p2_angles)
+plot_grid(plot_grid(p1_angles, p2_angles), p3_angles, nrow = 2)
 
 ```
+
+# Fits
+
+```{r}
+load("Ch2_distributions/Ch2_fits.RData")
+```
+
+```{r}
+reg_fits_info %>% 
+  dplyr::select(., dist, dBIC, ID, model) %>% 
+  distinct() %>% 
+  filter(., dBIC == 0) -> bestmodel
+
+#bestmodel
+```
+
+```{r fig.width=12}
+
+cp.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, boot) %>%
+  group_by(boot) %>%
+  distinct() %>%
+  ungroup() %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  mutate(model = "CP") %>%
+  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme(legend.position = "none") +
+  geom_label(data = bestmodel %>% filter(., model == "CP"),
+             aes(x = model, y = -0.05, label = dist)) -> cp.fit
+
+pp.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
+  group_by(fgroup, boot) %>%
+  distinct() %>%
+  group_by(fgroup) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme(legend.position = "none") +
+  geom_label(data = bestmodel %>% filter(., model == "PP"),
+             aes(x = ID, y = -0.05, label = dist))-> pp.fit
+
+np.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
+  group_by(individual, boot) %>%
+  distinct() %>%
+  group_by(individual) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  geom_label(data = bestmodel %>% filter(., model == "NP"),
+             aes(x = ID, y = -0.05, label = dist)) -> np.fit
+
+legend <- get_legend(np.fit + theme(legend.position = "bottom"))
+
+plot_grid(cp.fit, pp.fit, 
+          np.fit + theme(legend.position = "none"), 
+          ncol = 3, rel_widths = c(0.4,1,1.4)) -> col_grid
+
+plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))
+
+```
+
+```{r}
+# Difference to the second best model
+
+reg_fits_info %>% 
+  dplyr::select(., dist, dBIC, ID, model) %>% 
+  distinct() %>% 
+  ggplot(., aes(x = ID, y = dBIC, color = dist)) +
+  #facet_wrap(~model) +
+  geom_point()
+
+```
+
+Calculate the BIC for the models:
+
+```{r}
+reg_fits_info %>% 
+  dplyr::select(model, ID, dist, loglik, n, kpars) %>% 
+  distinct() %>% 
+  group_by(model, dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  mutate(deltaBIC_withinmodels = signif(BIC - min(BIC), 3)) %>% 
+  ungroup() %>% 
+  mutate(deltaBIC_acrossmodels = signif(BIC - min(BIC), 3)) %>% 
+  ggplot(., aes(x = model, y = BIC, color = dist)) +
+  geom_point()
+```

### 2021-12-15 Ch2_distributions/Ch2_distribution_fits.R
saving different objects

@@ -214,4 +214,6 @@ for(i in 1:nboots){
 
 
 save.image(file = "Ch2_distributions/fits_df.RData")
-
+save(nboots, dist, dist.used, ids, fgs, kpars, param, reg_fits_info,
+     cp.boot.fits, pp.boot.fits, np.boot.fits,
+     file = "Ch2_distributions/Ch2_fits.RData")

### 2021-12-15 Ch2_distributions/Ch2_Figures.Rmd
Updates to figures.

@@
 library(fitdistrplus)
+library(stringr)
+library(gt)
 
@@
 
-```{r Figure1, fig.height=6, fig.width=4}
+```{r include=FALSE}
+# Color palette ----------------------------------------
+my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012",
+              "#0d907a","#b9bec3","#31aec5", "#653625", "#2C5C5D",
+              "#DEB41E", "#2D3335", "#E2BF80", "#87A986", "#59879A",
+              "#9C1D29", "#24716B", "#4a92b0")
+scales::show_col(my.cols1)
+
+my.cols2 <- c("#23262f", "#0d907a", "#DEB41E", 
+              "#9C1D29", "#c76620", "#4a92b0",
+              "#669e46", "grey")
+scales::show_col(my.cols2)
+
+```
+
+```{r}
+
+ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
+  #           color = "blue") +
+  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+  theme_classic() +
+  scale_color_manual(values = my.cols2) +
+  theme(legend.position = "none")
+```
+
+```{r eval=FALSE, Figure1, fig.height=6, fig.width=4}
 # Figure 1 ---------------------------------------------
 # Distribution of velocities at the different pooling levels
+
+cols.fig1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
 
@@
   #           color = "blue") +
-  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
+  geom_line(stat = "density", color = "black") +
   geom_vline(xintercept = 0, color = "grey") +
@@
   labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() -> cp_lines
+  theme_classic() +
+  lims(y = c(0, 0.05)) -> cp_lines
 
@@
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
+  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density") +
   # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
@@
   labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() -> pp_lines
+  theme_classic() +
+  scale_color_manual(values = cols.fig1) +
+  theme(legend.position = "none") +
+  lims(y = c(0, 0.05)) -> np_lines
 
@@
   #geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
-  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
+  geom_line(aes(x = mpm, group = fam_g, color = fam_g),
+            stat = "density") +
   #geom_line(stat = "density", color = "#1191d1", lwd = 1) +
@@
   labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() -> np_lines
+  theme_classic() +
+  scale_color_manual(values = cols.fig1) +
+  theme(legend.position = "none") +
+  lims(y = c(0, 0.05)) -> pp_lines
 
 plot_grid(cp_lines, pp_lines, np_lines, nrow = 3)
+
+```
+
+# Fits
+
+```{r}
+load("Ch2_distributions/Ch2_fits.RData")
+```
+
+```{r}
+reg_fits_info %>% 
+  dplyr::select(., dist, dBIC, ID, model) %>% 
+  distinct() %>% 
+  filter(., dBIC == 0) -> bestmodel
+
+#bestmodel
+```
+
+# Figure 2 - 
+HERE - get rid of the first panel. Make figure later with percent support at the pooling levels so Fig 2 only shows the importance of variaiton since different models fit different bootsptraps.
+
+```{r fig.width=12}
+
+cols.fig2 <- c("#b9bec3", 
+               "#0d907a", "#DEB41E", "#9C1D29", "#23262f")
+
+cp.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, boot) %>%
+  group_by(boot) %>%
+  distinct() %>%
+  ungroup() %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  mutate(model = "CP") %>%
+  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  labs(y = "Percent Support") +
+  theme_classic() +
+  theme(legend.position = "none",
+        axis.title.x = element_blank()) +
+  geom_label(data = bestmodel %>% filter(., model == "CP"),
+             aes(x = model, y = -0.05, label = dist)) +
+  scale_fill_manual(values = cols.fig2) -> cp.fit
+
+pp.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
+  group_by(fgroup, boot) %>%
+  distinct() %>%
+  group_by(fgroup) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme_classic() +
+  theme(legend.position = "none",
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank()) +
+  geom_label(data = bestmodel %>% filter(., model == "PP"),
+             aes(x = ID, y = -0.05, label = dist)) +
+  scale_fill_manual(values = cols.fig2) -> pp.fit
+
+np.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
+  group_by(individual, boot) %>%
+  distinct() %>%
+  group_by(individual) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank()) +
+  geom_label(data = bestmodel %>% filter(., model == "NP"),
+             aes(x = ID, y = -0.05, label = dist)) +
+  scale_fill_manual(values = cols.fig2)  -> np.fit
+
+legend <- get_legend(np.fit + theme(legend.position = "bottom") +
+                       guides(fill=guide_legend(title="Distribution")))
+
+plot_grid(cp.fit, pp.fit, 
+          np.fit + theme(legend.position = "none"), 
+          ncol = 3, rel_widths = c(0.8,1,1.4)) -> col_grid
+
+plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))
+
+```
+
+```{r eval=FALSE}
+# Difference to the second best model
+
+reg_fits_info %>% 
+  dplyr::select(., dist, dBIC, ID, model) %>% 
+  distinct() %>% 
+  ggplot(., aes(x = ID, y = dBIC, color = dist)) +
+  #facet_wrap(~model) +
+  geom_point()
+
+```
+
+Calculate the BIC for the models:
+
+```{r}
+reg_fits_info %>% 
+  dplyr::select(model, ID, dist, loglik, n, kpars) %>% 
+  distinct() %>% 
+  group_by(model, dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) -> A
+
+reg_fits_info %>% 
+  filter(., model != "CP") %>% 
+  dplyr::select(model, ID, dist, loglik, n, kpars, dBIC) %>% 
+  distinct() %>% 
+  filter(., dBIC == 0) %>% 
+  group_by(model) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  transmute(model = model,
+            dist = "Multi",
+            BIC = BIC) -> B
+
+rbind.data.frame(A, B) -> C
+
+C %>%
+  group_by(model) %>% 
+  mutate(deltaBIC_withinmodels = signif(BIC - min(BIC), 3)) %>% 
+  ungroup() %>% 
+  mutate(deltaBIC_acrossmodels = signif(BIC - min(BIC), 3)) %>% 
+  arrange(model) -> BIC_table
+```
+
+```{r}
+cp.boot.fits %>% 
+  dplyr::select(dist, bic, boot) %>% 
+  distinct() %>% 
+  transmute(dist = dist,
+            BIC = bic,
+            boot = boot,
+            model = "CP") %>% 
+  group_by(boot) %>% 
+  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
+  ungroup() -> cp.bic
+
+pp.boot.fits %>% 
+  dplyr::select(loglik, n, kpars, dist, fgroup, boot) %>% 
+  distinct() %>% 
+  group_by(boot, dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  transmute(dist = dist,
+            BIC = BIC,
+            boot = boot,
+            model = "PP") %>% 
+  bind_rows(., pp.boot.fits %>% 
+  dplyr::select(loglik, n, kpars, dist, fgroup, boot, dBIC) %>% 
+  distinct() %>% 
+  filter(., dBIC == 0) %>% 
+  group_by(boot) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  transmute(dist = "multi",
+            BIC = BIC,
+            boot = boot, 
+            model = "PP")) %>% 
+  group_by(boot) %>% 
+  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
+  ungroup() %>% 
+  arrange(boot) -> pp.bic
+
+np.boot.fits %>% 
+  dplyr::select(loglik, n, kpars, dist, individual, boot) %>% 
+  distinct() %>% 
+  group_by(boot, dist) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  transmute(dist = dist,
+            BIC = BIC,
+            boot = boot,
+            model = "NP") %>%   
+  bind_rows(., np.boot.fits %>% 
+  dplyr::select(loglik, n, kpars, dist, individual, boot, dBIC) %>% 
+  distinct() %>% 
+  filter(., dBIC == 0) %>% 
+  group_by(boot) %>% 
+  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
+  transmute(dist = "multi",
+            BIC = BIC,
+            boot = boot, 
+            model = "NP")) %>% 
+  group_by(boot) %>% 
+  mutate(., deltaBIC = signif(BIC - min(BIC), 3)) %>% 
+  ungroup() %>% 
+  arrange(boot) -> np.bic
+
+```
+# Figure 3
+
+These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
+
+```{r}
+cp.bic %>% 
+  bind_rows(pp.bic) %>% 
+  bind_rows(np.bic) %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
+  ggplot(., aes(x = model, color = dist, y = BIC)) +
+  geom_boxplot() +
+  scale_color_manual(values = cols.fig2) +
+  labs(x = "Pooling Model", y = "Raw BIC values") +
+  theme_classic()
+```
+
+```{r}
+cp.bic %>% 
+  bind_rows(pp.bic) %>% 
+  bind_rows(np.bic) %>% 
+  filter(., deltaBIC == 0) %>% 
+  group_by(model) %>% 
+  count(dist) %>% 
+  mutate(prcnt_support = n/nboots) %>%
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
+  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+  scale_fill_manual(values = cols.fig2) +
+  geom_col() +
+  theme_classic() +
+  labs(x = "Pooling Level", y = "Percent Support")
+```
+
+# Table 1 -
+
+For no bootstraps, just what are the BIC values we select.
+
+```{r}
+
+BIC_table %>% 
+  mutate(dist = ifelse(dist == "lnorm", "lognormal", dist),
+         dist = str_to_title(dist)) %>% 
+  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
+  arrange(., model) -> BIC_table
+# BIC_table
+
+```
+
+```{r}
+
+#library(gt)
+
+gt_tbl <- gt(BIC_table[, 2:5], rowname_col = "dist")
+
+gt_tbl %>% 
+  tab_header(
+    title = md("**Model comparisons across levels**")
+  ) %>% 
+  tab_stubhead(label = "Model") %>% 
+  tab_row_group(
+    group = "NP",
+    rows = 8:11
+  ) %>% 
+  tab_row_group(
+    group = "PP",
+    rows = 4:7
+  ) %>% 
+  tab_row_group(
+    group = "CP", 
+    rows = 1:3
+  ) %>% 
+  tab_spanner(
+    label = md("**BIC**"),
+    columns = vars(BIC, deltaBIC_withinmodels, deltaBIC_acrossmodels)
+  ) %>% 
+  cols_label(
+    deltaBIC_withinmodels = html("&Delta; BIC<sub>within</sub>"),
+    deltaBIC_acrossmodels = html("&Delta; BIC<sub>across</sub>"),
+  )
+
+# -> gt_table_bic
+#   
+# gtsave(gt_table_bic, "Ch2_distributions/aic_bic_table.png") 
+```
+
+```{r eval = FALSE}
+knitr::include_graphics("Ch2_distributions/aic_bic_table.png")
+```
+
+# Figure 4
+
+Fix this.
+The idea is that each bootstrap is represented here with their BIC value for each model.
+We see that there's very strong evidence for the multi distribution model at both PP and NP levels.
+The summary quantiles later show extre support for this.
+
+```{r}
+plot_grid(cp.bic %>% 
+  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
+  geom_point(),
+  pp.bic %>% 
+  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
+  geom_point(),
+  np.bic %>% 
+  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
+  geom_point(), nrow = 3)
+
+```
+
+On average, how many units away is the second model from the best one?
+
+**CP**
+
+```{r}
+cp.bic %>% 
+  filter(., deltaBIC != 0) %>% 
+  group_by(boot) %>% 
+  summarise(min = min(deltaBIC)) %>% 
+  summary()
+```
+
+**PP** 
+```{r}
+pp.bic %>% 
+  filter(., deltaBIC != 0) %>% 
+  group_by(boot) %>% 
+  summarise(min = min(deltaBIC)) %>% 
+  summary()
+```
+
+**NP**
+```{r}
+np.bic %>% 
+  filter(., deltaBIC != 0) %>% 
+  group_by(boot) %>% 
+  summarise(min = min(deltaBIC)) %>% 
+  summary()
 ```
@@
 ```
-
-# Fits
-
-```{r}
-load("Ch2_distributions/Ch2_fits.RData")
-```
-
-```{r}
-reg_fits_info %>% 
-  dplyr::select(., dist, dBIC, ID, model) %>% 
-  distinct() %>% 
-  filter(., dBIC == 0) -> bestmodel
-
-#bestmodel
-```
-
-```{r fig.width=12}
-
-cp.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, boot) %>%
-  group_by(boot) %>%
-  distinct() %>%
-  ungroup() %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  mutate(model = "CP") %>%
-  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  theme(legend.position = "none") +
-  geom_label(data = bestmodel %>% filter(., model == "CP"),
-             aes(x = model, y = -0.05, label = dist)) -> cp.fit
-
-pp.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
-  group_by(fgroup, boot) %>%
-  distinct() %>%
-  group_by(fgroup) %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  theme(legend.position = "none") +
-  geom_label(data = bestmodel %>% filter(., model == "PP"),
-             aes(x = ID, y = -0.05, label = dist))-> pp.fit
-
-np.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
-  group_by(individual, boot) %>%
-  distinct() %>%
-  group_by(individual) %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  geom_label(data = bestmodel %>% filter(., model == "NP"),
-             aes(x = ID, y = -0.05, label = dist)) -> np.fit
-
-legend <- get_legend(np.fit + theme(legend.position = "bottom"))
-
-plot_grid(cp.fit, pp.fit, 
-          np.fit + theme(legend.position = "none"), 
-          ncol = 3, rel_widths = c(0.4,1,1.4)) -> col_grid
-
-plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))
-
-```
-
-```{r}
-# Difference to the second best model
-
-reg_fits_info %>% 
-  dplyr::select(., dist, dBIC, ID, model) %>% 
-  distinct() %>% 
-  ggplot(., aes(x = ID, y = dBIC, color = dist)) +
-  #facet_wrap(~model) +
-  geom_point()
-
-```
-
-Calculate the BIC for the models:
-
-```{r}
-reg_fits_info %>% 
-  dplyr::select(model, ID, dist, loglik, n, kpars) %>% 
-  distinct() %>% 
-  group_by(model, dist) %>% 
-  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
-  mutate(deltaBIC_withinmodels = signif(BIC - min(BIC), 3)) %>% 
-  ungroup() %>% 
-  mutate(deltaBIC_acrossmodels = signif(BIC - min(BIC), 3)) %>% 
-  ggplot(., aes(x = model, y = BIC, color = dist)) +
-  geom_point()
-```

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Progress with figures.

@@
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = id), color = "grey", 
+            stat = "density", alpha = 0.8) +
   # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
@@
 #bestmodel
-```
-
-# Figure 2 - 
-HERE - get rid of the first panel. Make figure later with percent support at the pooling levels so Fig 2 only shows the importance of variaiton since different models fit different bootsptraps.
-
-```{r fig.width=12}
-
-cols.fig2 <- c("#b9bec3", 
-               "#0d907a", "#DEB41E", "#9C1D29", "#23262f")
-
-cp.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, boot) %>%
-  group_by(boot) %>%
-  distinct() %>%
-  ungroup() %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  mutate(model = "CP") %>%
-  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  labs(y = "Percent Support") +
-  theme_classic() +
-  theme(legend.position = "none",
-        axis.title.x = element_blank()) +
-  geom_label(data = bestmodel %>% filter(., model == "CP"),
-             aes(x = model, y = -0.05, label = dist)) +
-  scale_fill_manual(values = cols.fig2) -> cp.fit
-
-pp.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
-  group_by(fgroup, boot) %>%
-  distinct() %>%
-  group_by(fgroup) %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  theme_classic() +
-  theme(legend.position = "none",
-        axis.title.y = element_blank(),
-        axis.title.x = element_blank()) +
-  geom_label(data = bestmodel %>% filter(., model == "PP"),
-             aes(x = ID, y = -0.05, label = dist)) +
-  scale_fill_manual(values = cols.fig2) -> pp.fit
-
-np.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
-  group_by(individual, boot) %>%
-  distinct() %>%
-  group_by(individual) %>%
-  filter(dBIC == 0) %>%
-  count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
-  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
-  geom_col() +
-  theme_classic() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank()) +
-  geom_label(data = bestmodel %>% filter(., model == "NP"),
-             aes(x = ID, y = -0.05, label = dist)) +
-  scale_fill_manual(values = cols.fig2)  -> np.fit
-
-legend <- get_legend(np.fit + theme(legend.position = "bottom") +
-                       guides(fill=guide_legend(title="Distribution")))
-
-plot_grid(cp.fit, pp.fit, 
-          np.fit + theme(legend.position = "none"), 
-          ncol = 3, rel_widths = c(0.8,1,1.4)) -> col_grid
-
-plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))
-
 ```
@@
 ```
-# Figure 3
-
-These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
-
-```{r}
-cp.bic %>% 
-  bind_rows(pp.bic) %>% 
-  bind_rows(np.bic) %>% 
-  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
-  ggplot(., aes(x = model, color = dist, y = BIC)) +
-  geom_boxplot() +
-  scale_color_manual(values = cols.fig2) +
-  labs(x = "Pooling Model", y = "Raw BIC values") +
-  theme_classic()
-```
-
-```{r}
-cp.bic %>% 
-  bind_rows(pp.bic) %>% 
-  bind_rows(np.bic) %>% 
-  filter(., deltaBIC == 0) %>% 
-  group_by(model) %>% 
-  count(dist) %>% 
-  mutate(prcnt_support = n/nboots) %>%
-  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
-  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
-  scale_fill_manual(values = cols.fig2) +
-  geom_col() +
-  theme_classic() +
-  labs(x = "Pooling Level", y = "Percent Support")
-```
-
 # Table 1 -
@@
 
+# Figure 2 -
+
+```{r fig.width=12, fig.height=6}
+
+cols.fig2 <- c("#b9bec3", 
+               "#0d907a", "#DEB41E", "#9C1D29", "#23262f")
+
+cp.bic %>% 
+  bind_rows(pp.bic) %>% 
+  bind_rows(np.bic) %>% 
+  filter(., deltaBIC == 0) %>% 
+  group_by(model) %>% 
+  count(dist) %>% 
+  mutate(prcnt_support = n/nboots) %>%
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
+  ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+  scale_fill_manual(values = cols.fig2) +
+  geom_col() +
+  theme_classic() +
+  scale_y_continuous(labels = scales::percent) +
+  labs(x = "Pooling Level", y = "Percent Support") +
+  theme(axis.title.x = element_blank()) +
+  geom_label(data = bestmodel %>%
+               filter(., model == "CP"),
+             aes(x = model, y = -0.05, label = dist)) -> pooling.support
+
+# cp.boot.fits %>%
+#   dplyr::select(., bic, dist, dBIC, boot) %>%
+#   group_by(boot) %>%
+#   distinct() %>%
+#   ungroup() %>%
+#   filter(dBIC == 0) %>%
+#   count(dist) %>%
+#   mutate(prcnt_support = n/nboots) %>%
+#   mutate(model = "CP") %>%
+#   ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
+#   geom_col() +
+#   labs(y = "Percent Support") +
+#   theme_classic() +
+#   theme(legend.position = "none",
+#         axis.title.x = element_blank()) +
+#   geom_label(data = bestmodel %>% filter(., model == "CP"),
+#              aes(x = model, y = -0.05, label = dist)) +
+#   scale_fill_manual(values = cols.fig2) -> cp.fit
+
+pp.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
+  group_by(fgroup, boot) %>%
+  distinct() %>%
+  group_by(fgroup) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme_classic() +
+  theme(legend.position = "none",
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank()) +
+  scale_y_continuous(labels = scales::percent) +
+  geom_label(data = bestmodel %>% filter(., model == "PP"),
+             aes(x = ID, y = -0.05, label = dist)) +
+  scale_fill_manual(values = cols.fig2) -> pp.support
+
+np.boot.fits %>%
+  dplyr::select(., bic, dist, dBIC, individual, boot) %>%
+  group_by(individual, boot) %>%
+  distinct() %>%
+  group_by(individual) %>%
+  filter(dBIC == 0) %>%
+  count(dist) %>%
+  mutate(prcnt_support = n/nboots) %>%
+  ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
+  geom_col() +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank()) +
+  scale_y_continuous(labels = scales::percent) +
+  geom_label(data = bestmodel %>% filter(., model == "NP"),
+             aes(x = ID, y = -0.05, label = dist)) +
+  scale_fill_manual(values = cols.fig2)  -> np.support
+
+# legend <- get_legend(np.fit + theme(legend.position = "bottom") +
+#                        guides(fill=guide_legend(title="Distribution")))
+model.legend <- get_legend(pooling.support + theme(legend.position = "bottom") +
+                             guides(fill=guide_legend(title = "Distribution model")))
+
+# plot_grid(cp.fit, pp.fit, 
+#           np.fit + theme(legend.position = "none"), 
+#           ncol = 3, rel_widths = c(0.8,1,1.4)) -> col_grid
+# 
+# plot_grid(col_grid, legend, nrow = 2, rel_heights = c(1, 0.1))
+
+# first_row <- plot_grid(NULL, 
+#                        pooling.support + theme(legend.position = "none"),
+#                        NULL, rel_widths = c(0.3, 1, 0.3))
+# 
+# second_row <- plot_grid(pp.support, 
+#                         np.support + theme(legend.position = "none"),
+#                         ncol = 2, rel_widths = c(1, 1.2))
+# plot_grid(pooling.support + theme(legend.position = "none"),
+#           second_row, model.legend, nrow = 3, rel_heights = c(1,1,0.2))
+
+bar_col <- plot_grid(pooling.support + theme(legend.position = "none"),
+                     pp.support, 
+                     np.support + theme(legend.position = "none"),
+                     ncol = 3, rel_widths = c(0.4, 1, 1.4))
+plot_grid(bar_col, model.legend, nrow = 2, rel_heights = c(1, 0.1))
+
+```
+
+# Figure 3
+
+These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
+
+```{r}
+cp.bic %>% 
+  bind_rows(pp.bic) %>% 
+  bind_rows(np.bic) %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
+  ggplot(., aes(x = model, color = dist, y = BIC)) +
+  geom_boxplot() +
+  scale_color_manual(values = cols.fig2) +
+  labs(x = "Pooling Model", y = "Raw BIC values") +
+  theme_classic() +
+  guides(color=guide_legend(title = "Distribution model")) +
+  theme(legend.position = "bottom")
+
+```
+
 # Figure 4
@@
 We see that there's very strong evidence for the multi distribution model at both PP and NP levels.
-The summary quantiles later show extre support for this.
+The summary quantiles later show very high support for this.
+Difference here between incorporating variation at the expense of sample size, and getting high support, or staying with high sample size without variation.
 
-```{r}
-plot_grid(cp.bic %>% 
+```{r fig.height=6}
+
+cp.bic %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
   ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
-  geom_point(),
+  #geom_col() +
+  geom_point() +
+  scale_color_manual(values = cols.fig2) +
+  theme_classic() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  labs(y = "Bootstrap replicates", x = "") +
+  theme(legend.position = "none") -> Fig4a
+
 pp.bic %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
   ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
-  geom_point(),
+  #geom_col() +
+  geom_point() +
+  scale_color_manual(values = cols.fig2) +
+  theme_classic() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  labs(y = "Bootstrap replicates", x = "") +
+  theme(legend.position = "none") -> Fig4b
+
 np.bic %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
   ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
-  geom_point(), nrow = 3)
+  #geom_col() +
+  geom_point() +
+  scale_color_manual(values = cols.fig2) +
+  theme_classic() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  labs(y = "Bootstrap replicates", x = "BIC units from best model") -> Fig4c
+
+legend4 <- get_legend(Fig4c +
+                       guides(color=guide_legend(title = "Distribution \n model")))
+
+plot_grid(Fig4a, Fig4b, 
+          Fig4c + theme(legend.position = "none"), nrow = 3) -> fig4
+
+plot_grid(fig4, legend4, ncol = 2, rel_widths = c(1, 0.15))
 
@@
   summary()
+```
+
+What about the parameters of the best fit distributions? Meaning, that for each boostrap, keep only the best model. Plot those.
+
+**CP**
+
+```{r fig.height=6}
+cp.boot.fits %>% 
+  filter(., dBIC == 0) %>% 
+  ggplot(., aes(y = estimate)) +
+  facet_wrap(dist~param, ncol = 2, scales = "free") +
+  geom_boxplot()
+```
+
+**PP**
+
+```{r fig.height=6}
+pp.boot.fits %>% 
+  filter(., dBIC == 0) %>% 
+  ggplot(., aes(y = estimate, x = fgroup)) +
+  facet_wrap(dist~param, ncol = 2, scales = "free") +
+  geom_boxplot()
+```
+
+**NP**
+
+```{r fig.height=6}
+np.boot.fits %>% 
+  filter(., dBIC == 0) %>% 
+  ggplot(., aes(y = estimate, x = individual)) +
+  facet_wrap(dist~param, ncol = 2, scales = "free") +
+  geom_boxplot()
+```
+
+# Visualize them as density curves:
+
+```{r}
+
 ```

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Figure for curves is not working and I don't know that it is worth it

@@
 
+data <- cp.boot.fits
+
+  data %>% 
+    filter(dBIC == 0, dist == "gamma", param == "shape") -> gam.shape
+
+  data %>% 
+    filter(dBIC == 0, dist == "gamma", param == "shape") -> gam.scale
+
+  data %>% 
+    filter(dBIC == 0, dist == "lnorm", param == "meanlog") -> ln.mean
+
+    data %>% 
+    filter(dBIC == 0, dist == "lnorm", param == "sdlog") -> ln.sd
+
+  data %>% 
+    filter(dBIC == 0, dist == "weibull", param == "shape") -> wei.shape
+
+  data %>% 
+    filter(dBIC == 0, dist == "weibull", param == "scale") -> wei.scale
+
+  gamma.curves <- purrr::map(seq(1:nrow(gam.shape)), function(y)
+  stat_function(fun = dlnorm, args = list(shape = gam.shape$estimate[y],
+                                          scale = gam.scale$estimate[y]),
+                                          color = cols.fig2[1]))
+
+  lnorm.curves <- purrr::map(seq(1:nrow(ln.mean)), function(y)
+  stat_function(fun = dlnorm, args = list(meanlog = ln.mean$estimate[y],
+                                          sdlog = ln.sd$estimate[y]),
+                                          color = cols.fig2[2]))
+
+  weibull.curves <- purrr::map(seq(1:nrow(wei.scale)), function(y)
+  stat_function(fun = dlnorm, args = list(scale = wei.scale$estimate[y],
+                                          shape = wei.shape$estimate[y]),
+                                          color = cols.fig2[3]))
+
+  reg_fits_info %>% 
+  filter(., model == "CP", dBIC == 0) -> b
+
+  ggplot() +
+    gamma.curves +
+    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
+    #                                         sdlog = b$estimate[2])) +
+    lims(x = c(0, 200)) +
+    theme_classic() -> curves1
+
+    ggplot() +
+    lnorm.curves +
+    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
+    #                                         sdlog = b$estimate[2])) +
+    lims(x = c(0, 200)) +
+    theme_classic() -> curves2
+
+    ggplot() +
+    weibull.curves +
+    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
+    #                                         sdlog = b$estimate[2])) +
+    lims(x = c(0, 200)) +
+    theme_classic() -> curves3
+
+    plot_grid(curves1, curves2, curves3, nrow = 3)
+
 ```

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Progress.
almost done with figures for step length models.

--- 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
@@
 
-```{r fig.height=6}
+```{r fig.height=4}
 
@@
   #geom_col() +
-  geom_point() +
+  geom_point(alpha = 0.8, shape = 15) +
   scale_color_manual(values = cols.fig2) +
@@
         axis.ticks.y = element_blank()) +
-  labs(y = "Bootstrap replicates", x = "") +
+  labs(y = "Bootstrap \n replicates", x = "") +
   theme(legend.position = "none") -> Fig4a
@@
         axis.ticks.y = element_blank()) +
-  labs(y = "Bootstrap replicates", x = "") +
+  labs(y = "Bootstrap \n replicates", x = "") +
   theme(legend.position = "none") -> Fig4b
@@
         axis.ticks.y = element_blank()) +
-  labs(y = "Bootstrap replicates", x = "BIC units from best model") -> Fig4c
+  labs(y = "Bootstrap \n replicates", x = "BIC units from best model") -> Fig4c
 
@@
 
-# Visualize them as density curves:
-
-```{r}
-
-```
-
 # Figure X - angles

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Figure 1 with caption

@@
 
-# Figure 1
+# Figure 1 - Density plots for velocity
 
@@
 
-```{r}
+```{r Figure1, fig.width=6, fig.height=4}
 
@@
   theme(legend.position = "none")
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure1.png")
 ```
 
-```{r eval=FALSE, Figure1, fig.height=6, fig.width=4}
+Figure 1 - Probability density plots of velocity data for each individual (grey lines), and pooled across individuals (black line).
+Considerable variation from the population level density (black line) is observed for various individuals.
+Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.
+
+```{r eval=FALSE, fig.height=6, fig.width=4}
 # Figure 1 ---------------------------------------------

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Table 1  caption

@@
 
-Calculate the BIC for the models:
+```{r}
+# Calculate the BIC for the models:
 
-```{r}
 reg_fits_info %>% 
@@
 ```
-# Table 1 -
+# Table 1 - BIC values for models across pooling levels
 
-For no bootstraps, just what are the BIC values we select.
+Table 1 - BIC values obtained for models fitted to velocity data across pooling levels.
+Probability density functions considered included the Gamma, Weibull, and Lognormal distributions.
+Multi distribution models selected the best fitting distribution model for each family group or individual, allowing for variation not only in estimated parameters, but also in the distribution used.
+Based on BIC values, the best fitting model is the Multi-distribution with Partial Pooling, closely followed by the Complete Pooling Lognormal model.
 

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Labels for Figure 2.

@@
 
-# Fits
+<!-- # Fits  -->
 
@@
 
-```{r fig.width=12, fig.height=6}
+```{r Figure2, fig.width=12, fig.height=6}
 
@@
   mutate(prcnt_support = n/nboots) %>%
-  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi"))) %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
+         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
   ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
@@
                      np.support + theme(legend.position = "none"),
-                     ncol = 3, rel_widths = c(0.4, 1, 1.4))
+                     ncol = 3, rel_widths = c(0.4, 1, 1.4), 
+                     labels = c("A)", "B)", "C)"), label_size = 10)
 plot_grid(bar_col, model.legend, nrow = 2, rel_heights = c(1, 0.1))
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
 

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Figure 2 titles and captions

@@
 
-# Figure 2 -
+# Figure 2 - Percent Support
 
@@
 
-# Figure 3
+Figure 2 - Percent support for the different distribution models at the three pooling levels.
+Percent support is based on 1000 bootstrapped replicas for each scenario.
+Labels on the x axis show the best fitting model for the original datasets.
+A) percent support at the three pooling levels, with CP having over 50% support for the lognormal distribution, in agreement with the model fit to the complete dataset.
+PP and NP scenarios show 100% support for the multi-distribution model, which considers the best fitting model for each family group or individual, respectively.
+B) Percent support for each model in the family groups.
+C) Support for each model at the individual level.
 
-These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
+```{r eval=FALSE}
+# These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
 
-```{r}
 cp.bic %>% 
@@
 
-```{r fig.height=4}
+```{r eval=FALSE, fig.height=4}
 
@@
 
+```
+
+```{r fig.height=4}
+cp.bic %>% 
+  bind_rows(., pp.bic) %>% 
+  bind_rows(., np.bic) %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
+         model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
+  ggplot(., aes(x = deltaBIC, color = dist, y = boot)) +
+  facet_wrap(~model, nrow = 3) +
+  #geom_col() +
+  geom_point(alpha = 0.8, shape = 15) +
+  scale_color_manual(values = cols.fig2) +
+  theme_classic() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  labs(y = "Bootstrap replicates", x = "BIC units from best model") +
+  theme(legend.position = "right") +
+  guides(color=guide_legend(title = "Distribution \n model"))
 ```

### 2021-12-27 Ch2_distributions/Ch2_Figures.Rmd
Figure 4 almost

@@
 
-# Figure 2 - Percent Support
+# Figure 3 - Percent Support
 
-```{r Figure2, fig.width=12, fig.height=6}
+```{r Figure3, fig.width=12, fig.height=6}
 
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
+ggsave2(filename = "Ch2_distributions/Figures/Figure3.png")
 
@@
 
-Figure 2 - Percent support for the different distribution models at the three pooling levels.
+Figure 3 - Percent support for the different distribution models at the three pooling levels.
 Percent support is based on 1000 bootstrapped replicas for each scenario.
@@
 
-# Figure 4
+# Figure 4 - BIC units from best model
 
-Fix this.
+<!-- Fix this.
 The idea is that each bootstrap is represented here with their BIC value for each model.
@@
 Difference here between incorporating variation at the expense of sample size, and getting high support, or staying with high sample size without variation.
+-->
 
@@
   guides(color=guide_legend(title = "Distribution \n model"))
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
 ```

### 2021-12-28 Ch2_distributions/Ch2_Figures.Rmd
Figure 4 caption.

@@
 
+Figure 4 - Delta BIC values for each bootstrap in the three pooling scenarios.
+Each bootstrap is represented in the y axis, with BIC units from the best model shown in the x axis.
+For the first panel, the CP scenario shows significant overlap among models for each bootstrap.
+Given that multi distribution models for the PP and NP scenarios have 100% support, this means they have the lowest BIC score, or a $\Delta$ BIC equal to zero, and thus show as a straight line at x=0 in the plots above.
+
 On average, how many units away is the second model from the best one?
@@
 
-What about the parameters of the best fit distributions? Meaning, that for each boostrap, keep only the best model. Plot those.
+# Appendix figures
+
+To tell the same story, we see variation in the parameters estimated for each bootstrap under various models.
 

### 2021-12-28 Ch2_distributions/Ch2_Figures.Rmd
Table2

@@
 
-On average, how many units away is the second model from the best one?
+# Table 2 - Average BIC units from best model
 
-**CP**
+Table 2 - Mean and median distance for second best model in BIC units, for each of the pooling scenarios.
 
-```{r}
+```{r Table2}
+# cp.bic %>% 
+#   filter(., deltaBIC != 0) %>% 
+#   group_by(boot) %>% 
+#   summarise(min = min(deltaBIC)) %>% 
+#   summary()
+# 
+# pp.bic %>% 
+#   filter(., deltaBIC != 0) %>% 
+#   group_by(boot) %>% 
+#   summarise(min = min(deltaBIC)) %>% 
+#   summary()
+# 
+# np.bic %>% 
+#   filter(., deltaBIC != 0) %>% 
+#   group_by(boot) %>% 
+#   summarise(min = min(deltaBIC)) %>% 
+#   summary()
+
 cp.bic %>% 
+  bind_rows(pp.bic) %>% 
+  bind_rows(np.bic) %>% 
   filter(., deltaBIC != 0) %>% 
-  group_by(boot) %>% 
+  group_by(model, boot) %>% 
   summarise(min = min(deltaBIC)) %>% 
-  summary()
-```
+  group_by(model) %>% 
+  summarise(median = median(min),
+            mean = mean(min))
 
-**PP** 
-```{r}
-pp.bic %>% 
-  filter(., deltaBIC != 0) %>% 
-  group_by(boot) %>% 
-  summarise(min = min(deltaBIC)) %>% 
-  summary()
-```
-
-**NP**
-```{r}
-np.bic %>% 
-  filter(., deltaBIC != 0) %>% 
-  group_by(boot) %>% 
-  summarise(min = min(deltaBIC)) %>% 
-  summary()
 ```

### 2022-01-03 Ch2_distributions/Ch2_Figures.Rmd
Change visualization of tables.

@@
   arrange(., model) -> BIC_table
-# BIC_table
+
+BIC_table
 

### 2022-01-05 Ch2_distributions/Ch2_Figures.Rmd
Editing first figure to show variation in both individuals and social groups.

@@
 
-```{r Figure1, fig.width=6, fig.height=4}
+```{r Figure1, fig.width=12, fig.height=4}
 
-ptpl %>%
+zoom_dims <- c(90, 200, 0, 0.01)
+annot_xy <- c(50, 200, 0.025, 0.045)
+box_color <- "blue"
+
+ind_dens_plot <- ptpl %>%
   ggplot(., aes((x = mpm))) +
@@
             stat = "density", alpha = 0.8) +
-  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
-  #           color = "blue") +
   geom_line(stat = "density", color = "black", lwd = 1) +
@@
   labs(y = "Density", x = "Velocity in m/min") +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
   theme_classic() +
@@
   theme(legend.position = "none")
+
+ind_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> ind_zoom
+
+ind_dens_plot +
+  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a
+
+fam_dens_plot <- ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = fam_g), color = "grey", 
+            stat = "density", alpha = 0.8) +
+  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  theme_classic() +
+  scale_color_manual(values = my.cols2) +
+  theme(legend.position = "none")
+
+fam_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> fam_zoom
+
+fam_dens_plot +
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b
+
+plot_grid(a, b)
 

### 2022-01-05 Ch2_distributions/Ch2_Figures.Rmd
Making a color and bw version of Figure1.

@@
 
-```{r Figure1, fig.width=12, fig.height=4}
+```{r Figure1col, fig.width=12, fig.height=4}
 
@@
   ggplot(., aes((x = mpm))) +
-  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
-  geom_line(aes(x = mpm, group = id), color = "grey", 
-            stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
   geom_line(stat = "density", color = "black", lwd = 1) +
@@
   ggplot(., aes((x = mpm))) +
-  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
-  geom_line(aes(x = mpm, group = fam_g), color = "grey", 
-            stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
+  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
   geom_line(stat = "density", color = "black", lwd = 1) +
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure1.png")
+ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
+```
+
+```{r Figure1bw, fig.width=12, fig.height=4}
+
+zoom_dims <- c(90, 200, 0, 0.01)
+annot_xy <- c(50, 200, 0.025, 0.045)
+box_color <- "blue"
+
+ind_dens_plot <- ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
+  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  theme_classic() +
+  scale_color_manual(values = my.cols2) +
+  theme(legend.position = "none")
+
+ind_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> ind_zoom
+
+ind_dens_plot +
+  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a
+
+fam_dens_plot <- ptpl %>%
+  ggplot(., aes((x = mpm))) +
+  #geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
+  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  theme_classic() +
+  scale_color_manual(values = my.cols2) +
+  theme(legend.position = "none")
+
+fam_dens_plot +
+  coord_cartesian(
+    xlim = zoom_dims[1:2],
+    ylim = zoom_dims[3:4]) +
+  theme(title = element_blank()) -> fam_zoom
+
+fam_dens_plot +
+  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b
+
+plot_grid(a, b)
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure1_bw.png")
 ```

### 2022-01-05 Ch2_distributions/Ch2_Figures.Rmd
Updated html file, and have two options for figure 1.

@@
 ```
+
+## F1 - Color
+
+Color version - each social group has a different color.
 
@@
 
-plot_grid(a, b)
+plot_grid(b,a, labels = c("A)", "B)"))
 
@@
 ```
+
+## F1 - BW
+
+Black and white version seems more clear to me.
+Maybe worth including a different in the underlying curves to make sure the point comes across that one is for individuals, and the other for social groups.
 
@@
 
-plot_grid(a, b)
+plot_grid(b, a, labels = c("A)", "B)"))
 
@@
 
-Figure 1 - Probability density plots of velocity data for each individual (grey lines), and pooled across individuals (black line).
-Considerable variation from the population level density (black line) is observed for various individuals.
+Figure 1 - Kernel density estimates for the distribution of velocity data at different pooling levels, with the dark black density curve showing complete pooling.
+A) Partial pooling representation of the data, where each curve displays the density of velocities across a social group.
+B) No pooling scenario, where each density curve is associated to a single individual's velocity data.
+Plot inserts show a zoom to the tail of the distribution of velocity data in both panels.
+We observe considerable variation for both partial and no pooling scenarios, when compared to the single black density curve that represents the complete pooling.
 Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.
-
-```{r eval=FALSE, fig.height=6, fig.width=4}
-# Figure 1 ---------------------------------------------
-# Distribution of velocities at the different pooling levels
-
-cols.fig1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
-
-ptpl %>%
-  ggplot(., aes((x = mpm))) +
-  #geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
-  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
-  #           color = "blue") +
-  geom_line(stat = "density", color = "black") +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() +
-  lims(y = c(0, 0.05)) -> cp_lines
-
-ptpl %>%
-  ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density") +
-  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
-  #           color = "blue") +
-  #geom_line(stat = "density", color = "#1191d1", lwd = 1) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() +
-  scale_color_manual(values = cols.fig1) +
-  theme(legend.position = "none") +
-  lims(y = c(0, 0.05)) -> np_lines
-
-ptpl %>%
-  ggplot(., aes((x = mpm))) +
-  #geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
-  geom_line(aes(x = mpm, group = fam_g, color = fam_g),
-            stat = "density") +
-  #geom_line(stat = "density", color = "#1191d1", lwd = 1) +
-  geom_vline(xintercept = 0, color = "grey") +
-  geom_hline(yintercept = 0, color = "grey") +
-  labs(y = "Density", x = "Velocity in m/min") +
-  theme_classic() +
-  scale_color_manual(values = cols.fig1) +
-  theme(legend.position = "none") +
-  lims(y = c(0, 0.05)) -> pp_lines
-
-plot_grid(cp_lines, pp_lines, np_lines, nrow = 3)
-
-```
 

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
updates using the tidy data for lcoations

@@
 # Data ----------------------------------------------------
-# The script for this data is in the data-raw folder
-load("data/ptpl.rda")
+# The script for this data is in the Orig_data_KH
+load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
 
 ptpl %>%
-  filter(., mpm != 0) -> ptpl
+  mutate(T_minutes = dt/60,
+         Bird_ID = id,
+         mpm = dist/T_minutes,
+         R2n = lead(R2n)) %>%
+  filter(mpm != 0) %>%
+  group_by(Bird_ID) %>%
+  add_tally() %>%
+  filter(n >= 30) -> ptpl
 ```
@@
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = 0.8) +
   #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
@@
 fam_dens_plot <- ptpl %>%
+  drop_na(sgroup) %>% 
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = 0.8) +
   #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
@@
 fam_dens_plot <- ptpl %>%
+  drop_na(sgroup) %>% 
   ggplot(., aes((x = mpm))) +
   #geom_line(aes(x = mpm, group = fam_g, color = fam_g), stat = "density", alpha = 0.8) +
-  geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = sgroup), color = "grey",stat = "density", alpha = 0.8) +
   geom_line(stat = "density", color = "black", lwd = 1) +
@@
 pp.boot.fits %>% 
-  dplyr::select(loglik, n, kpars, dist, fgroup, boot) %>% 
+  dplyr::select(loglik, n, kpars, dist, group, boot) %>% 
   distinct() %>% 
@@
   bind_rows(., pp.boot.fits %>% 
-  dplyr::select(loglik, n, kpars, dist, fgroup, boot, dBIC) %>% 
+  dplyr::select(loglik, n, kpars, dist, group, boot, dBIC) %>% 
   distinct() %>% 
@@
 
-```{r Figure3, fig.width=12, fig.height=6}
+```{r Figure3, fig.width=12, fig.height=5}
 
@@
   ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
-  scale_fill_manual(values = cols.fig2) +
+  scale_fill_manual(values = cols.fig2, drop = FALSE) +
   geom_col() +
@@
                filter(., model == "CP"),
-             aes(x = model, y = -0.05, label = dist)) -> pooling.support
+             aes(x = model, y = -0.05, label = dist), size = 2.5) -> pooling.support
 
@@
 pp.boot.fits %>%
-  dplyr::select(., bic, dist, dBIC, fgroup, boot) %>%
-  group_by(fgroup, boot) %>%
+  dplyr::select(., bic, dist, dBIC, group, boot) %>%
+  group_by(group, boot) %>%
   distinct() %>%
-  group_by(fgroup) %>%
+  group_by(group) %>%
   filter(dBIC == 0) %>%
@@
   mutate(prcnt_support = n/nboots) %>%
-  ggplot(., aes(x = fgroup, y = prcnt_support, fill = dist)) +
+  ggplot(., aes(x = group, y = prcnt_support, fill = dist)) +
   geom_col() +
@@
   geom_label(data = bestmodel %>% filter(., model == "PP"),
-             aes(x = ID, y = -0.05, label = dist)) +
+             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
   scale_fill_manual(values = cols.fig2) -> pp.support
@@
   count(dist) %>%
-  mutate(prcnt_support = n/nboots) %>%
+  mutate(prcnt_support = n/nboots,
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>%
   ggplot(., aes(x = individual, y = prcnt_support, fill = dist)) +
@@
   geom_label(data = bestmodel %>% filter(., model == "NP"),
-             aes(x = ID, y = -0.05, label = dist)) +
+             aes(x = ID, y = -0.05, label = dist), size = 2.5) +
   scale_fill_manual(values = cols.fig2)  -> np.support
@@
         legend.position = "none") +
-  facet_wrap(~fam_g, nrow = 2) +
+  facet_wrap(~group, nrow = 2) +
   theme(axis.text = element_blank()) +

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Parameter variation for np scenario.

@@
   #geom_col() +
-  geom_point(alpha = 0.8, shape = 15) +
+  geom_point(alpha = 0.8, shape = 15, size = 0.8) +
   scale_color_manual(values = cols.fig2) +
@@
   filter(., deltaBIC != 0) %>% 
+  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
   group_by(model, boot) %>% 
@@
   group_by(model) %>% 
-  summarise(median = median(min),
+  summarise(minimum = min(min),
+            median = median(min),
             mean = mean(min))
@@
   filter(., dBIC == 0) %>% 
-  ggplot(., aes(y = estimate)) +
-  facet_wrap(dist~param, ncol = 2, scales = "free") +
-  geom_boxplot()
+  dplyr::select(boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape)) +
+  geom_point()
 ```
@@
 ```{r fig.height=6}
+
 np.boot.fits %>%
   filter(., dBIC == 0) %>% 
-  ggplot(., aes(y = estimate, x = individual)) +
-  facet_wrap(dist~param, ncol = 2, scales = "free") +
-  geom_boxplot()
+  dplyr::select(individual, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>%
+  filter(., dist == "gamma") %>% 
+  ggplot(., aes(x = rate, y = shape, color = individual)) +
+  geom_point() -> a
+
+np.boot.fits %>%
+  filter(., dBIC == 0) %>% 
+  dplyr::select(individual, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>%
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = individual)) +
+  geom_point() -> b
+
+np.boot.fits %>%
+  filter(., dBIC == 0) %>% 
+  dplyr::select(individual, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape, color = individual)) +
+  geom_point() -> c
+
+plot_grid(a, b, c)
 ```

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Working on figure for parameter space.

@@
 
-# Appendix figures
+# Figure X - Best fit parameters
 
@@
 
-**CP**
+```{r}
 
-```{r fig.height=6}
 cp.boot.fits %>%
@@
   dplyr::select(boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) %>%
-  filter(., dist == "weibull") %>% 
-  ggplot(., aes(x = scale, y = shape)) +
-  geom_point()
-```
+  pivot_wider(names_from = param, values_from = estimate) -> cp.best
 
-**PP**
-
-```{r fig.height=6}
 pp.boot.fits %>%
   filter(., dBIC == 0) %>% 
-  ggplot(., aes(y = estimate, x = fgroup)) +
-  facet_wrap(dist~param, ncol = 2, scales = "free") +
-  geom_boxplot()
-```
-
-**NP**
-
-```{r fig.height=6}
+  dplyr::select(group, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) -> pp.best
 
@@
   pivot_wider(names_from = param, values_from = estimate) %>% 
+  mutate(id = str_remove(individual, "B"), 
+         group = case_when(
+    id %in% c(1,3,5) ~ "G1",
+    id %in% c(7) ~ "G2",
+    id %in% c(13, 19) ~ "G3",
+    id %in% c(22) ~ "G4",
+    id %in% c(28) ~ "G5",
+    id %in% c(49, 84) ~ "G6",
+    id %in% c(29, 30) ~ "G7"
+  )) %>%
+  #slice_sample(., n = 100) %>% 
+  arrange(group) %>% 
+  group_by(group) %>% 
+  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
+#View(np.best)
+
+```
+
+```{r FigureX, fig.height=12, fig.width=12}
+library(MetBrewer)
+
+colsx <- met.brewer("Gauguin", n = 7)
+aval <- 0.3
+
+figx.theme <- theme_bw() +
+  theme(legend.position = "none")
+
+cp.best %>% 
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog)) +
+  geom_point(alpha = aval) +
+  figx.theme -> cp.ln
+
+cp.best %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape)) +
+  geom_point(alpha = aval) +
+  figx.theme -> cp.wei
+
+cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)
+
+pp.best %>% 
   filter(., dist == "gamma") %>% 
-  ggplot(., aes(x = rate, y = shape, color = individual)) +
-  geom_point() -> a
+  ggplot(., aes(x = rate, y = shape, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> pp.gam
 
-np.boot.fits %>%
-  filter(., dBIC == 0) %>% 
-  dplyr::select(individual, boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) %>%
+pp.best %>%
   filter(., dist == "lnorm") %>% 
-  ggplot(., aes(x = meanlog, y = sdlog, color = individual)) +
-  geom_point() -> b
+  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> pp.ln
 
-np.boot.fits %>%
-  filter(., dBIC == 0) %>% 
-  dplyr::select(individual, boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) %>%
+pp.best %>%
   filter(., dist == "weibull") %>% 
-  ggplot(., aes(x = scale, y = shape, color = individual)) +
-  geom_point() -> c
+  ggplot(., aes(x = scale, y = shape, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> pp.wei
 
-plot_grid(a, b, c)
+pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1)
+
+np.best %>% 
+  filter(., dist == "gamma") %>% 
+  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> np.gam
+
+np.best %>% 
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> np.ln
+
+np.best %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  figx.theme -> np.wei
+
+np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1)
+
+plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)
 ```
@@
 
-```{r fig.width=8, fig.height=6}
+```{r fig.width=8, fig.height=6, eval = FALSE}
 p1_angles <- ptpl %>% 

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Change lims for gamma plot

@@
 library(gt)
+library(MetBrewer)
+library(purrr)
 
@@
 
+cp.best
+
 pp.boot.fits %>%
@@
 
+# What values to use
+map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
+map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
+map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
+map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
+map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
+map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
+
 ```
 
-```{r FigureX, fig.height=12, fig.width=12}
-library(MetBrewer)
+```{r FigureX, fig.height=9, fig.width=9}
 
-colsx <- met.brewer("Gauguin", n = 7)
+colsx <- met.brewer("Tiepolo", n = 7)
 aval <- 0.3
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
   figx.theme -> pp.gam
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
   figx.theme -> np.gam
@@
 plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)
+
+ggsave2(filename = "Ch2_distributions/Figures/Figurex.png")
 ```

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Adjust plot limits

@@
   geom_point(alpha = aval) +
+  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
   figx.theme -> cp.ln
@@
   geom_point(alpha = aval) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
   figx.theme -> cp.wei
@@
   scale_color_manual(values=colsx) +
-  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
   figx.theme -> pp.gam
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
   figx.theme -> pp.ln
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
   figx.theme -> pp.wei
@@
   scale_color_manual(values=colsx) +
-  lims(x = c(0, 0.23), y = c(0.4, 2.4)) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
   figx.theme -> np.gam
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
   figx.theme -> np.ln
@@
   scale_color_manual(values=colsx) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
   figx.theme -> np.wei

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Minor details to the figure.

@@
 
-cp.best
-
 pp.boot.fits %>%
@@
   dplyr::select(group, boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) -> pp.best
+  pivot_wider(names_from = param, values_from = estimate) %>% 
+  mutate(group = as.factor(group)) -> pp.best
 
@@
   #slice_sample(., n = 100) %>%
+  mutate(group = as.factor(group)) %>% 
   arrange(group) %>% 
@@
   geom_point(alpha = aval) +
-  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
   figx.theme -> cp.ln
@@
 
-cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)
+#cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)
 
@@
   geom_point(alpha = aval) +
-  scale_color_manual(values=colsx) +
+  scale_color_manual(values=colsx, drop=FALSE) +
   lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
@@
   geom_point(alpha = aval) +
-  scale_color_manual(values=colsx) +
-  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
+  scale_color_manual(values=colsx, drop=FALSE) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
   figx.theme -> pp.ln
@@
   geom_point(alpha = aval) +
-  scale_color_manual(values=colsx) +
+  scale_color_manual(values=colsx, drop=FALSE) +
   lims(x = c(5, 80), y = c(0, 2.1)) +
@@
   geom_point(alpha = aval) +
-  scale_color_manual(values=colsx) +
-  lims(x = c(0.7, 3.5), y = c(0.5, 2.1)) +
+  scale_color_manual(values=colsx, drop=FALSE) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
   figx.theme -> np.ln
@@
 np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1)
+
+legend.grid <- get_legend(pp.best %>%
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=colsx) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  theme_bw() +
+  guides(color = guide_legend(title = "Social Group", ncol = 2,
+                              override.aes = list(alpha = 0.9, size = 5))))
+
+cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
 

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Changed labels for plot grid.

@@
 
-#cp.grid <- plot_grid(NULL, cp.ln, cp.wei, ncol = 3)
+cp.grid <- plot_grid(cp.ln, cp.wei, ncol = 2, labels = c("A)", "B)"), label_size = 9)
 
@@
 
-pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1)
+pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1, labels = c("C)", "D)", "E)"), label_size = 9)
 
@@
 
-np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1)
+np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1, labels = c("F)", "G)", "H)"), label_size = 9)
 
@@
 
-cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
+#cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
+row1 <- plot_grid(legend.grid, cp.grid, ncol = 2, rel_widths = c(1,2))
 
-plot_grid(cp.grid, pp.grid, np.grid, nrow = 3)
+plot_grid(row1, pp.grid, np.grid, nrow = 3)
 

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Figure x. ready.

@@
 figx.theme <- theme_bw() +
-  theme(legend.position = "none")
+  theme(legend.position = "none",
+        axis.title = element_text(size = 8))
 
@@
   lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "CP - lnorm") +
   figx.theme -> cp.ln
@@
   lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "CP - weibull") +
   figx.theme -> cp.wei
@@
   lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
+  labs(subtitle = "PP - gamma") +
   figx.theme -> pp.gam
@@
   lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "PP - lnorm") +
   figx.theme -> pp.ln
@@
   lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "PP - weibull") +
   figx.theme -> pp.wei
@@
   lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
+  labs(subtitle = "NP - gamma") +
   figx.theme -> np.gam
@@
   lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "NP - lnorm") +
   figx.theme -> np.ln
@@
   lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "NP - weibull") +
   figx.theme -> np.wei

### 2022-01-06 Ch2_distributions/Ch2_Figures.Rmd
Good! I like these figures.

@@
 # What values to use
-map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
-map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
-map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
-map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
-map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
-map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
+# map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
+# map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
+# map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
+# map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
+# map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
+# map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
 

### 2022-01-07 Ch2_distributions/Ch2_Figures.Rmd
Changed the order of figures.

@@
 
-```{r include=FALSE}
+```{r LoadMovData, include=FALSE}
 set.seed(20211207)
@@
 
-# Figure 1 - Density plots for velocity
-
-```{r include=FALSE}
+```{r Colors, include=FALSE}
 # Color palette ----------------------------------------
@@
               "#669e46", "grey")
-scales::show_col(my.cols2)
+scales::show_col(my.cols1)
 
+# Colors for social groups ----------------------------------------
+
+sgroup_col <- met.brewer("Tiepolo", n = 7)
+
+# Colors for models ---------------------------------
+
+mod_col <- met.brewer("Hokusai1", n=4)
+mod_col <- c("#4C6838", "#C1B489", "#8EBF72", "#91A5A0")
+mod_col <- c("#264653", "#2a9d8f", "#e2b33c", "#e76f51")
+
+scales::show_col(mod_col)
 ```
 
-## F1 - Color
+# Figure 1 - Density plots for velocity
 
-Color version - each social group has a different color.
+<!-- Color version - each social group has a different color.   -->
 
-```{r Figure1col, fig.width=12, fig.height=4}
+```{r Figure1col, fig.width=12, fig.height=4.5}
 
@@
 box_color <- "blue"
+aval <- 0.6
 
@@
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = id, color = sgroup), stat = "density", alpha = aval, size=1) +
   #geom_line(aes(x = mpm, group = id), color = "grey", stat = "density", alpha = 0.8) +
-  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_line(stat = "density", color = "black", size = 1.3) +
   geom_vline(xintercept = 0, color = "grey") +
@@
   theme_classic() +
-  scale_color_manual(values = my.cols2) +
+  #scale_color_manual(values = my.cols2) +
+  scale_color_manual(values = sgroup_col) +
   theme(legend.position = "none")
@@
   ggplot(., aes((x = mpm))) +
-  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = 0.8) +
+  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = aval, size = 1) +
   #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
-  geom_line(stat = "density", color = "black", lwd = 1) +
+  geom_line(stat = "density", color = "black", size = 1.3) +
   geom_vline(xintercept = 0, color = "grey") +
@@
 
-plot_grid(b,a, labels = c("A)", "B)"))
+toprow <- plot_grid(b,a, labels = c("A)", "B)"))
+
+fig1leg <- get_legend(ptpl %>%
+  drop_na(sgroup) %>% 
+  ggplot(., aes((x = mpm))) +
+  geom_line(aes(x = mpm, group = sgroup, color = sgroup), stat = "density", alpha = aval, size = 1.1) +
+  #geom_line(aes(x = mpm, group = fam_g), color = "grey",stat = "density", alpha = 0.8) +
+  geom_line(stat = "density", color = "black", size = 1.2) +
+  geom_vline(xintercept = 0, color = "grey") +
+  geom_hline(yintercept = 0, color = "grey") +
+  labs(y = "Density", x = "Velocity in m/min") +
+    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
+  theme_classic() +
+  #scale_color_manual(values = my.cols2) +
+  scale_color_manual(values = sgroup_col) +
+    guides(color = guide_legend(title = "Social group",
+                                override.aes = list(alpha = 0.8)))+
+    theme(legend.position = "bottom"))
+
+plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
 
@@
 
-## F1 - BW
+<!-- ## F1 - BW  -->
 
-Black and white version seems more clear to me.
+<!-- Black and white version seems more clear to me.
 Maybe worth including a different in the underlying curves to make sure the point comes across that one is for individuals, and the other for social groups.
+-->
 
-```{r Figure1bw, fig.width=12, fig.height=4}
+```{r Figure1bw,  eval = FALSE, fig.width=12, fig.height=4}
 
@@
 B) No pooling scenario, where each density curve is associated to a single individual's velocity data.
+Individuals belonging to the same social group share the line color.
 Plot inserts show a zoom to the tail of the distribution of velocity data in both panels.
@@
 
-```{r}
+```{r LoadFitData}
 load("Ch2_distributions/Ch2_fits.RData")
@@
 
-```{r}
+```{r CalcBestModel}
 reg_fits_info %>% 
@@
 
-```{r eval=FALSE}
+```{r BICdist, eval=FALSE}
 # Difference to the second best model
@@
 
-```{r}
+```{r CalcBICTable}
 # Calculate the BIC for the models:
@@
 
-```{r}
+```{r BootstrapBIC}
 cp.boot.fits %>% 
@@
 
-```{r}
+```{r GenerateBICtable}
 
@@
 
-```{r eval=FALSE}
+```{r Generate_gt_Table, eval=FALSE}
 
@@
 
+# Figure 2 - Best fit parameters
+
+To tell the same story, we see variation in the parameters estimated for each bootstrap under various models.
+
+```{r Bootstrap_dBICzero}
+
+cp.boot.fits %>%
+  filter(., dBIC == 0) %>% 
+  dplyr::select(boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) -> cp.best
+
+pp.boot.fits %>%
+  filter(., dBIC == 0) %>% 
+  dplyr::select(group, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>% 
+  mutate(group = as.factor(group)) -> pp.best
+
+np.boot.fits %>%
+  filter(., dBIC == 0) %>% 
+  dplyr::select(individual, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>% 
+  mutate(id = str_remove(individual, "B"), 
+         group = case_when(
+    id %in% c(1,3,5) ~ "G1",
+    id %in% c(7) ~ "G2",
+    id %in% c(13, 19) ~ "G3",
+    id %in% c(22) ~ "G4",
+    id %in% c(28) ~ "G5",
+    id %in% c(49, 84) ~ "G6",
+    id %in% c(29, 30) ~ "G7"
+  )) %>%
+  #slice_sample(., n = 100) %>%
+  mutate(group = as.factor(group)) %>% 
+  arrange(group) %>% 
+  group_by(group) %>% 
+  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
+#View(np.best)
+
+# What values to use
+# map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
+# map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
+# map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
+# map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
+# map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
+# map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
+
+```
+
+```{r Figure2, fig.height=9, fig.width=9}
+
+#colsx <- met.brewer("Tiepolo", n = 7)
+aval <- 0.5
+
+figx.theme <- theme_bw() +
+  theme(legend.position = "none",
+        axis.title = element_text(size = 8))
+
+cp.best %>% 
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog)) +
+  geom_point(alpha = aval) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "CP - lnorm") +
+  figx.theme -> cp.ln
+
+cp.best %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape)) +
+  geom_point(alpha = aval) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "CP - weibull") +
+  figx.theme -> cp.wei
+
+cp.grid <- plot_grid(cp.ln, cp.wei, ncol = 2, labels = c("A)", "B)"), label_size = 9)
+
+pp.best %>% 
+  filter(., dist == "gamma") %>% 
+  ggplot(., aes(x = rate, y = shape, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
+  labs(subtitle = "PP - gamma") +
+  figx.theme -> pp.gam
+
+pp.best %>%
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "PP - lnorm") +
+  figx.theme -> pp.ln
+
+pp.best %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "PP - weibull") +
+  figx.theme -> pp.wei
+
+pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1, labels = c("C)", "D)", "E)"), label_size = 9)
+
+np.best %>% 
+  filter(., dist == "gamma") %>% 
+  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
+  labs(subtitle = "NP - gamma") +
+  figx.theme -> np.gam
+
+np.best %>% 
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  labs(subtitle = "NP - lnorm") +
+  figx.theme -> np.ln
+
+np.best %>%
+  filter(., dist == "weibull") %>% 
+  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(5, 80), y = c(0, 2.1)) +
+  labs(subtitle = "NP - weibull") +
+  figx.theme -> np.wei
+
+np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1, labels = c("F)", "G)", "H)"), label_size = 9)
+
+legend.grid <- get_legend(pp.best %>%
+  filter(., dist == "lnorm") %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
+  geom_point(alpha = aval) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+  theme_bw() +
+  guides(color = guide_legend(title = "Social Group", ncol = 2,
+                              override.aes = list(alpha = 0.9, size = 5))))
+
+#cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
+row1 <- plot_grid(legend.grid, cp.grid, ncol = 2, rel_widths = c(1,2))
+
+plot_grid(row1, pp.grid, np.grid, nrow = 3)
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
+```
+
 # Figure 3 - Percent Support
@@
   ggplot(., aes(x = model, y = prcnt_support, fill = dist)) +
-  scale_fill_manual(values = cols.fig2, drop = FALSE) +
+  #scale_fill_manual(values = cols.fig2, drop = FALSE) +
+  scale_fill_manual(values = mod_col, drop = FALSE) +
   geom_col() +
@@
              aes(x = ID, y = -0.05, label = dist), size = 2.5) +
-  scale_fill_manual(values = cols.fig2) -> pp.support
+  #scale_fill_manual(values = cols.fig2) +
+  scale_fill_manual(values = mod_col, drop = FALSE) +
+  NULL -> pp.support
 
@@
              aes(x = ID, y = -0.05, label = dist), size = 2.5) +
-  scale_fill_manual(values = cols.fig2)  -> np.support
+  #scale_fill_manual(values = cols.fig2) +
+  scale_fill_manual(values = mod_col, drop = FALSE) +
+  NULL -> np.support
 
@@
 
-```{r eval=FALSE}
+```{r BICboxplots, eval=FALSE}
 # These boxplots should be showing the distribution of the BIC values for the three pooling levels with their models.
@@
   geom_point(alpha = 0.8, shape = 15) +
-  scale_color_manual(values = cols.fig2) +
+  #scale_color_manual(values = cols.fig2) +
+  scale_color_manual(values = mod_col, drop = FALSE) +
   theme_classic() +
@@
 
-```{r fig.height=4}
+```{r Figure4, fig.height=4}
 cp.bic %>% 
@@
   #geom_col() +
-  geom_point(alpha = 0.8, shape = 15, size = 0.8) +
-  scale_color_manual(values = cols.fig2) +
+  geom_point(alpha = 0.9, shape = 15, size = 0.9) +
+  #scale_color_manual(values = cols.fig2) +
+  scale_color_manual(values = mod_col, drop = FALSE) +
   theme_classic() +
@@
   theme(legend.position = "right") +
-  guides(color=guide_legend(title = "Distribution \n model"))
+  guides(color=guide_legend(title = "Distribution \n model", override.aes = list(size = 5)))
 
@@
             median = median(min),
-            mean = mean(min))
+            mean = mean(min),
+            q2.5 = quantile(min, probs = 0.025),
+            q97.5 = quantile(min, probs = 0.975))
 
-```
-
-# Figure X - Best fit parameters
-
-To tell the same story, we see variation in the parameters estimated for each bootstrap under various models.
-
-```{r}
-
-cp.boot.fits %>%
-  filter(., dBIC == 0) %>% 
-  dplyr::select(boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) -> cp.best
-
-pp.boot.fits %>%
-  filter(., dBIC == 0) %>% 
-  dplyr::select(group, boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) %>% 
-  mutate(group = as.factor(group)) -> pp.best
-
-np.boot.fits %>%
-  filter(., dBIC == 0) %>% 
-  dplyr::select(individual, boot, estimate, param, dist) %>% 
-  pivot_wider(names_from = param, values_from = estimate) %>% 
-  mutate(id = str_remove(individual, "B"), 
-         group = case_when(
-    id %in% c(1,3,5) ~ "G1",
-    id %in% c(7) ~ "G2",
-    id %in% c(13, 19) ~ "G3",
-    id %in% c(22) ~ "G4",
-    id %in% c(28) ~ "G5",
-    id %in% c(49, 84) ~ "G6",
-    id %in% c(29, 30) ~ "G7"
-  )) %>%
-  #slice_sample(., n = 100) %>%
-  mutate(group = as.factor(group)) %>% 
-  arrange(group) %>% 
-  group_by(group) %>% 
-  mutate(shapeid = as.character(as.numeric(as.factor(individual)))) -> np.best
-#View(np.best)
-
-# What values to use
-# map_dbl(cp.best[,-c(1,2)], min, na.rm = TRUE)
-# map_dbl(cp.best[,-c(1,2)], max, na.rm = TRUE)
-# map_dbl(pp.best[,-c(1:3)], min, na.rm = TRUE)
-# map_dbl(pp.best[,-c(1:3)], max, na.rm = TRUE)
-# map_dbl(np.best[,c(4:8)], min, na.rm = TRUE)
-# map_dbl(np.best[,c(4:8)], max, na.rm = TRUE)
-
-```
-
-```{r FigureX, fig.height=9, fig.width=9}
-
-colsx <- met.brewer("Tiepolo", n = 7)
-aval <- 0.3
-
-figx.theme <- theme_bw() +
-  theme(legend.position = "none",
-        axis.title = element_text(size = 8))
-
-cp.best %>% 
-  filter(., dist == "lnorm") %>% 
-  ggplot(., aes(x = meanlog, y = sdlog)) +
-  geom_point(alpha = aval) +
-  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
-  labs(subtitle = "CP - lnorm") +
-  figx.theme -> cp.ln
-
-cp.best %>%
-  filter(., dist == "weibull") %>% 
-  ggplot(., aes(x = scale, y = shape)) +
-  geom_point(alpha = aval) +
-  lims(x = c(5, 80), y = c(0, 2.1)) +
-  labs(subtitle = "CP - weibull") +
-  figx.theme -> cp.wei
-
-cp.grid <- plot_grid(cp.ln, cp.wei, ncol = 2, labels = c("A)", "B)"), label_size = 9)
-
-pp.best %>% 
-  filter(., dist == "gamma") %>% 
-  ggplot(., aes(x = rate, y = shape, color = group)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
-  labs(subtitle = "PP - gamma") +
-  figx.theme -> pp.gam
-
-pp.best %>%
-  filter(., dist == "lnorm") %>% 
-  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
-  labs(subtitle = "PP - lnorm") +
-  figx.theme -> pp.ln
-
-pp.best %>%
-  filter(., dist == "weibull") %>% 
-  ggplot(., aes(x = scale, y = shape, color = group)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(5, 80), y = c(0, 2.1)) +
-  labs(subtitle = "PP - weibull") +
-  figx.theme -> pp.wei
-
-pp.grid <- plot_grid(pp.gam, pp.ln, pp.wei, nrow = 1, labels = c("C)", "D)", "E)"), label_size = 9)
-
-np.best %>% 
-  filter(., dist == "gamma") %>% 
-  ggplot(., aes(x = rate, y = shape, color = group, shape = shapeid)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(0, 0.23), y = c(0.4, 2.3)) +
-  labs(subtitle = "NP - gamma") +
-  figx.theme -> np.gam
-
-np.best %>% 
-  filter(., dist == "lnorm") %>% 
-  ggplot(., aes(x = meanlog, y = sdlog, color = group, shape = shapeid)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
-  labs(subtitle = "NP - lnorm") +
-  figx.theme -> np.ln
-
-np.best %>%
-  filter(., dist == "weibull") %>% 
-  ggplot(., aes(x = scale, y = shape, color = group, shape = shapeid)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx, drop=FALSE) +
-  lims(x = c(5, 80), y = c(0, 2.1)) +
-  labs(subtitle = "NP - weibull") +
-  figx.theme -> np.wei
-
-np.grid <- plot_grid(np.gam, np.ln, np.wei, nrow = 1, labels = c("F)", "G)", "H)"), label_size = 9)
-
-legend.grid <- get_legend(pp.best %>%
-  filter(., dist == "lnorm") %>% 
-  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
-  geom_point(alpha = aval) +
-  scale_color_manual(values=colsx) +
-  lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
-  theme_bw() +
-  guides(color = guide_legend(title = "Social Group", ncol = 2,
-                              override.aes = list(alpha = 0.9, size = 5))))
-
-#cp.grid <- plot_grid(legend.grid, cp.ln, cp.wei, ncol = 3)
-row1 <- plot_grid(legend.grid, cp.grid, ncol = 2, rel_widths = c(1,2))
-
-plot_grid(row1, pp.grid, np.grid, nrow = 3)
-
-ggsave2(filename = "Ch2_distributions/Figures/Figurex.png")
 ```

### 2022-01-07 Ch2_distributions/Ch2_Figures.Rmd
All figures and tables ready with captions.

@@
 output:
+  word_document:
+    toc: yes
   html_document:
-    toc: true
+    toc: yes
 ---
@@
 
+Figure 2 -Parameter space for best fitting models under the three pooling scenarios for 1000 bootstrap replicas.
+Complete pooling approaches showed best fitting models under the lognormal (panel A.) and weibull (B.) distributions, but no models under a gamma distribution.
+C)-E) Panels show placement of best fitting models under the three distributions with each color representing a different social group.
+Under the NP scenario (panels F.-H.) individuals belongig to the same social group are represented with a different shape.
+
 # Figure 3 - Percent Support
@@
 
-```{r Figure4, fig.height=4}
+```{r eval=FALSE, fig.height=4}
 cp.bic %>% 
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
+#ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
 ```
 
-Figure 4 - Delta BIC values for each bootstrap in the three pooling scenarios.
-Each bootstrap is represented in the y axis, with BIC units from the best model shown in the x axis.
-For the first panel, the CP scenario shows significant overlap among models for each bootstrap.
-Given that multi distribution models for the PP and NP scenarios have 100% support, this means they have the lowest BIC score, or a $\Delta$ BIC equal to zero, and thus show as a straight line at x=0 in the plots above.
+```{r Figure4}
+
+cp.bic %>% 
+  bind_rows(., pp.bic) %>% 
+  bind_rows(., np.bic) %>% 
+  mutate(dist = factor(dist, levels = c("gamma", "lnorm", "weibull", "multi")),
+         model = factor(model, levels = c("CP", "PP", "NP"))) -> all.bic
+
+all.bic %>% 
+  filter(., deltaBIC != 0) %>% 
+  ggplot(., aes(x = model, y = deltaBIC)) +
+  #geom_violin() +
+  #geom_boxplot(width = 0.4, coef = 0, outlier.shape = NA) +
+  geom_jitter(data = all.bic, 
+              #%>% group_by(model) %>% slice_sample(n=400),
+              aes(x = model, y = deltaBIC, color = dist), width = 0.3, alpha = 0.6) +
+  #geom_boxplot(color = "black", width = 0.4, fill = "white", alpha = 0.8) +
+  geom_violin(color = "black", width = 0.4, fill = "white", alpha = 0.6) +
+  geom_boxplot(width = 0.1, coef = 0, outlier.shape = NA) +
+  scale_color_manual(values = mod_col, drop = FALSE) +
+  theme_classic() + 
+  labs(x = "", y = "BIC units from best model") +
+  theme(legend.position = "bottom") +
+  guides(color=guide_legend(title = "Distribution", override.aes = list(size = 5, alpha = 0.9)))
+
+ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
+
+```
+
+Figure 4 - Distributions of $\Delta BIC$ values for models under the three different pooling scenarios.
+Best fit model is aligned at y = 0, thus in the case of the PP and NP scenario, the orange bar at y=0 is actually the $\Delta BIC$ value being zero for the multi-distribution model for all bootstraps.
+The violin plots describe the density of $\Delta BIC$ units away from the best model.
+The box overlay shows the median, and lower and upper quartiles of this distribution for the three different pooling levels.
 
@@
 
-```{r fig.width=8, fig.height=6, eval = FALSE}
+```{r fig.width=8, fig.height=6}
 p1_angles <- ptpl %>% 
@@
         legend.position = "none") +
-  facet_wrap(~group, nrow = 2) +
+  facet_wrap(~sgroup, nrow = 2) +
   theme(axis.text = element_blank()) +
@@
         legend.position = "none") +
-  facet_wrap(~B_id, nrow = 2) +
+  facet_wrap(~Bird_ID, nrow = 2) +
   theme(axis.text = element_blank()) +

### 2022-01-10 Ch2_distributions/Ch2_Figures.Rmd
Not knitting to word.
Saving tables as csv files.

@@
 output:
-  word_document:
-    toc: yes
   html_document:
@@
 Probability density functions considered included the Gamma, Weibull, and Lognormal distributions.
-Multi distribution models selected the best fitting distribution model for each family group or individual, allowing for variation not only in estimated parameters, but also in the distribution used.
-Based on BIC values, the best fitting model is the Multi-distribution with Partial Pooling, closely followed by the Complete Pooling Lognormal model.
+Multi distribution models selected the best fitting distribution model for each social group or individual, allowing for variation not only in estimated parameters, but also in the distribution used.
+Based on BIC values, the best fitting model is the Multi-distribution with Partial Pooling, followed by the Lognormal PP, and Lognormal CP.
 
@@
 BIC_table
+write.csv(BIC_table, file = "Ch2_distributions/Figures/bic_table.csv")
 
@@
 
-#library(gt)
+library(gt)
 
@@
     deltaBIC_acrossmodels = html("&Delta; BIC<sub>across</sub>"),
-  )
+  ) -> gt_table_bic
 
-# -> gt_table_bic
-#   
-# gtsave(gt_table_bic, "Ch2_distributions/aic_bic_table.png") 
+gtsave(gt_table_bic, "Ch2_distributions/Figures/bic_table.png")
 ```
@@
             q2.5 = quantile(min, probs = 0.025),
-            q97.5 = quantile(min, probs = 0.975))
+            q97.5 = quantile(min, probs = 0.975)) -> bic_2nd
+
+bic_2nd
+
+write.csv(bic_2nd, file = "Ch2_distributions/Figures/bic_2nd.csv")
 

### 2022-01-10 Ch2_distributions/Ch2_Figures.Rmd
Added to Figure 1 to include the variation in the time intervals.

@@
 
-plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
+#plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
+#ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
+```
+
+```{r fig.width=12, fig.height=4.5}
+ptpl %>%
+  drop_na(mpm) %>%
+  filter(mpm != 0) %>%
+  group_by(Bird_ID) %>%
+  add_tally() %>%
+  filter(n >= 30) -> nonzerompm
+
+nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(individual, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = individual, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Individual bird tag",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "none") -> np_ints
+
+nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(sgroup, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Social group",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "none") -> pp_ints
+
+legend_row <- get_legend(nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(sgroup, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Individual bird tag",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Time interval\n in minutes", nrow = 1)) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "bottom"))
+
+plot_row <- plot_grid(pp_ints, np_ints, nrow = 1, labels = c("C)", "D)"))
+#plot_grid(plot_row, legend_row, ncol = 1, rel_heights = c(1, 0.1))
+```
+
+```{r Figure1, fig.height=9, fig.width=12}
+
+a <- plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
+b <- plot_grid(plot_row, legend_row, ncol = 1, rel_heights = c(1, 0.1))
+
+plot_grid(a, NULL, b, ncol = 1, rel_heights = c(1, 0.1, 1))
+ggsave2(filename = "Ch2_distributions/Figures/Figure1.png")
+
 ```
@@
 Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.
+Panels C) and D) show the variation in number of observations and the length of time intervals recorded at the group and individual level.
 

### 2022-01-10 Ch2_distributions/Ch2_Figures.Rmd
Figures for angles are done. NEed captions now.

@@
 
-# Figure X - angles
-
-```{r fig.width=8, fig.height=6}
+# Figure 5 - angles
+
+```{r Figure5, fig.width=8, fig.height=6}
 p1_angles <- ptpl %>% 
@@
 
-```
+ggsave("Ch2_distributions/Figures/Figure5.png")
+
+```
+
+```{r}
+
+# Relative angle requires at least three consecutive observations since it is looking at changes in direction.
+Whereas, the absolute angle is just the direction of movement based on the absolute plane, and thus it only requires two consecutive observations.
+ptpl %>% 
+  ungroup() %>% 
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  dplyr::select(individual, sgroup, rel.angle, abs.angle) -> angles_df
+```
+
+```{r eval = FALSE}
+p1_angles <- angles_df %>% 
+  drop_na(abs.angle) %>% 
+  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
+                          abs.angle * 180/pi + 360)) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  labs(title = "Complete pooling")
+
+p2_angles <- angles_df %>% 
+  drop_na(abs.angle) %>% 
+  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
+                          abs.angle * 180/pi + 360)) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  facet_wrap(~sgroup, nrow = 2) +
+  theme(axis.text = element_blank()) +
+  labs(title = "Partial pooling")
+
+p3_angles <- angles_df %>% 
+  drop_na(abs.angle) %>% 
+  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
+                          abs.angle * 180/pi + 360)) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  facet_wrap(~ individual, nrow = 2) +
+  theme(axis.text = element_blank()) +
+  labs(title = "No pooling")
+
+plot_grid(plot_grid(p1_angles, p2_angles), p3_angles, nrow = 2)
+```
+
+```{r}
+
+library(CircStats)
+
+ptpl %>%
+  drop_na(rel.angle) %>% 
+  group_by(Bird_ID) %>%
+  add_tally() %>%
+  filter(n >= 30)  %>% 
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  dplyr::select(individual, sgroup, rel.angle, abs.angle) %>%
+  drop_na(individual, rel.angle) -> angles_df
+
+# Estimate for complete pooling
+
+mu0 <- circ.mean(angles_df$rel.angle)
+rho0 <- est.rho(angles_df$rel.angle)
+angle.params <- as.data.frame(wrpcauchy.ml(angles_df$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
+  mutate(model = "CP",
+         group = NA)
+
+# Partial pooling
+
+sgroups <- paste0("G", 1:7)
+
+for(i in 1:7){
+
+  sub_data <- angles_df %>%
+    drop_na(rel.angle) %>%
+    filter(., sgroup == sgroups[i])
+
+  mu0 <- circ.mean(sub_data$rel.angle)
+  rho0 <- est.rho(sub_data$rel.angle)
+  a <- as.data.frame(wrpcauchy.ml(sub_data$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
+    mutate(model = "PP",
+           group = sgroups[i])
+
+  angle.params <- rbind.data.frame(angle.params, a)
+
+}
+
+# No pooling
+
+individuals <- unique(angles_df$individual)
+
+for(i in 1:12){
+
+  sub_data <- angles_df %>%
+    drop_na(rel.angle) %>%
+    filter(., individual == individuals[i])
+
+  mu0 <- circ.mean(sub_data$rel.angle)
+  rho0 <- est.rho(sub_data$rel.angle)
+  a <- as.data.frame(wrpcauchy.ml(sub_data$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
+    mutate(model = "NP",
+           group = individuals[i])
+
+  angle.params <- rbind.data.frame(angle.params, a)
+
+}
+
+```
+
+```{r Figure6, fig.width=6, fig.height=3}
+cp.mu <- angle.params$mu[which(angle.params$model=="CP")]
+cp.rho <- angle.params$rho[which(angle.params$model=="CP")]
+
+angle.params %>% 
+  mutate(id = ifelse(str_detect(group, "B"), str_replace(group, "B", ""), group),
+         id = case_when(
+    id %in% c(1,3,5) ~ "G1",
+    id %in% c(7) ~ "G2",
+    id %in% c(13, 19) ~ "G3",
+    id %in% c(22) ~ "G4",
+    id %in% c(28) ~ "G5",
+    id %in% c(49, 84) ~ "G6",
+    id %in% c(29, 30) ~ "G7",
+    str_detect(id, "G") ~ id
+  ),
+  id = as.factor(id)) -> angle.params
+
+angle.params %>% 
+  filter(., model != "CP") %>% 
+  ggplot(., aes(x = model, y = mu)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.1, aes(color = id)) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  geom_hline(yintercept = cp.mu, color = my.cols1[4], size = 1) +
+  labs(x = "Pooling scenario") +
+  theme_classic() +
+  theme(legend.position = "none") -> muplot
+
+angle.params %>% 
+  filter(., model != "CP") %>% 
+  ggplot(., aes(x = model, y = rho)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.1, aes(color = id)) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  geom_hline(yintercept = cp.rho, color = my.cols1[4], size = 1) +
+  labs(x = "Pooling scenario") +
+  theme_classic() +
+  theme(legend.position = "none") -> rhoplot
+
+cir.legend <- get_legend(angle.params %>% 
+  filter(., model != "CP") %>% 
+  ggplot(., aes(x = model, y = rho)) +
+  geom_boxplot() +
+  geom_jitter(width = 0.1, aes(color = id)) +
+  scale_color_manual(values=sgroup_col, drop=FALSE) +
+  guides(color = guide_legend(title = "Social \n group")) +
+  geom_hline(yintercept = cp.rho, color = my.cols1[4], size = 1) +
+  labs(x = "Pooling scenario") +
+  theme_classic())
+
+A <- plot_grid(muplot, rhoplot, nrow = 1, labels = c("A)", "B)"), label_size = 10)
+plot_grid(A, cir.legend, nrow = 1, rel_widths = c(1, 0.1))
+
+ggsave("Ch2_distributions/Figures/Figure6.png")
+```

### 2022-01-10 Ch2_distributions/Ch2_angle_fits.R
This is on the markdown now.

@@ -13,25 +13,72 @@ library(CircStats)
 
 # Data ----------------------------------------------------
 # The script for this data is in the data-raw folder
-load("data/ptpl.rda")
+load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
+
+
+ptpl %>%
+  mutate(individual = paste0("B", id))%>%
+  dplyr::select(individual, sgroup, rel.angle, abs.angle) %>%
+  drop_na(individual, rel.angle) -> angles_df
+
 
 # Wrapped Cauchy fit
 
 ?dwrpcauchy
 
-#vector of angles in radians:
-
-ptpl %>%
-  drop_na(rel.angle) -> angle_data
-
 
 # Estimate for complete pooling
 
-mu0 <- circ.mean(angle_data$rel.angle)
-rho0 <- est.rho(angle_data$rel.angle)
-a <- wrpcauchy.ml(angle_data$rel.angle, mu0 = mu0, rho0 = rho0)
+mu0 <- circ.mean(angles_df$rel.angle)
+rho0 <- est.rho(angles_df$rel.angle)
+angle.params <- as.data.frame(wrpcauchy.ml(angles_df$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
+  mutate(model = "CP",
+         group = NA)
 
 
+# Partial pooling
+
+sgroups <- paste0("G", 1:7)
+
+
+
+for(i in 1:7){
+
+  sub_data <- angles_df %>%
+    drop_na(rel.angle) %>%
+    filter(., sgroup == sgroups[i])
+
+  mu0 <- circ.mean(sub_data$rel.angle)
+  rho0 <- est.rho(sub_data$rel.angle)
+  a <- as.data.frame(wrpcauchy.ml(sub_data$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
+    mutate(model = "PP",
+           group = sgroups[i])
+
+  angle.params <- rbind.data.frame(angle.params, a)
+
+}
+
+# No pooling
+
+individuals <- unique(angles_df$individual)
+
+
+
+for(i in 1:15){
+
+  sub_data <- angles_df %>%
+    drop_na(rel.angle) %>%
+    filter(., individual == individuals[i])
+
+  mu0 <- circ.mean(sub_data$rel.angle)
+  rho0 <- est.rho(sub_data$rel.angle)
[…]

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Actually changing the order of the figures.

@@
 scales::show_col(mod_col)
+```
+
+# Figure 1 - Descriptions of the data
+
+```{r fig.width=12, fig.height=4.5}
+ptpl %>%
+  drop_na(mpm) %>%
+  filter(mpm != 0) %>%
+  group_by(Bird_ID) %>%
+  add_tally() %>%
+  filter(n >= 30) -> nonzerompm
+
+# To know the number of speed data points for each individual
+# nonzerompm %>% group_by(Bird_ID) %>% count() %>% arrange(n)
+
+# To know the number of speed data points per interval category
+# nonzerompm %>% group_by(T_minutes) %>% count() %>% mutate(percent = n/nrow(nonzerompm))
+
+nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(individual, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = individual, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Individual bird tag",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "none") -> np_ints
+
+nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(sgroup, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Social group",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "none") -> pp_ints
+
+legend_row <- get_legend(nonzerompm %>%
+  mutate(individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  group_by(sgroup, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
+  geom_bar(stat = "identity") +
+  theme_classic() +
+  labs(x = "Individual bird tag",
+       y = "Number of intervals recorded") +
+  #scale_fill_viridis_d(option = "magma", direction = -1) +
+  guides(fill = guide_legend(title = "Time interval\n in minutes", nrow = 1)) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "bottom"))
+
+plot_row <- plot_grid(pp_ints, np_ints, nrow = 1, labels = c("C)", "D)"))
+#plot_grid(plot_row, legend_row, ncol = 1, rel_heights = c(1, 0.1))
 ```
@@
 
-```{r fig.width=12, fig.height=4.5}
-ptpl %>%
-  drop_na(mpm) %>%
-  filter(mpm != 0) %>%
-  group_by(Bird_ID) %>%
-  add_tally() %>%
-  filter(n >= 30) -> nonzerompm
-
-nonzerompm %>%
-  mutate(individual = paste0("B", Bird_ID),
-         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
-  group_by(individual, T_minutes) %>%
-  count() %>%
-  ggplot(aes(x = individual, y = n, fill = as.factor(T_minutes))) +
-  geom_bar(stat = "identity") +
-  theme_classic() +
-  labs(x = "Individual bird tag",
-       y = "Number of intervals recorded") +
-  #scale_fill_viridis_d(option = "magma", direction = -1) +
-  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
-  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
-  theme(legend.position = "none") -> np_ints
-
-nonzerompm %>%
-  mutate(individual = paste0("B", Bird_ID),
-         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
-  group_by(sgroup, T_minutes) %>%
-  count() %>%
-  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
-  geom_bar(stat = "identity") +
-  theme_classic() +
-  labs(x = "Social group",
-       y = "Number of intervals recorded") +
-  #scale_fill_viridis_d(option = "magma", direction = -1) +
-  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
-  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
-  theme(legend.position = "none") -> pp_ints
-
-legend_row <- get_legend(nonzerompm %>%
-  mutate(individual = paste0("B", Bird_ID),
-         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
-  group_by(sgroup, T_minutes) %>%
-  count() %>%
-  ggplot(aes(x = sgroup, y = n, fill = as.factor(T_minutes))) +
-  geom_bar(stat = "identity") +
-  theme_classic() +
-  labs(x = "Individual bird tag",
-       y = "Number of intervals recorded") +
-  #scale_fill_viridis_d(option = "magma", direction = -1) +
-  guides(fill = guide_legend(title = "Time interval\n in minutes", nrow = 1)) +
-  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
-  theme(legend.position = "bottom"))
-
-plot_row <- plot_grid(pp_ints, np_ints, nrow = 1, labels = c("C)", "D)"))
-#plot_grid(plot_row, legend_row, ncol = 1, rel_heights = c(1, 0.1))
+```{r eval=FALSE}
+# Getting some data for the results
+ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
+  dplyr::select(Bird_ID, burstn) %>% 
+  filter(., burstn >=2) %>% 
+  distinct() %>% #summary()
+  ggplot(., aes(x = Bird_ID, y = burstn)) + 
+  geom_boxplot()
+
 ```
@@
   dplyr::select(individual, sgroup, rel.angle, abs.angle) -> angles_df
+
+# Some info on the angles df
+
+angles_df %>% 
+  drop_na(rel.angle)
 ```

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Changing the order of the figures.

@@
 
+rawptpl <- ptpl
+
 ptpl %>%
@@
 
-```{r fig.width=12, fig.height=4.5}
+```{r Figure1, fig.width=12, fig.height=4.5}
 ptpl %>%
@@
   guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
-  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
-  theme(legend.position = "none") -> np_ints
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14))
+
+  #theme(legend.position = "none") -> np_ints
+
+# This is the information on the bursts and number of relocations per individual
+
+# ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
+#   dplyr::select(Bird_ID, burstn) %>% 
+#   filter(., burstn >= 2) %>% 
+#   distinct() %>% #summary()
+#   #group_by(., Bird_ID) %>% count() %>% arrange(n)
+#   ggplot(., aes(x = Bird_ID, y = burstn)) + 
+#   geom_violin() +
+#   geom_boxplot(width = 0.1)
+
+ggsave("Ch2_distributions/Figures/Figure1.png")
+```
+
+```{r eval = FALSE}
+
+# These are the plot and legend for the number of observations and intervals when we consider the data at the family level.
 
@@
 #ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
-```
-
-```{r eval=FALSE}
-# Getting some data for the results
-ptpl %>% group_by(burst) %>% add_tally(name = "burstn") %>% 
-  dplyr::select(Bird_ID, burstn) %>% 
-  filter(., burstn >=2) %>% 
-  distinct() %>% #summary()
-  ggplot(., aes(x = Bird_ID, y = burstn)) + 
-  geom_boxplot()
-
 ```

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Changing the order of figures.

@@
 
-```{r Figure1, fig.width=12, fig.height=4.5}
+```{r Figure1, fig.width=12, fig.height=5.5}
 ptpl %>%
@@
   #scale_fill_viridis_d(option = "magma", direction = -1) +
-  guides(fill = guide_legend(title = "Tracking interval\n in minutes")) +
-  scale_fill_manual(values = met.brewer("Hiroshige", n = 14))
+  guides(fill = guide_legend(title = "Tracking interval\n in minutes", nrow = 1)) +
+  scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
+  theme(legend.position = "top") -> np_ints
 
@@
 
+ptpl %>% 
+  drop_na(rel.angle) %>% 
+  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
+                          rel.angle * 180/pi + 360),
+         individual = paste0("B", Bird_ID),
+         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
+  ggplot(., aes(x = d.angle)) +
+  geom_histogram(color = "grey", fill = "grey") +
+  coord_polar(theta = "x", start = -pi/2, direction = -1) +
+  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
+  theme_minimal() +
+  theme(axis.title = element_blank(),
+        axis.text.y = element_blank(),
+        legend.position = "none") +
+  facet_wrap(~individual, nrow = 1) +
+  theme(axis.text = element_blank()) -> np_angles
+
+plot_grid(np_ints, np_angles, nrow = 2, rel_heights = c(1, 0.7), labels = c("A)", "B)"), label_size = 10)
+
 ggsave("Ch2_distributions/Figures/Figure1.png")
 ```
+
+Figure 1 - A)Breakdown of the time intervals in the available data for each individual tagged bird.
+The majority of relocation points are recorded at 15 or 30 minute intervals.
+However, the intervals between relocations can get up to 210 minutes.
+Each relocation estimates the position of the animal, and a minimum of two consecutive relocations are necessary to estimate a trajectory, direction, and velocity.
+B) Distribution of relative angles for each individual.
+Relative angles require a minimum of three consecutive relocations to estimate the change in direction.
 
@@
 
-# Figure 1 - Density plots for velocity
+# Figure 2 - Density plots for velocity
 
@@
 
-```{r Figure1col, fig.width=12, fig.height=4.5}
+```{r Figure2, fig.width=12, fig.height=4.5}
 
@@
 
-#ggsave2(filename = "Ch2_distributions/Figures/Figure1_color.png")
-```
-
-```{r Figure1, fig.height=9, fig.width=12}
+ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
+```
+
+```{r Figure1old, fig.height=9, fig.width=12, eval = FALSE}
 
@@
 
-Figure 1 - Kernel density estimates for the distribution of velocity data at different pooling levels, with the dark black density curve showing complete pooling.
+Figure 2 - Kernel density estimates for the distribution of velocity data at different pooling levels, with the dark black density curve showing complete pooling.
 A) Partial pooling representation of the data, where each curve displays the density of velocities across a social group.
@@
 Particular focus towards the tails, where certain individuals possess much higher densities for large velocities, something that gets dampened when considering pooled data for velocity densities.
-Panels C) and D) show the variation in number of observations and the length of time intervals recorded at the group and individual level.
 

### 2022-01-12 Ch2_distributions/Ch2_Figures.Rmd
Final

@@
   labs(x = "Individual bird tag",
-       y = "Number of intervals recorded") +
+       y = "Number of observations") +
   #scale_fill_viridis_d(option = "magma", direction = -1) +
@@
   scale_fill_manual(values = met.brewer("Hiroshige", n = 14)) +
-  theme(legend.position = "top") -> np_ints
+  theme(legend.position = "bottom") -> np_ints
 
@@
 box_color <- "blue"
-aval <- 0.6
+aval <- 0.7
 
@@
 
-#plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
+plot_grid(toprow, fig1leg, ncol = 1, rel_heights = c(1, 0.1))
 
@@
 
-# Figure 2 - Best fit parameters
+# Figure 3 - Best fit parameters
 
@@
 
-```{r Figure2, fig.height=9, fig.width=9}
+```{r Figure3, fig.height=9, fig.width=9}
 
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure2.png")
-```
-
-Figure 2 -Parameter space for best fitting models under the three pooling scenarios for 1000 bootstrap replicas.
+ggsave2(filename = "Ch2_distributions/Figures/Figure3.png")
+```
+
+Figure 3 -Parameter space for best fitting models under the three pooling scenarios for 1000 bootstrap replicas.
 Complete pooling approaches showed best fitting models under the lognormal (panel A.) and weibull (B.) distributions, but no models under a gamma distribution.
@@
 
-# Figure 3 - Percent Support
-
-```{r Figure3, fig.width=12, fig.height=5}
+# Figure 4 - Percent Support
+
+```{r Figure4, fig.width=12, fig.height=5}
 
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure3.png")
-
-```
-
-Figure 3 - Percent support for the different distribution models at the three pooling levels.
+ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
+
+```
+
+Figure 4 - Percent support for the different distribution models at the three pooling levels.
 Percent support is based on 1000 bootstrapped replicas for each scenario.
@@
 
-# Figure 4 - BIC units from best model
+# Figure 5 - BIC units from best model
 
@@
 
-```{r Figure4}
+```{r Figure5}
 
@@
 
-ggsave2(filename = "Ch2_distributions/Figures/Figure4.png")
-
-```
-
-Figure 4 - Distributions of $\Delta BIC$ values for models under the three different pooling scenarios.
+ggsave2(filename = "Ch2_distributions/Figures/Figure5.png")
+
+```
+
+Figure 5 - Distributions of $\Delta BIC$ values for models under the three different pooling scenarios.
 Best fit model is aligned at y = 0, thus in the case of the PP and NP scenario, the orange bar at y=0 is actually the $\Delta BIC$ value being zero for the multi-distribution model for all bootstraps.
@@
 
-# Figure 5 - angles
-
-```{r Figure5, fig.width=8, fig.height=6}
+# Figure 6 - angles
+
+```{r FigureNA, eval=FALSE, fig.width=8, fig.height=6}
 p1_angles <- ptpl %>% 
@@
 
-angles_df %>% 
-  drop_na(rel.angle)
+# angles_df %>% 
+#   drop_na(rel.angle) %>% group_by(individual) %>% count() %>% arrange(n)
 ```
@@
 
-```{r}
+```{r FitAngleDists}
 
@@
 ```
+
+Figure 6 - Parameters estimated for a wrapped Cauchy distribution for relative angles for individuals, and social groups across the different pooling levels.
+Color is used to describe the social groups to which individuals belong to.
+The orange line on both plots represents the parameter values estimated using all the data under the complete pooling approach.

### 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
initial tests

--- 2021-08-19 Ch1_movement_rates/Ch1_Appendix_A.Rmd
@@
 ---
-title: "Implications of animal movement rate variation in spatial patterns of seed dispersal"
+  title: "Mixture distribution data generation"
 author: "Javiera Rudolph"
-date: "8/12/2021"
+date: "1/20/2022"
 output:
@@
 
-Let's say there is a variation in animal movement rates, and it depends on multiple factors, such as size of the animal, breeding status, nesting, etc.
-So, it can also be seasonal.
-Since movement rates can't really be negative, we will use a lognormal distribution to describe this variation in movement rates among individuals from a population.
-
-Let $X_i$ be a positive random variable that is log-normally distributed $(i.e.
-X_i \sim Lognormal(\mu_i, \sigma_i^2)$ describing the distribution of movement rates for an animal population $i$.
-Such population's average movement rate being $\mu_i$ and the variance of their movement rates $\sigma_i^2$.
-These average movement rates can depend on homerange size for example, or seasonality (i.e.
-breeding, nesting, etc.).
-We will assume we have three different populations, where perhaps some of them have larger home ranges, creating more variance across movement rates.
-To make things a little easier, we will consider all populations have the same average movement rate $(i.e.
-\mu_1=\mu_1=\mu_3 = 1)$, but different standard deviation $(\sigma_1=0.3, \sigma_2=0.5, \sigma_3=0.5)$.
-Note that variance, $\sigma^2$ is the square of standard deviation, $\sigma$.
-We can visualize the distribution of movement rates for each of these populations:
-
-```{r}
-set.seed(98)
-
-av.mov.rate <- 1
-max.x <- 10
-
-mycols <- c("red", "green", "blue")
-#create density plots
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.3),
-      from=0, to=max.x,
-      col=mycols[1],
-      main = 'Log Normally distributed movement rates for three populations', #add title
-      ylab = 'Density', #change y-axis label
-      )
-
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=0.5), 
-      from=0, to=max.x,
-      col=mycols[2], add=TRUE)
-
-curve(dlnorm(x, meanlog=av.mov.rate, sdlog=1), 
-      from=0, to=max.x,
-      col=mycols[3], add=TRUE)
-
-#add legend
-legend("topright", legend=c("sdlog=.3", "sdlog=.5", "sdlog=1"),
-       col=mycols, lty=1, cex=1.2)
+```{r LoadFitData}
+load("Ch2_distributions/Ch2_fits.RData")
 ```
-
-Now, lets sample a movement rate, $m$, for 5 individuals $(i.e.
-j = 1, ...,5)$ from the first population $(i.e.
-m_{1,j} = m_{1,1}, ....., m_{1,5})$.
-We will simulate animal movement with a simple random walk, with movement length $l$ sampled from an exponential distribution, $l \sim exp(m_{i,j})$, and movement angle, $\theta$, from a uniform distribution, $\theta \sim U(0, 360)$.
-
-```{r}
-n.individuals <- 5
-m_1 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.3),3))
-m_2 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 0.5),3))
-m_3 <- sort(round(rlnorm(n.individuals, meanlog = av.mov.rate, sdlog = 1),3))
-```
-
-We can look at how those exponential distributions look for each of the individuals in those populations.
-Each curve describes the distribution of movement lengths for each of the five individuals in the population.
-Each panel represents one of the populations.
-
-```{r fig.width=12}
-
-par(mfrow=c(1,3))
-mycols <- rainbow(n.individuals, s=1)
-
-range <- c(-0.1,max.x+5)
-#create density plots
-#########################################################################
-# Fist population
-curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
-      from=range[1], to=range[2], 
-      col=mycols[1],
-      main = 'Distribution of movement lengths', #add title
-      ylab = 'Density', #change y-axis label
-      xlab = "x"
-      )
-for(i in 2:5){
-  curve(dexp(x, 1/m_1[i]), 
-        from=range[1], to=range[2],
-        col=mycols[i], add=TRUE)
-}
-
-#add legend
-legend("topright", legend= m_1,
-       col=mycols, lty=1, cex=1.2)
-#########################################################################
-# Second population
-curve(dexp(x, 1/m_2[1]), #notice rate for exponential is 1/movement rate.
-      from=range[1], to=range[2], 
-      col=mycols[1],
-      main = 'Distribution of movement lengths', #add title
-      ylab = 'Density', #change y-axis label
-      xlab = "x"
-      )
-for(i in 2:5){
-  curve(dexp(x, 1/m_2[i]), 
-        from=range[1], to=range[2],
-        col=mycols[i], add=TRUE)
-}
-
-#add legend
-legend("topright", legend= m_2,
-       col=mycols, lty=1, cex=1.2)
-
-#########################################################################
-# Third population
-curve(dexp(x, 1/m_3[1]), #notice rate for exponential is 1/movement rate.
-      from=range[1], to=range[2], 
-      col=mycols[1],
-      main = 'Distribution of movement lengths', #add title
-      ylab = 'Density', #change y-axis label
-      xlab = "x"
-      )
-for(i in 2:5){
-  curve(dexp(x, 1/m_3[i]), 
-        from=range[1], to=range[2],
-        col=mycols[i], add=TRUE)
-}
-
-#add legend
-legend("topright", legend= m_3,
-       col=mycols, lty=1, cex=1.2)
-```
-
-```{r eval=FALSE}
-t <- 100 # Number of time steps
-individual <- 5
-
-tru.rate <- m_1[individual] # In case I want to do scale 1/rate
-movedist <- rexp(t, rate = 1/tru.rate)
-angle <- runif(t, min = 0, max = 360)
-distx <- movedist*cos(angle)
-xloc <- c(0, cumsum(distx))
-disty <- movedist*sin(angle)
-yloc <- c(0, cumsum(disty))
-animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
-
-plot(x = xloc, y = yloc, col = mycols[individual], type = "l", main = paste("Rate", tru.rate))
-
-```
-
-```{r}
-sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
-  tru.rate <- round(prm, 3)
-  movedist <- rexp(t, rate = 1/tru.rate)
-  angle <- runif(t, min = 0, max = 360)
-  distx <- movedist*cos(angle)
-  xloc <- c(0, cumsum(distx))
-  disty <- movedist*sin(angle)
-  yloc <- c(0, cumsum(disty))
-  animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
-  if(plot.it == TRUE){
-    plot(x = xloc, y = yloc, type = "l", main = paste("Rate=",tru.rate))
-  }
-  if(return.data.frame == TRUE){
-    return(animalTraj)
-  }
-}
-```
-
-```{r eval=FALSE}
-par(mfrow=c(2,5))
-
-for(j in 1:individual){
-  sim_movement(m_1[j])}
-
-```
-
-```{r eval=FALSE}
-
-df <- sim_movement(m_1[1], plot.it = FALSE, return.data.frame = TRUE)
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc)) +
-  geom_path()
-
-```
-
-## Individual movement
-For each population, we can simulate the movement of every individual using a random walk.
-Colors correspond to the individuals in the plot above.
-Every individual is sorted based on their average movement rate, so that the first individuals, colored in red, correspond to the smallest movement rate.
-In contrast, individuals described by violet correspond to the individuals with the highest movement rate in that population.
-```{r eval=FALSE}
-nruns <- 3
-# Population1
-df <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-  a <- sim_movement(m_1[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
-    mutate(indiv = as.factor(j),
-           run = paste("r_", k))
-  df <- rbind.data.frame(df, a)
-}
-}
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  theme_bw()
-
-# Population2
-df <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-  a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
-    mutate(indiv = as.factor(j),
-           run = paste("r_", k))
-  df <- rbind.data.frame(df, a)
-}
-}
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  theme_bw()
-
-# Population3
-df <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-  a <- sim_movement(m_3[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
-    mutate(indiv = as.factor(j),
-           run = paste("r_", k))
-  df <- rbind.data.frame(df, a)
-}
-}
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  theme_bw()
-```
-
-```{r}
-nruns <- 3
-m.data <- data.frame(m_1, m_2, m_3)
-
-df <- NULL
-
-for(m in 1:3){
-  m.0 <- m.data[m]
-  for(j in 1:n.individuals){
-    for(k in 1:nruns){
-      a <- sim_movement(m.0[j,], plot.it = FALSE, return.data.frame = TRUE) %>% 
-        mutate(indiv = as.factor(j),
-               run = paste0("r_", k),
-               popu = paste0("p_",m))
-      df <- rbind.data.frame(df, a)
-    }
-  }
-}
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
-  facet_wrap(~popu) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  NULL
-```
-
-## Example individual
-### Simulate movement and seed droppings
-
-Now, we get the animals to disperse seeds.
-To do this, we combine seed gut retention times and animal movement.
-We can visualize this for one individual.
-Each simulation run consists of the animal disperser starting at point (0,0) and getting a number of seeds, each of which has an associated gut retention time $(grt \sim Gamma(4,5))$.
-The simulation run ends once all seeds have dropped.
-For that run, we calculate the average seed location by taking the average of x and y coordinates of all seeds.
-We also calculate seed dispersion as a measure of how close to each other or how scattered the seeds are for that run.
-```{r eval=FALSE}
-nseeds <- 20
-grt <- round(rgamma(nseeds, shape = 4, scale = 5))
-t.grt <- max(grt)
-
-animalTraj <- sim_movement(m_1[1], t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
-
-animalTraj %>% 
-  left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
-  mutate(disp = sqrt(xloc^2+yloc^2)) -> df
-
-df %>% 
-  drop_na(s.id) %>% 
-  mutate(xi = (mean(xloc)-xloc)^2,
-         yi = (mean(yloc)-yloc)^2) %>% 
-  summarise(x = mean(xloc),
-            y = mean(yloc),
-            av.disp = mean(disp),
-            se.disp = sd(disp)/sqrt(n()),
-            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
-
-# Calculate the mean location of seeds
-x_m <- mean(seed_loc$xloc)
-y_m <- mean(seed_loc$yloc)
-mean_dispersal <- mean(seed_loc$dispersal)
-se_dispersal <- sd(seed_loc$dispersal)/sqrt(length(seed_loc$dispersal))
-
-# Calculate seed dispersion
-xi <- (x_m - seed_loc$xloc)^2
-yi <- (y_m - seed_loc$yloc)^2
-seed_dispersion <- sum(sqrt(xi + yi))/length(seed_loc$time)
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc)) +
-  geom_path() +
-  geom_point(data = df %>% drop_na(s.id), 
-             aes(x = xloc, y = yloc)) +
-  geom_point(data = s.df,
-             aes(x = x, y = y), color = "Red") # Mean location of seeds
-
-```
-
-```{r}
-sim_seeds <- function(nseeds = 20, m.prms = NULL,...){
-  grt <- round(rgamma(nseeds, shape = 4, scale = 5))
-  t.grt <- max(grt)
-
-  df <- sim_movement(m.prms, t = t.grt, plot.it = FALSE, return.data.frame = TRUE)
-
-  df %>% 
-    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
-    mutate(disp = sqrt(xloc^2+yloc^2)) -> df
-
-  return(df)
-}
-
-summ_seeds <- function(df = NULL){
-  df %>% 
-  drop_na(s.id) %>% 
-  mutate(xi = (mean(xloc)-xloc)^2,
-         yi = (mean(yloc)-yloc)^2) %>% 
-  summarise(x = mean(xloc),
-            y = mean(yloc),
-            av.disp = mean(disp),
-            se.disp = sd(disp)/sqrt(n()),
-            dsprsn = sum(sqrt(xi+yi))/n()) -> s.df
-  return(s.df)
-}
-
-# a <- sim_seeds(m.prms = m_1[1])
-# summ_seeds(a)
-```
-
-```{r message=FALSE}
-nruns <- 100
-ex.i <- 1
-df <- NULL
-summ.df <- NULL
-
-for(j in 1:ex.i){
-  for(k in 1:nruns){
-    a <- sim_seeds(m.prms = m_1[j]) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    b <- summ_seeds(a) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    df <- rbind.data.frame(df, a) 
-    summ.df <- rbind.data.frame(summ.df, b) 
-}
-}
-```
-
-```{r}
-
-df %>% 
-  ggplot(., aes(x = xloc, y=yloc, 
-                group = run,
-                color = indiv)) +
-  # facet_wrap(~run) +
-  geom_path() +
-  scale_color_manual(values = mycols) +
-  geom_point(data = df %>% drop_na(s.id), 
-             aes(x = xloc, y = yloc)) +
-  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
-  theme_bw() +
-  labs(title = "Animal seed droppings", caption = "Lines show an individual's trajectory.\n Red dots show all seed droppings.\n Black dots show average location of seed per run") +
-  theme(legend.position = "none") -> p1
-# p1
-
-df %>% 
-  ggplot(., aes(x = xloc, y = yloc)) +
-  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
-  geom_bin2d() +
-  # geom_hex() +
-  # scale_fill_continuous(type = "viridis") +
-  scale_fill_gradient(low = "grey", high = "black") +
-  # geom_point(data = df %>% drop_na(s.id), 
-  #            aes(x = xloc, y = yloc), color = mycols[ex.i], alpha = 0.3) +
-  # geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  labs(title = "Density of animal movement") -> p2
-# p2
-
-cowplot::plot_grid(p1, p2)
-
-# summ.df %>% 
-#   ggplot(., aes(y = dsprsn)) +
-#   geom_boxplot()
-# 
-# summ.df %>% 
-#   ggplot(., aes(x = av.disp)) +
-#   geom_density(color = "blue") + # for the average dispersal per run
-#   geom_density(data = df %>% drop_na(s.id),
-#                  aes(x = disp)) + # for every seed
-#   theme_bw()
-```
-### Fit distribution function to seed dispersal data
-
-The end goal here is to understand how variation in animal movement rates can impact seed dispersal patterns.
-To get a metric of this seed dispersal, we fit a weibull distribution to the seed dispersal data generated by the previous simulation.
-Every run has 20 seeds, and we did this 100 times, thus we randomly sample 50 seeds to fit a Weibull distribution and get an approximated seed dispersal kernel.
-
-```{r message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
-# s.df <- df %>% drop_na(s.id)
-
-s.df <- df %>% drop_na(s.id) %>% 
-  sample_n(., 50)
-
-g <- fitdist(s.df$disp, distr = "weibull")
-```
-
-```{r}
-summary(g)
-plot(g)
-
-# library(MASS)
-# fitdistr(s.df$disp, densfun = "weibull")
-```
-
-# Simulation for population 1
-```{r message=FALSE}
-nruns <- 20
-
-df <- NULL
-summ.df <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-    a <- sim_seeds(m.prms = m_1[j]) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    b <- summ_seeds(a) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    df <- rbind.data.frame(df, a) 
-    summ.df <- rbind.data.frame(summ.df, b) 
-}
-}
-```
-
-Visualize animal movement and seed dispersal.
-It is kind of obvious, but individuals that move further away, also disperse seeds further away and scatter them more.
-Red points are every seed dispersed, black points show the average seed location per run.
-Each panel corresponds to one individual disperser.
-```{r}
-df %>% 
-  ggplot(., aes(x = xloc, y = yloc)) +
-  facet_wrap(~indiv) +
-  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
-  geom_bin2d() +
-  # geom_hex() +
-  # scale_fill_continuous(type = "viridis") +
-  scale_fill_gradient(low = "grey", high = "black") +
-  geom_point(data = df %>% drop_na(s.id),
-             aes(x = xloc, y = yloc), color = "red", alpha = 0.3) +
-  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
-  theme_bw()
-```
-
-Seed dispersal kernels produced by each individual.
-```{r}
-df %>% 
-  drop_na(s.id) %>% 
-  ggplot(., aes(x = disp, color = indiv)) +
-  geom_density() +
-  scale_color_manual(values = mycols) +
-  theme_bw()
-
-```
-
-Dispersion.
-We calculate dispersion for every simulated run.
-Every run means an individual disperser gets 20 seeds, they move until they drop all seeds.
-Then, dispersion measures how far away from each other every seed is.
-```{r}
-summ.df %>% 
-  ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Dispersion") +
-  theme_bw() +
-  theme(legend.position = "none") -> p1
-# p1
-
-summ.df %>% 
-  ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Average dispersal per run") +
-  theme_bw() +
-  theme(legend.position = "none") -> p2
-# p2
-
-plot_grid(p1, p2)
-```
-```{r eval=FALSE}
-# Sample once for estimating parameters
-s.df <- df %>% drop_na(s.id) %>%
-  group_by(indiv) %>%
-  sample_n(., 50)
-
-# s.df <- df %>% drop_na(s.id)
-
-weib.fits <- NULL
-
-for(i in 1:n.individuals){
-  dat <- s.df %>% 
-    filter(indiv == i)
-  #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-  g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                          est.scale = as.numeric(g$estimate[2]),
-                          loglik = g$loglik, indiv = i)
-  weib.fits <- rbind.data.frame(weib.fits, prms.weib)
-  # plot(g)
-}
-
-weib.fits
-```
-
-Bootstrapping?  
-Since there are hundreds or thousands of seeds getting dispersed between all the simulations, we will randomly sample seeds and fit a weibull distribution to generate the seed dispersal kernels.
-The visualization shows the parameters estimated for each bootstrap, for each individual (no pooling) or when we pool all the seed dispersal data (complete pooling).
-```{r}
-n.boots <- 10
-samp.size <- 30
-weib.boot <- NULL
-
-for(j in 1:n.boots){
-      s.df <- df %>% drop_na(s.id) %>%
-      group_by(indiv) %>%
-      sample_n(., samp.size)
-
-    # s.df <- df %>% drop_na(s.id)
-
-    weib.fits <- NULL
-
-    for(i in 1:n.individuals){
-      dat <- s.df %>% 
-        filter(indiv == i)
-      #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-      g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-      prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                              est.scale = as.numeric(g$estimate[2]),
-                              loglik = g$loglik, indiv = i)
-      weib.fits <- rbind.data.frame(weib.fits, prms.weib)
-      # plot(g)
-    }
-
-    weib.boot <- rbind.data.frame(weib.boot, weib.fits %>% mutate(boot = j))
-}
-
-# weib.boot
-```
-
-```{r eval=FALSE}
-
-weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
-  geom_violin() +
-  scale_color_manual(values = mycols) +
-  #geom_boxplot(width = 0.1) +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Shape") +
-  theme_bw() -> p1
-
-weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
-  geom_violin() +
-  scale_color_manual(values = mycols) +
-  #geom_boxplot(width = 0.1) +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Scale") +
-  theme_bw() -> p2
-
-plot_grid(p1, p2)
-```
-
-**What happens when we do complete pooling of the data instead of analyzing the variation by individuals.
-If instead we take all seed dispersal data and randomly sample seeds, and fit a Weibull kernel?** This is the comparisson between pooling or no pooling of seed dispersal data.
-
-```{r}
-weib.boot.pool <- NULL
-
-for(j in 1:n.boots){
-      s.df <- df %>% drop_na(s.id) %>%
-      sample_n(., samp.size)
-
-    g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
-
-    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                              est.scale = as.numeric(g$estimate[2]),
-                              loglik = g$loglik, indiv = 0)
-
-    weib.boot.pool <- rbind.data.frame(weib.boot.pool, prms.weib %>% mutate(boot = j))
-}
-
-```
-
-```{r}
-
-weib.boot %>% 
-  rbind.data.frame(., weib.boot.pool) -> weib.boot
-
-weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
-  geom_violin() +
-  scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.1) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Shape") +
-  theme_bw() -> p1
-# p1
-
-weib.boot %>% 
-  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
-  geom_violin() +
-  scale_color_manual(values = c("black", mycols)) +
-  #geom_boxplot(width = 0.1) +
-  # geom_point() +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Scale") +
-  theme_bw() -> p2
-
-plot_grid(p1, p2)
-```
-
-```{r}
-weib.curves <- NULL
-
-for(i in 1:5){
-  weib.boot %>% 
-  filter(indiv == i) -> a
-
-  b <- purrr::map(seq(1:nrow(a)), function(y)
-    stat_function(fun = dweibull, args = list(scale = a$est.scale[y], shape = a$est.shape[y]), color = mycols[i], alpha = 0.3))
-
-  weib.curves <- append(weib.curves, b)
-}
-
-weib.boot %>% 
-  filter(indiv == 0) -> c
-weib.curves.pool <- purrr::map(seq(1:nrow(a)), function(y)
-    stat_function(fun = dweibull, args = list(scale = c$est.scale[y], shape = c$est.shape[y]), color = "black", alpha = 0.8))
-
-# ggplot(data = data.frame(x = c(1, 60)), aes(x)) +
-#   weib.curves +
-#   ylab("Density") + xlab("Distance (m)") +
-#   theme_bw()  +
-#   theme(legend.position = c(0.7, 0.7),
-#         legend.title = element_blank()) 
-df %>%
-  drop_na(s.id) %>% 
-  ggplot(., aes(x = disp)) +
-  geom_histogram(aes(y = ..density..), fill = "grey") +
-  theme_bw() -> p
-# p
-# 
-# p +
-#   stat_function(fun = dweibull, args = list(scale = weib.boot$est.scale[1], shape = weib.boot$est.shape[1]), color = "red")
-
-p + 
-  weib.curves +
-  weib.curves.pool
-
-```
-
-This is only an example for the first population, but the overall idea is that if an individual has a larger movement rate, it moves more and this tends to translate into moving further away.
-As a consequence, the individuals with higher movement rates disperse seeds farther away and more scattered, in comparison to individuals with lower movement rates.
-Thus, the seed dispersal kernels produced by these individuals also show this trend, where individuals with higher movement rates disperse seeds further.
-This shows with the fatter tails of the kernels, evidenced by the larger scale parameters from fitted Weibull distributions.
-When we pool the seed dispersal data, we ignore individual differences in how each disperser moved the seeds, and estimate a single dispersal kernel sampling from all the seeds, regardless of who dispersed it.
-
-## Comparisson of seed dispersal kernels across populations  
-These populations all have the same average movement rates, but their variance is different.
-Since we are sampling individuals from these lognormally distributed populations, that means that the populations have similar averages, but in the first population individuals are very similar to each other, whereas in the third population, the individuals have movement rates more spread out.
-By having individuals more spread out, it means that not only are we getting individuals with much higher movement rates, we are also getting them with much lower movement rates as well.
-Depending on the population, we could also ask whether or not all populations follow this lognormal distribution.
-This is more of a behavior question, do all animals move at the same rate?
-meaning all very close to the average.
-Do most animals move at the same rate, except for some very few that like to explore and go far away?
-Perhaps this population needs a more skewed distribution with a longer tail.
-Or perhaps this relates to breeding seasons instead, or droughts.
-
-```{r}
-
-# For second population
-df2 <- NULL
-summ.df2 <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-    a <- sim_seeds(m.prms = m_2[j]) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    b <- summ_seeds(a) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    df2 <- rbind.data.frame(df2, a) 
-    summ.df2 <- rbind.data.frame(summ.df2, b) 
-  }
-}
-
-# #If we wanted to visualize 
-# summ.df2 %>% 
-#   ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
-#   geom_boxplot() +
-#   geom_point(color = "grey", alpha = 0.5) +
-#   labs(title = "Dispersion") +
-#   theme_bw() +
-#   theme(legend.position = "none") -> p1
-# # p1
-# 
-# summ.df2 %>% 
-#   ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
-#   geom_boxplot() +
-#   geom_point(color = "grey", alpha = 0.5) +
-#   labs(title = "Average dispersal per run") +
-#   theme_bw() +
-#   theme(legend.position = "none") -> p2
-# # p2
-# 
-# plot_grid(p1, p2)
-
-########################################################
-# Bootstrap for individuals
-weib.boot2 <- NULL
-
-for(j in 1:n.boots){
-  s.df <- df2 %>% drop_na(s.id) %>%
-    group_by(indiv) %>%
-    sample_n(., samp.size)
-
-  # s.df <- df %>% drop_na(s.id)
-
-  weib.fits <- NULL
-
-  for(i in 1:n.individuals){
-    dat <- s.df %>% 
-      filter(indiv == i)
-    #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-    g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                            est.scale = as.numeric(g$estimate[2]),
-                            loglik = g$loglik, indiv = i)
-    weib.fits <- rbind.data.frame(weib.fits, prms.weib)
-    # plot(g)
-  }
-
-  weib.boot2 <- rbind.data.frame(weib.boot2, weib.fits %>% mutate(boot = j))
-}
-
-# Pooled bootstrap
-weib.boot.pool2 <- NULL
-
-for(j in 1:n.boots){
-  s.df <- df2 %>% drop_na(s.id) %>%
-    sample_n(., samp.size)
-
-  g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
-
-  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                          est.scale = as.numeric(g$estimate[2]),
-                          loglik = g$loglik, indiv = 0)
-
-  weib.boot.pool2 <- rbind.data.frame(weib.boot.pool2, prms.weib %>% mutate(boot = j))
-}
-```
-
-```{r}
-
-# For Third population
-df3 <- NULL
-summ.df3 <- NULL
-
-for(j in 1:n.individuals){
-  for(k in 1:nruns){
-    a <- sim_seeds(m.prms = m_3[j]) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    b <- summ_seeds(a) %>% 
-      mutate(indiv = as.factor(j),
-             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))
-
-    df3 <- rbind.data.frame(df3, a) 
-    summ.df3 <- rbind.data.frame(summ.df3, b) 
-  }
-}
-
-# #If we wanted to visualize 
-# summ.df3 %>% 
-#   ggplot(., aes(y = dsprsn, x = indiv, color = indiv)) +
-#   geom_boxplot() +
-#   geom_point(color = "grey", alpha = 0.5) +
-#   labs(title = "Dispersion") +
-#   theme_bw() +
-#   theme(legend.position = "none") -> p1
-# # p1
-# 
-# summ.df3 %>% 
-#   ggplot(., aes(y = av.disp, x = indiv, color = indiv)) +
-#   geom_boxplot() +
-#   geom_point(color = "grey", alpha = 0.5) +
-#   labs(title = "Average dispersal per run") +
-#   theme_bw() +
-#   theme(legend.position = "none") -> p2
-# # p2
-# 
-# plot_grid(p1, p2)
-
-########################################################
-# Bootstrap for individuals
-weib.boot3 <- NULL
-
-for(j in 1:n.boots){
-  s.df <- df3 %>% drop_na(s.id) %>%
-    group_by(indiv) %>%
-    sample_n(., samp.size)
-
-  # s.df <- df %>% drop_na(s.id)
-
-  weib.fits <- NULL
-
-  for(i in 1:n.individuals){
-    dat <- s.df %>% 
-      filter(indiv == i)
-    #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
-    g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
-    prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                            est.scale = as.numeric(g$estimate[2]),
-                            loglik = g$loglik, indiv = i)
-    weib.fits <- rbind.data.frame(weib.fits, prms.weib)
-    # plot(g)
-  }
-
-  weib.boot3 <- rbind.data.frame(weib.boot3, weib.fits %>% mutate(boot = j))
-}
-
-# Pooled bootstrap
-weib.boot.pool3 <- NULL
-
-for(j in 1:n.boots){
-  s.df <- df3 %>% drop_na(s.id) %>%
-    sample_n(., samp.size)
-
-  g <- fitdistr(s.df$disp, densfun = "weibull", lower = c(0,0))
-
-  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
-                          est.scale = as.numeric(g$estimate[2]),
-                          loglik = g$loglik, indiv = 0)
-
-  weib.boot.pool3 <- rbind.data.frame(weib.boot.pool3, prms.weib %>% mutate(boot = j))
-}
-```
-
-```{r}
-
-weib.boot.pool %>% 
-  mutate(popu = 1) %>% 
-  bind_rows(., weib.boot.pool2 %>% 
-              mutate(popu = 2)) %>% 
-  bind_rows(., weib.boot.pool3 %>% 
-              mutate(popu = 3)) -> weib.boot.pool
-
-weib.boot.pool %>% 
-  ggplot(., aes(x = factor(popu), y = est.shape, color = factor(popu))) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  # geom_boxplot(width = 0.1) +
-  # geom_point(color = "grey", alpha = 0.5) +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Shape") +
-  theme_bw() -> p1
-# p1
-
-weib.boot.pool %>% 
-  ggplot(., aes(x = factor(popu), y = est.scale, color = factor(popu))) +
-  geom_violin() +
-  # scale_color_manual(values = c("black", mycols)) +
-  #geom_boxplot(width = 0.1) +
-  # geom_point() +
-  stat_summary(fun.data=mean_sdl, mult=1, 
-                 geom="pointrange", color="black") +
-  labs(title = "Scale") +
-  theme_bw() -> p2
-
-plot_grid(p1, p2)
-```
-```{r}
-summ.df %>% 
-  mutate(popu = 1) %>% 
-  bind_rows(summ.df2 %>% 
-              mutate(popu = 2)) %>% 
-  bind_rows(., summ.df3 %>% 
-              mutate(popu = 3)) %>% 
-  ggplot(., aes(y = dsprsn, x = factor(popu), color = factor(popu))) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Dispersion") +
-  theme_bw() +
-  theme(legend.position = "none") -> p1
-# p1
-
-summ.df %>% 
-  mutate(popu = 1) %>% 
-  bind_rows(summ.df2 %>% 
-              mutate(popu = 2)) %>% 
-  bind_rows(., summ.df3 %>% 
-              mutate(popu = 3)) %>% 
-  ggplot(., aes(y = av.disp, x = factor(popu), color = factor(popu))) +
-  geom_boxplot() +
-  geom_point(color = "grey", alpha = 0.5) +
-  labs(title = "Average dispersal per run") +
-  theme_bw() +
-  theme(legend.position = "none") -> p2
-# p2
-
-plot_grid(p1, p2)
-```

### 2022-01-20 Ch3_samplesize/Ch3_data_gen.R

@@ -1,0 +1,37 @@
+mus <- c(3,5,7,11,20,30)
+sigsqs <- c(1,1.5,1.5,2,2,3)
+xs <- seq(0,35,by=0.1)
+# Pyramid age structure
+pis <- c(0.4, 0.2,0.20,0.10,0.07,0.03)
+
+samp.size <- 50000
+all.samples <- rep(0,samp.size)
+for(i in 1:samp.size){
+
+  which.age <- sample(1:6, size=1, replace=TRUE, prob=pis)
+  all.samples[i] <- rnorm(n=1,mean=mus[which.age], sd=sigsqs[which.age])
+}
+
+
+par(mfrow=c(2,1))
+plot(xs,dnorm(x=xs, mean = mus[1], sd=1), type ="l", col="gray",xlab="Trait distribution per age class", ylab="Density")
+points(xs,dnorm(x=xs, mean = mus[2], sd=sigsqs[2]), type ="l", col="gray")
+points(xs,dnorm(x=xs, mean = mus[3], sd=sigsqs[3]), type ="l", col="gray")
+points(xs,dnorm(x=xs, mean = mus[4], sd=sigsqs[4]), type ="l", col="gray")
+points(xs,dnorm(x=xs, mean = mus[5], sd=sigsqs[5]), type ="l", col="gray")
+points(xs,dnorm(x=xs, mean = mus[6], sd=sigsqs[6]), type ="l", col="gray")
+
+hist(all.samples, main= paste0("Sample from proportions 0.4, 0.2,0.20,0.15,0.05"))
+
+# JAVI - using a lognormal
+
+meanlogs <- c(1, 1.5, 2, 2.5)
+sdlogs <- c(0.5, 0.3, 1, 0.75)
+xs <- seq(0,10, by = 0.1)
+
+
+plot(xs, dlnorm(x = xs, meanlog = meanlogs[1], sdlog = sdlogs[1]), type = "l", col = "grey", ylab = "Density")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[2], sdlog = sdlogs[2]), type = "l", col = "red")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[3], sdlog = sdlogs[3]), type = "l", col = "blue")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[4], sdlog = sdlogs[4]), type = "l", col = "green")
+

### 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
Working on parameters for simulation

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
-knitr::opts_chunk$set(fig.width=12, fig.height=6)
+#knitr::opts_chunk$set(fig.width=12, fig.height=6)
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 ```
@@
 ```
+
+Thinking that to parameterize the distributions for the simulation in Ch3, I could use the fits from Ch2 under the PP model with the lognormal distribution:
+
+```{r}
+# Some theme stuff
+
+library(MetBrewer)
+
+sgroup_col <- met.brewer("Tiepolo", n = 7)
+aval <- 0.3
+
+figx.theme <- theme_bw() +
+  theme(legend.position = "right",
+        axis.title = element_text(size = 8))
+
+# Select only the PP lnorm data
+pp.boot.fits %>%
+  #filter(., dBIC == 0) %>% 
+  filter(., dist == "lnorm") %>% 
+  dplyr::select(group, boot, estimate, param, dist) %>% 
+  pivot_wider(names_from = param, values_from = estimate) %>% 
+  mutate(group = as.factor(group)) -> lnpp.params
+
+lnpp.params %>% 
+  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
+    geom_point(alpha = aval) +
+    scale_color_manual(values=sgroup_col, drop=FALSE) +
+    lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
+    labs(subtitle = "PP - lnorm") +
+    figx.theme +
+  guides(color = guide_legend(title = "Group", override.aes = list(alpha = 1, size = 5)))
+
+```
+
+```{r}
+# Use the parameters from the figure above to simulate data?
+
+lnpp.params %>% 
+  group_by(group) %>% 
+  summarise(meanlogs = median(meanlog),
+            sdlogs = median(sdlog)) -> logparams
+
+meanlogs <- logparams$meanlogs
+sdlogs <- logparams$sdlogs
+
+density_curves <- purrr::map(1:7, function(y) stat_function(fun = dlnorm,
+                                                            args = list(meanlog = meanlogs[y], sdlog = sdlogs[y]),
+                                                            color = sgroup_col[y]))
+
+ggplot() +
+  density_curves +
+  figx.theme +
+  lims(x = c(0, 30), y = c(0, 0.2))
+
+```
+
+Using base R
+
+```{r}
+meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
+sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)
+
+xs <- seq(0,20, by = 0.1)
+
+par(mfrow=c(2,1))
+plot(xs, dlnorm(x = xs, meanlog = meanlogs[1], sdlog = sdlogs[1]), type = "l", col = "grey", ylab = "Density")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[2], sdlog = sdlogs[2]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[3], sdlog = sdlogs[3]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[4], sdlog = sdlogs[4]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[5], sdlog = sdlogs[5]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[6], sdlog = sdlogs[6]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[7], sdlog = sdlogs[7]), type = "l", col = "grey")
+
+```

### 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
Making the mixed distribution with parameters from the PP lnorm data in Ch2

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
-#knitr::opts_chunk$set(fig.width=12, fig.height=6)
+knitr::opts_chunk$set(fig.width=6, fig.height=4)
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
@@
 
-```{r}
+```{r fig.height=12, fig.width=12}
 meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
 sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)
+
+samepis <- 1/7
+pis <- rep(samepis, 7)
+
+samp.size <- 50000
+all.samples <- rep(0,samp.size)
+for(i in 1:samp.size){
+
+  which.group <- sample(1:7, size=1, replace=TRUE, prob=pis)
+  all.samples[i] <- rlnorm(n=1,mean=meanlogs[which.group], sd=sdlogs[which.group])
+}
 
@@
 
+hist(all.samples, main= paste0("Sample"))
+
 ```

### 2022-01-20 Ch3_samplesize/Ch3_data_gen.R

@@ -25,13 +25,30 @@ hist(all.samples, main= paste0("Sample from proportions 0.4, 0.2,0.20,0.15,0.05"
 
 # JAVI - using a lognormal
 
-meanlogs <- c(1, 1.5, 2, 2.5)
-sdlogs <- c(0.5, 0.3, 1, 0.75)
-xs <- seq(0,10, by = 0.1)
+meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
+sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)
+
+samepis <- 1/7
+pis <- rep(samepis, 7)
 
 
+samp.size <- 50000
+all.samples <- rep(0,samp.size)
+for(i in 1:samp.size){
+
+  which.group <- sample(1:7, size=1, replace=TRUE, prob=pis)
+  all.samples[i] <- rlnorm(n=1,mean=meanlogs[which.group], sd=sdlogs[which.group])
+}
+
+xs <- seq(0,20, by = 0.1)
+
+par(mfrow=c(2,1))
 plot(xs, dlnorm(x = xs, meanlog = meanlogs[1], sdlog = sdlogs[1]), type = "l", col = "grey", ylab = "Density")
-points(xs, dlnorm(x = xs, meanlog = meanlogs[2], sdlog = sdlogs[2]), type = "l", col = "red")
-points(xs, dlnorm(x = xs, meanlog = meanlogs[3], sdlog = sdlogs[3]), type = "l", col = "blue")
-points(xs, dlnorm(x = xs, meanlog = meanlogs[4], sdlog = sdlogs[4]), type = "l", col = "green")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[2], sdlog = sdlogs[2]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[3], sdlog = sdlogs[3]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[4], sdlog = sdlogs[4]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[5], sdlog = sdlogs[5]), type = "l", col = "grey")
+points(xs, dlnorm(x = xs, meanlog = meanlogs[6], sdlog = sdlogs[6]), type = "l", col = "grey")
[…]

### 2022-02-04 Ch3_samplesize/ideafeb4.Rmd
Following my instincts here

---
title: "Mixture distribution data generation"
author: "Javiera Rudolph"
date: "1/20/2022"
output:
  html_document:
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(Hmisc)
```

Q: What type of sampling scheme gives the highest probability of recovering the true distribution of long distance seed dispersal events?

In the previous two chapters we have set the stage to show that individual and social group variation matter, they have consequences for the seed dispersal services that these animals provide. In particular, we showed that when we include individual heterogeneity in animal movement, then frugivore-generated seed dispersal kernels have fatter tails, which means a larger number of long-distance dispersal events.

Based on that background, what we will be trying to show here is which sampling scheme is better to recover the highest number of long-distance dispersal events. We will do this by changing the number of individuals sampled versus the length of the time series or number of observations, to which we will evaluate the resulting seed dispersal kernel tails.

### 2022-02-04 Ch3_samplesize/scratch.R

@@ -1,0 +1,63 @@
+# Compare to the data I'm trying to recreate
+load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
+
+realdist <- ptpl %>% drop_na(rel.angle) %>% transmute(realdist = dist/dt*900) %>% pull(realdist)
+hist(realdist)
+summary(realdist)
+
+
+
+# DATA comparison -------------------------
+## Get the data in -----------------------
+load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
+
+
+ptpl %>%
+  filter(dist != 0) %>%
+  drop_na(sgroup) %>%
+  group_by(id) %>%
+  add_tally() %>%
+  filter(n >= 30) %>%
+  ungroup() %>%
+  mutate(stplen = dist/(dt/900)) %>%
+  dplyr::select(., dist, stplen, id, sgroup) -> ptpl
+
+## Get some summary tables -------
+# Overall summary of the step lengths
+summary(ptpl$stplen)
+
+ptpl %>%
+  group_by(sgroup, id) %>%
+  nest() %>%
+  arrange(sgroup) %>%
+  mutate(nobs = map_int(data, .f = nrow),
+         summ = map(data, summary),
+         stplen = map(data, pull, stplen)) %>%
+  mutate(model = map(stplen, fitdist, distr = "lnorm")) -> a
+
+
+
+ptpl %>%
+  ggplot(., aes(x = stplen, group = id)) +
+  facet_wrap(~sgroup) +
+  geom_line(stat = "density") +
+  theme_minimal()
+
+load("Ch2_distributions/Ch2_fits.RData")
+
+## lnorm fits to data --------------------------
+
+reg_fits_info %>%
+  filter(., dist=="lnorm" & model == "NP") %>%
+  dplyr::select(estimate, param, ID) %>%
+  pivot_wider(names_from = param, values_from = estimate) %>%
+  mutate(color =MetBrewer::met.brewer("Hiroshige", n=12)) -> data_prms
+
+lnorm_data_dens <- purrr::map(1:12, function(y) stat_function(fun = dlnorm,
+                                                              args = list(meanlog = data_prms$meanlog[y], sdlog = data_prms$sdlog[y]),
+                                                              color = data_prms$color[y]))
+ggplot() +
+  lnorm_data_dens +
+  theme_minimal() +
+  lims(x = c(0, 50)) -> data_dens_plot
+

### 2022-02-04 Ch3_samplesize/ideafeb4.Rmd
Progress on my ideas.

@@
 We will do this by changing the number of individuals sampled versus the length of the time series or number of observations, to which we will evaluate the resulting seed dispersal kernel tails.
+
+**What is the mathematical framework for this simulation?**  
+First, we simulate a 'master' dataset which we assume to be the 'true' process
+
+1.    Define the process used to generate animal movement  
+2.    Define how to incorporate social group and individual variation  
+3.    Establish any potential movement boundaries (max of 3000m in 15min from the data)  
+4.    Generate seed dispersal kernels  
+5.    Use Extreme values approach to describe the tail of seed dispersal kernels
+
+Then, we design a sampling scheme.   
+My hypothesis is that there will be a critical threshold, after which increasing the number of observations per individual won't matter to understand the tail of dispersal kernels, and we will benefit from sampling more individuals, instead of sampling fewer individuals with more observations.
+
+1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations?*  
+2.

### 2022-02-04 Ch3_samplesize/ideafeb4.Rmd
Brainstorming

@@
 ---
-title: "Mixture distribution data generation"
+title: "Brainstorm for Ch3"
 author: "Javiera Rudolph"
-date: "1/20/2022"
+date: "2/4/2022"
 output:
@@
 
-1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations?*  
-2.
+1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations? of individuals or the seeds?*  
+    *       We are trying to answer if it is better to sample 3 individuals and follow them for months, getting 100s of observations for each individual.  
+    *       OR if it is better that we sample 10 or 20 individuals, and follow them for a couple of weeks only and get maybe only 30, 50 observations for each.
+
+      **My guess, is that it will be better to sample more individuals for shorter time frames, because the question is trying to capture these long distance movements which may vary by individual.**
+
+2.   We use

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
Taking a different approach, so deleted previous lognormals that came from Ch2

--- 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
-knitr::opts_chunk$set(fig.width=12, fig.height=6)
+knitr::opts_chunk$set(fig.width=6, fig.height=4)
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 ```
@@
 ```
-
-```{r LoadFitData}
-load("Ch2_distributions/Ch2_fits.RData")
-```

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
Densities for the social group.

@@
 library(cowplot)
-library(fitdistrplus)
-library(Hmisc)
 ```
+
+```{r}
+set.seed(20220214)
+
+## Functions ----------------------------------------------------
+# Building this function so that we get the parameters for a desired mean and standard deviation using a lognormal distribution
+desired_mean_sd <- function(mean, sd){
+
+  mu <- log(mean*2/(sqrt(mean*2+sd*2)))
+  sigsq <- log(1+(sd*2/mean*2))
+
+  return(data.frame(mu = mu, sigsq = sigsq))
+}
+
+exp.val <- function(mu, sigsq){
+  exp(mu + sqrt(sigsq))
+}
+```
+
+We use a mixture model to simulate step lengths for animal movement using a lognormal distribution for step length.
+We incorporate two levels of heterogeneity by including social group and individual variation.
+The assumption follows that individuals belonging to the same group will follow a similar movement but with a different variance.
+
+We use a mixture model since this is a common approach to characterize subpopulations, and the mixture distribution is sort of a weighted average for the contributions of each subpopulation to the general population.
+$$ 
+f(x) = \sum_{i=1}^{n} \pi_{i} f_i(x)
+$$
+Where $\pi_i$ represents the weight associated to social group $i$ and $f_i(x)$ is the distribution describing the step lengths of the social group.
+We incorporate individual variation by describing the distribution of social group step lengths $f_i(x)$ as a mixture as well.
+
+$$
+f_i(x) = \sum_{j=1}^s w_j g_j(x)
+$$
+
+We assume that each individual has the same weight (i.e., $w_1 = w_2 = \cdots = w_s$), and that the proportion of individuals in each social group determines the weight for the social group (i.e., $\pi_i$) relative to the overall population.
+
+For our toy model, we assume four social groups ($i=4$), where each group has between 4-7 individuals assigned randomly, with a total of 22 individuals in our simulated population.
+
+```{r echo=TRUE}
+# MIXTURE MODEL --------------------------------------------------
+## Mixture proportions ----------------------------------------
+# We assume four categories of individuals with increasing movement.
+
+ngroup <- 4
+npergroup <- sample(3:7, ngroup, replace = TRUE) 
+npop <- sum(npergroup)
+
+pis <- npergroup/npop
+#sum(pis)
+#hist(pis)
+
+## Mixture components --------------------------------------
+### Each of these curves represents the average of the social group.
+# Since movement lengths are only positive, we use a lognormal distribution to describe them
+
+# CASE1
+
+pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))
+
+# Special case I am considering where for each category the mean doubles, and then sd=mean*0.6
+# pars <- desired_mean_sd(mean = c(150, 300, 600, 1200), sd = c(90, 180, 360, 720))
+
+mus <- pars$mu
+sigsqs <- pars$sigsq
+dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
+
+### PLOT the mixture components -------------------------------
+lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
+                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
+                              color = dens_cols[y], size=1))
+ggplot() +
+  lnorm_densities +
+  theme_minimal() +
+  labs(y = "Density") +
+  lims(x = c(0, 150)) -> densities_plot
+densities_plot
+
+```
+
+```{r}
+
+# SAMPLING --------------------------------------------------------------
+
+samp.size <- 50000
+all.samples <- rep(0,samp.size)
+for(i in 1:samp.size){
+
+  which.cat <- sample(1:4, size=1, replace=TRUE, prob=pis)
+  all.samples[i] <- rlnorm(n=1,meanlog=mus[which.cat], sdlog=sigsqs[which.cat])
+}
+
+## PLOT the samples ---------------------------------------------
+# This is our f(x) from the main text
+data.tail <- data.frame(values = all.samples, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)
+head(data.tail)
+
+ggplot(data.frame(all.samples), aes(x = all.samples)) +
+  geom_histogram(bins = 100) +
+  geom_point(data = data.tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
+  labs(y = "Frequency", x = "Distance") +
+  theme_minimal() -> sampleshist
+
+# VIZ -----------------------------------
+plot_grid(densities_plot, sampleshist, nrow=2, labels="AUTO")
+#ggsave("Ch3_samplesize/TestFig.png")
+
+summary(all.samples)
+
+```

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
Code for simulating individual densities is done

@@
 
-```{r echo=TRUE}
+```{r echo=TRUE, fig.width=9, fig.height=4}
 # MIXTURE MODEL --------------------------------------------------
@@
 # CASE1
-
-pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))
+means <- c(160, 300, 600, 1000)
+sds <- c(90, 120, 160, 200)
 
 # Special case I am considering where for each category the mean doubles, and then sd=mean*0.6
-# pars <- desired_mean_sd(mean = c(150, 300, 600, 1200), sd = c(90, 180, 360, 720))
+# means <- c(150, 300, 600, 1200)
+# sds <- c(90, 180, 360, 720)
+
+pars <- desired_mean_sd(mean = means, sd = sds)
 
@@
   labs(y = "Density") +
-  lims(x = c(0, 150)) -> densities_plot
+  lims(x = c(0, 150)) +
+  #scale_y_sqrt(limits = c(0, NA)) +
+  NULL -> densities_plot
 densities_plot
@@
 
+Now, let's simulate the individuals
+
 ```{r}
+pars_df <- data.frame(sgroup = 1:ngroup, npergroup = npergroup, pis = pis, mu = mus, sigsqs = sigsqs, mean = means, sd = sds)
+#pars_df
+
+```
+
+Thinking out loud: Let's make the variation for the individuals normal.
+So, we multiply the variance for that percentage and then estimate it?
+The mu stays the same, we do a sample from the standard normal?
+Or do we follow percentages.
+Since we have a different number of individuals per group, I'd go with the standard normal approach.
+
+```{r}
+
+indiv_pars <- data.frame()
+
+for(i in 1:ngroup){
+  nindiv <- pars_df$npergroup[i]
+  indiv.means <- rep(pars_df$mean[i], nindiv)
+  indiv.var <- rnorm(nindiv, sd = 0.3)
+  indiv.sds <- pars_df$sd[i] + (pars_df$sd[i]*indiv.var)
+
+  indiv.pars <- desired_mean_sd(mean = indiv.means, sd = indiv.sds)
+
+  sgroup <- pars_df$sgroup[i]
+  id <- paste0("G", sgroup, ".I", 1:nindiv)
+
+  a <- cbind(id, sgroup, indiv.means, indiv.var, indiv.sds, indiv.pars)
+
+  indiv_pars <- rbind.data.frame(indiv_pars, a)
+
+}
+
+```
+
+```{r}
+# make the curves for each individual
+
+indiv_densities <- purrr::map(1:nrow(indiv_pars), function(y) stat_function(fun = dlnorm,
+                                                             args = list(meanlog = indiv_pars$mu[y], sdlog = indiv_pars$sigsq[y]),
+                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.5))
+ggplot() +
+  indiv_densities +
+  lnorm_densities +
+  theme_minimal() +
+  labs(y = "Density") +
+  lims(x = c(0, 150)) +
+  #scale_y_sqrt(limits = c(0, NA)) +
+  NULL -> indiv_densities
+indiv_densities
+
+```
+
+```{r eval=FALSE}
 

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
individual densities

@@
 ### PLOT the mixture components -------------------------------
-lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
+lnorm_densities <- purrr::map(1:ngroup, function(y) stat_function(fun = dlnorm,
                                                              args = list(meanlog = mus[y], sdlog = sigsqs[y]),
@@
                                                              args = list(meanlog = indiv_pars$mu[y], sdlog = indiv_pars$sigsq[y]),
-                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.5))
+                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.3))
 ggplot() +

### 2022-02-15 Ch3_samplesize/mess/Ch3_toymodel_sgonly.Rmd
Trying to tackle the mess. Moved things around and renamed.

---
title: "Toy Model"
author: "Javiera Rudolph"
date: "1/20/2022"
output:
  html_document:
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=6, fig.height=4)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE}
set.seed(20220201)

library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
```

```{r Functions}
## Functions ----------------------------------------------------
# Building this function so that we get the parameters for a desired mean and standard deviation.
desired_mean_sd <- function(mean, sd){

  mu <- log(mean*2/(sqrt(mean*2+sd*2)))
  sigsq <- log(1+(sd*2/mean*2))

  return(data.frame(mu = mu, sigsq = sigsq))
}

exp.val <- function(mu, sigsq){
  exp(mu + sqrt(sigsq))
}

### Lomax functions --------------------------

lomax.pdf <- function(x,alpha,k, log.scale=FALSE){

  if(log.scale==FALSE){out <- (k/(alpha+x))*(alpha/(alpha+x))^k
  }else{
    out <- log(k) + k*log(alpha) - (k+1)*log(alpha+x)
  }

  return(out)
}

lomax.cdf <- function(x,alpha,k){

  return(1-(alpha/(alpha+x))^k)

}

ft.nllike <- function(guess=init.betas, designmat=designmat,Y=Y){

  Xbeta         <- designmat%*%guess
  alphas        <- exp(Xbeta) # because alpha = ln(X*betas)
  n             <- length(Y)
  sumlogapy     <- sum(log(alphas+Y))
  k.hat         <- n/(sumlogapy - sum(Xbeta))
  lnft.yis     <- lomax.pdf(x=Y, alpha=alphas,k=k.hat,log.scale=TRUE)
  lnL           <- sum(lnft.yis)
  nll           <- -lnL
  return(nll)
}

lomax.glm <- function(formula=~1, my.dataf, response){

  Y           <- response
  n           <- length(Y)
  designmat   <- model.matrix(formula, data=my.dataf)
  nbetas      <- ncol(designmat)
  init.betas  <- rep(1.5,nbetas)

  opt.out <- optim(par=init.betas, fn=ft.nllike, method="BFGS",
                   designmat=designmat, Y=Y)

  mles          <- opt.out$par
  nll.hat       <- opt.out$value
  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
  Xbeta.hat     <- designmat%*%mles
  alphas.hat    <- exp(Xbeta.hat)
  sumlogapy.hat <- sum(log(alphas.hat+Y))
  k.hat         <- n/(sumlogapy.hat - sum(Xbeta.hat))

  out.list <- list(opt.out = opt.out, designmat=designmat,Y=Y, mles=mles, nll.hat=nll.hat, BIC.mod = BIC.mod,
                   alphas.hat=alphas.hat, k.hat=k.hat,data=my.dataf)

  return(out.list)

}

# Probability that it is greater.
lomax.st <- function(x=x, alpha=alpha, k=k){
  out <- alpha/(alpha+x)
  return(out^k)
}

# calculate the mean of the fit

lomax.mean <- function(alpha=alpha, k=k){
  return(alpha/(k+1))
}

# Assess the fit using model quantiles to make a qqplot
lomax.quantile <- function(alpha, k, p){
  return(alpha*(((1-p)^(1/k))-1))
}

```

```{r}

#########  playing with a simulation trial to assess how good hat(P(X>x)) is
#########  assuming data came from a lomax (when in fact it didn't)

## Mixture proportions ----------------------------------------
# We assume four categories of individuals with increasing movement.
pis <- c( 0.1, 0.2, 0.3, 0.4)

pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))

mus <- pars$mu
sigsqs <- pars$sigsq
dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
                              color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) -> densities_plot
densities_plot

```

```{r}

# Create the TRUE data

samp.size <- 50000
all.samples <- rep(0,samp.size)
categ <- rep(0,samp.size)

for(i in 1:samp.size){

  which.cat <- sample(1:4, size=1, replace=TRUE, prob=pis)
  all.samples[i] <- rlnorm(n=1,meanlog=mus[which.cat], sdlog=sigsqs[which.cat])
  categ[i] <- which.cat
}

sim.df <- data.frame(dists= all.samples, categ=categ)
```

```{r}
# Now the experiments and sampling

samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
num.ns <- length(samp.sizes)
q.tests <- c(100, 250,500,1000)
num.qs <- length(q.tests)

all.sampsizes <- rep(samp.sizes,each=num.qs)
all.qtests <- rep(q.tests,num.ns)
ntests <- length(all.sampsizes)

cdfs.hat <- rep(0, ntests)

for(i in 1:ntests){

      ith.n   <- all.sampsizes[i]
      ith.samples <- data.frame(x = sample(all.samples, ith.n))
      mod1 <- lomax.glm(formula = ~1, my.dataf = ith.samples, response = ith.samples$x)
      ith.a <- mod1$alphas.hat[1]
      ith.k <- mod1$k.hat

      ith.q <- all.qtests[i]
      ith.cdf <- 1- lomax.cdf(x = ith.q, alpha = ith.a, k = ith.k)
      cdfs.hat[i] <- ith.cdf

}

true.cdfs <- rep(0,num.qs)
for(i in 1:num.qs){

  iq <- q.tests[i]

  true.cdfs[i] <- sum(all.samples>iq)/length(all.samples)

}

all.true.cdfs <- rep(true.cdfs,num.ns)

sim.test.df <- data.frame(all.sampsizes=all.sampsizes, all.qtests=all.qtests,cdfs.hat=cdfs.hat,
                          true.cdfs = all.true.cdfs)

```

### 2022-02-15 Ch3_samplesize/mess/Datagen_viz.Rmd
Trying to tackle the mess. Moved things around and renamed.

--- 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
@@
 
-For our toy model, we assume four social groups ($i=4$), where each group has between 4-7 individuals assigned randomly, with a total of 22 individuals in our simulated population.
+For our toy model, we assume four social groups ($i=4$), where each group has between 4-7 individuals assigned randomly.
+
+Initially, we only consider the four groups:
 
@@
 
-Now, let's simulate the individuals
+We simulate the data coming from this process and then use different sample sizes and thresholds to estimate the tail. 
+I think this means that increasing sample size is fine, but it is actually selecting low thresholds that creates the most variation in the estimates.
+
+```{r}
+load("Ch3_samplesize/resamp.RData")
+# Keep in mind that the pis for this are different and chosen randomly from the toymodel script. 
+# pis <- c( 0.1, 0.2, 0.3, 0.4)
+
+resamp.df %>% 
+  mutate(diff = (cdfs.hat-true.cdfs), 
+         sampsize = factor(all.sampsizes),
+         tailthresh = factor(all.qtests))-> resamp.df
+
+resamp.df %>% 
+  #filter(., all.sampsizes == "80") %>%  
+  ggplot(., aes(x = sampsize, y = diff, color = tailthresh)) +
+  geom_boxplot() +
+  labs(x = "Sample size", y = "Estimated/True") +
+  #scale_y_log10() +
+  theme_minimal()
+
+```
+
+We want to know how "off" the estimates are from the truth.
+```{r}
+resamp.df %>% 
+  group_by(sampsize, tailthresh) %>% 
+  summarise(est.bias = signif(mean(diff), 3))
+
+resamp.df %>% 
+  group_by(sampsize, tailthresh) %>% 
+  summarise(est.bias = signif(mean(diff), 3)) %>% 
+  ggplot(., aes(x = sampsize, color = tailthresh, y = est.bias)) +
+  geom_point() +
+  scale_y_continuous(labels = scales::percent) +
+  theme_minimal()
+
+```
+
+### Now, let's simulate the individuals
 
@@
 ```
-
-Thinking out loud: Let's make the variation for the individuals normal.
-So, we multiply the variance for that percentage and then estimate it?
-The mu stays the same, we do a sample from the standard normal?
-Or do we follow percentages.
-Since we have a different number of individuals per group, I'd go with the standard normal approach.
 
@@
 ```
+
+```{r}
+# Generate the data
+
+```

### 2022-02-15 Ch3_samplesize/Ch3_functions.R

@@ -1,0 +1,92 @@
+### Lomax functions --------------------------
+
+lomax.pdf <- function(x,alpha,k, log.scale=FALSE){
+
+  if(log.scale==FALSE){out <- (k/(alpha+x))*(alpha/(alpha+x))^k
+  }else{
+    out <- log(k) + k*log(alpha) - (k+1)*log(alpha+x)
+  }
+
+  return(out)
+}
+
+
+lomax.cdf <- function(x,alpha,k){
+
+  return(1-(alpha/(alpha+x))^k)
+
+}
+
+ft.nllike <- function(guess=init.betas, designmat=designmat,Y=Y){
+
+  Xbeta         <- designmat%*%guess
+  alphas        <- exp(Xbeta) # because alpha = ln(X*betas)
+  n             <- length(Y)
+  sumlogapy     <- sum(log(alphas+Y))
+  k.hat         <- n/(sumlogapy - sum(Xbeta))
+  lnft.yis     <- lomax.pdf(x=Y, alpha=alphas,k=k.hat,log.scale=TRUE)
+  lnL           <- sum(lnft.yis)
+  nll           <- -lnL
+  return(nll)
+}
+
+lomax.glm <- function(formula=~1, my.dataf, response){
+
+  Y           <- response
+  n           <- length(Y)
+  designmat   <- model.matrix(formula, data=my.dataf)
+  nbetas      <- ncol(designmat)
+  init.betas  <- rep(1.5,nbetas)
+
+  opt.out <- optim(par=init.betas, fn=ft.nllike, method="BFGS",
+                   designmat=designmat, Y=Y)
+
+  mles          <- opt.out$par
+  nll.hat       <- opt.out$value
+  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
+  Xbeta.hat     <- designmat%*%mles
+  alphas.hat    <- exp(Xbeta.hat)
+  sumlogapy.hat <- sum(log(alphas.hat+Y))
+  k.hat         <- n/(sumlogapy.hat - sum(Xbeta.hat))
+
+  out.list <- list(opt.out = opt.out, designmat=designmat,Y=Y, mles=mles, nll.hat=nll.hat, BIC.mod = BIC.mod,
+                   alphas.hat=alphas.hat, k.hat=k.hat,data=my.dataf)
+
+  return(out.list)
+
+}
+# Sample 1000 movements and fit a lomax
+
+my.df <- data.frame(x = sample(all.samples, 1000))
[…]

### 2022-02-15 Ch3_samplesize/Ch3_simulation.R

@@ -1,0 +1,298 @@
+##########################################
+## DATA GENERATION CH3
+#########################################
+
+# I think the overall question for this is chapter is:
+#         Can we accurately estimate the true proportion of rare events produced by a complex model using a simpler hierarchical model?
+
+# Our complex model is one that considers individual variation in animal movement, with increasing mean and variance for specific groups
+# We use a mixture modeling approach, where each component distribution is associated to an individual's state or age.
+# We assume that an individual's stage will affect their movement.
+# We assume, for example, very young birds might not move as far, as will nesting or molting birds, whereas adults will move more.
+
+# The overall assumption for this model is that individuals vary in how much they move, which we determine based on step lengths only.
+# With some groups having an overall larger variance and mean than other groups.
+# The proportions, or weights, of the mixture, should follow a bell curve for now
+# With the average movers being the majority of the group, and low or high movement individuals being less abundant.
+
+# Libraries -----------------------------------------------
+set.seed(20220201)
+
+library(aracari)
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+library(tidyr)
+library(purrr)
+library(fitdistrplus)
+
+## Functions ----------------------------------------------------
+# Building this function so that we get the parameters for a desired mean and standard deviation.
+desired_mean_sd <- function(mean, sd){
+
+  mu <- log(mean*2/(sqrt(mean*2+sd*2)))
+  sigsq <- log(1+(sd*2/mean*2))
+
+  return(data.frame(mu = mu, sigsq = sigsq))
+}
+
+exp.val <- function(mu, sigsq){
+  exp(mu + sqrt(sigsq))
+}
+
+
+# MIXTURE MODEL --------------------------------------------------
+## Mixture proportions ----------------------------------------
[…]

### 2022-02-15 Ch3_samplesize/Ch3_Figures.Rmd
Figures.

--- 2022-02-15 Ch3_samplesize/mess/Datagen_viz.Rmd
@@
   mutate(diff = (cdfs.hat-true.cdfs),
+         est.over.true = cdfs.hat/true.cdfs,
          sampsize = factor(all.sampsizes),
@@
   #filter(., all.sampsizes == "80") %>%  
-  ggplot(., aes(x = sampsize, y = diff, color = tailthresh)) +
+  ggplot(., aes(x = sampsize, y = est.over.true, color = tailthresh)) +
   geom_boxplot() +
@@
 ```{r}
-resamp.df %>% 
-  group_by(sampsize, tailthresh) %>% 
-  summarise(est.bias = signif(mean(diff), 3))
 
@@
   group_by(sampsize, tailthresh) %>% 
-  summarise(est.bias = signif(mean(diff), 3)) %>% 
-  ggplot(., aes(x = sampsize, color = tailthresh, y = est.bias)) +
+  summarise(mean.diff = signif(mean(diff), 3)) %>% 
+  ggplot(., aes(x = sampsize, color = tailthresh, y = mean.diff)) +
   geom_point() +
@@
 
-### Now, let's simulate the individuals
+### Should I simulate the individuals
 

### 2022-02-15 Ch2_distributions/Ch2_R2n.R
Not really using this here.

@@ -1,257 +1,0 @@
-# 20211207 Data analysis
-
-# Libraries -----------------------------------------------
-set.seed(20211207)
-
-library(aracari)
-library(dplyr)
-library(ggplot2)
-library(tidyr)
-library(purrr)
-library(fitdistrplus)
-
-# Data ----------------------------------------------------
-# The script for this data is in the data-raw folder
-#load("data/ptpl.rda")
-
-# ptpl %>%
-#   filter(., mpm != 0) -> ptpl
-
-load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
-
-
-# Focus on R2n
-# R2n is the net squared displacement between the first relocation and every subsequent relocation.
-# We don't have long-enough time series for each of these bursts, and they are spaced out in different time intervals
-# So calculate an animal's velocity using the sqrt(R2n) over the time.
-
-
-ptpl %>%
-  dplyr::select(id, sgroup, date, burst, R2n, dt) %>%
-  mutate(sqR2n = sqrt(lead(R2n))) %>%
-  group_by(burst) %>%
-  mutate(ct0 = ifelse(is.na(dt) == T, 0, dt),
-         ct = cumsum(ct0)/60) %>%
-  ungroup() %>%
-  drop_na(dt) %>%
-  mutate(vel.R2n = sqR2n/ct) %>%
-  filter(vel.R2n != 0) %>%
-  group_by(id) %>%
-  add_tally() %>%
-  filter(n >= 30) -> r2n_ptpl
-
-View(r2n_ptpl)
-
-
-
-ptpl %>%
-  mutate(T_minutes = dt/60,
-         Bird_ID = id,
-         mpm = dist/T_minutes,
-         R2n = lead(R2n)) %>%
-  filter(mpm != 0) %>%
-  group_by(Bird_ID) %>%
-  add_tally() %>%
-  filter(n >= 30) -> ptpl
-
-
-dist.used <- c("gamma", "weibull", "lnorm")
-param <- c("shape", "rate", "shape", "scale", "meanlog", "sdlog")
-dist <- c("gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
-kpars <- c(2, 2, 2, 2, 2, 2)
-
-
-# Complete pooling fits -------------------------------------
-
-## Function to save the fit information and parameters -----
-
-build_fits_df <- function(x){
-
-  nm <- deparse(substitute(x))
-
-  x %>%
[…]

### 2022-02-15 Ch2_distributions/Orig_data_KH/explore_figures.R
Just exploratory figures.

@@ -1,0 +1,80 @@
+# Test script
+
+load("Ch2_distributions/Orig_data_KH/tidy_data.RData")
+
+# This is the code included in the raw-data folder, but I don't want to restrict stuff yet.
+
+# ptpl %>%
+#   mutate(T_minutes = dt/60,
+#          Bird_ID = id,
+#          mpm = dist/T_minutes,
+#          R2n = lead(R2n)) %>%
+#   filter(T_minutes != 0 & T_minutes %in% c(15, 30, 45, 60, 75, 90)) %>%
+#   group_by(Bird_ID) %>%
+#   add_tally() %>%
+#   filter(n >= 30) -> ptpl
+
+# For home range, Kimberly used the cutoff of 38 point observations.
+
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+
+ptpl <- ptpl %>%
+  mutate(T_minutes = dt/60,
+         Bird_ID = id,
+         mpm = dist/T_minutes,
+         R2n = lead(R2n))
+
+id.order <- ptpl %>% dplyr::select(Bird_ID, group) %>% distinct()
+
+ptpl %>% arrange(., group) %>%
+  mutate(Bird_ID = factor(Bird_ID, levels = id.order$Bird_ID)) -> ptpl
+
+obs.individual <- ptpl %>%
+  group_by(Bird_ID) %>%
+  summarise(N_Obs = n()) %>%
+  mutate(status = ifelse(N_Obs<30, "exclude",
+                         ifelse(N_Obs>40, "include", "edge")))
+
+obs.individual$Bird_ID <- factor(obs.individual$Bird_ID, levels = unique(obs.individual$Bird_ID))
+
+ggplot(obs.individual, aes(x=Bird_ID, y = N_Obs, fill = status)) +
+  geom_col() +
+  theme_bw() +
+  scale_fill_grey(start = 0, end = 0.8) +
+  geom_hline(yintercept = 40, color = "red") +
+  labs(title = "Number of observations by individual",
+       caption = "We use 40 observations as the minimum to consider individuals for our analysis. \n Individual Bird_ID 29 has 38 observations and is right in the edge of the threshold established")
+
+
+ptpl %>%
+  filter(T_minutes != 0) %>%
+  group_by(Bird_ID, T_minutes) %>%
+  count() %>%
+  ggplot(aes(x = as.factor(Bird_ID), y = n, fill = as.factor(T_minutes))) +
[…]

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
This chapter is killing me. Can't even decide on the scripts

---
title: "Ch3 process"
author: "Javiera Rudolph"
date: "1/20/2022"
output:
  html_document:
  toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=4, fig.height=3)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
# Libraries -----------------------------------------------
set.seed(20220201)

library(aracari)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(fitdistrplus)
```

# Methods  
We use a theoretical and simulation-based approach to understand how estimates of long-distance movements change with sample size and the choice of threshold value to describe a long-distance movement. We focus on testing the effectiveness of using a Lomax distribution to describe the probability of long-distance movements arising from complex mixture models incorporating individual variability.

## Simulating group variability with a finite mixture distribution model

Mixture distribution models are commonly used to describe the distribution of a process generated by multiple subpopulations. In the case of seed dispersal, mixture models have been used to describe the multimodality of seed dispersal kernels, specifically when accounting for disperser behaviors which lead to seed clumping. In the case of animal movement, mixture models and extensions are used to describe the multiple behaviors associated to an individual in movement. In our case, we use a mixture model to describe different subgroups which differ from each other in the distribution of step lengths. This is a theoretical example, a toy model, which includes four groups, each described by a lognormal distribution with a different set of parameters.

```{r MixtureParamFX}
## Parameter functions for mixture ----------------------------------------------------
# Building this function so that we get the parameters for a desired mean and standard deviation.
desired_mean_sd <- function(mean, sd){

  mu <- log(mean*2/(sqrt(mean*2+sd*2)))
  sigsq <- log(1+(sd*2/mean*2))

  return(data.frame(mu = mu, sigsq = sigsq))
}

exp.val <- function(mu, sigsq){
  exp(mu + sqrt(sigsq))
}
```

<!-- Thinking of things that need to be tested: like if we change the different weights. Also, varying the parameters for the distributions. Is this essentially a sensitivity analysis? -->

```{r}
# MIXTURE MODEL --------------------------------------------------
## Mixture proportions ----------------------------------------
# We assume four categories of individuals with increasing movement.
pis <- c( 0.1, 0.2, 0.3, 0.4)

## Mixture components --------------------------------------
# Since movement lengths are only positive, we use a lognormal distribution to describe them

# TEST 1

pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))

# thinking of how to calculate the cdf for a mixture
#plnorm(80, meanlog = pars$mu[1], sdlog = pars$sigsq[1], lower.tail = FALSE)

dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = pars$mu[y], sdlog = pars$sigsq[y]),
                                                             color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150), y = c(0,0.05)) -> densities_plot
densities_plot

```

We sample step lengths and generate a single distribution using the following weights: `r pis`

```{r fig.width=8}
# SAMPLING --------------------------------------------------------------

samp.size <- 50000
all.samples <- rep(0,samp.size)
categ <- rep(0,samp.size)

for(i in 1:samp.size){

  which.cat <- sample(1:4, size=1, replace=TRUE, prob=pis)
  all.samples[i] <- rlnorm(n=1,meanlog=pars$mu[which.cat], sdlog=pars$sigsq[which.cat])
  categ[i] <- which.cat
}

## PLOT the samples ---------------------------------------------
# This is our f(x) from the main text
data.tail <- data.frame(values = all.samples, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)
#head(data.tail)

ggplot(data.frame(all.samples), aes(x = all.samples)) +
  geom_histogram(bins = 100) +
  geom_point(data = data.tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_minimal() -> sampleshist

ggplot(data.frame(all.samples), aes(x = all.samples)) +
  geom_density() +
  labs(y = "Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_minimal() -> samplesdens

plot_grid(sampleshist, samplesdens)

```

Testing the results if using purrr instead of a for loop:

```{r fig.width=8}
#Trying an alternative way of drawing the samples

cat.samp.sizes <- samp.size*pis

purrrsampls <- tibble(gID = c(1:4), pars) %>% 
  mutate(data = purrr::map(gID, function(y) rlnorm(cat.samp.sizes[y], mu[y], sigsq[y])))

purrrsampls %>% 
  dplyr::select(., gID, data) %>% 
  unnest(cols = c(data)) -> simplsamps

simplsamps %>%
  ggplot(., aes(x = data)) +
  geom_histogram(bins = 100) +
  geom_point(data = data.tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_minimal() -> sampleshist

simplsamps %>% 
  ggplot(., aes(x = data)) +
  geom_density() +
  labs(y = "Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_minimal() -> samplesdens

plot_grid(sampleshist, samplesdens)

```

```{r LOMAX}
# All the lomax functions

# FITTING -------------------------------------
# We use a Lomax distribution, which is actually a special case of generalized Pareto distribution
# The Lomax or Patro type II has support on x=0, and is a heavy tail distribution
# Jose's document shows that it arises from incorporating variability in the rate parameter of an exponential distribution, using a gamma distribution - which he calls the hierarchical
# It only has two parameters, alpha(shape) and lambda(scale)

lomax.pdf <- function(x,alpha,k, log.scale=FALSE){

  if(log.scale==FALSE){out <- (k/(alpha+x))*(alpha/(alpha+x))^k
  }else{
    out <- log(k) + k*log(alpha) - (k+1)*log(alpha+x)
  }

  return(out)
}

lomax.cdf <- function(x,alpha,k){

  return(1-(alpha/(alpha+x))^k)

}

ft.nllike2 <- function(guess=init.betas, designmat=designmat,Y=Y){

  nbetasp1      <- length(init.betas)
  k             <- exp(guess[1])
  Xbeta         <- designmat%*%guess[2:nbetasp1]
  alphas        <- exp(Xbeta) # because alpha = ln(X*betas)
  n             <- length(Y)

  #sumlogapy     <- sum(log(alphas+Y))
  #k.hat         <- n/(sumlogapy - sum(Xbeta))
  lnft.yis     <- lomax.pdf(x=Y, alpha=alphas,k=k,log.scale=TRUE)
  lnL           <- sum(lnft.yis)
  nll           <- -lnL

  return(nll)
}

lomax.glm <- function(formula=~1, my.dataf, response){

  Y           <- response
  n           <- length(Y)
  designmat   <- model.matrix(formula, data=my.dataf)
  nbetas      <- ncol(designmat)
  init.betas  <- c(4,rep(5,nbetas))

  opt.out <- optim(par=init.betas, fn=ft.nllike2, method = "Nelder-Mead",
                   designmat=designmat, Y=Y)

  mles          <- opt.out$par
  nll.hat       <- opt.out$value
  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
  Xbeta.hat     <- designmat%*%mles[-1]
  alphas.hat    <- exp(Xbeta.hat)
  #sumlogapy.hat <- sum(log(alphas.hat+Y))
  k.hat         <-  mles[1] #n/(sumlogapy.hat - sum(Xbeta.hat))

  out.list <- list(opt.out = opt.out, designmat=designmat,Y=Y, mles=mles, nll.hat=nll.hat, BIC.mod = BIC.mod,
                   alphas.hat=alphas.hat, k.hat=k.hat,data=my.dataf)

  return(out.list)

}

```

Running the experiment once:

```{r echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds

samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
num.ns <- length(samp.sizes)
q.tests <- c(100, 250,500,1000)
num.qs <- length(q.tests)

all.sampsizes <- rep(samp.sizes,each=num.qs)
all.qtests <- rep(q.tests,num.ns)
ntests <- length(all.sampsizes)

cdfs.hat <- rep(0, ntests)

for(i in 1:ntests){
  ith.n   <- all.sampsizes[i]
  ith.samples <- data.frame(x = sample(all.samples, ith.n))

  formula=~1
  my.dataf = ith.samples
  response = ith.samples$x

  Y           <- response
  n           <- length(Y)
  designmat   <- model.matrix(formula, data=my.dataf)
  nbetas      <- ncol(designmat)
  init.betas  <- c(4,rep(5,nbetas))

  opt.out <- optim(par=init.betas, fn=ft.nllike2, method = "Nelder-Mead",
                   designmat=designmat, Y=Y)

  mles          <- opt.out$par
  nll.hat       <- opt.out$value
  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
  Xbeta.hat     <- designmat%*%mles[-1]
  alphas.hat    <- exp(Xbeta.hat)
  #sumlogapy.hat <- sum(log(alphas.hat+Y))
  k.hat         <-  mles[1] #n/(sumlogapy.hat - sum(Xbeta.hat))

  mod1 <- list(opt.out = opt.out, designmat=designmat,Y=Y, mles=mles, nll.hat=nll.hat, BIC.mod = BIC.mod,
                   alphas.hat=alphas.hat, k.hat=k.hat,data=my.dataf)

  ith.a <- mod1$alphas.hat[1]
  ith.k <- mod1$k.hat

  ith.q <- all.qtests[i]
  ith.cdf <- 1- lomax.cdf(x = ith.q, alpha = ith.a, k = ith.k)
  cdfs.hat[i] <- ith.cdf

}

true.cdfs <- rep(0,num.qs)
for(i in 1:num.qs){

  iq <- q.tests[i]

  true.cdfs[i] <- sum(all.samples>iq)/length(all.samples)

}

all.true.cdfs <- rep(true.cdfs,num.ns)

sim.test.df <- data.frame(all.sampsizes=all.sampsizes, all.qtests=all.qtests,cdfs.hat=cdfs.hat,
                          true.cdfs = all.true.cdfs)
```

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
The samples are done. Need to fit models.

@@
 
-pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))
+pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 250))
 
@@
 
+# ### PLOT the mixture components CDF -------------------------------
+# lnorm_cdfs <- purrr::map(1:4, function(y) stat_function(fun = plnorm,
+#                                                              args = list(meanlog = pars$mu[y], sdlog = pars$sigsq[y]),
+#                                                              color = dens_cols[y], size=1))
+# ggplot() +
+#   lnorm_cdfs +
+#   theme_minimal() +
+#   labs(y = "Density") +
+#   lims(x = c(50, 250), y = c(0.9, 1))
+#        
 ```
@@
 ```{r fig.width=8}
-# SAMPLING --------------------------------------------------------------
-
+# Using purrr to get samples instead of a for loop. More efficient.
 samp.size <- 50000
-all.samples <- rep(0,samp.size)
-categ <- rep(0,samp.size)
-
-for(i in 1:samp.size){
-
-  which.cat <- sample(1:4, size=1, replace=TRUE, prob=pis)
-  all.samples[i] <- rlnorm(n=1,meanlog=pars$mu[which.cat], sdlog=pars$sigsq[which.cat])
-  categ[i] <- which.cat
-}
-
-## PLOT the samples ---------------------------------------------
-# This is our f(x) from the main text
-data.tail <- data.frame(values = all.samples, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)
-#head(data.tail)
-
-ggplot(data.frame(all.samples), aes(x = all.samples)) +
-  geom_histogram(bins = 100) +
-  geom_point(data = data.tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
-  labs(y = "Frequency", x = "Distance") +
-  #lims(x = c(0, 150)) +
-  theme_minimal() -> sampleshist
-
-ggplot(data.frame(all.samples), aes(x = all.samples)) +
-  geom_density() +
-  labs(y = "Density", x = "Distance") +
-  lims(x = c(0, 150), y = c(0,0.05)) +
-  theme_minimal() -> samplesdens
-
-plot_grid(sampleshist, samplesdens)
-
-```
-
-Testing the results if using purrr instead of a for loop:
-
-```{r fig.width=8}
-#Trying an alternative way of drawing the samples
-
 cat.samp.sizes <- samp.size*pis
@@
   unnest(cols = c(data)) -> simplsamps
+
+data.tail <- data.frame(values = simplsamps$data, y = 100) %>% arrange(desc(values)) %>% filter(values >=250)
 
@@
 plot_grid(sampleshist, samplesdens)
+
+```
+
+Answering some questions about the underlying process.
+
+What is the true CDF of the function that generates the process? This is the CDF of the mixture distribution, which is straightforward to calculate.
+
+$$
+f(x) = \sum_{i=1}^n w_i p_i(x) \Rightarrow F(x) = \sum_{i=1}^n w_i P_i(x)
+$$
+
+```{r}
+thresh.vals <- c(100, 250, 500, 750, 1000)
+samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
+
+```
+
+The thresholds we want to consider are the following:`r thresh.vals` and the weights haven't changed.
+So, we get the cdf for each $p_i(x)$ for each threshold.
+This means we get $P(x >= c(100, 250, 500, 1000))$ for each curve and weigh it.
+
+```{r eval = FALSE}
+# Getting weird stuff so taking this step by step
+y <- 4
+
+ggplot() +
+  stat_function(fun = dlnorm, args = list(meanlog = pars$mu[y], sdlog = pars$sigsq[y]),
+                                                             color = dens_cols[y], size=1) +
+  theme_minimal() +
+  labs(y = "Density") +
+  lims(x = c(0, 150), y = c(0,0.05))
+
+cdfs <- NULL
+for(y in 1:4){
+  a <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE)
+  b <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE) * pis[y]
+
+  c <- rbind(a,b)
+
+  out <- cbind(c, c(y, y))
+
+  cdfs <- rbind.data.frame(cdfs, out)
+}
+names(cdfs) <- c(thresh.vals, "curve")
+cdfs
+
+```
+
+```{r}
+weighted.cdfs <- NULL
+for(y in 1:4){
+  a <- plnorm(thresh.vals, meanlog = pars$mu[y], sdlog = pars$sigsq[y], lower.tail = FALSE) * pis[y]
+  weighted.cdfs <- rbind(weighted.cdfs, a)
+}
+w.cdfs <- colSums(weighted.cdfs)
+
+tibble(thresh.vals) %>% 
+  mutate(w.cdfs = w.cdfs,
+         w.cdfs = round(w.cdfs, 5),
+         samp.n = map_dbl(1:length(thresh.vals), function(y) length(which(simplsamps$data >= thresh.vals[y]))),
+         samp.p = signif(samp.n/samp.size, 3)) %>% 
+  knitr::kable()
 
@@
 
-```{r echo=TRUE}
+```{r eval = FALSE, echo=TRUE}
 ###################################

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
I'm having issues with the estimation of parameters. I don't think this is right.

@@
 
+lomax.st <- function(x=x, alpha=alpha, k=k){
+  out <- alpha/(alpha+x)
+  return(out^k)
+}
+
+lomax.mean <- function(alpha=alpha, k=k){
+  return(alpha/(k+1))
+}
+
 ft.nllike2 <- function(guess=init.betas, designmat=designmat,Y=Y){
@@
 
-```{r eval = FALSE, echo=TRUE}
+```{r}
+# First estimate the mles for the different sample sizes
+
+mles.sampsizes <- data.frame(samp.size = samp.sizes, alphas = 0, khats = 0)
+
+for(i in 1:length(samp.sizes)){
+  ith.n   <- mles.sampsizes$samp.size[i]
+  ith.samples <- data.frame(x = sample(simplsamps$data, ith.n))
+
+  # The glm.lomax was giving me an error. Kept saying it couldn't find the init betas but worked when I ran it line by line.
+
+  # From the glm framework, we are not including covariates here
+  # The next three lines are the arguments to the glm lomax function
+  formula=~1
+  my.dataf = ith.samples
+  response = ith.samples$x
+
+  # This is the glm lomax function deconstructed
+  Y           <- response
+  n           <- length(Y)
+  designmat   <- model.matrix(formula, data=my.dataf)
+  nbetas      <- ncol(designmat)
+  init.betas  <- c(4,rep(5,nbetas))
+
+  opt.out <- optim(par=init.betas, fn=ft.nllike2, method = "Nelder-Mead",
+                   designmat=designmat, Y=Y)
+
+  mles          <- opt.out$par
+  nll.hat       <- opt.out$value
+  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
+  Xbeta.hat     <- designmat%*%mles[-1]
+  alphas.hat    <- exp(Xbeta.hat)
+  #sumlogapy.hat <- sum(log(alphas.hat+Y))
+  k.hat         <-  mles[1] #n/(sumlogapy.hat - sum(Xbeta.hat))
+
+  mles.sampsizes$alphas[i] <- alphas.hat
+  mles.sampsizes$khats[i] <- k.hat
+}
+
+mles.sampsizes %>% 
+  mutate(mean = lomax.mean(alphas, khats))
+
+```
+```{r}
+# Now calculate the cdfs for each distribution and for each threshold
+
+1-lomax.cdf(thresh.vals, alpha = mles.sampsizes$alphas[1], k = mles.sampsizes$khats[1])
+
+```
+
+```{r echo=TRUE}
 ###################################
 # Run the experiments with different sample sizes and tail thresholds
+
+all.samples <- simplsamps$data
 
@@
 
-true.cdfs <- rep(0,num.qs)
-for(i in 1:num.qs){
-
-  iq <- q.tests[i]
-
-  true.cdfs[i] <- sum(all.samples>iq)/length(all.samples)
-
-}
-
-all.true.cdfs <- rep(true.cdfs,num.ns)
-
-sim.test.df <- data.frame(all.sampsizes=all.sampsizes, all.qtests=all.qtests,cdfs.hat=cdfs.hat,
-                          true.cdfs = all.true.cdfs)
 ```

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Trying to troubleshoot.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
 knitr::opts_chunk$set(fig.width=4, fig.height=3)
@@
 
-```{r eval = FALSE}
+```{r echo=FALSE, eval = FALSE}
 # Getting weird stuff so taking this step by step
@@
 mles.sampsizes %>% 
-  mutate(mean = lomax.mean(alphas, khats))
+  mutate(mean = lomax.mean(alphas, khats),
+         tail100 = lomax.cdf(100, alphas, khats),
+         tail250 = lomax.cdf(250, alphas, khats),
+         tail500 = lomax.cdf(500, alphas, khats),
+         tail750 = lomax.cdf(750, alphas, khats),
+         tail1k = lomax.cdf(1000, alphas, khats)) %>% 
+  #mutate(across(c(2:8), signif, digits=3)) %>% 
+  mutate(across(starts_with("tail"), signif, digits=3))
 
@@
 ```{r}
-# Now calculate the cdfs for each distribution and for each threshold
+# But if we do 1-cdf, which should be P(X>=x) we get high numbers.
 
@@
 
-```{r echo=TRUE}
+```{r eval=FALSE, echo=FALSE}
 ###################################

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Well, trying to get around this with a different package.

@@
 ```
-
 ```{r eval=FALSE, echo=FALSE}
@@
 ```
+
+# GP approach
+
+Going off script here and going to try and do this in a way I understand it and with functions I already know.
+
+```{r results='hide'}
+library(extRemes)
+
+fevd.mles <- data.frame(samp.size = rep(samp.sizes, length(thresh.vals)), threshold = thresh.vals, scale = 0, shape = 0, nllh = 0)
+
+for(i in 1:nrow(fevd.mles)){
+  ith.n        <- fevd.mles$samp.size[i]
+  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))
+  # Can't use this because by setting those higher thresholds we have one data point and can't fit anything to it. 
+  #ith.thresh   <- fevd.mles$threshold[i]
+
+  # So, setting the threshold to 0 so we can compare to Lomax.
+  ith.thresh <- 0
+
+  ith.fit      <- fevd(ith.samples$x, threshold = ith.thresh, type = "GP")
+
+  mles          <- summary(ith.fit)$par
+  nll.hat       <- summary(ith.fit)$nllh
+  BIC.mod       <- summary(ith.fit)$BIC
+
+  fevd.mles$scale[i] <- mles[1]
+  fevd.mles$shape[i] <- mles[2]
+  fevd.mles$nllh[i]  <- nll.hat
+
+}
+
+```
+
+```{r}
+fevd.mles
+```
+
+So, we try to make the link to a Generalized Pareto distribution with the Lomax.The Lomax distribution is a special case of a Pareto where the parameters are as follows:  
+- The location is $\mu = 0$ 
+- The shape parameter is $\xi = 1/\alpha$
+- The scale parameter is $\sigma = \lambda/\alpha$
+
+Where the pdf of the lomax follows:
+$$
+p(x) = \frac{\alpha}{\lambda}\left[ 1 +  \frac{x}{\lambda}  \right]^{-\alpha + 1} = \left( \frac{\lambda}{x+\lambda} \right)^{\alpha} \left( \frac{\alpha}{x+\lambda} \right)
+$$
+And in JM Ponciano's parameterization: $\alpha = k$ and $\lambda = \alpha$, which means in comparison to the Generalized Pareto:
+
+- The location is $\mu = 0$ 
+- The shape parameter is $\xi = 1/k$
+- The scale parameter is $\sigma = \alpha/k$
+
+```{r}
+gp2lomax.jmp <- function(shape, scale){
+  k     <- 1/shape
+  alpha <- scale*k
+}
+```
+
+So, now we use the parameter estimates from the GP to get the parameters as a Lomax, and use those parameters to get the cdfs and means.
+
+```{r}
+
+fevd.mles %>% 
+  mutate(ks = 1/shape,
+         alphas = scale*ks) %>% 
+  dplyr::select(-c(scale, shape)) %>% 
+  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
+         tail = 1- est.cdf, 
+         mean = lomax.mean(alphas, ks)) -> est.lomax.mles
+est.lomax.mles %>% knitr::kable()
+
+```
+
+And visually, we
+
+```{r}
+
+```

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Getting ready to run and save this. Monte Carlo sim.

@@
          samp.n = map_dbl(1:length(thresh.vals), function(y) length(which(simplsamps$data >= thresh.vals[y]))),
-         samp.p = signif(samp.n/samp.size, 3)) %>% 
+         samp.p = signif(samp.n/samp.size, 3)) -> tru.cdfs
+
+tru.cdfs %>% 
   knitr::kable()
@@
   ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))
-  # Can't use this because by setting those higher thresholds we have one data point and can't fit anything to it. 
-  #ith.thresh   <- fevd.mles$threshold[i]
 
   # So, setting the threshold to 0 so we can compare to Lomax.
-  ith.thresh <- 0
 
-  ith.fit      <- fevd(ith.samples$x, threshold = ith.thresh, type = "GP")
+  ith.fit      <- fevd(ith.samples$x, threshold = 0, type = "GP")
 
@@
 
+  ith.thresh   <- fevd.mles$threshold[i]
+  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)
 }
@@
 ```{r}
-fevd.mles
+fevd.mles %>% 
+  knitr::kable()
 ```
@@
          alphas = scale*ks) %>% 
-  dplyr::select(-c(scale, shape)) %>% 
+  #dplyr::select(-c(scale, shape)) %>% 
   mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
@@
 ```  
+The NaN I get in the previous dataframe are due to 0/0, so, undefined? What should I make of it?
 
-And visually, we
+So, now I will estimate the ratio between the estimated cdf and the true cdf.
 
-```{r}
+```{r fig.width=8}
+
+est.lomax.mles %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
+         tails.ratio = tail/tru.tails,
+         thresh = factor(threshold)) %>%
+  drop_na(tails.ratio) %>% 
+  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
+  geom_point() +
+  labs(title = "Lomax") +
+  theme_minimal() -> lomax.tail
+
+est.lomax.mles %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)),
+         gp.tails.ratio = gp.tail/tru.tails,
+         thresh = factor(threshold)) %>%
+  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
+  geom_point() +
+  labs(title = "GP")
+  theme_minimal() -> gp.tail
+
+plot_grid(lomax.tail, gp.tail)
 
 ```
+
+Now, we repeat the process to see how much this varies...
+
+```{r results='hide'}
+nreps <- 100
+gp.mles.reps <- data.frame(NULL)
+
+for(j in 1:nreps){
+
+  ith.mle.df <- data.frame(samp.size = rep(samp.sizes, length(thresh.vals)), threshold = thresh.vals,
+                           scale = 0, shape = 0, nllh = 0, gp.tail = 0, rep = 0)
+
+  for(i in 1:nrow(ith.mle.df)){
+  ith.n        <- ith.mle.df$samp.size[i]
+  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))
+
+  # So, setting the threshold to 0 so we can compare to Lomax.
+
+  ith.fit      <- fevd(ith.samples$x, threshold = 0, type = "GP")
+
+  mles          <- summary(ith.fit)$par
+  nll.hat       <- summary(ith.fit)$nllh
+  BIC.mod       <- summary(ith.fit)$BIC
+
+  ith.mle.df$scale[i] <- mles[1]
+  ith.mle.df$shape[i] <- mles[2]
+  ith.mle.df$nllh[i]  <- nll.hat
+  ith.mle.df$rep[i] <- paste0("rep", j)
+
+  ith.thresh   <- fevd.mles$threshold[i]
+  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)
+
+  }
+
+  gp.mles.reps <- rbind.data.frame(gp.mles.reps, ith.mle.df)
+
+}
+save.image(gp.mles.reps, "Ch3_samplesize/testdf.RData")
+```

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
did it! need to make the big runs now.

@@
   geom_point() +
-  labs(title = "GP")
+  labs(title = "GP") +
   theme_minimal() -> gp.tail
@@
 ```{r results='hide'}
-nreps <- 100
+nreps <- 2
 gp.mles.reps <- data.frame(NULL)
@@
 
-  ith.thresh   <- fevd.mles$threshold[i]
-  fevd.mles$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)
+  ith.thresh   <- ith.mle.df$threshold[i]
+  ith.mle.df$gp.tail[i] <- pextRemes(ith.fit, ith.thresh, lower.tail = FALSE)
 
@@
 }
-save.image(gp.mles.reps, "Ch3_samplesize/testdf.RData")
+
+gp.mles.reps %>% 
+  mutate(ks = 1/shape,
+         alphas = scale*ks) %>% 
+  #dplyr::select(-c(scale, shape)) %>% 
+  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
+         tail = 1- est.cdf, 
+         mean = lomax.mean(alphas, ks)) -> gp.mles.reps
+
+save(gp.mles.reps, file = "Ch3_samplesize/testdf.RData")
 ```
+
+Let's see
+
+```{r fig.width=8}
+
+n.tru.cdfs <- nrow(gp.mles.reps)/length(tru.cdfs$w.cdfs)
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         tails.ratio = tail/tru.tails,
+         thresh = factor(threshold)) %>%
+  drop_na(tails.ratio) %>% 
+  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "Lomax") +
+  theme_minimal() -> lomax.tail
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         gp.tails.ratio = gp.tail/tru.tails,
+         thresh = factor(threshold)) %>%
+  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "GP") +
+  theme_minimal() -> gp.tail
+
+plot_grid(lomax.tail, gp.tail)
+
+```

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Done with 100!

@@
 ```{r results='hide'}
-nreps <- 2
+nreps <- 100
 gp.mles.reps <- data.frame(NULL)
@@
          tails.ratio = tail/tru.tails,
-         thresh = factor(threshold)) %>%
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
   drop_na(tails.ratio) %>% 
@@
          gp.tails.ratio = gp.tail/tru.tails,
-         thresh = factor(threshold)) %>%
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
   mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Ah! running 1000

@@
 ```{r results='hide'}
-nreps <- 100
+nreps <- 1000
 gp.mles.reps <- data.frame(NULL)
@@
 ```
+
+Restrict the y axis
+
+```{r fig.width=8}
+
+n.tru.cdfs <- nrow(gp.mles.reps)/length(tru.cdfs$w.cdfs)
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         tails.ratio = tail/tru.tails,
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
+  drop_na(tails.ratio) %>% 
+  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "Lomax") +
+  lims(y = c(-1, 3)) +
+  theme_minimal() -> lomax.tail
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         gp.tails.ratio = gp.tail/tru.tails,
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
+  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "GP") +
+  lims(y = c(-1, 3)) +
+  theme_minimal() -> gp.tail
+
+plot_grid(lomax.tail, gp.tail)
+
+```
+
+Check the mean:
+
+```{r}
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         tails.ratio = tail/tru.tails,
+         gp.tails.ratio = gp.tail/tru.tails) %>% 
+  group_by(samp.size, threshold) %>% 
+  summarise(mean.ratio = mean(tails.ratio),
+            mean.gp.ratio = mean(gp.tails.ratio))
+```

### 2022-02-17 Ch3_samplesize/Ch3_simulation.R

@@ -107,9 +107,40 @@ plot_grid(densities_plot, sampleshist, nrow=2, labels="AUTO")
 summary(all.samples)
 
 # FUNCTIONS ---------------------------------
-source("Ch3_samplesize/Ch3_functions.R")
+lomax.pdf <- function(x,alpha,k, log.scale=FALSE){
 
-###################################
+  if(log.scale==FALSE){out <- (k/(alpha+x))*(alpha/(alpha+x))^k
+  }else{
+    out <- log(k) + k*log(alpha) - (k+1)*log(alpha+x)
+  }
+
+  return(out)
+}
+
+lomax.cdf <- function(x,alpha,k){
+
+  return(1-(alpha/(alpha+x))^k)
+
+}
+
+
+ft.nllike2 <- function(guess=init.betas, designmat=designmat,Y=Y){
+
+  nbetasp1      <- length(init.betas)
+  k             <- exp(guess[1])
+  Xbeta         <- designmat%*%guess[2:nbetasp1]
+  alphas        <- exp(Xbeta) # because alpha = ln(X*betas)
+  n             <- length(Y)
+
+  #sumlogapy     <- sum(log(alphas+Y))
+  #k.hat         <- n/(sumlogapy - sum(Xbeta))
+  lnft.yis     <- lomax.pdf(x=Y, alpha=alphas,k=k,log.scale=TRUE)
+  lnL           <- sum(lnft.yis)
+  nll           <- -lnL
+
+  return(nll)
+}
+
 # Run the experiments with different sample sizes and tail thresholds
 
 samp.sizes <- c(80, 200, 500, 800, 1000, 1600)
@@ -125,10 +156,35 @@ cdfs.hat <- rep(0, ntests)
 
 
 for(i in 1:ntests){
-
   ith.n   <- all.sampsizes[i]
   ith.samples <- data.frame(x = sample(all.samples, ith.n))
-  mod1 <- lomax.glm(formula = ~1, my.dataf = ith.samples, response = ith.samples$x)
+
+  formula=~1
+  my.dataf = ith.samples
+  response = ith.samples$x
+
+
+  Y           <- response
+  n           <- length(Y)
+  designmat   <- model.matrix(formula, data=my.dataf)
+  nbetas      <- ncol(designmat)
+  init.betas  <- c(4,rep(5,nbetas))
+
[…]

### 2022-02-18 Ch3_samplesize/Ch3_process.Rmd
Fixed the errors so now all functions work.

--- 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
@@
 lomax.mean <- function(alpha=alpha, k=k){
-  return(alpha/(k+1))
+  return(alpha/(k-1))
 }
@@
 
-  nbetasp1      <- length(init.betas)
+  nbetasp1      <- length(guess)
   k             <- exp(guess[1])
@@
   Xbeta.hat     <- designmat%*%mles[-1]
-  alphas.hat    <- exp(Xbeta.hat)
+  alphas.hat    <- log(Xbeta.hat)
   #sumlogapy.hat <- sum(log(alphas.hat+Y))
@@
 
-  # The glm.lomax was giving me an error. Kept saying it couldn't find the init betas but worked when I ran it line by line.
+  mod1 <- lomax.glm(formula = ~1, my.dataf = ith.samples, response = ith.samples$x)
+  ith.a <- mod1$alphas.hat[1]
+  ith.k <- mod1$k.hat
 
-  # From the glm framework, we are not including covariates here
-  # The next three lines are the arguments to the glm lomax function
-  formula=~1
-  my.dataf = ith.samples
-  response = ith.samples$x
-
-  # This is the glm lomax function deconstructed
-  Y           <- response
-  n           <- length(Y)
-  designmat   <- model.matrix(formula, data=my.dataf)
-  nbetas      <- ncol(designmat)
-  init.betas  <- c(4,rep(5,nbetas))
-
-  opt.out <- optim(par=init.betas, fn=ft.nllike2, method = "Nelder-Mead",
-                   designmat=designmat, Y=Y)
-
-  mles          <- opt.out$par
-  nll.hat       <- opt.out$value
-  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
-  Xbeta.hat     <- designmat%*%mles[-1]
-  alphas.hat    <- exp(Xbeta.hat)
-  #sumlogapy.hat <- sum(log(alphas.hat+Y))
-  k.hat         <-  mles[1] #n/(sumlogapy.hat - sum(Xbeta.hat))
-
-  mles.sampsizes$alphas[i] <- alphas.hat
-  mles.sampsizes$khats[i] <- k.hat
+  mles.sampsizes$alphas[i] <- ith.a
+  mles.sampsizes$khats[i] <- ith.k
 }
@@
   mutate(mean = lomax.mean(alphas, khats),
-         tail100 = lomax.cdf(100, alphas, khats),
-         tail250 = lomax.cdf(250, alphas, khats),
-         tail500 = lomax.cdf(500, alphas, khats),
-         tail750 = lomax.cdf(750, alphas, khats),
-         tail1k = lomax.cdf(1000, alphas, khats)) %>% 
+         tail100 = lomax.st(100, alphas, khats),
+         tail250 = lomax.st(250, alphas, khats),
+         tail500 = lomax.st(500, alphas, khats),
+         tail750 = lomax.st(750, alphas, khats),
+         tail1k = lomax.st(1000, alphas, khats)) %>% 
   #mutate(across(c(2:8), signif, digits=3)) %>% 
@@
 ```
+
 ```{r}
-# But if we do 1-cdf, which should be P(X>=x) we get high numbers.
-
-1-lomax.cdf(thresh.vals, alpha = mles.sampsizes$alphas[1], k = mles.sampsizes$khats[1])
-
-```
-```{r eval=FALSE, echo=FALSE}
 ###################################
@@
 
-  formula=~1
-  my.dataf = ith.samples
-  response = ith.samples$x
-
-  Y           <- response
-  n           <- length(Y)
-  designmat   <- model.matrix(formula, data=my.dataf)
-  nbetas      <- ncol(designmat)
-  init.betas  <- c(4,rep(5,nbetas))
-
-  opt.out <- optim(par=init.betas, fn=ft.nllike2, method = "Nelder-Mead",
-                   designmat=designmat, Y=Y)
-
-  mles          <- opt.out$par
-  nll.hat       <- opt.out$value
-  BIC.mod       <- 2*nll.hat + nbetas*log(length(Y))
-  Xbeta.hat     <- designmat%*%mles[-1]
-  alphas.hat    <- exp(Xbeta.hat)
-  #sumlogapy.hat <- sum(log(alphas.hat+Y))
-  k.hat         <-  mles[1] #n/(sumlogapy.hat - sum(Xbeta.hat))
-
-  mod1 <- list(opt.out = opt.out, designmat=designmat,Y=Y, mles=mles, nll.hat=nll.hat, BIC.mod = BIC.mod,
-                   alphas.hat=alphas.hat, k.hat=k.hat,data=my.dataf)
+  mod1 <- lomax.glm(formula = ~1, my.dataf = ith.samples, response = ith.samples$x)
 
@@
   ith.q <- all.qtests[i]
-  ith.cdf <- 1- lomax.cdf(x = ith.q, alpha = ith.a, k = ith.k)
+  ith.cdf <- lomax.st(x = ith.q, alpha = ith.a, k = ith.k)
   cdfs.hat[i] <- ith.cdf
@@
 
-```{r results='hide'}
-nreps <- 100
+```{r eval=FALSE, results='hide'}
+# I already ran this chunk and it takes a very long time (a night), so saved the result and I'm just loading it in the next chunk
+nreps <- 1000
 gp.mles.reps <- data.frame(NULL)
@@
 
+```{r}
+load("Ch3_samplesize/testdf.RData")
+```
+
 Let's see
@@
 ```
+
+Restrict the y axis
+
+```{r fig.width=8}
+
+n.tru.cdfs <- nrow(gp.mles.reps)/length(tru.cdfs$w.cdfs)
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         tails.ratio = tail/tru.tails,
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
+  drop_na(tails.ratio) %>% 
+  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "Lomax") +
+  lims(y = c(-0.1, 3)) +
+  theme_minimal() -> lomax.tail
+
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         gp.tails.ratio = gp.tail/tru.tails,
+         thresh = factor(threshold),
+         samp.size = factor(samp.size)) %>%
+  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
+  geom_boxplot() +
+  labs(title = "GP") +
+  lims(y = c(-0.1, 3)) +
+  theme_minimal() -> gp.tail
+
+plot_grid(lomax.tail, gp.tail)
+
+```
+
+Check the mean:
+
+```{r}
+gp.mles.reps %>% 
+  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
+         tails.ratio = tail/tru.tails,
+         gp.tails.ratio = gp.tail/tru.tails) %>% 
+  group_by(samp.size, threshold) %>% 
+  summarise(mean.ratio = mean(tails.ratio),
+            mean.gp.ratio = mean(gp.tails.ratio),
+            ste.gp.ratio = sd(gp.tails.ratio)/sqrt(length(gp.tails.ratio))) -> tail.ratio.means
+
+tail.ratio.means %>%
+  knitr::kable()
+```
+
+```{r fig.width=8}
+tail.ratio.means %>% 
+  ggplot(., aes(x = factor(threshold), y = mean.gp.ratio, color = factor(samp.size))) +
+  #geom_point() +
+  geom_jitter(size = 2, width = 0.2, alpha = 0.8) +
+  #scale_y_log10() +
+  theme_minimal()
+```

### 2022-02-18 Ch3_samplesize/Ch3_process.Rmd
The test works and the functions work, so putting these into the actual functions script.

@@
 num.ns <- length(samp.sizes)
-q.tests <- c(100, 250,500,1000)
+q.tests <- c(100, 250,500,750,1000)
 num.qs <- length(q.tests)
@@
 
+ith.a <- rep(0, ntests)
+ith.k <- rep(0, ntests)
+
 for(i in 1:ntests){
@@
 
-  ith.a <- mod1$alphas.hat[1]
-  ith.k <- mod1$k.hat
+  ith.a[i] <- mod1$alphas.hat[1]
+  ith.k[i] <- mod1$k.hat
 
   ith.q <- all.qtests[i]
-  ith.cdf <- lomax.st(x = ith.q, alpha = ith.a, k = ith.k)
+  ith.cdf <- lomax.st(x = ith.q, alpha = ith.a[i], k = ith.k[i])
   cdfs.hat[i] <- ith.cdf
@@
 
+lomax.fits <- data.frame(samp.sizes = all.sampsizes, threshold = all.qtests, alphas = ith.a, ks = ith.k, lomax.tail = cdfs.hat,
+                         tru.tails = rep(tru.cdfs$w.cdfs, length(samp.sizes)))
+```
+
+```{r eval=FALSE, echo=FALSE}
+lomax.fits %>% 
+  mutate(tails.ratio = lomax.tail/tru.tails,
+         thresh = factor(threshold),
+         samp.sizes = factor(samp.sizes)) %>%
+  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
+  ggplot(., aes(x = samp.sizes, y = tails.ratio, color = thresh)) +
+  geom_jitter(alpha = 0.8, width = 0.2) +
+  labs(title = "Lomax") +
+  theme_minimal()
 ```

### 2022-02-18 Ch3_samplesize/Ch3_functions.R
Building the functions script from the Rmd file

@@ -1,92 +1,101 @@
-### Lomax functions --------------------------
+##########################################
+## Javiera Rudolph                      ##
+### Functions used for Ch3              ##
+## February 18, 2022                    ##
+##########################################
 
-lomax.pdf <- function(x,alpha,k, log.scale=FALSE){
 
-  if(log.scale==FALSE){out <- (k/(alpha+x))*(alpha/(alpha+x))^k
-  }else{
-    out <- log(k) + k*log(alpha) - (k+1)*log(alpha+x)
-  }
 
-  return(out)
+##########################################
+# Data simulation ------------------------
+
+
+## Mixture model -------------------------
+
+# The weights right now are just set as values
+# but this can change, and we could use a distribution
+# to sample them from
+
+### Weights ------------------------------
+
+# This is not created yet, but on the list
+
+generate.pis <- functions(n){
+  NULL
 }
 
 
-lomax.cdf <- function(x,alpha,k){
+### Components --------------------------
 
-  return(1-(alpha/(alpha+x))^k)
+#### Parameters -------------------------
+# since I get confused with logs and such
+# The following function helps gives the
+# parameters for a lognormal that has the
+# desired mean and variance:
 
+desired_mean_sd <- function(mu_x, sigsq_x){
+
+  mu <- log(mu_x^2/(sqrt(mu_x^2+sigsq_x)))
+  sigsq <- log(1+(sigsq_x/mu_x^2))
+
+  return(data.frame(mu, sigsq))
 }
 
-ft.nllike <- function(guess=init.betas, designmat=designmat,Y=Y){
+# Now, for a Lnorm(mu, sigsq), get mean and var
 
-  Xbeta         <- designmat%*%guess
-  alphas        <- exp(Xbeta) # because alpha = ln(X*betas)
-  n             <- length(Y)
-  sumlogapy     <- sum(log(alphas+Y))
-  k.hat         <- n/(sumlogapy - sum(Xbeta))
-  lnft.yis     <- lomax.pdf(x=Y, alpha=alphas,k=k.hat,log.scale=TRUE)
-  lnL           <- sum(lnft.yis)
-  nll           <- -lnL
-  return(nll)
+lnorm_mean_var <- function(mu, sigsq){
+
+  lnorm_mean <- exp(mu + (sigsq/2))
[…]

### 2022-02-18 Ch3_samplesize/Ch3_functions.R
Troubleshooting functions for mean and variance of lognormal

@@ -20,8 +20,8 @@
 
 # This is not created yet, but on the list
 
-generate.pis <- functions(n){
-  NULL
+generate.pis <- function(n){
+  n
 }
 
 
@@ -33,24 +33,23 @@ generate.pis <- functions(n){
 # parameters for a lognormal that has the
 # desired mean and variance:
 
-desired_mean_sd <- function(mu_x, sigsq_x){
+desired_mean_sd <- function(mu_x, sd_x){
 
-  mu <- log(mu_x^2/(sqrt(mu_x^2+sigsq_x)))
-  sigsq <- log(1+(sigsq_x/mu_x^2))
+  mu <- log(mu_x^2/(sqrt(mu_x^2+sd_x^2)))
+  sigma <- log(1+(sd_x/mu_x^2))
 
-  return(data.frame(mu, sigsq))
+  return(data.frame(mu, sigma))
 }
 
 # Now, for a Lnorm(mu, sigsq), get mean and var
 
-lnorm_mean_var <- function(mu, sigsq){
+lnorm_mean_var <- function(mu, sigma){
 
-  lnorm_mean <- exp(mu + (sigsq/2))
-  lnorm_var  <- (exp(sigsq)-1)*exp(2*mu+sigsq)
+  lnorm_mean <- exp(mu + ((sigma^2)/2))
+  lnorm_var  <- (exp(sigma^2)-1)*exp(2*mu+sigma^2)
 
   return(data.frame(lnorm_mean, lnorm_var))
 }
-
 
 #### Components --------------------------
 

### 2022-02-18 Ch3_samplesize/Ch3_simulation.R

@@ -2,19 +2,6 @@
 ## DATA GENERATION CH3
 #########################################
 
-# I think the overall question for this is chapter is:
-#         Can we accurately estimate the true proportion of rare events produced by a complex model using a simpler hierarchical model?
-
-# Our complex model is one that considers individual variation in animal movement, with increasing mean and variance for specific groups
-# We use a mixture modeling approach, where each component distribution is associated to an individual's state or age.
-# We assume that an individual's stage will affect their movement.
-# We assume, for example, very young birds might not move as far, as will nesting or molting birds, whereas adults will move more.
-
-# The overall assumption for this model is that individuals vary in how much they move, which we determine based on step lengths only.
-# With some groups having an overall larger variance and mean than other groups.
-# The proportions, or weights, of the mixture, should follow a bell curve for now
-# With the average movers being the majority of the group, and low or high movement individuals being less abundant.
-
 # Libraries -----------------------------------------------
 set.seed(20220201)
 
@@ -27,19 +14,7 @@ library(purrr)
 library(fitdistrplus)
 
 ## Functions ----------------------------------------------------
-# Building this function so that we get the parameters for a desired mean and standard deviation.
-desired_mean_sd <- function(mean, sd){
-
-  mu <- log(mean*2/(sqrt(mean*2+sd*2)))
-  sigsq <- log(1+(sd*2/mean*2))
-
-  return(data.frame(mu = mu, sigsq = sigsq))
-}
-
-exp.val <- function(mu, sigsq){
-  exp(mu + sqrt(sigsq))
-}
-
+source("Ch3_samplesize/Ch3_functions.R")
 
 # MIXTURE MODEL --------------------------------------------------
 ## Mixture proportions ----------------------------------------
@@ -51,15 +26,22 @@ hist(pis)
 ## Mixture components --------------------------------------
 # Since movement lengths are only positive, we use a lognormal distribution to describe them
 
-# CASE1: same variance for all, but change expected values
+# CASE1
 
-pars <- desired_mean_sd(mean = c(160, 300, 600, 1000), sd = c(90, 120, 160, 200))
+# desired_mean_sd <- function(mean, sd){
+#
[…]

### 2022-02-28 Ch3_samplesize/Ch3_process.R
Trying to tackle the mess. Moving old files out, and updating with the stuff from the local desktop.

@@ -61,7 +61,7 @@ save(truth_df, file = paste0("Ch3_samplesize/", dir_scenario, "/mixturesamples.R
 # This is the data that we consider our "truth"
 
 # Extract the tail (the highest values) to visualize later in the histogram since they are too few to show in the bins
-tru_tail <- data.frame(values = truth_df$x_samps, y = 100) %>% arrange(desc(values)) %>% filter(values >=100)
+tru_tail <- data.frame(values = truth_df$x_samps, y = 100) %>% arrange(desc(values)) %>% filter(values >=50)
 
 # Histogram plus the points in the tail.
 truth_df %>%
@@ -125,7 +125,7 @@ for(i in 1:nrow(mles_df)){
   ith_samps <- data.frame(x_star = sample(truth_df$x_samps, ith_n))
   ith_tail <- length(which(ith_samps$x_star >= ith_thresh))
   mles_df$tail_p[i] <- ith_tail/ith_n
-
+  
   # Fit Lomax
   optim_out <- optim(par=log(c(1.5, 1.5)), fn=nllike.simp, method="BFGS", Y=ith_samps$x_star)
   mles_star <- exp(optim_out$par)
@@ -133,14 +133,14 @@ for(i in 1:nrow(mles_df)){
   k_star <- mles_star[2]
   mles_df$alpha_star[i] <-alpha_star
   mles_df$k_star[i] <- k_star
-
+  
   # Check with Lomax GLM
   glm_out <- lomax.glm(formula=~1, my.dataf=ith_samps, response=ith_samps$x_star)
   alpha.2 <- glm_out$alphas.hat[1]
   k.2     <- glm_out$k.hat
   mles_df$alpha_glm[i] <-alpha.2
   mles_df$k_glm[i] <- k.2
-
+  
   # Check with GP fit
   ith_evd <- fevd(ith_samps$x_star, threshold = 0, type = "GP")
   gp_scale <- summary(ith_evd)$par[1]
@@ -149,22 +149,22 @@ for(i in 1:nrow(mles_df)){
   mles_df$k_GP[i] <- 1/gp_shape
   mles_df$scale[i] <- gp_scale
   mles_df$shape[i] <- gp_shape
-
-
-
+  
+  
+  
   # Estimate the tail
   #Lomax simple
   log_St_star <- lomax.St(x = ith_thresh,alpha = alpha_star,k = k_star,log.scale=TRUE)
[…]

### 2022-02-28 Ch3_samplesize/Ch3_scenarios.R

@@ -1,56 +1,97 @@
-# For the simulations, I want to consider four different scenarios
 
 # Libraries -----------------------------------------------
-set.seed(20220201)
+set.seed(271367)
 
-library(aracari)
 library(dplyr)
 library(ggplot2)
 library(cowplot)
 library(tidyr)
 library(purrr)
 library(fitdistrplus)
+library(extRemes)
+
 
 source("Ch3_samplesize/Ch3_functions.R")
 
-# ORIGINAL
-scenario <- "_original"
+# points_for_boxplots <- 50
+# B <- 1000
+
+points_for_boxplots <- 30
+B <- 100
+
+# ORIGINAL SCENARIO --------------------------------------
+dir_scenario <- "original"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
 desired_means <- c(28, 32, 40, 50)
 desired_sds <- c(49.7, 39.9, 33.3, 31.1)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-source("Ch3_samplesize/Ch3_simulation.R")
+source("Ch3_samplesize/Ch3_process.R")
 
-# 1) All groups have the same mean but different variance
-scenario <- "_case1"
+
+
+################################################################
+### These are only sort of test scenarios
+# Doing less simulations so they don't take as long
+
+points_for_boxplots <- 30
+B <- 100
+
+# SAME MEAN INCREASING SD ------------------------------
+dir_scenario <- "samemean_upsd"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
 desired_means <- c(30, 30, 30, 30)
 desired_sds <- c(20, 30, 40, 50)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-source("Ch3_samplesize/Ch3_simulation.R")
+source("Ch3_samplesize/Ch3_process.R")
 
-# 2) All groups have different means but the same variance
-scenario <- "_case2"
+#INCREASING MEANS DECRESING SD --------------------------------------
[…]

### 2022-02-28 Ch3_samplesize/PoncianoDesktopFeb26/Ch3_samplesize/Ch3_2-22-22.R

@@ -1,1149 +1,0 @@
-#################################
-## CH3 script
-#################################
-
-
-# Libraries -----------------------------------------------
-# set.seed(20220201)
-
-library(dplyr)
-library(ggplot2)
-library(cowplot)
-library(tidyr)
-library(purrr)
-library(fitdistrplus)
-library(extRemes)
-
-# Lnorm parms functions --------------------------------------
-
-desired_mean_sd <- function(mu_x, sd_x){
-
-  sigsq <- sd_x^2
-
-  mu <- log(mu_x^2/(sqrt(mu_x^2+sigsq)))
-  sigma_sq <- log(1+(sigsq/mu_x^2))
-  sigma <- sqrt(sigma_sq)
-
-  return(data.frame(meanlog = mu, sigma_sq = sigma_sq, sdlog = sigma))
-}
-
-# Now, for a Lnorm(meanlog, sdlog), get mean and var
-
-lnorm_mean_var <- function(mean_log, sd_log){
-
-  lnorm_mean <- exp(mean_log + ((sd_log^2)/2))
-  lnorm_var  <- (exp(sd_log^2)-1)*exp(2*mean_log+sd_log^2)
-  lnorm_sd   <- sqrt(lnorm_var)
-
-  return(data.frame(lnorm_mean, lnorm_var, lnorm_sd))
-}
-
-
-# ORIGINAL SCENARIO --------------------------------------
-dir_scenario <- "orig_feb26_tests"
-
-if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
-  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
-
-points_for_boxplots <- 100
-B <- 10
-
-desired_means <- c(28, 32, 40, 50)
-desired_sds <- c(49.7, 39.9, 33.3, 31.1)
-pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-
-## Mixture distribution --------------------------------------
-# We know that real data arise from a mix of complex processes.
-# We simulate our 'truth' from a mixture distribution
-
-# These are the weights for the distribution
-pis <- c( 0.1, 0.2, 0.3, 0.4)
-
-# The color associated to each mixture component
-dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
-
-# Build the densities for plotting
[…]

### 2022-02-28 Ch3_samplesize/PoncianoDesktopFeb26/Ch3_samplesize/Ch3_scenarios.R

@@ -1,29 +1,0 @@
-
-# Libraries -----------------------------------------------
-set.seed(22227)
-
-library(dplyr)
-library(ggplot2)
-library(cowplot)
-library(tidyr)
-library(purrr)
-library(fitdistrplus)
-library(extRemes)
-
-
-source("Ch3_samplesize/Ch3_functions.R")
-
-
-# ORIGINAL SCENARIO --------------------------------------
-dir_scenario <- "original"
-
-if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
-  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
-
-points_for_boxplots <- 50
-B <- 1000
-
-desired_means <- c(28, 32, 40, 50)
-desired_sds <- c(49.7, 39.9, 33.3, 31.1)
-pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-source("Ch3_samplesize/Ch3_process.R")

### 2022-02-28 Ch3_samplesize/mess/Ch3_scenarios.R

@@ -1,0 +1,56 @@
+# For the simulations, I want to consider four different scenarios
+
+# Libraries -----------------------------------------------
+set.seed(20220201)
+
+library(aracari)
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+library(tidyr)
+library(purrr)
+library(fitdistrplus)
+
+source("Ch3_samplesize/Ch3_functions.R")
+
+# ORIGINAL
+scenario <- "_original"
+desired_means <- c(28, 32, 40, 50)
+desired_sds <- c(49.7, 39.9, 33.3, 31.1)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/Ch3_simulation.R")
+
+# 1) All groups have the same mean but different variance
+scenario <- "_case1"
+desired_means <- c(30, 30, 30, 30)
+desired_sds <- c(20, 30, 40, 50)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/Ch3_simulation.R")
+
+# 2) All groups have different means but the same variance
+scenario <- "_case2"
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(25, 25, 25, 25)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/Ch3_simulation.R")
+
+# 3) Increasing mean and variance for groups
+scenario <- "_case3"
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(20, 30, 40, 50)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/Ch3_simulation.R")
+
+# 4) Increasing mean and decreasing variance for groups
+scenario <- "_case4"
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(30, 25, 15, 10)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/Ch3_simulation.R")
+
+
+
+
+
+
+

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Starting the md file for the figures

---
title: "Extreme Value Chapter"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r libraries}
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
```

```{r loadData}
path <- "Ch3_samplesize/original/"
load(paste0(path, "mixturesamples.RData"))
load(paste0(path, "nreps_mles_df.RData"))
load(paste0(path, "nonpar_glm.RData"))
load(paste0(path, "par_glm.RData"))
load(paste0(path, "GP_runs.RData"))

source("Ch3_samplesize/Ch3_functions.R")
```

# Figure 1

The mixture distribution used to generate the data:

```{r fig.width=12, fig.height=8}
desired_means <- c(28, 32, 40, 50)
desired_sds <- c(49.7, 39.9, 33.3, 31.1)
pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
# These are the weights for the distribution
pis <- c( 0.1, 0.2, 0.3, 0.4)

# The color associated to each mixture component
dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")

# Build the densities for plotting
weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))

# Plot density components of the mixture
ggplot() +
  weighted_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) -> densities_plot
# densities_plot

# Plot the means and sd for each of the curves
data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
  mutate(lo = desired_means - desired_sds,
         hi = desired_means + desired_sds) %>%
  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
  scale_color_manual(values = dens_cols) +
  labs(y = "Mean +/- SD") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") -> means_sd_plot
# means_sd_plot

# Align these plots to have multiple panels lates
top_row <- plot_grid(densities_plot, means_sd_plot, rel_widths = c(2,1))

tru_tail <- data.frame(values = truth_df$x_samps, y = 100) %>% arrange(desc(values)) %>% filter(values >=50)

# Histogram plus the points in the tail.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_histogram(bins = 100) +
  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
  labs(y = "Frequency", x = "Distance") +
  #lims(x = c(0, 150)) +
  theme_minimal() -> truth_hist
# truth_hist

# Density curve for the mixture based on the 50k samples.
truth_df %>%
  ggplot(., aes(x = x_samps)) +
  geom_density() +
  labs(y = "Density", x = "Distance") +
  lims(x = c(0, 150), y = c(0,0.05)) +
  theme_minimal() -> truth_density
# truth_density

# Visualize both in one frame
# plot_grid(truth_hist, truth_density)

## Figure 1 -----------------------------

bottom_row <- plot_grid(truth_hist, truth_density)

plot_grid(top_row, bottom_row,nrow = 2)

```

```{r}
# Stuff needed for plots later

# TEST VALUES --------------------------------------
## Thresholds ----------------
# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
# But we can know the quantiles of our sample.
# summary(truth_df$x_samps)
# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))

thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
tibble(thresh_tests) %>%
  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
         theta = n_overthresh/tru_n) -> thetas
thetas

## Sample sizes --------------------
samp_n_tests <- c(80, 200, 500, 800, 1000, 1600)

all_test_combos <- data.frame(expand.grid(thresh_tests = thresh_tests, samp_n_tests = samp_n_tests))
```

# Figure 2
Show the first comparisson between the Lomax and Lomax GLM estimations

```{r}
nreps_mles_df %>% 
  ggplot()

```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Working on Figure 1

@@
 library(purrr)
+library(MetBrewer)
 ```
@@
 source("Ch3_samplesize/Ch3_functions.R")
+```
+
+```{r}
+# Color palettes
+
+pal_sampsize <- met.brewer("Hokusai3", n = 6)
+pal_threshold <- met.brewer("Derain", n = 7)
+pal_mixture <- met.brewer("Hokusai1", n = 4)
+theta_color <- "steelblue"
+
 ```
@@
 # thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
+tru_n <- 50000
+w_samp_sizes <- pis*tru_n
 
@@
          theta = n_overthresh/tru_n) -> thetas
-thetas
 
@@
 
-# Figure 2
-Show the first comparisson between the Lomax and Lomax GLM estimations
+The actual values of theta for the 50k sample we took from the mixture distribution:
 
 ```{r}
-nreps_mles_df %>% 
-  ggplot()
+thetas %>% 
+  knitr::kable()
+```
+
+# Figure 2
+First let's see the true thetas, which because of small numbers we are visualizing in log scale for the second panel:
+
+```{r fig.width=10, fig.height=3}
+thetas %>% 
+  ggplot(., aes(x = thresh_tests, y = theta)) +
+  geom_point(size = 4, shape = 18, color = theta_color) +
+  labs(x = "Long-distance level", y = "Theta") +
+  theme_bw() -> a
+
+thetas %>% 
+  ggplot(., aes(x = thresh_tests, y = theta)) +
+  geom_point(size = 4, shape = 18, color = theta_color) +
+  labs(x = "Long-distance level", y = "Theta", Title = "Log Scale") +
+  theme_bw() +
+  scale_y_log10() -> b
+
+plot_grid(a, b, ncol = 2)
 
 ```
+
+Now, we explore how the estimates compare. These are already in log scale because they are small:
+
+```{r fig.width=12}
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_point() +
+  labs(x = "Long-distance level", y = "Estimated thetas") +
+  theme_bw()
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
I like the boxplots

@@
 
-```{r fig.width=10, fig.height=3}
+```{r fig.width=6, fig.height=2}
 thetas %>% 
@@
 
-```{r fig.width=12}
+```{r fig.width=6, fig.height=4}
 nreps_mles_df %>% 
@@
   # facet_wrap(~samp_n_tests, nrow = 1) +
-  geom_point() +
-  labs(x = "Long-distance level", y = "Estimated thetas") +
-  theme_bw()
+  geom_point(alpha = 0.8, size = 3, color = "grey27") +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() -> a
+
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_point(alpha = 0.8, size = 3, color = "grey27") +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() -> b
+
+plot_grid(a, b, nrow = 2)
 
 ```
+
+Since there are so many points, we can see them a little more scattered with jitter:
+
+```{r fig.width=6, fig.height=4}
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_jitter(alpha = 0.8, size = 3, color = "grey27") +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() -> a
+
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_jitter(alpha = 0.8, size = 3, color = "grey27") +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() -> b
+
+plot_grid(a, b, nrow = 2)
+```
+
+But we are seeing aggregated data, and we tested at different sample sizes:
+
+```{r fig.width=8, fig.height=4}
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_jitter(alpha = 0.8, size = 3, aes(color = factor(samp_n_tests))) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "Simple Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() +
+  theme(legend.position = "none") -> a
+
+nreps_mles_df %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_jitter(alpha = 0.8, size = 3, aes(color = factor(samp_n_tests))) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Long-distance level", y = "Estimated thetas", title = "GLM Lomax") +
+  scale_x_continuous(breaks = thresh_tests) +
+  theme_bw() +
+  theme(legend.position = "right") + 
+  guides(color = guide_legend(title = "Sample Size")) -> b
+
+ableg <- get_legend(b)
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```
+
+Can I see this as boxplots or something else? To see the differences in sample size more clearly.
+
+```{r fig.width=8, fig.height=4}
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat, fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Long-distance level", y = "Theta hat", title = "Simple Lomax") +
+  theme_bw() +
+  theme(legend.position = "none") -> a
+
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2, fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "Theta hat", title = "GLM Lomax") +
+  theme_bw() +
+  theme(legend.position = "right") -> b
+
+ableg <- get_legend(b)
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Figures updating

@@
 library(MetBrewer)
+library(stringr)
 ```
@@
 ```
+
+# Figure 3
+Introduce the numerical estimation thing with the simple lomax:
+
+```{r}
+nreps_mles_df %>% 
+  ggplot()+
+  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
+  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
+  scale_y_log10() +
+  scale_x_log10() +
+  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
+  labs(x = "Log(alpha)", y = "Log(k)", title = "Lomax Parameter Space") +
+  theme_bw() +
+  theme(legend.position = "bottom")
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Bias figure ready

--- 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
@@
 ```
+
+```{r eval = FALSE, fig.width=8, fig.height=4}
+
+# See it compared to the original theta
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "Simple Lomax") +
+  theme_bw() +
+  theme(legend.position = "none") -> a
+
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
+  theme_bw() +
+  theme(legend.position = "right") -> b
+
+ableg <- get_legend(b)
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```
+
+# Figure 3
+Introduce the numerical estimation thing with the simple lomax:
+
+```{r fig.width=7, fig.height=4}
+nreps_mles_df %>% 
+  ggplot()+
+  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
+  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
+  scale_y_log10() +
+  scale_x_log10() +
+  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
+  labs(x = "Log(alpha)", y = "Log(k)") +
+  theme_bw() +
+  theme(legend.position = "bottom") -> a
+
+nreps_mles_df %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>% 
+  ggplot()+
+  facet_wrap(~labelsamp) +
+  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
+  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
+  scale_y_log10() +
+  scale_x_log10() +
+  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
+  labs(x = "Log(alpha)", y = "Log(k)") +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.text = element_blank()) -> b
+
+ableg <- get_legend(a)
+
+top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2)
+
+plot_grid(top, ableg, nrow = 2, rel_heights = c(1, 0.1))
+
+```
+
+# Figure 4
+
+Do MSE? or bias to show that the are biased estimators:
+
+```{r fig.height=3, fig.width=7}
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  group_by(thresh_tests, samp_n_tests) %>% 
+  summarize(Eval_theta_hat = mean(log_St_hat2),
+            theta = mean(theta),
+            bias = Eval_theta_hat - theta) %>% 
+  ggplot(., aes(y = bias, x = thresh_tests)) +
+  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "Bias", title = "GLM Lomax") +
+  theme_bw()
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
MSE figure

@@
 
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests),
+         theta_diff= log_St_hat2 - theta) %>% 
+  group_by(thresh_tests, samp_n_tests) %>% 
+  summarize(Eval_theta_hat = mean(log_St_hat2),
+            MSE = mean(theta_diff)^2,
+            theta = mean(theta),
+            bias = Eval_theta_hat - theta) %>% 
+  ggplot(., aes(y = MSE, x = thresh_tests)) +
+  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
+  theme_bw()
+
 ```
+
+# Figure 5
+Bias correction
+
+```{r}
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Something isn't working.

@@
 
+long_corr_df %>% 
+  group_by(thresh_tests, samp_n_tests, type) %>% 
+  summarise(meanval = mean(value)) %>% 
+  ungroup() %>% 
+  right_join(., thetas[, c(1,3)]) %>% 
+  mutate(thresh_tests = factor(thresh_tests)) -> means_df
+
+par_glm %>% 
+  mutate(hat = theta_hat - theta,
+         bar = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, hat, bar) %>% 
+  pivot_longer(cols = c(hat, bar), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(correctiontype = "Parametric") -> corr_a
+
+nonpar_glm %>% 
+  mutate(hat = theta_hat - theta,
+         bar = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, hat, bar) %>% 
+  pivot_longer(cols = c(hat, bar), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(correctiontype = "Nonparametric") -> corr_b
+
+correction_df <- rbind.data.frame(corr_a, corr_b)
+
 ```
+
+```{r fig.height=10, fig.width=10}
+
+corr_a %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
+  facet_wrap(~labelsamp) +
+  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
+  scale_fill_manual(values = c("grey47", "white"), name = "Correction") +
+  labs(x = "Long-distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
+  theme_bw() +
+  scale_y_continuous(limits = quantile(long_corr_df$value, c(0.1, 0.9))) +
+  theme(legend.position = "none") -> a
+
+corr_b %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
+  facet_wrap(~labelsamp) +
+  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
+  scale_fill_manual(values = c("grey47", "white")) +
+  labs(x = "Long-distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
+  theme_bw() +
+  scale_y_continuous(limits = quantile(long_corr_df$value, c(0.1, 0.9))) +
+  theme(legend.position = "bottom") -> b
+
+plot_grid(a,b + theme(legend.position = "none"), nrow = 2)
+
+```

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Bias correction included.

--- 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
@@
 
+# long_corr_df %>% 
+#   group_by(thresh_tests, samp_n_tests, type) %>% 
+#   summarise(meanval = mean(value)) %>% 
+#   ungroup() %>% 
+#   right_join(., thetas[, c(1,3)]) %>% 
+#   mutate(thresh_tests = factor(thresh_tests)) -> means_df
+
+par_glm %>% 
+  mutate(Original = theta_hat - theta,
+         Corrected = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
+  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(correctiontype = "Parametric") -> corr_a
+
+nonpar_glm %>% 
+  mutate(Original = theta_hat - theta,
+         Corrected = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
+  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(correctiontype = "Nonparametric") -> corr_b
+
+correction_df <- rbind.data.frame(corr_a, corr_b)
+
 ```
+
+```{r fig.height=10, fig.width=10}
+
+corr_a %>% 
+  right_join(., thetas) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
+  facet_wrap(~labelsamp) +
+  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
+  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
+  scale_fill_manual(values = c("grey47", "white"), name = "") +
+  labs(x = "Long-distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
+  theme_bw() +
+  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
+  theme(legend.position = "right") -> a
+
+corr_b %>% 
+  right_join(., thetas) %>%
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
+  facet_wrap(~labelsamp) +
+  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
+  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
+  scale_fill_manual(values = c("grey47", "white"), name = "") +
+  labs(x = "Long-distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
+  theme_bw() +
+  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
+  theme(legend.position = "right") -> b
+
+plot_grid(a, b, nrow = 2)
+
+```

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Working slowly on the details

@@
     toc: yes
+    self_contained: false
 ---
@@
 library(stringr)
+library(latex2exp)
 ```
@@
 theta_color <- "steelblue"
+pal_bias <- met.brewer("Lakota", n=5)
 
@@
 dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
+# dens_cols <- pal_mixture
 
@@
 
-```{r fig.width=6, fig.height=2}
-thetas %>% 
-  ggplot(., aes(x = thresh_tests, y = theta)) +
-  geom_point(size = 4, shape = 18, color = theta_color) +
-  labs(x = "Long-distance level", y = "Theta") +
-  theme_bw() -> a
+```{r fig.width=5, fig.height=2.5}
+# thetas %>% 
+#   ggplot(., aes(x = thresh_tests, y = theta)) +
+#   geom_point(size = 4, shape = 18, color = theta_color) +
+#   labs(x = "Long-distance level", y = "Theta") +
+#   theme_bw() -> a
 
 thetas %>% 
-  ggplot(., aes(x = thresh_tests, y = theta)) +
-  geom_point(size = 4, shape = 18, color = theta_color) +
-  labs(x = "Long-distance level", y = "Theta", Title = "Log Scale") +
+  ggplot(., aes(x = thresh_tests, y = log(theta))) +
+  geom_point(size = 3, shape = 18, color = theta_color) +
+  labs(x = "Distance level", y = "log(theta)") +
+  scale_x_continuous(breaks = thresh_tests) +
   theme_bw() +
-  scale_y_log10() -> b
-
-plot_grid(a, b, ncol = 2)
+  theme(axis.text.x = element_text(angle = 30)) -> b
+b
+# plot_grid(a, b, ncol = 2)
 
@@
 
-Now, we explore how the estimates compare. These are already in log scale because they are small:
-
-```{r fig.width=6, fig.height=4}
+```{r eval = FALSE, fig.width=6, fig.height=4}
 nreps_mles_df %>% 
@@
 
-Since there are so many points, we can see them a little more scattered with jitter:
-
-```{r fig.width=6, fig.height=4}
+```{r eval = FALSE, fig.width=6, fig.height=4}
 nreps_mles_df %>% 
@@
 
-But we are seeing aggregated data, and we tested at different sample sizes:
-
-```{r fig.width=8, fig.height=4}
+```{r eval = FALSE, fig.width=8, fig.height=4}
 nreps_mles_df %>% 
@@
 
-Can I see this as boxplots or something else? To see the differences in sample size more clearly.
-
-```{r fig.width=8, fig.height=4}
+```{r eval = FALSE, fig.width=8, fig.height=4}
 nreps_mles_df %>% 
@@
 
-```{r eval = FALSE, fig.width=8, fig.height=4}
+```{r fig.width=8, fig.height=4}
 
@@
   scale_color_manual(values = pal_sampsize) +
-  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "Simple Lomax") +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
   theme_bw() +
@@
   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
   theme_bw() +
@@
 plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```
+
+```{r fig.width=10, fig.height=5}
+
+# See it compared to the original theta
+nreps_mles_df %>% 
+  filter(., thresh_tests < 250) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
+  theme_bw() +
+  theme(legend.position = "none") -> a1
+
+nreps_mles_df %>% 
+  filter(., thresh_tests >= 250) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Distance level", y = " ", subtitle = " ") +
+  theme_bw() +
+  theme(legend.position = "none") -> a2
+
+a <- plot_grid(a1, a2, ncol = 2)
+
+nreps_mles_df %>% 
+  filter(., thresh_tests < 250) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
+  theme_bw() +
+  theme(legend.position = "none") -> b1
+
+nreps_mles_df %>% 
+  filter(., thresh_tests >= 250) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Distance level", y = " ", subtitle = " ") +
+  theme_bw() +
+  theme(legend.position = "none") -> b2
+
+b2
+
+b <- plot_grid(b1, b2, ncol = 2)
+
+ableg <- get_legend(b + theme(legend.position = "right"))
+
+abplot <- plot_grid(a, b, nrow = 2, labels = c("A", "B"))
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.2))
 
@@
 ```
+
+```{r eval = FALSE, fig.width=10}
+corr_b %>% 
+  bind_rows(., corr_a) %>% 
+  right_join(., thetas) %>%
+  group_by(thresh_tests, samp_n_tests, type, correctiontype) %>% 
+  summarize(Eval_theta_hat = mean(value),
+            theta = mean(theta),
+            bias = Eval_theta_hat - theta) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>% 
+  mutate(bootcat = case_when(type == "Corrected" & correctiontype == "Nonparametric" ~ "NP - C",
+                             type == "Corrected" & correctiontype == "Parametric" ~ "P - C",
+                             type == "Original" & correctiontype == "Nonparametric" ~ "NP - UC",
+                             type == "Original" & correctiontype == "Parametric" ~ "P - UC")) %>% 
+  ggplot(., aes(y = bias, x = thresh_tests)) +
+  facet_wrap(~labelsamp) +
+  geom_jitter(aes(color = bootcat), size = 4, alpha = 0.8, width = 0.1) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = pal_bias, name = "") +
+  labs(x = "Long-distance level", y = "Bias") +
+  theme_bw()
+```
+
+# Figure 6
+Compare to the GP
+
+```{r fig.width=8, fig.height=4}
+
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
+  theme_bw() +
+  theme(legend.position = "right") -> b
+
+ableg <- get_legend(b)
+
+GP_mles %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
+  theme_bw() +
+  theme(legend.position = "none") -> a
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```
+
+```{r fig.width=8, fig.height=4}
+
+nreps_mles_df %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
+  theme_bw() +
+  theme(legend.position = "right") +
+  lims(y = c(-5, 5)) -> b
+
+ableg <- get_legend(b)
+
+GP_mles %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
+  theme_bw() +
+  theme(legend.position = "none")+
+  lims(y = c(-5, 5)) -> a
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+
+```

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Progress

@@
 nreps_mles_df %>% 
-  filter(., thresh_tests < 250) %>% 
+  filter(., thresh_tests < 500) %>% 
   mutate(samp_n_tests = factor(samp_n_tests),
@@
 nreps_mles_df %>% 
-  filter(., thresh_tests >= 250) %>% 
+  filter(., thresh_tests >= 500) %>% 
   mutate(samp_n_tests = factor(samp_n_tests),
@@
 
-b2
-
 b <- plot_grid(b1, b2, ncol = 2)
 
-ableg <- get_legend(b + theme(legend.position = "right"))
+ableg <- get_legend(b1 + theme(legend.position = "right"))
 
@@
   geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
-  geom_hline(yintercept = 0, color = "red") +
+  geom_hline(yintercept = 0, color = "grey") +
   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "Bias", title = "GLM Lomax") +
+  labs(x = "Distance level", y = "Bias", title = "GLM Lomax") +
   theme_bw()
 
-nreps_mles_df %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests),
-         theta_diff= log_St_hat2 - theta) %>% 
-  group_by(thresh_tests, samp_n_tests) %>% 
-  summarize(Eval_theta_hat = mean(log_St_hat2),
-            MSE = mean(theta_diff)^2,
-            theta = mean(theta),
-            bias = Eval_theta_hat - theta) %>% 
-  ggplot(., aes(y = MSE, x = thresh_tests)) +
-  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
-  geom_hline(yintercept = 0, color = "red") +
-  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
-  theme_bw()
+# 
+# nreps_mles_df %>% 
+#   mutate(samp_n_tests = factor(samp_n_tests),
+#          thresh_tests = factor(thresh_tests),
+#          theta_diff= log_St_hat2 - theta) %>% 
+#   group_by(thresh_tests, samp_n_tests) %>% 
+#   summarize(Eval_theta_hat = mean(log_St_hat2),
+#             MSE = mean(theta_diff)^2,
+#             theta = mean(theta),
+#             bias = Eval_theta_hat - theta) %>% 
+#   ggplot(., aes(y = MSE, x = thresh_tests)) +
+#   geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
+#   geom_hline(yintercept = 0, color = "red") +
+#   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
+#   labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
+#   theme_bw()
 

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
argh

@@
 
-```{r fig.height=3, fig.width=7}
+```{r fig.height=2.5, fig.width=5}
 nreps_mles_df %>% 
@@
   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Distance level", y = "Bias", title = "GLM Lomax") +
+  labs(x = "Distance level", y = "Bias", subtitle = "GLM Lomax") +
   theme_bw()
@@
 
-```{r fig.height=10, fig.width=10}
+```{r fig.width=12, fig.height=6}
+nonpar_glm %>% 
+  mutate(Original = theta_hat - theta,
+         # Corrected = log_theta_stars - theta,
+         Corrected = theta_bar - theta,) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
+  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  # filter(., thresh_tests < 500) %>% 
+  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
+  mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
+  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
+  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = c("black", "grey"), name = " ") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
+  theme_bw()
+
+```
+
+```{r fig.height=6, fig.width=12}
 
 corr_a %>% 
-  right_join(., thetas) %>% 
   mutate(samp_n_tests = factor(samp_n_tests),
@@
   ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
-  facet_wrap(~labelsamp) +
+  facet_wrap(~labelsamp, nrow=1) +
+  geom_hline(yintercept = 0, color = "red") +
   geom_boxplot(alpha = 0.9, outlier.shape = NA) +
-  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
   scale_fill_manual(values = c("grey47", "white"), name = "") +
-  labs(x = "Long-distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
+  labs(x = "Distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
   theme_bw() +
@@
 corr_b %>% 
-  right_join(., thetas) %>%
   mutate(samp_n_tests = factor(samp_n_tests),
@@
   ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
-  facet_wrap(~labelsamp) +
+  facet_wrap(~labelsamp, nrow=1) +
+  geom_hline(yintercept = 0, color = "red") +
   geom_boxplot(alpha = 0.9, outlier.shape = NA) +
-  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
   scale_fill_manual(values = c("grey47", "white"), name = "") +
-  labs(x = "Long-distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
+  labs(x = "Distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
   theme_bw() +

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Building figure for the mixtures.

@@
 ---
-title: "Extreme Value Chapter"
+title: "Extreme Value Chapter 3"
 author: "Javiera Rudolph"
@@
 
-# Figure 1
+# Figure 1 - the mixture scenarios considered
 
@@
 
-```{r fig.width=12, fig.height=8}
-desired_means <- c(28, 32, 40, 50)
-desired_sds <- c(49.7, 39.9, 33.3, 31.1)
-pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-# These are the weights for the distribution
-pis <- c( 0.1, 0.2, 0.3, 0.4)
+```{r Mixtures_FX}
+# Figure 1 function to make multiples
 
-# The color associated to each mixture component
-dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
-# dens_cols <- pal_mixture
+mixtures_plot_fx <- function(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds, weighted = FALSE){
 
-# Build the densities for plotting
-weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))
+  if(weighted == TRUE){
+    lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))
+  } else{
+    lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=1, alpha = 0.8))
+  }
 
@@
   ggplot() +
-  weighted_densities +
-  theme_minimal() +
+    lnorm_densities +
+    theme_minimal(base_size = 6) +
     labs(y = "Density") +
@@
     labs(y = "Mean +/- SD") +
-  theme_minimal() +
+    theme_minimal(base_size = 6) +
     theme(axis.title.x = element_blank(),
@@
   # Align these plots to have multiple panels lates
-top_row <- plot_grid(densities_plot, means_sd_plot, rel_widths = c(2,1))
+  plot_grid(NULL, means_sd_plot, densities_plot, rel_widths = c(0.1, 1, 3), nrow = 1)
+}
+
+```
+
+```{r fig.width=4, fig.height=5}
+# Scenarios:
+pis <- c( 0.1, 0.2, 0.3, 0.4)
+dens_cols <- pal_mixture
+
+# SAME SD INCREASING MEAN ------------------------------
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(25, 25, 25, 25)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+# SAME MEAN INCREASING SD ------------------------------
+desired_means <- c(30, 30, 30, 30)
+desired_sds <- c(20, 30, 40, 50)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+A2 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+# INCREASING SD INCREASING MEAN ------------------------------
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(20, 30, 40, 50)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+A3 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+# DECREASING BOTH ------------------------------
+desired_means <- c(60, 50, 40, 30)
+desired_sds <- c(50, 40, 30, 20)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+#INCREASING MEANS DECRESING SD --------------------------------------
+desired_means <- c(30, 35, 40, 50)
+desired_sds <- c(50, 40, 35, 30)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+A5 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
+ggsave("Ch3_samplesize/Figures/Figure1.png")
+```
+
+```{r}
+desired_means <- c(28, 32, 40, 50)
+desired_sds <- c(49.7, 39.9, 33.3, 31.1)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+# These are the weights for the distribution
+pis <- c( 0.1, 0.2, 0.3, 0.4)
+
+# The color associated to each mixture component
+dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
+# dens_cols <- pal_mixture
+
+top_row <- fig1_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
 

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 1 and the mixtures are ready

@@
 
+```
+
+```{r}
+# Stuff needed for plots later
+
+# TEST VALUES --------------------------------------
+## Thresholds ----------------
+# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
+# But we can know the quantiles of our sample.
+# summary(truth_df$x_samps)
+# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
+tru_n <- 50000
+w_samp_sizes <- pis*tru_n
+
+thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
+tibble(thresh_tests) %>%
+  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
+                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
+         theta = n_overthresh/tru_n) -> thetas
+
+## Sample sizes --------------------
+samp_n_tests <- c(80, 200, 500, 800, 1000, 1600)
+
+all_test_combos <- data.frame(expand.grid(thresh_tests = thresh_tests, samp_n_tests = samp_n_tests))
 ```
@@
 plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
-ggsave("Ch3_samplesize/Figures/Figure1.png")
+ggsave("Ch3_samplesize/Figures/Many_mixtures.png")
 ```
 
-```{r}
+```{r fig.width=6, fig.height=3}
 desired_means <- c(28, 32, 40, 50)
@@
 
-top_row <- fig1_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+# Build the densities for plotting
+weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=1, alpha = 0.8))
+
+# Plot density components of the mixture
+ggplot() +
+  weighted_densities +
+  theme_bw(base_size = 5) +
+  labs(y = "Component Densities") +
+  lims(x = c(0, 150)) -> densities_plot
+
+# Plot the means and sd for each of the curves
+data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
+  mutate(lo = desired_means - desired_sds,
+         hi = desired_means + desired_sds) %>%
+  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
+  geom_point(size = 2) +
+  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
+  scale_color_manual(values = dens_cols) +
+  labs(y = "Mean +/- SD") +
+  theme_bw(base_size = 5) +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        legend.position = "none") -> means_sd_plot
 
@@
   geom_histogram(bins = 100) +
-  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
-  labs(y = "Frequency", x = "Distance") +
+  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "grey47", alpha = 0.5, size = 1) +
+  geom_vline(xintercept = thresh_tests, color = dens_cols[4], linetype = "dashed", size = 0.3) +
+  labs(y = "Frequency in Population", x = "Distance") +
   #lims(x = c(0, 150)) +
-  theme_minimal() -> truth_hist
+  theme_bw(base_size = 5) -> truth_hist
 # truth_hist
@@
   geom_density() +
-  labs(y = "Density", x = "Distance") +
+  labs(y = "Mixture Density", x = "Distance") +
   lims(x = c(0, 150), y = c(0,0.05)) +
-  theme_minimal() -> truth_density
+  theme_bw(base_size = 5) +
+  theme(axis.title.x = element_blank()) -> truth_density
 # truth_density
@@
 
-bottom_row <- plot_grid(truth_hist, truth_density)
+top_row <- plot_grid(means_sd_plot, densities_plot, truth_density, nrow = 1, rel_widths = c(1,2,2), labels = "AUTO", label_size = 6)
 
-plot_grid(top_row, bottom_row,nrow = 2)
+plot_grid(top_row, truth_hist, nrow = 2, labels = c("", "D"), label_size = 6)
+ggsave("Ch3_samplesize/Figures/Figure1.png")
 
-```
-
-```{r}
-# Stuff needed for plots later
-
-# TEST VALUES --------------------------------------
-## Thresholds ----------------
-# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
-# But we can know the quantiles of our sample.
-# summary(truth_df$x_samps)
-# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
-tru_n <- 50000
-w_samp_sizes <- pis*tru_n
-
-thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
-tibble(thresh_tests) %>%
-  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
-                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
-         theta = n_overthresh/tru_n) -> thetas
-
-## Sample sizes --------------------
-samp_n_tests <- c(80, 200, 500, 800, 1000, 1600)
-
-all_test_combos <- data.frame(expand.grid(thresh_tests = thresh_tests, samp_n_tests = samp_n_tests))
 ```

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 1 is ready and in the word document now

--- 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
@@
 
-# Figure 1 - the mixture scenarios considered
+```{r}
+# Stuff needed for plots later
+
+# TEST VALUES --------------------------------------
+## Thresholds ----------------
+# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
+# But we can know the quantiles of our sample.
+# summary(truth_df$x_samps)
+# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
+tru_n <- 50000
+w_samp_sizes <- pis*tru_n
+
+thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
+tibble(thresh_tests) %>%
+  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
+                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
+         theta = n_overthresh/tru_n) -> thetas
+
+## Sample sizes --------------------
+samp_n_tests <- c(80, 200, 500, 800, 1000, 1600)
+
+all_test_combos <- data.frame(expand.grid(thresh_tests = thresh_tests, samp_n_tests = samp_n_tests))
+```
+
+# Figure 1
 
@@
 
-top_row <- fig1_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+# Build the densities for plotting
+weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=1, alpha = 0.8))
+
+# Plot density components of the mixture
+ggplot() +
+  weighted_densities +
+  theme_bw(base_size = 7) +
+  labs(y = "Component Densities") +
+  lims(x = c(0, 150)) -> densities_plot
+
+# Plot the means and sd for each of the curves
+data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
+  mutate(lo = desired_means - desired_sds,
+         hi = desired_means + desired_sds) %>%
+  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
+  geom_point(size = 2) +
+  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
+  scale_color_manual(values = dens_cols) +
+  labs(y = "Mean +/- SD") +
+  theme_bw(base_size = 7) +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        legend.position = "none") -> means_sd_plot
 
@@
   geom_histogram(bins = 100) +
-  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "black", alpha = 0.5) +
+  geom_point(data = tru_tail[1:50,], aes(x = values, y = y), color = "grey47", alpha = 0.9, size = 1) +
+  geom_vline(xintercept = thresh_tests, color = dens_cols[4], linetype = "dashed", size = 0.3) +
   labs(y = "Frequency", x = "Distance") +
   #lims(x = c(0, 150)) +
-  theme_minimal() -> truth_hist
+  theme_bw(base_size = 7) -> truth_hist
 # truth_hist
@@
   geom_density() +
-  labs(y = "Density", x = "Distance") +
+  labs(y = "Mixture Density", x = "Distance") +
   lims(x = c(0, 150), y = c(0,0.05)) +
-  theme_minimal() -> truth_density
+  theme_bw(base_size = 7) +
+  theme(axis.title.x = element_blank()) -> truth_density
 # truth_density
@@
 
-bottom_row <- plot_grid(truth_hist, truth_density)
+top_row <- plot_grid(means_sd_plot, densities_plot, truth_density, nrow = 1, rel_widths = c(1,2,2), labels = "AUTO", label_size = 8)
 
-plot_grid(top_row, bottom_row,nrow = 2)
+plot_grid(top_row, truth_hist, nrow = 2, labels = c("", "D"), label_size = 8)
+ggsave("Ch3_samplesize/Figures/Figure1.png")
 
@@
 
-```{r}
-# Stuff needed for plots later
-
-# TEST VALUES --------------------------------------
-## Thresholds ----------------
-# Thresholds based on quantiles: because when we have a sample, we still don't know the truth
-# But we can know the quantiles of our sample.
-# summary(truth_df$x_samps)
-# thresh_tests <- round(quantile(truth_df$x_samps, c(0.5, 0.75, 0.9, 0.99, 0.999, 0.9999), names = FALSE))
-tru_n <- 50000
-w_samp_sizes <- pis*tru_n
-
-thresh_tests <- c(50, 100, 150, 250, 500, 750, 1000)
-tibble(thresh_tests) %>%
-  mutate(n_overthresh = map_dbl(1:length(thresh_tests),
-                                function(y) length(which(truth_df$x_samps >= thresh_tests[y]))),
-         theta = n_overthresh/tru_n) -> thetas
-
-## Sample sizes --------------------
-samp_n_tests <- c(80, 200, 500, 800, 1000, 1600)
-
-all_test_combos <- data.frame(expand.grid(thresh_tests = thresh_tests, samp_n_tests = samp_n_tests))
-```
+# Table 1
 
@@
   knitr::kable()
+write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
 ```

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 2 is ready and in the document.

@@
 
-```{r fig.width=8, fig.height=4}
+```{r fig.width=6, fig.height=5}
 
@@
   scale_color_manual(values = pal_sampsize) +
-  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
-  theme_bw() +
+  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
+  theme_bw(base_size = 7) +
   theme(legend.position = "none") -> a
@@
   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
-  theme_bw() +
+  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
+  theme_bw(base_size = 7) +
   theme(legend.position = "right") -> b
@@
 
-abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+GP_mles %>% 
+    mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
+  theme_bw(base_size = 7) +
+  theme(legend.position = "none") -> c
+
+abplot <- plot_grid(a, b + theme(legend.position = "none"), c, nrow = 3)
 
 plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+ggsave("Ch3_samplesize/Figures/Figure2.png")
 
@@
 
-```{r fig.width=10, fig.height=5}
+```{r eval=FALSE, fig.width=10, fig.height=5}
 

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Figure 3 for parameter estimation is ready and in the word document.

--- 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
@@
 # Figure 2
-First let's see the true thetas, which because of small numbers we are visualizing in log scale for the second panel:
 
-```{r fig.width=5, fig.height=2.5}
+```{r eval=FALSE, fig.width=5, fig.height=2.5}
 # thetas %>% 
@@
 
-```{r fig.width=8, fig.height=4}
+```{r fig.width=6, fig.height=4}
 
@@
   scale_color_manual(values = pal_sampsize) +
-  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
-  theme_bw() +
+  labs(x = " ", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Simple Lomax") +
+  theme_bw(base_size = 8) +
   theme(legend.position = "none") -> a
@@
   scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
-  theme_bw() +
+  labs(x = "", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "GLM Lomax") +
+  theme_bw(base_size = 8) +
   theme(legend.position = "right") -> b
@@
 
-abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
+GP_mles %>% 
+    mutate(samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
+  # facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_fill_manual(values = pal_sampsize) +
+  scale_color_manual(values = pal_sampsize) +
+  labs(x = "Distance level", y = TeX(r'($log(\hat{\theta} / \theta)$)'), subtitle = "Generalized Pareto") +
+  theme_bw(base_size = 8) +
+  theme(legend.position = "none") -> c
 
-plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
+abplot <- plot_grid(a, b + theme(legend.position = "none"), c, nrow = 3, labels = "AUTO", label_size = 8)
+
+plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.2))
+ggsave("Ch3_samplesize/Figures/Figure2.png")
 
@@
 
-```{r fig.width=7, fig.height=4}
+```{r fig.width=4, fig.height=2.5}
 nreps_mles_df %>% 

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Working on Figure 4

@@
 
-```{r fig.width=4, fig.height=2.5}
+```{r fig.width=6, fig.height=3}
 nreps_mles_df %>% 
@@
 
-top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2)
+top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2, labels = "AUTO", label_size = 8)
 
 plot_grid(top, ableg, nrow = 2, rel_heights = c(1, 0.1))
+ggsave("Ch3_samplesize/Figures/Figure3.png")
 
@@
 
-Do MSE? or bias to show that the are biased estimators:
+Bias correction in GLM Lomax
 
-```{r fig.height=2.5, fig.width=5}
+```{r eval = FALSE, fig.height=2.5, fig.width=5}
 nreps_mles_df %>% 
@@
 ```
-
-# Figure 5
-Bias correction
 

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Working on the parametric and nonpar correction figures.

@@
 ```{r fig.width=12, fig.height=6}
+
+lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
+extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")
+
 nonpar_glm %>% 
   mutate(Original = theta_hat - theta,
-         # Corrected = log_theta_stars - theta,
-         Corrected = theta_bar - theta,) %>% 
+         Corrected = theta_bar - theta) %>% 
   dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
@@
   filter(., !is.infinite(value)) %>% 
-  # filter(., thresh_tests < 500) %>% 
-  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests)) %>% 
-  mutate(labelsamp = paste("n =", samp_n_tests),
-         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
-  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
+  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
+         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
+         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
+         samp_n_tests = factor(samp_n_tests)) %>% 
   ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
@@
   scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
+  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Nonparametric") +
+  theme_bw()
+
+```
+
+```{r fig.width=12, fig.height=6}
+
+lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
+extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")
+
+par_glm %>% 
+  mutate(Original = theta_hat - theta,
+         Corrected = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
+  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
+         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
+         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
+  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = c("black", "grey"), name = " ") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Parametric") +
   theme_bw()

### 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
Trying to knit this but is going slow.

@@
 tru_n <- 50000
+pis <- c( 0.1, 0.2, 0.3, 0.4)
 w_samp_sizes <- pis*tru_n
@@
   knitr::kable()
-write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
+# write.csv(thetas, file = "Ch3_samplesize/Figures/table1.csv")
 ```

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Figure 6 is sort of mixed with 2 now.

--- 2022-03-01 Ch3_samplesize/Figures_Ch3.Rmd
@@
     toc: yes
-    self_contained: false
 ---
@@
 
-```{r fig.width=12, fig.height=6}
+```{r eval = FALSE, fig.width=12, fig.height=6}
+
+lowlabs <- paste0("n = ", samp_n_tests[1:6], "-lower")
+extlabs <- paste0("n = ", samp_n_tests[1:6], "-extremes")
+
 nonpar_glm %>% 
   mutate(Original = theta_hat - theta,
-         # Corrected = log_theta_stars - theta,
-         Corrected = theta_bar - theta,) %>% 
+         Corrected = theta_bar - theta) %>% 
   dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
@@
   filter(., !is.infinite(value)) %>% 
-  # filter(., thresh_tests < 500) %>% 
-  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower dist", "extremes"), levels = c("lower dist", "extremes"))) %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
+  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
+         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
+         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
+         samp_n_tests = factor(samp_n_tests),
          thresh_tests = factor(thresh_tests)) %>% 
-  mutate(labelsamp = paste("n =", samp_n_tests),
-         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
-  mutate(onelinelabel = paste0(labelsamp,"-",thresholdsep)) %>% 
+  ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
+  facet_wrap(~onelinelabel, nrow = 2, scales = "free") +
+  geom_boxplot(alpha = 0.9) +
+  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = c("black", "grey47"), name = " ") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Nonparametric") +
+  theme_bw(base_size = 10) -> nonpar_bxplts
+
+par_glm %>% 
+  mutate(Original = theta_hat - theta,
+         Corrected = theta_bar - theta) %>% 
+  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
+  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
+  filter(., !is.infinite(value)) %>% 
+  mutate(thresholdsep = factor(ifelse(thresh_tests<500, "lower", "extremes"), levels = c("lower", "extremes")),
+         onelinelabel = paste0("n = ", samp_n_tests, "-", thresholdsep),
+         onelinelabel = factor(onelinelabel, levels = c(lowlabs, extlabs)),
+         samp_n_tests = factor(samp_n_tests),
+         thresh_tests = factor(thresh_tests)) %>% 
   ggplot(., aes(x = thresh_tests, y = value, fill = samp_n_tests, color = type)) +
@@
   scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Distance level", y = "Estimates of theta", subtitle = " ") +
-  theme_bw()
+  labs(x = "Distance level", y = "Estimates of theta", subtitle = "Parametric") +
+  theme_bw(base_size = 10) -> par_bxplts
+
+bxplts_legend <- get_legend(par_bxplts)
+
+bxplts <- plot_grid(nonpar_bxplts+ theme(legend.position = "none"),
+          par_bxplts + theme(legend.position = "none"), nrow = 2)
+
+plot_grid(bxplts, bxplts_legend, ncol = 2, rel_widths = c(1, 0.1))
 
@@
   theme_bw() +
-  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
+  # scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
   theme(legend.position = "right") -> a
@@
   theme_bw() +
-  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
+  # scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
   theme(legend.position = "right") -> b
@@
 ```
-
-# Figure 6
-Compare to the GP
-
-```{r fig.width=8, fig.height=4}
-
-nreps_mles_df %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests)) %>% 
-  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
-  # facet_wrap(~samp_n_tests, nrow = 1) +
-  geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
-  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
-  theme_bw() +
-  theme(legend.position = "right") -> b
-
-ableg <- get_legend(b)
-
-GP_mles %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests)) %>% 
-  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
-  # facet_wrap(~samp_n_tests, nrow = 1) +
-  geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
-  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
-  theme_bw() +
-  theme(legend.position = "none") -> a
-
-abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
-
-plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
-
-```
-
-```{r fig.width=8, fig.height=4}
-
-nreps_mles_df %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests)) %>% 
-  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
-  # facet_wrap(~samp_n_tests, nrow = 1) +
-  geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
-  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
-  theme_bw() +
-  theme(legend.position = "right") +
-  lims(y = c(-5, 5)) -> b
-
-ableg <- get_legend(b)
-
-GP_mles %>% 
-  mutate(samp_n_tests = factor(samp_n_tests),
-         thresh_tests = factor(thresh_tests)) %>% 
-  ggplot(., aes(x = thresh_tests, y = log(quant_theta/theta), fill = samp_n_tests, color = samp_n_tests)) +
-  # facet_wrap(~samp_n_tests, nrow = 1) +
-  geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
-  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
-  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
-  labs(x = "Long-distance level", y = "log(GP_theta/theta)", title = "Generalized Pareto") +
-  theme_bw() +
-  theme(legend.position = "none")+
-  lims(y = c(-5, 5)) -> a
-
-abplot <- plot_grid(a, b + theme(legend.position = "none"), nrow = 2)
-
-plot_grid(abplot, ableg, ncol = 2, rel_widths = c(1, 0.3))
-
-```

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
what am I even doing?

@@
 
-```{r fig.height=6, fig.width=12}
+```{r fig.height=4, fig.width=12}
 
@@
   geom_hline(yintercept = 0, color = "red") +
-  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
+  geom_boxplot(alpha = 0.9) +
   scale_fill_manual(values = c("grey47", "white"), name = "") +

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Pretty sure all figures are ready now.

@@
 
-Bias correction in GLM Lomax
+Bias correction
 
@@
 
-```{r fig.height=4, fig.width=12}
+```{r eval=FALSE, fig.height=6, fig.width=12}
 
@@
 ```
+
+Nonparametric bootstrap correction for both the GLM Lomax and GP
+
+```{r fig.width=10, fig.height=4}
+dir_scenario <- "allinone_original"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+# allin1df %>%
+#   ggplot(., aes(x = factor(thresh_tests), y = log(gp_theta_hat/theta))) +
+#   geom_hline(yintercept = 0, color = "red") +
+#   geom_boxplot() -> a
+# 
+# allin1df %>%
+#   ggplot(., aes(x = factor(thresh_tests), y = log(gp_theta_bar/theta))) +
+#   geom_hline(yintercept = 0, color = "red") +
+#   geom_boxplot() -> b
+# 
+# plot_grid(a,b, ncol = 2)
+```
+
+```{r Fig4, fig.width=12, fig.height=5}
+
+allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
+  facet_wrap(~labelsamp, nrow = 2) +
+  geom_boxplot() +
+  scale_color_manual(values = pal_mixture[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = pal_mixture[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red") +
+  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
+  theme_bw()
+ggsave("Ch3_samplesize/Figures/Figure4.png")
+```
+
+```{r Figure5, fig.width=12, fig.height=4}
+
+i_threshold <- 50
+
+allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) -> readyplot_df
+
+baseplot_fx <- function(i_threshold){readyplot_df %>% 
+  filter(., thresh_tests == i_threshold) %>% 
+  ggplot(., aes(x = samp_n_tests, y = theta_val, color = type, fill = samp_n_tests)) +
+  # facet_wrap(~thresh_tests, scales = "free", ncol=4) +
+  geom_boxplot() +
+  scale_color_manual(values = c("black", "grey"), name = "Estimator") +
+  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
+  geom_hline(yintercept = 0, color = "red") +
+  labs(y = "Theta ratio", subtitle = paste("Dist. level =", i_threshold)) +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title.x = element_blank())}
+
+baseplot <- baseplot_fx(50) +
+  theme(legend.position = "right",
+        legend.box = "horizontal") +
+  guides(fill = guide_legend(ncol = 2))
+
+baselegend <- get_legend(baseplot)
+
+# Distance level plots
+
+t50 <- baseplot_fx(50)
+t100 <- baseplot_fx(100)
+t150 <- baseplot_fx(150)
+t250 <- baseplot_fx(250)
+t500 <- baseplot_fx(500)
+t750 <- baseplot_fx(750)
+t1000 <- baseplot_fx(1000)
+
+toprow <- plot_grid(t50, t100, t150, t250, nrow = 1) 
+bottomrow <- plot_grid(t500, t750, t1000, baselegend, nrow = 1)
+
+plot_grid(toprow, bottomrow, nrow=2)
+ggsave("Ch3_samplesize/Figures/Figure5.png")
+
+```
+
+```{r eval = FALSE, fig.width=12, fig.height=3}
+
+allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, lomax_theta_hat, lomax_theta_bar, theta) %>%
+  mutate(original = lomax_theta_hat - log(theta),
+         corrected = lomax_theta_bar - log(theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  ggplot(., aes(x = factor(thresh_tests), y = theta_val, color = type)) +
+  facet_wrap(~samp_n_tests, nrow = 1) +
+  geom_boxplot() +
+  geom_hline(yintercept = 0, color = "red") +
+  theme_bw()
+```
+
+```{r eval=FALSE}
+
+allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, lomax_theta_hat, lomax_theta_bar, theta) %>%
+  mutate(original = lomax_theta_hat,
+         corrected = lomax_theta_bar) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  group_by(thresh_tests, samp_n_tests, type) %>%
+  summarise(ExpVal_theta_hat = mean(theta_val),
+            theta = log(mean(theta)),
+            bias = ExpVal_theta_hat - theta) %>%
+  ggplot(., aes(x = thresh_tests, y = bias, color = type)) +
+  facet_wrap(~samp_n_tests) +
+  geom_point() +
+  theme_bw()
+
+allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = gp_theta_hat,
+         corrected = gp_theta_bar) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  group_by(thresh_tests, samp_n_tests, type) %>%
+  summarise(ExpVal_theta_hat = mean(theta_val),
+            theta = mean(theta),
+            bias = ExpVal_theta_hat - theta) %>%
+  ggplot(., aes(x = thresh_tests, y = bias, color = type)) +
+  facet_wrap(~samp_n_tests) +
+  geom_point() +
+  theme_bw()
+
+```

### 2022-03-02 Ch3_samplesize/allinone_original.R
Ok, running these all in ones for the additional scenarios.

@@ -1,0 +1,254 @@
+#
+# # Libraries -----------------------------------------------
+# set.seed(271367)
+#
+# library(dplyr)
+# library(ggplot2)
+# library(cowplot)
+# library(tidyr)
+# library(purrr)
+# library(fitdistrplus)
+# library(extRemes)
+#
+#
+# source("Ch3_samplesize/Ch3_functions.R")
+#
+# # points_for_boxplots <- 50
+# # B <- 1000
+#
+# points_for_boxplots <- 50
+# B <- 200
+#
+# # ORIGINAL SCENARIO --------------------------------------
+# dir_scenario <- "allinone_original"
+#
+# if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+#   dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+#
+# desired_means <- c(28, 32, 40, 50)
+# desired_sds <- c(49.7, 39.9, 33.3, 31.1)
+# pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+
+
+
+
+
+
+
+
+
+# Data simulation ---------------------------
+
+# These are the weights for the distribution
+pis <- c( 0.1, 0.2, 0.3, 0.4)
+
+# The color associated to each mixture component
+dens_cols <- c("#264653", "#2a9d8f", "#f4a261", "#e76f51")
+
+# Build the densities for plotting
+weighted_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm, args = list(meanlog = pars$meanlog[y], sdlog = pars$sdlog[y]), color = dens_cols[y], size=pis[y]*5, alpha = 0.8))
+
+# Plot density components of the mixture
+ggplot() +
+  weighted_densities +
+  theme_minimal() +
+  labs(y = "Density") +
+  lims(x = c(0, 150)) -> densities_plot
+# densities_plot
+
+# Plot the means and sd for each of the curves
+data.frame(desired_means, desired_sds, gID = factor(1:4)) %>%
+  mutate(lo = desired_means - desired_sds,
+         hi = desired_means + desired_sds) %>%
+  ggplot(., aes(x = gID, y = desired_means, color = gID)) +
+  geom_point(size = 2) +
+  geom_errorbar(aes(ymin = lo, ymax = hi), width = 0.1, size = 1) +
+  scale_color_manual(values = dens_cols) +
[…]

### 2022-03-02 Ch3_samplesize/allinone_scenarios.R

@@ -1,0 +1,77 @@
+# Get results for this on the allinone script
+
+
+
+# Libraries -----------------------------------------------
+set.seed(271367)
+
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+library(tidyr)
+library(purrr)
+library(fitdistrplus)
+library(extRemes)
+
+
+source("Ch3_samplesize/Ch3_functions.R")
+
+# points_for_boxplots <- 50
+# B <- 1000
+
+points_for_boxplots <- 30
+B <- 100
+
+
+
+# SAME MEAN INCREASING SD ------------------------------
+dir_scenario <- "ain1_samemean_upsd"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
+desired_means <- c(30, 30, 30, 30)
+desired_sds <- c(20, 30, 40, 50)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+#INCREASING MEANS DECRESING SD --------------------------------------
+dir_scenario <- "ain1_upmean_downsd"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
+desired_means <- c(30, 35, 40, 50)
+desired_sds <- c(50, 40, 35, 30)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+# SAME SD INCREASING MEAN ------------------------------
+dir_scenario <- "ain1_samesd_upmean"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
+desired_means <- c(30, 40, 50, 60)
+desired_sds <- c(25, 25, 25, 25)
+pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+
+# INCREASING SD INCREASING MEAN ------------------------------
+dir_scenario <- "ain1_upsd_upmean"
+
+if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
+  dir.create(paste0("Ch3_samplesize/", dir_scenario))}
+
+desired_means <- c(30, 40, 50, 60)
[…]

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Cleaning up. Ready to run the other scenarios.

@@
   geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
   scale_fill_manual(values = pal_sampsize) +
@@
   geom_boxplot(alpha = 0.9) +
-  geom_hline(yintercept = 0, color = "red") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
   scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
@@
 
-```{r Fig4, fig.width=12, fig.height=5}
+```{r Fig4, fig.width=6, fig.height=6}
 
@@
   ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
-  facet_wrap(~labelsamp, nrow = 2) +
+  facet_wrap(~labelsamp, nrow = 3) +
   geom_boxplot() +
-  scale_color_manual(values = pal_mixture[c(1,4)], name = "Bias") +
-  scale_fill_manual(values = pal_mixture[c(2,3)], name = "Bias") +
-  geom_hline(yintercept = 0, color = "red") +
+  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
   labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +

### 2022-03-02 Ch3_samplesize/allinone_scenarios.R

@@ -33,6 +33,8 @@ if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
 desired_means <- c(30, 30, 30, 30)
 desired_sds <- c(20, 30, 40, 50)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/allinone.R")
+
 
 #INCREASING MEANS DECRESING SD --------------------------------------
 dir_scenario <- "ain1_upmean_downsd"
@@ -43,6 +45,7 @@ if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
 desired_means <- c(30, 35, 40, 50)
 desired_sds <- c(50, 40, 35, 30)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/allinone.R")
 
 # SAME SD INCREASING MEAN ------------------------------
 dir_scenario <- "ain1_samesd_upmean"
@@ -53,6 +56,7 @@ if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
 desired_means <- c(30, 40, 50, 60)
 desired_sds <- c(25, 25, 25, 25)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/allinone.R")
 
 # INCREASING SD INCREASING MEAN ------------------------------
 dir_scenario <- "ain1_upsd_upmean"
@@ -63,6 +67,7 @@ if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
 desired_means <- c(30, 40, 50, 60)
 desired_sds <- c(20, 30, 40, 50)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/allinone.R")
 
 # DECREASING BOTH ------------------------------
 dir_scenario <- "ain1_downsd_downmean"
@@ -73,5 +78,6 @@ if(dir.exists(paste0("Ch3_samplesize/", dir_scenario)) == FALSE){
 desired_means <- c(60, 50, 40, 30)
 desired_sds <- c(50, 40, 30, 20)
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
+source("Ch3_samplesize/allinone.R")
 
 

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Writing code to see if it works to bring in the other mixture simulations.

@@
 
+bias_bxplot_fx <- function(data){
+  data %>% 
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
+  facet_wrap(~labelsamp, nrow = 1) +
+  geom_boxplot() +
+  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
+  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
+  theme_bw()
+}
+
 ```
@@
 A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+dir_scenario <- "ain1_samesd_upmean"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B1 <- bias_bxplot_fx(allin1df)
 

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
working on the appendix figure.

--- 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
@@
 
+bias_bxplot_fx <- function(data){
+  data %>% 
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
+  facet_wrap(~labelsamp, nrow = 1) +
+  geom_boxplot() +
+  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
+  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
+  theme_bw() +
+    theme(legend.position = "none")
+}
+
 ```
@@
 
+dir_scenario <- "ain1_samesd_upmean"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B1 <- bias_bxplot_fx(allin1df)
+
 # SAME MEAN INCREASING SD ------------------------------
@@
 A2 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+dir_scenario <- "ain1_samemean_upsd"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B2 <- bias_bxplot_fx(allin1df)
 
@@
 
+dir_scenario <- "ain1_upsd_upmean"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B3 <- bias_bxplot_fx(allin1df)
+
 # DECREASING BOTH ------------------------------
@@
 A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
+
+dir_scenario <- "ain1_downsd_downmean"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B4 <- bias_bxplot_fx(allin1df)
 
@@
 
-plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
+dir_scenario <- "ain1_upmean_downsd"
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+
+B5 <- bias_bxplot_fx(allin1df)
+
+Bs <- plot_grid(B1, B2, B3, B4, ncol = 1)
+As <- plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
+
 ggsave("Ch3_samplesize/Figures/Many_mixtures.png")
+```
+```{r}
+Bs
 ```

### 2022-03-03 Ch3_samplesize/Figures_Ch3.Rmd
Mixtures figure is done

--- 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
@@
 
+bias_bxplot_fx <- function(data){
+  data %>% 
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
+  # facet_wrap(~labelsamp, nrow = 1) +
+  geom_boxplot() +
+  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
+  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = " ") +
+  theme_bw(base_size = 8) +
+  theme(legend.position = "none")
+}
+
 ```
 
-```{r fig.width=4, fig.height=5}
+```{r fig.width=10, fig.height=5}
 # Scenarios:
@@
 # SAME SD INCREASING MEAN ------------------------------
+dir_scenario <- "ain1_samesd_upmean"
+
 desired_means <- c(30, 40, 50, 60)
@@
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-
 A1 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
 
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+B1 <- bias_bxplot_fx(allin1df)
+
 # SAME MEAN INCREASING SD ------------------------------
+
+dir_scenario <- "ain1_samemean_upsd"
+
 desired_means <- c(30, 30, 30, 30)
@@
 
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+B2 <- bias_bxplot_fx(allin1df)
+
 # INCREASING SD INCREASING MEAN ------------------------------
+dir_scenario <- "ain1_upsd_upmean"
+
 desired_means <- c(30, 40, 50, 60)
@@
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-
 A3 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
 
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+B3 <- bias_bxplot_fx(allin1df)
+
 # DECREASING BOTH ------------------------------
+dir_scenario <- "ain1_downsd_downmean"
+
 desired_means <- c(60, 50, 40, 30)
@@
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-
 A4 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
 
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+B4 <- allin1df %>%
+  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
+  mutate(original = log(gp_theta_hat/theta),
+         corrected = log(gp_theta_bar/theta)) %>%
+  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
+  drop_na() %>%
+  mutate(thresh_tests = factor(thresh_tests),
+         samp_n_tests = factor(samp_n_tests)) %>% 
+  mutate(labelsamp = paste("n =", samp_n_tests),
+         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
+  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
+  # facet_wrap(~labelsamp, nrow = 1) +
+  geom_boxplot() +
+  scale_color_manual(values = dens_cols[c(1,4)], name = "Bias") +
+  scale_fill_manual(values = dens_cols[c(2,3)], name = "Bias") +
+  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
+  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance level estimated") +
+  theme_bw(base_size = 8) +
+  theme(legend.position = "none")
+
 #INCREASING MEANS DECRESING SD --------------------------------------
+dir_scenario <- "ain1_upmean_downsd"
+
 desired_means <- c(30, 35, 40, 50)
@@
 pars <- desired_mean_sd(mu_x = desired_means, sd_x = desired_sds)
-
 A5 <- mixtures_plot_fx(pars = pars, dens_cols = dens_cols, pis = pis, desired_means = desired_means, desired_sds = desired_sds)
 
-plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
+load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))
+B5 <- bias_bxplot_fx(allin1df)
+
+# PLOT ----------------------------------
+
+nolegBs <- plot_grid(B1, B2, B3, B4, ncol = 1)
+legend_Bs <- get_legend(B4+ theme(legend.position = "right")) 
+Bs <- plot_grid(nolegBs, legend_Bs, ncol = 2, rel_widths = c(1, 0.2))
+
+As <- plot_grid(A1, A2, A3, A4, ncol = 1, labels = "AUTO", label_size = 8)
+
+plot_grid(As, Bs, ncol = 2, rel_widths = c(1, 1.5))
+
 ggsave("Ch3_samplesize/Figures/Many_mixtures.png")
+```
+```{r}
+Bs
 ```

### 2023-08-07 README.Rmd
Deleted little thing
Somehow, my previous README was deleted...

--- 2021-03-19 README.Rmd
@@
 ---
+
+[![DOI](https://zenodo.org/badge/292314570.svg)](https://zenodo.org/badge/latestdoi/292314570)
 
@@
 
-Access the
+My dissertation work is focused on the ecological consequences of individual variation in animal movement, from a modeling perspective.
+I am sharing this whole repository in an effort to keep science open and reproducible.
+All of my analyses and data are included in this repository.
+As of today (March 11, 2022) all three chapters are in the process of editing with coauthors for submission to scientific journals.
+Therefore, everything available on this repository is still a draft/manuscript/or work in progress.
+Please reach out if you have any questions or inquiries.
+I do ask that if you use any of the information within this repo, that you cite it.
+Thank you!
 
-- [seed dispersal paper](https://javirudolph.github.io/aracari/paper/paper.html) and the [figures](https://javirudolph.github.io/aracari/paper/figures_tables.html)
-- [animal movement paper](https://javirudolph.github.io/aracari/movement_paper/rudolph_ch2.html)  
-- [distributions paper](https://javirudolph.github.io/aracari/distributions_paper/rudolph_distributions.html)
+- CH1 - Consequences of incorporating heterogeneity in animal movement rates into models of seed dispersal.
+In this chapter we used a very simple random walk to model seed dispersal by animals in a homogeneous landscape.
+The main question here was whether or not incorporating individual variation in our simulations had an effect on the resulting dispersal kernels.
+We found that it does, and that by incorporating this variation, we allow for dispersal kernels to have fatter tails and increase the number of long-distance seed dispersal events.
+You can find the [Full Text](https://javirudolph.github.io/aracari/Ch1_movement_rates/FJRudolph_Ch1_0311.pdf) or the [Figures](https://javirudolph.github.io/aracari/Ch1_movement_rates/Ch1_Figures.html) and an [Appendix](https://javirudolph.github.io/aracari/Ch1_movement_rates/Ch1_Appendix_A.html)
 
----
-## Installation
+- CH2 - Velocity-Based Analysis of Radio Telemetry Data to Explore Individual Variation in Animal Movement [Full Text](https://javirudolph.github.io/aracari/Ch2_distributions/FJRudolph_CH2_0311.pdf) [Figures](https://javirudolph.github.io/aracari/Ch2_distributions/Ch2_Figures.html)
 
-You can install the development version from [GitHub](https://github.com/) with:
+- CH3 - Estimating Extreme Displacements Under a Lomax Generalized Linear Model Framework: The Role of Sample Size and Threshold Choice.
+[Full Text](https://javirudolph.github.io/aracari/Ch3_samplesize/FJ_Rudolph_CH3_0303.pdf).
 
-``` r
-# install.packages("devtools")
-devtools::install_github("javirudolph/aracari")
-```
+-----
